### 2018-09-18 paper/Paper Title.Rmd
created a rough outline for the paper

---
title: "Paper Title (Something about Applying LIME to Bullet Data)"
author: "Katherine Goode and Heike Hoffman"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background/Literature Review

# Problem Statement

# Overview of LIME

# Explain the Data (TS 224)

# Results (using LIME on a TS)

### 2018-09-19 paper/Paper Title.Rmd
paragraph on test set 224

@@
 title: "Paper Title (Something about Applying LIME to Bullet Data)"
-author: "Katherine Goode and Heike Hoffman"
+author: "Katherine Goode and Heike Hofmann"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 output: pdf_document
+bibliography: references.bib
 ---
@@
 
-# Explain the Data (TS 224)
+# The Hamby 224 Clone
+
+The Hamby 224 Clone is organized as a test set of a cloned (sub-)set of the Hamby 224 bullets.
+As with all Hamby sets [@hamby], Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets.
+The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
+Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet.
+Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
+The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets  or from a different source.
+This situation is similar to what a Firearms and Toolmarks Examiner might encounter in case work.
 
 # Results (using LIME on a TS)
+
+# References

### 2018-09-20 code/01-data cleaning.R
started applying lime to hamby 224

@@ -1,0 +1,62 @@
+## R Code for LIME Bullet Paper
+## Purpose: cleaning the Hamby 224 data
+## Last updated: 2018/09/20
+
+# Load libraries
+library(tidyverse)
+library(bulletr)
+
+# Load in the Hamby 224 datasets
+hamby224_set1 <- readRDS("./data/h224-set1-features.rds")
+hamby224_set11 <- readRDS("./data/h224-set11-features.rds")
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Clean the Hamby 224 set 1 data
+hamby224_set1_cleaned <- hamby224_set1 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby 224"), 
+         set = factor("1"),
+         bullet1 = factor(bullet1),
+         bullet2 = factor(bullet2),
+         land1 = factor(land1),
+         land2 = factor(land2)) %>%
+  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+# Clean the Hamby 224 set 11 data
+hamby224_set11_cleaned <- hamby224_set11 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby 224"), 
+         set = factor("2"),
+         bullet1 = recode(factor(bullet1), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         bullet2 = recode(factor(bullet2), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         land1 = recode(factor(land1), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
+         land2 = recode(factor(land2), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
[…]

### 2018-09-20 code/02-applying lime.R

@@ -1,0 +1,75 @@
+## R Code for LIME Bullet Paper
+## Purpose: applying lime to the hamby 224 bullet data
+## Last updated: 2018/09/20
+
+# Load libraries
+library(bulletr)
+library(lime)
+library(randomForest)
+
+## -----------------------------------------------------------------------
+## Loading Data
+## -----------------------------------------------------------------------
+
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("./data/hamby173and252_train.csv")
+
+# Load in the testing data (Hamby 224 sets 1 and 11)
+hamby224_test <- read.csv("./data/hamby224_test.csv")
+
+## -----------------------------------------------------------------------
+## Applying LIME
+## -----------------------------------------------------------------------
+
+# Apply the lime function from the lime package (with a seed set)
+# Note that the as_classifier must be added since rtrees is from the
+# randomForest package and not fit using caret or one of the other 
+# available models specified in the lime package. Additionally, the
+# randomForest package must be loaded in order to run the functions
+# from the lime package. (I should check on exactly how this works.)
+set.seed(84902)
+hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
+                      model = as_classifier(rtrees))
+
+# Save the lime object
+saveRDS(hamby224_lime, "./data/hamby224_lime.rds")
+
+# Apply the explain function from the lime package (with a seed set)
+set.seed(84902)
+hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
+                                  hamby224_lime, 
+                                  n_labels = 1, 
+                                  n_features = 3)
+
+# Save the explain object
+saveRDS(hamby224_explain, "./data/hamby224_explain.rds")
+
+## -----------------------------------------------------------------------
+## Joining Test Data with Explain Object
+## -----------------------------------------------------------------------
+
+# Add a case variable to the test data
+hamby224_test <- hamby224_test %>%
+  mutate(case = as.character(1:dim(hamby224_test)[1])) %>%
+  select(case, study:samesource)
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Join the data and the explanations and edit and add additional variables
+hamby224_test_explain <- full_join(hamby224_test, hamby224_explain, by = "case") %>%
+  mutate(case = factor(case),
[…]

### 2018-09-20 paper/paper.Rmd
started working on lime plots in paper

---
title: "Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Background/Literature Review

# Problem Statement

# Overview of LIME

# The Hamby 224 Clone

The Hamby 224 Clone is organized as a test set of a cloned (sub-)set of the Hamby 224 bullets. As with all Hamby sets [@hamby], Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets. The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets  or from a different source. This situation is similar to what a Firearms and Toolmarks Examiner might encounter in case work.

# Applying LIME

```{r}
# Read in the Hamby 224 combined test data and explanations
hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")

hamby224_test_explain %>% 
  filter(set == "1") %>% 
  select(case, bullet1:land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)

hamby224_test_explain %>% 
  filter(set == "1") %>% 
  select(case, bullet1:land2, mypred) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = mypred)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)

hamby224_test_explain %>% 
  filter(set == "1") %>% 
  select(case, bullet1:land2, label_prob) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = label_prob)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)

hamby224_test_explain %>% 
  filter(set == "1") %>% 
  select(case, bullet1:land2, samesource) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = samesource)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() 
```

# Results (using LIME on a TS)

# References

### 2018-09-20 code/03-create images.R
started working on saving images

@@ -1,0 +1,16 @@
+## R Code for LIME Bullet Paper
+## Purpose: creating images lime images
+## Last updated: 2018/09/20
+
+# Load libraries 
+library(lime)
+
+# Read in the explanation object
+hamby224_explain <- readRDS("./data/hamby224_explain.rds")
+
+# Read in the combined test data and explanation object
+hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
+
+png("./figures/hamby244_testset1_b1_b1_land1_land1.png")
+plot_features(hamby224_explain[1:3,])
+dev.off()

### 2018-09-24 code/01-data cleaning.R
wrote code for creating plot_feature images

@@ -20,7 +20,7 @@ hamby224_set1_cleaned <- hamby224_set1 %>%
          bullet2 = bulletB, 
          land1 = landA,
          land2 = landB) %>%
-  mutate(study = factor("Hamby 224"), 
+  mutate(study = factor("Hamby_224"), 
          set = factor("1"),
          bullet1 = factor(bullet1),
          bullet2 = factor(bullet2),
@@ -35,7 +35,7 @@ hamby224_set11_cleaned <- hamby224_set11 %>%
          bullet2 = bulletB, 
          land1 = landA,
          land2 = landB) %>%
-  mutate(study = factor("Hamby 224"), 
+  mutate(study = factor("Hamby_224"), 
          set = factor("2"),
          bullet1 = recode(factor(bullet1), 
                           "Bullet 1" = "1", 

### 2018-09-24 code/03-create images.R

@@ -1,9 +1,37 @@
 ## R Code for LIME Bullet Paper
 ## Purpose: creating images lime images
-## Last updated: 2018/09/20
+## Last updated: 2018/09/24
 
 # Load libraries 
 library(lime)
+library(tidyverse)
+
+## -----------------------------------------------------------------------
+## Create the function for saving the figures
+## -----------------------------------------------------------------------
+
+# Function for creating and saving a lime plot_features plot for a specified case
+plot_features_function <- function(case_number, explain, test_explain){
+ 
+  # INPUTS:
+  #   case_number - case number to create the plot for
+  #   explain - a lime explain object
+  #   test_explain - a dataframe of the joined test data and lime explain object
+  
+  # Subset the test_explain data frame to only case one row from the case of interest
+  test_explain_sub <- test_explain %>% 
+    filter(case == case_number) %>% 
+    slice(1)
+  
+  # Create and save the image
+  plot_features(explain %>% filter(case == case_number))
+  ggsave(file = test_explain_sub$figure_file_location)
+  
+}
+
+## -----------------------------------------------------------------------
+## Load and prepare data
+## -----------------------------------------------------------------------
 
 # Read in the explanation object
 hamby224_explain <- readRDS("./data/hamby224_explain.rds")
@@ -11,6 +39,20 @@ hamby224_explain <- readRDS("./data/hamby224_explain.rds")
 # Read in the combined test data and explanation object
 hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
 
-png("./figures/hamby244_testset1_b1_b1_land1_land1.png")
-plot_features(hamby224_explain[1:3,])
-dev.off()
+# Add a variable for the figure file location for each case
+hamby224_test_explain <- hamby224_test_explain %>%
+  mutate(figure_file_location = paste0("./figures/", study, "_testset", set, "_b", bullet1, 
+                                       "_b", bullet2, "_land", land1, "_land", land2, ".png"))
+
+# Save the updated version of the test_explain data
+saveRDS(hamby224_test_explain, "./data/hamby224_test_explain.rds")
+
+## -----------------------------------------------------------------------
+## Create and save the images
+## -----------------------------------------------------------------------
+
+# Apply the plot_features_function to all of the cases in the Hamby 224 dataset
+purrr::map(.x = 1:max(as.numeric(hamby224_test_explain$case)),
+           .f = plot_features_function,
+           explain = hamby224_explain,
+           test_explain = hamby224_test_explain)

### 2018-09-24 paper/paper.Rmd
updated paper structure

@@
 date: "`r format(Sys.time(), '%B %d, %Y')`"
-output: pdf_document
+output: 
+  pdf_document:
+    number_sections: true
 bibliography: references.bib
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
+
+# Load libraries
+library(dplyr)
+library(ggplot2)
 ```
 
-# Background/Literature Review
+# Introduction
 
-# Problem Statement
+- background
+- motivation
+- literature review
+- problem statement
 
-# Overview of LIME
+# Data
 
-# The Hamby 224 Clone
+## Training Data: The Hamby...
+
+## Testing Data: The Hamby 224 Clone
 
@@
 
-# Applying LIME
+#  Methods
+
+## Random Forest Model
+
+## Overview of LIME
+
+## Applying LIME
+
+## Visualizing the LIME Explanations
 
@@
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+```
 
+```{r}
 hamby224_test_explain %>%
@@
 
-# Results (using LIME on a TS)
+# Results
+
+# Discussion
 

### 2018-09-25 paper/paper.Rmd
worked on intro to paper

@@
 library(ggplot2)
+library(lime)
 ```
@@
 
+Bullet matching is a practice that has historically been performed by hand by specially trained firearm examiners.
+The examiners visually assess the striation markings on the bullets under a high powered microscope to determine whether the bullets were fired from the same gun barrel.
+In more recent times, the scientific community has been calling for the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of an uncertainty along with the conclusion drawn from the analysis.
+
+This led Hare, Hofmann, and Carriquiry (2017) to propose a new computer automated method of bullet matching.
+The method involves obtaining a bullet signature from a scan of the bullet, computing a handful of variables that measure the similarity between two signatures, and fitting a random forest model to the obtained similarity variables.
+The model can be trained on a set of known bullet matches and non-matches and used to predict on a new set of bullet signature comparisons.
+The results from the paper suggest that the random forest model leads to accurate bullet matching predictions.
+The authors found that when their model was applied to a testing dataset (?), the resulting error rate was 0%.
+
+While random forest models often result in good predictions (reference?), it well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to understand which variables played an important role in the creation of the predictions.
+This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction.
+
+Bullet matching is commonly used as evidence for convictions in court cases.
+Thus, it is important to not only provide accurate predictions and an associated uncertainty level but also to explain which variables were important in making the prediction.
+This paper applies LIME to the random forest model used for bullet matching to assess which variables are driving the predictions made by the model.
+
 # Data
@@
 ## Training Data: The Hamby...
+
+(fill in once we know which data will be used to train the new random forest model)
 
@@
 ## Random Forest Model
+
+(fill in once the new random forest model has been fit)
 
@@
 
+```{r}
+hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+
+lime::plot_explanations(hamby224_explain)
+
+hamby224_test_explain %>%
+  filter(set == "1") %>%
+  ggplot(aes(x = case, y = feature_desc)) + 
+  geom_tile(aes(fill = feature_weight)) + 
+  facet_grid(feature ~ label, space = "free", scale = "free") + 
+  theme(axis.text.x = element_text(angle = 90)) +
+  scale_fill_gradient2(midpoint = 0)
+
+hamby224_test_explain %>%
+  filter(set == "1", samesource == "FALSE") %>%
+  ggplot(aes(x = case, y = feature_desc)) + 
+  geom_tile(aes(fill = feature_weight)) + 
+  facet_grid(feature ~ bullet1, space = "free", scale = "free") + 
+  theme(axis.text.x = element_text(angle = 90)) +
+  scale_fill_gradient2(midpoint = 0)
+
+hamby224_test_explain %>%
+  filter(set == "1", samesource == "FALSE") %>%
+  ggplot(aes(x = case, y = feature_desc)) + 
+  geom_tile(aes(fill = feature_weight)) + 
+  facet_grid(bullet1 ~ bullet2, space = "free", scale = "free") + 
+  theme(axis.text.x = element_text(angle = 90)) +
+  scale_fill_gradient2(midpoint = 0)
+```
+
 # Results

### 2018-09-25 paper/paper.Rmd
figure height and width

@@
 
+Some plots to tryout working with the new explanations...
+
 ```{r}
@@
 
-```{r}
+```{r, fig.width = 8, fig.height = 4}
 hamby224_explain <- readRDS("../data/hamby224_explain.rds")
@@
   theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0)
+  scale_fill_gradient2(midpoint = 0) +
+  theme(legend.position = "bottom")
 ```

### 2018-09-25 code/01b-sort categories.R
ordering levels

@@ -1,0 +1,26 @@
+library(tidyverse)
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+
+hamby224_test_explain$feature_desc <- 
+  factor(hamby224_test_explain$feature_desc)
+
+hamby224_test_explain$feature <- 
+  factor(hamby224_test_explain$feature)
+
+hamby224_test_explain$feature_number <- readr::parse_number(hamby224_test_explain$feature_desc)
+hamby224_test_explain$strictly_less <- FALSE
+hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
+
+hamby224_test_explain <- hamby224_test_explain %>%
+  mutate(
+    feature_desc = reorder(feature_desc, strictly_less),
+    feature_desc = reorder(feature_desc, feature_number),
+    feature_desc = reorder(feature_desc, as.numeric(feature))
+  )
+  
+hamby224_test_explain %>%
+  ggplot(aes(x = feature_desc)) + geom_bar() +
+  coord_flip()
+
+ 
+saveRDS(hamby224_test_explain, file="../data/hamby224_test_explain.rds")

### 2018-09-25 paper/paper.Rmd
added sentence
moving legend

@@
   theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0)
+  scale_fill_gradient2(midpoint = 0) +
+  theme(legend.position = "bottom") +
+  ylab("Feature Sets")
 

### 2018-10-12 code/01-data cleaning.R
moved code into r markdown

@@ -1,62 +1,0 @@
-## R Code for LIME Bullet Paper
-## Purpose: cleaning the Hamby 224 data
-## Last updated: 2018/09/20
-
-# Load libraries
-library(tidyverse)
-library(bulletr)
-
-# Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("./data/h224-set1-features.rds")
-hamby224_set11 <- readRDS("./data/h224-set11-features.rds")
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
-
-# Clean the Hamby 224 set 1 data
-hamby224_set1_cleaned <- hamby224_set1 %>%
-  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-  rename(bullet1 = bulletA,
-         bullet2 = bulletB, 
-         land1 = landA,
-         land2 = landB) %>%
-  mutate(study = factor("Hamby_224"), 
-         set = factor("1"),
-         bullet1 = factor(bullet1),
-         bullet2 = factor(bullet2),
-         land1 = factor(land1),
-         land2 = factor(land2)) %>%
-  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
-
-# Clean the Hamby 224 set 11 data
-hamby224_set11_cleaned <- hamby224_set11 %>%
-  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-  rename(bullet1 = bulletA,
-         bullet2 = bulletB, 
-         land1 = landA,
-         land2 = landB) %>%
-  mutate(study = factor("Hamby_224"), 
-         set = factor("2"),
-         bullet1 = recode(factor(bullet1), 
-                          "Bullet 1" = "1", 
-                          "Bullet 2" = "2", 
-                          "Bullet I" = "I"),
-         bullet2 = recode(factor(bullet2), 
-                          "Bullet 1" = "1", 
-                          "Bullet 2" = "2", 
-                          "Bullet I" = "I"),
-         land1 = recode(factor(land1), 
-                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
-                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
-         land2 = recode(factor(land2), 
-                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
[…]

### 2018-10-12 code/02-applying lime.R

@@ -1,75 +1,0 @@
-## R Code for LIME Bullet Paper
-## Purpose: applying lime to the hamby 224 bullet data
-## Last updated: 2018/09/20
-
-# Load libraries
-library(bulletr)
-library(lime)
-library(randomForest)
-
-## -----------------------------------------------------------------------
-## Loading Data
-## -----------------------------------------------------------------------
-
-# Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("./data/hamby173and252_train.csv")
-
-# Load in the testing data (Hamby 224 sets 1 and 11)
-hamby224_test <- read.csv("./data/hamby224_test.csv")
-
-## -----------------------------------------------------------------------
-## Applying LIME
-## -----------------------------------------------------------------------
-
-# Apply the lime function from the lime package (with a seed set)
-# Note that the as_classifier must be added since rtrees is from the
-# randomForest package and not fit using caret or one of the other 
-# available models specified in the lime package. Additionally, the
-# randomForest package must be loaded in order to run the functions
-# from the lime package. (I should check on exactly how this works.)
-set.seed(84902)
-hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
-                      model = as_classifier(rtrees))
-
-# Save the lime object
-saveRDS(hamby224_lime, "./data/hamby224_lime.rds")
-
-# Apply the explain function from the lime package (with a seed set)
-set.seed(84902)
-hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
-                                  hamby224_lime, 
-                                  n_labels = 1, 
-                                  n_features = 3)
-
-# Save the explain object
-saveRDS(hamby224_explain, "./data/hamby224_explain.rds")
-
-## -----------------------------------------------------------------------
-## Joining Test Data with Explain Object
-## -----------------------------------------------------------------------
-
-# Add a case variable to the test data
-hamby224_test <- hamby224_test %>%
-  mutate(case = as.character(1:dim(hamby224_test)[1])) %>%
-  select(case, study:samesource)
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
-
-# Join the data and the explanations and edit and add additional variables
-hamby224_test_explain <- full_join(hamby224_test, hamby224_explain, by = "case") %>%
-  mutate(case = factor(case),
[…]

### 2018-10-12 code/02b-sort categories.R

@@ -1,26 +1,0 @@
-library(tidyverse)
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-hamby224_test_explain$feature_desc <- 
-  factor(hamby224_test_explain$feature_desc)
-
-hamby224_test_explain$feature <- 
-  factor(hamby224_test_explain$feature)
-
-hamby224_test_explain$feature_number <- readr::parse_number(hamby224_test_explain$feature_desc)
-hamby224_test_explain$strictly_less <- FALSE
-hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
-
-hamby224_test_explain <- hamby224_test_explain %>%
-  mutate(
-    feature_desc = reorder(feature_desc, strictly_less),
-    feature_desc = reorder(feature_desc, feature_number),
-    feature_desc = reorder(feature_desc, as.numeric(feature))
-  )
-  
-hamby224_test_explain %>%
-  ggplot(aes(x = feature_desc)) + geom_bar() +
-  coord_flip()
-
- 
-saveRDS(hamby224_test_explain, file="../data/hamby224_test_explain.rds")

### 2018-10-12 paper/paper.Rmd
moved code to paper

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE, cache = TRUE)
 
 # Load libraries
-library(dplyr)
-library(ggplot2)
+library(tidyverse)
+library(bulletr)
 library(lime)
+library(randomForest)
 ```
@@
 
+```{r echo = FALSE}
+
+# Cleaning the Hamby 224 data -------------------------------------------------
+
+# Load in the Hamby 224 datasets
+hamby224_set1 <- readRDS("../data/h224-set1-features.rds")
+hamby224_set11 <- readRDS("../data/h224-set11-features.rds")
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Clean the Hamby 224 set 1 data
+hamby224_set1_cleaned <- hamby224_set1 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby_224"), 
+         set = factor("1"),
+         bullet1 = factor(bullet1),
+         bullet2 = factor(bullet2),
+         land1 = factor(land1),
+         land2 = factor(land2)) %>%
+  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+# Clean the Hamby 224 set 11 data
+hamby224_set11_cleaned <- hamby224_set11 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby_224"), 
+         set = factor("2"),
+         bullet1 = recode(factor(bullet1), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         bullet2 = recode(factor(bullet2), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         land1 = recode(factor(land1), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
+         land2 = recode(factor(land2), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6")) %>%
+  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+# Join the two cleaned Hamby 224 sets into one testing set
+hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
+                                            hamby224_set11_cleaned))
+```
+
 ## Random Forest Model
@@
 
+```{r echo = FALSE}
+
+# Applying LIME -------------------------------------------------
+
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+
+# Apply the lime function from the lime package (with a seed set)
+# Note that the as_classifier must be added since rtrees is from the
+# randomForest package and not fit using caret or one of the other 
+# available models specified in the lime package. Additionally, the
+# randomForest package must be loaded in order to run the functions
+# from the lime package. (I should check on exactly how this works.)
+set.seed(84902)
+hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
+                      model = as_classifier(rtrees))
+
+# Apply the explain function from the lime package (with a seed set)
+set.seed(84902)
+hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
+                                  hamby224_lime, 
+                                  n_labels = 1, 
+                                  n_features = 3)
+
+# Add a case variable to the test data
+hamby224_test <- hamby224_test %>%
+  mutate(case = as.character(1:dim(hamby224_test)[1])) %>%
+  select(case, study:samesource)
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Join the data and the explanations and edit and add additional variables
+hamby224_test_explain <- full_join(hamby224_test, hamby224_explain, by = "case") %>%
+  mutate(case = factor(case),
+         set = factor(set),
+         bullet1 = factor(bullet1),
+         bullet2 = factor(bullet2),
+         land1 = factor(land1),
+         land2 = factor(land2)) %>%
+  mutate(mypred = rep(predict(rtrees, hamby224_test %>% select(rf_features), 
+                              type = "prob")[,2], each = 3)) %>%
+  select(case:rfscore, mypred, samesource:prediction)
+
+hamby224_test_explain$feature_desc <- factor(hamby224_test_explain$feature_desc)
+hamby224_test_explain$feature <- factor(hamby224_test_explain$feature)
+
+hamby224_test_explain$feature_number <- readr::parse_number(hamby224_test_explain$feature_desc)
+hamby224_test_explain$strictly_less <- FALSE
+hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
+
+hamby224_test_explain <- hamby224_test_explain %>%
+  mutate(
+    feature_desc = reorder(feature_desc, strictly_less),
+    feature_desc = reorder(feature_desc, feature_number),
+    feature_desc = reorder(feature_desc, as.numeric(feature))
+  )
+```
+
 ## Visualizing the LIME Explanations
@@
 ```{r}
-# Read in the Hamby 224 combined test data and explanations
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-```
+hamby224_test_explain %>%
+  ggplot(aes(x = feature_desc)) + 
+  geom_bar() +
+  coord_flip()
 
-```{r}
 hamby224_test_explain %>%

### 2018-10-15 paper/paper.Rmd
updated code in paper to save important objects (again)

--- 2018-09-25 paper/paper.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)
 
 # Load libraries
-library(dplyr)
-library(ggplot2)
+library(tidyverse)
+library(bulletr)
 library(lime)
+library(randomForest)
 ```
@@
 
-Bullet matching is a practice that has historically been performed by hand by specially trained firearm examiners.
+The process of matching bullets to the gun that shot the bullet has traditionally been performed by hand by specially trained firearm examiners.
 The examiners visually assess the striation markings on the bullets under a high powered microscope to determine whether the bullets were fired from the same gun barrel.
-In more recent times, the scientific community has been calling for the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of an uncertainty along with the conclusion drawn from the analysis.
+Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of an uncertainty along with the conclusion drawn from the analysis.
 
@@
 
+```{r}
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+```
+
 ## Testing Data: The Hamby 224 Clone
@@
 This situation is similar to what a Firearms and Toolmarks Examiner might encounter in case work.
+
+```{r}
+# Load in the Hamby 224 datasets
+hamby224_set1 <- readRDS("../data/h224-set1-features.rds")
+hamby224_set11 <- readRDS("../data/h224-set11-features.rds")
+```
+
+```{r}
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Clean the Hamby 224 set 1 data
+hamby224_set1_cleaned <- hamby224_set1 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby_224"), 
+         set = factor("1"),
+         bullet1 = factor(bullet1),
+         bullet2 = factor(bullet2),
+         land1 = factor(land1),
+         land2 = factor(land2)) %>%
+  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+# Clean the Hamby 224 set 11 data
+hamby224_set11_cleaned <- hamby224_set11 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
+  mutate(study = factor("Hamby_224"), 
+         set = factor("2"),
+         bullet1 = recode(factor(bullet1), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         bullet2 = recode(factor(bullet2), 
+                          "Bullet 1" = "1", 
+                          "Bullet 2" = "2", 
+                          "Bullet I" = "I"),
+         land1 = recode(factor(land1), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
+         land2 = recode(factor(land2), 
+                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6")) %>%
+  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+# Join the two cleaned Hamby 224 sets into one testing set
+hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
+                                            hamby224_set11_cleaned))
+
+# Save the test data as a .csv file
+write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)
+```
 
@@
 
+```{r echo = FALSE}
+# Apply the lime function from the lime package (with a seed set)
+# Note that the as_classifier must be added since rtrees is from the
+# randomForest package and not fit using caret or one of the other 
+# available models specified in the lime package. Additionally, the
+# randomForest package must be loaded in order to run the functions
+# from the lime package. (I should check on exactly how this works.)
+set.seed(84902)
+hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
+                      model = as_classifier(rtrees))
+
+# Save the lime object
+saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
+```
+
+```{r}
+# Apply the explain function from the lime package (with a seed set)
+set.seed(84902)
+hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
+                                  hamby224_lime, 
+                                  n_labels = 1, 
+                                  n_features = 3)
+
+# Save the explainer object
+saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
+```
+
+```{r echo = FALSE}
+# Add a case variable to the test data
+hamby224_test <- hamby224_test %>%
+  mutate(case = as.character(1:dim(hamby224_test)[1])) %>%
+  select(case, study:samesource)
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+
+# Join the data and the explanations and edit and add additional variables
+hamby224_test_explain <- full_join(hamby224_test, hamby224_explain, by = "case") %>%
+  mutate(case = factor(case),
+         set = factor(set),
+         bullet1 = factor(bullet1),
+         bullet2 = factor(bullet2),
+         land1 = factor(land1),
+         land2 = factor(land2)) %>%
+  mutate(mypred = rep(predict(rtrees, hamby224_test %>% select(rf_features), 
+                              type = "prob")[,2], each = 3)) %>%
+  select(case:rfscore, mypred, samesource:prediction) %>%
+  mutate(feature_desc = factor(feature_desc),
+         feature = factor(feature)) %>%
+  mutate(feature_number = readr::parse_number(feature_desc),
+         strictly_less = FALSE)
+
+# Finish creating the strictly less than variable
+hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
+
+# Reorder the variable of feature_desc for plotting purposes
+hamby224_test_explain <- hamby224_test_explain %>%
+  mutate(
+    feature_desc = reorder(feature_desc, strictly_less),
+    feature_desc = reorder(feature_desc, feature_number),
+    feature_desc = reorder(feature_desc, as.numeric(feature))
+  )
+
+# Save the combined test and explain data
+saveRDS(hamby224_test_explain, "../data/hamby224_test_explain.rds")
+```
+
 ## Visualizing the LIME Explanations
@@
 ```{r}
-# Read in the Hamby 224 combined test data and explanations
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_test_explain %>%
+  ggplot(aes(x = feature_desc)) + 
+  geom_bar() +
+  coord_flip()
 ```
@@
   scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)
+```
 
-hamby224_test_explain %>%
-  filter(set == "1") %>%
-  select(case, bullet1:land2, mypred) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2)) +
-  geom_tile(aes(fill = mypred)) +
-  facet_grid(bullet1 ~ bullet2) +
-  theme_bw() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)
-
-hamby224_test_explain %>%
-  filter(set == "1") %>%
-  select(case, bullet1:land2, label_prob) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2)) +
-  geom_tile(aes(fill = label_prob)) +
-  facet_grid(bullet1 ~ bullet2) +
-  theme_bw() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)
-
+```{r}
 hamby224_test_explain %>%
@@
 ```{r, fig.width = 8, fig.height = 4}
-hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+lime::plot_explanations(hamby224_explain)
+```
 
-lime::plot_explanations(hamby224_explain)
-
+```{r}
 hamby224_test_explain %>%
@@
   theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0)
+  scale_fill_gradient2(midpoint = 0) +
+  theme(legend.position = "bottom") +
+  ylab("Feature Sets") 
+```
 
+```{r}
 hamby224_test_explain %>%
@@
   scale_fill_gradient2(midpoint = 0)
+```
 
+```{r}
 hamby224_test_explain %>%

### 2018-10-16 paper/paper.Rmd
started creating the Shiny app

@@
 ```{r setup, include = FALSE}
+# Set knitr options
 knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)
@@
   mutate(study = factor("Hamby_224"), 
-         set = factor("2"),
+         set = factor("11"),
          bullet1 = recode(factor(bullet1), 

### 2018-10-16 bullet_explanations_app/app.R

@@ -1,0 +1,89 @@
+## The beginning of a Shiny app for visualizing the LIME explanations
+
+# Load libraries
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(plotly)
+library(lime)
+
+# Input data
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+   
+   # Application title
+   titlePanel("LIME Explanations for Bullet Matching"),
+   
+   # Sidebar with a slider input for number of bins 
+   sidebarLayout(
+      sidebarPanel(h1("Test Datasets"),
+          selectInput("testset", 
+                      label = "Select a Hamby 224 test dataset", 
+                      choices = c("Set 1", "Set 11"))
+      ),
+      
+      # Show a plot of the generated distribution
+      mainPanel(h1("Plots"),
+                plotlyOutput("tileplot"),
+                plotOutput("featureplot")
+                )
+   )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+  
+  # Create the tile plot
+  output$tileplot <- renderPlotly({
+    
+    # Grab the number of the chosen test set
+    chosen = unlist(strsplit(input$testset, split = " "))[2]
+    
+    # Create a tile plot of the random forest predictions for all land comparisons
+    hamby224_test_explain %>%
+      filter(set == chosen) %>%
+      select(case, bullet1:land2, rfscore) %>%
+      distinct() %>%
+      ggplot(aes(x = land1, y = land2)) +
+      geom_tile(aes(fill = rfscore)) +
+      facet_grid(bullet1 ~ bullet2) +
+      theme_bw() +
+      scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+      labs(x = "Land 1", y = "Land 2", fill = "RF Score", 
+           title = paste0("Hamby 224 Data (", input$testset, ")"))
+    
+  })
+  
+  # Create the feature plot
+  output$featureplot <- renderPlot({
+    
+    # Grab the number of the chosen test set
+    chosen = unlist(strsplit(input$testset, split = " "))[2]
+
+    # Create the LIME features plot
+    plot_features(hamby224_test_explain %>% filter(set == chosen) %>% slice(1:3))
+
+  })
+    
+}
[…]

### 2018-10-16 bullet_explanations_app/app.R
added my own feature plot

@@ -27,7 +27,8 @@ ui <- fluidPage(
       # Show a plot of the generated distribution
       mainPanel(h1("Plots"),
                 plotlyOutput("tileplot"),
-                plotOutput("featureplot")
+                plotOutput("featureplot"),
+                plotOutput("myfeatureplot")
                 )
    )
 )
@@ -65,6 +66,38 @@ server <- function(input, output) {
     # Create the LIME features plot
     plot_features(hamby224_test_explain %>% filter(set == chosen) %>% slice(1:3))
 
+  })
+  
+  # Create my own feature plot
+  output$myfeatureplot <- renderPlot({
+    
+    # Grab the number of the chosen test set
+    chosen = unlist(strsplit(input$testset, split = " "))[2]
+    
+    try <- hamby224_test_explain %>%
+      filter(set == chosen) %>%
+      slice(1:3) %>%
+      mutate(feature_desc = reorder(feature_desc, as.numeric(feature_weight)),
+             evidence = if_else(feature_weight >= 0, "Supports", "Contradicts"))
+    
+    tryinfo <- try %>% 
+      slice(1) %>%
+      select(study, set, bullet1, bullet2, land1, land2)
+    
+    ggplot(try, aes(x = feature_desc, y = feature_weight)) + 
+      geom_col(aes(fill = evidence)) + 
+      coord_flip() + 
+      theme_minimal() +
+      theme(legend.position = "bottom") +
+      labs(x = "Feature Weight", y = "Feature Bin", fill = "Evidence:",
+           title = paste0("Lime Explanation for \n", 
+                          "   Study: ", tryinfo$study, "\n",
+                          "   Set: ", tryinfo$set, "\n",
+                          "   1st Bullet: ", tryinfo$bullet1, "\n",
+                          "   Second Bullet: ", tryinfo$bullet2, "\n",
+                          "   First Land: ", tryinfo$land1, "\n",
+                          "   Second Land: ", tryinfo$land2, "\n"))
+    
   })
     
 }

### 2018-10-16 bullet_explanations_app/app.R
some attempted updates to the app

@@ -10,6 +10,20 @@ library(lime)
 # Input data
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 
+# tiny1 <- data.frame(expand.grid(land1 = factor(1:6),
+#                                land2 = factor(1:6), 
+#                                bullet1 = factor(c("1", "2", "Q")),
+#                                bullet2 = factor(c("1", "2", "Q"))))
+# 
+# tiny2 <- data.frame(expand.grid(land1 = factor(1:6),
+#                                land2 = factor(1:6), 
+#                                bullet1 = factor(c("1", "2", "I")),
+#                                bullet2 = factor(c("1", "2", "I"))))
+# 
+# tiny <- rbind(tiny1, tiny2)
+# 
+# hamby224_test_explain <- left_join(tiny, hamby224_test_explain, by = c("land1", "land2", "bullet1", "bullet2"))
+
 # Define UI for application that draws a histogram
 ui <- fluidPage(
    
@@ -27,6 +41,7 @@ ui <- fluidPage(
       # Show a plot of the generated distribution
       mainPanel(h1("Plots"),
                 plotlyOutput("tileplot"),
+                verbatimTextOutput("click"),
                 plotOutput("featureplot"),
                 plotOutput("myfeatureplot")
                 )
@@ -43,11 +58,12 @@ server <- function(input, output) {
     chosen = unlist(strsplit(input$testset, split = " "))[2]
     
     # Create a tile plot of the random forest predictions for all land comparisons
-    hamby224_test_explain %>%
+    plot <- hamby224_test_explain %>%
       filter(set == chosen) %>%
       select(case, bullet1:land2, rfscore) %>%
       distinct() %>%
-      ggplot(aes(x = land1, y = land2)) +
+      mutate(rfscore = replace(rfscore, is.na(rfscore), -1)) %>%
+      ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2, key = case)) +
       geom_tile(aes(fill = rfscore)) +
       facet_grid(bullet1 ~ bullet2) +
       theme_bw() +
@@ -55,21 +71,42 @@ server <- function(input, output) {
       labs(x = "Land 1", y = "Land 2", fill = "RF Score", 
            title = paste0("Hamby 224 Data (", input$testset, ")"))
     
+    ggplotly(plot, source = "tileplot")
+    
   })
-  
+
+  output$click <- renderPrint({
[…]

### 2018-10-18 bullet_explanations_app/app.R
added NA rows to the app data

@@ -10,19 +10,22 @@ library(lime)
 # Input data
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 
-# tiny1 <- data.frame(expand.grid(land1 = factor(1:6),
-#                                land2 = factor(1:6), 
-#                                bullet1 = factor(c("1", "2", "Q")),
-#                                bullet2 = factor(c("1", "2", "Q"))))
-# 
-# tiny2 <- data.frame(expand.grid(land1 = factor(1:6),
-#                                land2 = factor(1:6), 
-#                                bullet1 = factor(c("1", "2", "I")),
-#                                bullet2 = factor(c("1", "2", "I"))))
-# 
-# tiny <- rbind(tiny1, tiny2)
-# 
-# hamby224_test_explain <- left_join(tiny, hamby224_test_explain, by = c("land1", "land2", "bullet1", "bullet2"))
+# Create a dataset with all combinations of lands and bullets for each set
+perms1 <- data.frame(set = factor(1),
+                    expand.grid(land1 = factor(1:6),
+                                land2 = factor(1:6),
+                                bullet1 = factor(c("1", "2", "Q")),
+                                bullet2 = factor(c("1", "2", "Q"))))
+perms11 <- data.frame(set = factor(11),
+                    expand.grid(land1 = factor(1:6),
+                                land2 = factor(1:6), 
+                                bullet1 = factor(c("1", "2", "I")),
+                                bullet2 = factor(c("1", "2", "I"))))
+perms <- rbind(perms1, perms11)
+
+# Join the combinations and the data so that all combinations have a row in the data
+hamby224_test_explain_NAs <- left_join(perms, hamby224_test_explain,
+                                       by = c("set", "land1", "land2", "bullet1", "bullet2"))
 
 # Define UI for application that draws a histogram
 ui <- fluidPage(
@@ -42,9 +45,7 @@ ui <- fluidPage(
       mainPanel(h1("Plots"),
                 plotlyOutput("tileplot"),
                 verbatimTextOutput("click"),
-                plotOutput("featureplot"),
-                plotOutput("myfeatureplot")
-                )
+                plotOutput("featureplot"))
    )
 )
 
[…]

### 2018-10-18 bullet_explanations_app/app.R
got click function to work in app and worked on the layout

@@ -7,25 +7,33 @@ library(dplyr)
 library(plotly)
 library(lime)
 
-# Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+## ------------------------------------------------------------------------------------
+## Data steps
+## ------------------------------------------------------------------------------------
 
-# Create a dataset with all combinations of lands and bullets for each set
-perms1 <- data.frame(set = factor(1),
+# Input data
+hamby224_test_explain <<- readRDS("../data/hamby224_test_explain.rds")
+
+# Create a dataset with all combinations of lands and bullets comparisons for each set
+combs1 <- data.frame(set = factor(1),
                     expand.grid(land1 = factor(1:6),
                                 land2 = factor(1:6),
                                 bullet1 = factor(c("1", "2", "Q")),
                                 bullet2 = factor(c("1", "2", "Q"))))
-perms11 <- data.frame(set = factor(11),
+combs11 <- data.frame(set = factor(11),
                     expand.grid(land1 = factor(1:6),
                                 land2 = factor(1:6), 
                                 bullet1 = factor(c("1", "2", "I")),
                                 bullet2 = factor(c("1", "2", "I"))))
-perms <- rbind(perms1, perms11)
+combs <- rbind(combs1, combs11)
 
 # Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(perms, hamby224_test_explain,
+hamby224_test_explain_NAs <<- left_join(combs, hamby224_test_explain,
                                        by = c("set", "land1", "land2", "bullet1", "bullet2"))
+
+## ------------------------------------------------------------------------------------
+## UI setup
+## ------------------------------------------------------------------------------------
 
 # Define UI for application that draws a histogram
 ui <- fluidPage(
@@ -33,21 +41,23 @@ ui <- fluidPage(
    # Application title
    titlePanel("LIME Explanations for Bullet Matching"),
    
-   # Sidebar with a slider input for number of bins 
-   sidebarLayout(
-      sidebarPanel(h1("Test Datasets"),
-          selectInput("testset", 
-                      label = "Select a Hamby 224 test dataset", 
-                      choices = c("Set 1", "Set 11"))
-      ),
-      
-      # Show a plot of the generated distribution
-      mainPanel(h1("Plots"),
-                plotlyOutput("tileplot"),
[…]

### 2018-10-23 app/app.R
changed name of app folder

@@ -12,7 +12,7 @@ library(lime)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <<- readRDS("../data/hamby224_test_explain.rds")
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 
 # Create a dataset with all combinations of lands and bullets comparisons for each set
 combs1 <- data.frame(set = factor(1),
@@ -28,7 +28,7 @@ combs11 <- data.frame(set = factor(11),
 combs <- rbind(combs1, combs11)
 
 # Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <<- left_join(combs, hamby224_test_explain,
+hamby224_test_explain_NAs <- left_join(combs, hamby224_test_explain,
                                        by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
   mutate(bullet1 = forcats::fct_recode(bullet1, "bullet 1" = "1", "bullet 2" = "2", 
                                        "bullet Q" = "Q", "bullet I" = "I"),
@@ -48,12 +48,12 @@ ui <- fluidPage(
    fluidRow(column(3, selectInput("testset", 
                         label = "Select a Hamby 224 dataset", 
                         choices = c("Set 1", "Set 11")))),
-   
-   # fluidRow(column(3, selectInput("testset", 
-   #                                label = "Select a Hamby 224 test dataset", 
-   #                                choices = c("Set 1", "Set 11"))),
-   #          column(3, verbatimTextOutput("click"))),
-   
+
+   # fluidRow(column(3, selectInput("testset",
+   #                                 label = "Select a Hamby 224 test dataset",
+   #                                 choices = c("Set 1", "Set 11"))),
+   #           column(3, verbatimTextOutput("click"))),
+
    fluidRow(column(6, plotlyOutput("tileplot")),
             column(6, plotOutput("featureplot")))
    
@@ -89,12 +89,12 @@ server <- function(input, output) {
     
   })
   
-  # # Print the values of the event data
+  # Print the values of the event data
   # output$click <- renderPrint({
-  #   
+  # 
   #   # Obtain the click data
   #   click_data <- event_data("plotly_click", source = "tileplot")
-  #   
+  # 
   #   # Print selected comparison
   #   if(length(click_data) > 0) click_data else "nothing selected"
   # 
@@ -104,7 +104,7 @@ server <- function(input, output) {
[…]

### 2018-10-23 paper/paper.Rmd
worked a bit more on introduction (need to keep working on this)

@@
 ---
-title: "Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)"
+title: "Interpreting Random Forest Predictions for Firearm Identification Using LIME"
 author: "Katherine Goode and Heike Hofmann"
@@
 
-- background
-- motivation
-- literature review
-- problem statement
+The discipline of firearm identification examines bullets to determine the likelihood that a bullet found in a criminal case was fired from a particular gun.
+This is a procedure that has traditionally been performed by hand.
+Specially trained examiners visually assess the striations on the unknown bullet from the crime that were created when the bullet passed through the gun barrel to those on a known bullet that was fired from the gun under evalution.
+Often a comparison microscope is used that allows the examiners to view both bullets at the same time (National Research Counci 2009).
+The examiners use the ability to compare the two bullets to determine whether the two bullets were fired from the same gun barrel.
 
-The process of matching bullets to the gun that shot the bullet has traditionally been performed by hand by specially trained firearm examiners.
-The examiners visually assess the striation markings on the bullets under a high powered microscope to determine whether the bullets were fired from the same gun barrel.
-Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of an uncertainty along with the conclusion drawn from the analysis.
-
+Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of a measure of uncertainty in addition to the conclusion drawn from the analysis.
 This led Hare, Hofmann, and Carriquiry (2017) to propose a new computer automated method of bullet matching.
-The method involves obtaining a bullet signature from a scan of the bullet, computing a handful of variables that measure the similarity between two signatures, and fitting a random forest model to the obtained similarity variables.
-The model can be trained on a set of known bullet matches and non-matches and used to predict on a new set of bullet signature comparisons.
-The results from the paper suggest that the random forest model leads to accurate bullet matching predictions.
+The method involves obtaining bullet signatures from the scans of the two bullets, computing a handful of variables that measure the similarity between two signatures, and fitting a random forest model to the similarity variables.
+The model can be trained on a set of known bullet matches and non-matches.
+Then it can be used to predict on a new set of bullet signature comparisons.
+The results from the paper suggest that the random forest model leads to highly accurate bullet matching predictions.
 The authors found that when their model was applied to a testing dataset (?), the resulting error rate was 0%.
 
-While random forest models often result in good predictions (reference?), it well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to understand which variables played an important role in the creation of the predictions.
-This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction.
+While random forest models often result in good predictions, it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
+For example, it is not possible to tell which variables played an important role in the creation of individual predictions.
+This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction using a linear model.
+This allows for the ability to understand which were the driving variables in a prediction of interest.
 
-Bullet matching is commonly used as evidence for convictions in court cases.
-Thus, it is important to not only provide accurate predictions and an associated uncertainty level but also to explain which variables were important in making the prediction.
-This paper applies LIME to the random forest model used for bullet matching to assess which variables are driving the predictions made by the model.
+Since firearm identification identification is commonly used as evidence for convictions in court cases, it is important to not only provide accurate predictions and an associated uncertainty level but also to understand which variables were important in making the prediction.
+Firearm examiners could use LIME to check whether or not the predictions created by LIME are reasonable.
+This paper provides an example of the application of LIME to an updated version of the random forest model from the Hare paper used for bullet matching.
 

### 2018-10-23 paper/paper.Rmd
worked more on introduction

@@
 
+(need to finish adding sources)
+
 The discipline of firearm identification examines bullets to determine the likelihood that a bullet found in a criminal case was fired from a particular gun.
-This is a procedure that has traditionally been performed by hand.
-Specially trained examiners visually assess the striations on the unknown bullet from the crime that were created when the bullet passed through the gun barrel to those on a known bullet that was fired from the gun under evalution.
-Often a comparison microscope is used that allows the examiners to view both bullets at the same time (National Research Counci 2009).
-The examiners use the ability to compare the two bullets to determine whether the two bullets were fired from the same gun barrel.
+To do this, the bullet from the crime will be compared with a bullet that was known to be fired from the gun under evaluation.
+Traditionally, this is a procedure that has been performed by hand.
+Specially trained examiners visually compare the microscopoic bullet striations that were created when the bullets passed through the gun barrel.
+Often a comparison microscope is used that allows the examiners to view both bullets at the same time (National Research Council 2009).
+The examiners use this ability to determine whether the two bullets were fired from the same gun barrel.
 
-Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations that would allow for the reporting of a measure of uncertainty in addition to the conclusion drawn from the analysis.
-This led Hare, Hofmann, and Carriquiry (2017) to propose a new computer automated method of bullet matching.
-The method involves obtaining bullet signatures from the scans of the two bullets, computing a handful of variables that measure the similarity between two signatures, and fitting a random forest model to the similarity variables.
-The model can be trained on a set of known bullet matches and non-matches.
-Then it can be used to predict on a new set of bullet signature comparisons.
+Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations.
+These methods would allow for the reporting of a measure of uncertainty in addition to the conclusion drawn from the analysis.
+This led Hare, Hofmann, and Carriquiry (2017) to propose a new computer automated method of bullet matching that could supplement the visual inspection by the firearm examiners.
+Their method involves obtaining bullet signatures of the striations from the scans of the two bullets, computing variables that measure the similarity of the two signatures, and using a trained random forest model to determine the probability of a match based on the similarity variables.
+They trained their model on a set of known bullet matches and non-matches from the Hamby study.
+They demonstrated how the random forest model can be used to make prediction on a new set of bullet signature comparisons.
 The results from the paper suggest that the random forest model leads to highly accurate bullet matching predictions.
@@
 
-While random forest models often result in good predictions, it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
+While random forest models often result in good predictions as seen in Hare, Hofmann, and Carriquiry (2017), it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
 For example, it is not possible to tell which variables played an important role in the creation of individual predictions.
-This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction using a linear model.
-This allows for the ability to understand which were the driving variables in a prediction of interest.
+This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction using a linear regression model.
+This allows for the ability to understand which were the driving variables that led to a prediction of interest.
 
-Since firearm identification identification is commonly used as evidence for convictions in court cases, it is important to not only provide accurate predictions and an associated uncertainty level but also to understand which variables were important in making the prediction.
-Firearm examiners could use LIME to check whether or not the predictions created by LIME are reasonable.
-This paper provides an example of the application of LIME to an updated version of the random forest model from the Hare paper used for bullet matching.
+Since firearm identification identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess the model that is being used to quantify the probability that a bullet was fired from a gun.
+LIME provides the ability to understand which were the key variables used by the random forest model to make a prediction, which would allow firearm examiners to check whether or not the predictions created by the random forest are based on reasonable variables.
+
+This paper provides an example of the application of LIME to a bullet matching problem.
+(provide more details about what is contained in the papers - i.e.
+section 2 describes the Hamby data; section 3 describes the random forest model and LIME; ...)
 

### 2018-10-23 paper/paper.Rmd
spell check

@@
 Traditionally, this is a procedure that has been performed by hand.
-Specially trained examiners visually compare the microscopoic bullet striations that were created when the bullets passed through the gun barrel.
+Specially trained examiners visually compare the microscopic bullet striations that were created when the bullets passed through the gun barrel.
 Often a comparison microscope is used that allows the examiners to view both bullets at the same time (National Research Council 2009).
@@
 
-While random forest models often result in good predictions as seen in Hare, Hofmann, and Carriquiry (2017), it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
+While random forest models often result in good predictions as seen in Hare, Hofmann, and Carriquiry, it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
 For example, it is not possible to tell which variables played an important role in the creation of individual predictions.

### 2018-10-24 app/app.R
updated to do list and removed commented code from app

@@ -49,11 +49,6 @@ ui <- fluidPage(
                         label = "Select a Hamby 224 dataset", 
                         choices = c("Set 1", "Set 11")))),
 
-   # fluidRow(column(3, selectInput("testset",
-   #                                 label = "Select a Hamby 224 test dataset",
-   #                                 choices = c("Set 1", "Set 11"))),
-   #           column(3, verbatimTextOutput("click"))),
-
    fluidRow(column(6, plotlyOutput("tileplot")),
             column(6, plotOutput("featureplot")))
    
@@ -79,7 +74,7 @@ server <- function(input, output) {
       distinct() %>%
       ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
       geom_tile(aes(fill = rfscore)) +
-      facet_grid(bullet1 ~ bullet2) +
+      facet_grid(bullet1 ~ bullet2, scales = "free") +
       theme_bw() +
       scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
       labs(x = "Land 1", y = "Land 2", fill = "RF Score", 
@@ -88,17 +83,6 @@ server <- function(input, output) {
     ggplotly(plot, source = "tileplot", width = 700, height = 550)
     
   })
-  
-  # Print the values of the event data
-  # output$click <- renderPrint({
-  # 
-  #   # Obtain the click data
-  #   click_data <- event_data("plotly_click", source = "tileplot")
-  # 
-  #   # Print selected comparison
-  #   if(length(click_data) > 0) click_data else "nothing selected"
-  # 
-  # })
   
   # Create my own feature plot
   output$featureplot <- renderPlot({

### 2018-10-25 paper/paper.Rmd
added if else statements to paper

@@
 
+# If the test data does not exist, clean the data, create the test data, and save it
+# Otherwise, load in the test data
+if(!file.exists("../data/hamby224_test.csv")) {
+
   # Clean the Hamby 224 set 1 data
@@
   hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
-                                            hamby224_set11_cleaned))
+                                              hamby224_set11_cleaned)) %>%
+    mutate(case = as.character(1:length(study))) %>%
+    select(case, study:samesource)
 
@@
   write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)
+
+} else {
+
+  # Read in the test data
+  hamby224_test <- read.csv("../data/hamby224_test.csv")
+
+}
 ```
@@
 ```{r echo = FALSE}
+# Apply the lime function if the file does not already exist
+if(!file.exists("../data/hamby224_lime.rds")) {
+
   # Apply the lime function from the lime package (with a seed set)
@@
   saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
+
+} else {
+
+  # Load in the lime object
+  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
+
+}
 ```
@@
 ```{r}
+# Apply explain function if the file does not already exist
+if(!file.exists("../data/hamby224_explain.rds")) {
+
   # Apply the explain function from the lime package (with a seed set)
@@
   saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
+
+} else {
+
+  # Load in the explain object
+  hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+
+}
 ```
@@
 ```{r echo = FALSE}
-# Add a case variable to the test data
-hamby224_test <- hamby224_test %>%
-  mutate(case = as.character(1:dim(hamby224_test)[1])) %>%
-  select(case, study:samesource)
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
+# Create the test_explain combined data if the file does not already exist
+if(!file.exists("../data/hamby224_test_explain.rds")) {
 
   # Join the data and the explanations and edit and add additional variables
-hamby224_test_explain <- full_join(hamby224_test, hamby224_explain, by = "case") %>%
+  hamby224_test_explain <- hamby224_test %>%
+    mutate(case = as.character(case)) %>%
+    full_join(hamby224_explain, by = "case") %>%
     mutate(case = factor(case),
@@
   saveRDS(hamby224_test_explain, "../data/hamby224_test_explain.rds")
+
+} else {
+
+  # Load in the data
+  hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+
+}
 ```
@@
 
-```{r}
-hamby224_test_explain %>%
-  filter(set == "1") %>%
-  select(case, bullet1:land2, samesource) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2)) +
-  geom_tile(aes(fill = samesource)) +
-  facet_grid(bullet1 ~ bullet2) +
-  theme_bw()
-```
-
-```{r, fig.width = 8, fig.height = 4}
-lime::plot_explanations(hamby224_explain)
-```
-
-```{r}
-hamby224_test_explain %>%
-  filter(set == "1") %>%
-  ggplot(aes(x = case, y = feature_desc)) + 
-  geom_tile(aes(fill = feature_weight)) + 
-  facet_grid(feature ~ label, space = "free", scale = "free") + 
-  theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0) +
-  theme(legend.position = "bottom") +
-  ylab("Feature Sets") 
-```
-
-```{r}
-hamby224_test_explain %>%
-  filter(set == "1", samesource == "FALSE") %>%
-  ggplot(aes(x = case, y = feature_desc)) + 
-  geom_tile(aes(fill = feature_weight)) + 
-  facet_grid(feature ~ bullet1, space = "free", scale = "free") + 
-  theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0)
-```
-
-```{r}
-hamby224_test_explain %>%
-  filter(set == "1", samesource == "FALSE") %>%
-  ggplot(aes(x = case, y = feature_desc)) + 
-  geom_tile(aes(fill = feature_weight)) + 
-  facet_grid(bullet1 ~ bullet2, space = "free", scale = "free") + 
-  theme(axis.text.x = element_text(angle = 90)) +
-  scale_fill_gradient2(midpoint = 0) +
-  theme(legend.position = "bottom")
-```
-
 # Results

### 2018-10-25 app/app.R
worked on app

@@ -15,25 +15,26 @@ library(lime)
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 
 # Create a dataset with all combinations of lands and bullets comparisons for each set
-combs1 <- data.frame(set = factor(1),
+combinations1 <- data.frame(set = factor(1),
                     expand.grid(land1 = factor(1:6),
                                 land2 = factor(1:6),
                                 bullet1 = factor(c("1", "2", "Q")),
                                 bullet2 = factor(c("1", "2", "Q"))))
-combs11 <- data.frame(set = factor(11),
+combinations11 <- data.frame(set = factor(11),
                     expand.grid(land1 = factor(1:6),
                                 land2 = factor(1:6), 
                                 bullet1 = factor(c("1", "2", "I")),
                                 bullet2 = factor(c("1", "2", "I"))))
-combs <- rbind(combs1, combs11)
+combinations <- rbind(combinations1, combinations11)
 
 # Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(combs, hamby224_test_explain,
+hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
                                        by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  mutate(bullet1 = forcats::fct_recode(bullet1, "bullet 1" = "1", "bullet 2" = "2", 
-                                       "bullet Q" = "Q", "bullet I" = "I"),
-         bullet2 = forcats::fct_recode(bullet2, "bullet 1" = "1", "bullet 2" = "2", 
-                                       "bullet Q" = "Q", "bullet I" = "I"))
+  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"),
+         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"),
+         rfscore = round(rfscore, 3))
 
 ## ------------------------------------------------------------------------------------
 ## UI setup
@@ -69,20 +70,28 @@ server <- function(input, output) {
     
     # Create a tile plot of the random forest predictions for all land comparisons
     plot <- hamby224_test_explain_NAs %>%
-      filter(set == chosen_set) %>%
+      filter(set == chosen_set,
[…]

### 2018-10-29 app/app.R
app updates from last Friday

@@ -4,8 +4,11 @@
 library(shiny)
 library(ggplot2)
 library(dplyr)
+library(tidyr)
 library(plotly)
 library(lime)
+library(cowplot)
+library(grDevices)
 
 ## ------------------------------------------------------------------------------------
 ## Data steps
@@ -28,13 +31,14 @@ combinations11 <- data.frame(set = factor(11),
 combinations <- rbind(combinations1, combinations11)
 
 # Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
+hamby224_test_explain_NAs <<- left_join(combinations, hamby224_test_explain,
                                        by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
   mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
                                        "Questioned" = "Q", "Questioned" = "I"),
          bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
                                        "Questioned" = "Q", "Questioned" = "I"),
-         rfscore = round(rfscore, 3))
+         rfscore = round(rfscore, 3),
+         feature_magnitude = feature_weight * feature_value)
 
 ## ------------------------------------------------------------------------------------
 ## UI setup
@@ -71,16 +75,16 @@ server <- function(input, output) {
     # Create a tile plot of the random forest predictions for all land comparisons
     plot <- hamby224_test_explain_NAs %>%
       filter(set == chosen_set,
-             !(bullet2 == "Questioned" & bullet1 == "Known 1"),
-             !(bullet2 == "Questioned" & bullet1 == "Known 2"),
-             !(bullet2 == "Known 2" & bullet1 == "Known 1")) %>%
+             !(bullet1 == "Questioned" & bullet2 == "Known 1"),
+             !(bullet1 == "Questioned" & bullet2 == "Known 2"),
+             !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
       select(case, bullet1, bullet2, land1, land2, rfscore) %>%
       distinct() %>%
       ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-                 text = paste('Random Forest Score: ', ifelse(is.na(rfscore), "Missing due to tank rash", rfscore),
[…]

### 2018-10-29 paper/paper.Rmd
worked on labelling bins

@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
 
@@
                                     hamby224_lime,
-                                    n_labels = 1, 
+                                    labels = "TRUE",
                                     n_features = 3)
@@
 ```{r echo = FALSE}
+# Function to use for creating bin labels in the test_explain dataset
+bin_labeller <- function(bin_cuts, feature, feature_value){
+
+  # Create a dataframe of bins cuts
+  bin_cuts <- data.frame(matrix(unlist(hamby224_lime$bin_cuts), nrow = 9, byrow = TRUE)) %>%
+    rename("Q0" = X1, "Q25" = X2, "Q50" = X3, "Q75" = X4, "Q100" = X5) %>%
+    mutate(Feature = rf_features) %>%
+    select(Feature, Q0:Q100)
+
+  # Subset the bin cuts table to the selected feature
+  feature_bin_cuts <- bin_cuts %>% filter(Feature == feature)
+
+  # Determine which bin the case falls in
+  if(feature_value < feature_bin_cuts$Q25){
+    feature_bin <- "lower"
+  } else if (feature_bin_cuts$Q25 <= feature_value & feature_value < feature_bin_cuts$Q50){
+    feature_bin <- "lower middle"
+  } else if (feature_bin_cuts$Q50 <= feature_value & feature_value < feature_bin_cuts$Q75){
+    feature_bin <- "upper middle"
+  } else if (feature_bin_cuts$Q75 <= feature_value){
+    feature_bin <- "upper"
+  }
+
+  # Return the bin
+  return(feature_bin)
+
+}
+```
+
+```{r}
 # Create the test_explain combined data if the file does not already exist
@@
   hamby224_test_explain <- hamby224_test_explain %>%
-    mutate(
-      feature_desc = reorder(feature_desc, strictly_less),
+    mutate(feature_desc = reorder(feature_desc, strictly_less),
            feature_desc = reorder(feature_desc, feature_number),
-      feature_desc = reorder(feature_desc, as.numeric(feature))
-    )
+           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
+    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
+    select(case:feature_desc, feature_number:feature_bin, data, prediction)
 

### 2018-10-30 code/03-create images.R
removed some old unecessary code

@@ -1,58 +1,0 @@
-## R Code for LIME Bullet Paper
-## Purpose: creating images lime images
-## Last updated: 2018/09/24
-
-# Load libraries 
-library(lime)
-library(tidyverse)
-
-## -----------------------------------------------------------------------
-## Create the function for saving the figures
-## -----------------------------------------------------------------------
-
-# Function for creating and saving a lime plot_features plot for a specified case
-plot_features_function <- function(case_number, explain, test_explain){
- 
-  # INPUTS:
-  #   case_number - case number to create the plot for
-  #   explain - a lime explain object
-  #   test_explain - a dataframe of the joined test data and lime explain object
-  
-  # Subset the test_explain data frame to only case one row from the case of interest
-  test_explain_sub <- test_explain %>% 
-    filter(case == case_number) %>% 
-    slice(1)
-  
-  # Create and save the image
-  plot_features(explain %>% filter(case == case_number))
-  ggsave(file = test_explain_sub$figure_file_location)
-  
-}
-
-## -----------------------------------------------------------------------
-## Load and prepare data
-## -----------------------------------------------------------------------
-
-# Read in the explanation object
-hamby224_explain <- readRDS("./data/hamby224_explain.rds")
-
-# Read in the combined test data and explanation object
-hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
-
-# Add a variable for the figure file location for each case
-hamby224_test_explain <- hamby224_test_explain %>%
-  mutate(figure_file_location = paste0("./figures/", study, "_testset", set, "_b", bullet1, 
-                                       "_b", bullet2, "_land", land1, "_land", land2, ".png"))
-
-# Save the updated version of the test_explain data
-saveRDS(hamby224_test_explain, "./data/hamby224_test_explain.rds")
-
-## -----------------------------------------------------------------------
-## Create and save the images
-## -----------------------------------------------------------------------
-
-# Apply the plot_features_function to all of the cases in the Hamby 224 dataset
-purrr::map(.x = 1:max(as.numeric(hamby224_test_explain$case)),
-           .f = plot_features_function,
-           explain = hamby224_explain,
-           test_explain = hamby224_test_explain)

### 2018-10-30 code/example-plotly.R

@@ -1,97 +1,0 @@
-library(plotly)
-library(htmlwidgets)
-
-mtcars$url <- paste0(
-  "http://google.com/#q=", 
-  rownames(mtcars)
-)
-
-p <- plot_ly(mtcars, x = ~wt, y = ~mpg) %>%
-  add_markers(customdata = ~url)
-
-# open google search (on click)
-onRender(p, "
-         function(el, x) {
-         el.on('plotly_click', function(d) {
-         var url = d.points[0].customdata;
-         window.open(url);
-         });
-         }
-         ")
-
-# annotate graph (on click)
-onRender(p, "
-         function(el, x) {
-         el.on('plotly_click', function(d) {
-         var ann = {
-         text: d.points[0].customdata,
-         x: 0,
-         y: 0,
-         xref: 'paper',
-         yref: 'paper',
-         yshift: -40,
-         showarrow: false
-         }
-         Plotly.relayout(el.id, {annotations: [ann]})
-         });
-         }
-         ")
-
-# annotate on hover
-onRender(p, "
-         function(el, x) {
-         el.on('plotly_hover', function(d) {
-         var ann = {
-         text: d.points[0].customdata,
-         x: 0,
-         y: 0,
-         xref: 'paper',
-         yref: 'paper',
-         yshift: -40,
-         showarrow: false
-         }
-         Plotly.relayout(el.id, {annotations: [ann]})
-         });
-         }
-         ")
-
-# combine highlight() api with custom javascript
-mtcars %>%
-  highlight_key() %>%
-  plot_ly(x = ~wt, y = ~mpg, customdata = ~url) %>%
-  highlight(color = "red") %>%
-  onRender("
-           function(el, x) {
-           el.on('plotly_click', function(d) {
-           var ann = {
-           text: d.points[0].customdata,
-           x: 0,
-           y: 0,
-           xref: 'paper',
-           yref: 'paper',
-           yshift: -40,
-           showarrow: false
-           }
-           Plotly.relayout(el.id, {annotations: [ann]})
-           });
-           }
-           ")
-
-# inspect different plotly.js events via browser console
-# see also https://plot.ly/javascript/plotlyjs-events/
-onRender(p, "
-         function(el, x) {
-         el.on('plotly_hover', function(d) {
-         console.log('hover', d)
-         });
-         el.on('plotly_click', function(d) {
-         console.log('click', d)
-         });
-         el.on('plotly_selected', function(d) {
[…]

### 2018-10-30 code/individual plots.R

@@ -1,100 +1,0 @@
-library(plotly)
-library(ggplot)
-
-# Input data
-hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
-
-# Create a dataset with all combinations of lands and bullets comparisons for each set
-combinations1 <- data.frame(set = factor(1),
-                            expand.grid(land1 = factor(1:6),
-                                        land2 = factor(1:6),
-                                        bullet1 = factor(c("1", "2", "Q")),
-                                        bullet2 = factor(c("1", "2", "Q"))))
-combinations11 <- data.frame(set = factor(11),
-                             expand.grid(land1 = factor(1:6),
-                                         land2 = factor(1:6), 
-                                         bullet1 = factor(c("1", "2", "I")),
-                                         bullet2 = factor(c("1", "2", "I"))))
-combinations <- rbind(combinations1, combinations11)
-
-# Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
-                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"),
-         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"))
-
-p1 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_bw() +
[…]

### 2018-10-30 app/app.R
removed old comments

@@ -44,7 +44,6 @@ hamby224_test_explain_NAs <<- left_join(combinations, hamby224_test_explain,
 ## UI setup
 ## ------------------------------------------------------------------------------------
 
-# Define UI for application that draws a histogram
 ui <- fluidPage(
    
    # Application title
@@ -63,7 +62,6 @@ ui <- fluidPage(
 ## Server setup
 ## ------------------------------------------------------------------------------------
 
-# Define server logic required to draw a histogram
 server <- function(input, output) {
   
   # Create the tile plot
@@ -131,7 +129,7 @@ server <- function(input, output) {
                  land2 == location$land2,
                  bullet1 == location$bullet1,
                  bullet2 == location$bullet2) %>%
-          mutate(feature_desc = reorder(feature_desc, abs(as.numeric(feature_weight))),
+          mutate(feature = reorder(feature, abs(as.numeric(feature_weight))),
                  evidence = factor(if_else(feature_weight >= 0, "Supports Same Source", "Supports Different Source"), 
                                    levels = c("Supports Different Source", "Supports Same Source")))
         
@@ -142,19 +140,20 @@ server <- function(input, output) {
         
         # Grab the observed predictor values for the case of interest
         case_data <- selected_comparison %>%
-          select(feature, feature_value) %>%
-          mutate(feature_value = round(feature_value, 3)) %>%
-          arrange(feature_value) %>%
+          select(feature, feature_weight, feature_value) %>%
+          mutate(feature_value = round(feature_value, 3),
+                 feature = reorder(feature, -abs(as.numeric(feature_weight)))) %>%
+          select(-feature_weight) %>%
           spread(key = feature, value = feature_value)
         
         # Create the feature plot
-        feature_plot <- ggplot(selected_comparison, aes(x = feature_desc, y = abs(feature_weight))) +
+        feature_plot <- ggplot(selected_comparison, aes(x = feature, y = abs(feature_weight))) +
           geom_col(aes(fill = evidence)) +
           ylim(0, xlimit1) +
           coord_flip() +
           theme_minimal() +
           theme(legend.position = "none") +
-          labs(y = "Feature Weight", x = "Feature Bin", fill = "") +
+          labs(y = "Feature Magnitude (Absolute Value of Ridge Regression Coefficient)", x = "Feature", fill = "") +
           scale_fill_manual(values = c("Supports Same Source" = "darkorange", "Supports Different Source" = "darkgrey"),
                             drop = FALSE)
         
[…]

### 2018-10-30 paper/paper.Rmd
switched closure side with bins

@@
   # Determine which bin the case falls in
-  if(feature_value < feature_bin_cuts$Q25){
-    feature_bin <- "lower"
-  } else if (feature_bin_cuts$Q25 <= feature_value & feature_value < feature_bin_cuts$Q50){
-    feature_bin <- "lower middle"
-  } else if (feature_bin_cuts$Q50 <= feature_value & feature_value < feature_bin_cuts$Q75){
-    feature_bin <- "upper middle"
-  } else if (feature_bin_cuts$Q75 <= feature_value){
-    feature_bin <- "upper"
+  if(feature_value <= feature_bin_cuts$Q25){
+    feature_bin <- paste("lower", feature, "bin")
+  } else if (feature_bin_cuts$Q25 < feature_value & feature_value <= feature_bin_cuts$Q50){
+    feature_bin <- paste("lower middle", feature, "bin")
+  } else if (feature_bin_cuts$Q50 < feature_value & feature_value <= feature_bin_cuts$Q75){
+    feature_bin <- paste("upper middle", feature, "bin")
+  } else if (feature_bin_cuts$Q75 < feature_value){
+    feature_bin <- paste("upper", feature, "bin")
   }
@@
     mutate(feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE)
+           strictly_less = FALSE) %>%
+    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value))
 
@@
 
-  # Reorder the variable of feature_desc for plotting purposes
+  # Reorder the variables of feature_desc and feature_bin for plotting purposes
   hamby224_test_explain <- hamby224_test_explain %>%
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
     select(case:feature_desc, feature_number:feature_bin, data, prediction)

### 2018-10-30 code/dead_space_example.R
added a dead space example

@@ -1,0 +1,34 @@
+# Example with Plotly to show dead space in heatmap
+
+# System information
+# R version 3.5.1 (2018-07-02)
+# Platform: x86_64-apple-darwin15.6.0 (64-bit)
+# Running under: macOS  10.14
+
+# Load libraries
+library(plotly) # version ‘4.8.0’
+library(ggplot2) # version ‘3.1.0’
+library(tidyr) # version ‘0.8.2’
+
+# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
+
+# Create dataset
+m <- matrix(rnorm(9), nrow = 3, ncol = 3)
+
+# Create plotly heatmap - no deadspace to be found
+plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
+
+# Example using ggplotly function -----------------------------------------------------
+
+# Reshape the data for ggplot
+m_gathered <- data.frame(m) %>%
+  gather(key = column) %>%
+  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
+  select(column, row, value)
+
+# Create ggplot heatmap
+p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
+  geom_tile()
+
+# Apply plotly to ggplot heatmap - deadspace in the middle of (X1, X1)
+ggplotly(p)

### 2018-10-30 code/individual_plots.R

@@ -1,0 +1,100 @@
+library(plotly)
+library(ggplot)
+
+# Input data
+hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
+
+# Create a dataset with all combinations of lands and bullets comparisons for each set
+combinations1 <- data.frame(set = factor(1),
+                            expand.grid(land1 = factor(1:6),
+                                        land2 = factor(1:6),
+                                        bullet1 = factor(c("1", "2", "Q")),
+                                        bullet2 = factor(c("1", "2", "Q"))))
+combinations11 <- data.frame(set = factor(11),
+                             expand.grid(land1 = factor(1:6),
+                                         land2 = factor(1:6), 
+                                         bullet1 = factor(c("1", "2", "I")),
+                                         bullet2 = factor(c("1", "2", "I"))))
+combinations <- rbind(combinations1, combinations11)
+
+# Join the combinations and the data so that all combinations have a row in the data
+hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
+                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
+  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"),
+         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"))
+
+p1 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_bw() +
[…]

### 2018-10-30 code/dead_space_example.R
updated dead space example

@@ -6,9 +6,9 @@
 # Running under: macOS  10.14
 
 # Load libraries
-library(plotly) # version ‘4.8.0’
-library(ggplot2) # version ‘3.1.0’
-library(tidyr) # version ‘0.8.2’
+library(plotly) # version 4.8.0
+library(ggplot2) # version 3.1.0
+library(tidyr) # version 0.8.2
 
 # Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
 

### 2018-10-31 paper/paper.Rmd
updates to app

@@
                                     hamby224_lime,
-                                    labels = "TRUE",
+                                    labels = "FALSE",
                                     n_features = 3)
@@
 
-Some plots to tryout working with the new explanations...
+Thoughts on the visualizations:
+
+- It would be interesting to see the "magnitude" associated with a variable for a prediction, but
+  this would require obtaining the scaled values of the perturbations.
+- This seems much more meaningful to me than just the model coefficient associated with the variable.
+- The current version shows which variables in the model have the largest coefficients.
+- However, the importance of the variable might change depending on the observed value associated
+  with the prediction of interest.
 

### 2018-10-31 app/app.R

@@ -37,8 +37,9 @@ hamby224_test_explain_NAs <<- left_join(combinations, hamby224_test_explain,
                                        "Questioned" = "Q", "Questioned" = "I"),
          bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
                                        "Questioned" = "Q", "Questioned" = "I"),
-         rfscore = round(rfscore, 3),
-         feature_magnitude = feature_weight * feature_value)
+         land1 = forcats::fct_recode(land1, "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
+                                     "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
+         rfscore = round(rfscore, 3))
 
 ## ------------------------------------------------------------------------------------
 ## UI setup
@@ -64,6 +65,8 @@ ui <- fluidPage(
 
 server <- function(input, output) {
   
+  tileplot_mark <- reactiveValues(a = NULL)
+  
   # Create the tile plot
   output$tileplot <- renderPlotly({
     
@@ -72,29 +75,38 @@ server <- function(input, output) {
     
     # Create a tile plot of the random forest predictions for all land comparisons
     plot <- hamby224_test_explain_NAs %>%
-      filter(set == chosen_set,
-             !(bullet1 == "Questioned" & bullet2 == "Known 1"),
-             !(bullet1 == "Questioned" & bullet2 == "Known 2"),
-             !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
-      select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-      distinct() %>%
-      ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-                 text = paste('Bullets Compared: ', bullet1, "- Land ", land1, "vs", bullet2, "- Land", land2,
-                              '\nRandom Forest Score: ', ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
-      geom_tile(aes(fill = rfscore)) +
-      facet_grid(bullet2 ~ bullet1, scales = "free") +
-      theme_minimal() +
-      scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-      labs(x = "Land 1", y = "Land 2", fill = "RF Score", 
-           title = paste0("Hamby 224 Data (", input$testset, ")"))
+        filter(set == chosen_set,
[…]

### 2018-10-31 code/dead_space_example.R

@@ -15,7 +15,7 @@ library(tidyr) # version 0.8.2
 # Create dataset
 m <- matrix(rnorm(9), nrow = 3, ncol = 3)
 
-# Create plotly heatmap - no deadspace to be found
+# Create plotly heatmap - no dead space to be found
 plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
 
 # Example using ggplotly function -----------------------------------------------------
@@ -28,7 +28,17 @@ m_gathered <- data.frame(m) %>%
 
 # Create ggplot heatmap
 p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
+  geom_tile() + 
+  scale_x_discrete(expand = c(0, 0)) + 
+  scale_y_discrete(expand = c(0, 0))
 
-# Apply plotly to ggplot heatmap - deadspace in the middle of (X1, X1)
+# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
 ggplotly(p)
+
+# Create ggplot heatmap without a legend
+p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
+  geom_tile() +
+  theme(legend.position = "none") 
+
+# Apply plotly to ggplot heatmap - the dead space is gone!
+ggplotly(p_nolegend)

### 2018-10-31 code/individual_plots.R

@@ -1,5 +1,9 @@
+# Code for creating the heatmap plots using individual plots
+
+# Load libraries 
 library(plotly)
-library(ggplot)
+library(ggplot2)
+library(dplyr)
 
 # Input data
 hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
@@ -25,6 +29,8 @@ hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
          bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
                                        "Questioned" = "Q", "Questioned" = "I"))
 
+chosen_set = 1
+
 p1 <- hamby224_test_explain_NAs %>%
   filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@ -32,9 +38,10 @@ p1 <- hamby224_test_explain_NAs %>%
   ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
   geom_tile(aes(fill = rfscore)) +
   facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_bw() +
+  theme_minimal() +
   scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
 
 p2 <- hamby224_test_explain_NAs %>%
   filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 2") %>%
@@ -43,9 +50,10 @@ p2 <- hamby224_test_explain_NAs %>%
   ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
   geom_tile(aes(fill = rfscore)) +
   facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_bw() +
+  theme_minimal() +
   scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
 
[…]

### 2018-11-01 paper/paper.Rmd
moved all data steps to paper from app and cleaned up the code - also added mark to app

@@
            land2 = landB) %>%
-    mutate(study = factor("Hamby_224"), 
-           set = factor("1"),
-           bullet1 = factor(bullet1),
-           bullet2 = factor(bullet2),
-           land1 = factor(land1),
-           land2 = factor(land2)) %>%
+    mutate(study = factor("Hamby 224"), 
+           set = factor("Set 1"),
+           bullet1 = recode(factor(bullet1), "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
+           bullet2 = recode(factor(bullet2), "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
+           land1 = recode(factor(land1), "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
+                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
+           land2 = recode(factor(land2), "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
+                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
     select(study, set, bullet1:land2, rf_features, rfscore, samesource)
@@
            land2 = landB) %>%
-    mutate(study = factor("Hamby_224"), 
-           set = factor("11"),
-           bullet1 = recode(factor(bullet1), 
-                            "Bullet 1" = "1", 
-                            "Bullet 2" = "2", 
-                            "Bullet I" = "I"),
-           bullet2 = recode(factor(bullet2), 
-                            "Bullet 1" = "1", 
-                            "Bullet 2" = "2", 
-                            "Bullet I" = "I"),
-           land1 = recode(factor(land1), 
-                          "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
-                          "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
-           land2 = recode(factor(land2), 
-                          "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
-                          "Land 4" = "4", "Land 5" = "5", "Land 6" = "6")) %>%
+    mutate(study = factor("Hamby 224"), 
+           set = factor("Set 11"),
+           bullet1 = recode(factor(bullet1), "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
+                            "Bullet I" = "Questioned"),
+           bullet2 = recode(factor(bullet2), "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
+                            "Bullet I" = "Questioned")) %>%
     select(study, set, bullet1:land2, rf_features, rfscore, samesource)
+
+  # Create a dataset with all combinations of lands and bullets comparisons for each set
+  combinations <- data.frame(set = factor(rep(c("Set 1", "Set 11"), each = 324)),
+                      expand.grid(land1 = factor(c("Land 1", "Land 2", "Land 3", 
+                                                   "Land 4", "Land 5", "Land 6")),
+                                  land2 = factor(c("Land 1", "Land 2", "Land 3", 
+                                                   "Land 4", "Land 5", "Land 6")),
+                                  bullet1 = factor(c("Known 1", "Known 2", "Questioned")),
+                                  bullet2 = factor(c("Known 1", "Known 2", "Questioned"))))
 
@@
                                               hamby224_set11_cleaned)) %>%
-    mutate(case = as.character(1:length(study))) %>%
+    mutate(set = factor(set),
+           bullet1 = factor(bullet1),
+           bullet2 = factor(bullet2),
+           land1 = factor(land1),
+           land2 = factor(land2)) %>%
+    right_join(combinations, by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
+    filter(!(bullet1 == "Questioned" & bullet2 == "Known 1"),
+           !(bullet1 == "Questioned" & bullet2 == "Known 2"),
+           !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
+    arrange(rfscore) %>%
+    mutate(case = factor(1:length(study))) %>%
     select(case, study:samesource)
@@
   set.seed(84902)
-  hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
+  hamby224_explain <- lime::explain(hamby224_test %>% 
+                                      arrange(case) %>% 
+                                      select(rf_features) %>% 
+                                      na.omit(), 
                                     hamby224_lime,
@@
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(bin_cuts, feature, feature_value){
+bin_labeller <- function(feature, feature_value){
+
+  if (is.na(feature)) {
+
+    # Set feature_bin to NA if feature is NA
+    feature_bin <- NA
+
+  } else {
 
@@
     if(feature_value <= feature_bin_cuts$Q25){
-    feature_bin <- paste("lower", feature, "bin")
+      feature_bin <- paste(feature, "(lower bin)")
     } else if (feature_bin_cuts$Q25 < feature_value & feature_value <= feature_bin_cuts$Q50){
-    feature_bin <- paste("lower middle", feature, "bin")
+      feature_bin <- paste(feature, "(lower middle bin)")
     } else if (feature_bin_cuts$Q50 < feature_value & feature_value <= feature_bin_cuts$Q75){
-    feature_bin <- paste("upper middle", feature, "bin")
+      feature_bin <- paste(feature, "(upper middle bin)")
     } else if (feature_bin_cuts$Q75 < feature_value){
-    feature_bin <- paste("upper", feature, "bin")
+      feature_bin <- paste(feature, "(upper bin)")
+    }
+
   }
@@
     mutate(case = factor(case),
-           set = factor(set),
-           bullet1 = factor(bullet1),
-           bullet2 = factor(bullet2),
-           land1 = factor(land1),
-           land2 = factor(land2)) %>%
-    mutate(mypred = rep(predict(rtrees, hamby224_test %>% select(rf_features), 
-                                type = "prob")[,2], each = 3)) %>%
-    select(case:rfscore, mypred, samesource:prediction) %>%
-    mutate(feature_desc = factor(feature_desc),
-           feature = factor(feature)) %>%
+           feature_desc = factor(feature_desc),
+           feature = factor(feature),
+           feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
     mutate(feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE) %>%
-    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value))
+           strictly_less = FALSE)
 
@@
 hamby224_test_explain %>%
-  filter(set == "1") %>%
-  select(case, bullet1:land2, rfscore) %>%
+      filter(set == "Set 1") %>%
+      mutate(rfscore = round(rfscore, 3)) %>%
+      select(case, bullet1, bullet2, land1, land2, rfscore) %>%
       distinct() %>%
-  ggplot(aes(x = land1, y = land2)) +
+      ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
+                 text = paste('Bullets Compared: ', bullet1, "-", land1, 
+                              "vs", bullet2, "-", land2,
+                              '\nRandom Forest Score: ', 
+                              ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
       geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet1 ~ bullet2) +
-  theme_bw() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)
+      facet_grid(bullet2 ~ bullet1, scales = "free") +
+      theme_minimal() +
+      scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
+      theme(axis.text.x = element_text(angle = 45, hjust = 1),
+            strip.text.x = element_blank(),
+            strip.text.y = element_blank()) +
+      labs(x = "Known 1                            Known 2                            Questioned", 
+           y = "Known 1                            Known 2                            Questioned", 
+           fill = "RF Score")
 ```

### 2018-11-01 app/app.R

@@ -11,139 +11,134 @@ library(cowplot)
 library(grDevices)
 
 ## ------------------------------------------------------------------------------------
-## Data steps
+## Data Steps
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-# Create a dataset with all combinations of lands and bullets comparisons for each set
-combinations1 <- data.frame(set = factor(1),
-                    expand.grid(land1 = factor(1:6),
-                                land2 = factor(1:6),
-                                bullet1 = factor(c("1", "2", "Q")),
-                                bullet2 = factor(c("1", "2", "Q"))))
-combinations11 <- data.frame(set = factor(11),
-                    expand.grid(land1 = factor(1:6),
-                                land2 = factor(1:6), 
-                                bullet1 = factor(c("1", "2", "I")),
-                                bullet2 = factor(c("1", "2", "I"))))
-combinations <- rbind(combinations1, combinations11)
-
-# Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <<- left_join(combinations, hamby224_test_explain,
-                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"),
-         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"),
-         land1 = forcats::fct_recode(land1, "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
-                                     "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
-         rfscore = round(rfscore, 3))
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds") 
 
 ## ------------------------------------------------------------------------------------
-## UI setup
+## UI Setup
 ## ------------------------------------------------------------------------------------
 
+# Layout of the app
 ui <- fluidPage(
    
    # Application title
    titlePanel("LIME Explanations for Bullet Matching"),
    
-   fluidRow(column(3, selectInput("testset", 
+   # Set selector
+   fluidRow(column(3, selectInput("set", 
[…]

### 2018-11-01 code/dead_space_example.R

@@ -28,12 +28,13 @@ m_gathered <- data.frame(m) %>%
 
 # Create ggplot heatmap
 p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() + 
-  scale_x_discrete(expand = c(0, 0)) + 
-  scale_y_discrete(expand = c(0, 0))
+  geom_tile()
 
 # Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
 ggplotly(p)
+
+# Carson's suggested fix for now
+style(ggplotly(p), hoverinfo = "skip", traces = 2)
 
 # Create ggplot heatmap without a legend
 p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
@@ -42,3 +43,5 @@ p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
 
 # Apply plotly to ggplot heatmap - the dead space is gone!
 ggplotly(p_nolegend)
+
+plotly_json(p)

### 2018-11-01 code/individual_plots.R

@@ -108,5 +108,7 @@ p9 <- hamby224_test_explain_NAs %>%
   scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
   labs(x = "Land 1", y = "Land 2", fill = "RF Score")
 
-subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows = 3, titleX = TRUE, titleY = TRUE, margin = 0.03)
+style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows = 3, titleX = TRUE, titleY = TRUE, margin = 0.03),
+      hoverinfo = "skip",
+      traces = 7)
 

### 2018-11-01 app/app.R
updated libraries in app

@@ -6,9 +6,7 @@ library(ggplot2)
 library(dplyr)
 library(tidyr)
 library(plotly)
-library(lime)
 library(cowplot)
-library(grDevices)
 
 ## ------------------------------------------------------------------------------------
 ## Data Steps

### 2018-11-01 app/app.R
updated the app to use the new version of plotly

@@ -83,18 +83,14 @@ server <- function(input, output) {
                        aes(label = "x"))
       
       # Make the plot interactive
-      style(ggplotly(plot, source = "tileplot", width = 700, height = 550, tooltip = "text"),
-            hoverinfo = "skip", 
-            traces = 8)
+      ggplotly(plot, source = "tileplot", width = 700, height = 550, tooltip = "text")
       
     } else {
       
       # Make the plot interactive
-      style(ggplotly(plot, source = "tileplot", width = 700, height = 550, tooltip = "text"),
-            hoverinfo = "skip", 
-            traces = 7)
-    }
+      ggplotly(plot, source = "tileplot", width = 700, height = 550, tooltip = "text")
     
+      }
     
   })
   

### 2018-11-02 paper/paper.Rmd
copied and pasted lime procedure - now need to work on this

@@
 
-(fill in once the new random forest model has been fit)
+## Overview of LIME
 
-## Overview of LIME
+Step 0: Split iris data into training and testing datasets
+Step 1: Fit a complex model to the training data
+Step 2: Obtain distributions of the variables from the training data
+Step 3: Sample from each of the variable distributions $n$ times
+Step 4: Obtain predictions for sampled values using the complex model
+For each testing case use the random forest model to make a prediction for each of the $n=5000$ samples
+In the iris data, the predictions are represented by the probability that a flower is a particular species
+Step 5: Obtain similarity score between data observation and sampled values
+LIME uses exponential kernel function
+  ...
+where
+$x_{obs}$: observed data vector to predict
+$x_{sampled}$: sampled data vector from distribution of training variables
+$D(\cdot, \cdot)$: distance function such as euclidean distance, cosine distance, etc.
+$\sigma$: width (default set to 0.75 in lime)
+Step 6: Perform feature selection by fiting a model to the sampled data and associated predictions (weighted by the similarity scores)
+The user can specify the number of variables (features) they would like to select: $m$
+With the iris data, the following three models will be fit to perform variable selection to select $m=2$ features:
+To perform variable selection lime supports: 
+ forward selection with ridge regression
+ highest weight with ridge regression
+ LASSO
+ tree models
+auto: forward selection if $m\le6$, highest weight otherwise
+Step 7: Fit a simple model to regress the predictions on the $m$ selected predictor variables (weighted by the similarity scores)
+Currently, `lime` is programmed to use ridge regression as the simple model
+If the response is categorical, the user can select how many categories they want to explain
+In this example, only setosa will be explained
+If petal length and sepal length were selected as the most important features for the first case in the testing data, then the simple model is
+Step 8: Extract the feature weights and use them as the explanations
 

### 2018-11-05 app/app.R
added r2, simple model prob, and simple model intercept to description

@@ -13,7 +13,7 @@ library(cowplot)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds") 
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 
 ## ------------------------------------------------------------------------------------
 ## UI Setup
@@ -139,7 +139,8 @@ server <- function(input, output) {
         # Create a data frame with the appropriate labels
         labels <- selected_comparison %>% 
           slice(1) %>%
-          select(study, set, bullet1, bullet2, land1, land2, rfscore)
+          select(study, set, bullet1, bullet2, land1, land2, 
+                 rfscore, model_r2, model_prediction, model_intercept)
         
         # Grab the observed predictor values for the case of interest
         case_data <- selected_comparison %>%
@@ -169,7 +170,10 @@ server <- function(input, output) {
         # Create a subtitle
         subtitle <- ggdraw() + draw_label(paste("Study: ", labels$study, labels$set,
                                                 "\nBullets Compared: ", labels$bullet1, "-", labels$land1, " vs ", labels$bullet2, "-", labels$land2,
-                                                "\nRandom Forest Score: ", round(labels$rfscore, 3),
+                                                "\nRandom Forest Probability of a Match: ", round(labels$rfscore, 3),
+                                                "\nSimple Model Probability of a Match: ", round(labels$model_prediction, 3),
+                                                "\nSimple Model R2: ", round(labels$model_r2, 3),
+                                                "\nSimple Model Intercept: ", round(labels$model_intercept, 3),
                                                 "\n\nObserved Variable Values:", 
                                                 "\n", names(case_data)[1], " = ", case_data[,1],
                                                 "\n", names(case_data)[2], " = ", case_data[,2],
@@ -181,7 +185,7 @@ server <- function(input, output) {
         legend <- get_legend(feature_plot + theme(legend.position = "bottom"))
         
         # Create a grid of plotting components
-        plot_grid(title, subtitle, feature_plot, legend, ncol = 1, rel_heights = c(0.1, 0.4, 1))
+        plot_grid(title, subtitle, feature_plot, legend, ncol = 1, rel_heights = c(0.1, 0.6, 1))
         
       } else{
         

### 2018-11-05 paper/paper.Rmd
wrote a (very) rough draft of the lime procedure with the random forest model and created some visualizations to look compare the rf probabilities to the simple probabilities

--- 2018-11-01 paper/paper.Rmd
@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE)
 
@@
 
-## Training Data: The Hamby...
-
-(fill in once we know which data will be used to train the new random forest model)
+## Training Data: The Hamby 173 and 252 Datasets
 
@@
 The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets  or from a different source.
-This situation is similar to what a Firearms and Toolmarks Examiner might encounter in case work.
+This situation is similar to what a firearms and toolmarks examiner might encounter in case work.
 
@@
 
-(fill in once the new random forest model has been fit)
+## Overview of LIME
 
-## Overview of LIME
+LIME was developed by Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin in response to the issue of black box prediction models, which are complex models that may produce accurate predictions but do not allow for interpretability.
+The LIME algorithm can be applied to any predictive model.
+It provides an explanation for an individual prediction of interest by fitting a linear regression model in a local region around the prediction.
+Linear regression models contain a well known form and coefficients that can be interpreted.
+
+The developers of LIME wrote a Python package to implement LIME, and Thomas Lin Pedersen adapted their work to create an R package called `lime`.
+This paper will use version `r packageVersion("lime")` of the R package `lime`.
+The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
+For simplicity, the steps are described as what happens to one case in the test data.
+Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
+
+\begin{enumerate}
+\item Distributions for each of the features in the training data are obtained.
+
+\begin{quote}
+The method that `lime` uses to obtain the distribution differs based on the feature type.
+All of the features in the Hamby datasets are numeric.
+For numeric features, the default option in `lime` (`quantile\_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
+The default number of bins is 4 (`n\_bins = 4`).
+\end{quote}
+
+\item $n$ samples from each of the feature distributions are drawn.
+
+\begin{quote}
+To do this, `lime` draws a sample from a Uniform(0,1) distribution and uses the bin information to compute a sample drawn from the feature distribution.
+\end{quote}
+
+\item Predictions for the testing data using the random forest model are computed.
+
+\begin{quote}
+The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
+Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
+\end{quote}
+
+\item Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
+
+\begin{quote}
+The way that the similarity score is computed depends on the type of feature.
+Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
+Then, by default, the Gower distance is used to compute the similarity score.
+(using the `gower` package in R)
+\end{quote}
+
+\item Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value.
+The 0-1 versions of the features are used.
+
+\begin{quote}
+The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
+\begin{enumerate}
+\item forward selection with ridge regression
+\item highest weight with ridge regression
+\item LASSO model
+\item tree model
+\item default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
+\end{enumerate}
+\end{quote}
+
+\item A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
+If the response is categorical, the user can select how many categories and which categories they want to explain.
+
+  $$P(Match = TRUE) = \beta_0 + 
+  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
+  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
+  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
+
+For the prediction of interest,
+
+  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
+
+\item The feature weights are extracted and used as the explanations.
+
+\end{enumerate}
 
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(case:feature_desc, feature_number:feature_bin, data, prediction)
+    select(case:feature_desc, feature_bin:strictly_less, data, prediction)
 
@@
 
+```{r}
+# Check to see if model_prediction is the sum of the coefficients from the simple model
+hamby224_test_explain %>% 
+  filter(case == 1) %>%
+  select(model_intercept, feature, feature_weight, model_prediction, rfscore)
+
+simple_model <-  data.frame(term = c("intercept", 
+                    as.character(hamby224_test_explain %>% filter(case == 1) %>% pull(feature))),
+           coefficients = c(subset(hamby224_test_explain, case == 1)$model_intercept[1],
+                            hamby224_test_explain %>% filter(case == 1) %>% pull(feature_weight)))
+
+# It is!
+sum(simple_model$coefficients)
+subset(hamby224_test_explain, case == 1)$model_prediction[1]
+```
+
+```{r}
+check <- hamby224_test_explain %>%
+  select(-data, -prediction) %>%
+  group_by(case) %>%
+  slice(1) %>%
+  select(case, set, rfscore, model_prediction) %>%
+  mutate(diff = rfscore - model_prediction,
+         mean = (rfscore + model_prediction) / 2)
+
+sum((subset(check$diff, check$set == "Set 1"))^2, na.rm = TRUE)
+sum((subset(check$diff, check$set == "Set 11"))^2, na.rm = TRUE)
+```
+
+Below is are plots of the probability of a match computed from the "simple" (ridge regression) model in `lime` versus the probability of a match computed from the `rtrees` random forest model for both the Hamby224 Set 1 and Set 11 test cases.
+Linear regression lines have been fit through the points.
+Both plots show that there is a weak negative linear relationship between the two variables.
+This suggests that as the probability of a match increases in the random forest, the simple model is doing a worse job of computing a probability that agrees with the random forest model.
+However, the Hamby 224 test sets 1 and 11 do not have many observations with high random forest scores.
+Each test set should only have 18 matches.
+The trend may be different if there was more cases with high random forest scores.
+However, it appears that the cases that are a match have some of the lowest model_prediction scores overall.
+
+```{r fig.width = 6, fig.height = 4}
+ggplot(check, aes(x = rfscore, y = model_prediction)) + 
+  geom_point() + 
+  facet_grid( ~ set) + 
+  theme_bw() + 
+  stat_smooth(method = "lm")
+```
+
+The plots below show the absolute value of the difference between the random forest probability and the simple model probabilty versus the random forest probability.
+These plots show a clear v-shaped trend that suggests that the simple model is doing the best job of replicating the random forest probabilty around the random forest probability of 0.5.
+That is, the simple model seems to be doing a worse job of computing accurate predictions in the extremes of the random forest scores.
+
+```{r fig.width = 6, fig.height = 4}
+ggplot(check, aes(x = rfscore, y = abs(diff))) + 
+  geom_point() + 
+  facet_grid( ~ set) +
+  theme_bw()
+```
+
+The plot below shows the difference of the two model probabilities versus the random forest score.
+This shows that when the random forest score is low, the simple model is over estimating the probability, and when the random forest score is high, the simple model is underestimating the probability.
+
+```{r fig.width = 6, fig.height = 4}
+ggplot(check, aes(x = rfscore, y = diff)) + 
+  geom_point() + 
+  facet_grid( ~ set) +
+  geom_hline(yintercept = 0, color = "blue") +
+  theme_bw()
+```
+
 ## Visualizing the LIME Explanations
-
-Thoughts on the visualizations:
-
-- It would be interesting to see the "magnitude" associated with a variable for a prediction, but
-  this would require obtaining the scaled values of the perturbations.
-- This seems much more meaningful to me than just the model coefficient associated with the variable.
-- The current version shows which variables in the model have the largest coefficients.
-- However, the importance of the variable might change depending on the observed value associated
-  with the prediction of interest.
 

### 2018-11-06 app/app.R
added bin table to app

@@ -7,6 +7,7 @@ library(dplyr)
 library(tidyr)
 library(plotly)
 library(cowplot)
+library(gridExtra)
 
 ## ------------------------------------------------------------------------------------
 ## Data Steps
@@ -14,6 +15,36 @@ library(cowplot)
 
 # Input data
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_bins <- read.csv("../data/hamby_bins.csv")
+
+# Function for creating a table with the bin information relating to specified features
+bin_table <- function(features, bin_cuts = hamby224_bins){
+  
+  # Subset the bin cuts table to the selected feature
+  selected_bin_cuts <- bin_cuts %>% 
+    filter(Feature %in% features) %>% 
+    mutate_if(is.numeric, ~round(., 2))
+  
+  # Create an empty matrix to put the bins in
+  table_matrix <- matrix(numeric(3*4), nrow = 3)
+  
+  # Create the bins and put in the matrix
+  for(i in 1:3){
+    table_matrix[i,] <- c(paste0("(", "-\U221E, ", selected_bin_cuts[i,2], "]"),
+                          paste0("(", selected_bin_cuts[i,2], ", ", selected_bin_cuts[i,3], "]"),
+                          paste0("(", selected_bin_cuts[i,3], ", ", selected_bin_cuts[i,4], "]"), 
+                          paste0("(", selected_bin_cuts[i,4], ", ", "\U221E)"))
+  }
+  
+  # Turn the matrix into a dataframe
+  table <- data.frame(Feature = features, table_matrix) %>%
+    rename("Lower Bin" = "X1", "Lower Middle Bin" = "X2", 
+           "Upper Middle Bin" = "X3", "Upper Bin" = "X4")
+  
+  # Return the bin dataframe
+  return(table)
+  
+}
 
 ## ------------------------------------------------------------------------------------
 ## UI Setup
@@ -26,13 +57,13 @@ ui <- fluidPage(
    titlePanel("LIME Explanations for Bullet Matching"),
    
    # Set selector
-   fluidRow(column(3, selectInput("set", 
+   column(6, selectInput("set", 
                         label = "Select a Hamby 224 dataset", 
-                        choices = c("Set 1", "Set 11")))),
+                        choices = c("Set 1", "Set 11")),
+          plotlyOutput("tileplot")),
 
    # Panel for plots
[…]

### 2018-11-06 paper/paper.Rmd
worked more on LIME description

@@
 
-LIME was developed by Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin in response to the issue of black box prediction models, which are complex models that may produce accurate predictions but do not allow for interpretability.
-The LIME algorithm can be applied to any predictive model.
-It provides an explanation for an individual prediction of interest by fitting a linear regression model in a local region around the prediction.
-Linear regression models contain a well known form and coefficients that can be interpreted.
+Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin developed LIME in response to the interpretabiliby issue of many machine learning techniques.
+Many models used in machine learning are referred to as black box prediction models since they are complex models that may provide accurate predictions but are not able to be interpreted.
+That is, it is not possible to understand the relationship between the features and the response variable.
+Without being able to interpret the models, it becomes difficult to diagnose why a model is producing the predictions that it is.
+The developers claim that LIME allows users to check which variables are driving the predictions made by the model.
+This further allows users to determine whether their model is trustworthy.
+
+LIME was designed to be a generalized algorithm that can be applied to any predictive model to return an "explanation" for an individual prediction of interest.
+This explanation is meant to convey which features from the model are driving the prediction created by the complex model.
+In the next section, I will provide a detailed description of how the LIME algorithm obtains the explanation when applied to a random forest model with numeric features.
+For now, general overview of the LIME algorithm will be explained.
+
+Suppose that a complex model has been fit on a training dataset with $k$ features and a response variable that may either be numeric or categorical.
+This trained model will be applied to a testing dataset containing the $k$ features to obtain predictions.
+It is of interest to understand which variables played an important role in the predictions.
+LIME will be applied to one of the cases in the testing dataset to obtain an explanation.
+To create the explanation, LIME starts by approximating the distribution of each of the $k$ features in the training dataset.
+It then simulates a large dataframe from these distributions.
+The simulated data are used to perform feature selection to determine the $m$ most important features.
+Then a weighted ridge regression model is fit to standardized versions of the selected $m$ features from the simulated data.
+The model assigns higher weights to observations closer to the observed case of interest.
+A linear model is used since it has a well known form and coefficients that can be interpreted.
+The coefficients from the model are extracted and used to "explain" the importance of the variables.
+Features with a larger absolute value of their coefficient are implied to play a larger role in the creation of the prediction.
+
+## Applying LIME
 
 The developers of LIME wrote a Python package to implement LIME, and Thomas Lin Pedersen adapted their work to create an R package called `lime`.
-This paper will use version `r packageVersion("lime")` of the R package `lime`.
+This paper will use version `r packageVersion("lime")` of the R package `lime` in the analysis of the bullet matching data.
 The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
@@
 Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
+
+Let
+  $$Y_{jk} = \begin{cases} 
+  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
+  0 & \mbox{otherwise}
+  \end{cases}$$
+be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
 
@@
 
-## Applying LIME
-
-```{r echo = FALSE}
+```{r}
 # Apply the lime function if the file does not already exist
@@
 
-```{r echo = FALSE}
+```{r}
+if (!file.exists("../data/hamby_bins.csv")) {
+
+  # Create a dataframe of bins cuts
+  hamby_bins <- data.frame(matrix(unlist(hamby224_lime$bin_cuts), 
+                                  nrow = 9, byrow = TRUE)) %>%
+      rename("Q0" = X1, "Q25" = X2, "Q50" = X3, "Q75" = X4, "Q100" = X5) %>%
+      mutate(Feature = rf_features) %>%
+      select(Feature, Q0:Q100)
+
+  # Save the bin cuts
+  write.csv(hamby_bins, "../data/hamby_bins.csv", row.names = FALSE)
+
+} else {
+
+  # Load in the bins csv
+  hamby_bins <- read.csv("../data/hamby_bins.csv")
+
+}
+```
+
+```{r}
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value){
+bin_labeller <- function(feature, feature_value, bin_cuts = hamby_bins){
 
@@
 
-    # Create a dataframe of bins cuts
-    bin_cuts <- data.frame(matrix(unlist(hamby224_lime$bin_cuts), nrow = 9, byrow = TRUE)) %>%
-      rename("Q0" = X1, "Q25" = X2, "Q50" = X3, "Q75" = X4, "Q100" = X5) %>%
-      mutate(Feature = rf_features) %>%
-      select(Feature, Q0:Q100)
-
     # Subset the bin cuts table to the selected feature
@@
       feature_bin <- paste(feature, "(lower bin)")
-    } else if (feature_bin_cuts$Q25 < feature_value & feature_value <= feature_bin_cuts$Q50){
+    } else if (feature_bin_cuts$Q25 < feature_value & 
+               feature_value <= feature_bin_cuts$Q50){
       feature_bin <- paste(feature, "(lower middle bin)")
-    } else if (feature_bin_cuts$Q50 < feature_value & feature_value <= feature_bin_cuts$Q75){
+    } else if (feature_bin_cuts$Q50 < feature_value & 
+               feature_value <= feature_bin_cuts$Q75){
       feature_bin <- paste(feature, "(upper middle bin)")
@@
            feature = factor(feature),
-           feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
+           feature_bin = mapply(bin_labeller, feature = feature, 
+                                feature_value = feature_value)) %>%
     mutate(feature_number = readr::parse_number(feature_desc),
@@
   # Finish creating the strictly less than variable
-  hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
+  hamby224_test_explain$strictly_less[grep("< ", 
+                                           hamby224_test_explain$feature_desc)] <- TRUE
 
@@
   slice(1) %>%
-  select(case, set, rfscore, model_prediction) %>%
+  select(case, set, rfscore, model_prediction, model_r2) %>%
   mutate(diff = rfscore - model_prediction,
@@
 
-```{r fig.width = 6, fig.height = 4}
+THe points are also colored by the $R^2$ value from the simple model.
+This plot suggests that the simple models with a prediction close to 0.5 have a better fit, but the $R^2$ values are still low.
+I am not sure what to make of this.
+However, it does not appear that the $R^2$ is related to the probability from the random forest.
+
+```{r fig.width = 8, fig.height = 4}
 ggplot(check, aes(x = rfscore, y = model_prediction)) + 
-  geom_point() + 
+  geom_point(aes(color = model_r2)) + 
   facet_grid( ~ set) + 
@@
 
-```{r fig.width = 6, fig.height = 4}
+```{r fig.width = 8, fig.height = 4}
 ggplot(check, aes(x = rfscore, y = abs(diff))) + 
-  geom_point() + 
+  geom_point(aes(color = model_r2)) + 
   facet_grid( ~ set) +
@@
 
-```{r fig.width = 6, fig.height = 4}
+```{r fig.width = 8, fig.height = 4}
 ggplot(check, aes(x = rfscore, y = diff)) + 
-  geom_point() + 
+  geom_point(aes(color = model_r2)) + 
   facet_grid( ~ set) +
@@
       scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-      theme(axis.text.x = element_text(angle = 45, hjust = 1),
-            strip.text.x = element_blank(),
-            strip.text.y = element_blank()) +
-      labs(x = "Known 1                            Known 2                            Questioned", 
-           y = "Known 1                            Known 2                            Questioned", 
-           fill = "RF Score")
+      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+      labs(x = "", y = "", fill = "RF Score")
 ```

### 2018-11-13 paper/paper.Rmd
made bin functions generalizable and added feature distribution plots

@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, fig.pos = "center")
 
@@
 library(bulletr)
+library(randomForest)
 library(lime)
-library(randomForest)
+library(cowplot)
 ```
@@
 
+```{r}
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+```
+
+```{r fig.height = 5, fig.width = 8}
+# Create plots of the feature distributions colored by samesource for the training data
+hamby173and252_train %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+```{r fig.height = 5, fig.width = 8}
+# Create plots of the feature distributions colored by samesource for the training data
+# using the position = "fill" option
+hamby173and252_train %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(position = "fill", bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+```{r fig.height = 4, fig.width = 9}
+# Create a correlation heatmap of the match comparisons in the training data
+cor_match <- hamby173and252_train %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == TRUE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") + 
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Match Comparisons")
+
+# Create a correlation heatmap of the non-match comparisons in the training data
+cor_nonmatch <- hamby173and252_train %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == FALSE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") +
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Non-Match Comparisons")
+
+# Create a title for the panel of plots
+cor_title <- ggdraw() +
+  draw_label("Correlation of Feature Variables in the Training Data", 
+             fontface = "bold", 
+             size = 16,
+             x = 0.5,
+             hjust = 0.5)
+
+# Create a joined legend for the panel of plots
+cor_legend <- get_legend(cor_match + theme(legend.position = "right"))
+
+# Create the panel of plots
+plot_grid(cor_title, 
+          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
+          ncol = 1,
+          rel_heights = c(0.25, 3))
+```
+
 ## Testing Data: The Hamby 224 Clone
@@
 ```{r}
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
-
 # If the test data does not exist, clean the data, create the test data, and save it
@@
            set = factor("Set 1"),
-           bullet1 = recode(factor(bullet1), "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-           bullet2 = recode(factor(bullet2), "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-           land1 = recode(factor(land1), "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
+           bullet1 = recode(factor(bullet1), 
+                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
+           bullet2 = recode(factor(bullet2), 
+                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
+           land1 = recode(factor(land1), 
+                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                           "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
-           land2 = recode(factor(land2), "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
+           land2 = recode(factor(land2), 
+                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                           "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
@@
            set = factor("Set 11"),
-           bullet1 = recode(factor(bullet1), "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
+           bullet1 = recode(factor(bullet1), 
+                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                             "Bullet I" = "Questioned"),
-           bullet2 = recode(factor(bullet2), "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
+           bullet2 = recode(factor(bullet2), 
+                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                             "Bullet I" = "Questioned")) %>%
@@
 
-Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin developed LIME in response to the interpretabiliby issue of many machine learning techniques.
+Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin developed LIME in response to the interpretation issue of many machine learning techniques.
 Many models used in machine learning are referred to as black box prediction models since they are complex models that may provide accurate predictions but are not able to be interpreted.
@@
   hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
-                        model = as_classifier(rtrees))
+                        model = as_classifier(rtrees),
+                        n_bins = 6)
 
@@
                                     hamby224_lime,
-                                    labels = "FALSE",
+                                    labels = "TRUE",
                                     n_features = 3)
@@
 ```{r}
+# Function for writing bins given the bin boundaries
+write_bins <- function(bin_data){
+
+  # Compute the number of bins based the input dataframe
+  nbins = length(bin_data) - 2
+
+  # Create an empty matrix to store the bins in
+  row <- matrix(NA, nrow = 1, ncol = nbins + 1)
+
+  # Put the feature name in the first column
+  row[,1] <- as.character(bin_data[[1]])
+
+  # Put the 1st through 2nd to last bins in the 2nd through 2nd to last columns
+  row[,2:nbins] <- sapply(2:nbins, 
+                          FUN = function(number) sprintf("[%.2f, %.2f)", 
+                                                         as.numeric(bin_data[number]),
+                                                         as.numeric(bin_data[number + 1])))
+
+  # Fill in the last column with the upper bin (based on whether it should be infinite or not)
+  row[,nbins + 1] <- ifelse(is.na(bin_data[nbins + 2]),
+                            sprintf("(%.2f, %s)", as.numeric(bin_data[nbins + 1]), "\U221E"),
+                            sprintf("(%.2f, %.2f]", as.numeric(bin_data[nbins + 1]),
+                                    as.numeric(bin_data[nbins + 2])))
+
+  return(row)
+
+}
+```
+
+```{r}
+# Create a dataframe with the bins
 if (!file.exists("../data/hamby_bins.csv")) {
 
-  # Create a dataframe of bins cuts
-  hamby_bins <- data.frame(matrix(unlist(hamby224_lime$bin_cuts), 
-                                  nrow = 9, byrow = TRUE)) %>%
-      rename("Q0" = X1, "Q25" = X2, "Q50" = X3, "Q75" = X4, "Q100" = X5) %>%
-      mutate(Feature = rf_features) %>%
-      select(Feature, Q0:Q100)
+  # Determine the nubmer of bins
+  nbins <- length(hamby224_lime$bin_cuts[[1]]) - 1
+
+  # Create a dataframe of bin boundaries
+  hamby_divisions <- data.frame(Feature = rf_features, 
+                                Lower = c(0, -1, 0, 0, 0, 0, 0, 0, 0),
+                           matrix(unlist(hamby224_lime$bin_cuts), nrow = 9, 
+                                  byrow = TRUE)[,2:nbins],
+                           Upper = c(1, 1, rep(NA, 7)))
+
+  # Use my function "write_bins" to create a dataframe with the bins
+  hamby_bins <- data.frame(t(apply(hamby_divisions, 1, write_bins)))
+
+  # Assign appropriate names to the bin columns
+  names(hamby_bins) <- c("Feature", "Lower Bin", 
+                         sapply(1:(nbins-2), function(bin) sprintf("Middle Bin %.0f", bin)),
+                         "Upper Bin")
 
@@
 
+  # Replace the periods with spaces in the feature names
+  names(hamby_bins) <- gsub(".", " ", names(hamby_bins), fixed = TRUE)
+
 }
@@
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, bin_cuts = hamby_bins){
+bin_labeller <- function(feature, feature_value, bin_data = hamby_divisions){
 
@@
     # Subset the bin cuts table to the selected feature
-    feature_bin_cuts <- bin_cuts %>% filter(Feature == feature)
+    feature_bin_data <- bin_data %>%
+      filter(Feature == feature) %>%
+      select(-Feature, -Lower, -Upper)
+
+    # Compute the number of bins based the input dataframe
+    nbins = length(bin_data) - 2
 
     # Determine which bin the case falls in
-    if(feature_value <= feature_bin_cuts$Q25){
+    if(feature_value <= feature_bin_data[1]){
       feature_bin <- paste(feature, "(lower bin)")
-    } else if (feature_bin_cuts$Q25 < feature_value & 
-               feature_value <= feature_bin_cuts$Q50){
-      feature_bin <- paste(feature, "(lower middle bin)")
-    } else if (feature_bin_cuts$Q50 < feature_value & 
-               feature_value <= feature_bin_cuts$Q75){
-      feature_bin <- paste(feature, "(upper middle bin)")
-    } else if (feature_bin_cuts$Q75 < feature_value){
+    } else if (feature_bin_data[nbins - 1] < feature_value){
       feature_bin <- paste(feature, "(upper bin)")
+    } else {
+      middle_bin_checks <- data.frame(middle_bin_number = 1:(nbins-2),
+                                      contained = sapply(1:(nbins - 2),
+                                                         FUN = function(number) {
+                                                           feature_bin_data[number] < feature_value &
+                                                           feature_value <= feature_bin_data[number + 1]}))
+      feature_bin <- sprintf("%s (middle bin %.0f)", 
+                             feature,
+                             middle_bin_checks %>% filter(contained == TRUE) %>% pull(middle_bin_number))
     }
@@
 ```{r}
-# Check to see if model_prediction is the sum of the coefficients from the simple model
-hamby224_test_explain %>% 
-  filter(case == 1) %>%
-  select(model_intercept, feature, feature_weight, model_prediction, rfscore)
-
-simple_model <-  data.frame(term = c("intercept", 
-                    as.character(hamby224_test_explain %>% filter(case == 1) %>% pull(feature))),
-           coefficients = c(subset(hamby224_test_explain, case == 1)$model_intercept[1],
-                            hamby224_test_explain %>% filter(case == 1) %>% pull(feature_weight)))
-
-# It is!
-sum(simple_model$coefficients)
-subset(hamby224_test_explain, case == 1)$model_prediction[1]
-```
-
-```{r}
 check <- hamby224_test_explain %>%
@@
 
-THe points are also colored by the $R^2$ value from the simple model.
+The points are also colored by the $R^2$ value from the simple model.
 This plot suggests that the simple models with a prediction close to 0.5 have a better fit, but the $R^2$ values are still low.
@@
 
-The plots below show the absolute value of the difference between the random forest probability and the simple model probabilty versus the random forest probability.
-These plots show a clear v-shaped trend that suggests that the simple model is doing the best job of replicating the random forest probabilty around the random forest probability of 0.5.
+The plots below show the absolute value of the difference between the random forest probability and the simple model probability versus the random forest probability.
+These plots show a clear v-shaped trend that suggests that the simple model is doing the best job of replicating the random forest probability around the random forest probability of 0.5.
 That is, the simple model seems to be doing a worse job of computing accurate predictions in the extremes of the random forest scores.

### 2018-11-13 app/app.R

@@ -17,32 +17,24 @@ library(gridExtra)
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 hamby224_bins <- read.csv("../data/hamby_bins.csv")
 
+# Replace the periods with spaces in the feature names
+names(hamby_bins) <- gsub(".", " ", names(hamby_bins), fixed = TRUE)
+
+## ------------------------------------------------------------------------------------
+## Functions
+## ------------------------------------------------------------------------------------
+
 # Function for creating a table with the bin information relating to specified features
 bin_table <- function(features, bin_cuts = hamby224_bins){
-  
+
   # Subset the bin cuts table to the selected feature
   selected_bin_cuts <- bin_cuts %>% 
-    filter(Feature %in% features) %>% 
-    mutate_if(is.numeric, ~round(., 2))
-  
-  # Create an empty matrix to put the bins in
-  table_matrix <- matrix(numeric(3*4), nrow = 3)
-  
-  # Create the bins and put in the matrix
-  for(i in 1:3){
-    table_matrix[i,] <- c(paste0("(", "-\U221E, ", selected_bin_cuts[i,2], "]"),
-                          paste0("(", selected_bin_cuts[i,2], ", ", selected_bin_cuts[i,3], "]"),
-                          paste0("(", selected_bin_cuts[i,3], ", ", selected_bin_cuts[i,4], "]"), 
-                          paste0("(", selected_bin_cuts[i,4], ", ", "\U221E)"))
-  }
-  
-  # Turn the matrix into a dataframe
-  table <- data.frame(Feature = features, table_matrix) %>%
-    rename("Lower Bin" = "X1", "Lower Middle Bin" = "X2", 
-           "Upper Middle Bin" = "X3", "Upper Bin" = "X4")
+    filter(Feature %in% features) %>%
+    mutate(Feature = factor(Feature, levels = features)) %>%
+    arrange(Feature)
   
   # Return the bin dataframe
-  return(table)
+  return(selected_bin_cuts)
   
 }
 
@@ -97,24 +89,26 @@ server <- function(input, output) {
       geom_tile(aes(fill = rfscore)) +
       facet_grid(bullet2 ~ bullet1, scales = "free") +
       theme_minimal() +
-      scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
[…]

### 2018-11-13 code/comparing caret and randomForest with LIME.R
wrote some code for comparing rf to caret in LIME

@@ -1,0 +1,71 @@
+# Code for comparing the output from LIME when the model is 
+# fit with caret and randomForest
+# Last Updated: 2018/11/13
+
+## Set up -----------------------------------------------------------------------------
+
+# Load libraries
+library(caret)
+library(lime)
+library(randomForest)
+
+# Split up the data set
+iris_test <- iris[1:5, 1:4]
+iris_train <- iris[-(1:5), 1:4]
+iris_lab <- iris[[5]][-(1:5)]
+
+## LIME with caret --------------------------------------------------------------------
+
+# Create Random Forest model on iris data
+caret_model <- train(iris_train, iris_lab, method = 'rf')
+
+# Create an explainer object
+caret_explainer <- lime(iris_train, caret_model)
+
+# Explain new observation
+caret_explanation <- explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
+
+# The output is provided in a consistent tabular format and includes the
+# output from the model.
+head(caret_explanation)
+
+## LIME with randomForest -------------------------------------------------------------
+
+rf_model <- randomForest(iris_train, iris_lab)
+
+# Create an explainer object
+rf_explainer <- lime(iris_train, model = as_classifier(rf_model))
+
+# Explain new observation
+rf_explanation <- explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
+
+# The output is provided in a consistent tabular format and includes the
+# output from the model.
+head(rf_explanation)
+
+## Comparisons -----------------------------------------------------------------------
+
+# Grab the numeric caret explanation variables of interest
+caret_numeric <- caret_explanation %>%
+  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
+  gather(key = "variable", value = "caret_value")
+
+# Grab the numeric randomForest explanation variables of interest
+rf_numeric <- rf_explanation %>%
+  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
+  gather(key = "variable", value = "rf_value")
+
+# Join the two
+lime_numeric <- caret_numeric %>%
+  mutate(rf_value = rf_numeric$rf_value, 
+         variable = factor(variable))
+
+# Look at the MSEs for the variables
+lime_numeric %>%
+  group_by(variable) %>%
+  summarise(MSE = sum((caret_value - rf_value)^2))
+
+# Scatterplots of the randomForest versus caret variable values
[…]

### 2018-11-13 app/app.R
fixed bin data name

@@ -18,7 +18,7 @@ hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 hamby224_bins <- read.csv("../data/hamby_bins.csv")
 
 # Replace the periods with spaces in the feature names
-names(hamby_bins) <- gsub(".", " ", names(hamby_bins), fixed = TRUE)
+names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)
 
 ## ------------------------------------------------------------------------------------
 ## Functions

### 2018-11-13 code/comparing caret and randomForest with LIME.R
fixed MSE

@@ -63,7 +63,7 @@ lime_numeric <- caret_numeric %>%
 # Look at the MSEs for the variables
 lime_numeric %>%
   group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2))
+  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
 
 # Scatterplots of the randomForest versus caret variable values
 ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 

### 2018-11-13 code/helper_functions.R
moved paper functions to an R script

@@ -1,0 +1,78 @@
+## Helper fFunctions for the Paper
+
+## ---------------------------------------------------------------
+## Write Bin Dataframe 
+## ---------------------------------------------------------------
+
+# Function for writing bins given the bin boundaries
+write_bins <- function(bin_data){
+  
+  # Compute the number of bins based the input dataframe
+  nbins = length(bin_data) - 2
+  
+  # Create an empty matrix to store the bins in
+  bin_matrix <- matrix(NA, nrow = 1, ncol = nbins + 1)
+  
+  # Put the feature name in the first column
+  bin_matrix[,1] <- as.character(bin_data[[1]])
+  
+  # Put the 1st through 2nd to last bins in the 2nd through 2nd to last columns
+  bin_matrix[,2:nbins] <- sapply(2:nbins, 
+                          FUN = function(number) sprintf("[%.2f, %.2f)", 
+                                                         as.numeric(bin_data[number]),
+                                                         as.numeric(bin_data[number + 1])))
+  
+  # Fill in the last column with the upper bin (based on whether it should be infinite or not)
+  bin_matrix[,nbins + 1] <- ifelse(is.na(bin_data[nbins + 2]),
+                            sprintf("(%.2f, %s)", as.numeric(bin_data[nbins + 1]), "\U221E"),
+                            sprintf("(%.2f, %.2f]", as.numeric(bin_data[nbins + 1]),
+                                    as.numeric(bin_data[nbins + 2])))
+  
+  return(bin_matrix)
+  
+}
+
+## ---------------------------------------------------------------
+## Label Feature Bins
+## ---------------------------------------------------------------
+
+# Function to use for creating bin labels in the test_explain dataset
+bin_labeller <- function(feature, feature_value, bin_data = hamby_divisions){
+  
+  if (is.na(feature)) {
+    
+    # Set feature_bin to NA if feature is NA
+    feature_bin <- NA
+    
+  } else {
+    
+    # Subset the bin cuts table to the selected feature
+    feature_bin_data <- bin_data %>%
+      filter(Feature == feature) %>%
+      select(-Feature, -Lower, -Upper)
+    
+    # Compute the number of bins based the input dataframe
+    nbins = length(bin_data) - 2
+    
+    # Determine which bin the case falls in
+    if(feature_value <= feature_bin_data[1]){
+      feature_bin <- paste(feature, "(lower bin)")
+    } else if (feature_bin_data[nbins - 1] < feature_value){
+      feature_bin <- paste(feature, "(upper bin)")
+    } else {
[…]

### 2018-11-13 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
changed paper file name

--- 2018-11-13 paper/paper.Rmd
@@
 library(cowplot)
+
+# Source functions
+source("../code/helper_functions.R")
 ```
@@
                         model = as_classifier(rtrees),
-                        n_bins = 6)
+                        n_bins = 4)
 
@@
 ```{r}
-# Function for writing bins given the bin boundaries
-write_bins <- function(bin_data){
-
-  # Compute the number of bins based the input dataframe
-  nbins = length(bin_data) - 2
-
-  # Create an empty matrix to store the bins in
-  row <- matrix(NA, nrow = 1, ncol = nbins + 1)
-
-  # Put the feature name in the first column
-  row[,1] <- as.character(bin_data[[1]])
-
-  # Put the 1st through 2nd to last bins in the 2nd through 2nd to last columns
-  row[,2:nbins] <- sapply(2:nbins, 
-                          FUN = function(number) sprintf("[%.2f, %.2f)", 
-                                                         as.numeric(bin_data[number]),
-                                                         as.numeric(bin_data[number + 1])))
-
-  # Fill in the last column with the upper bin (based on whether it should be infinite or not)
-  row[,nbins + 1] <- ifelse(is.na(bin_data[nbins + 2]),
-                            sprintf("(%.2f, %s)", as.numeric(bin_data[nbins + 1]), "\U221E"),
-                            sprintf("(%.2f, %.2f]", as.numeric(bin_data[nbins + 1]),
-                                    as.numeric(bin_data[nbins + 2])))
-
-  return(row)
-
-}
-```
-
-```{r}
 # Create a dataframe with the bins
@@
   # Assign appropriate names to the bin columns
+  if (nbins == 2){
+    names(hamby_bins) <- c("Feature", "Lower Bin", "Upper Bin")
+  } else {
     names(hamby_bins) <- c("Feature", "Lower Bin", 
-                         sapply(1:(nbins-2), function(bin) sprintf("Middle Bin %.0f", bin)),
+                           sapply(1:(nbins-2), 
+                                  function(bin) sprintf("Middle Bin %.0f", bin)),
                            "Upper Bin")
+  }
 
@@
 ```{r}
-# Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, bin_data = hamby_divisions){
-
-  if (is.na(feature)) {
-
-    # Set feature_bin to NA if feature is NA
-    feature_bin <- NA
-
-  } else {
-
-    # Subset the bin cuts table to the selected feature
-    feature_bin_data <- bin_data %>%
-      filter(Feature == feature) %>%
-      select(-Feature, -Lower, -Upper)
-
-    # Compute the number of bins based the input dataframe
-    nbins = length(bin_data) - 2
-
-    # Determine which bin the case falls in
-    if(feature_value <= feature_bin_data[1]){
-      feature_bin <- paste(feature, "(lower bin)")
-    } else if (feature_bin_data[nbins - 1] < feature_value){
-      feature_bin <- paste(feature, "(upper bin)")
-    } else {
-      middle_bin_checks <- data.frame(middle_bin_number = 1:(nbins-2),
-                                      contained = sapply(1:(nbins - 2),
-                                                         FUN = function(number) {
-                                                           feature_bin_data[number] < feature_value &
-                                                           feature_value <= feature_bin_data[number + 1]}))
-      feature_bin <- sprintf("%s (middle bin %.0f)", 
-                             feature,
-                             middle_bin_checks %>% filter(contained == TRUE) %>% pull(middle_bin_number))
-    }
-
-  }
-
-  # Return the bin
-  return(feature_bin)
-
-}
-```
-
-```{r}
 # Create the test_explain combined data if the file does not already exist
@@
   # Join the data and the explanations and edit and add additional variables
+  # Create the feature bin labels using my function "bin_labeller"
   hamby224_test_explain <- hamby224_test %>%
@@
            feature_desc = factor(feature_desc),
-           feature = factor(feature),
            feature_bin = mapply(bin_labeller, feature = feature, 
@@
     mutate(feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE)
+           strictly_less = FALSE, 
+           feature = factor(feature))
 
@@
   slice(1) %>%
-  select(case, set, rfscore, model_prediction, model_r2) %>%
+  ungroup() %>%
+  select(case, set, rf_features, rfscore, model_prediction, model_r2) %>%
   mutate(diff = rfscore - model_prediction,
@@
 sum((subset(check$diff, check$set == "Set 11"))^2, na.rm = TRUE)
+
+check %>%
+  filter(set == "Set 1") %>%
+  select(rf_features, diff, -case) %>%
+  gather(key = feature, value = feature_value, rf_features) %>%
+  select(feature, feature_value, diff) %>%
+  ggplot(aes(x = feature_value, y = diff)) + 
+  geom_point() + 
+  facet_wrap( ~ feature, scales = "free") + 
+  geom_hline(yintercept = 0, color = "blue")
 ```
@@
 
+Ideas for improvement of LIME: 
+  - change the binning method
+
 # References

### 2018-11-13 code/helper_functions.R
typo

@@ -1,4 +1,4 @@
-## Helper fFunctions for the Paper
+## Helper Functions for the Paper
 
 ## ---------------------------------------------------------------
 ## Write Bin Dataframe 

### 2018-11-13 app/app.R
started working on coloring table

@@ -212,7 +212,7 @@ server <- function(input, output) {
         # Grab and order the features for the bin table
         selected_features <- selected_comparison %>%
           arrange(desc(abs(feature_weight))) %>%
-          select(feature, feature_weight)
+          select(feature, feature_weight, evidence)
         
         # Create a table with the bin cuts
         table <- tableGrob(bin_table(selected_features$feature), 
@@ -220,7 +220,8 @@ server <- function(input, output) {
                            rows = NULL)
         
         # Create a grid of plotting components
-        plot_grid(title, subtitle, feature_plot, legend, table, ncol = 1, rel_heights = c(0.05, 0.5, 0.8, 0.05, 0.4))
+        plot_grid(title, subtitle, feature_plot, legend, table, ncol = 1, 
+                  rel_heights = c(0.05, 0.5, 0.8, 0.05, 0.4))
         
       } else{
         

### 2018-11-13 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
added a section for ideas to improve LIME

@@
 Ideas for improvement of LIME: 
-  - change the binning method
+  - change the binning method:
+    - lime is not good with linear relationships with classifiers due to the 
+    inside-outside binning - it would be better to use a cumulative approach
+  - consider interactions in the ridge regression model
+  - learn lambda in the ridge regression
 

### 2018-11-18 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
started running lime for different numbers of bins

@@
 library(cowplot)
+library(purrr)
 
@@
 ```{r}
-# Apply the lime function if the file does not already exist
+# Apply the run_lime function if the lime results file does not already exist
 if(!file.exists("../data/hamby224_lime.rds")) {
 
-  # Apply the lime function from the lime package (with a seed set)
-  # Note that the as_classifier must be added since rtrees is from the
-  # randomForest package and not fit using caret or one of the other 
-  # available models specified in the lime package. Additionally, the
-  # randomForest package must be loaded in order to run the functions
-  # from the lime package. (I should check on exactly how this works.)
-  set.seed(84902)
-  hamby224_lime <- lime(x = hamby173and252_train %>% select(rf_features),
-                        model = as_classifier(rtrees),
-                        n_bins = 4)
+  # Specify the number of bins to use
+  nbins = 2:10
 
-  # Save the lime object
+  # Run the lime functions for the specified number of bins 
+  hamby224_all_results <- map(.x = nbins, 
+             .f = run_lime, # run_lime is one of my helper functions
+             train = hamby173and252_train %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3)
+
+  # Separate the lime and explain function results
+  hamby224_lime <- map(hamby224_all_results, function(list) list$lime)
+  hamby224_explain <- map_df(hamby224_all_results, function(list) list$explain)
+
+  # Save the lime and explain results objects
   saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
-
-} else {
-
-  # Load in the lime object
-  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
-
-}
-```
-
-```{r}
-# Apply explain function if the file does not already exist
-if(!file.exists("../data/hamby224_explain.rds")) {
-
-  # Apply the explain function from the lime package (with a seed set)
-  set.seed(84902)
-  hamby224_explain <- lime::explain(hamby224_test %>% 
-                                      arrange(case) %>% 
-                                      select(rf_features) %>% 
-                                      na.omit(), 
-                                    hamby224_lime,
-                                    labels = "TRUE",
-                                    n_features = 3)
-
-  # Save the explainer object
   saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
@@
 
-  # Load in the explain object
+  # Load in the lime results object
+  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
   hamby224_explain <- readRDS("../data/hamby224_explain.rds")
@@
 # Create a dataframe with the bins
-if (!file.exists("../data/hamby_bins.csv")) {
+if (!file.exists("../data/hamby224_bins.csv")) {
 
-  # Determine the nubmer of bins
-  nbins <- length(hamby224_lime$bin_cuts[[1]]) - 1
+  # Create a list a dataframes with the bin boundaries and bins 
+  # for the different evaluations of the lime functions
+  hamby224_bin_list <- map(hamby224_lime, create_bin_data)
 
-  # Create a dataframe of bin boundaries
-  hamby_divisions <- data.frame(Feature = rf_features, 
-                                Lower = c(0, -1, 0, 0, 0, 0, 0, 0, 0),
-                           matrix(unlist(hamby224_lime$bin_cuts), nrow = 9, 
-                                  byrow = TRUE)[,2:nbins],
-                           Upper = c(1, 1, rep(NA, 7)))
+  # Save the bin boundaries and the bins as separate dataframes
+  hamby224_bin_boundaries <- map(hamby224_bin_list, function(m) m$boundaries)
+  hamby224_bins <- map(hamby224_bin_list, function(m) m$bins)
 
-  # Use my function "write_bins" to create a dataframe with the bins
-  hamby_bins <- data.frame(t(apply(hamby_divisions, 1, write_bins)))
-
-  # Assign appropriate names to the bin columns
-  if (nbins == 2){
-    names(hamby_bins) <- c("Feature", "Lower Bin", "Upper Bin")
-  } else {
-    names(hamby_bins) <- c("Feature", "Lower Bin", 
-                           sapply(1:(nbins-2), 
-                                  function(bin) sprintf("Middle Bin %.0f", bin)),
-                           "Upper Bin")
-  }
-
-  # Save the bin cuts
-  write.csv(hamby_bins, "../data/hamby_bins.csv", row.names = FALSE)
+  # Save the bin boundaries and bins
+  saveRDS(hamby224_bin_boundaries, "../data/hamby224_bin_boundaries.rds")
+  saveRDS(hamby224_bins, "../data/hamby224_bins.rds")
 
@@
 
-  # Load in the bins csv
-  hamby_bins <- read.csv("../data/hamby_bins.csv")
-
-  # Replace the periods with spaces in the feature names
-  names(hamby_bins) <- gsub(".", " ", names(hamby_bins), fixed = TRUE)
+  # Load in the bin boundaries and bins
+  hamby224_bin_boundaries <- readRDS("../data/hamby224_bin_boundaries.rds")
+  hamby224_bins <- readRDS("../data/hamby224_bins.rds")
 
@@
     mutate(case = as.character(case)) %>%
-    full_join(hamby224_explain, by = "case") %>%
+    full_join(hamby224_explain_results, by = "case") %>%
     mutate(case = factor(case),
-           feature_desc = factor(feature_desc),
-           feature_bin = mapply(bin_labeller, feature = feature, 
-                                feature_value = feature_value)) %>%
+           feature = factor(feature),
+           feature_desc = factor(feature_desc)) %>%
     mutate(feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE, 
-           feature = factor(feature))
+           strictly_less = FALSE) %>%
+    arrange(nbins)
+
+  # mutate(feature_bin = mapply(bin_labeller, feature = feature, 
+  #                               feature_value = feature_value))
 

### 2018-11-18 code/helper_functions.R

@@ -1,7 +1,29 @@
 ## Helper Functions for the Paper
 
 ## ---------------------------------------------------------------
-## Write Bin Dataframe 
+## Run the Lime Functions
+## ---------------------------------------------------------------
+
+# Function for running the lime functions which runs the lime and explain 
+# objects in a list
+run_lime <- function(train, test, rfmodel, nbins, label, nfeatures){
+  
+  # Set a seed
+  set.seed(84902)
+  
+  # Run the lime function
+  lime <- lime(x = train, model = rfmodel, n_bins = nbins)
+  
+  # Run the explain function and add a variable for the number of bins
+  explain <- explain(x = test, explainer = lime, labels = label, n_features = nfeatures) %>%
+    mutate(nbins = nbins)
+  
+  return(list(lime = lime, explain = explain))
+  
+}
+
+## ---------------------------------------------------------------
+## Write the Bins
 ## ---------------------------------------------------------------
 
 # Function for writing bins given the bin boundaries
@@ -33,11 +55,44 @@ write_bins <- function(bin_data){
 }
 
 ## ---------------------------------------------------------------
+## Create a Data Frame with the Bins
+## ---------------------------------------------------------------
+
+create_bin_data <- function(lime_object){
+  
+  # Determine the nubmer of bins
+  nbins <- length(lime_object$bin_cuts[[1]]) - 1
+  
+  # Create a dataframe of bin boundaries
+  bin_boundaries <- data.frame(Feature = rf_features,
+                               Lower = c(0, -1, rep(0, 7)),
+                               matrix(unlist(lime_object$bin_cuts), nrow = 9, 
+                                      byrow = TRUE)[,2:nbins],
+                               Upper = c(1, 1, rep(NA, 7)))
+  
+  # Use my function "write_bins" to create a dataframe with the bins
+  bins <- data.frame(t(apply(bin_boundaries, 1, write_bins)))
+  
+  # Assign appropriate names to the bin columns
+  if (nbins == 2){
+    names(bins) <- c("Feature", "Lower Bin", "Upper Bin")
+  } else {
+    names(bins) <- c("Feature", 
+                     "Lower Bin",
+                     sapply(1:(nbins - 2), function(bin) sprintf("Middle Bin %.0f", bin)),
+                     "Upper Bin")
+  }
+  
+  return(list(boundaries = bin_boundaries, bins = bins))
+  
+}
+
+## ---------------------------------------------------------------
 ## Label Feature Bins
[…]

### 2018-11-19 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
fixed code so it now runs with the dataset with multiple implementations of lime

@@
 To create the explanation, LIME starts by approximating the distribution of each of the $k$ features in the training dataset.
-It then simulates a large dataframe from these distributions.
+It then simulates a large data frame from these distributions.
 The simulated data are used to perform feature selection to determine the $m$ most important features.
@@
 
-  # Specify the number of bins to use
-  nbins = 2:10
+  # Specify the options to use with lime 
+  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
+                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
+                                    nbins = rep(2:10, 2),
+                                    use_density = rep(NA, 18)) %>%
+  mutate(case = 1:length(nbins)) %>%
+  select(case, bin_continuous, nbins, quantile_bins, use_density)
 
   # Run the lime functions for the specified number of bins
-  hamby224_all_results <- map(.x = nbins, 
+  hamby224_all_results <- pmap(.l = as.list(hamby224_lime_cases[1,-1]),
              .f = run_lime, # run_lime is one of my helper functions
@@
 
-  # Save the lime and explain results objects
+  # Name the items in the lime list
+  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_cases[1,])[1], function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
+              hamby224_lime_cases$bin_continuous[case],
+              hamby224_lime_cases$quantile_bins[case],
+              hamby224_lime_cases$nbins[case],
+              hamby224_lime_cases$use_density[case]))
+
+  # Save the lime and explain results objects and the case info
   saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
   saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
+  saveRDS(hamby224_lime_cases, "../data/hamby224_lime_cases.rds")
 
@@
   hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+  hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 
@@
     mutate(case = as.character(case)) %>%
-    full_join(hamby224_explain_results, by = "case") %>%
+    full_join(hamby224_explain, by = "case") %>%
     mutate(case = factor(case),
-           feature = factor(feature),
-           feature_desc = factor(feature_desc)) %>%
-    mutate(feature_number = readr::parse_number(feature_desc),
+           feature_desc = factor(feature_desc),
+           feature_bin = pmap_chr(list(feature = feature, 
+                                 feature_value = feature_value,
+                                 b_c = bin_continuous,
+                                 q_b = quantile_bins,
+                                 n_b = nbins,
+                                 u_d = use_density),
+                            .f = bin_labeller, # bin_labeller is one of my helper functions
+                            bin_data = hamby224_bin_boundaries,
+                            case_info = hamby224_lime_cases)) %>%
+    mutate(feature = factor(feature),
+           nbins = factor(nbins),
+           feature_number = readr::parse_number(feature_desc),
            strictly_less = FALSE) %>%
     arrange(nbins)
-
-  # mutate(feature_bin = mapply(bin_labeller, feature = feature, 
-  #                               feature_value = feature_value))
 
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(case:feature_desc, feature_bin:strictly_less, data, prediction)
+    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
+           data, prediction)
 
@@
 ```{r}
-check <- hamby224_test_explain %>%
+hamby224_lime_comparisons <- hamby224_test_explain %>%
   select(-data, -prediction) %>%
-  group_by(case) %>%
+  group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
   slice(1) %>%
   ungroup() %>%
-  select(case, set, rf_features, rfscore, model_prediction, model_r2) %>%
+  select(bin_continuous, quantile_bins, nbins, use_density, case, set, rf_features, rfscore, model_prediction, model_r2) %>%
   mutate(diff = rfscore - model_prediction,
@@
 
-sum((subset(check$diff, check$set == "Set 1"))^2, na.rm = TRUE)
-sum((subset(check$diff, check$set == "Set 11"))^2, na.rm = TRUE)
+hamby224_lime_comparisons %>%
+  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
+  summarise(mse = (sum(diff)^2) / length(diff)) %>%
+  arrange(set)
 
-check %>%
-  filter(set == "Set 1") %>%
+hamby224_lime_comparisons %>%
+  filter(nbins == "2", set == "Set 1") %>%
   select(rf_features, diff, -case) %>%
@@
 
-```{r fig.width = 8, fig.height = 4}
-ggplot(check, aes(x = rfscore, y = model_prediction)) + 
+```{r fig.width = 8, fig.height = 4, eval = FALSE}
+ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = model_prediction)) + 
   geom_point(aes(color = model_r2)) + 
-  facet_grid( ~ set) + 
+  facet_grid(nbins ~ set) + 
   theme_bw() + 
@@
 
-```{r fig.width = 8, fig.height = 4}
-ggplot(check, aes(x = rfscore, y = abs(diff))) + 
+```{r fig.width = 8, fig.height = 4, eval = FALSE}
+ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = abs(diff))) + 
   geom_point(aes(color = model_r2)) + 
-  facet_grid( ~ set) +
+  facet_grid(nbins ~ set) +
   theme_bw()
@@
 
-```{r fig.width = 8, fig.height = 4}
-ggplot(check, aes(x = rfscore, y = diff)) + 
+```{r fig.width = 8, fig.height = 4, eval = FALSE}
+ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = diff)) + 
   geom_point(aes(color = model_r2)) + 
-  facet_grid( ~ set) +
+  facet_grid(nbins ~ set) +
   geom_hline(yintercept = 0, color = "blue") +
@@
 
-```{r}
+```{r, eval = FALSE}
 hamby224_test_explain %>%
@@
   geom_bar() +
-  coord_flip()
+  coord_flip() + 
+  facet_grid(set ~ nbins)
 ```
 
-```{r}
+```{r, eval = FALSE}
 hamby224_test_explain %>%
-  filter(set == "Set 1") %>%
+  filter(set == "Set 1", nbins == "3") %>%
   mutate(rfscore = round(rfscore, 3)) %>%

### 2018-11-19 app/app.R

@@ -15,7 +15,7 @@ library(gridExtra)
 
 # Input data
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-hamby224_bins <- read.csv("../data/hamby_bins.csv")
+hamby224_bins <- readRDS("../data/hamby224_bins.rds")
 
 # Replace the periods with spaces in the feature names
 names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)

### 2018-11-19 code/helper_functions.R

@@ -6,17 +6,22 @@
 
 # Function for running the lime functions which runs the lime and explain 
 # objects in a list
-run_lime <- function(train, test, rfmodel, nbins, label, nfeatures){
+run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
+                     train, test, rfmodel, label, nfeatures){
   
   # Set a seed
   set.seed(84902)
   
   # Run the lime function
-  lime <- lime(x = train, model = rfmodel, n_bins = nbins)
+  lime <- lime(x = train, model = rfmodel, bin_continuous = bin_continuous, 
+               n_bins = nbins, quantile_bins = quantile_bins, use_density = use_density)
   
   # Run the explain function and add a variable for the number of bins
   explain <- explain(x = test, explainer = lime, labels = label, n_features = nfeatures) %>%
-    mutate(nbins = nbins)
+    mutate(bin_continuous = bin_continuous,
+           quantile_bins = quantile_bins,
+           nbins = nbins,
+           use_density = use_density)
   
   return(list(lime = lime, explain = explain))
   
@@ -92,7 +97,7 @@ create_bin_data <- function(lime_object){
 ## ---------------------------------------------------------------
 
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, nbins, bin_data){
+bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, case_info){
   
   if (is.na(feature)) {
     
@@ -101,22 +106,28 @@ bin_labeller <- function(feature, feature_value, nbins, bin_data){
     
   } else {
     
-    # Subset the bin cuts table to the selected feature
-    feature_bin_data <- bin_data %>%
-      filter(Feature == feature) %>%
-      select(-Feature, -Lower, -Upper)
+    # Determine which item in the list of bin divisions to grab 
+    # based on the case info
+    selected_list_item <- case_info %>%
+      filter(bin_continuous == b_c, 
+             quantile_bins == q_b,
+             nbins == n_b, 
+             is.na(use_density)) %>%
+      pull(case)
     
-    # Compute the number of bins based the input dataframe
-    nbins = length(bin_data) - 2
+    # Subset the bin cuts table to the selected feature
+    feature_bin_data <- bin_data[[selected_list_item]] %>%
+      filter(Feature == as.character(feature)) %>%
+      select(-Feature, -Lower, -Upper)
     
     # Determine which bin the case falls in
     if(feature_value <= feature_bin_data[1]){
[…]

### 2018-11-19 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
added lime options to paper and prepared code to run for a large set of lime options

@@
 \begin{quote}
-To do this, `lime` draws a sample from a Uniform(0,1) distribution and uses the bin information to compute a sample drawn from the feature distribution.
+To do this, `lime` has several options (mostly quoted from `lime` package for now):
+\begin{itemize}
+\item bin\_continuous = TRUE should continuous variables be binned?
+\item quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
+\item n\_bins = 4 number of bins if bin\_continuous is TRUE
+\item use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
+\end{itemize}
 \end{quote}
@@
   # Specify the options to use with lime 
-  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
-                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
-                                    nbins = rep(2:10, 2),
-                                    use_density = rep(NA, 18)) %>%
+  hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 18), rep(FALSE, 2)),
+                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9), rep(NA, 2)),
+                                    nbins = c(rep(2:10, 2), rep(NA, 2)),
+                                    use_density = c(rep(NA, 18), TRUE, FALSE)) %>%
   mutate(case = 1:length(nbins)) %>%
@@
   # Run the lime functions for the specified number of bins
-  hamby224_all_results <- pmap(.l = as.list(hamby224_lime_cases[1,-1]),
+  hamby224_all_results <- pmap(.l = as.list(hamby224_lime_cases[,-1]),
              .f = run_lime, # run_lime is one of my helper functions
@@
   # Name the items in the lime list
-  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_cases[1,])[1], function(case) 
+  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_cases)[1], function(case) 
       sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
@@
 ```{r}
+# Create the lime comparison data if the file does not already exist
+if(!file.exists("../data/hamby224_lime_comparisons.rds")) {
+
+  # Create a data frame with the interesting information relating to the differe
+  # evaluations of lime and compute the difference and mean between the rf and rr
+  # model predictions
   hamby224_lime_comparisons <- hamby224_test_explain %>%
@@
     ungroup() %>%
-  select(bin_continuous, quantile_bins, nbins, use_density, case, set, rf_features, rfscore, model_prediction, model_r2) %>%
+    select(bin_continuous, quantile_bins, nbins, use_density, 
+           set, case, rf_features, rfscore, model_prediction, model_r2) %>%
     mutate(diff = rfscore - model_prediction,
@@
 
+  # Save the lime comparison data frame
+  saveRDS(hamby224_lime_comparisons, "../data/hamby224_lime_comparisons.rds")
+
+} else {
+
+  # Load in the lime comparison data frame
+  hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+
+}
+```
+
+```{r}
 hamby224_lime_comparisons %>%
@@
   arrange(set)
+```
 
+```{r}
 hamby224_lime_comparisons %>%
@@
 
-```{r fig.width = 8, fig.height = 4, eval = FALSE}
+```{r fig.width = 8, fig.height = 4}
 ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = model_prediction)) + 
@@
 
-```{r fig.width = 8, fig.height = 4, eval = FALSE}
+```{r fig.width = 8, fig.height = 4}
 ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = abs(diff))) + 
@@
 
-```{r fig.width = 8, fig.height = 4, eval = FALSE}
+```{r fig.width = 8, fig.height = 4}
 ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = diff)) + 
@@
 
-```{r, eval = FALSE}
+```{r}
 hamby224_test_explain %>%
@@
 
-```{r, eval = FALSE}
+```{r}
 hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "3") %>%
+  filter(set == "Set 1", nbins == "2") %>%
   mutate(rfscore = round(rfscore, 3)) %>%

### 2018-11-19 app/app.R

@@ -14,8 +14,10 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds") %>%
+  filter(bin_continuous == TRUE, quantile_bins == TRUE, nbins == 2, is.na(use_density))
+  
+hamby224_bins <- readRDS("../data/hamby224_bins.rds")[[1]]
 
 # Replace the periods with spaces in the feature names
 names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)

### 2018-11-20 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
ran lime with grid of nbins and other input options and made visualizations with the output

@@
   # Specify the options to use with lime 
-  hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 18), rep(FALSE, 2)),
-                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9), rep(NA, 2)),
-                                    nbins = c(rep(2:10, 2), rep(NA, 2)),
-                                    use_density = c(rep(NA, 18), TRUE, FALSE)) %>%
+  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
+                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
+                                    nbins = rep(2:10, 2),
+                                    use_density = rep(NA, 18)) %>%
   mutate(case = 1:length(nbins)) %>%
@@
 ```{r}
-hamby224_lime_comparisons %>%
+hamby224_lime_mse <- hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore)) %>%
   group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
@@
 ```{r}
+hamby224_lime_mse %>%
+  group_by(set) %>%
+  arrange(mse) %>%
+  slice(1:2)
+```
+
+```{r}
+hamby224_lime_mse %>%
+  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
+  geom_point() + 
+  geom_line() + 
+  facet_grid( ~ set) + 
+  theme_bw()
+```
+
+```{r}
 hamby224_lime_comparisons %>%
-  filter(nbins == "2", set == "Set 1") %>%
+  filter(quantile_bins == TRUE, nbins == "8", set == "Set 1") %>%
   select(rf_features, diff, -case) %>%
@@
   geom_point() + 
-  facet_wrap( ~ feature, scales = "free") + 
+  facet_wrap(~ feature, scales = "free") + 
   geom_hline(yintercept = 0, color = "blue")
@@
 
-Below is are plots of the probability of a match computed from the "simple" (ridge regression) model in `lime` versus the probability of a match computed from the `rtrees` random forest model for both the Hamby224 Set 1 and Set 11 test cases.
-Linear regression lines have been fit through the points.
-Both plots show that there is a weak negative linear relationship between the two variables.
-This suggests that as the probability of a match increases in the random forest, the simple model is doing a worse job of computing a probability that agrees with the random forest model.
-However, the Hamby 224 test sets 1 and 11 do not have many observations with high random forest scores.
-Each test set should only have 18 matches.
-The trend may be different if there was more cases with high random forest scores.
-However, it appears that the cases that are a match have some of the lowest model_prediction scores overall.
-
-The points are also colored by the $R^2$ value from the simple model.
-This plot suggests that the simple models with a prediction close to 0.5 have a better fit, but the $R^2$ values are still low.
-I am not sure what to make of this.
-However, it does not appear that the $R^2$ is related to the probability from the random forest.
+```{r}
+hamby224_lime_comparisons %>%
+  filter(quantile_bins == TRUE, nbins == "3", set == "Set 11") %>%
+  select(rf_features, diff, -case) %>%
+  gather(key = feature, value = feature_value, rf_features) %>%
+  select(feature, feature_value, diff) %>%
+  ggplot(aes(x = feature_value, y = diff)) + 
+  geom_point() + 
+  facet_wrap(~ feature, scales = "free") + 
+  geom_hline(yintercept = 0, color = "blue")
+```
 
 ```{r fig.width = 8, fig.height = 4}
-ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = model_prediction)) + 
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 1") %>%
+  ggplot(aes(x = rfscore, y = model_prediction)) + 
   geom_point(aes(color = model_r2)) + 
-  facet_grid(nbins ~ set) + 
+  facet_wrap( ~ nbins) + 
   theme_bw() + 
@@
 
-The plots below show the absolute value of the difference between the random forest probability and the simple model probability versus the random forest probability.
-These plots show a clear v-shaped trend that suggests that the simple model is doing the best job of replicating the random forest probability around the random forest probability of 0.5.
-That is, the simple model seems to be doing a worse job of computing accurate predictions in the extremes of the random forest scores.
+```{r fig.width = 8, fig.height = 4}
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 11") %>%
+  ggplot(aes(x = rfscore, y = model_prediction)) + 
+  geom_point(aes(color = model_r2)) + 
+  facet_wrap( ~ nbins) + 
+  theme_bw() + 
+  stat_smooth(method = "lm")
+```
 
 ```{r fig.width = 8, fig.height = 4}
-ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = abs(diff))) + 
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 1") %>%
+  ggplot(aes(x = rfscore, y = abs(diff))) + 
   geom_point(aes(color = model_r2)) + 
@@
 
-The plot below shows the difference of the two model probabilities versus the random forest score.
-This shows that when the random forest score is low, the simple model is over estimating the probability, and when the random forest score is high, the simple model is underestimating the probability.
+```{r fig.width = 8, fig.height = 4}
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 11") %>%
+  ggplot(aes(x = rfscore, y = abs(diff))) + 
+  geom_point(aes(color = model_r2)) + 
+  facet_grid(nbins ~ set) +
+  theme_bw()
+```
 
 ```{r fig.width = 8, fig.height = 4}
-ggplot(hamby224_lime_comparisons, aes(x = rfscore, y = diff)) + 
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 1") %>%
+  ggplot(aes(x = rfscore, y = diff)) + 
+  geom_point(aes(color = model_r2)) + 
+  facet_grid(nbins ~ set) +
+  geom_hline(yintercept = 0, color = "blue") +
+  theme_bw()
+```
+
+```{r fig.width = 8, fig.height = 4}
+hamby224_lime_comparisons %>%
+  filter(!is.na(rfscore), set == "Set 11") %>%
+  ggplot(aes(x = rfscore, y = diff)) + 
   geom_point(aes(color = model_r2)) + 
@@
 hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "2") %>%
+  filter(set == "Set 1", nbins == "8") %>%
   mutate(rfscore = round(rfscore, 3)) %>%

### 2018-11-20 app/app.R
worked on updating app to look at the new explanations

@@ -14,23 +14,22 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds") %>%
-  filter(bin_continuous == TRUE, quantile_bins == TRUE, nbins == 2, is.na(use_density))
-  
-hamby224_bins <- readRDS("../data/hamby224_bins.rds")[[1]]
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 
 # Replace the periods with spaces in the feature names
-names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)
+#names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)
 
 ## ------------------------------------------------------------------------------------
 ## Functions
 ## ------------------------------------------------------------------------------------
 
 # Function for creating a table with the bin information relating to specified features
-bin_table <- function(features, bin_cuts = hamby224_bins){
+bin_table <- function(features, bin_cuts = hamby224_bins, case){
 
   # Subset the bin cuts table to the selected feature
-  selected_bin_cuts <- bin_cuts %>% 
+  selected_bin_cuts <- bin_cuts[[case]] %>% 
     filter(Feature %in% features) %>%
     mutate(Feature = factor(Feature, levels = features)) %>%
     arrange(Feature)
@@ -77,9 +76,12 @@ server <- function(input, output) {
     # Grab the number of the chosen set
     chosen_set <- paste("Set", unlist(strsplit(input$set, split = " "))[2])
     
+    # Specify nbins based on the chosen_set
+    bins = ifelse(chosen_set == "Set 1", 8, 3)
+    
     # Create a tile plot of the random forest predictions
     plot <- hamby224_test_explain %>%
-      filter(set == chosen_set) %>%
+      filter(set == chosen_set, quantile_bins == TRUE, nbins == bins) %>%
       mutate(rfscore = round(rfscore, 3)) %>%
       select(case, bullet1, bullet2, land1, land2, rfscore) %>%
       distinct() %>%
@@ -152,9 +154,14 @@ server <- function(input, output) {
         # Save the locations to use for the reactive mark on the tileplot
[…]

### 2018-11-20 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
created options in app to choose from the different LIME implementations and started working on handling the bin_continuous = FALSE case

@@
 ```{r}
+# Specify the options to use with lime 
+hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
+                                      quantile_bins = rep(TRUE, 2),
+                                      nbins = rep(4, 2),
+                                      use_density = c(TRUE, FALSE)) %>%
+  mutate(case = 1:length(nbins)) %>%
+  select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+# Run the lime functions for the specified number of bins
+hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
+           .f = run_lime, # run_lime is one of my helper functions
+           train = hamby173and252_train %>% select(rf_features),
+           test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+           rfmodel = as_classifier(rtrees),
+           label = "TRUE",
+           nfeatures = 3)
+
+# Separate the lime and explain function results
+hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
+hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
+```
+
+```{r}
 # Create a dataframe with the bins
@@
 ```{r}
-hamby224_lime_mse <- hamby224_lime_comparisons %>%
+hamby224_lime_results <- hamby224_lime_comparisons %>%
   filter(!is.na(rfscore)) %>%
   group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
-  summarise(mse = (sum(diff)^2) / length(diff)) %>%
+  summarise(mse = (sum(diff)^2) / length(diff),
+            ave_r2 = mean(model_r2)) %>%
   arrange(set)
@@
 ```{r}
-hamby224_lime_mse %>%
+hamby224_lime_results %>%
   group_by(set) %>%
@@
 ```{r}
-hamby224_lime_mse %>%
+hamby224_lime_results %>%
   ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
+  geom_point() + 
+  geom_line() + 
+  facet_grid( ~ set) + 
+  theme_bw()
+```
+
+```{r}
+hamby224_lime_results %>%
+  group_by(set) %>%
+  arrange(ave_r2) %>%
+  slice(1:2)
+```
+
+```{r}
+hamby224_lime_results %>%
+  ggplot(aes(x = nbins, y = ave_r2, color = quantile_bins, group = quantile_bins)) +
   geom_point() + 
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(nbins ~ set) +
+  facet_wrap( ~ nbins) +
   theme_bw()
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(nbins ~ set) +
+  facet_wrap( ~ nbins) +
   geom_hline(yintercept = 0, color = "blue") +
@@
   distinct() %>%
+  bind_rows(hamby224_test_explain %>%
+                  filter(is.na(rfscore), set == "Set 1") %>%
+                  select(case, bullet1, bullet2, land1, land2, rfscore)) %>%
   ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,

### 2018-11-20 app/app.R

@@ -18,9 +18,6 @@ hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 hamby224_bins <- readRDS("../data/hamby224_bins.rds")
 hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 
-# Replace the periods with spaces in the feature names
-#names(hamby224_bins) <- gsub(".", " ", names(hamby224_bins), fixed = TRUE)
-
 ## ------------------------------------------------------------------------------------
 ## Functions
 ## ------------------------------------------------------------------------------------
@@ -48,15 +45,25 @@ ui <- fluidPage(
    
    # Application title
    titlePanel("LIME Explanations for Bullet Matching"),
-   
-   # Set selector
-   column(6, selectInput("set", 
-                        label = "Select a Hamby 224 dataset", 
-                        choices = c("Set 1", "Set 11")),
+  
+   # Panel for selections and tileplot
+   column(width = 6,
+          fluidRow(column(width = 6,
+                          selectInput("set", 
+                                      label = "Select a Hamby 224 dataset", 
+                                      choices = c("Set 1", "Set 11")),
+                          selectInput("bintype", 
+                                      label = "Select the bin type for LIME", 
+                                      choices = c("Quantile Bins", "Equally Spaced Bins"))),
+                   column(width = 6,
+                          selectInput("nbins", 
+                                      label = "Select the number of bins to use for LIME", 
+                                      choices = c(2:10)))),
           plotlyOutput("tileplot")),
 
-   # Panel for plots
-   column(6, fluidRow(plotOutput("featureplot")))
+   # Panel for feature plot
+   column(width = 6, 
+          fluidRow(plotOutput("featureplot")))
    
 )
 
@@ -73,18 +80,20 @@ server <- function(input, output) {
   # Create the tile plot
   output$tileplot <- renderPlotly({
     
-    # Grab the number of the chosen set
+    # Grab the chosen input options
     chosen_set <- paste("Set", unlist(strsplit(input$set, split = " "))[2])
-    
-    # Specify nbins based on the chosen_set
-    bins = ifelse(chosen_set == "Set 1", 8, 3)
+    chosen_bintype <- ifelse(input$bintype == "Quantile Bins", TRUE, FALSE)
+    chosen_nbins <- input$nbins
     
     # Create a tile plot of the random forest predictions
[…]

### 2018-11-20 code/helper_functions.R

@@ -81,6 +81,8 @@ create_bin_data <- function(lime_object){
   # Assign appropriate names to the bin columns
   if (nbins == 2){
     names(bins) <- c("Feature", "Lower Bin", "Upper Bin")
+  } else if (nbins == 3) {
+    names(bins) <- c("Feature", "Lower Bin", "Middle Bin", "Upper Bin")
   } else {
     names(bins) <- c("Feature", 
                      "Lower Bin",
@@ -131,9 +133,15 @@ bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, c
                                                          FUN = function(number) {
                                                            feature_bin_data[number] < feature_value &
                                                              feature_value <= feature_bin_data[number + 1]}))
-      feature_bin <- sprintf("%s (middle bin %.0f)", 
-                             feature,
-                             middle_bin_checks %>% filter(contained == TRUE) %>% pull(middle_bin_number))
+      
+      if (n_b == 3){
+        feature_bin = sprintf("%s (middle bin)", feature)
+      } else {
+        feature_bin <- sprintf("%s (middle bin %.0f)", 
+                               feature,
+                               middle_bin_checks %>% filter(contained == TRUE) %>% pull(middle_bin_number))
+      }
+      
     }
     
   }

### 2018-11-27 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on adding bin_continuous = FALSE options to the app - still some problems to fix :(

@@
 
+Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
+Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+
 ```{r}
@@
   # Specify the options to use with lime 
-  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
-                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
-                                    nbins = rep(2:10, 2),
-                                    use_density = rep(NA, 18)) %>%
+  hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
+                                    quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)),
+                                    nbins = c(rep(2:6, 2), rep(4, 2)),
+                                    use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
   mutate(case = 1:length(nbins)) %>%
@@
 
+  # Specify the options to use with lime with no bins
+  # hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
+  #                                           quantile_bins = rep(TRUE, 2),
+  #                                           nbins = rep(4, 2),
+  #                                           use_density = c(TRUE, FALSE)) %>%
+  #   mutate(case = 1:length(nbins)) %>%
+  #   select(case, bin_continuous, nbins, quantile_bins, use_density)
+  # 
+  # # Run the lime functions for the specified number of bins
+  # hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
+  #          .f = run_lime, # run_lime is one of my helper functions
+  #          train = hamby173and252_train %>% select(rf_features),
+  #          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+  #          rfmodel = as_classifier(rtrees),
+  #          label = "TRUE",
+  #          nfeatures = 3)
+
+  # # Separate the lime and explain function results
+  # hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
+  # hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
+  # 
+  # # Bind the lime dataframes with bin_continuous TRUE and FALSE
+  # hamby224_lime <- c(hamby224_lime, hamby224_lime_no_bins)
+  # hamby224_explain <- bind_rows(hamby224_explain, hamby224_explain_no_bins)
+
   # Save the lime and explain results objects and the case info
@@
 }
-```
-
-```{r}
-# Specify the options to use with lime 
-hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
-                                      quantile_bins = rep(TRUE, 2),
-                                      nbins = rep(4, 2),
-                                      use_density = c(TRUE, FALSE)) %>%
-  mutate(case = 1:length(nbins)) %>%
-  select(case, bin_continuous, nbins, quantile_bins, use_density)
-
-# Run the lime functions for the specified number of bins
-hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
-           .f = run_lime, # run_lime is one of my helper functions
-           train = hamby173and252_train %>% select(rf_features),
-           test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-           rfmodel = as_classifier(rtrees),
-           label = "TRUE",
-           nfeatures = 3)
-
-# Separate the lime and explain function results
-hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
-hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
 ```
@@
   # Finish creating the strictly less than variable
-  hamby224_test_explain$strictly_less[grep("< ", 
-                                           hamby224_test_explain$feature_desc)] <- TRUE
+  hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
 
@@
 hamby224_lime_results %>%
-  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
+  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
+         nbins_update = factor(ifelse(bin_continuous == FALSE, "0", nbins))) %>%
+  ggplot(aes(x = nbins_update, y = mse, color = bc_qb)) +
   geom_point() + 
-  geom_line() + 
   facet_grid( ~ set) + 
@@
   - learn lambda in the ridge regression
+  - could add a penalty for the number of parameters in the model (or the number of bins)
+  - could start with a fine grid of bins and then go backwards and fit the models on this sampled data
+  - could try a type of ANOVA test if we can have nested models or if we can assume nesting
+  - could compute something like an R^2_adj
 

### 2018-11-27 app/app.R

@@ -15,6 +15,7 @@ library(gridExtra)
 
 # Input data
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_test_explain["use_density"][is.na(hamby224_test_explain[c("use_density")])] <- TRUE
 hamby224_bins <- readRDS("../data/hamby224_bins.rds")
 hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 
@@ -52,13 +53,12 @@ ui <- fluidPage(
                           selectInput("set", 
                                       label = "Select a Hamby 224 dataset", 
                                       choices = c("Set 1", "Set 11")),
-                          selectInput("bintype", 
-                                      label = "Select the bin type for LIME", 
-                                      choices = c("Quantile Bins", "Equally Spaced Bins"))),
+                         uiOutput('bintype')),
                    column(width = 6,
-                          selectInput("nbins", 
-                                      label = "Select the number of bins to use for LIME", 
-                                      choices = c(2:10)))),
+                          selectInput("density", 
+                                      label = "Select density estimation method for LIME", 
+                                      choices = c("Bins", "Kernel Density", "Normal Approximation")),
+                          uiOutput('nbins'))),
           plotlyOutput("tileplot")),
 
    # Panel for feature plot
@@ -74,6 +74,45 @@ ui <- fluidPage(
 # Create the plots to include in the app
 server <- function(input, output) {
   
+  # Specify bin type options based on density estimation type
+  output$bintype = renderUI({
+    
+    # Determine the specified density estimation method
+    type = input$density
+
+    # Specify the bin type options based on the density estimation
+    if (type == "Bins"){
+      options <- c("Quantile Bins", "Equally Spaced Bins")
+    } else {
+      options <- NA
+    }
+    
+    # Create the selection object
+    selectInput('bintype',
+                label = "Select the bin type for LIME", 
+                choices = options)
+  })
+  
+  # Specify options for number of bins based on density estimation type
+  output$nbins = renderUI({
+    
+    # Determine the specified density estimation method
+    type = input$density
+    
+    # Specify the options for number of bins
+    if (type == "Bins"){
+      options <- 2:6
[…]

### 2018-11-27 code/helper_functions.R

@@ -65,32 +65,43 @@ write_bins <- function(bin_data){
 
 create_bin_data <- function(lime_object){
   
-  # Determine the nubmer of bins
-  nbins <- length(lime_object$bin_cuts[[1]]) - 1
+  # If bin_continuous = TRUE, create a list with data frames on bin information
+  if (lime_object$bin_continuous == TRUE){
+    
+    # Determine the nubmer of bins
+    nbins <- length(lime_object$bin_cuts[[1]]) - 1
+    
+    # Create a dataframe of bin boundaries
+    bin_boundaries <- data.frame(Feature = rf_features,
+                                 Lower = c(0, -1, rep(0, 7)),
+                                 matrix(unlist(lime_object$bin_cuts), nrow = 9, 
+                                        byrow = TRUE)[,2:nbins],
+                                 Upper = c(1, 1, rep(NA, 7)))
+    
+    # Use my function "write_bins" to create a dataframe with the bins
+    bins <- data.frame(t(apply(bin_boundaries, 1, write_bins)))
+    
+    # Assign appropriate names to the bin columns
+    if (nbins == 2){
+      names(bins) <- c("Feature", "Lower Bin", "Upper Bin")
+    } else if (nbins == 3) {
+      names(bins) <- c("Feature", "Lower Bin", "Middle Bin", "Upper Bin")
+    } else {
+      names(bins) <- c("Feature", 
+                       "Lower Bin",
+                       sapply(1:(nbins - 2), function(bin) sprintf("Middle Bin %.0f", bin)),
+                       "Upper Bin")
+    }
+    
+    return(list(boundaries = bin_boundaries, bins = bins))
   
-  # Create a dataframe of bin boundaries
-  bin_boundaries <- data.frame(Feature = rf_features,
-                               Lower = c(0, -1, rep(0, 7)),
-                               matrix(unlist(lime_object$bin_cuts), nrow = 9, 
-                                      byrow = TRUE)[,2:nbins],
-                               Upper = c(1, 1, rep(NA, 7)))
-  
-  # Use my function "write_bins" to create a dataframe with the bins
-  bins <- data.frame(t(apply(bin_boundaries, 1, write_bins)))
-  
-  # Assign appropriate names to the bin columns
-  if (nbins == 2){
-    names(bins) <- c("Feature", "Lower Bin", "Upper Bin")
-  } else if (nbins == 3) {
-    names(bins) <- c("Feature", "Lower Bin", "Middle Bin", "Upper Bin")
[…]

### 2018-11-27 ok/app.R

@@ -1,0 +1,28 @@
+runApp(list(
+  ui = bootstrapPage(
+    selectInput("density", 
+                label = "Select density estimation method for LIME", 
+                choices = c("Bins", "Kernel Density", "Normal Approximation")),
+    uiOutput('bintype')
+  ),
+  server = function(input, output){
+    output$bintype = renderUI({
+      type = input$density
+      selectInput('bintype2', 'Columns', ifelse(type == "Bins", "hi", "bye"))
+    })
+  }
+))
+
+
+runApp(list(
+  ui = bootstrapPage(
+    selectInput('dataset', 'Choose Dataset', c('mtcars', 'iris')),
+    uiOutput('columns')
+  ),
+  server = function(input, output){
+    output$columns = renderUI({
+      mydata = get(input$dataset)
+      selectInput('columns2', 'Columns', names(mydata))
+    })
+  }
+))

### 2018-11-27 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on subsampling

--- 2018-11-20 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 ```{r}
+hamby173and252_train_sub <- hamby173and252_train %>%
+  filter(samesource == FALSE) %>%
+  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
+  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
+```
+
+```{r}
 # Obtain features used when fitting the rtrees random forest
@@
   theme(legend.position = "bottom")
+
+# Same plot but with the subsampled training data
+hamby173and252_train_sub %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 hamby173and252_train %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(position = "fill", bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+# Same plot but with the subsampled training data
+hamby173and252_train_sub %>% 
   select(rf_features, samesource) %>%
@@
 
+Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
+Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+
+```{r}
+# Specify the options to use with lime 
+hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
+                                    quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)),
+                                    nbins = c(rep(2:6, 2), rep(4, 2)),
+                                    use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
+  mutate(case = 1:length(nbins)) %>%
+  select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+# Save the cases
+saveRDS(hamby224_lime_cases, "../data/hamby224_lime_cases.rds")
+```
+
 ```{r}
@@
 if(!file.exists("../data/hamby224_lime.rds")) {
-
-  # Specify the options to use with lime 
-  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
-                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
-                                    nbins = rep(2:10, 2),
-                                    use_density = rep(NA, 18)) %>%
-  mutate(case = 1:length(nbins)) %>%
-  select(case, bin_continuous, nbins, quantile_bins, use_density)
 
@@
   saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
-  saveRDS(hamby224_lime_cases, "../data/hamby224_lime_cases.rds")
 
@@
   hamby224_explain <- readRDS("../data/hamby224_explain.rds")
-  hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
+
+}
+```
+
+```{r}
+# Apply the run_lime function if the lime results file does not already exist
+if(!file.exists("../data/hamby224_sub_lime.rds")) {
+
+  # Run the lime functions for the specified number of bins
+  hamby224_sub_all_results <- pmap(.l = as.list(hamby224_lime_cases[,-1]),
+             .f = run_lime, # run_lime is one of my helper functions
+             train = hamby173and252_train_sub %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3)
+
+  # Separate the lime and explain function results
+  hamby224_sub_lime <- map(hamby224_sub_all_results, function(list) list$lime)
+  hamby224_sub_explain <- map_df(hamby224_sub_all_results, function(list) list$explain)
+
+  # Name the items in the lime list
+  names(hamby224_sub_lime) <- map_chr(1:dim(hamby224_lime_cases)[1], function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
+              hamby224_lime_cases$bin_continuous[case],
+              hamby224_lime_cases$quantile_bins[case],
+              hamby224_lime_cases$nbins[case],
+              hamby224_lime_cases$use_density[case]))
+
+  # Save the lime and explain results objects and the case info
+  saveRDS(hamby224_sub_lime, "../data/hamby224_sub_lime.rds")
+  saveRDS(hamby224_sub_explain, "../data/hamby224_sub_explain.rds")
+
+} else {
+
+  # Load in the lime results object
+  hamby224_sub_lime <- readRDS("../data/hamby224_sub_lime.rds")
+  hamby224_sub_explain <- readRDS("../data/hamby224_sub_explain.rds")
 
@@
   hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+
+}
+```
+
+```{r}
+# Create a dataframe with the bins
+if (!file.exists("../data/hamby224_sub_bins.csv")) {
+
+  # Create a list a dataframes with the bin boundaries and bins 
+  # for the different evaluations of the lime functions
+  hamby224_sub_bin_list <- map(hamby224_sub_lime, create_bin_data)
+
+  # Save the bin boundaries and the bins as separate dataframes
+  hamby224_sub_bin_boundaries <- map(hamby224_sub_bin_list, function(m) m$boundaries)
+  hamby224_sub_bins <- map(hamby224_sub_bin_list, function(m) m$bins)
+
+  # Save the bin boundaries and bins
+  saveRDS(hamby224_sub_bin_boundaries, "../data/hamby224_sub_bin_boundaries.rds")
+  saveRDS(hamby224_sub_bins, "../data/hamby224_sub_bins.rds")
+
+} else {
+
+  # Load in the bin boundaries and bins
+  hamby224_sub_bin_boundaries <- readRDS("../data/hamby224_sub_bin_boundaries.rds")
+  hamby224_sub_bins <- readRDS("../data/hamby224_sub_bins.rds")
 
@@
   hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+
+}
+```
+
+```{r}
+# Create the test_explain combined data if the file does not already exist
+if(!file.exists("../data/hamby224_sub_test_explain.rds")) {
+
+  # Join the data and the explanations and edit and add additional variables
+  # Create the feature bin labels using my function "bin_labeller"
+  hamby224_sub_test_explain <- hamby224_test %>%
+    mutate(case = as.character(case)) %>%
+    full_join(hamby224_sub_explain, by = "case") %>%
+    mutate(case = factor(case),
+           feature_desc = factor(feature_desc),
+           feature_bin = pmap_chr(list(feature = feature, 
+                                 feature_value = feature_value,
+                                 b_c = bin_continuous,
+                                 q_b = quantile_bins,
+                                 n_b = nbins,
+                                 u_d = use_density),
+                            .f = bin_labeller, # bin_labeller is one of my helper functions
+                            bin_data = hamby224_sub_bin_boundaries,
+                            case_info = hamby224_lime_cases)) %>%
+    mutate(feature = factor(feature),
+           nbins = factor(nbins),
+           feature_number = readr::parse_number(feature_desc),
+           strictly_less = FALSE) %>%
+    arrange(nbins)
+
+  # Finish creating the strictly less than variable
+  hamby224_sub_test_explain$strictly_less[grep("< ", hamby224_sub_test_explain$feature_desc)] <- TRUE
+
+  # Reorder the variables of feature_desc and feature_bin for plotting purposes
+  hamby224_sub_test_explain <- hamby224_sub_test_explain %>%
+    mutate(feature_desc = reorder(feature_desc, strictly_less),
+           feature_desc = reorder(feature_desc, feature_number),
+           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
+    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
+           data, prediction)
+
+  # Save the combined test and explain data
+  saveRDS(hamby224_sub_test_explain, "../data/hamby224_sub_test_explain.rds")
+
+} else {
+
+  # Load in the data
+  hamby224_sub_test_explain <- readRDS("../data/hamby224_sub_test_explain.rds")
 
@@
 ```{r}
-hamby224_lime_mse <- hamby224_lime_comparisons %>%
+# Create the lime comparison data if the file does not already exist
+if(!file.exists("../data/hamby224_sub_lime_comparisons.rds")) {
+
+  # Create a data frame with the interesting information relating to the differe
+  # evaluations of lime and compute the difference and mean between the rf and rr
+  # model predictions
+  hamby224_sub_lime_comparisons <- hamby224_sub_test_explain %>%
+    select(-data, -prediction) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
+    slice(1) %>%
+    ungroup() %>%
+    select(bin_continuous, quantile_bins, nbins, use_density, 
+           set, case, rf_features, rfscore, model_prediction, model_r2) %>%
+    mutate(diff = rfscore - model_prediction,
+           mean = (rfscore + model_prediction) / 2)
+
+  # Save the lime comparison data frame
+  saveRDS(hamby224_sub_lime_comparisons, "../data/hamby224_sub_lime_comparisons.rds")
+
+} else {
+
+  # Load in the lime comparison data frame
+  hamby224_sub_lime_comparisons <- readRDS("../data/hamby224_sub_lime_comparisons.rds")
+
+}
+```
+
+```{r}
+hamby224_lime_results <- hamby224_lime_comparisons %>%
   filter(!is.na(rfscore)) %>%
   group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
-  summarise(mse = (sum(diff)^2) / length(diff)) %>%
+  summarise(mse = (sum(diff)^2) / length(diff),
+            ave_r2 = mean(model_r2)) %>%
+  arrange(set)
+
+hamby224_sub_lime_results <- hamby224_sub_lime_comparisons %>%
+  filter(!is.na(rfscore)) %>%
+  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
+  summarise(mse = (sum(diff)^2) / length(diff),
+            ave_r2 = mean(model_r2)) %>%
   arrange(set)
@@
 ```{r}
-hamby224_lime_mse %>%
+hamby224_lime_results %>%
+  group_by(set) %>%
+  arrange(mse) %>%
+  slice(1:2)
+
+hamby224_sub_lime_results %>%
   group_by(set) %>%
@@
 ```{r}
-hamby224_lime_mse %>%
-  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
+hamby224_lime_results %>%
+  ungroup() %>%
+  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
+         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
+  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
+  geom_point() + 
+  geom_line() + 
+  facet_grid( ~ set) + 
+  theme_bw()
+
+hamby224_sub_lime_results %>%
+  ungroup() %>%
+  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
+         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
+  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
   geom_point() + 
@@
 ```{r}
+hamby224_lime_results %>%
+  group_by(set) %>%
+  arrange(desc(ave_r2)) %>%
+  slice(1:2)
+
+hamby224_sub_lime_results %>%
+  group_by(set) %>%
+  arrange(desc(ave_r2)) %>%
+  slice(1:2)
+```
+
+```{r}
+hamby224_lime_results %>%
+  ungroup() %>%
+  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
+         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
+  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
+  geom_point() + 
+  geom_line() + 
+  facet_grid( ~ set) + 
+  theme_bw()
+
+hamby224_sub_lime_results %>%
+  ungroup() %>%
+  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
+         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
+  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
+  geom_point() + 
+  geom_line() + 
+  facet_grid( ~ set) + 
+  theme_bw()
+```
+
+```{r eval = FALSE}
 hamby224_lime_comparisons %>%
@@
   geom_hline(yintercept = 0, color = "blue")
-```
 
-```{r}
 hamby224_lime_comparisons %>%
@@
   geom_hline(yintercept = 0, color = "blue")
-```
 
-```{r fig.width = 8, fig.height = 4}
 hamby224_lime_comparisons %>%
@@
   stat_smooth(method = "lm")
-```
 
-```{r fig.width = 8, fig.height = 4}
 hamby224_lime_comparisons %>%
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(nbins ~ set) +
+  facet_wrap( ~ nbins) +
   theme_bw()
-```
 
-```{r fig.width = 8, fig.height = 4}
 hamby224_lime_comparisons %>%
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(nbins ~ set) +
+  facet_wrap( ~ nbins) +
   geom_hline(yintercept = 0, color = "blue") +
   theme_bw()
-```
 
-```{r fig.width = 8, fig.height = 4}
 hamby224_lime_comparisons %>%
@@
 hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "8") %>%
+  filter(set == "Set 1", nbins == "2") %>%
   mutate(rfscore = round(rfscore, 3)) %>%
@@
   scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank()) +
   labs(x = "", y = "", fill = "RF Score")

### 2018-11-27 app/app.R

@@ -14,9 +14,10 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-hamby224_test_explain["use_density"][is.na(hamby224_test_explain[c("use_density")])] <- TRUE
-hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+hamby224_full_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_sub_test_explain <- readRDS("../data/hamby224_sub_test_explain.rds")
+hamby224_full_bins <- readRDS("../data/hamby224_bins.rds")
+hamby224_sub_bins <- readRDS("../data/hamby224_sub_bins.rds")
 hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 
 ## ------------------------------------------------------------------------------------
@@ -24,7 +25,7 @@ hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
 ## ------------------------------------------------------------------------------------
 
 # Function for creating a table with the bin information relating to specified features
-bin_table <- function(features, bin_cuts = hamby224_bins, case){
+bin_table <- function(features, case, bin_cuts){
 
   # Subset the bin cuts table to the selected feature
   selected_bin_cuts <- bin_cuts[[case]] %>% 
@@ -53,12 +54,15 @@ ui <- fluidPage(
                           selectInput("set", 
                                       label = "Select a Hamby 224 dataset", 
                                       choices = c("Set 1", "Set 11")),
-                         uiOutput('bintype')),
-                   column(width = 6,
                           selectInput("density", 
                                       label = "Select density estimation method for LIME", 
                                       choices = c("Bins", "Kernel Density", "Normal Approximation")),
-                          uiOutput('nbins'))),
+                          uiOutput('nbins')),
+                   column(width = 6,
+                          selectInput("data",
+                                      label = "Select version of training data",
+                                      choices = c("Full", "Subsampled")),
+                          uiOutput('bintype'))),
           plotlyOutput("tileplot")),
 
    # Panel for feature plot
@@ -108,7 +112,7 @@ server <- function(input, output) {
     
     # Create the selection object
     selectInput("nbins", 
-                label = "Select the number of bins to use for LIME", 
[…]

### 2018-11-27 code/helper_functions.R

@@ -125,7 +125,7 @@ bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, c
       filter(bin_continuous == b_c, 
              quantile_bins == q_b,
              nbins == n_b, 
-             is.na(use_density)) %>%
+             use_density == u_d) %>%
       pull(case)
     
     # Subset the bin cuts table to the selected feature

### 2018-11-28 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked more on subsampling

@@
 ```{r}
+# Create a subsampled version of the training data
+if (!file.exists("../data/hamby173and252_train_sub.csv")) {
+
+  # Create the data (with a set seed)
+  set.seed(1837592)
   hamby173and252_train_sub <- hamby173and252_train %>%
@@
     bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
+
+  # Save the subsampled data
+  write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
+
+} else {
+
+  # Load in the subsampled training data
+  hamby173and252_train_sub <- read.csv("../data/hamby173and252_train_sub.csv")
+
+}
 ```
@@
 ```{r}
+# Apply the run_lime function if the lime results file does not already exist
+if(!file.exists("../data/hamby224_lime_inputs.rds")) {
+
   # Specify the options to use with lime
-hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
-                                    quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)),
-                                    nbins = c(rep(2:6, 2), rep(4, 2)),
-                                    use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
-  mutate(case = 1:length(nbins)) %>%
-  select(case, bin_continuous, nbins, quantile_bins, use_density)
+  hamby224_lime_inputs <- data.frame(data_name = c(rep("Full", 12), rep("Subsampled", 12)),
+                                     bin_continuous = rep(c(rep(TRUE, 10), rep(FALSE, 2)), 2),
+                                     quantile_bins = rep(c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)), 2),
+                                     nbins = rep(c(rep(2:6, 2), rep(4, 2)), 2),
+                                     use_density = rep(c(rep(TRUE, 10), TRUE, FALSE)), 2) %>%
+    mutate(case = 1:length(data_name)) %>%
+    select(case, data_name, bin_continuous, nbins, quantile_bins, use_density)
 
-# Save the cases
-saveRDS(hamby224_lime_cases, "../data/hamby224_lime_cases.rds")
-```
-
-```{r}
-# Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("../data/hamby224_lime.rds")) {
-
-  # Run the lime functions for the specified number of bins
-  hamby224_all_results <- pmap(.l = as.list(hamby224_lime_cases[,-1]),
+  # Apply lime to the full training data with the specified input options
+  hamby224_lime_explain_full <- pmap(.l = as.list(hamby224_lime_inputs %>% 
+                                                    filter(data_name == "Full") %>%
+                                                    select(-case, -data_name)),
              .f = run_lime, # run_lime is one of my helper functions
+             data_name = "Full",
              train = hamby173and252_train %>% select(rf_features),
@@
              label = "TRUE",
-             nfeatures = 3)
+             nfeatures = 3,
+             seed = TRUE)
 
-  # Separate the lime and explain function results
-  hamby224_lime <- map(hamby224_all_results, function(list) list$lime)
-  hamby224_explain <- map_df(hamby224_all_results, function(list) list$explain)
+  # Separate the lime and explain function results from the full data
+  hamby224_lime_full <- map(hamby224_lime_explain_full, function(list) list$lime)
+  hamby224_explain_full <- map_df(hamby224_lime_explain_full, function(list) list$explain)
+
+  # Apply lime to the subsampled training data with the specified input options
+  hamby224_lime_explain_sub <- pmap(.l = as.list(hamby224_lime_inputs %>% 
+                                               filter(data_name == "Subsampled") %>%
+                                               select(-case, -data_name)),
+             .f = run_lime, # run_lime is one of my helper functions
+             data_name = "Subsampled",
+             train = hamby173and252_train_sub %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3,
+             seed = TRUE)
+
+  # Separate the lime and explain function results from the subsampled data
+  hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
+  hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
+
+  # Join the lime results from the full and subsampled training data
+  hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
+  hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
 
   # Name the items in the lime list
-  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_cases)[1], function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
-              hamby224_lime_cases$bin_continuous[case],
-              hamby224_lime_cases$quantile_bins[case],
-              hamby224_lime_cases$nbins[case],
-              hamby224_lime_cases$use_density[case]))
+  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_inputs)[1], function(case) 
+      sprintf("case: data = %s, bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
+              hamby224_lime_inputs$data_name[case],
+              hamby224_lime_inputs$bin_continuous[case],
+              hamby224_lime_inputs$quantile_bins[case],
+              hamby224_lime_inputs$nbins[case],
+              hamby224_lime_inputs$use_density[case]))
 
-  # Save the lime and explain results objects and the case info
+  # Save the lime objects
+  saveRDS(hamby224_lime_inputs, "../data/hamby224_lime_inputs.rds")
   saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
@@
 
-  # Load in the lime results object
+  # Load in the lime objects
+  hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
   hamby224_lime <- readRDS("../data/hamby224_lime.rds")
   hamby224_explain <- readRDS("../data/hamby224_explain.rds")
-
-}
-```
-
-```{r}
-# Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("../data/hamby224_sub_lime.rds")) {
-
-  # Run the lime functions for the specified number of bins
-  hamby224_sub_all_results <- pmap(.l = as.list(hamby224_lime_cases[,-1]),
-             .f = run_lime, # run_lime is one of my helper functions
-             train = hamby173and252_train_sub %>% select(rf_features),
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3)
-
-  # Separate the lime and explain function results
-  hamby224_sub_lime <- map(hamby224_sub_all_results, function(list) list$lime)
-  hamby224_sub_explain <- map_df(hamby224_sub_all_results, function(list) list$explain)
-
-  # Name the items in the lime list
-  names(hamby224_sub_lime) <- map_chr(1:dim(hamby224_lime_cases)[1], function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
-              hamby224_lime_cases$bin_continuous[case],
-              hamby224_lime_cases$quantile_bins[case],
-              hamby224_lime_cases$nbins[case],
-              hamby224_lime_cases$use_density[case]))
-
-  # Save the lime and explain results objects and the case info
-  saveRDS(hamby224_sub_lime, "../data/hamby224_sub_lime.rds")
-  saveRDS(hamby224_sub_explain, "../data/hamby224_sub_explain.rds")
-
-} else {
-
-  # Load in the lime results object
-  hamby224_sub_lime <- readRDS("../data/hamby224_sub_lime.rds")
-  hamby224_sub_explain <- readRDS("../data/hamby224_sub_explain.rds")
 
@@
 ```{r}
-# Create a dataframe with the bins
-if (!file.exists("../data/hamby224_sub_bins.csv")) {
-
-  # Create a list a dataframes with the bin boundaries and bins 
-  # for the different evaluations of the lime functions
-  hamby224_sub_bin_list <- map(hamby224_sub_lime, create_bin_data)
-
-  # Save the bin boundaries and the bins as separate dataframes
-  hamby224_sub_bin_boundaries <- map(hamby224_sub_bin_list, function(m) m$boundaries)
-  hamby224_sub_bins <- map(hamby224_sub_bin_list, function(m) m$bins)
-
-  # Save the bin boundaries and bins
-  saveRDS(hamby224_sub_bin_boundaries, "../data/hamby224_sub_bin_boundaries.rds")
-  saveRDS(hamby224_sub_bins, "../data/hamby224_sub_bins.rds")
-
-} else {
-
-  # Load in the bin boundaries and bins
-  hamby224_sub_bin_boundaries <- readRDS("../data/hamby224_sub_bin_boundaries.rds")
-  hamby224_sub_bins <- readRDS("../data/hamby224_sub_bins.rds")
-
-}
-```
-
-```{r}
 # Create the test_explain combined data if the file does not already exist
@@
                                   feature_value = feature_value,
+                                  d_n = training_data, 
                                   b_c = bin_continuous,
@@
                             bin_data = hamby224_bin_boundaries,
-                            case_info = hamby224_lime_cases)) %>%
+                            case_info = hamby224_lime_inputs)) %>%
     mutate(feature = factor(feature),
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
+    select(training_data:use_density, case:feature_desc, feature_bin:strictly_less, 
            data, prediction)
@@
 ```{r}
-# Create the test_explain combined data if the file does not already exist
-if(!file.exists("../data/hamby224_sub_test_explain.rds")) {
-
-  # Join the data and the explanations and edit and add additional variables
-  # Create the feature bin labels using my function "bin_labeller"
-  hamby224_sub_test_explain <- hamby224_test %>%
-    mutate(case = as.character(case)) %>%
-    full_join(hamby224_sub_explain, by = "case") %>%
-    mutate(case = factor(case),
-           feature_desc = factor(feature_desc),
-           feature_bin = pmap_chr(list(feature = feature, 
-                                 feature_value = feature_value,
-                                 b_c = bin_continuous,
-                                 q_b = quantile_bins,
-                                 n_b = nbins,
-                                 u_d = use_density),
-                            .f = bin_labeller, # bin_labeller is one of my helper functions
-                            bin_data = hamby224_sub_bin_boundaries,
-                            case_info = hamby224_lime_cases)) %>%
-    mutate(feature = factor(feature),
-           nbins = factor(nbins),
-           feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE) %>%
-    arrange(nbins)
-
-  # Finish creating the strictly less than variable
-  hamby224_sub_test_explain$strictly_less[grep("< ", hamby224_sub_test_explain$feature_desc)] <- TRUE
-
-  # Reorder the variables of feature_desc and feature_bin for plotting purposes
-  hamby224_sub_test_explain <- hamby224_sub_test_explain %>%
-    mutate(feature_desc = reorder(feature_desc, strictly_less),
-           feature_desc = reorder(feature_desc, feature_number),
-           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
-           data, prediction)
-
-  # Save the combined test and explain data
-  saveRDS(hamby224_sub_test_explain, "../data/hamby224_sub_test_explain.rds")
-
-} else {
-
-  # Load in the data
-  hamby224_sub_test_explain <- readRDS("../data/hamby224_sub_test_explain.rds")
-
-}
-```
-
-```{r}
 # Create the lime comparison data if the file does not already exist
@@
     select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
+    group_by(training_data, case, bin_continuous, quantile_bins, nbins, use_density) %>%
     slice(1) %>%
     ungroup() %>%
-    select(bin_continuous, quantile_bins, nbins, use_density, 
+    select(training_data, bin_continuous, quantile_bins, nbins, use_density, 
            set, case, rf_features, rfscore, model_prediction, model_r2) %>%
@@
 ```{r}
-# Create the lime comparison data if the file does not already exist
-if(!file.exists("../data/hamby224_sub_lime_comparisons.rds")) {
-
-  # Create a data frame with the interesting information relating to the differe
-  # evaluations of lime and compute the difference and mean between the rf and rr
-  # model predictions
-  hamby224_sub_lime_comparisons <- hamby224_sub_test_explain %>%
-    select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
-    slice(1) %>%
-    ungroup() %>%
-    select(bin_continuous, quantile_bins, nbins, use_density, 
-           set, case, rf_features, rfscore, model_prediction, model_r2) %>%
-    mutate(diff = rfscore - model_prediction,
-           mean = (rfscore + model_prediction) / 2)
-
-  # Save the lime comparison data frame
-  saveRDS(hamby224_sub_lime_comparisons, "../data/hamby224_sub_lime_comparisons.rds")
-
-} else {
-
-  # Load in the lime comparison data frame
-  hamby224_sub_lime_comparisons <- readRDS("../data/hamby224_sub_lime_comparisons.rds")
-
-}
-```
-
-```{r}
 hamby224_lime_results <- hamby224_lime_comparisons %>%
   filter(!is.na(rfscore)) %>%
-  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
+  group_by(training_data, bin_continuous, quantile_bins, nbins, use_density, set) %>%
   summarise(mse = (sum(diff)^2) / length(diff),
             ave_r2 = mean(model_r2)) %>%
-  arrange(set)
-
-hamby224_sub_lime_results <- hamby224_sub_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
-  summarise(mse = (sum(diff)^2) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set)
+  arrange(training_data, set)
 ```
@@
 hamby224_lime_results %>%
-  group_by(set) %>%
-  arrange(mse) %>%
-  slice(1:2)
-
-hamby224_sub_lime_results %>%
-  group_by(set) %>%
+  group_by(training_data, set) %>%
   arrange(mse) %>%
@@
   geom_line() + 
-  facet_grid( ~ set) + 
-  theme_bw()
-
-hamby224_sub_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
-  geom_point() + 
-  geom_line() + 
-  facet_grid( ~ set) + 
+  facet_grid(training_data ~ set) + 
   theme_bw()
@@
 hamby224_lime_results %>%
-  group_by(set) %>%
-  arrange(desc(ave_r2)) %>%
-  slice(1:2)
-
-hamby224_sub_lime_results %>%
-  group_by(set) %>%
+  group_by(training_data, set) %>%
   arrange(desc(ave_r2)) %>%
@@
   geom_line() + 
-  facet_grid( ~ set) + 
-  theme_bw()
-
-hamby224_sub_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
-  geom_point() + 
-  geom_line() + 
-  facet_grid( ~ set) + 
+  facet_grid(training_data ~ set) + 
   theme_bw()
@@
 hamby224_test_explain %>%
+  filter(training_data == "Full", set == "Set 1", nbins == "2") %>%
   ggplot(aes(x = feature_desc)) + 
@@
   coord_flip() + 
-  facet_grid(set ~ nbins)
+  facet_grid(set ~ .)
 ```
@@
 hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "2") %>%
+  filter(training_data == "Full", set == "Set 1", nbins == "2") %>%
   mutate(rfscore = round(rfscore, 3)) %>%

### 2018-11-28 app/app.R

@@ -14,11 +14,10 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_full_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-hamby224_sub_test_explain <- readRDS("../data/hamby224_sub_test_explain.rds")
-hamby224_full_bins <- readRDS("../data/hamby224_bins.rds")
-hamby224_sub_bins <- readRDS("../data/hamby224_sub_bins.rds")
-hamby224_lime_cases <- readRDS("../data/hamby224_lime_cases.rds")
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
 
 ## ------------------------------------------------------------------------------------
 ## Functions
@@ -48,26 +47,33 @@ ui <- fluidPage(
    # Application title
    titlePanel("LIME Explanations for Bullet Matching"),
   
-   # Panel for selections and tileplot
-   column(width = 6,
-          fluidRow(column(width = 6,
-                          selectInput("set", 
-                                      label = "Select a Hamby 224 dataset", 
-                                      choices = c("Set 1", "Set 11")),
-                          selectInput("density", 
-                                      label = "Select density estimation method for LIME", 
-                                      choices = c("Bins", "Kernel Density", "Normal Approximation")),
-                          uiOutput('nbins')),
-                   column(width = 6,
-                          selectInput("data",
-                                      label = "Select version of training data",
-                                      choices = c("Full", "Subsampled")),
-                          uiOutput('bintype'))),
-          plotlyOutput("tileplot")),
-
-   # Panel for feature plot
-   column(width = 6, 
-          fluidRow(plotOutput("featureplot")))
+   # Row for input options
+   fluidRow(title = "LIME Input Options",
+            column(width = 3,
+                   selectInput("set", 
+                               label = "Select a Hamby 224 dataset", 
+                               choices = c("Set 1", "Set 11"))),
+            column(width = 3, 
+                   selectInput("data",
[…]

### 2018-11-28 code/helper_functions.R

@@ -7,10 +7,11 @@
 # Function for running the lime functions which runs the lime and explain 
 # objects in a list
 run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
-                     train, test, rfmodel, label, nfeatures){
+                     data_name, train, test, rfmodel, label, nfeatures, 
+                     seed = TRUE){
   
-  # Set a seed
-  set.seed(84902)
+  # Set a seed if requested
+  if (seed == TRUE) set.seed(84902)
   
   # Run the lime function
   lime <- lime(x = train, model = rfmodel, bin_continuous = bin_continuous, 
@@ -18,7 +19,8 @@ run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
   
   # Run the explain function and add a variable for the number of bins
   explain <- explain(x = test, explainer = lime, labels = label, n_features = nfeatures) %>%
-    mutate(bin_continuous = bin_continuous,
+    mutate(training_data = data_name,
+           bin_continuous = bin_continuous,
            quantile_bins = quantile_bins,
            nbins = nbins,
            use_density = use_density)
@@ -110,7 +112,7 @@ create_bin_data <- function(lime_object){
 ## ---------------------------------------------------------------
 
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, case_info){
+bin_labeller <- function(feature, feature_value, d_n, b_c, q_b, n_b, u_d, bin_data, case_info){
   
   if (is.na(feature) | b_c == FALSE) {
     
@@ -122,7 +124,8 @@ bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, c
     # Determine which item in the list of bin divisions to grab 
     # based on the case info
     selected_list_item <- case_info %>%
-      filter(bin_continuous == b_c, 
+      filter(data_name == d_n,
+             bin_continuous == b_c, 
              quantile_bins == q_b,
              nbins == n_b, 
              use_density == u_d) %>%

### 2018-11-28 ok/app.R

@@ -1,28 +1,0 @@
-runApp(list(
-  ui = bootstrapPage(
-    selectInput("density", 
-                label = "Select density estimation method for LIME", 
-                choices = c("Bins", "Kernel Density", "Normal Approximation")),
-    uiOutput('bintype')
-  ),
-  server = function(input, output){
-    output$bintype = renderUI({
-      type = input$density
-      selectInput('bintype2', 'Columns', ifelse(type == "Bins", "hi", "bye"))
-    })
-  }
-))
-
-
-runApp(list(
-  ui = bootstrapPage(
-    selectInput('dataset', 'Choose Dataset', c('mtcars', 'iris')),
-    uiOutput('columns')
-  ),
-  server = function(input, output){
-    output$columns = renderUI({
-      mydata = get(input$dataset)
-      selectInput('columns2', 'Columns', names(mydata))
-    })
-  }
-))

### 2018-11-28 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
updated seeds

@@
   # Create the data (with a set seed)
-  set.seed(1837592)
+  set.seed(20181128)
   hamby173and252_train_sub <- hamby173and252_train %>%

### 2018-11-28 code/helper_functions.R

@@ -11,7 +11,7 @@ run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
                      seed = TRUE){
   
   # Set a seed if requested
-  if (seed == TRUE) set.seed(84902)
+  if (seed == TRUE) set.seed(20181128)
   
   # Run the lime function
   lime <- lime(x = train, model = rfmodel, bin_continuous = bin_continuous, 

### 2018-12-04 paper/Interpreting_Random_Forest_Predictions_for_Firearm_Identification_Using_LIME.Rmd
a bunch of work from the last week that I forgot to commit - removed subsampling and reran code - cleaned up app code and improved app - started work on assessing variability

--- 2018-11-28 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 library(purrr)
+library(future)
+library(furrr)
 
@@
 ```{r}
-# Create a subsampled version of the training data
-if (!file.exists("../data/hamby173and252_train_sub.csv")) {
-
-  # Create the data (with a set seed)
-  set.seed(1837592)
-  hamby173and252_train_sub <- hamby173and252_train %>%
-    filter(samesource == FALSE) %>%
-    slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-    bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-  # Save the subsampled data
-  write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-} else {
-
-  # Load in the subsampled training data
-  hamby173and252_train_sub <- read.csv("../data/hamby173and252_train_sub.csv")
-
-}
-```
-
-```{r}
 # Obtain features used when fitting the rtrees random forest
@@
   theme(legend.position = "bottom")
-
-# Same plot but with the subsampled training data
-hamby173and252_train_sub %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?") +
-  theme_bw() +
-  theme(legend.position = "bottom")
 ```
@@
 hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-
-# Same plot but with the subsampled training data
-hamby173and252_train_sub %>% 
   select(rf_features, samesource) %>%
@@
   # Specify the options to use with lime
-  hamby224_lime_inputs <- data.frame(data_name = c(rep("Full", 12), rep("Subsampled", 12)),
-                                     bin_continuous = rep(c(rep(TRUE, 10), rep(FALSE, 2)), 2),
-                                     quantile_bins = rep(c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)), 2),
-                                     nbins = rep(c(rep(2:6, 2), rep(4, 2)), 2),
-                                     use_density = rep(c(rep(TRUE, 10), TRUE, FALSE)), 2) %>%
-    mutate(case = 1:length(data_name)) %>%
-    select(case, data_name, bin_continuous, nbins, quantile_bins, use_density)
+  hamby224_lime_inputs <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
+                                     quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), 
+                                                       rep(TRUE, 2)),
+                                     nbins = c(rep(2:6, 2), rep(4, 2)),
+                                     use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
+    mutate(case = 1:length(bin_continuous)) %>%
+    select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
 
   # Apply lime to the full training data with the specified input options
-  hamby224_lime_explain_full <- pmap(.l = as.list(hamby224_lime_inputs %>% 
-                                                    filter(data_name == "Full") %>%
-                                                    select(-case, -data_name)),
+  hamby224_lime_explain <- future_pmap(.l = as.list(hamby224_lime_inputs %>% 
+                                                    select(-case)),
              .f = run_lime, # run_lime is one of my helper functions
-             data_name = "Full",
              train = hamby173and252_train %>% select(rf_features),
@@
   # Separate the lime and explain function results from the full data
-  hamby224_lime_full <- map(hamby224_lime_explain_full, function(list) list$lime)
-  hamby224_explain_full <- map_df(hamby224_lime_explain_full, function(list) list$explain)
-
-  # Apply lime to the subsampled training data with the specified input options
-  hamby224_lime_explain_sub <- pmap(.l = as.list(hamby224_lime_inputs %>% 
-                                               filter(data_name == "Subsampled") %>%
-                                               select(-case, -data_name)),
-             .f = run_lime, # run_lime is one of my helper functions
-             data_name = "Subsampled",
-             train = hamby173and252_train_sub %>% select(rf_features),
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = TRUE)
-
-  # Separate the lime and explain function results from the subsampled data
-  hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-  hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-  # Join the lime results from the full and subsampled training data
-  hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-  hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
+  hamby224_lime <- map(hamby224_lime_explain, function(list) list$lime)
+  hamby224_explain <- map_df(hamby224_lime_explain, function(list) list$explain)
 
@@
   names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_inputs)[1], function(case) 
-      sprintf("case: data = %s, bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
-              hamby224_lime_inputs$data_name[case],
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
               hamby224_lime_inputs$bin_continuous[case],
@@
                                   feature_value = feature_value,
-                                  d_n = training_data, 
                                   b_c = bin_continuous,
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(training_data:use_density, case:feature_desc, feature_bin:strictly_less, 
+    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
            data, prediction)
@@
     select(-data, -prediction) %>%
-    group_by(training_data, case, bin_continuous, quantile_bins, nbins, use_density) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
     slice(1) %>%
     ungroup() %>%
-    select(training_data, bin_continuous, quantile_bins, nbins, use_density, 
+    select(bin_continuous, quantile_bins, nbins, use_density, 
            set, case, rf_features, rfscore, model_prediction, model_r2) %>%
@@
   filter(!is.na(rfscore)) %>%
-  group_by(training_data, bin_continuous, quantile_bins, nbins, use_density, set) %>%
+  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
   summarise(mse = (sum(diff)^2) / length(diff),
             ave_r2 = mean(model_r2)) %>%
-  arrange(training_data, set)
+  arrange(set)
 ```
@@
 hamby224_lime_results %>%
-  group_by(training_data, set) %>%
-  arrange(mse) %>%
-  slice(1:2)
+  arrange(mse)
 ```
@@
   geom_line() + 
-  facet_grid(training_data ~ set) + 
+  facet_grid( ~ set) + 
   theme_bw()
@@
 hamby224_lime_results %>%
-  group_by(training_data, set) %>%
+  group_by(set) %>%
   arrange(desc(ave_r2)) %>%
@@
   geom_line() + 
-  facet_grid(training_data ~ set) + 
+  facet_grid(~ set) + 
   theme_bw()
@@
 
+## Assessing the Variability of the LIME Results
+
+```{r}
+# Perform the sensitivity analysis if not already saved
+if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+
+  # Specify the inputs for the sensitivity analysis 
+  sensitivity_inputs <- data.frame(bin_continuous = rep(TRUE, 100),
+                                   quantile_bins = rep(c(TRUE, FALSE), each = 50),
+                                   nbins = rep(2:6, each = 10),
+                                   use_density = rep(TRUE, 100)) %>%
+    mutate(case = 1:length(bin_continuous)) %>%
+    select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Run lime for the sensitivity analysis
+  sensitivity_outputs <- future_pmap(.l = as.list(sensitivity_inputs %>% select(-case)),
+             .f = run_lime, # run_lime is one of my helper functions
+             train = hamby173and252_train %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3,
+             seed = FALSE) %>%
+    map_df(function(list) list$explain) %>%
+    mutate(rep = factor(rep(rep(1:10, each = dim(hamby224_test %>% na.omit())[1] * 3), 10))) %>%
+    full_join(hamby224_test %>% na.omit() %>% 
+                mutate(case = as.character(case)), by = "case") %>%
+    mutate(case = factor(case)) %>%
+    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
+
+  # Save the sensitivity inputs and outputs
+  saveRDS(sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
+  sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+
+}
+
+sensitivity_results <- sensitivity_outputs %>%
+  mutate(diff = rfscore - model_prediction) %>%
+  group_by(rep, bin_continuous, nbins, quantile_bins, use_density) %>%
+  summarise(mse = sum((diff)^2) / length(diff))
+
+sensitivity_results %>%
+  group_by(bin_continuous, nbins, quantile_bins, use_density) %>%
+  summarise(mean = mean(mse),
+            sd = sd(mse))
+
+sensitivity_results %>%
+  ggplot(aes(x = factor(nbins), y = mse)) + 
+  geom_boxplot() + 
+  geom_point()
+```
+
 ## Visualizing the LIME Explanations
@@
 hamby224_test_explain %>%
-  filter(training_data == "Full", set == "Set 1", nbins == "2") %>%
+  filter(set == "Set 1", nbins == "2") %>%
   ggplot(aes(x = feature_desc)) + 
@@
 ```{r}
-hamby224_test_explain %>%
-  filter(training_data == "Full", set == "Set 1", nbins == "2") %>%
-  mutate(rfscore = round(rfscore, 3)) %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  bind_rows(hamby224_test_explain %>%
-                  filter(is.na(rfscore), set == "Set 1") %>%
-                  select(case, bullet1, bullet2, land1, land2, rfscore)) %>%
+hamby224_test %>%
+  filter(set == "Set 1") %>%
   ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,

### 2018-12-04 app/app.R

@@ -14,7 +14,7 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby224_test <- read.csv("../data/hamby224_test.csv")
 hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 hamby224_bins <- readRDS("../data/hamby224_bins.rds")
 hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
@@ -25,7 +25,7 @@ hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
 
 # Function for creating a table with the bin information relating to specified features
 bin_table <- function(features, case, bin_cuts){
-
+  
   # Subset the bin cuts table to the selected feature
   selected_bin_cuts <- bin_cuts[[case]] %>% 
     filter(Feature %in% features) %>%
@@ -43,37 +43,39 @@ bin_table <- function(features, case, bin_cuts){
 
 # Layout of the app
 ui <- fluidPage(
-   
-   # Application title
-   titlePanel("LIME Explanations for Bullet Matching"),
   
-   # Row for input options
-   fluidRow(title = "LIME Input Options",
-            column(width = 3,
-                   selectInput("set", 
-                               label = "Select a Hamby 224 dataset", 
-                               choices = c("Set 1", "Set 11"))),
-            column(width = 3, 
-                   selectInput("data",
-                               label = "Select version of training data",
-                               choices = c("Full", "Subsampled"))),
-            column(width = 3,
-                   selectInput("density", 
-                               label = "Select density estimation method for LIME", 
-                               choices = c("Bins", "Kernel Density", "Normal Approximation"))),
-            column(width = 3,
-                   uiOutput('bintype'),
-                   uiOutput('nbins'))),
-   
-   # Row for heatmap and lime feature plot
-   fluidRow(column(width = 6,
-                   plotlyOutput("tileplot")),
-            column(width = 6, 
-                   plotOutput("featureplot")))
-   
-   # Row for information about the LIME bins
-   # fluidRow(column(width = 6,
-   #                 plotOutput("distributionplot")))
+  theme = shinythemes::shinytheme("lumen"),
+  
+  # Application title
+  titlePanel("LIME Explanations for Bullet Matching"),
+  
+  # Row for input options
+  fluidRow(column(width = 6,
[…]

### 2018-12-04 code/comparing_times_furrr.R

@@ -1,0 +1,35 @@
+
+# It took about half the time when using the function from furrr!
+
+library(tictoc)
+library(future)
+library(furrr)
+
+# This should take 6 seconds in total running sequentially
+plan(sequential)
+tic()
+sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
+                                                         select(-case)),
+                                          .f = run_lime, # run_lime is one of my helper functions
+                                          train = hamby173and252_train %>% select(rf_features),
+                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                          rfmodel = as_classifier(rtrees),
+                                          label = "TRUE",
+                                          nfeatures = 3,
+                                          seed = FALSE)
+toc()
+# 218.188 sec elapsed
+
+plan(multiprocess)
+tic()
+sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
+                                                         select(-case)),
+                                          .f = run_lime, # run_lime is one of my helper functions
+                                          train = hamby173and252_train %>% select(rf_features),
+                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                          rfmodel = as_classifier(rtrees),
+                                          label = "TRUE",
+                                          nfeatures = 3,
+                                          seed = FALSE)
+toc()
+# 107.731 sec elapsed

### 2018-12-04 code/helper_functions.R

@@ -7,7 +7,7 @@
 # Function for running the lime functions which runs the lime and explain 
 # objects in a list
 run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
-                     data_name, train, test, rfmodel, label, nfeatures, 
+                     train, test, rfmodel, label, nfeatures, 
                      seed = TRUE){
   
   # Set a seed if requested
@@ -19,8 +19,7 @@ run_lime <- function(bin_continuous, quantile_bins, nbins, use_density,
   
   # Run the explain function and add a variable for the number of bins
   explain <- explain(x = test, explainer = lime, labels = label, n_features = nfeatures) %>%
-    mutate(training_data = data_name,
-           bin_continuous = bin_continuous,
+    mutate(bin_continuous = bin_continuous,
            quantile_bins = quantile_bins,
            nbins = nbins,
            use_density = use_density)
@@ -112,7 +111,7 @@ create_bin_data <- function(lime_object){
 ## ---------------------------------------------------------------
 
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, d_n, b_c, q_b, n_b, u_d, bin_data, case_info){
+bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, case_info){
   
   if (is.na(feature) | b_c == FALSE) {
     
@@ -124,8 +123,7 @@ bin_labeller <- function(feature, feature_value, d_n, b_c, q_b, n_b, u_d, bin_da
     # Determine which item in the list of bin divisions to grab 
     # based on the case info
     selected_list_item <- case_info %>%
-      filter(data_name == d_n,
-             bin_continuous == b_c, 
+      filter(bin_continuous == b_c, 
              quantile_bins == q_b,
              nbins == n_b, 
              use_density == u_d) %>%

### 2018-12-04 code/subsample_code.R

@@ -1,0 +1,31 @@
+# Code saved for future use for the sampling data
+
+# Create the data (with a set seed)
+set.seed(20181128)
+hamby173and252_train_sub <- hamby173and252_train %>%
+  filter(samesource == FALSE) %>%
+  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
+  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
+
+# Save the subsampled data
+write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
+
+# Apply lime to the subsampled training data with the specified input options
+hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
+                                                        select(-case)),
+                                         .f = run_lime, # run_lime is one of my helper functions
+                                         train = hamby173and252_train_sub %>% select(rf_features),
+                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                         rfmodel = as_classifier(rtrees),
+                                         label = "TRUE",
+                                         nfeatures = 3,
+                                         seed = TRUE) %>%
+  mutate(training_data = factor("Subsampled"))
+
+# Separate the lime and explain function results from the subsampled data
+hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
+hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
+
+# Join the lime results from the full and subsampled training data
+hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
+hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)

### 2018-12-04 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on visualizing and summarizing sensativity analysis results

--- 2018-11-28 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 hamby224_lime_results %>%
-  group_by(training_data, set) %>%
+  group_by(set) %>%
   arrange(mse) %>%
@@
 
+## Assessing the Variability of the LIME Results
+
+```{r}
+# Perform the sensitivity analysis if not already saved
+if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+
+  # Specify the number of reps and input cases
+  nreps = 10
+  noptions = 12
+
+  # Specify the inputs for the sensitivity analysis
+  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
+                                                      rep(FALSE, nreps * 2)),
+                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
+                                                     rep(TRUE, nreps * 2)),
+                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
+                                             rep(4, nreps * 2)),
+                                   use_density = c(rep(TRUE, nreps * 11), 
+                                                   rep(FALSE, nreps))) %>%
+    mutate(case = 1:(nreps * noptions)) %>%
+    select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Run lime for the sensitivity analysis
+  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
+                                                             select(-case)),
+             .f = run_lime, # run_lime is one of my helper functions
+             train = hamby173and252_train %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3,
+             seed = FALSE) %>%
+    map_df(function(list) list$explain) %>%
+    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
+                            noptions))) %>%
+    full_join(hamby224_test %>% na.omit() %>% 
+                mutate(case = as.character(case)), by = "case") %>%
+    mutate(case = factor(case)) %>%
+    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
+
+  # Save the sensitivity inputs and outputs
+  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+
+}
+```
+
+```{r}
+hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
+  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
+                            sprintf("%.0f quantile bins", nbins),
+                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
+                                   sprintf("%.0f equally space bins", nbins),
+                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
+                                          "kernel density", "normal approximation"))),
+         diff = rfscore - model_prediction) %>%
+  mutate(situation = fct_relevel(situation, 
+                                 "2 quantile bins", 
+                                 "3 quantile bins",
+                                 "4 quantile bins",
+                                 "5 quantile bins",
+                                 "6 quantile bins"))
+
+hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
+  group_by(set, rep, situation) %>%
+  summarise(mse = sum((diff)^2) / length(diff))
+```
+
+```{r}
+hamby224_sensitivity_results %>%
+  group_by(set, case, rep, situation) %>%
+  slice(1) %>%
+  ungroup() %>%
+  group_by(set, case, situation) %>%
+  summarise(nlevels = length(levels(factor(feature))),
+            count = n()) %>%
+  ungroup() %>%
+  group_by(set, situation) %>%
+  summarise(mean_nlevels = mean(nlevels),
+            sd_nlevels = sd(nlevels),
+            upper = mean(nlevels) + sd(nlevels),
+            lower = mean(nlevels) - sd(nlevels)) %>%
+  ggplot(aes(x = situation, y = mean_nlevels)) + 
+  geom_point() + 
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_grid(. ~ set) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+dat <- data.frame()
+
+hamby224_sensitivity_results %>%
+  filter(set == "Set 1") %>%
+  group_by(case, situation, rep) %>%
+  slice(1) %>%
+  ggplot(aes(x = case, fill = feature)) + 
+  geom_bar(position = "stack") + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) + 
+  theme(legend.position = "bottom")
+```
+
+```{r}
+hamby224_sensitivity_mses %>%
+  group_by(set, situation) %>%
+  summarise(mean = mean(mse),
+            sd = sd(mse))
+```
+
+```{r}
+hamby224_sensitivity_mses %>%
+  ggplot(aes(x = situation, y = mse)) + 
+  geom_boxplot() + 
+  geom_point() + 
+  facet_grid( ~ set) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "", y = "MSE")
+```
+
 ## Visualizing the LIME Explanations
@@
   - could compute something like an R^2_adj
+  - could force the intercept to be 0.5
+  - try out the subsampling
 

### 2018-12-11 journal/applying LIME to bullet data journal.Rmd
worked on visualizing the variation results and moved a lot of code to my "new" journal

---
title: "Applying LIME to Bullet Data Journal"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, fig.pos = "center")

# Load libraries
library(tidyverse)
library(bulletr)
library(randomForest)
library(lime)
library(cowplot)
library(purrr)
library(future)
library(furrr)

# Source functions
source("../code/helper_functions.R")

# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper

# Read in the test_explain data
hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")

# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(rtrees$importance)
```

# December 5, 2018 to December 11, 2018

I decided to start a journal this week to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data. I have been trying to decide which input values to use for LIME in the forensic examiners' paper, and I have decided that I would like to simplify matters even more by only focusing on a few input options. I have considered a handful of ways of answering this question (accuracy within one implementation of lime, accuracy across 10 implementations of lime, etc.), but I would like to reserve some of these ways for a future more technical paper. However, I would like a place to store my work to use for future purposes, and it would be nice to have a place to work where I do not feel the need to optimize code. I am hoping that this will be a place where I can write drafts of code and create first versions of graphics. Then I can clean up and organize the code when I write the paper.

Prior to this journal, I had been working on all of my ideas in the R markdown document for the paper, but now I am going to transfer a lot of that code to this journal. Many of the sections below include work that I did earlier this semester. I am just transferring them here now. Later I will move the necessary parts to the paper.

## Previous Work

### Feature Plots of Training and Testing Data Filled by `samesource`

I created the following two plots of the training data as suggested by Heike. The histograms below show the distributions of the features used in the random forest `rtrees`. The histograms are filled by the `samesource` variable, which is the truth of whether or not the comparison is from the same barrel and land. The default histograms make it hard to compare the distributions of the matches and non-matches since there are many more comparisons that have `samesource == FALSE`.

```{r}
# Create plots of the feature distributions colored by samesource for the training data
hamby173and252_train %>% 
  select(rf_features, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, samesource) %>%
  ggplot(aes(x = value, fill = samesource)) + 
  geom_histogram(bins = 30) + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
       title = "Hamby 173 and 252 Training Data") +
  theme_bw() +
  theme(legend.position = "bottom")
```

By setting `position = "fill"` in the `geom_histogram` function, it is easier to compare the matches and non-matches. <span style="color:teal"> These plots could be used in the future to hand select the bins for lime. Additionally, fitting a logistic regression to this data could also be used to determine the LC50, LC10, ad LC90, which could be used as the bins for lime. </span>

```{r}
# Create plots of the feature distributions colored by samesource for the training data
# using the position = "fill" option
hamby173and252_train %>% 
  select(rf_features, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, samesource) %>%
  ggplot(aes(x = value, fill = samesource)) + 
  geom_histogram(position = "fill", bins = 30) + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
       title = "Hamby 173 and 252 Training Data") +
  theme_bw() +
  theme(legend.position = "bottom")
```

The plots below have the same structure, but they are created with the Hamby 224 testing data. I chose to not separate the testing data by sets, but this is something that could be done later if necessary.

```{r}
# Create plots of the feature distributions colored by samesource for the testing data
hamby224_test %>% 
  select(rf_features, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, samesource) %>%
  ggplot(aes(x = value, fill = samesource)) + 
  geom_histogram(bins = 30) + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
       title = "Hamby 224 Testing Data") +
  theme_bw() +
  theme(legend.position = "bottom")

# Create plots of the feature distributions colored by samesource for the testing 
# data using the position = "fill" option
hamby224_test %>% 
  select(rf_features, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, samesource) %>%
  ggplot(aes(x = value, fill = samesource)) + 
  geom_histogram(position = "fill", bins = 30) + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
       title = "Hamby 224 Testing Data") +
  theme_bw() +
  theme(legend.position = "bottom")
```

### Correlation Plots of Training and Testing Data

I made these plots to look at the correlation between features in the training data within the TRUE and FALSE cases of samesource. The features are highly correlated for the match comparisons. It is clear that the variables are more correlated with the match comparisons than the non-match comparisons. However, there are still some variables that are relatively highly correlation with the non-match comparisons.

```{r fig.height = 4, fig.width = 9}
# Create a correlation heatmap of the match comparisons in the training data
cor_match <- hamby173and252_train %>%
  select(rf_features, samesource) %>%
  filter(samesource == TRUE) %>%
  select(-samesource) %>%
  cor() %>%
  reshape2::melt() %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") + 
  labs(x = "", y = "", fill = "Correlation",
       title = "Match Comparisons")

# Create a correlation heatmap of the non-match comparisons in the training data
cor_nonmatch <- hamby173and252_train %>%
  select(rf_features, samesource) %>%
  filter(samesource == FALSE) %>%
  select(-samesource) %>%
  cor() %>%
  reshape2::melt() %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(x = "", y = "", fill = "Correlation",
       title = "Non-Match Comparisons")

# Create a title for the panel of plots
cor_title <- ggdraw() +
  draw_label("Correlation of Feature Variables in the Training Data", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             hjust = 0.5)

# Create a joined legend for the panel of plots
cor_legend <- get_legend(cor_match + theme(legend.position = "right"))

# Create the panel of plots
plot_grid(cor_title, 
          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
          ncol = 1,
          rel_heights = c(0.25, 3))
```

The plots below show the correlations for the testing data. The patterns in the plots look really similar to ones of the training data.

```{r fig.height = 4, fig.width = 9}
# Create a correlation heatmap of the match comparisons in the training data
cor_match_test <- hamby224_test %>%
  select(rf_features, samesource) %>%
  filter(samesource == TRUE) %>%
  select(-samesource) %>%
  cor() %>%
  reshape2::melt() %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") + 
  labs(x = "", y = "", fill = "Correlation",
       title = "Match Comparisons")

# Create a correlation heatmap of the non-match comparisons in the training data
cor_nonmatch_test <- hamby224_test %>%
  select(rf_features, samesource) %>%
  filter(samesource == FALSE) %>%
  select(-samesource) %>%
  cor() %>%
  reshape2::melt() %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(x = "", y = "", fill = "Correlation",
       title = "Non-Match Comparisons")

# Create a title for the panel of plots
cor_title_test <- ggdraw() +
  draw_label("Correlation of Feature Variables in the Testing Data", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             hjust = 0.5)

# Create a joined legend for the panel of plots
cor_legend_test <- get_legend(cor_match_test + theme(legend.position = "right"))

# Create the panel of plots
plot_grid(cor_title_test, 
          plot_grid(cor_match_test, cor_nonmatch_test, cor_legend_test, 
                    ncol = 3, rel_widths = c(2, 2, 0.5)),
          ncol = 1,
          rel_heights = c(0.25, 3))
```

### Visualizing the LIME Explanations

```{r}
hamby224_test_explain %>%
  filter(set == "Set 1", nbins == "2") %>%
  ggplot(aes(x = feature_desc)) +
  geom_bar() +
  coord_flip() +
  facet_grid(set ~ .)
```

```{r}
hamby224_test %>%
  filter(set == "Set 1") %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
             text = paste('Bullets Compared: ', bullet1, "-", land1, 
                          "vs", bullet2, "-", land2,
                          '\nRandom Forest Score: ', 
                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet2 ~ bullet1, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(x = "", y = "", fill = "RF Score")
```

### Draft of LIME Procedure from the `lime` R Package

I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm. It needs a lot of work, but it is a start. The final version of this will end up in the technical stats paper critiquing LIME. The version in the firearm examiner's paper will be much simpler...

The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare. For simplicity, the steps are described as what happens to one case in the test data. Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.

Let
  $$Y_{jk} = \begin{cases} 
  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
  0 & \mbox{otherwise}
  \end{cases}$$
be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the

1. Distributions for each of the features in the training data are obtained. 
    + The method that `lime` uses to obtain the distribution differs based on the feature type. All of the features in the Hamby datasets are numeric. For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected. The default number of bins is 4 (`n_bins = 4`).

2. Many ($n$) samples from each of the feature distributions are drawn.
     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
      * bin\_continuous = TRUE should continuous variables be binned?
      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
      * n\_bins = 4 number of bins if bin\_continuous is TRUE
      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)

3. Predictions for the testing data using the random forest model are computed.
     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match. Since the random forest is a classification model, `lime` is set to return the prediction probabilities.

4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
    + The way that the similarity score is computed depends on the type of feature. Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point. Then, by default, the Gower distance is used to compute the similarity score. (using the `gower` package in R)

5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
      * forward selection with ridge regression
      * highest weight with ridge regression
      * LASSO model
      * tree model
      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise

6. A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores. If the response is categorical, the user can select how many categories and which categories they want to explain.
  $$P(Match = TRUE) = \beta_0 + 
  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
For the prediction of interest, 
  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
7. The feature weights are extracted and used as the explanations.

Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all. Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.

## Work on Determining Input Values for LIME

### Assessing the Accuracy of LIME

```{r}
hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
```

```{r}
hamby224_lime_results <- hamby224_lime_comparisons %>%
  filter(!is.na(rfscore)) %>%
  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
  summarise(mse = (sum(diff)^2) / length(diff),
            ave_r2 = mean(model_r2)) %>%
  arrange(set)
```

```{r}
hamby224_lime_results %>%
  ungroup() %>%
  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
  geom_point() + 
  geom_line() + 
  facet_grid( ~ set) + 
  theme_bw()
```

```{r}
hamby224_lime_results %>%
  ungroup() %>%
  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
  geom_point() + 
  geom_line() + 
  facet_grid(~ set) + 
  theme_bw()
```

```{r eval = FALSE}
hamby224_lime_comparisons %>%
  filter(quantile_bins == TRUE, nbins == "3", set == "Set 1") %>%
  select(rf_features, diff, -case) %>%
  gather(key = feature, value = feature_value, rf_features) %>%
  select(feature, feature_value, diff) %>%
  ggplot(aes(x = feature_value, y = diff)) + 
  geom_point() + 
  facet_wrap(~ feature, scales = "free") + 
  geom_hline(yintercept = 0, color = "blue")

hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = model_prediction)) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) + 
  theme_bw() + 
  stat_smooth(method = "lm")

hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = abs(diff))) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  theme_bw()

hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = diff)) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  geom_hline(yintercept = 0, color = "blue") +
  theme_bw()
```

### Assessing the Variability of the LIME Results

```{r}
# Perform the sensitivity analysis if not already saved
if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {

  # Specify the number of reps and input cases
  nreps = 10
  noptions = 12

  # Specify the inputs for the sensitivity analysis
  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
                                                      rep(FALSE, nreps * 2)),
                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
                                                     rep(TRUE, nreps * 2)),
                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
                                             rep(4, nreps * 2)),
                                   use_density = c(rep(TRUE, nreps * 11), 
                                                   rep(FALSE, nreps))) %>%
    mutate(case = 1:(nreps * noptions)) %>%
    select(case, bin_continuous, nbins, quantile_bins, use_density)

  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Run lime for the sensitivity analysis
  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
                                                             select(-case)),
             .f = run_lime, # run_lime is one of my helper functions
             train = hamby173and252_train %>% select(rf_features),
             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
             rfmodel = as_classifier(rtrees),
             label = "TRUE",
             nfeatures = 3,
             seed = FALSE) %>%
    map_df(function(list) list$explain) %>%
    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
                            noptions))) %>%
    full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)

  # Save the sensitivity inputs and outputs
  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")

} else {

  # Load in the sensitivity inputs and outputs
  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")

}
```

```{r}
hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
                            sprintf("%.0f quantile bins", nbins),
                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
                                   sprintf("%.0f equally space bins", nbins),
                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
                                          "kernel density", "normal approximation"))),
         diff = rfscore - model_prediction) %>%
  mutate(situation = fct_relevel(situation, 
                                 "2 quantile bins", 
                                 "3 quantile bins",
                                 "4 quantile bins",
                                 "5 quantile bins",
                                 "6 quantile bins"))

hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
  group_by(set, rep, situation) %>%
  summarise(mse = sum((diff)^2) / length(diff))
```

```{r}
hamby224_consistency <- hamby224_sensitivity_results %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(set, situation, case) %>%
  summarise(nlevels = length(levels(factor(feature))),
            count = n()) %>%
  ungroup() %>%
  group_by(set, situation) %>%
  summarise(mean_nlevels = mean(nlevels),
            sd_nlevels = sd(nlevels),
            upper = mean(nlevels) + sd(nlevels),
            lower = mean(nlevels) - sd(nlevels),
            max = max(nlevels),
            min = min(nlevels))
```

```{r}
hamby224_consistency %>%
  ggplot(aes(x = situation, y = mean_nlevels)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_grid(. ~ set) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
hamby224_sensitivity_results %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(set, situation, case) %>%
  summarise(nlevels = length(levels(factor(feature)))) %>%
  ggplot(aes(x = situation, fill = factor(nlevels))) + 
  geom_bar(position = "stack") +
  facet_grid( ~ set) + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, hjust = 1))
```

The plot below needs some work, but it does contain some interesting information. Right now, I am only concentrating on set 1. We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case. We can also see that different variables are selected as important depending on the number of bins. It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases. On the other hand, the quantile bins choose different first variables for the cases.

```{r}
hamby224_sensitivity_results %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 12)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_brewer(palette = "Blues")
```

```{r}
hamby224_sensitivity_mses %>%
  ggplot(aes(x = situation, y = mse)) + 
  geom_boxplot() + 
  geom_point() + 
  facet_grid( ~ set) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x = "", y = "MSE")
```

### Deciding on LIME Input Settings

```{r}
joined_results <- hamby224_lime_results %>%
  ungroup() %>%
  mutate(nbins = as.numeric(as.character(nbins))) %>%
  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
                            sprintf("%.0f quantile bins", nbins),
                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
                                   sprintf("%.0f equally space bins", nbins),
                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
                                          "kernel density", "normal approximation")))) %>%
  mutate(situation = fct_relevel(situation, 
                                 "2 quantile bins", 
                                 "3 quantile bins",
                                 "4 quantile bins",
                                 "5 quantile bins",
                                 "6 quantile bins")) %>%
  select(set, situation, mse, ave_r2) %>%
  full_join(hamby224_sensitivity_mses %>%
              group_by(set, situation) %>%
              summarise(mean_sensitivity_mse = mean(mse), 
                        sd_sensitivity_mse = sd(mse)),
            by = c("set", "situation")) %>%
  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
            by = c("set", "situation")) %>%
  #filter(!(situation %in% c("normal approximation", "kernel density"))) %>%
  group_by(set) %>%
  mutate(mse_order = dense_rank(mse),
         ave_r2_order = dense_rank(desc(ave_r2)),
         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
         mean_nlevels_order = dense_rank(mean_nlevels))
```

```{r}
joined_results %>%
  ungroup() %>%
  filter(set == "Set 1") %>%
  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  knitr::kable()

joined_results %>%
  ungroup() %>%
  filter(set == "Set 11") %>%
  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  knitr::kable()
```

### 2018-12-11 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on visualizing the variation results and moved a lot of code to my "new" journal

@@
 rf_features <- rownames(rtrees$importance)
-```
-
-```{r fig.height = 5, fig.width = 8}
-# Create plots of the feature distributions colored by samesource for the training data
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-```{r fig.height = 5, fig.width = 8}
-# Create plots of the feature distributions colored by samesource for the training data
-# using the position = "fill" option
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-```{r fig.height = 4, fig.width = 9}
-# Create a correlation heatmap of the match comparisons in the training data
-cor_match <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == TRUE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Match Comparisons")
-
-# Create a correlation heatmap of the non-match comparisons in the training data
-cor_nonmatch <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == FALSE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") +
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Non-Match Comparisons")
-
-# Create a title for the panel of plots
-cor_title <- ggdraw() +
-  draw_label("Correlation of Feature Variables in the Training Data", 
-             fontface = "bold", 
-             size = 16,
-             x = 0.5,
-             hjust = 0.5)
-
-# Create a joined legend for the panel of plots
-cor_legend <- get_legend(cor_match + theme(legend.position = "right"))
-
-# Create the panel of plots
-plot_grid(cor_title, 
-          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
-          ncol = 1,
-          rel_heights = c(0.25, 3))
 ```
@@
 
+The developers of LIME wrote a Python package to implement LIME, and Thomas Lin Pedersen adapted their work to create an R package called `lime`.
+This paper will use version `r packageVersion("lime")` of the R package `lime` in the analysis of the bullet matching data.
+
 ## Applying LIME
 
-The developers of LIME wrote a Python package to implement LIME, and Thomas Lin Pedersen adapted their work to create an R package called `lime`.
-This paper will use version `r packageVersion("lime")` of the R package `lime` in the analysis of the bullet matching data.
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
-
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
-
-\begin{enumerate}
-\item Distributions for each of the features in the training data are obtained.
-
-\begin{quote}
-The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile\_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n\_bins = 4`).
-\end{quote}
-
-\item $n$ samples from each of the feature distributions are drawn.
-
-\begin{quote}
-To do this, `lime` has several options (mostly quoted from `lime` package for now):
-\begin{itemize}
-\item bin\_continuous = TRUE should continuous variables be binned?
-\item quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-\item n\_bins = 4 number of bins if bin\_continuous is TRUE
-\item use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
-\end{itemize}
-\end{quote}
-
-\item Predictions for the testing data using the random forest model are computed.
-
-\begin{quote}
-The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-\end{quote}
-
-\item Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-
-\begin{quote}
-The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-\end{quote}
-
-\item Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value.
-The 0-1 versions of the features are used.
-
-\begin{quote}
-The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-\begin{enumerate}
-\item forward selection with ridge regression
-\item highest weight with ridge regression
-\item LASSO model
-\item tree model
-\item default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-\end{enumerate}
-\end{quote}
-
-\item A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-
-For the prediction of interest,
-
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-
-\item The feature weights are extracted and used as the explanations.
-
-\end{enumerate}
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+(this is the section where I will describe how lime was applied and which input values were used)
 
@@
 
-  # Create a data frame with the interesting information relating to the differe
+  # Create a data frame with the interesting information relating to the different
   # evaluations of lime and compute the difference and mean between the rf and rr
@@
 
-```{r}
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
-  summarise(mse = (sum(diff)^2) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set)
-```
-
-```{r}
-hamby224_lime_results %>%
-  group_by(set) %>%
-  arrange(mse) %>%
-  slice(1:2)
-```
-
-```{r}
-hamby224_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
-  geom_point() + 
-  geom_line() + 
-  facet_grid( ~ set) + 
-  theme_bw()
-```
-
-```{r}
-hamby224_lime_results %>%
-  group_by(set) %>%
-  arrange(desc(ave_r2)) %>%
-  slice(1:2)
-```
-
-```{r}
-hamby224_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
-  geom_point() + 
-  geom_line() + 
-  facet_grid(~ set) + 
-  theme_bw()
-```
-
-```{r eval = FALSE}
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == TRUE, nbins == "8", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue")
-
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == TRUE, nbins == "3", set == "Set 11") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue")
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm")
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 11") %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm")
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  theme_bw()
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 11") %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  theme_bw()
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = diff)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  geom_hline(yintercept = 0, color = "blue") +
-  theme_bw()
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 11") %>%
-  ggplot(aes(x = rfscore, y = diff)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  geom_hline(yintercept = 0, color = "blue") +
-  theme_bw()
-```
-
-## Assessing the Variability of the LIME Results
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 12
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
-                                                      rep(FALSE, nreps * 2)),
-                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                     rep(TRUE, nreps * 2)),
-                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
-                                             rep(4, nreps * 2)),
-                                   use_density = c(rep(TRUE, nreps * 11), 
-                                                   rep(FALSE, nreps))) %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous, nbins, quantile_bins, use_density)
-
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis
-  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
-                                                             select(-case)),
-             .f = run_lime, # run_lime is one of my helper functions
-             train = hamby173and252_train %>% select(rf_features),
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions))) %>%
-    full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
-  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
-                            sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
-                                   sprintf("%.0f equally space bins", nbins),
-                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
-                                          "kernel density", "normal approximation"))),
-         diff = rfscore - model_prediction) %>%
-  mutate(situation = fct_relevel(situation, 
-                                 "2 quantile bins", 
-                                 "3 quantile bins",
-                                 "4 quantile bins",
-                                 "5 quantile bins",
-                                 "6 quantile bins"))
-
-hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
-  group_by(set, rep, situation) %>%
-  summarise(mse = sum((diff)^2) / length(diff))
-```
-
-```{r}
-hamby224_sensitivity_results %>%
-  group_by(set, case, rep, situation) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, case, situation) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels)) %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_point() + 
-  geom_errorbar(aes(ymin = lower, ymax = upper)) +
-  facet_grid(. ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-```{r}
-dat <- data.frame()
-
-hamby224_sensitivity_results %>%
-  filter(set == "Set 1") %>%
-  group_by(case, situation, rep) %>%
-  slice(1) %>%
-  ggplot(aes(x = case, fill = feature)) + 
-  geom_bar(position = "stack") + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) + 
-  theme(legend.position = "bottom")
-```
-
-```{r}
-hamby224_sensitivity_mses %>%
-  group_by(set, situation) %>%
-  summarise(mean = mean(mse),
-            sd = sd(mse))
-```
-
-```{r}
-hamby224_sensitivity_mses %>%
-  ggplot(aes(x = situation, y = mse)) + 
-  geom_boxplot() + 
-  geom_point() + 
-  facet_grid( ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "", y = "MSE")
-```
-
 ## Visualizing the LIME Explanations
-
-```{r}
-hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "2") %>%
-  ggplot(aes(x = feature_desc)) + 
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
-
-```{r}
-hamby224_test %>%
-  filter(set == "Set 1") %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-             text = paste('Bullets Compared: ', bullet1, "-", land1, 
-                          "vs", bullet2, "-", land2,
-                          '\nRandom Forest Score: ', 
-                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
-  geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet2 ~ bullet1, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank()) +
-  labs(x = "", y = "", fill = "RF Score")
-```
 

### 2018-12-11 app/app.R

@@ -44,8 +44,6 @@ bin_table <- function(features, case, bin_cuts){
 # Layout of the app
 ui <- fluidPage(
   
-  theme = shinythemes::shinytheme("lumen"),
-  
   # Application title
   titlePanel("LIME Explanations for Bullet Matching"),
   

### 2018-12-11 journal/applying LIME to bullet data journal.Rmd
worked more on writing the journal entry

@@
   ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 30) + 
+  geom_histogram(bins = 15) + 
   facet_wrap( ~ feature, scales = "free") +
@@
   ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 30) + 
+  geom_histogram(position = "fill", bins = 15) + 
   facet_wrap( ~ feature, scales = "free") +
@@
 
-### Visualizing the LIME Explanations
+### Visualizations of the LIME Explanations
+
+Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
+This one has been created from the lime explanations with 2 quantile bins.
+It includes all three of the chosen features for each case in the testing dataset.
+For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
 
@@
 hamby224_test_explain %>%
-  filter(set == "Set 1", nbins == "2") %>%
+  filter(nbins == "2", quantile_bins == TRUE) %>%
   ggplot(aes(x = feature_desc)) +
@@
 ```
+
+The plot below is the model for the one that will be used in the app for exploring the `lime` explanations from the bullet matching data. This is the data from set 1 of the testing dataset.
 
@@
 
-### Assessing the Accuracy of LIME
+When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
+This led me to try applying LIME with a handful of input values.
+However, since LIME is based on random permutations, I was curious to know how consistent the results were.
+This led me to try running each implementation for specific starting values a handful of times.
+The next two sections consider the results from these studies.
+
+### Assessing the Accuracy of the LIME Results
+
+The figures in this section are created from the implementations of LIME on the set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, kernel density estimation, and normal distribtion approximation.
+Each set of input values was only run once.
 
 ```{r}
+# Read in the lime comparison data (the comparisons are run in the firearm examiner
+# paper since they will be discussed in the paper)
 hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
 ```
+
+#### Complex versus Simple Model Predictions
+
+The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
+The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
+The plot is faceted by number of bins and whether or not the bins are equally spaced or based on quantiles.
+The points are colored by the $R^2$ value from the fit of the simple model.
+The lines are linear regression lines fit to the data points within a facet.
+We would hope that there is a linear relationship between these two variables.
+None of the cases show strong linear trends, but some are more linear than others.
+The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
+The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
+I noticed that within the facets, the points are in mostly horiztonal strips, and the number of strips is about the number of bins from the lime implementation.
+
+```{r}
+hamby224_lime_comparisons %>%
+  mutate(quantile_bins = fct_recode(factor(quantile_bins), "equal bins" = "FALSE",
+                                    "quantile bins" = "TRUE")) %>%
+  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
+  ggplot(aes(x = rfscore, y = model_prediction)) + 
+  geom_point(aes(color = model_r2)) + 
+  facet_grid(quantile_bins ~ nbins) + 
+  theme_bw() + 
+  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
+The points are faceted by number of bins and whether the bins are equally spaced or based on quantiles.
+Again, the points are colored by the $R^2$ values from the simple model.
+All cases show a v-shaped trend.
+The low part of the v occurs around a random forest score of about 0.25.
+That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
+It gets worse near the extremes.
+However, it is interesting to note that with the equally spaced bins, the absolute difference decreases near 1 for 3 to 6 bins.
+This si not the case with the quantile bins.
+It appears that the equally spaced bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
+
+```{r}
+hamby224_lime_comparisons %>%
+  mutate(quantile_bins = fct_recode(factor(quantile_bins), "equal bins" = "FALSE",
+                                    "quantile bins" = "TRUE")) %>%
+  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
+  ggplot(aes(x = rfscore, y = abs(diff))) + 
+  geom_point(aes(color = model_r2)) + 
+  facet_grid(quantile_bins ~ nbins) + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+At somepoint, I got the idea in my head that it woudl be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
+The plot below shows one example with the data from 3 equally spaced bins.
+There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
+This may be something to return to.
+
+```{r}
+hamby224_lime_comparisons %>%
+  filter(quantile_bins == FALSE, nbins == "3", set == "Set 1") %>%
+  select(rf_features, diff, -case) %>%
+  gather(key = feature, value = feature_value, rf_features) %>%
+  select(feature, feature_value, diff) %>%
+  ggplot(aes(x = feature_value, y = diff)) + 
+  geom_point() + 
+  facet_wrap(~ feature, scales = "free") + 
+  geom_hline(yintercept = 0, color = "blue")
+```
+
+#### Comparing Input Values by MSE and $R^2$
 
@@
   facet_grid(~ set) + 
-  theme_bw()
-```
-
-```{r eval = FALSE}
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == TRUE, nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue")
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm")
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  theme_bw()
-
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1") %>%
-  ggplot(aes(x = rfscore, y = diff)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_wrap( ~ nbins) +
-  geom_hline(yintercept = 0, color = "blue") +
   theme_bw()

### 2018-12-11 journal/applying LIME to bullet data journal.Rmd
worked more on journal entry

@@
 
+In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
+I defined the mean squared error as
+  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple}}-\hat{p}_{\mbox{complex}})^2}{n}$$
+where $n$ is the number of observations in the testing dataset (within a set).
+Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
+
 ```{r}
@@
   group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
-  summarise(mse = (sum(diff)^2) / length(diff),
+  summarise(mse = (sum(diff^2)) / length(diff),
             ave_r2 = mean(model_r2)) %>%
-  arrange(set)
+  arrange(set) %>%
+  ungroup() %>%
+  mutate(nbins = as.numeric(as.character(nbins))) %>%
+  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
+                            sprintf("%.0f quantile bins", nbins),
+                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
+                                   sprintf("%.0f equally spaced bins", nbins),
+                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
+                                          "kernel density", "normal approximation")))) %>%
+  mutate(situation = fct_relevel(situation, 
+                                 "2 quantile bins", 
+                                 "3 quantile bins",
+                                 "4 quantile bins",
+                                 "5 quantile bins",
+                                 "6 quantile bins"))
 ```
+
+The plot below shows the mean squared errors for each of the input situations faceted by set.
+In both cases, the lowest mean squared error occurs with 3 equally spaced bins.
+This seems to suggest that using 3 equally spaced bins should provide better explanations.
 
@@
 hamby224_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = mse, color = bc_qb, group = bc_qb)) +
+  ggplot(aes(x = situation, y = mse)) +
   geom_point() + 
-  geom_line() + 
   facet_grid( ~ set) + 
-  theme_bw()
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 ```
+
+The plot below shows the average $R^2$ value for each of the input situations faceted by set.
+The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
+The $R^2$ values for 3 equally spaced bins are in the middle.
 
@@
 hamby224_lime_results %>%
-  ungroup() %>%
-  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
-         nbins = factor(ifelse(bin_continuous == FALSE, NA, as.character(nbins)))) %>%
-  ggplot(aes(x = nbins, y = ave_r2, color = bc_qb, group = bc_qb)) +
+  ggplot(aes(x = situation, y = ave_r2)) +
   geom_point() + 
-  geom_line() + 
-  facet_grid(~ set) + 
-  theme_bw()
+  facet_grid( ~ set) + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 ```
@@
 ### Assessing the Variability of the LIME Results
+
+In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times.
+I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
 
@@
                             ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
-                                   sprintf("%.0f equally space bins", nbins),
+                                   sprintf("%.0f equally spaced bins", nbins),
                                    ifelse(bin_continuous == FALSE & use_density == TRUE, 
@@
                                  "6 quantile bins"))
+```
 
+```{r}
 hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
@@
   summarise(mse = sum((diff)^2) / length(diff))
+```
+
+The plot below shows boxplots of the 10 mean squared errors computed for each of the input situations for each set.
+There does not appear to be much variation for most of the cases.
+The largest amount of variation occurs with 4 and 5 equally spaced bins.
+There is moderate variability for 3 equally spaced bins, but all of the 10 runs resulted in much lower mses than any of the other situations.
+This still seems to support the choice of using 3 equally spaced quantile bins for both sets.
+
+```{r}
+hamby224_sensitivity_mses %>%
+  ggplot(aes(x = situation, y = mse)) + 
+  geom_boxplot() + 
+  geom_point() + 
+  facet_grid( ~ set) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "", y = "MSE")
 ```
@@
 
+To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
+I then computed the average number of different top features chosen by LIME within a input situations for each set.
+The plot below contains these values shown as the dots.
+The error bars represent one standard deviation above and below the mean.
+Note that the number of levels cannot go below 1, but the error bars go below 1.
+I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
+
+There are a handful of situations with a mean near one and very little variation.
+However, the largest mean is around 2, which is not very high.
+This seems to suggest that LIME is relatively consistent across runs.
+
 ```{r}
@@
 ```
+
+The bar chart below shows the proportion of different number of top features chosen across all test cases within a set for each input situation.
+This shows that the most different features chosen was four.
+However, many of the caes only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
 
@@
 
-```{r}
+```{r fig.height = 8, fig.width = 10}
 hamby224_sensitivity_results %>%
@@
         axis.ticks.y = element_blank()) + 
-  scale_fill_brewer(palette = "Blues")
-```
-
-```{r}
-hamby224_sensitivity_mses %>%
-  ggplot(aes(x = situation, y = mse)) + 
-  geom_boxplot() + 
-  geom_point() + 
-  facet_grid( ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "", y = "MSE")
+  scale_fill_brewer(palette = "Blues") + 
+  labs(x = "cases")
 ```
@@
 ### Deciding on LIME Input Settings
+
+In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
+The first table below is for set 1, and the second table below is for set 11.
 

### 2018-12-12 journal/applying LIME to bullet data journal.Rmd
finished journal entry for this week

@@
 
-# December 5, 2018 to December 11, 2018
+# December 5, 2018 to December 14, 2018
 
@@
                                  "5 quantile bins",
-                                 "6 quantile bins"))
+                                 "6 quantile bins")) %>%
+  mutate(bin_situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE,
+                                "quantile bins",
+                                ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
+                                       "equally spaced bins", "other")))
 ```
@@
 hamby224_lime_results %>%
-  ggplot(aes(x = situation, y = mse)) +
+  ggplot(aes(x = situation, y = mse, color = bin_situation)) +
   geom_point() + 
@@
   theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+        legend.position = "bottom")
 ```
@@
 hamby224_lime_results %>%
-  ggplot(aes(x = situation, y = ave_r2)) +
+  ggplot(aes(x = situation, y = ave_r2, color = bin_situation)) +
   geom_point() + 
@@
   theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom")
 ```
@@
 hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
-  group_by(set, rep, situation) %>%
+  group_by(set, rep, situation, bin_situation) %>%
   summarise(mse = sum((diff)^2) / length(diff))
@@
   ggplot(aes(x = situation, y = mse)) + 
-  geom_boxplot() + 
+  geom_boxplot(aes(color = bin_situation)) + 
   geom_point() + 
@@
 hamby224_consistency <- hamby224_sensitivity_results %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
+  select(set, situation, bin_situation, case, rep, feature, feature_weight) %>%
   mutate(feature_weight_abs = abs(feature_weight)) %>%
@@
   ungroup() %>%
-  group_by(set, situation, case) %>%
+  group_by(set, situation, bin_situation, case) %>%
   summarise(nlevels = length(levels(factor(feature))),
@@
   ungroup() %>%
-  group_by(set, situation) %>%
+  group_by(set, situation, bin_situation) %>%
   summarise(mean_nlevels = mean(nlevels),
@@
   ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_point() + 
+  geom_point(aes(color = bin_situation)) + 
   geom_errorbar(aes(ymin = lower, ymax = upper)) +
@@
   theme(legend.position = "bottom", 
-        axis.text.x = element_text(angle = 45, hjust = 1))
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
 ```
@@
 On the other hand, the quantile bins choose different first variables for the cases.
+
+The fact that different features get chosen as the top feature for different estimation techniques makes sense.
+You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
+For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
+This is the feature that lime most frequently chooses.
+You can make similar arguments for other cases as well.
+Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
+I think this is what leads some input values to better LIME explanations and lower MSEs than others.
 
@@
 
+I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
+I realized it would be helpful to view the relationship between the features and the random forest score.
+The plots below show the testing data with random forest score versus each of the features.
+The points are colored by the samesource variable.
+
+```{r}
+hamby224_test %>% 
+  select(rf_features, rfscore, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, rfscore, samesource) %>%
+  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
+  geom_point() + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
+       title = "Hamby 224 Testing Data") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+```
+
 ### Deciding on LIME Input Settings
@@
 The first table below is for set 1, and the second table below is for set 11.
+
+While using these to help me decide which input settings to use, I had a handful of thoughts:
+
+* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
+* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
+This makes me think that it would be okay to base my decision off of the results from the single rep.
+* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
+* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
+Right now, the feature plots from these explanations are not very helpful.
+I would need to adjust the intercept or something.
+
+Based on the MSEs from the single impelementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
 
@@
             by = c("set", "situation")) %>%
-  #filter(!(situation %in% c("normal approximation", "kernel density"))) %>%
   group_by(set) %>%
@@
   arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  knitr::kable()
+  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
+                rownames = FALSE,
+                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
+                             "Mean R2"),
+                caption = "Results from Set 1")
 
@@
   arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  knitr::kable()
+  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
+                rownames = FALSE,
+                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
+                             "Mean R2"),
+                caption = "Results from Set 11")
 ```

### 2018-12-14 journal/applying LIME to bullet data journal.Rmd
small changes

@@
 I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple}}-\hat{p}_{\mbox{complex}})^2}{n}$$
+  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
 where $n$ is the number of observations in the testing dataset (within a set).
@@
 ```
+
+```{r}
+library(rpart)
+
+tree <- rpart(samesource ~ ccf, data = hamby173and252_train, 
+              control = rpart.control(cp = 0.0005, maxdepth = 2))
+plot(tree)
+text(tree)
+
+tree2 <- cutree(tree, k = 5)
+```

### 2018-12-14 app/app.R

@@ -47,9 +47,11 @@ ui <- fluidPage(
   # Application title
   titlePanel("LIME Explanations for Bullet Matching"),
   
+  # fluidRow(column(width = 12,
+  #                 checkboxInput("limeoptions", "Show LIME Input Options", value = FALSE))),
+  
   # Row for input options
   fluidRow(column(width = 6,
-                  #p("This app allows the user to explore the LIME explanations for Hamby 224 predictions made by the random forest model rtrees."),
                   fluidRow(column(width = 6,
                                   selectInput("set", 
                                               label = "Select a Hamby 224 dataset", 
@@ -58,17 +60,20 @@ ui <- fluidPage(
                                     condition = "input.density == 'Bins'",
                                     selectInput('bintype',
                                                 label = "Select the bin type for LIME", 
-                                                choices =  c("Quantile Bins", 
-                                                             "Equally Spaced Bins")))),
+                                                choices =  c("Equally Spaced Bins",
+                                                             "Quantile Bins"),
+                                                selected = "Equally Spaced Bins"))),
                            column(width = 6,
                                   selectInput("density", 
                                               label = "Select density estimation method for LIME", 
-                                              choices = c("Bins", "Kernel Density", "Normal Approximation")),
+                                              choices = c("Bins", "Kernel Density", "Normal Approximation"),
+                                              selected = "Bins"),
                                   conditionalPanel(
                                     condition = "input.density == 'Bins'",
                                     selectInput("nbins", 
                                                 label = "Select the number of bins for LIME", 
-                                                choices = 2:6)))),
+                                                choices = 2:6,
+                                                selected = 3)))),
                   plotlyOutput("tileplot")),
           
            column(width = 6,

### 2018-12-19 journal/applying LIME to bullet data journal.Rmd
updated journal after meeting and made two versions of app

@@
 
-# December 5, 2018 to December 14, 2018
+## December 5, 2018 to December 14, 2018
 
@@
 
-## Previous Work
+### Previous Work
 
-### Feature Plots of Training and Testing Data Filled by `samesource`
+#### Feature Plots of Training and Testing Data Filled by `samesource`
 
@@
 
-### Correlation Plots of Training and Testing Data
+#### Correlation Plots of Training and Testing Data
 
@@
 
-### Visualizations of the LIME Explanations
+#### Visualizations of the LIME Explanations
 
@@
 
-### Draft of LIME Procedure from the `lime` R Package
+#### Draft of LIME Procedure from the `lime` R Package
 
@@
 
-## Work on Determining Input Values for LIME
+### Work on Determining Input Values for LIME
 
@@
 
-### Assessing the Accuracy of the LIME Results
+#### Assessing the Accuracy of the LIME Results
 
@@
 
-#### Complex versus Simple Model Predictions
+##### Complex versus Simple Model Predictions
 
@@
 
-#### Comparing Input Values by MSE and $R^2$
+##### Comparing Input Values by MSE and $R^2$
 
@@
 
-### Assessing the Variability of the LIME Results
+#### Assessing the Variability of the LIME Results
 
@@
 
+In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
+Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
+In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
+
 ```{r fig.height = 8, fig.width = 10}
@@
 
-### Deciding on LIME Input Settings
+#### Deciding on LIME Input Settings
 
@@
 
-```{r}
-library(rpart)
+#### Notes on meeting with Heike
 
-tree <- rpart(samesource ~ ccf, data = hamby173and252_train, 
-              control = rpart.control(cp = 0.0005, maxdepth = 2))
-plot(tree)
-text(tree)
+* We talked about including the penalty for the number of parameters in the dicussion of the paper.
+* We talked about using a tree to choose the bins.
+This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
+(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
+* Look at the AUC after binning
 
-tree2 <- cutree(tree, k = 5)
+## December 15, 2018 to January 8, 2018
+
+Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
+Here is an example using the function below with the predictor variable of ccf.
+
+```{r echo = TRUE}
+treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
 ```

### 2018-12-19 app/app.R

@@ -47,8 +47,8 @@ ui <- fluidPage(
   # Application title
   titlePanel("LIME Explanations for Bullet Matching"),
   
-  # fluidRow(column(width = 12,
-  #                 checkboxInput("limeoptions", "Show LIME Input Options", value = FALSE))),
+  fluidRow(column(width = 12,
+                 checkboxInput("limeoptions", "Show LIME input options", value = FALSE))),
   
   # Row for input options
   fluidRow(column(width = 6,
@@ -56,14 +56,16 @@ ui <- fluidPage(
                                   selectInput("set", 
                                               label = "Select a Hamby 224 dataset", 
                                               choices = c("Set 1", "Set 11")),
+                                  conditionalPanel(condition = "input.limeoptions",
                                   conditionalPanel(
                                     condition = "input.density == 'Bins'",
                                     selectInput('bintype',
                                                 label = "Select the bin type for LIME", 
                                                 choices =  c("Equally Spaced Bins",
                                                              "Quantile Bins"),
-                                                selected = "Equally Spaced Bins"))),
+                                                selected = "Equally Spaced Bins")))),
                            column(width = 6,
+                                  conditionalPanel(condition = "input.limeoptions",
                                   selectInput("density", 
                                               label = "Select density estimation method for LIME", 
                                               choices = c("Bins", "Kernel Density", "Normal Approximation"),
@@ -73,7 +75,7 @@ ui <- fluidPage(
                                     selectInput("nbins", 
                                                 label = "Select the number of bins for LIME", 
                                                 choices = 2:6,
-                                                selected = 3)))),
+                                                selected = 3))))),
                   plotlyOutput("tileplot")),
           
            column(width = 6,
@@ -128,7 +130,7 @@ server <- function(input, output) {
       } 
       
       # Make the plot interactive
-      ggplotly(plot, source = "tileplot", width = 700, height = 550, tooltip = "text") %>%
+      ggplotly(plot, source = "tileplot", width = 635, height = 525, tooltip = "text") %>%
         style(hoverinfo = "skip", traces = 7) %>% 
         config(displayModeBar = FALSE)
   

### 2018-12-19 code/helper_functions.R

@@ -162,3 +162,60 @@ bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, bin_data, c
   return(feature_bin)
   
 }
+
+## ---------------------------------------------------------------
+## Create Bins using a Tree
+## ---------------------------------------------------------------
+
+# Function to get from a tree to k bins:
+# Inputs: x = feature, y = response variable, k = number of bins
+# Outputs: k-1 values for breakpoints (does not include minimum and maximum)
+
+library(tidyverse)
+library(rpart)
+library(partykit)
+
+treebink <- function (y, x, k, minsplit = 20) {
+  
+  cp <- 0.01
+  tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
+  while ((nrow(tree$cptable) < k) & (cp > 1e-9)) {
+    cp <- cp/10
+    tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
+  }
+  cpdf <- data.frame(tree$cptable)
+  idx <- which(cpdf$nsplit == k-1)
+  if (length(idx) == 0) idx <- nrow(cpdf)
+  cp <- cpdf$CP[idx]
+  tree <-  rpart::prune(tree, cp = cp)
+  
+  ###############
+  # now we have a tree with the right number of splits
+  
+  nodes <- partykit:::.list.rules.party(as.party(tree))
+  dframe <- data.frame(rule = nodes)
+  dframe$split <- strsplit(as.character(dframe$rule), " & ")
+  dframe$id <- 1:nrow(dframe)
+  
+  dframe <- dframe %>% unnest(split)
+  dframe <- dframe %>% mutate(value = readr::parse_number(split)
+                              #  lower = stringr::str_detect(split, pattern = ">=")
+  )
+  # we could now do all sorts of fancy interval output, but we just need the breaks
+  breaks <- sort(unique(dframe$value))
+  if (length(breaks) != k-1) warning("Not enough intervals found, consider decreasing minsplit (default is 20)")
+  breaks
+  
+}
+
+# Examples:
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 5)
+# 
+# # gives warning
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 10)
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 10, minsplit = 5)
[…]

### 2019-01-16 journal/applying LIME to bullet data journal.Rmd
worked on implementing tree based binning method

@@
 date: "`r format(Sys.time(), '%B %d, %Y')`"
-output: html_document
+output:
+  html_document:
+    toc: true
+    toc_depth: 4
+    toc_float: true
 ---
@@
 
-## December 5, 2018 to December 14, 2018
+## 12/5/18 - 12/14/18
 
@@
 
-The figures in this section are created from the implementations of LIME on the set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, kernel density estimation, and normal distribtion approximation.
+The figures in this section are created from the implementations of LIME on the set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, kernel density estimation, and normal distribution approximation.
 Each set of input values was only run once.
@@
 The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-I noticed that within the facets, the points are in mostly horiztonal strips, and the number of strips is about the number of bins from the lime implementation.
+I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the number of bins from the lime implementation.
 
@@
 However, it is interesting to note that with the equally spaced bins, the absolute difference decreases near 1 for 3 to 6 bins.
-This si not the case with the quantile bins.
+This is not the case with the quantile bins.
 It appears that the equally spaced bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
@@
 
-At somepoint, I got the idea in my head that it woudl be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
+At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
 The plot below shows one example with the data from 3 equally spaced bins.
@@
 This shows that the most different features chosen was four.
-However, many of the caes only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
+However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
 
@@
 
-Based on the MSEs from the single impelementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
+Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
 
@@
 
-* We talked about including the penalty for the number of parameters in the dicussion of the paper.
+* We talked about including the penalty for the number of parameters in the discussion of the paper.
 * We talked about using a tree to choose the bins.
@@
 
-## December 15, 2018 to January 8, 2018
+## 12/15/18 - 1/13/19
 
@@
 ```
+
+## 1/14/19 - ?
+
+### Goals
+
+Goals for spring semester:
+
+- implement ideas for better binning methods
+- write draft of firearm examiner's paper with everything but the methods and results sections
+- find an idea that leads to better LIME explanations
+- once the better LIME binning method has been selected, write the methods and results sections
+- make plans for the statistical paper
+
+Goals for week 1:
+
+- set up meeting time with Heike
+- get tree method up and running
+- start to work on evaluation of the results of the new method
+- start looking into the weights
+- work on introduction and data section of firearm examiners' paper
+
+### Visualizations of Tree Based Bins Results
+
+```{r}
+# I need to fix the situations to new options 
+hamby224_test_explain %>%
+  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
+                            sprintf("%.0f quantile bins", nbins),
+                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
+                                   sprintf("%.0f equally spaced bins", nbins),
+                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
+                                          "kernel density", "normal approximation"))),
+         diff = rfscore - model_prediction) %>%
+  mutate(situation = fct_relevel(situation, 
+                                 "2 quantile bins", 
+                                 "3 quantile bins",
+                                 "4 quantile bins",
+                                 "5 quantile bins",
+                                 "6 quantile bins")) %>%
+  mutate(bin_situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE,
+                                "quantile bins",
+                                ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
+                                       "equally spaced bins", "other"))) %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  na.omit() %>%
+  select(situation, case, feature, feature_weight) %>%
+  ggplot(aes(x = case, y = situation, fill = feature)) + 
+  geom_tile()
+```

### 2019-01-16 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
small changes
worked on implementing tree based binning method

@@
 This allows for the ability to understand which were the driving variables that led to a prediction of interest.
+
+(should probably list other current methods for interpreting random forests)
 
@@
   # Specify the options to use with lime
-  hamby224_lime_inputs <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
+  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 15), rep(FALSE, 2)),
                                quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), 
-                                                       rep(TRUE, 2)),
-                                     nbins = c(rep(2:6, 2), rep(4, 2)),
-                                     use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
-    mutate(case = 1:length(bin_continuous)) %>%
-    select(case, bin_continuous, nbins, quantile_bins, use_density)
+                                                 rep(TRUE, 5), rep(TRUE, 2)),
+                               nbins = c(rep(2:6, 3), rep(4, 2)),
+                               use_density = c(rep(TRUE, 15), TRUE, FALSE),
+                               bin_method = c(rep("quantile_bins", 5),
+                                              rep("equally_spaced", 5),
+                                              rep("tree", 5),
+                                              rep("quantile_bins", 2)))
 
@@
   # Apply lime to the full training data with the specified input options
-  hamby224_lime_explain <- future_pmap(.l = as.list(hamby224_lime_inputs %>% 
-                                                    select(-case)),
+  hamby224_lime_explain <- future_pmap(.l = hamby224_lime_inputs,
              .f = run_lime, # run_lime is one of my helper functions
@@
              test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             response = hamby173and252_train$samesource,
              rfmodel = as_classifier(rtrees),
@@
   # Name the items in the lime list
-  names(hamby224_lime) <- map_chr(1:dim(hamby224_lime_inputs)[1], function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s",
+  names(hamby224_lime) <- map_chr(1:length(hamby224_lime_inputs), function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s",
               hamby224_lime_inputs$bin_continuous[case],
@@
               hamby224_lime_inputs$nbins[case],
-              hamby224_lime_inputs$use_density[case]))
+              hamby224_lime_inputs$use_density[case],
+              hamby224_lime_inputs$bin_method[case]))
+
+  hamby224_lime_inputs <- hamby224_lime_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(hamby224_lime_inputs), 
+           dimnames = list(NULL, names(hamby224_lime_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:length(hamby224_lime_inputs$quantile_bins)) %>%
+    select(case, bin_continuous:bin_method)
 
@@
                                   n_b = nbins,
-                                  u_d = use_density),
+                                  u_d = use_density,
+                                  b_m = bin_method),
                             .f = bin_labeller, # bin_labeller is one of my helper functions
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(bin_continuous:use_density, case:feature_desc, feature_bin:strictly_less, 
+    select(bin_continuous:bin_method, case:feature_desc, feature_bin:strictly_less, 
            data, prediction)
@@
     select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method) %>%
     slice(1) %>%
@@
 
-## Visualizing the LIME Explanations
+## Development of Shiny App for Visualizing the LIME Explanations
 
 # Results
+
+- show examples of using the app and what we have learned from the LIME explanations
 

### 2019-01-16 app/app.R

@@ -62,7 +62,8 @@ ui <- fluidPage(
                                     selectInput('bintype',
                                                 label = "Select the bin type for LIME", 
                                                 choices =  c("Equally Spaced Bins",
-                                                             "Quantile Bins"),
+                                                             "Quantile Bins",
+                                                             "Tree Based Bins"),
                                                 selected = "Equally Spaced Bins")))),
                            column(width = 6,
                                   conditionalPanel(condition = "input.limeoptions",
@@ -176,16 +177,22 @@ server <- function(input, output) {
           chosen_estimator <- TRUE
           chosen_bintype <- TRUE
           chosen_nbins <- 4
+          chosen_method <- "quantile_bins"
         } else if (input$density == "Normal Approximation") {
           chosen_bins <- FALSE
           chosen_estimator <- FALSE
           chosen_bintype <- TRUE
           chosen_nbins <- 4
+          chosen_method <- "quantile_bins"
         } else {
           chosen_bins <- TRUE
           chosen_estimator <- TRUE
-          chosen_bintype <- ifelse(input$bintype == "Quantile Bins", TRUE, FALSE)
+          chosen_bintype <- ifelse(input$bintype %in% c("Quantile Bins", "Tree Based Bins"),
+                                   TRUE, FALSE)
           chosen_nbins <- input$nbins
+          chosen_method <- ifelse(input$bintype == "Quantile Bins", "quantile_bins",
+                                  ifelse(input$bintype == "Equally Spaced Bins", "equally_spaced",
+                                         "tree"))
         }
         
         # Create a dataset with the feature information for the selected comparison
@@ -195,6 +202,7 @@ server <- function(input, output) {
                  quantile_bins == chosen_bintype,
                  nbins == chosen_nbins,
                  use_density == chosen_estimator,
+                 bin_method == chosen_method,
                  land1 == as.character(location$land1),
                  land2 == as.character(location$land2),
                  bullet1 == location$bullet1,
@@ -280,7 +288,7 @@ server <- function(input, output) {
     if(length(click_data)){
       
       if(!is.na(click_data$z)){
-            
+          
         # Grab the chosen input options
         chosen_set <- paste("Set", unlist(strsplit(input$set, split = " "))[2])
         if (input$density == "Kernel Density") {
@@ -288,16 +296,22 @@ server <- function(input, output) {
           chosen_estimator <- TRUE
[…]

### 2019-01-16 code/helper_functions.R

@@ -1,28 +1,187 @@
 ## Helper Functions for the Paper
 
 ## ---------------------------------------------------------------
+## Create Bins using a Tree
+## ---------------------------------------------------------------
+
+# Function to get from a tree to k bins:
+# Inputs: x = feature, y = response variable, k = number of bins
+# Outputs: k-1 values for breakpoints (does not include minimum and maximum)
+
+library(tidyverse)
+library(rpart)
+library(partykit)
+
+treebink <- function (y, x, k, minsplit = 20) {
+  
+  cp <- 0.01
+  tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
+  while ((nrow(tree$cptable) < k) & (cp > 1e-9)) {
+    cp <- cp/10
+    tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
+  }
+  cpdf <- data.frame(tree$cptable)
+  cpdf$ksplits <- cpdf$nsplit-(k-1)
+  idx <- which.min(abs(cpdf$ksplits))
+   
+  cp <- cpdf$CP[idx]
+  tree <-  rpart::prune(tree, cp = cp)
+  
+  ###############
+  # now we have a tree with the right number of splits
+  
+  nodes <- partykit:::.list.rules.party(as.party(tree))
+  dframe <- data.frame(rule = nodes)
+  dframe$split <- strsplit(as.character(dframe$rule), " & ")
+  dframe$id <- 1:nrow(dframe)
+  
+  dframe <- dframe %>% unnest(split)
+  dframe <- dframe %>% mutate(value = readr::parse_number(split)
+                              #  lower = stringr::str_detect(split, pattern = ">=")
+  )
+  # we could now do all sorts of fancy interval output, but we just need the breaks
+  breaks <- sort(unique(dframe$value))
+  if (length(breaks) != k-1) warning("Not enough intervals found, consider decreasing minsplit (default is 20)")
+  breaks
+  
+}
+
+# Examples:
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 5)
+# 
+# # gives warning
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 10)
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 10, minsplit = 5)
+# 
+# # gives warning
+# treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 5, minsplit = 40)
+
[…]

### 2019-01-16 journal/applying LIME to bullet data journal.Rmd
worked more on updating code to implement trees and started reorganizing journal

@@
 ---
-title: "Applying LIME to Bullet Data Journal"
+title: "Applying LIME to Bullet Data Research Journal"
 author: "Katherine Goode"
@@
     toc: true
-    toc_depth: 4
+    toc_depth: 2
     toc_float: true
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, fig.pos = "center")
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
+                      fig.pos = "center")
+```
 
+# Overview
+
+I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
+I have been trying to decide which input values to use for LIME in the forensic examiners' paper, and I have decided that I would like to simplify matters even more by only focusing on a few input options.
+I have considered a handful of ways of answering this question (accuracy within one implementation of lime, accuracy across 10 implementations of lime, etc.), but I would like to reserve some of these ways for a future more technical paper.
+However, I would like a place to store my work to use for future purposes, and it would be nice to have a place to work where I do not feel the need to optimize code.
+I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
+Then I can clean up and organize the code when I write the paper.
+
+Prior to this journal, I had been working on all of my ideas in the R markdown document for the paper, but now I am going to transfer a lot of that code to this journal.
+Many of the sections below include work that I did earlier this semester.
+I am just transferring them here now.
+Later I will move the necessary parts to the paper.
+
+```{r}
 # Load libraries
@@
 
-## 12/5/18 - 12/14/18
+# Plots of Features
 
-I decided to start a journal this week to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I have been trying to decide which input values to use for LIME in the forensic examiners' paper, and I have decided that I would like to simplify matters even more by only focusing on a few input options.
-I have considered a handful of ways of answering this question (accuracy within one implementation of lime, accuracy across 10 implementations of lime, etc.), but I would like to reserve some of these ways for a future more technical paper.
-However, I would like a place to store my work to use for future purposes, and it would be nice to have a place to work where I do not feel the need to optimize code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the paper.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the paper, but now I am going to transfer a lot of that code to this journal.
-Many of the sections below include work that I did earlier this semester.
-I am just transferring them here now.
-Later I will move the necessary parts to the paper.
-
-### Previous Work
-
-#### Feature Plots of Training and Testing Data Filled by `samesource`
+## Distributions by `samesource`
 
@@
 
-#### Correlation Plots of Training and Testing Data
+## Correlations
 
@@
 
-#### Visualizations of the LIME Explanations
+# Visualizations of Explanations
 
@@
 
-#### Draft of LIME Procedure from the `lime` R Package
+# Draft of LIME Procedure
 
@@
 
-### Work on Determining Input Values for LIME
+# Tree Based Bins
+
+## Functions
+
+Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
+Here is an example using the function below with the predictor variable of ccf.
+
+```{r echo = TRUE}
+treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
+```
+
+I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
+The output from `mylime` can then be input into the `explain` function to obtain explanations.
+I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
+I've been working on redoing code from earlier in this journal to work for the added binning method.
+
+There seems to be a problem with `treebink` with certain variables with high enough bins. The function returns more than the desired number of bins. Heike is going to look into this.
+
+# Assessing Lime Explanations
 
@@
 
-#### Assessing the Accuracy of the LIME Results
+## Accuracy
 
@@
 
-##### Complex versus Simple Model Predictions
+### Complex versus Simple Model Predictions
 
@@
 hamby224_lime_comparisons %>%
-  mutate(quantile_bins = fct_recode(factor(quantile_bins), "equal bins" = "FALSE",
-                                    "quantile bins" = "TRUE")) %>%
   filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(quantile_bins ~ nbins) + 
+  facet_grid(bin_method ~ nbins) + 
   theme_bw() + 
@@
 hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, nbins == "3", set == "Set 1") %>%
+  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
   select(rf_features, diff, -case) %>%
@@
 
-##### Comparing Input Values by MSE and $R^2$
+### Comparing Input Values by MSE and $R^2$
 
@@
   filter(!is.na(rfscore)) %>%
-  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
+  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
+           bin_method, set) %>%
   summarise(mse = (sum(diff^2)) / length(diff),
@@
   arrange(set) %>%
-  ungroup() %>%
-  mutate(nbins = as.numeric(as.character(nbins))) %>%
-  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
-                            sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
-                                   sprintf("%.0f equally spaced bins", nbins),
-                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
-                                          "kernel density", "normal approximation")))) %>%
-  mutate(situation = fct_relevel(situation, 
-                                 "2 quantile bins", 
-                                 "3 quantile bins",
-                                 "4 quantile bins",
-                                 "5 quantile bins",
-                                 "6 quantile bins")) %>%
-  mutate(bin_situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE,
-                                "quantile bins",
-                                ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
-                                       "equally spaced bins", "other")))
+  ungroup()
 ```
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom")
+        legend.position = "bottom") + 
+  labs(x = "Situation", y = "MSE", color = "")
 ```
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom")
+        legend.position = "bottom") + 
+  labs(x = "Situation", y = "Average R2", color = "")
 ```
 
-#### Assessing the Variability of the LIME Results
+## Variability
 
@@
 
-#### Deciding on LIME Input Settings
+## Input Rankings
 
@@
 
-#### Notes on meeting with Heike
+## Heike's Suggestions
 
@@
 
-## 12/15/18 - 1/13/19
+## Results from One Implementation
 
-Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
-Here is an example using the function below with the predictor variable of ccf.
+```{r}
+# Selects only the top features for the cases where binning was used
+top_features <- hamby224_test_explain %>%
+  filter(bin_situation != "other") %>%
+  select(set, situation, bin_situation, case, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, desc(feature_weight_abs)) %>%
+  group_by(situation, case) %>%
+  slice(1)
 
-```{r echo = TRUE}
-treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
+# Plots the top feature for each case for each bin situation
+ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
+  geom_tile() + 
+  facet_grid(set ~ bin_situation, scales = "free") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+
+# Plots the proportions of number of top features chosen across number of bins for a case
+# within a binning method
+top_features %>%
+  group_by(set, case, bin_situation) %>%
+  summarise(nfeatures = length(levels(factor(feature)))) %>%
+  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
+  geom_bar(position = "stack") + 
+  facet_grid(set ~ .) + 
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues")
 ```
 
-## 1/14/19 - ?
+## Assessing Variability
 
-### Goals
-
-Goals for spring semester:
-
-- implement ideas for better binning methods
-- write draft of firearm examiner's paper with everything but the methods and results sections
-- find an idea that leads to better LIME explanations
-- once the better LIME binning method has been selected, write the methods and results sections
-- make plans for the statistical paper
-
-Goals for week 1:
-
-- set up meeting time with Heike
-- get tree method up and running
-- start to work on evaluation of the results of the new method
-- start looking into the weights
-- work on introduction and data section of firearm examiners' paper
-
-### Visualizations of Tree Based Bins Results
+In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times.
+I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
 
 ```{r}
-# I need to fix the situations to new options 
-hamby224_test_explain %>%
+# Perform the sensitivity analysis if not already saved
+if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+
+  # Specify the number of reps and input cases
+  nreps = 10
+  noptions = 12
+
+  # Specify the inputs for the sensitivity analysis
+  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
+                                                      rep(FALSE, nreps * 2)),
+                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
+                                                     rep(TRUE, nreps * 2)),
+                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
+                                             rep(4, nreps * 2)),
+                                   use_density = c(rep(TRUE, nreps * 11), 
+                                                   rep(FALSE, nreps))) %>%
+    mutate(case = 1:(nreps * noptions)) %>%
+    select(case, bin_continuous, nbins, quantile_bins, use_density)
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Run lime for the sensitivity analysis
+  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
+                                                             select(-case)),
+             .f = run_lime, # run_lime is one of my helper functions
+             train = hamby173and252_train %>% select(rf_features),
+             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3,
+             seed = FALSE) %>%
+    map_df(function(list) list$explain) %>%
+    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
+                            noptions))) %>%
+    full_join(hamby224_test %>% na.omit() %>% 
+                mutate(case = as.character(case)), by = "case") %>%
+    mutate(case = factor(case)) %>%
+    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
+
+  # Save the sensitivity inputs and outputs
+  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+
+}
+```
+
+```{r}
+hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
   mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
@@
                                 ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
-                                       "equally spaced bins", "other"))) %>%
+                                       "equally spaced bins", "other")))
+```
+
+```{r}
+hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
+  group_by(set, rep, situation, bin_situation) %>%
+  summarise(mse = sum((diff)^2) / length(diff))
+```
+
+The plot below shows boxplots of the 10 mean squared errors computed for each of the input situations for each set.
+There does not appear to be much variation for most of the cases.
+The largest amount of variation occurs with 4 and 5 equally spaced bins.
+There is moderate variability for 3 equally spaced bins, but all of the 10 runs resulted in much lower mses than any of the other situations.
+This still seems to support the choice of using 3 equally spaced quantile bins for both sets.
+
+```{r}
+hamby224_sensitivity_mses %>%
+  ggplot(aes(x = situation, y = mse)) + 
+  geom_boxplot(aes(color = bin_situation)) + 
+  geom_point() + 
+  facet_grid( ~ set) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "", y = "MSE")
+```
+
+```{r}
+hamby224_consistency <- hamby224_sensitivity_results %>%
+  select(set, situation, bin_situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(1) %>%
+  ungroup() %>%
+  group_by(set, situation, bin_situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature))),
+            count = n()) %>%
+  ungroup() %>%
+  group_by(set, situation, bin_situation) %>%
+  summarise(mean_nlevels = mean(nlevels),
+            sd_nlevels = sd(nlevels),
+            upper = mean(nlevels) + sd(nlevels),
+            lower = mean(nlevels) - sd(nlevels),
+            max = max(nlevels),
+            min = min(nlevels))
+```
+
+To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
+I then computed the average number of different top features chosen by LIME within a input situations for each set.
+The plot below contains these values shown as the dots.
+The error bars represent one standard deviation above and below the mean.
+Note that the number of levels cannot go below 1, but the error bars go below 1.
+I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
+
+There are a handful of situations with a mean near one and very little variation.
+However, the largest mean is around 2, which is not very high.
+This seems to suggest that LIME is relatively consistent across runs.
+
+```{r}
+hamby224_consistency %>%
+  ggplot(aes(x = situation, y = mean_nlevels)) + 
+  geom_point(aes(color = bin_situation)) + 
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_grid(. ~ set) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+The bar chart below shows the proportion of different number of top features chosen across all test cases within a set for each input situation.
+This shows that the most different features chosen was four.
+However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
+
+```{r}
+hamby224_sensitivity_results %>%
+  select(set, situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(1) %>%
+  ungroup() %>%
+  group_by(set, situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature)))) %>%
+  ggplot(aes(x = situation, fill = factor(nlevels))) + 
+  geom_bar(position = "stack") +
+  facet_grid( ~ set) + 
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+```
+
+The plot below needs some work, but it does contain some interesting information.
+Right now, I am only concentrating on set 1.
+We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
+We can also see that different variables are selected as important depending on the number of bins.
+It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
+On the other hand, the quantile bins choose different first variables for the cases.
+
+The fact that different features get chosen as the top feature for different estimation techniques makes sense.
+You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
+For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
+This is the feature that lime most frequently chooses.
+You can make similar arguments for other cases as well.
+Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
+I think this is what leads some input values to better LIME explanations and lower MSEs than others.
+
+In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
+Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
+In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
+
+```{r fig.height = 8, fig.width = 10}
+hamby224_sensitivity_results %>%
   filter(set == "Set 1") %>%
   droplevels() %>%
-  na.omit() %>%
-  select(situation, case, feature, feature_weight) %>%
-  ggplot(aes(x = case, y = situation, fill = feature)) + 
-  geom_tile()
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(1) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 12)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) +
+  #facet_grid(nlevels ~ situation) +
+  theme(legend.position = "bottom",
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_brewer(palette = "Blues") + 
+  labs(x = "cases")
 ```

### 2019-01-16 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked more on updating code to implement trees and started reorganizing journal

@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, fig.pos = "center")
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
+                      fig.pos = "center")
 
@@
 
-  # Reorder the variables of feature_desc and feature_bin for plotting purposes
+  # Reorder the variables of feature_desc and feature_bin for plotting purposes and
+  # create new variables of situation and bin_situation
   hamby224_test_explain <- hamby224_test_explain %>%
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(bin_continuous:bin_method, case:feature_desc, feature_bin:strictly_less, 
-           data, prediction)
+    mutate(nbins = as.numeric(as.character(nbins)),
+           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                              sprintf("%.0f quantile bins", nbins),
+                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                     sprintf("%.0f equally spaced bins", nbins),
+                                     ifelse(bin_continuous == TRUE & bin_method == "tree",
+                                            sprintf("%.0f tree based bins", nbins),
+                                            ifelse(bin_continuous == FALSE & use_density == TRUE, 
+                                                   "kernel density", 
+                                                   "normal approximation")))) %>%
+             fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
+                         "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
+                         "3 equally spaced bins", "4 equally spaced bins",
+                         "5 equally spaced bins", "6 equally spaced bins")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
+                                "quantile bins",
+                                ifelse(bin_method == "equally_spaced" & bin_continuous == TRUE,
+                                       "equally spaced bins", 
+                                       ifelse(bin_method == "tree" & bin_continuous == TRUE,
+                                              "tree based bins", "other")))) %>%
+    mutate(bin_situation = factor(bin_situation)) %>%
+    select(situation, bin_situation, bin_continuous:bin_method, case:feature_desc,
+           feature_bin:strictly_less, data, prediction)
 
@@
     ungroup() %>%
-    select(bin_continuous, quantile_bins, nbins, use_density, 
+    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, nbins, use_density, 
            set, case, rf_features, rfscore, model_prediction, model_r2) %>%

### 2019-01-16 journal/applying LIME to bullet data journal.Rmd
added some old code in R scripts to the journal

@@
 library(lime)
+library(caret)
 library(cowplot)
@@
 Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+
+# Caret vs RandomForest
+
+The `lime` function in lime is set up to work with specific packages.
+For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
+I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
+It seemed to work.
+However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
+To do this, I used the iris data.
+The code below goes through the process of fiting the two models (`rf_model` and `caret_model`).
+Then the `lime` and `explain` functions are applied to both models.
+
+```{r}
+# Code for comparing the output from LIME when the model is 
+# fit with caret and randomForest
+# Last Updated: 2018/11/13
+
+## Set up -----------------------------------------------------------------------------
+
+# Split up the data set
+iris_test <- iris[1:5, 1:4]
+iris_train <- iris[-(1:5), 1:4]
+iris_lab <- iris[[5]][-(1:5)]
+
+## LIME with caret --------------------------------------------------------------------
+
+# Create Random Forest model on iris data
+caret_model <- train(iris_train, iris_lab, method = 'rf')
+
+# Create an explainer object
+caret_explainer <- lime(iris_train, caret_model)
+
+# Explain new observation
+caret_explanation <- explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
+
+## LIME with randomForest -------------------------------------------------------------
+
+rf_model <- randomForest(iris_train, iris_lab)
+
+# Create an explainer object
+rf_explainer <- lime(iris_train, model = as_classifier(rf_model))
+
+# Explain new observation
+rf_explanation <- explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
+```
+
+To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
+I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
+Since lime is based on random permutations, I would not expect the values from the two models to be exact.
+However, I would like them to be close.
+The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
+We decided this seems like the two versions of the explanations are reasonably exchangeable.
+
+```{r}
+## Comparisons -----------------------------------------------------------------------
+
+# Grab the numeric caret explanation variables of interest
+caret_numeric <- caret_explanation %>%
+  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
+  gather(key = "variable", value = "caret_value")
+
+# Grab the numeric randomForest explanation variables of interest
+rf_numeric <- rf_explanation %>%
+  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
+  gather(key = "variable", value = "rf_value")
+
+# Join the two
+lime_numeric <- caret_numeric %>%
+  mutate(rf_value = rf_numeric$rf_value, 
+         variable = factor(variable))
+
+# Look at the MSEs for the variables
+lime_numeric %>%
+  group_by(variable) %>%
+  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
+
+# Scatterplots of the randomForest versus caret variable values
+ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
+  geom_point() + 
+  facet_wrap( ~ variable, scales = "free") + 
+  geom_abline(intercept = 0, slope = 1)
+```
+
+# Comparing Furrr Times
+
+The amount of time it took me to run the explain function with all of my input options was getting pretty long.
+Heike suggest that I use the furrr package, which implements the purrr functions using the speeed of the future package.
+I ran and timed the code below to see how much faster the code was.
+Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
+
+```{r eval = FALSE}
+# It took about half the time when using the function from furrr!
+
+library(tictoc)
+library(future)
+library(furrr)
+
+# Slow way
+plan(sequential)
+tictoc::tic()
+sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
+                                                         select(-case)),
+                                          .f = run_lime, # run_lime is one of my helper functions
+                                          train = hamby173and252_train %>% select(rf_features),
+                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                          rfmodel = as_classifier(rtrees),
+                                          label = "TRUE",
+                                          nfeatures = 3,
+                                          seed = FALSE)
+tictoc::toc()
+# 218.188 sec elapsed
+
+# Fast way
+plan(multiprocess)
+tictoc::tic()
+sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
+                                                         select(-case)),
+                                          .f = run_lime, # run_lime is one of my helper functions
+                                          train = hamby173and252_train %>% select(rf_features),
+                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                          rfmodel = as_classifier(rtrees),
+                                          label = "TRUE",
+                                          nfeatures = 3,
+                                          seed = FALSE)
+tictoc::toc()
+# 107.731 sec elapsed
+```
 

### 2019-01-16 code/comparing caret and randomForest with LIME.R

@@ -1,71 +1,0 @@
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Load libraries
-library(caret)
-library(lime)
-library(randomForest)
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-# The output is provided in a consistent tabular format and includes the
-# output from the model.
-head(caret_explanation)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
-
-# The output is provided in a consistent tabular format and includes the
-# output from the model.
-head(rf_explanation)
-
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
[…]

### 2019-01-16 code/comparing_times_furrr.R

@@ -1,35 +1,0 @@
-
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# This should take 6 seconds in total running sequentially
-plan(sequential)
-tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-toc()
-# 218.188 sec elapsed
-
-plan(multiprocess)
-tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-toc()
-# 107.731 sec elapsed

### 2019-01-17 journal/applying LIME to bullet data journal.Rmd
finished updating journal and edited all possible code to work with tree results

@@
 # Load libraries
-library(tidyverse)
 library(bulletr)
-library(randomForest)
-library(lime)
 library(caret)
 library(cowplot)
+library(furrr)
+library(future)
+library(lime)
+library(plotly)
 library(purrr)
-library(future)
-library(furrr)
+library(randomForest)
+library(tidyverse)
 
@@
 
+I also wrote some code to create the above plot using individual plots instead of facets. This is included below (but not executed).
+
+```{r eval = FALSE}
+# Code for creating the heatmap plots using individual plots
+
+# Input data
+hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
+
+# Create a dataset with all combinations of lands and bullets comparisons for each set
+combinations1 <- data.frame(set = factor(1),
+                            expand.grid(land1 = factor(1:6),
+                                        land2 = factor(1:6),
+                                        bullet1 = factor(c("1", "2", "Q")),
+                                        bullet2 = factor(c("1", "2", "Q"))))
+combinations11 <- data.frame(set = factor(11),
+                             expand.grid(land1 = factor(1:6),
+                                         land2 = factor(1:6), 
+                                         bullet1 = factor(c("1", "2", "I")),
+                                         bullet2 = factor(c("1", "2", "I"))))
+combinations <- rbind(combinations1, combinations11)
+
+# Join the combinations and the data so that all combinations have a row in the data
+hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
+                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
+  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"),
+         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
+                                       "Questioned" = "Q", "Questioned" = "I"))
+
+chosen_set = 1
+
+p1 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p2 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 2") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p3 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p4 <- ggplot() + geom_blank() + theme_classic()
+
+p5 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Known 2") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p6 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p7 <- ggplot() + geom_blank() + theme_classic()
+
+p8 <- ggplot() + geom_blank() + theme_classic()
+
+p9 <- hamby224_test_explain_NAs %>%
+  filter(set == chosen_set, bullet1 == "Questioned", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
+
+style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows = 3, titleX = TRUE, titleY = TRUE, margin = 0.03),
+      hoverinfo = "skip",
+      traces = 7)
+```
+
 # Draft of LIME Procedure
@@
 # Create an explainer object
-caret_explainer <- lime(iris_train, caret_model)
+caret_explainer <- lime::lime(iris_train, caret_model)
 
 # Explain new observation
-caret_explanation <- explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
+caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
 
@@
 # Create an explainer object
-rf_explainer <- lime(iris_train, model = as_classifier(rf_model))
+rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
 
 # Explain new observation
-rf_explanation <- explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
+rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
 ```
@@
 
+# Subsampled Bins
+
+One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles.
+The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`.
+By subsampling, it might allow for better locations to bin the data.
+I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.
+
+```{r eval = FALSE}
+# Code saved for future use for the sampling data
+
+# Create the data (with a set seed)
+set.seed(20181128)
+hamby173and252_train_sub <- hamby173and252_train %>%
+  filter(samesource == FALSE) %>%
+  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
+  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
+
+# Save the subsampled data
+write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
+
+# Apply lime to the subsampled training data with the specified input options
+hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
+                                                        select(-case)),
+                                         .f = run_lime, # run_lime is one of my helper functions
+                                         train = hamby173and252_train_sub %>% select(rf_features),
+                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+                                         rfmodel = as_classifier(rtrees),
+                                         label = "TRUE",
+                                         nfeatures = 3,
+                                         seed = TRUE) %>%
+  mutate(training_data = factor("Subsampled"))
+
+# Separate the lime and explain function results from the subsampled data
+hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
+hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
+
+# Join the lime results from the full and subsampled training data
+hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
+hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
+```
+
 # Tree Based Bins
 
-## Functions
+Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins.
+That is, the divisions in the tree could be used as the bin cuts.
+This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
+(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
 
 Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
+The function is stored in the file   `helper_functions.R`.
 Here is an example using the function below with the predictor variable of ccf.
@@
 
+However, there seems to be a problem with `treebink`.
+For certain variables, when a high number of bins is requessted, the function returns more than the desired number of bins.
+Heike is going to look into this.
+
 I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
+This function is also included in the file `helper_functions.R`.
 The output from `mylime` can then be input into the `explain` function to obtain explanations.
 I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
-I've been working on redoing code from earlier in this journal to work for the added binning method.
-
-There seems to be a problem with `treebink` with certain variables with high enough bins. The function returns more than the desired number of bins. Heike is going to look into this.
 
@@
 This led me to try applying LIME with a handful of input values.
-However, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation for specific starting values a handful of times.
-The next two sections consider the results from these studies.
+I also have tried running LIME with the tree based bins.
+Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
+This led me to try running each implementation a handful of times.
+I have attempted to evaulate these results by both considering the accuracy and consistency of the results.
 
@@
 
-The figures in this section are created from the implementations of LIME on the set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, kernel density estimation, and normal distribution approximation.
+The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
 Each set of input values was only run once.
@@
 The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and whether or not the bins are equally spaced or based on quantiles.
+The plot is faceted by number of bins and the type of bin.
 The points are colored by the $R^2$ value from the fit of the simple model.
@@
 The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the number of bins from the lime implementation.
+The tree based bins do the best job with predictions above 0.6 for all number of bins.
+The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
+I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
 
@@
 The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and whether the bins are equally spaced or based on quantiles.
+The points are faceted by number of bins and bin type.
 Again, the points are colored by the $R^2$ values from the simple model.
@@
 It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins, the absolute difference decreases near 1 for 3 to 6 bins.
+However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
 This is not the case with the quantile bins.
-It appears that the equally spaced bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
+It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
 
@@
 
-## Variability
-
-In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times.
+## Consistency with One Implementation
+
+```{r}
+# Selects only the top features for the cases where binning was used
+top_features <- hamby224_test_explain %>%
+  filter(bin_situation != "other") %>%
+  select(set, situation, bin_situation, nbins, case, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, desc(feature_weight_abs)) %>%
+  group_by(situation, case) %>%
+  slice(1)
+```
+
+```{r}
+# Plots the top feature for each case for each bin situation
+ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
+  geom_tile() + 
+  facet_grid(set ~ bin_situation, scales = "free") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+```
+
+```{r}
+# Plots the proportions of number of top features chosen across number of bins for a case
+# within a binning method
+top_features %>%
+  group_by(set, case, bin_situation) %>%
+  summarise(nfeatures = length(levels(factor(feature)))) %>%
+  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
+  geom_bar(position = "stack") + 
+  facet_grid(set ~ .) + 
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues")
+```
+
+## Consistency Across Implementations
+
+In order to assess how variable the LIME results are, I ran each of the 17 input situations 10 times.
 I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
@@
   nreps = 10
-  noptions = 12
+  noptions = 17
 
   # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
+  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 15),
                                                          rep(FALSE, nreps * 2)),
                                       quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                     rep(TRUE, nreps * 2)),
-                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
+                                                        rep(TRUE, nreps * 7)),
+                                      nbins = c(rep(rep(2:6, each = nreps), 3), 
                                                 rep(4, nreps * 2)),
-                                   use_density = c(rep(TRUE, nreps * 11), 
-                                                   rep(FALSE, nreps))) %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous, nbins, quantile_bins, use_density)
-
+                                      use_density = c(rep(TRUE, nreps * 16), 
+                                                      rep(FALSE, nreps)),
+                                      bin_method = c(rep("quantile_bins", nreps * 5),
+                                                      rep("equally_spaced", nreps * 5),
+                                                      rep("tree", nreps * 5),
+                                                      rep("quantile_bins", nreps * 2)))
   # Tell R to run the upcoming code in parallel
@@
   # Run lime for the sensitivity analysis
-  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
-                                                             select(-case)),
+  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
              .f = run_lime, # run_lime is one of my helper functions
@@
     select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
+
+  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(hamby224_sensitivity_inputs), 
+           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:(nreps * noptions)) %>%
+    select(case, bin_continuous:bin_method)
 
@@
 joined_results <- hamby224_lime_results %>%
-  ungroup() %>%
-  mutate(nbins = as.numeric(as.character(nbins))) %>%
-  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
-                            sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
-                                   sprintf("%.0f equally spaced bins", nbins),
-                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
-                                          "kernel density", "normal approximation")))) %>%
-  mutate(situation = fct_relevel(situation, 
-                                 "2 quantile bins", 
-                                 "3 quantile bins",
-                                 "4 quantile bins",
-                                 "5 quantile bins",
-                                 "6 quantile bins")) %>%
   select(set, situation, mse, ave_r2) %>%
@@
 
-## Heike's Suggestions
+# Heike's Suggestions
 
 * We talked about including the penalty for the number of parameters in the discussion of the paper.
-* We talked about using a tree to choose the bins.
-This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
-(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
 * Look at the AUC after binning
-
-## Results from One Implementation
-
-```{r}
-# Selects only the top features for the cases where binning was used
-top_features <- hamby224_test_explain %>%
-  filter(bin_situation != "other") %>%
-  select(set, situation, bin_situation, case, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  group_by(situation, case) %>%
-  slice(1)
-
-# Plots the top feature for each case for each bin situation
-ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
-  geom_tile() + 
-  facet_grid(set ~ bin_situation, scales = "free") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
-
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-top_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(nfeatures = length(levels(factor(feature)))) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ .) + 
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues")
-```
-
-## Assessing Variability
-
-In order to assess how variable the LIME results are, I ran each of the 12 input situations 10 times.
-I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 12
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- data.frame(bin_continuous = c(rep(TRUE, nreps * 10), 
-                                                      rep(FALSE, nreps * 2)),
-                                   quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                     rep(TRUE, nreps * 2)),
-                                   nbins = c(rep(rep(2:6, each = nreps), 2), 
-                                             rep(4, nreps * 2)),
-                                   use_density = c(rep(TRUE, nreps * 11), 
-                                                   rep(FALSE, nreps))) %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous, nbins, quantile_bins, use_density)
-
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis
-  hamby224_sensitivity_outputs <- future_pmap(.l = as.list(hamby224_sensitivity_inputs %>%
-                                                             select(-case)),
-             .f = run_lime, # run_lime is one of my helper functions
-             train = hamby173and252_train %>% select(rf_features),
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions))) %>%
-    full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
-  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
-                            sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
-                                   sprintf("%.0f equally spaced bins", nbins),
-                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
-                                          "kernel density", "normal approximation"))),
-         diff = rfscore - model_prediction) %>%
-  mutate(situation = fct_relevel(situation, 
-                                 "2 quantile bins", 
-                                 "3 quantile bins",
-                                 "4 quantile bins",
-                                 "5 quantile bins",
-                                 "6 quantile bins")) %>%
-  mutate(bin_situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE,
-                                "quantile bins",
-                                ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
-                                       "equally spaced bins", "other")))
-```
-
-```{r}
-hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
-  group_by(set, rep, situation, bin_situation) %>%
-  summarise(mse = sum((diff)^2) / length(diff))
-```
-
-The plot below shows boxplots of the 10 mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins, but all of the 10 runs resulted in much lower mses than any of the other situations.
-This still seems to support the choice of using 3 equally spaced quantile bins for both sets.
-
-```{r}
-hamby224_sensitivity_mses %>%
-  ggplot(aes(x = situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) + 
-  geom_point() + 
-  facet_grid( ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "", y = "MSE")
-```
-
-```{r}
-hamby224_consistency <- hamby224_sensitivity_results %>%
-  select(set, situation, bin_situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels))
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_point(aes(color = bin_situation)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper)) +
-  facet_grid(. ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-The bar chart below shows the proportion of different number of top features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was four.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-hamby224_sensitivity_results %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, case) %>%
-  summarise(nlevels = length(levels(factor(feature)))) %>%
-  ggplot(aes(x = situation, fill = factor(nlevels))) + 
-  geom_bar(position = "stack") +
-  facet_grid( ~ set) + 
-  theme(legend.position = "bottom", 
-        axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
-```
-
-The plot below needs some work, but it does contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_results %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 12)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_brewer(palette = "Blues") + 
-  labs(x = "cases")
-```

### 2019-01-17 code/individual_plots.R

@@ -1,114 +1,0 @@
-# Code for creating the heatmap plots using individual plots
-
-# Load libraries 
-library(plotly)
-library(ggplot2)
-library(dplyr)
-
-# Input data
-hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
-
-# Create a dataset with all combinations of lands and bullets comparisons for each set
-combinations1 <- data.frame(set = factor(1),
-                            expand.grid(land1 = factor(1:6),
-                                        land2 = factor(1:6),
-                                        bullet1 = factor(c("1", "2", "Q")),
-                                        bullet2 = factor(c("1", "2", "Q"))))
-combinations11 <- data.frame(set = factor(11),
-                             expand.grid(land1 = factor(1:6),
-                                         land2 = factor(1:6), 
-                                         bullet1 = factor(c("1", "2", "I")),
-                                         bullet2 = factor(c("1", "2", "I"))))
-combinations <- rbind(combinations1, combinations11)
-
-# Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
-                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"),
-         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"))
-
-chosen_set = 1
-
-p1 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
[…]

### 2019-01-17 code/subsample_code.R

@@ -1,31 +1,0 @@
-# Code saved for future use for the sampling data
-
-# Create the data (with a set seed)
-set.seed(20181128)
-hamby173and252_train_sub <- hamby173and252_train %>%
-  filter(samesource == FALSE) %>%
-  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-# Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-# Apply lime to the subsampled training data with the specified input options
-hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
-                                                        select(-case)),
-                                         .f = run_lime, # run_lime is one of my helper functions
-                                         train = hamby173and252_train_sub %>% select(rf_features),
-                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                         rfmodel = as_classifier(rtrees),
-                                         label = "TRUE",
-                                         nfeatures = 3,
-                                         seed = TRUE) %>%
-  mutate(training_data = factor("Subsampled"))
-
-# Separate the lime and explain function results from the subsampled data
-hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-# Join the lime results from the full and subsampled training data
-hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)

### 2019-01-19 journal/applying LIME to bullet data journal.Rmd
started working on Fleiss's kappa

@@
 library(future)
+library(irr)
 library(lime)
@@
 
-# Caret vs RandomForest
+# Computation Issues
+
+## Caret vs RandomForest
 
@@
 To do this, I used the iris data.
-The code below goes through the process of fiting the two models (`rf_model` and `caret_model`).
+The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
 Then the `lime` and `explain` functions are applied to both models.
@@
 
-# Comparing Furrr Times
+## Comparing Furrr Times
 
 The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speeed of the future package.
+Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
 I ran and timed the code below to see how much faster the code was.
@@
 
-# Subsampled Bins
+# New Binning Methods
+
+## Subsampled Bins
 
@@
 
-# Tree Based Bins
+## Tree Based Bins
 
@@
 However, there seems to be a problem with `treebink`.
-For certain variables, when a high number of bins is requessted, the function returns more than the desired number of bins.
+For certain variables, when a high number of bins is requested, the function returns more than the desired number of bins.
 Heike is going to look into this.
@@
 This led me to try running each implementation a handful of times.
-I have attempted to evaulate these results by both considering the accuracy and consistency of the results.
+I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
 
@@
 
-```{r}
-# Selects only the top features for the cases where binning was used
-top_features <- hamby224_test_explain %>%
+I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
+I would like the features chosen to not depend on the number of bins used.
+Otherwise, it will be difficult to know how many bins to use.
+Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
+The code below creates a dataset that identifies the order in which the features are chosen by lime.
+
+```{r}
+# Creates a dataset that identifies the top chosen features by lim in order of first to third
+chosen_features <- hamby224_test_explain %>%
   filter(bin_situation != "other") %>%
@@
   arrange(situation, case, desc(feature_weight_abs)) %>%
-  group_by(situation, case) %>%
-  slice(1)
-```
+  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
+  select(-feature_weight, - feature_weight_abs) %>%
+  spread(explainer, feature)
+```
+
+In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
+Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
+It calculates the degree of agreement in classification over that which would be expected by chance.
+
+Need to write how it is computed, so I can better understand it's use: https://en.wikipedia.org/wiki/Fleiss%27_kappa
+
+I computed kappa for each bin situation separately for the top three features chosen.
+These values are plotted below for each set.
+For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the nubmer of bins followed by the tree based bins.
+The values of kappa for the quantile bins are slight to fair agreement.
+For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
+
+```{r}
+# Computes and plots the values of kappa
+chosen_features %>%
+  ungroup() %>%
+  select(-situation) %>%
+  gather(key = chosen, value = feature, first:third) %>%
+  spread(nbins, feature) %>%
+  select(-case) %>%
+  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
+  group_by(set, bin_situation, chosen) %>%
+  summarise(kappa = 
+              kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), ncol = 5))$value) %>%
+  arrange(chosen, set, bin_situation) %>%
+  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
+  geom_point() + 
+  geom_line() +
+  facet_grid( ~ set) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+```
+
+I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
 
@@
 # Plots the top feature for each case for each bin situation
-ggplot(top_features, aes(x = situation, y = case, fill = feature)) + 
+ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
   geom_tile() + 
@@
   scale_fill_brewer(palette = "Blues")
-```
+
+# Plots the second feature for each case for each bin situation
+ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
+  geom_tile() + 
+  facet_grid(set ~ bin_situation, scales = "free") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+
+# Plots the third feature for each case for each bin situation
+ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
+  geom_tile() + 
+  facet_grid(set ~ bin_situation, scales = "free") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+```
+
+I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
+The plots are separated by set.
 
@@
 # within a binning method
-top_features %>%
+chosen_features %>%
   group_by(set, case, bin_situation) %>%
-  summarise(nfeatures = length(levels(factor(feature)))) %>%
+  summarise(first = length(levels(factor(first))),
+            second = length(levels(factor(second))),
+            third = length(levels(factor(third)))) %>%
+  gather(chosen, nfeatures, first:third) %>%
   ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
   geom_bar(position = "stack") + 
-  facet_grid(set ~ .) + 
+  facet_grid(set ~ chosen) + 
   theme_bw() +

### 2019-01-20 code/helper_functions.R
fix to treebink

@@ -9,42 +9,37 @@
 # Outputs: k-1 values for breakpoints (does not include minimum and maximum)
 
 library(tidyverse)
-library(rpart)
-library(partykit)
+library(tree)
 
-treebink <- function (y, x, k, minsplit = 20) {
+treebink <- function (y, x, k, minsize = 10) {
   
-  cp <- 0.01
-  tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
-  while ((nrow(tree$cptable) < k) & (cp > 1e-9)) {
-    cp <- cp/10
-    tree <- rpart::rpart(y ~ x, control = rpart.control(cp = cp, minsplit = minsplit))
+  dev <- 0.01
+  tree <- tree::tree(y ~ x, control = tree::tree.control(nobs = length(y), mindev=dev, minsize = minsize))
+  while ((length(grep("<leaf>", tree$frame$var)) < k) & (dev > 1e-9)) {
+    dev <- dev/10
+    tree <- tree::tree(y ~ x, control = tree::tree.control(nobs = length(y), mindev=dev,  minsize = minsize))
   }
-  cpdf <- data.frame(tree$cptable)
-  cpdf$ksplits <- cpdf$nsplit-(k-1)
-  idx <- which.min(abs(cpdf$ksplits))
-   
-  cp <- cpdf$CP[idx]
-  tree <-  rpart::prune(tree, cp = cp)
+  tree <- tree::prune.tree(tree, best = k)
+  breaks <- na.omit(unique(parse_number(tree$frame$splits[,1])))
+  if (length(breaks) == k-1) return(sort(breaks)) # and we're happy because we got all the values we need
   
-  ###############
-  # now we have a tree with the right number of splits
   
-  nodes <- partykit:::.list.rules.party(as.party(tree))
-  dframe <- data.frame(rule = nodes)
-  dframe$split <- strsplit(as.character(dframe$rule), " & ")
-  dframe$id <- 1:nrow(dframe)
-  
-  dframe <- dframe %>% unnest(split)
-  dframe <- dframe %>% mutate(value = readr::parse_number(split)
-                              #  lower = stringr::str_detect(split, pattern = ">=")
-  )
-  # we could now do all sorts of fancy interval output, but we just need the breaks
-  breaks <- sort(unique(dframe$value))
[…]

### 2019-01-22 journal/applying LIME to bullet data journal.Rmd
updated sensativity analyses

@@
 
+She recently updated the function `treebink` to run using the tree package. Here are some comments from her about the code:
+
+"I've moved it from rpart to tree.
+I am not quite sure that the two packages are doing the exact same thing.
+They claim they do but they might be implemented a bit differently.
+What we are doing now is if there are too many splits, we look at the order in which the splits are made and roll back some of them.
+I haven't found a case that doesn't work, but obviously that doesn't show that there isn't any :)"
+
 I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
@@
   theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
   scale_fill_brewer(palette = "Blues")
@@
 hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
-  mutate(situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE, 
+  mutate(diff = rfscore - model_prediction,
+         nbins = as.numeric(as.character(nbins)),
+         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                             sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & quantile_bins == FALSE, 
+                            ifelse(bin_continuous == TRUE & 
+                                   bin_method == "equally_spaced",
                                    sprintf("%.0f equally spaced bins", nbins),
-                                   ifelse(bin_continuous == FALSE & use_density == TRUE, 
-                                          "kernel density", "normal approximation"))),
-         diff = rfscore - model_prediction) %>%
-  mutate(situation = fct_relevel(situation, 
-                                 "2 quantile bins", 
-                                 "3 quantile bins",
-                                 "4 quantile bins",
-                                 "5 quantile bins",
-                                 "6 quantile bins")) %>%
-  mutate(bin_situation = ifelse(bin_continuous == TRUE & quantile_bins == TRUE,
+                                   ifelse(bin_continuous == TRUE & bin_method == "tree",
+                                          sprintf("%.0f tree based bins", nbins),
+                                          ifelse(bin_continuous == FALSE & 
+                                                 use_density == TRUE, "kernel density",
+                                                 "normal approximation")))) %>%
+           fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
+                       "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
+                       "3 equally spaced bins", "4 equally spaced bins",
+                       "5 equally spaced bins", "6 equally spaced bins")) %>%
+  mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
                                 "quantile bins",
-                                ifelse(bin_continuous == TRUE & quantile_bins == FALSE,
-                                       "equally spaced bins", "other")))
+                                ifelse(bin_method == "equally_spaced" & 
+                                       bin_continuous == TRUE, "equally spaced bins", 
+                                       ifelse(bin_method == "tree" & bin_continuous == TRUE,
+                                              "tree based bins", "other")))) %>%
+    mutate(bin_situation = factor(bin_situation))
 ```
@@
   geom_boxplot(aes(color = bin_situation)) + 
-  geom_point() + 
+  #geom_point() + 
   facet_grid( ~ set) + 
@@
   ggplot(aes(x = situation, y = mean_nlevels)) + 
+  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
   geom_point(aes(color = bin_situation)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper)) +
   facet_grid(. ~ set) + 
@@
   scale_fill_brewer(palette = "Blues")
+
+hamby224_sensitivity_results %>%
+  select(set, situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(2) %>%
+  ungroup() %>%
+  group_by(set, situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature)))) %>%
+  ggplot(aes(x = situation, fill = factor(nlevels))) + 
+  geom_bar(position = "stack") +
+  facet_grid( ~ set) + 
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
+
+hamby224_sensitivity_results %>%
+  select(set, situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(3) %>%
+  ungroup() %>%
+  group_by(set, situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature)))) %>%
+  ggplot(aes(x = situation, fill = factor(nlevels))) + 
+  geom_bar(position = "stack") +
+  facet_grid( ~ set) + 
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "Blues")
 ```
@@
   arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 12)) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) +
+  #facet_grid(nlevels ~ situation) +
+  theme(legend.position = "bottom",
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_brewer(palette = "Blues") + 
+  labs(x = "cases")
+
+hamby224_sensitivity_results %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(2) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) +
+  #facet_grid(nlevels ~ situation) +
+  theme(legend.position = "bottom",
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_brewer(palette = "Blues") + 
+  labs(x = "cases")
+
+hamby224_sensitivity_results %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(3) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
   ggplot(aes(x = order, fill = feature)) + 

### 2019-01-22 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
updated sensativity analyses

@@
 # Load libraries
+library(bulletr)
+library(cowplot)
+library(furrr)
+library(future)
+library(lime)
+library(purrr)
+library(randomForest)
 library(tidyverse)
-library(bulletr)
-library(randomForest)
-library(lime)
-library(cowplot)
-library(purrr)
-library(future)
-library(furrr)
+library(tree)
 

### 2019-01-24 journal/applying LIME to bullet data journal.Rmd
worked on adding rfscore tree based bins

--- 2019-01-19 journal/applying LIME to bullet data journal.Rmd
@@
 
+## Plotly Dead Space Issue
+
+I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
+
+```{r eval = FALSE}
+# Example with Plotly to show dead space in heatmap
+
+# System information
+# R version 3.5.1 (2018-07-02)
+# Platform: x86_64-apple-darwin15.6.0 (64-bit)
+# Running under: macOS  10.14
+
+# Load libraries
+# library(plotly) # version 4.8.0
+# library(ggplot2) # version 3.1.0
+# library(tidyr) # version 0.8.2
+
+# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
+
+# Create dataset
+m <- matrix(rnorm(9), nrow = 3, ncol = 3)
+
+# Create plotly heatmap - no dead space to be found
+plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
+
+# Example using ggplotly function -----------------------------------------------------
+
+# Reshape the data for ggplot
+m_gathered <- data.frame(m) %>%
+  gather(key = column) %>%
+  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
+  select(column, row, value)
+
+# Create ggplot heatmap
+p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
+  geom_tile()
+
+# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
+ggplotly(p)
+
+# Carson's suggested fix for now
+style(ggplotly(p), hoverinfo = "skip", traces = 2)
+
+# Create ggplot heatmap without a legend
+p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
+  geom_tile() +
+  theme(legend.position = "none")
+
+# Apply plotly to ggplot heatmap - the dead space is gone!
+ggplotly(p_nolegend)
+```
+
 ## Caret vs RandomForest
@@
   geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_method ~ nbins) + 
+  facet_grid(bin_situation ~ nbins) + 
   theme_bw() + 
@@
   group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, set) %>%
+           bin_method, response, set) %>%
   summarise(mse = (sum(diff^2)) / length(diff),
@@
 The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the lowest mean squared error occurs with 3 equally spaced bins.
-This seems to suggest that using 3 equally spaced bins should provide better explanations.
+In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
 
@@
 hamby224_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
   ggplot(aes(x = situation, y = mse, color = bin_situation)) +
   geom_point() + 
-  facet_grid( ~ set) + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
   theme_bw() + 
@@
         legend.position = "bottom") + 
-  labs(x = "Situation", y = "MSE", color = "")
+  labs(x = "Situation", y = "MSE", color = "") + 
+  scale_color_brewer(palette = "RdYlBu")
 ```
@@
 The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle.
+The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
 
@@
 hamby224_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
   ggplot(aes(x = situation, y = ave_r2, color = bin_situation)) +
   geom_point() + 
-  facet_grid( ~ set) + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
   theme_bw() + 
@@
         legend.position = "bottom") + 
-  labs(x = "Situation", y = "Average R2", color = "")
+  labs(x = "Situation", y = "Average R2", color = "") + 
+  scale_color_brewer(palette = "RdYlBu")
 ```
@@
   filter(bin_situation != "other") %>%
-  select(set, situation, bin_situation, nbins, case, feature, feature_weight) %>%
+  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
   mutate(feature_weight_abs = abs(feature_weight)) %>%
@@
 It calculates the degree of agreement in classification over that which would be expected by chance.
-
-Need to write how it is computed, so I can better understand it's use: https://en.wikipedia.org/wiki/Fleiss%27_kappa
+A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
 
@@
   summarise(kappa = 
-              kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), ncol = 5))$value) %>%
+              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), ncol = 5))$value) %>%
   arrange(chosen, set, bin_situation) %>%
@@
   theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_color_brewer(palette = "Paired")
 ```
@@
 
-```{r}
+```{r fig.height = 8, fig.width = 8}
 # Plots the top feature for each case for each bin situation
@@
   geom_tile() + 
-  facet_grid(set ~ bin_situation, scales = "free") + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
   theme_bw() + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
+  scale_fill_brewer(palette = "Spectral")
 
@@
   geom_tile() + 
-  facet_grid(set ~ bin_situation, scales = "free") + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") +
   theme_bw() + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
+  scale_fill_brewer(palette = "Spectral")
 
@@
   geom_tile() + 
-  facet_grid(set ~ bin_situation, scales = "free") + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") +
   theme_bw() + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
+  scale_fill_brewer(palette = "Spectral")
 ```
@@
   facet_grid(set ~ chosen) + 
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues")
+  labs(x = "Bin Situation", y = "Count", fill = "Number of Features") + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
+  scale_fill_brewer(palette = "RdYlBu")
 ```
@@
 hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
-  group_by(set, rep, situation, bin_situation) %>%
+  group_by(set, rep, situation, bin_situation, nbins) %>%
   summarise(mse = sum((diff)^2) / length(diff))
@@
 hamby224_sensitivity_mses %>%
+  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
   ggplot(aes(x = situation, y = mse)) + 
   geom_boxplot(aes(color = bin_situation)) +
-  geom_point() + 
-  facet_grid( ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "", y = "MSE")
+  facet_grid(set ~ bins, scales = "free_x") + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
+  labs(x = "Situation", y = "MSE", color = "") + 
+  scale_color_brewer(palette = "RdYlBu")
 ```
@@
 hamby224_consistency <- hamby224_sensitivity_results %>%
-  select(set, situation, bin_situation, case, rep, feature, feature_weight) %>%
+  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
   mutate(feature_weight_abs = abs(feature_weight)) %>%
   arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
+  group_by(set, situation, nbins, case, rep) %>%
   slice(1) %>%
   ungroup() %>%
-  group_by(set, situation, bin_situation, case) %>%
+  group_by(set, situation, bin_situation, nbins, case) %>%
   summarise(nlevels = length(levels(factor(feature))),
@@
   ungroup() %>%
-  group_by(set, situation, bin_situation) %>%
+  group_by(set, situation, bin_situation, nbins) %>%
   summarise(mean_nlevels = mean(nlevels),
@@
 hamby224_consistency %>%
+  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
   ggplot(aes(x = situation, y = mean_nlevels)) + 
+  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
   geom_point(aes(color = bin_situation)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper)) +
-  facet_grid(. ~ set) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  facet_grid(set ~ bins, scales = "free_x") + 
+  labs(x = "Situation", y = "Mean Number of Features", color = "") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
+  scale_color_brewer(palette = "RdYlBu")
 ```
@@
   summarise(nlevels = length(levels(factor(feature)))) %>%
-  ggplot(aes(x = situation, fill = factor(nlevels))) + 
+  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
+  ggplot(aes(x = situation, fill = nlevels)) + 
   geom_bar(position = "stack") +
@@
         axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Blues")
+  scale_fill_brewer(palette = "RdYlBu") + 
+  labs(x = "Situation", y = "Count", fill = "Number of Features")
+
+hamby224_sensitivity_results %>%
+  select(set, situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(2) %>%
+  ungroup() %>%
+  group_by(set, situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature)))) %>%
+  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
+  ggplot(aes(x = situation, fill = nlevels)) + 
+  geom_bar(position = "stack") +
+  facet_grid( ~ set) + 
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "RdYlBu") + 
+  labs(x = "Situation", y = "Count", fill = "Number of Features")
+
+hamby224_sensitivity_results %>%
+  select(set, situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(set, situation, case, rep) %>%
+  slice(3) %>%
+  ungroup() %>%
+  group_by(set, situation, case) %>%
+  summarise(nlevels = length(levels(factor(feature)))) %>%
+  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
+  ggplot(aes(x = situation, fill = nlevels)) + 
+  geom_bar(position = "stack") +
+  facet_grid( ~ set) + 
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_brewer(palette = "RdYlBu") + 
+  labs(x = "Situation", y = "Count", fill = "Number of Features")
 ```
@@
   arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 12)) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
   ggplot(aes(x = order, fill = feature)) + 
@@
         axis.ticks.y = element_blank()) + 
-  scale_fill_brewer(palette = "Blues") + 
+  scale_fill_brewer(palette = "Spectral") + 
+  labs(x = "cases")
+
+hamby224_sensitivity_results %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(2) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) +
+  #facet_grid(nlevels ~ situation) +
+  theme(legend.position = "bottom",
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_brewer(palette = "Spectral") + 
+  labs(x = "cases")
+
+hamby224_sensitivity_results %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(3) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5) +
+  #facet_grid(nlevels ~ situation) +
+  theme(legend.position = "bottom",
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_brewer(palette = "Spectral") + 
   labs(x = "cases")
@@
 
-# Heike's Suggestions
-
-* We talked about including the penalty for the number of parameters in the discussion of the paper.
+# Future Ideas to Implement
+
+* Include a penalty for the number of parameters when choosing bins
 * Look at the AUC after binning
+* Compare the simple models based on different number of bins using an F-test
+* Determine the best number of bins to use for each variable

### 2019-01-24 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on adding rfscore tree based bins

--- 2019-01-16 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, fig.pos = "center")
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
+                      fig.pos = "center")
 
 # Load libraries
+library(bulletr)
+library(cowplot)
+library(furrr)
+library(future)
+library(lime)
+library(purrr)
+library(randomForest)
 library(tidyverse)
-library(bulletr)
-library(randomForest)
-library(lime)
-library(cowplot)
-library(purrr)
-library(future)
-library(furrr)
+library(tree)
 
@@
 rf_features <- rownames(rtrees$importance)
+
+# Add the random forest score to the training set
+hamby173and252_train$rfscore = predict(rtrees, 
+                                       hamby173and252_train %>% select(rf_features), 
+                                       type = "prob")[,2]
 ```
@@
   # Specify the options to use with lime
-  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 15), rep(FALSE, 2)),
+  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), rep(FALSE, 2)),
                                quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), 
-                                                 rep(TRUE, 5), rep(TRUE, 2)),
-                               nbins = c(rep(2:6, 3), rep(4, 2)),
-                               use_density = c(rep(TRUE, 15), TRUE, FALSE),
+                                                 rep(TRUE, 10), rep(TRUE, 2)),
+                               nbins = c(rep(2:6, 4), rep(4, 2)),
+                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
                                bin_method = c(rep("quantile_bins", 5),
                                               rep("equally_spaced", 5),
-                                              rep("tree", 5),
-                                              rep("quantile_bins", 2)))
+                                              rep("tree", 10),
+                                              rep("quantile_bins", 2)),
+                               response = c(rep(NA, 10), rep("samesource", 5), 
+                                            rep("rfscore", 5), rep(NA, 2)))
 
@@
              .f = run_lime, # run_lime is one of my helper functions
-             train = hamby173and252_train %>% select(rf_features),
+             features = rf_features,
+             train = hamby173and252_train,
              test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-             response = hamby173and252_train$samesource,
              rfmodel = as_classifier(rtrees),
@@
   names(hamby224_lime) <- map_chr(1:length(hamby224_lime_inputs), function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s",
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
               hamby224_lime_inputs$bin_continuous[case],
@@
               hamby224_lime_inputs$use_density[case],
-              hamby224_lime_inputs$bin_method[case]))
+              hamby224_lime_inputs$bin_method[case],
+              hamby224_lime_inputs$response[case]))
 
@@
     mutate(case = 1:length(hamby224_lime_inputs$quantile_bins)) %>%
-    select(case, bin_continuous:bin_method)
+    select(case, bin_continuous:response)
 
@@
                                   u_d = use_density,
-                                  b_m = bin_method),
+                                  b_m = bin_method,
+                                  r_v = response),
                             .f = bin_labeller, # bin_labeller is one of my helper functions
@@
            feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    select(bin_continuous:bin_method, case:feature_desc, feature_bin:strictly_less, 
-           data, prediction)
+    mutate(nbins = as.numeric(as.character(nbins)),
+           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                              sprintf("%.0f quantile bins", nbins),
+                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                     sprintf("%.0f equally spaced bins", nbins),
+                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "samesource",
+                                            sprintf("%.0f samesource tree based bins", nbins),
+                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "rfscore",
+                                              sprintf("%.0f rfscore tree based bins", nbins),
+                                              ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                     "kernel density", "normal approximation"))))) %>%
+             fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
+                         "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
+                         "3 equally spaced bins", "4 equally spaced bins",
+                         "5 equally spaced bins", "6 equally spaced bins",
+                         "2 samesource tree based bins", "3 samesource tree based bins",
+                         "4 samesource tree based bins", "5 samesource tree based bins",
+                         "6 samesource tree based bins")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
+                                "quantile bins",
+                                ifelse(bin_method == "equally_spaced" & bin_continuous == TRUE,
+                                       "equally spaced bins", 
+                                       ifelse(bin_method == "tree" & bin_continuous == TRUE & 
+                                                response == "samesource",
+                                              "samesource tree based bins", 
+                                              ifelse(bin_method == "tree" & bin_continuous == TRUE & 
+                                                response == "rfscore",
+                                                "rfscore tree based bins", "other"))))) %>%
+    mutate(bin_situation = factor(bin_situation)) %>%
+    select(situation, bin_situation, bin_continuous:response, case:feature_desc,
+           feature_bin:strictly_less, data, prediction)
 
@@
     select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method, response) %>%
     slice(1) %>%
     ungroup() %>%
-    select(bin_continuous, quantile_bins, nbins, use_density, 
-           set, case, rf_features, rfscore, model_prediction, model_r2) %>%
+    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, response, 
+           nbins, use_density, set, case, rf_features, rfscore, model_prediction, model_r2) %>%
     mutate(diff = rfscore - model_prediction,

### 2019-01-24 code/dead_space_example.R

@@ -1,47 +1,0 @@
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-library(plotly) # version 4.8.0
-library(ggplot2) # version 3.1.0
-library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none") 
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
-
-plotly_json(p)

### 2019-01-24 code/helper_functions.R

@@ -120,7 +120,7 @@ mylime <- function(x, y, model, preprocess = NULL, bin_continuous = TRUE, n_bins
         d_range <- range(x[[i]], na.rm = TRUE)
         seq(d_range[1], d_range[2], length.out = n_bins + 1)
       } else if (bin_method == "tree"){
-        inner <- treebink(y = y, x[[i]], k = n_bins)
+        inner <- treebink(y = y[[1]], x[[i]], k = n_bins)
         min <- min(x[[i]])
         max <- max(x[[i]])
         bins <- c(min, inner, max)
@@ -160,14 +160,19 @@ mylime <- function(x, y, model, preprocess = NULL, bin_continuous = TRUE, n_bins
 # Function for running the lime functions which runs the lime and explain 
 # objects in a list
 run_lime <- function(bin_continuous, quantile_bins, nbins, use_density, bin_method,
-                     train, test, response, rfmodel, label, nfeatures, seed = TRUE){
+                     response, features, train, test, rfmodel, label, nfeatures, seed = TRUE){
   
   # Set a seed if requested
   if (seed == TRUE) set.seed(20181128)
   
   # Run my lime function
-  lime <- mylime(x = train, y = response, model = rfmodel, bin_continuous = bin_continuous, 
-                 n_bins = nbins, quantile_bins = quantile_bins, use_density = use_density,
+  lime <- mylime(x = train %>% select(features), 
+                 y = ifelse(is.na(response), NA, train %>% select(response)), 
+                 model = rfmodel, 
+                 bin_continuous = bin_continuous, 
+                 n_bins = nbins, 
+                 quantile_bins = quantile_bins,
+                 use_density = use_density,
                  bin_method = bin_method)
   
   # Run the explain function and add a variable for the number of bins
@@ -176,7 +181,8 @@ run_lime <- function(bin_continuous, quantile_bins, nbins, use_density, bin_meth
            quantile_bins = quantile_bins,
            nbins = nbins,
            use_density = use_density,
-           bin_method = bin_method)
+           bin_method = bin_method,
+           response = response)
   
   return(list(lime = lime, explain = explain))
   
@@ -265,7 +271,7 @@ create_bin_data <- function(lime_object){
 ## ---------------------------------------------------------------
 
 # Function to use for creating bin labels in the test_explain dataset
-bin_labeller <- function(feature, feature_value, b_c, q_b, n_b, u_d, b_m, bin_data, case_info){
[…]

### 2019-01-25 journal/applying LIME to bullet data journal.Rmd
worked on cleaning up code after rfscore has been added

@@
 I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I have been trying to decide which input values to use for LIME in the forensic examiners' paper, and I have decided that I would like to simplify matters even more by only focusing on a few input options.
-I have considered a handful of ways of answering this question (accuracy within one implementation of lime, accuracy across 10 implementations of lime, etc.), but I would like to reserve some of these ways for a future more technical paper.
-However, I would like a place to store my work to use for future purposes, and it would be nice to have a place to work where I do not feel the need to optimize code.
+I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
 I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the paper.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the paper, but now I am going to transfer a lot of that code to this journal.
-Many of the sections below include work that I did earlier this semester.
-I am just transferring them here now.
+Then I can clean up and organize the code when I write the papers.
+
+Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
+I am transferring them here now.
 Later I will move the necessary parts to the paper.
@@
 library(future)
+library(gretchenalbrecht)
 library(irr)
@@
 
-```{r}
+```{r fig.height = 10}
+# Plot of fequency for each bin division for 2 quantile bins
 hamby224_test_explain %>%
-  filter(nbins == "2", quantile_bins == TRUE) %>%
+  filter(situation == "2 quantile") %>%
   ggplot(aes(x = feature_desc)) +
@@
 ```{r}
+# Heatmap of rfscore for each comparison in set 1
 hamby224_test %>%
@@
 
-I also wrote some code to create the above plot using individual plots instead of facets. This is included below (but not executed).
-
-```{r eval = FALSE}
+I also wrote some code to create the above plot using individual plots instead of facets. This is included below. (It is a bit outdated compared to my newer version of the plot.)
+
+```{r}
 # Code for creating the heatmap plots using individual plots
-
-# Input data
-hamby224_test_explain <- readRDS("./data/hamby224_test_explain.rds")
-
-# Create a dataset with all combinations of lands and bullets comparisons for each set
-combinations1 <- data.frame(set = factor(1),
-                            expand.grid(land1 = factor(1:6),
-                                        land2 = factor(1:6),
-                                        bullet1 = factor(c("1", "2", "Q")),
-                                        bullet2 = factor(c("1", "2", "Q"))))
-combinations11 <- data.frame(set = factor(11),
-                             expand.grid(land1 = factor(1:6),
-                                         land2 = factor(1:6), 
-                                         bullet1 = factor(c("1", "2", "I")),
-                                         bullet2 = factor(c("1", "2", "I"))))
-combinations <- rbind(combinations1, combinations11)
-
-# Join the combinations and the data so that all combinations have a row in the data
-hamby224_test_explain_NAs <- left_join(combinations, hamby224_test_explain,
-                                       by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  mutate(bullet1 = forcats::fct_recode(bullet1, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"),
-         bullet2 = forcats::fct_recode(bullet2, "Known 1" = "1", "Known 2" = "2", 
-                                       "Questioned" = "Q", "Questioned" = "I"))
-
-chosen_set = 1
-
-p1 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 1") %>%
+p1 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 1") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
   geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet1 ~ bullet2, scales = "free") +
   theme_minimal() +
@@
 
-p2 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Known 2") %>%
+p2 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 2") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
 
-p3 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 1", bullet2 == "Questioned") %>%
+p3 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Questioned") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
   geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet1 ~ bullet2, scales = "free") +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
   theme_minimal() +
@@
 
-p5 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Known 2") %>%
+p5 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Known 2") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
 
-p6 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Known 2", bullet2 == "Questioned") %>%
+p6 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Questioned") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
 
-p9 <- hamby224_test_explain_NAs %>%
-  filter(set == chosen_set, bullet1 == "Questioned", bullet2 == "Questioned") %>%
+p9 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Questioned", bullet2 == "Questioned") %>%
   select(case, bullet1, bullet2, land1, land2, rfscore) %>%
@@
 
-style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows = 3, titleX = TRUE, titleY = TRUE, margin = 0.03),
+style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, 
+              nrows = 3, 
+              titleX = TRUE, 
+              titleY = TRUE, 
+              margin = 0.03),
       hoverinfo = "skip",
@@
 
-```{r echo = TRUE}
+```{r}
+# Example using treebink
 treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
@@
 
-```{r}
+```{r fig.height = 8, fig.width = 10}
+# Plot of simple model versus complex model predictions
 hamby224_lime_comparisons %>%
@@
   stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
+       color = "Simple Model R2")
 ```
@@
 
-```{r}
+```{r fig.height = 8, fig.width = 10}
+# Plot of difference in predictions versus rfscore
 hamby224_lime_comparisons %>%
@@
   theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(x = "Complex Model Prediction (RF Score)", 
+       y = "Difference Between Complex and Simple Model Predictions",
+       color = "Simple Model R2")
 ```
@@
 ```{r}
+# Plots of model "residuals"
 hamby224_lime_comparisons %>%
@@
   facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue")
+  geom_hline(yintercept = 0, color = "blue") + 
+  labs(x = "Feature Value", y = "Residual")
 ```
@@
 ```{r}
+# Summarizing lime results
 hamby224_lime_results <- hamby224_lime_comparisons %>%
@@
 ```{r}
+# Plot of MSEs
 hamby224_lime_results %>%
   mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = situation, y = mse, color = bin_situation)) +
+  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
   geom_point() + 
@@
         legend.position = "bottom") + 
-  labs(x = "Situation", y = "MSE", color = "") + 
-  scale_color_brewer(palette = "RdYlBu")
+  labs(x = "Bin Type", y = "MSE", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
 ```
@@
 ```{r}
+# Plot of R^2s
 hamby224_lime_results %>%
   mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = situation, y = ave_r2, color = bin_situation)) +
+  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
   geom_point() + 
@@
         legend.position = "bottom") + 
-  labs(x = "Situation", y = "Average R2", color = "") + 
-  scale_color_brewer(palette = "RdYlBu")
+  labs(x = "Bin Type", y = "Average R2", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
 ```
@@
 ```{r}
-# Creates a dataset that identifies the top chosen features by lim in order of first to third
+# Creates a dataset that creates columns of the chosen features by lime from first to third
 chosen_features <- hamby224_test_explain %>%
-  filter(bin_situation != "other") %>%
+  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
+  filter(!is.na(rfscore)) %>%
   select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
@@
   mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, - feature_weight_abs) %>%
+  select(-feature_weight, -feature_weight_abs) %>%
   spread(explainer, feature)
@@
   summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), ncol = 5))$value) %>%
+              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
+                                        ncol = 5))$value) %>%
   arrange(chosen, set, bin_situation) %>%
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_brewer(palette = "Paired")
+  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
+  labs(x = "Bin Type", y = "Kappa", color = "Feature")
 ```
@@
   theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Spectral")
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "Case", fill = "Feature")
 
@@
   theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "Spectral")
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "Case", fill = "Feature")
 ```
@@
   facet_grid(set ~ chosen) + 
-  labs(x = "Bin Situation", y = "Count", fill = "Number of Features") + 
+  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
   theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_brewer(palette = "RdYlBu")
+  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
 ```
@@
 
-In order to assess how variable the LIME results are, I ran each of the 17 input situations 10 times.
-I wanted to look at the variability of the mse for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
+In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
+I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
 
@@
   nreps = 10
-  noptions = 17
+  noptions = 22
 
   # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 15),
+  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
                                                          rep(FALSE, nreps * 2)),
                                       quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 7)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 3), 
+                                                        rep(TRUE, nreps * 12)),
+                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
                                                 rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 16), 
+                                      use_density = c(rep(TRUE, nreps * 21), 
                                                       rep(FALSE, nreps)),
@@
                                                       rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 5),
-                                                      rep("quantile_bins", nreps * 2)))
+                                                      rep("tree", nreps * 10),
+                                                      rep("quantile_bins", nreps * 2)),
+                                      response = c(rep(NA, nreps * 10),
+                                                   rep("samesource", nreps * 5),
+                                                   rep("rfscore", nreps * 5),
+                                                   rep(NA, nreps * 2)))
   # Tell R to run the upcoming code in parallel
@@
 
-  # Run lime for the sensitivity analysis
+  # Run lime for the sensitivity analysis and organize the output
   hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
              .f = run_lime, # run_lime is one of my helper functions
-             train = hamby173and252_train %>% select(rf_features),
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             features = rf_features,
+             train = hamby173and252_train,
+             test = hamby224_test %>% 
+               arrange(case) %>% 
+               select(rf_features) %>% 
+               na.omit(),
              response = hamby173and252_train$samesource,
@@
     mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource)
-
+    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource) %>%
+    mutate(diff = rfscore - model_prediction,
+         nbins = as.numeric(as.character(nbins)),
+         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                            sprintf("%.0f quantile", nbins),
+                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                   sprintf("%.0f equally spaced", nbins),
+                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                            response == "samesource",
+                                          sprintf("%.0f samesource tree", nbins),
+                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                            response == "rfscore",
+                                            sprintf("%.0f rfscore tree", nbins),
+                                            ifelse(bin_continuous == FALSE & 
+                                                   use_density == TRUE, 
+                                                   "kernel density", 
+                                                   "normal approximation"))))) %>%
+           fct_relevel("2 quantile", "3 quantile", "4 quantile",
+                       "5 quantile", "6 quantile", "2 equally spaced",
+                       "3 equally spaced", "4 equally spaced",
+                       "5 equally spaced", "6 equally spaced",
+                       "2 samesource tree", "3 samesource tree",
+                       "4 samesource tree", "5 samesource tree",
+                       "6 samesource tree")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
+                                  bin_continuous == TRUE,
+                                  "quantile",
+                                  ifelse(bin_method == "equally_spaced" & 
+                                         bin_continuous == TRUE,
+                                         "equally spaced", 
+                                         ifelse(bin_method == "tree" & 
+                                                bin_continuous == TRUE & 
+                                                response == "samesource",
+                                                "samesource tree", 
+                                                ifelse(bin_method == "tree" & 
+                                                       bin_continuous == TRUE & 
+                                                       response == "rfscore",
+                                                       "rfscore tree", 
+                                                       ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                       "kernel density", 
+                                                       "normal approximation")))))) %>%
+    mutate(bin_situation = factor(bin_situation))
+
+  # Turn the input options into a dataframe to be saved
   hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
@@
 
-```{r}
+```{r eval = FALSE}
+# Code for organizing the sensitivity analysis results
 hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
-  mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile bins", nbins),
-                            ifelse(bin_continuous == TRUE & 
-                                   bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced bins", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree",
-                                          sprintf("%.0f tree based bins", nbins),
-                                          ifelse(bin_continuous == FALSE & 
-                                                 use_density == TRUE, "kernel density",
-                                                 "normal approximation")))) %>%
-           fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
-                       "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
-                       "3 equally spaced bins", "4 equally spaced bins",
-                       "5 equally spaced bins", "6 equally spaced bins")) %>%
-  mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
-                                "quantile bins",
-                                ifelse(bin_method == "equally_spaced" & 
-                                       bin_continuous == TRUE, "equally spaced bins", 
-                                       ifelse(bin_method == "tree" & bin_continuous == TRUE,
-                                              "tree based bins", "other")))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-hamby224_sensitivity_mses <- hamby224_sensitivity_results %>%
   group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff))
+  summarise(mse = sum((diff)^2) / length(diff),
+            ave_r2 = mean(model_r2))
 ```
@@
 
-```{r}
+```{r eval = FALSE}
+# Plots the MSEs from the sensativity analysis
 hamby224_sensitivity_mses %>%
@@
 
-```{r}
+```{r eval = FALSE}
+# Plots the average R^2 value from the sensativity analysis 
+hamby224_sensitivity_mses %>%
+  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
+  ggplot(aes(x = situation, y = ave_r2)) + 
+  geom_boxplot(aes(color = bin_situation)) +
+  facet_grid(set ~ bins, scales = "free_x") + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
+  labs(x = "Situation", y = "MSE", color = "") + 
+  scale_color_brewer(palette = "RdYlBu")
+```
+
+```{r eval = FALSE}
 hamby224_consistency <- hamby224_sensitivity_results %>%
@@
 
-```{r}
+```{r eval = FALSE}
 hamby224_consistency %>%
@@
 
-```{r}
+```{r eval = FALSE}
 hamby224_sensitivity_results %>%
@@
 
-```{r fig.height = 8, fig.width = 10}
+```{r fig.height = 8, fig.width = 10, eval = FALSE}
 hamby224_sensitivity_results %>%
@@
 
-```{r}
+```{r eval = FALSE}
 hamby224_test %>% 
@@
 
-```{r}
+```{r eval = FALSE}
 joined_results <- hamby224_lime_results %>%
@@
 
-```{r}
+```{r eval = FALSE}
 joined_results %>%

### 2019-01-25 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on cleaning up code after rfscore has been added

@@
 
-  # Specify the options to use with lime
-  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), rep(FALSE, 2)),
-                               quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), 
-                                                 rep(TRUE, 10), rep(TRUE, 2)),
-                               nbins = c(rep(2:6, 4), rep(4, 2)),
+  # Specify the input options to use with lime
+  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
+                                                  rep(FALSE, 2)),
+                               quantile_bins = c(rep(TRUE, 5), 
+                                                 rep(FALSE, 5), 
+                                                 rep(TRUE, 12)),
+                               nbins = c(rep(2:6, 4), 
+                                         rep(4, 2)),
                                use_density = c(rep(TRUE, 20), TRUE, FALSE),
@@
                                               rep("quantile_bins", 2)),
-                               response = c(rep(NA, 10), rep("samesource", 5), 
-                                            rep("rfscore", 5), rep(NA, 2)))
+                               response = c(rep(NA, 10), 
+                                            rep("samesource", 5), 
+                                            rep("rfscore", 5), 
+                                            rep(NA, 2)))
 
@@
              train = hamby173and252_train,
-             test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
+             test = hamby224_test %>% 
+               arrange(case) %>% 
+               select(rf_features) %>% 
+               na.omit(),
              rfmodel = as_classifier(rtrees),
@@
   names(hamby224_lime) <- map_chr(1:length(hamby224_lime_inputs), function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, 
+              use_density = %s, bin_method = %s, response = %s",
               hamby224_lime_inputs$bin_continuous[case],
@@
 
+  # Turn the lime input options into a dataframe before saving it
   hamby224_lime_inputs <- hamby224_lime_inputs %>%
@@
            situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                              sprintf("%.0f quantile bins", nbins),
+                              sprintf("%.0f quantile", nbins),
                               ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                     sprintf("%.0f equally spaced bins", nbins),
+                                     sprintf("%.0f equally spaced", nbins),
                                      ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                               response == "samesource",
-                                            sprintf("%.0f samesource tree based bins", nbins),
+                                            sprintf("%.0f samesource tree", nbins),
                                             ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                               response == "rfscore",
-                                              sprintf("%.0f rfscore tree based bins", nbins),
+                                              sprintf("%.0f rfscore tree", nbins),
                                               ifelse(bin_continuous == FALSE & 
                                                      use_density == TRUE, 
-                                                     "kernel density", "normal approximation"))))) %>%
-             fct_relevel("2 quantile bins", "3 quantile bins", "4 quantile bins",
-                         "5 quantile bins", "6 quantile bins", "2 equally spaced bins",
-                         "3 equally spaced bins", "4 equally spaced bins",
-                         "5 equally spaced bins", "6 equally spaced bins",
-                         "2 samesource tree based bins", "3 samesource tree based bins",
-                         "4 samesource tree based bins", "5 samesource tree based bins",
-                         "6 samesource tree based bins")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & bin_continuous == TRUE,
-                                "quantile bins",
-                                ifelse(bin_method == "equally_spaced" & bin_continuous == TRUE,
-                                       "equally spaced bins", 
-                                       ifelse(bin_method == "tree" & bin_continuous == TRUE & 
+                                                     "kernel density", 
+                                                     "normal approximation"))))) %>%
+             fct_relevel("2 quantile", "3 quantile", "4 quantile",
+                         "5 quantile", "6 quantile", "2 equally spaced",
+                         "3 equally spaced", "4 equally spaced",
+                         "5 equally spaced", "6 equally spaced",
+                         "2 samesource tree", "3 samesource tree",
+                         "4 samesource tree", "5 samesource tree",
+                         "6 samesource tree")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
+                                  bin_continuous == TRUE,
+                                  "quantile",
+                                  ifelse(bin_method == "equally_spaced" & 
+                                         bin_continuous == TRUE,
+                                         "equally spaced", 
+                                         ifelse(bin_method == "tree" & 
+                                                bin_continuous == TRUE & 
                                                 response == "samesource",
-                                              "samesource tree based bins", 
-                                              ifelse(bin_method == "tree" & bin_continuous == TRUE & 
+                                                "samesource tree", 
+                                                ifelse(bin_method == "tree" & 
+                                                       bin_continuous == TRUE & 
                                                        response == "rfscore",
-                                                "rfscore tree based bins", "other"))))) %>%
+                                                       "rfscore tree", 
+                                                       ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                       "kernel density", 
+                                                       "normal approximation")))))) %>%
     mutate(bin_situation = factor(bin_situation)) %>%

### 2019-01-25 code/helper_functions.R

@@ -13,12 +13,20 @@ library(tree)
 
 treebink <- function (y, x, k, minsize = 10) {
   
+  # Set the mindev: "The within-node deviance must be at least this times 
+  # that of the root node for the node to be split." 0.01 is the default
+  # value in the tree package.
   dev <- 0.01
-  tree <- tree::tree(y ~ x, control = tree::tree.control(nobs = length(y), mindev=dev, minsize = minsize))
+  
+  # Fit a tree with starting specifications
+  tree <- tree::tree(y ~ x, control = tree::tree.control(nobs = length(y), 
+                                                         mindev = dev, 
+                                                         minsize = minsize))
   while ((length(grep("<leaf>", tree$frame$var)) < k) & (dev > 1e-9)) {
     dev <- dev/10
     tree <- tree::tree(y ~ x, control = tree::tree.control(nobs = length(y), mindev=dev,  minsize = minsize))
   }
+  
   tree <- tree::prune.tree(tree, best = k)
   breaks <- na.omit(unique(parse_number(tree$frame$splits[,1])))
   if (length(breaks) == k-1) return(sort(breaks)) # and we're happy because we got all the values we need
@@ -39,7 +47,6 @@ treebink <- function (y, x, k, minsize = 10) {
   breaks
   
 }
-
 
 # Examples:
 # treebink(car.test.frame$Mileage, car.test.frame$Weight, k = 5)

### 2019-01-30 journal/applying LIME to bullet data journal.Rmd
added rfscore datasets and drafted an abstract for JSM

@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature")
+  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature")
+  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature")
+  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
 ```
@@
                na.omit(),
-             response = hamby173and252_train$samesource,
              rfmodel = as_classifier(rtrees),
@@
     mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions))) %>%
+                            noptions)))
+
+  # Turn the input options into a dataframe to be saved
+  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(hamby224_sensitivity_inputs), 
+           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:(nreps * noptions)) %>%
+    select(case, bin_continuous:bin_method)
+
+  # Save the sensitivity inputs and outputs
+  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+
+}
+```
+
+```{r eval = FALSE}
+hamby224_sensitivity <- hamby224_sensitivity_outputs %>%
   full_join(hamby224_test %>% na.omit() %>% 
@@
 
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r eval = FALSE}
 # Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_outputs %>%
+hamby224_sensitivity_results <- hamby224_sensitivity %>%
   group_by(set, rep, situation, bin_situation, nbins) %>%
@@
 # Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_mses %>%
+hamby224_sensitivity_results %>%
   mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%

### 2019-01-30 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
added rfscore datasets and drafted an abstract for JSM

@@
 # Add the random forest score to the training set
-hamby173and252_train$rfscore = predict(rtrees, 
-                                       hamby173and252_train %>% select(rf_features), 
-                                       type = "prob")[,2]
+# hamby173and252_train$rfscore = predict(rtrees,
+#                                        hamby173and252_train %>% select(rf_features),
+#                                        type = "prob")[,2]
+# 
+# Save the adjusted training data
+# write.csv(hamby173and252_train %>% select(-X), "../data/hamby173and252_train.csv",
+#           row.names = FALSE)
 ```

### 2019-01-30 presentations/jsm/jsm abstract.Rmd
added rfscore datasets and drafted an abstract for JSM

---
title: "JSM Abstract"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

### To submit a session abstract, you will need the following:

#### Session Type (Contributed, Topic-Contributed*, Roundtable)

Contributed

#### Session Subtype (Paper, Speed, Poster, A.M. or P.M. Roundtable)

Paper, speed, or poster (*Which should I list as the perferred session?*)

#### Primary Sponsor (ASA Committee, ASA Section, JSM Sponsoring Society). A pull-down screen with a pre-approved list is provided.

(*I am not sure what to list for this?*)

#### Abstract Title

An Assessment of LIME Input Options when Interpreting Random Forest Predictions for Bullet Matching Data
(*This seems too long and wordy...*)

#### Abstract Text (1200 character limit)

Random forests are known for their accurate predictive abilities, but they are a part of the family of machine learning models that lack interpretability. Recently, a technique called LIME was developed to provide local interpretations for predictive models. The technique fits a linear regression model to perturbations created from the observed data in a localized region around a prediction of interest and the predicted values associated with the perturbations computed using the complex model. The coefficents from the linear model are used to determine the influential variables. We apply LIME to a random forest fit to a bullet matching dataset using the lime package currently available in R. The LIME algorithm requires several input options that affect the way that the perturbations are created and how the model is interpreted. We assess the current options avaiable in the package and propose some new methods.

(*What are your thoughts aobut this? Is the focus of this abstract apporpriate for the talk?*)

#### Abstract Keywords

Key Words: random forest, LIME, interpretability

(*Are these okay?*)

#### Presenting author and co-author contact information. Please note, there can only be one presenting author. Accurate and unique email addresses are required for all authors.

Presenting author: Katherine Goode <kgoode@iastate.edu>

Co-author: Heike Hoffman <hofmann@iastate.edu>

#### Note:

- If the abstract can be considered for alternate session subtypes. The program committee will not have space for all paper abstracts received. Acceptance is more likely if the presentation can be made in different session formats.
- Information on abstract submission from: http://ww2.amstat.org/meetings/jsm/2019/submissions.cfm

### 2019-01-30 presentations/jsm/jsm abstract.Rmd
removed extra files and spelling check

@@
 The technique fits a linear regression model to perturbations created from the observed data in a localized region around a prediction of interest and the predicted values associated with the perturbations computed using the complex model.
-The coefficents from the linear model are used to determine the influential variables.
+The coefficients from the linear model are used to determine the influential variables.
 We apply LIME to a random forest fit to a bullet matching dataset using the lime package currently available in R.
 The LIME algorithm requires several input options that affect the way that the perturbations are created and how the model is interpreted.
-We assess the current options avaiable in the package and propose some new methods.
+We assess the current options available in the package and propose some new methods.
 

### 2019-01-30 presentations/jsm/jsm abstract.Rmd
quick update

@@
 
-An Assessment of LIME Input Options when Interpreting Random Forest Predictions for Bullet Matching Data
+An Assessment of the Application of LIME to Interpret Random Forest Predictions from Bullet Matching Data
+
 (*This seems too long and wordy...*)
@@
 The coefficients from the linear model are used to determine the influential variables.
-We apply LIME to a random forest fit to a bullet matching dataset using the lime package currently available in R.
+We apply LIME to a random forest fit to a forensics bullet matching dataset using the lime package currently available in R.
 The LIME algorithm requires several input options that affect the way that the perturbations are created and how the model is interpreted.
@@
 
-(*What are your thoughts aobut this? Is the focus of this abstract apporpriate for the talk?*)
+(*What are your thoughts about this? Is the focus of this abstract apporpriate for the talk?*)
 
@@
 
-Key Words: random forest, LIME, interpretability
+random forest, LIME, interpretability
 

### 2019-01-30 journal/applying LIME to bullet data journal.Rmd
finished updating code with rfscore based bins (finally!)

@@
 These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the nubmer of bins followed by the tree based bins.
+For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
 The values of kappa for the quantile bins are slight to fair agreement.
@@
 
-```{r eval = FALSE}
-hamby224_sensitivity <- hamby224_sensitivity_outputs %>%
+```{r}
+# Join the sensativity outputs with the test data
+hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
   full_join(hamby224_test %>% na.omit() %>% 
@@
     mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource) %>%
+    select(case, model_r2:feature_weight, bin_continuous:rep, 
+           set:land2, rfscore, samesource) %>%
     mutate(diff = rfscore - model_prediction,
@@
     mutate(bin_situation = factor(bin_situation))
-
+```
+
+```{r}
 # Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity %>%
+hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
   group_by(set, rep, situation, bin_situation, nbins) %>%
@@
 
-The plot below shows boxplots of the 10 mean squared errors computed for each of the input situations for each set.
+The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
 There does not appear to be much variation for most of the cases.
 The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins, but all of the 10 runs resulted in much lower mses than any of the other situations.
-This still seems to support the choice of using 3 equally spaced quantile bins for both sets.
-
-```{r eval = FALSE}
+There is moderate variability for 3 equally spaced bins.
+The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
+
+```{r}
 # Plots the MSEs from the sensativity analysis
 hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
-  ggplot(aes(x = situation, y = mse)) + 
+  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
+                       "other", as.character(nbins))) %>%
+  ggplot(aes(x = bin_situation, y = mse)) + 
   geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x") + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
   theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Situation", y = "MSE", color = "") + 
-  scale_color_brewer(palette = "RdYlBu")
-```
-
-```{r eval = FALSE}
+  labs(x = "Bin Type", y = "MSE", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
+There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
+
+```{r}
 # Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_mses %>%
-  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
-  ggplot(aes(x = situation, y = ave_r2)) + 
+hamby224_sensitivity_results %>%
+  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
+                       "other", as.character(nbins))) %>%
+  ggplot(aes(x = bin_situation, y = ave_r2)) + 
   geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x") + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
   theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Situation", y = "MSE", color = "") + 
-  scale_color_brewer(palette = "RdYlBu")
-```
-
-```{r eval = FALSE}
-hamby224_consistency <- hamby224_sensitivity_results %>%
+  labs(x = "Bin Type", y = "MSE", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
+I then computed the average number of different top features chosen by LIME within a input situations for each set.
+The plot below contains these values shown as the dots.
+The error bars represent one standard deviation above and below the mean.
+Note that the number of levels cannot go below 1, but the error bars go below 1.
+I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
+
+There are a handful of situations with a mean near one and very little variation.
+However, the largest mean is around 2, which is not very high.
+This seems to suggest that LIME is relatively consistent across runs.
+
+```{r}
+# Determine and plot the average and variability of the number levels for each case 
+# and input option
+hamby224_consistency <- hamby224_sensitivity_joined %>%
   select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
@@
             max = max(nlevels),
-            min = min(nlevels))
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r eval = FALSE}
+            min = min(nlevels)) %>%
+  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
+                       "other", as.character(nbins)))
+
 hamby224_consistency %>%
-  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
   ggplot(aes(x = situation, y = mean_nlevels)) + 
@@
   geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x") + 
-  labs(x = "Situation", y = "Mean Number of Features", color = "") +
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
+  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
   theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_brewer(palette = "RdYlBu")
-```
-
-The bar chart below shows the proportion of different number of top features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was four.
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
+This shows that the most different features chosen was seven.
 However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
 
-```{r eval = FALSE}
-hamby224_sensitivity_results %>%
+```{r}
+# Determine the order that the features are chosen within a case and 
+# set of input options
+sensitivity_chosen <- hamby224_sensitivity_joined %>%
   select(set, situation, case, rep, feature, feature_weight) %>%
@@
   arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
+  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
+  select(-feature_weight, -feature_weight_abs) %>%
+  spread(explainer, feature)
+```
+
+```{r}
+# Determine and plot the number of features chosen across the 10 reps within 
+# a set, input options, and feature level
+sensitivity_chosen %>%
   group_by(set, situation, case) %>%
-  summarise(nlevels = length(levels(factor(feature)))) %>%
-  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
-  ggplot(aes(x = situation, fill = nlevels)) + 
+  summarise(first = length(levels(factor(first))),
+            second = length(levels(factor(second))),
+            third = length(levels(factor(third)))) %>%
+  gather(chosen, nfeatures, first:third) %>%
+  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
   geom_bar(position = "stack") + 
-  facet_grid( ~ set) + 
-  theme(legend.position = "bottom", 
-        axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "RdYlBu") + 
-  labs(x = "Situation", y = "Count", fill = "Number of Features")
-
-hamby224_sensitivity_results %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(set, situation, case) %>%
-  summarise(nlevels = length(levels(factor(feature)))) %>%
-  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
-  ggplot(aes(x = situation, fill = nlevels)) + 
-  geom_bar(position = "stack") +
-  facet_grid( ~ set) + 
-  theme(legend.position = "bottom", 
-        axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "RdYlBu") + 
-  labs(x = "Situation", y = "Count", fill = "Number of Features")
-
-hamby224_sensitivity_results %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(set, situation, case) %>%
-  summarise(nlevels = length(levels(factor(feature)))) %>%
-  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
-  ggplot(aes(x = situation, fill = nlevels)) + 
-  geom_bar(position = "stack") +
-  facet_grid( ~ set) + 
-  theme(legend.position = "bottom", 
-        axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_fill_brewer(palette = "RdYlBu") + 
-  labs(x = "Situation", y = "Count", fill = "Number of Features")
-```
-
-The plot below needs some work, but it does contain some interesting information.
+  facet_grid(set ~ chosen) + 
+  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
+  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
+```
+
+The plots below need some work, but they contain some interesting information.
 Right now, I am only concentrating on set 1.
@@
 
-```{r fig.height = 8, fig.width = 10, eval = FALSE}
-hamby224_sensitivity_results %>%
+```{r fig.height = 8, fig.width = 10}
+hamby224_sensitivity_joined %>%
   filter(set == "Set 1") %>%
@@
   arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
+  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
   ggplot(aes(x = order, fill = feature)) + 
@@
         axis.ticks.y = element_blank()) + 
-  scale_fill_brewer(palette = "Spectral") + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
   labs(x = "cases")
 
-hamby224_sensitivity_results %>%
+hamby224_sensitivity_joined %>%
   filter(set == "Set 1") %>%
@@
         axis.ticks.y = element_blank()) + 
-  scale_fill_brewer(palette = "Spectral") + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
   labs(x = "cases")
@@
 
-```{r eval = FALSE}
+```{r}
 hamby224_test %>% 
@@
   theme(legend.position = "bottom")
-
 ```
@@
 
-```{r eval = FALSE}
+```{r}
 joined_results <- hamby224_lime_results %>%
   select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_mses %>%
+  full_join(hamby224_sensitivity_results %>%
               group_by(set, situation) %>%
@@
 
-```{r eval = FALSE}
+```{r}
 joined_results %>%
@@
 ```
-
-# Future Ideas to Implement
-
-* Include a penalty for the number of parameters when choosing bins
-* Look at the AUC after binning
-* Compare the simple models based on different number of bins using an F-test
-* Determine the best number of bins to use for each variable

### 2019-01-31 presentations/jsm/jsm abstract.Rmd
updated jsm abstract and info

@@
 
-Paper, speed, or poster (*Which should I list as the perferred session?*)
+Paper
 
@@
 
-(*I am not sure what to list for this?*)
+- the section on statistical learning and data science 
+- maybe the section on statistical computing
 
@@
 
-(*This seems too long and wordy...*)
-
 #### Abstract Text (1200 character limit)
@@
 Recently, a technique called LIME was developed to provide local interpretations for predictive models.
-The technique fits a linear regression model to perturbations created from the observed data in a localized region around a prediction of interest and the predicted values associated with the perturbations computed using the complex model.
+The technique fits a linear regression model to perturbations created from the observed data in a localized region around a prediction of interest.
+The predicted values associated with the perturbations computed using the complex model are used as the response variable in the regression.
 The coefficients from the linear model are used to determine the influential variables.
@@
 The LIME algorithm requires several input options that affect the way that the perturbations are created and how the model is interpreted.
-We assess the current options available in the package and propose some new methods.
-
-(*What are your thoughts about this? Is the focus of this abstract apporpriate for the talk?*)
+We assess the current options available in the package and propose some improvements.
 
@@
 
-random forest, LIME, interpretability
-
-(*Are these okay?*)
+random forest, LIME, black box model, interpretability
 
@@
 
-Co-author: Heike Hoffman <hofmann@iastate.edu>
+Co-author: Heike Hofmann <hofmann@iastate.edu>
 
@@
 - Information on abstract submission from: http://ww2.amstat.org/meetings/jsm/2019/submissions.cfm
+
+#### Abstract Info
+
+password to edit abstract: limebullet
+
+abstract number: 304552
+
+#### Revisions
+
+You may revise your abstract text, title, and keywords or add coauthors from December 3, 2018, through February 4, 2019, and April 1 through April 18, 2019.
+
+#### Proof of Progress
+
+All presenters must send proof of a paper in progress to the appropriate JSM session chair by May 17, 2019.
+Proof of a paper in progress can be a draft manuscript, detailed outline, PowerPoint slides, etc.
+If you do not send the required proof, your paper may be deleted from the program and become ineligible for publication in the JSM Proceedings.
+This requirement applies to all contributed and topic-contributed speakers and invited sessions with discussants.

### 2019-02-05 journal/applying LIME to bullet data journal.Rmd
changes during meeting

@@
 # Plots the top feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
+p <- ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
   geom_tile() + 
@@
 sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
+  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
   mutate(feature_weight_abs = abs(feature_weight)) %>%
@@
 
-```{r}
+```{r fig.width = 10}
 # Determine and plot the number of features chosen across the 10 reps within 
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
+  scale_fill_gretchenalbrecht(palette = "flood_tide", discrete = TRUE, reverse = FALSE)
+```
+
+I computed Fleiss's kappa for each sampling technique within a set across the 10 reps.
+These values are plotted below.
+Right now, the quantile methods and rfscore tree based bins seem to be the most consistent.
+However, I am not happy with some of the kappa values for cases where the next set of plots would suggest a high kappa, but the value is very low.
+I wonder if this a flaw in the Fleiss's kappa and would suggest that I use a different metric.
+
+```{r fig.width = 10}
+sensitivity_chosen %>%
+  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
+                       "other", 
+                       nbins)) %>%
+  gather(key = chosen, value = feature, first:third) %>%
+  spread(rep, feature) %>%
+  rename(rep1 = "1", rep2 = "2", rep3 = "3", rep4 = "4", rep5 = "5", 
+         rep6 = "6", rep7 = "7", rep8 = "8", rep9 = "9", rep10 = "10") %>%
+  group_by(set, situation, bin_situation, bins, chosen) %>%
+  summarise(kappa = 
+              irr::kappam.fleiss(matrix(c(rep1, rep2, rep3, rep4, rep5,
+                                          rep6, rep7, rep8, rep9, rep10), 
+                                        ncol = 10))$value,
+            nunique = length(unique(c(rep1, rep2, rep3, rep4, rep5, 
+                                      rep6, rep7, rep8, rep9, rep10)))) %>%
+  mutate(kappa = ifelse(is.nan(kappa), 1, kappa)) %>%
+  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) + 
+  geom_point() + 
+  geom_line(aes(linetype = chosen)) +
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
+  labs(x = "Sampling Technique", y = "Kappa", color = "Feature", linetype = "Feature")
 ```

### 2019-02-05 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
changes during meeting

@@
   # Name the items in the lime list
-  names(hamby224_lime) <- map_chr(1:length(hamby224_lime_inputs), function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, 
-              use_density = %s, bin_method = %s, response = %s",
+  names(hamby224_lime) <- map_chr(1:22, function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
               hamby224_lime_inputs$bin_continuous[case],

### 2019-02-06 journals/01-cleaning_training_data.Rmd
worked more on training data journal

---
title: "01-cleaning training data"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

# Overview

This was originally a part of a journal entry that I wrote in my 'Case Studies with LIME' repository. I took the code that I used to clean the training dataset from that entry and updated it in this entry. It should still produce essentially the same dataset. The dataset that gets saved from this journal is the one that I am using for this research project.

```{r}
# Load libraries
library(tidyverse)
library(plotly)
library(randomForest)
```

# The Raw Data

The dataset loaded in below is the original Hamby 172 and 252 dataset that Heike gave to me. Note that when the `hamby173and252` dataset is read in, the studies called "Cary" are excluded. The data file contains rows based on bullet scans from a different study. These rows are no longer being included since Heike has found the study they came from to be poorly executed.

```{r}
# Load in the Hamby 173 and 252 dataset
hamby173and252 <- read.csv("../data/features-hamby173and252.csv") %>%
  filter(study1 != "Cary", study2 != "Cary") %>%
  mutate(study1 = factor(study1), 
         study2 = factor(study2))
```

## Considering the Number of Rows in the Data

If we include symmetric comparisons, each set of test bullets should result in a dataset with
  $$(35 \mbox{ bullets} \times 6 \mbox{ lands})^2=44100 \mbox{ rows},$$
where a row would contain information on a pair of lands. If we do not include the symmetric comparisons, then the dataset should have
  $$\frac{(44100 \mbox{ rows} - (35 \mbox{ bullets} \times 6))}{2} + (35 \mbox{ bullets} \times 6) = 22155 \mbox{ rows}.$$
However, when I looked at the dimension of the datasets, neither of these seem to be the case. See the R code and output below. Note that `hamby173` is currently incorrectly labelled as `hamby44`. Both test sets have less than but close to 22,155 rows. This suggests that these do not include symmetric comparisons. When I checked with Heike, she confirmed that this is the case. This table also shows that there are comparisons across `hamby173` and `hamby252`. These missing observations will be explored more in the next section.

```{r}
# Summary of the number of observations in the Hamby173and252 datase
table(hamby173and252$study1, hamby173and252$study2)
```

## Understanding the Missing Observations

The plot below considers the number of observations within a barrel and bullet comparison from all known cases in the Hamby 173 and 252 data. We can see that the observations on the lower diagonals are missing in all cases which confirms that the symmetric comparisons were not included in the data. Additionally, a handful of cases have less than 36 observations. For the comparisons within the Hamby 173 or Hamby 252 study, the cells on the diagonals are less than 36, because none of the repeats from the symmetric comparisons of lands are included. The cells above the diagonal with less than 36 observations are missing some observations due to tank rash. For the comparisons across studies, the cases with less than expected are also due to tank rash. For some reason, the comparisons between bullets 1 from Hamby 173 and Hamby 252, the cells are being colored grey even though they have 36 observations. I am not sure why this is...

```{r}
# Create the plot to look at number of comparisons within the known bullets
countplot <- hamby173and252 %>%
  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
  group_by(study1, study2, barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(study1 + bullet1 ~ study2 + bullet2, scales = "free") +
  theme_minimal() + 
  labs(title = "Number of Observations per Barrel-Bullet Pair in Hamby 173")

# Make the plot interactive
ggplotly(countplot, width = 800, height = 700) %>%
  shiny::div(align = "center")
```

# Cleaning the Data

The code below cleans the training data. The cleaned data is saved and used as the training dataset for the rest of this research project.

```{r}
# Determine the letters associated with the unknown bullets
letters <- levels(hamby173and252$barrel1)[11:length(levels(hamby173and252$barrel1))]

# Cleaning the data:
#   - corrects the study 173 labels
#   - adjusts the bullet and barrel values for the unknowns
#   - renames the match variable as samesource
#   - selects the desired variables
hamby173and252_cleaned <- hamby173and252 %>%
  mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
         study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
         bullet1 = factor(ifelse(barrel1 %in% letters,
                                 as.character(barrel1),
                                 as.character(bullet1))),
         barrel1 = factor(ifelse(barrel1 %in% letters, 
                                 as.character("Unknown"), 
                                 as.character(barrel1))),
         bullet2 = factor(ifelse(barrel2 %in% letters,
                                 as.character(barrel2),
                                 as.character(bullet2))),
         barrel2 = factor(ifelse(barrel2 %in% letters, 
                                 as.character("Unknown"), 
                                 as.character(barrel2))),
         land1 = factor(land1),
         land2 = factor(land2),
         rfscore = predict(bulletr::rtrees, hamby173and252 %>%
                             select(rownames(bulletr::rtrees$importance)), 
                           type = "prob")[,2]) %>%
  rename(samesource = match) %>%
  select(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2,
         rownames(bulletr::rtrees$importance), samesource, rfscore)

# Save the datasets and response variables as .csv files
write.csv(hamby173and252_cleaned, 
          "../data/hamby173and252_cleaned.csv", 
          row.names = FALSE)
```

## Issue

The number of rtrees predictions does not match the length of my training data...

```{r}
dim(predict(bulletr::rtrees, type = "prob"))
dim(hamby173and252_cleaned)
```

### 2019-02-06 journals/applying LIME to bullet data journal.Rmd
worked more on training data journal

--- 2019-02-05 journal/applying LIME to bullet data journal.Rmd
@@
 Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+
+## Notation
+
+I need to install math jax to get this to work...
+
+\begin{itemize}
+\item $x\in\mathbb{R}^d$: original representation of an instance being explained
+\begin{itemize}
+\item e.g. feature vector containing word embeddings
+\end{itemize}
+\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
+\begin{itemize}
+\item e.g. bag of words
+\end{itemize}
+\item $G$: class of potentially interpretable models
+\begin{itemize}
+\item e.g. linear models, decision trees, rule lists
+\end{itemize}
+\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
+\item $\Omega(g)$: measure of complexity of $g$
+\begin{itemize}
+\item e.g. depth of a tree, number of non-zeros in a linear model
+\end{itemize}
+\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
+\begin{itemize}
+\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
+\end{itemize}
+\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
+\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
+\end{itemize}
+
+## Step by Step Procedure
+
+Step 1:
 

### 2019-02-07 journals/01-cleaning_training_and_testing_data.Rmd
finished moving training and testing data cleaning steps to journal 01

---
title: "01-cleaning training and testing data"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

# Overview

This journal includes the code that is used to clean the training and testing datasets.

```{r}
# Load libraries
library(tidyverse)
library(plotly)
library(randomForest)
```

Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the bulletr library. I create such a vector below to use in this journal.

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(bulletr::rtrees$importance)
```

# Training Data

This was originally a part of a journal entry that I wrote in my 'Case Studies with LIME' repository. I took the code that I used to clean the training dataset from that entry and updated it in this entry. It should still produce essentially the same dataset (with some possible changes to the level names of some of the barrels due to a 'factor' issue). The dataset that gets saved from this journal is the one that I am using for this research project.

### The Raw Data

The dataset loaded in below is the original Hamby 172 and 252 dataset that Heike gave to me. Note that when the `hamby173and252` dataset is read in, the studies called "Cary" are excluded. The data file contains rows based on bullet scans from a different study. These rows are no longer being included since Heike has found the study they came from to be poorly executed.

```{r}
# Load in the Hamby 173 and 252 dataset
hamby173and252_raw <- read.csv("../data/originals/features-hamby173and252.csv") %>%
  filter(study1 != "Cary", study2 != "Cary") %>%
  mutate(study1 = factor(study1), 
         study2 = factor(study2))
```

### Considering the Number of Rows in the Raw Data

If we include symmetric comparisons, each set of test bullets should result in a dataset with
  $$(35 \mbox{ bullets} \times 6 \mbox{ lands})^2=44100 \mbox{ rows},$$
where a row would contain information on a pair of lands. If we do not include the symmetric comparisons, then the dataset should have
  $$\frac{(44100 \mbox{ rows} - (35 \mbox{ bullets} \times 6))}{2} + (35 \mbox{ bullets} \times 6) = 22155 \mbox{ rows}.$$
However, when I looked at the dimension of the datasets, neither of these seem to be the case. See the R code and output below. Note that `hamby173` is currently incorrectly labelled as `hamby44`. Both test sets have less than but close to 22,155 rows. This suggests that these do not include symmetric comparisons. When I checked with Heike, she confirmed that this is the case. This table also shows that there are comparisons across `hamby173` and `hamby252`. These missing observations will be explored more in the next section.

```{r}
# Summary of the number of observations in the Hamby173and252 datase
table(hamby173and252_raw$study1, hamby173and252_raw$study2)
```

### Understanding the Missing Observations

The plot below considers the number of observations within a barrel and bullet comparison from all known cases in the Hamby 173 and 252 data. We can see that the observations on the lower diagonals are missing in all cases which confirms that the symmetric comparisons were not included in the data. Additionally, a handful of cases have less than 36 observations. For the comparisons within the Hamby 173 or Hamby 252 study, the cells on the diagonals are less than 36, because none of the repeats from the symmetric comparisons of lands are included. The cells above the diagonal with less than 36 observations are missing some observations due to tank rash. For the comparisons across studies, the cases with less than expected are also due to tank rash. For some reason, the comparisons between bullets 1 from Hamby 173 and Hamby 252, the cells are being colored grey even though they have 36 observations. I am not sure why this is...

```{r}
# Create the plot to look at number of comparisons within the known bullets
countplot <- hamby173and252_raw %>%
  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
  group_by(study1, study2, barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(study1 + bullet1 ~ study2 + bullet2, scales = "free") +
  theme_minimal() + 
  scale_fill_distiller(palette = "GnBu", direction = 1)

# Make the plot interactive
ggplotly(countplot, width = 800, height = 700) %>%
  shiny::div(align = "center")
```

### Cleaning the Trainng Data

The code below cleans the training data. The cleaning involves:

- correcting the study 173 labels
- adjustiing the bullet and barrel values for the unknowns
- renaming the match variable as samesource
- selecting the desired variables

```{r}
# Determine the letters associated with the unknown bullets
letters <- levels(hamby173and252_raw$barrel1)[11:length(levels(hamby173and252_raw$barrel1))]

# Cleaning the testing data
hamby173and252_train <- hamby173and252_raw %>%
  mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
         study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
         bullet1 = factor(ifelse(barrel1 %in% letters,
                                 as.character(barrel1),
                                 as.character(bullet1))),
         barrel1 = factor(ifelse(barrel1 %in% letters, 
                                 as.character("Unknown"), 
                                 as.character(barrel1))),
         bullet2 = factor(ifelse(barrel2 %in% letters,
                                 as.character(barrel2),
                                 as.character(bullet2))),
         barrel2 = factor(ifelse(barrel2 %in% letters, 
                                 as.character("Unknown"), 
                                 as.character(barrel2))),
         land1 = factor(land1),
         land2 = factor(land2),
         rfscore = predict(bulletr::rtrees, hamby173and252_raw %>%
                             select(rf_features), 
                           type = "prob")[,2]) %>%
  rename(samesource = match) %>%
  select(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2,
         rf_features, samesource, rfscore)
```

The cleaned data is saved and used as the training dataset for the rest of this research project.

```{r}
# Save the datasets and response variables as .csv files
write.csv(hamby173and252_train, "../data/hamby173and252_train.csv", row.names = FALSE)
```

### Issue

The number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.

```{r}
dim(predict(bulletr::rtrees, type = "prob"))
dim(hamby173and252_train)
```

# Testing Data

### The Raw Data

The original data files given to me by Heike are loaded in below. For now, we are working with only sets 1 and 11 from the Hamby 224 study. She may provide me with more in the future.

```{r}
# Load in the Hamby 224 datasets
hamby224_set1 <- readRDS("../data/originals/h224-set1-features.rds")
hamby224_set11 <- readRDS("../data/originals/h224-set11-features.rds")
```

### Cleaning the Testing Data

The code below cleans the data from both sets 1 and 11. This involves:

- selecting the desired variables
- renaming the bullet and land variables
- creating study and set variables
- recoding the bullet and land names

```{r}
# Clean the Hamby 224 set 1 data
hamby224_set1_cleaned <- hamby224_set1 %>%
  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
  rename(bullet1 = bulletA,
         bullet2 = bulletB, 
         land1 = landA,
         land2 = landB) %>%
  mutate(study = factor("Hamby 224"), 
         set = factor("Set 1"),
         bullet1 = recode(factor(bullet1), 
                          "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
         bullet2 = recode(factor(bullet2), 
                          "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
         land1 = recode(factor(land1), 
                        "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                        "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
         land2 = recode(factor(land2), 
                        "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                        "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
  select(study, set, bullet1:land2, rf_features, rfscore, samesource)

# Clean the Hamby 224 set 11 data
hamby224_set11_cleaned <- hamby224_set11 %>%
  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
  rename(bullet1 = bulletA,
         bullet2 = bulletB, 
         land1 = landA,
         land2 = landB) %>%
  mutate(study = factor("Hamby 224"), 
         set = factor("Set 11"),
         bullet1 = recode(factor(bullet1), 
                          "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                          "Bullet I" = "Questioned"),
         bullet2 = recode(factor(bullet2), 
                          "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                          "Bullet I" = "Questioned")) %>%
  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
```

The cleaned data from sets 1 and 11 are combined below into the testing dataset. Rows are added for the missing comparisons from the Hamby 224 study, and some additional cleaning is done.

```{r}
# Create a dataset with all combinations of lands and bullets comparisons for each set
combinations <- data.frame(set = factor(rep(c("Set 1", "Set 11"), each = 324)),
                    expand.grid(land1 = factor(c("Land 1", "Land 2", "Land 3", 
                                                 "Land 4", "Land 5", "Land 6")),
                                land2 = factor(c("Land 1", "Land 2", "Land 3", 
                                                 "Land 4", "Land 5", "Land 6")),
                                bullet1 = factor(c("Known 1", "Known 2", "Questioned")),
                                bullet2 = factor(c("Known 1", "Known 2", "Questioned"))))

# Join the two cleaned Hamby 224 sets into one testing set
hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
                                            hamby224_set11_cleaned)) %>%
  mutate(set = factor(set),
         bullet1 = factor(bullet1),
         bullet2 = factor(bullet2),
         land1 = factor(land1),
         land2 = factor(land2)) %>%
  right_join(combinations, by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
  filter(!(bullet1 == "Questioned" & bullet2 == "Known 1"),
         !(bullet1 == "Questioned" & bullet2 == "Known 2"),
         !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
  arrange(rfscore) %>%
  mutate(case = factor(1:length(study))) %>%
  select(case, study:samesource)
```

The testing data file is saved below.

```{r}
# Save the test data as a .csv file
write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)
```

### 2019-02-07 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
finished moving training and testing data cleaning steps to journal 01

--- 2019-02-05 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 
-```{r}
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
-
-# Add the random forest score to the training set
-# hamby173and252_train$rfscore = predict(rtrees,
-#                                        hamby173and252_train %>% select(rf_features),
-#                                        type = "prob")[,2]
-# 
-# Save the adjusted training data
-# write.csv(hamby173and252_train %>% select(-X), "../data/hamby173and252_train.csv",
-#           row.names = FALSE)
-```
-
 ## Testing Data: The Hamby 224 Clone
@@
 ```{r}
-# Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("../data/h224-set1-features.rds")
-hamby224_set11 <- readRDS("../data/h224-set11-features.rds")
-```
-
-```{r}
-# If the test data does not exist, clean the data, create the test data, and save it
-# Otherwise, load in the test data
-if(!file.exists("../data/hamby224_test.csv")) {
-
-  # Clean the Hamby 224 set 1 data
-  hamby224_set1_cleaned <- hamby224_set1 %>%
-    select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-    rename(bullet1 = bulletA,
-           bullet2 = bulletB, 
-           land1 = landA,
-           land2 = landB) %>%
-    mutate(study = factor("Hamby 224"), 
-           set = factor("Set 1"),
-           bullet1 = recode(factor(bullet1), 
-                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-           bullet2 = recode(factor(bullet2), 
-                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-           land1 = recode(factor(land1), 
-                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
-                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
-           land2 = recode(factor(land2), 
-                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
-                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
-    select(study, set, bullet1:land2, rf_features, rfscore, samesource)
-
-  # Clean the Hamby 224 set 11 data
-  hamby224_set11_cleaned <- hamby224_set11 %>%
-    select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-    rename(bullet1 = bulletA,
-           bullet2 = bulletB, 
-           land1 = landA,
-           land2 = landB) %>%
-    mutate(study = factor("Hamby 224"), 
-           set = factor("Set 11"),
-           bullet1 = recode(factor(bullet1), 
-                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
-                            "Bullet I" = "Questioned"),
-           bullet2 = recode(factor(bullet2), 
-                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
-                            "Bullet I" = "Questioned")) %>%
-    select(study, set, bullet1:land2, rf_features, rfscore, samesource)
-
-  # Create a dataset with all combinations of lands and bullets comparisons for each set
-  combinations <- data.frame(set = factor(rep(c("Set 1", "Set 11"), each = 324)),
-                      expand.grid(land1 = factor(c("Land 1", "Land 2", "Land 3", 
-                                                   "Land 4", "Land 5", "Land 6")),
-                                  land2 = factor(c("Land 1", "Land 2", "Land 3", 
-                                                   "Land 4", "Land 5", "Land 6")),
-                                  bullet1 = factor(c("Known 1", "Known 2", "Questioned")),
-                                  bullet2 = factor(c("Known 1", "Known 2", "Questioned"))))
-
-  # Join the two cleaned Hamby 224 sets into one testing set
-  hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
-                                              hamby224_set11_cleaned)) %>%
-    mutate(set = factor(set),
-           bullet1 = factor(bullet1),
-           bullet2 = factor(bullet2),
-           land1 = factor(land1),
-           land2 = factor(land2)) %>%
-    right_join(combinations, by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-    filter(!(bullet1 == "Questioned" & bullet2 == "Known 1"),
-           !(bullet1 == "Questioned" & bullet2 == "Known 2"),
-           !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
-    arrange(rfscore) %>%
-    mutate(case = factor(1:length(study))) %>%
-    select(case, study:samesource)
-
-  # Save the test data as a .csv file
-  write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)
-
-} else {
-
 # Read in the test data
 hamby224_test <- read.csv("../data/hamby224_test.csv")
-
-}
 ```
@@
 ## Random Forest Model
+
+```{r}
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(rtrees$importance)
+```
 

### 2019-02-07 journals/02-plotting_features.Rmd
added session info to journal 01

--- 2019-01-30 journal/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "02-plotting_features"
 author: "Katherine Goode"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-output:
-  html_document:
-    toc: true
-    toc_depth: 2
-    toc_float: true
+date: "2/7/2019"
+output: html_document
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      fig.pos = "center")
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This
 
 ```{r}
-# Load libraries
-library(bulletr)
-library(caret)
-library(cowplot)
-library(furrr)
-library(future)
-library(gretchenalbrecht)
-library(irr)
-library(lime)
-library(plotly)
-library(purrr)
-library(randomForest)
-library(tidyverse)
-
-# Source functions
-source("../code/helper_functions.R")
-
 # Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
@@
 ```
-
-# Visualizations of Explanations
-
-Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
-This one has been created from the lime explanations with 2 quantile bins.
-It includes all three of the chosen features for each case in the testing dataset.
-For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
-
-```{r fig.height = 10}
-# Plot of fequency for each bin division for 2 quantile bins
-hamby224_test_explain %>%
-  filter(situation == "2 quantile") %>%
-  ggplot(aes(x = feature_desc)) +
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
-
-The plot below is the model for the one that will be used in the app for exploring the `lime` explanations from the bullet matching data. This is the data from set 1 of the testing dataset.
-
-```{r}
-# Heatmap of rfscore for each comparison in set 1
-hamby224_test %>%
-  filter(set == "Set 1") %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-             text = paste('Bullets Compared: ', bullet1, "-", land1, 
-                          "vs", bullet2, "-", land2,
-                          '\nRandom Forest Score: ', 
-                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
-  geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet2 ~ bullet1, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank()) +
-  labs(x = "", y = "", fill = "RF Score")
-```
-
-I also wrote some code to create the above plot using individual plots instead of facets. This is included below. (It is a bit outdated compared to my newer version of the plot.)
-
-```{r}
-# Code for creating the heatmap plots using individual plots
-p1 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 1") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p2 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p3 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p4 <- ggplot() + geom_blank() + theme_classic()
-
-p5 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p6 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p7 <- ggplot() + geom_blank() + theme_classic()
-
-p8 <- ggplot() + geom_blank() + theme_classic()
-
-p9 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Questioned", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
-
-style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, 
-              nrows = 3, 
-              titleX = TRUE, 
-              titleY = TRUE, 
-              margin = 0.03),
-      hoverinfo = "skip",
-      traces = 7)
-```
-
-# Draft of LIME Procedure
-
-I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
-It needs a lot of work, but it is a start.
-The final version of this will end up in the technical stats paper critiquing LIME.
-The version in the firearm examiner's paper will be much simpler...
-
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
-
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
-
-1. Distributions for each of the features in the training data are obtained. 
-    + The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n_bins = 4`).
-
-2. Many ($n$) samples from each of the feature distributions are drawn.
-     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
-      * bin\_continuous = TRUE should continuous variables be binned?
-      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-      * n\_bins = 4 number of bins if bin\_continuous is TRUE
-      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
-
-3. Predictions for the testing data using the random forest model are computed.
-     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-
-4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-    + The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-
-5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
-    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-      * forward selection with ridge regression
-      * highest weight with ridge regression
-      * LASSO model
-      * tree model
-      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-
-6.
-A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-For the prediction of interest, 
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-7. The feature weights are extracted and used as the explanations.
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
-
-# Computation Issues
-
-## Plotly Dead Space Issue
-
-I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
-
-```{r eval = FALSE}
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-# library(plotly) # version 4.8.0
-# library(ggplot2) # version 3.1.0
-# library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none")
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
-```
-
-## Caret vs RandomForest
-
-The `lime` function in lime is set up to work with specific packages.
-For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
-I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
-It seemed to work.
-However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
-To do this, I used the iris data.
-The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
-Then the `lime` and `explain` functions are applied to both models.
-
-```{r}
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime::lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
-```
-
-To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
-I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
-Since lime is based on random permutations, I would not expect the values from the two models to be exact.
-However, I would like them to be close.
-The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
-We decided this seems like the two versions of the explanations are reasonably exchangeable.
-
-```{r}
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
-# Scatterplots of the randomForest versus caret variable values
-ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
-  geom_point() + 
-  facet_wrap( ~ variable, scales = "free") + 
-  geom_abline(intercept = 0, slope = 1)
-```
-
-## Comparing Furrr Times
-
-The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
-I ran and timed the code below to see how much faster the code was.
-Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
-
-```{r eval = FALSE}
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# Slow way
-plan(sequential)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 218.188 sec elapsed
-
-# Fast way
-plan(multiprocess)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 107.731 sec elapsed
-```
-
-# New Binning Methods
-
-## Subsampled Bins
-
-One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles.
-The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`.
-By subsampling, it might allow for better locations to bin the data.
-I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.
-
-```{r eval = FALSE}
-# Code saved for future use for the sampling data
-
-# Create the data (with a set seed)
-set.seed(20181128)
-hamby173and252_train_sub <- hamby173and252_train %>%
-  filter(samesource == FALSE) %>%
-  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-# Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-# Apply lime to the subsampled training data with the specified input options
-hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
-                                                        select(-case)),
-                                         .f = run_lime, # run_lime is one of my helper functions
-                                         train = hamby173and252_train_sub %>% select(rf_features),
-                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                         rfmodel = as_classifier(rtrees),
-                                         label = "TRUE",
-                                         nfeatures = 3,
-                                         seed = TRUE) %>%
-  mutate(training_data = factor("Subsampled"))
-
-# Separate the lime and explain function results from the subsampled data
-hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-# Join the lime results from the full and subsampled training data
-hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
-```
-
-## Tree Based Bins
-
-Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins.
-That is, the divisions in the tree could be used as the bin cuts.
-This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
-(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
-
-Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
-The function is stored in the file   `helper_functions.R`.
-Here is an example using the function below with the predictor variable of ccf.
-
-```{r}
-# Example using treebink
-treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
-```
-
-However, there seems to be a problem with `treebink`.
-For certain variables, when a high number of bins is requested, the function returns more than the desired number of bins.
-Heike is going to look into this.
-
-She recently updated the function `treebink` to run using the tree package. Here are some comments from her about the code:
-
-"I've moved it from rpart to tree.
-I am not quite sure that the two packages are doing the exact same thing.
-They claim they do but they might be implemented a bit differently.
-What we are doing now is if there are too many splits, we look at the order in which the splits are made and roll back some of them.
-I haven't found a case that doesn't work, but obviously that doesn't show that there isn't any :)"
-
-I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
-This function is also included in the file `helper_functions.R`.
-The output from `mylime` can then be input into the `explain` function to obtain explanations.
-I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
-
-# Assessing Lime Explanations
-
-When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
-This led me to try applying LIME with a handful of input values.
-I also have tried running LIME with the tree based bins.
-Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation a handful of times.
-I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
-
-## Accuracy
-
-The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
-Each set of input values was only run once.
-
-```{r}
-# Read in the lime comparison data (the comparisons are run in the firearm examiner
-# paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
-```
-
-### Complex versus Simple Model Predictions
-
-The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
-The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and the type of bin.
-The points are colored by the $R^2$ value from the fit of the simple model.
-The lines are linear regression lines fit to the data points within a facet.
-We would hope that there is a linear relationship between these two variables.
-None of the cases show strong linear trends, but some are more linear than others.
-The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
-The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-The tree based bins do the best job with predictions above 0.6 for all number of bins.
-The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of simple model versus complex model predictions
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
-       color = "Simple Model R2")
-```
-
-The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and bin type.
-Again, the points are colored by the $R^2$ values from the simple model.
-All cases show a v-shaped trend.
-The low part of the v occurs around a random forest score of about 0.25.
-That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
-It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
-This is not the case with the quantile bins.
-It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of difference in predictions versus rfscore
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x = "Complex Model Prediction (RF Score)", 
-       y = "Difference Between Complex and Simple Model Predictions",
-       color = "Simple Model R2")
-```
-
-At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
-The plot below shows one example with the data from 3 equally spaced bins.
-There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
-This may be something to return to.
-
-```{r}
-# Plots of model "residuals"
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue") + 
-  labs(x = "Feature Value", y = "Residual")
-```
-
-### Comparing Input Values by MSE and $R^2$
-
-In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
-I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
-where $n$ is the number of observations in the testing dataset (within a set).
-Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
-
-```{r}
-# Summarizing lime results
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response, set) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set) %>%
-  ungroup()
-```
-
-The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
-
-```{r}
-# Plot of MSEs
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot below shows the average $R^2$ value for each of the input situations faceted by set.
-The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
-
-```{r}
-# Plot of R^2s
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-## Consistency with One Implementation
-
-I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
-I would like the features chosen to not depend on the number of bins used.
-Otherwise, it will be difficult to know how many bins to use.
-Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
-The code below creates a dataset that identifies the order in which the features are chosen by lime.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-chosen_features <- hamby224_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
-Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
-It calculates the degree of agreement in classification over that which would be expected by chance.
-A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
-
-I computed kappa for each bin situation separately for the top three features chosen.
-These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
-The values of kappa for the quantile bins are slight to fair agreement.
-For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
-
-```{r}
-# Computes and plots the values of kappa
-chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(set, bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, set, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  facet_grid( ~ set) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
-
-```{r fig.height = 8, fig.width = 8}
-# Plots the top feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
-```
-
-I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
-The plots are separated by set.
-
-```{r}
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-chosen_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-## Consistency Across Implementations
-
-In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
-I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-# Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
-  group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff),
-            ave_r2 = mean(model_r2))
-```
-
-The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins.
-The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
-
-```{r}
-# Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
-There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
-
-```{r}
-# Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-# Determine and plot the average and variability of the number levels for each case 
-# and input option
-hamby224_consistency <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, nbins, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels)) %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", as.character(nbins)))
-
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
-  geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was seven.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-# Determine the order that the features are chosen within a case and 
-# set of input options
-sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-```{r}
-# Determine and plot the number of features chosen across the 10 reps within 
-# a set, input options, and feature level
-sensitivity_chosen %>%
-  group_by(set, situation, case) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-The plots below need some work, but they contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-```
-
-I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
-I realized it would be helpful to view the relationship between the features and the random forest score.
-The plots below show the testing data with random forest score versus each of the features.
-The points are colored by the samesource variable.
-
-```{r}
-hamby224_test %>% 
-  select(rf_features, rfscore, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, rfscore, samesource) %>%
-  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
-  geom_point() + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Input Rankings
-
-In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
-The first table below is for set 1, and the second table below is for set 11.
-
-While using these to help me decide which input settings to use, I had a handful of thoughts:
-
-* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
-* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
-This makes me think that it would be okay to base my decision off of the results from the single rep.
-* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
-* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
-Right now, the feature plots from these explanations are not very helpful.
-I would need to adjust the intercept or something.
-
-Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
-
-```{r}
-joined_results <- hamby224_lime_results %>%
-  select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_results %>%
-              group_by(set, situation) %>%
-              summarise(mean_sensitivity_mse = mean(mse), 
-                        sd_sensitivity_mse = sd(mse)),
-            by = c("set", "situation")) %>%
-  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
-            by = c("set", "situation")) %>%
-  group_by(set) %>%
-  mutate(mse_order = dense_rank(mse),
-         ave_r2_order = dense_rank(desc(ave_r2)),
-         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
-         mean_nlevels_order = dense_rank(mean_nlevels))
-```
-
-```{r}
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 1") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 1")
-
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 11") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 11")
-```

### 2019-02-07 journals/01-cleaning_training_and_testing_data.Rmd
added session info to journal 01
spelling check

@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
@@
 - correcting the study 173 labels
-- adjustiing the bullet and barrel values for the unknowns
+- adjusting the bullet and barrel values for the unknowns
 - renaming the match variable as samesource
@@
 - creating study and set variables
-- recoding the bullet and land names
+- re-coding the bullet and land names
 
@@
 ```
+
+# Session Info
+
+```{r}
+sessionInfo()
+```

### 2019-02-07 journals/02-plotting_features.Rmd
changed more to read.csv and write.csv and finished journal 02 on plotting features

@@
 author: "Katherine Goode"
-date: "2/7/2019"
-output: html_document
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+output:
+  html_document:
+    toc: true
+    toc_depth: 3
+    toc_float: true
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
 ```
@@
 
-This
+This journal contains plots of the random forest features from both the training and testing datasets.
+
+```{r}
+# Load libraries
+library(tidyverse)
+library(cowplot)
+```
+
+# The Data
+
+The cleaning training and testing datasets are loaded in below.
 
@@
 hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
+hamby224_test <- read.csv("../data/hamby224_test.csv")
+```
 
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+A vector containing the features used in the random forest `rtrees` is created below that will be used when creating some of the plots in this journal.
 
+```{r}
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
+rf_features <- rownames(bulletr::rtrees$importance)
 ```
@@
 
-## Distributions by `samesource`
+### Distributions by `samesource`
 
@@
   theme(legend.position = "bottom")
+```
 
+```{r}
 # Create plots of the feature distributions colored by samesource for the testing 
@@
 
-## Correlations
+### Correlations
 

### 2019-02-07 journals/02-plotting_training_and_testing_data.Rmd
added rfscore plots to journal 02

--- 2019-01-30 journal/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "02-plotting_features"
 author: "Katherine Goode"
@@
     toc: true
-    toc_depth: 2
+    toc_depth: 3
     toc_float: true
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      fig.pos = "center")
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
 ```
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This journal contains plots created from the training and testing datasets.
 
@@
 # Load libraries
-library(bulletr)
-library(caret)
+library(tidyverse)
 library(cowplot)
-library(furrr)
-library(future)
-library(gretchenalbrecht)
-library(irr)
-library(lime)
 library(plotly)
-library(purrr)
-library(randomForest)
-library(tidyverse)
+```
 
-# Source functions
-source("../code/helper_functions.R")
+# The Data
 
+The cleaning training and testing datasets are loaded in below.
+
+```{r}
 # Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
 hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
+hamby224_test <- read.csv("../data/hamby224_test.csv")
+```
 
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+A vector containing the features used in the random forest `rtrees` is created below that will be used when creating some of the plots in this journal.
 
+```{r}
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
+rf_features <- rownames(bulletr::rtrees$importance)
 ```
@@
 
-# Visualizations of Explanations
+# Random Forest Scores
 
-Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
-This one has been created from the lime explanations with 2 quantile bins.
-It includes all three of the chosen features for each case in the testing dataset.
-For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
-
-```{r fig.height = 10}
-# Plot of fequency for each bin division for 2 quantile bins
-hamby224_test_explain %>%
-  filter(situation == "2 quantile") %>%
-  ggplot(aes(x = feature_desc)) +
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
+### Facet Version
 
@@
 ```
+
+### Individual Plots Version
 
@@
 
-# Draft of LIME Procedure
-
-I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
-It needs a lot of work, but it is a start.
-The final version of this will end up in the technical stats paper critiquing LIME.
-The version in the firearm examiner's paper will be much simpler...
-
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
-
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
-
-1. Distributions for each of the features in the training data are obtained. 
-    + The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n_bins = 4`).
-
-2. Many ($n$) samples from each of the feature distributions are drawn.
-     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
-      * bin\_continuous = TRUE should continuous variables be binned?
-      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-      * n\_bins = 4 number of bins if bin\_continuous is TRUE
-      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
-
-3. Predictions for the testing data using the random forest model are computed.
-     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-
-4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-    + The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-
-5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
-    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-      * forward selection with ridge regression
-      * highest weight with ridge regression
-      * LASSO model
-      * tree model
-      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-
-6.
-A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-For the prediction of interest, 
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-7. The feature weights are extracted and used as the explanations.
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
-
-# Computation Issues
-
-## Plotly Dead Space Issue
-
-I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
-
-```{r eval = FALSE}
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-# library(plotly) # version 4.8.0
-# library(ggplot2) # version 3.1.0
-# library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none")
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
-```
-
-## Caret vs RandomForest
-
-The `lime` function in lime is set up to work with specific packages.
-For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
-I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
-It seemed to work.
-However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
-To do this, I used the iris data.
-The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
-Then the `lime` and `explain` functions are applied to both models.
+# Session Info
 
 ```{r}
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime::lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
+sessionInfo()
 ```
-
-To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
-I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
-Since lime is based on random permutations, I would not expect the values from the two models to be exact.
-However, I would like them to be close.
-The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
-We decided this seems like the two versions of the explanations are reasonably exchangeable.
-
-```{r}
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
-# Scatterplots of the randomForest versus caret variable values
-ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
-  geom_point() + 
-  facet_wrap( ~ variable, scales = "free") + 
-  geom_abline(intercept = 0, slope = 1)
-```
-
-## Comparing Furrr Times
-
-The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
-I ran and timed the code below to see how much faster the code was.
-Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
-
-```{r eval = FALSE}
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# Slow way
-plan(sequential)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 218.188 sec elapsed
-
-# Fast way
-plan(multiprocess)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 107.731 sec elapsed
-```
-
-# New Binning Methods
-
-## Subsampled Bins
-
-One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles.
-The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`.
-By subsampling, it might allow for better locations to bin the data.
-I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.
-
-```{r eval = FALSE}
-# Code saved for future use for the sampling data
-
-# Create the data (with a set seed)
-set.seed(20181128)
-hamby173and252_train_sub <- hamby173and252_train %>%
-  filter(samesource == FALSE) %>%
-  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-# Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-# Apply lime to the subsampled training data with the specified input options
-hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
-                                                        select(-case)),
-                                         .f = run_lime, # run_lime is one of my helper functions
-                                         train = hamby173and252_train_sub %>% select(rf_features),
-                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                         rfmodel = as_classifier(rtrees),
-                                         label = "TRUE",
-                                         nfeatures = 3,
-                                         seed = TRUE) %>%
-  mutate(training_data = factor("Subsampled"))
-
-# Separate the lime and explain function results from the subsampled data
-hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-# Join the lime results from the full and subsampled training data
-hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
-```
-
-## Tree Based Bins
-
-Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins.
-That is, the divisions in the tree could be used as the bin cuts.
-This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
-(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
-
-Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
-The function is stored in the file   `helper_functions.R`.
-Here is an example using the function below with the predictor variable of ccf.
-
-```{r}
-# Example using treebink
-treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
-```
-
-However, there seems to be a problem with `treebink`.
-For certain variables, when a high number of bins is requested, the function returns more than the desired number of bins.
-Heike is going to look into this.
-
-She recently updated the function `treebink` to run using the tree package. Here are some comments from her about the code:
-
-"I've moved it from rpart to tree.
-I am not quite sure that the two packages are doing the exact same thing.
-They claim they do but they might be implemented a bit differently.
-What we are doing now is if there are too many splits, we look at the order in which the splits are made and roll back some of them.
-I haven't found a case that doesn't work, but obviously that doesn't show that there isn't any :)"
-
-I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
-This function is also included in the file `helper_functions.R`.
-The output from `mylime` can then be input into the `explain` function to obtain explanations.
-I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
-
-# Assessing Lime Explanations
-
-When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
-This led me to try applying LIME with a handful of input values.
-I also have tried running LIME with the tree based bins.
-Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation a handful of times.
-I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
-
-## Accuracy
-
-The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
-Each set of input values was only run once.
-
-```{r}
-# Read in the lime comparison data (the comparisons are run in the firearm examiner
-# paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
-```
-
-### Complex versus Simple Model Predictions
-
-The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
-The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and the type of bin.
-The points are colored by the $R^2$ value from the fit of the simple model.
-The lines are linear regression lines fit to the data points within a facet.
-We would hope that there is a linear relationship between these two variables.
-None of the cases show strong linear trends, but some are more linear than others.
-The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
-The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-The tree based bins do the best job with predictions above 0.6 for all number of bins.
-The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of simple model versus complex model predictions
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
-       color = "Simple Model R2")
-```
-
-The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and bin type.
-Again, the points are colored by the $R^2$ values from the simple model.
-All cases show a v-shaped trend.
-The low part of the v occurs around a random forest score of about 0.25.
-That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
-It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
-This is not the case with the quantile bins.
-It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of difference in predictions versus rfscore
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x = "Complex Model Prediction (RF Score)", 
-       y = "Difference Between Complex and Simple Model Predictions",
-       color = "Simple Model R2")
-```
-
-At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
-The plot below shows one example with the data from 3 equally spaced bins.
-There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
-This may be something to return to.
-
-```{r}
-# Plots of model "residuals"
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue") + 
-  labs(x = "Feature Value", y = "Residual")
-```
-
-### Comparing Input Values by MSE and $R^2$
-
-In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
-I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
-where $n$ is the number of observations in the testing dataset (within a set).
-Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
-
-```{r}
-# Summarizing lime results
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response, set) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set) %>%
-  ungroup()
-```
-
-The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
-
-```{r}
-# Plot of MSEs
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot below shows the average $R^2$ value for each of the input situations faceted by set.
-The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
-
-```{r}
-# Plot of R^2s
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-## Consistency with One Implementation
-
-I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
-I would like the features chosen to not depend on the number of bins used.
-Otherwise, it will be difficult to know how many bins to use.
-Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
-The code below creates a dataset that identifies the order in which the features are chosen by lime.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-chosen_features <- hamby224_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
-Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
-It calculates the degree of agreement in classification over that which would be expected by chance.
-A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
-
-I computed kappa for each bin situation separately for the top three features chosen.
-These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
-The values of kappa for the quantile bins are slight to fair agreement.
-For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
-
-```{r}
-# Computes and plots the values of kappa
-chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(set, bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, set, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  facet_grid( ~ set) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
-
-```{r fig.height = 8, fig.width = 8}
-# Plots the top feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
-```
-
-I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
-The plots are separated by set.
-
-```{r}
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-chosen_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-## Consistency Across Implementations
-
-In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
-I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-# Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
-  group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff),
-            ave_r2 = mean(model_r2))
-```
-
-The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins.
-The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
-
-```{r}
-# Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
-There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
-
-```{r}
-# Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-# Determine and plot the average and variability of the number levels for each case 
-# and input option
-hamby224_consistency <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, nbins, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels)) %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", as.character(nbins)))
-
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
-  geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was seven.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-# Determine the order that the features are chosen within a case and 
-# set of input options
-sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-```{r}
-# Determine and plot the number of features chosen across the 10 reps within 
-# a set, input options, and feature level
-sensitivity_chosen %>%
-  group_by(set, situation, case) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-The plots below need some work, but they contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-```
-
-I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
-I realized it would be helpful to view the relationship between the features and the random forest score.
-The plots below show the testing data with random forest score versus each of the features.
-The points are colored by the samesource variable.
-
-```{r}
-hamby224_test %>% 
-  select(rf_features, rfscore, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, rfscore, samesource) %>%
-  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
-  geom_point() + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Input Rankings
-
-In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
-The first table below is for set 1, and the second table below is for set 11.
-
-While using these to help me decide which input settings to use, I had a handful of thoughts:
-
-* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
-* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
-This makes me think that it would be okay to base my decision off of the results from the single rep.
-* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
-* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
-Right now, the feature plots from these explanations are not very helpful.
-I would need to adjust the intercept or something.
-
-Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
-
-```{r}
-joined_results <- hamby224_lime_results %>%
-  select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_results %>%
-              group_by(set, situation) %>%
-              summarise(mean_sensitivity_mse = mean(mse), 
-                        sd_sensitivity_mse = sd(mse)),
-            by = c("set", "situation")) %>%
-  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
-            by = c("set", "situation")) %>%
-  group_by(set) %>%
-  mutate(mse_order = dense_rank(mse),
-         ave_r2_order = dense_rank(desc(ave_r2)),
-         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
-         mean_nlevels_order = dense_rank(mean_nlevels))
-```
-
-```{r}
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 1") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 1")
-
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 11") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 11")
-```

### 2019-02-07 journals/03-applying_lime.Rmd
started creating journal 03

--- 2019-02-07 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
 ---
-title: "Interpreting Random Forest Predictions for Firearm Identification Using LIME"
-author: "Katherine Goode and Heike Hofmann"
+title: "03-applying_lime"
+author: "Katherine Goode"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 output:
-  pdf_document:
-    number_sections: true
-bibliography: references.bib
+  html_document:
+    toc: true
+    toc_depth: 3
+    toc_float: true
 ---
@@
 ```{r setup, include = FALSE}
-# Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      fig.pos = "center")
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+```
 
+# Overview
+
+This journal contains a draft of the the lime procedure, the application of lime to the bullet data, and a plot created by Heike to visualize the lime explanations.
+
+```{r}
 # Load libraries
-library(bulletr)
-library(cowplot)
-library(furrr)
-library(future)
-library(lime)
-library(purrr)
-library(randomForest)
 library(tidyverse)
-library(tree)
 
@@
 
-# Introduction
-
-(need to finish adding sources)
-
-The discipline of firearm identification examines bullets to determine the likelihood that a bullet found in a criminal case was fired from a particular gun.
-To do this, the bullet from the crime will be compared with a bullet that was known to be fired from the gun under evaluation.
-Traditionally, this is a procedure that has been performed by hand.
-Specially trained examiners visually compare the microscopic bullet striations that were created when the bullets passed through the gun barrel.
-Often a comparison microscope is used that allows the examiners to view both bullets at the same time (National Research Council 2009).
-The examiners use this ability to determine whether the two bullets were fired from the same gun barrel.
-
-Recently, the scientific community has been encouraging the inclusion of more data driven techniques to be used in forensic investigations.
-These methods would allow for the reporting of a measure of uncertainty in addition to the conclusion drawn from the analysis.
-This led Hare, Hofmann, and Carriquiry (2017) to propose a new computer automated method of bullet matching that could supplement the visual inspection by the firearm examiners.
-Their method involves obtaining bullet signatures of the striations from the scans of the two bullets, computing variables that measure the similarity of the two signatures, and using a trained random forest model to determine the probability of a match based on the similarity variables.
-They trained their model on a set of known bullet matches and non-matches from the Hamby study.
-They demonstrated how the random forest model can be used to make prediction on a new set of bullet signature comparisons.
-The results from the paper suggest that the random forest model leads to highly accurate bullet matching predictions.
-The authors found that when their model was applied to a testing dataset (?), the resulting error rate was 0%.
-
-While random forest models often result in good predictions as seen in Hare, Hofmann, and Carriquiry, it is well known that a disadvantage of random forest models and other machine learning techniques is that it is difficult to interpret the models (reference?).
-For example, it is not possible to tell which variables played an important role in the creation of individual predictions.
-This issue led to the development of LIME (reference), which is an algorithm that examines the behavior of the complicated model on a local scale around a new prediction using a linear regression model.
-This allows for the ability to understand which were the driving variables that led to a prediction of interest.
-
-(should probably list other current methods for interpreting random forests)
-
-Since firearm identification identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess the model that is being used to quantify the probability that a bullet was fired from a gun.
-LIME provides the ability to understand which were the key variables used by the random forest model to make a prediction, which would allow firearm examiners to check whether or not the predictions created by the random forest are based on reasonable variables.
-
-This paper provides an example of the application of LIME to a bullet matching problem.
-(provide more details about what is contained in the papers - i.e.
-section 2 describes the Hamby data; section 3 describes the random forest model and LIME; ...)
-
 # Data
 
-## Training Data: The Hamby 173 and 252 Datasets
+The training and testing datasets are loaded in below.
 
 ```{r}
-# Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+# Read in the Hamby 224 test data
+hamby224_test <- read.csv("../data/hamby224_test.csv")
+
+# Read in the test_explain data
+hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 ```
 
-## Testing Data: The Hamby 224 Clone
-
-The Hamby 224 Clone is organized as a test set of a cloned (sub-)set of the Hamby 224 bullets.
-As with all Hamby sets [@hamby], Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets.
-The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
-Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet.
-Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
-The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets  or from a different source.
-This situation is similar to what a firearms and toolmarks examiner might encounter in case work.
-
-```{r}
-# Read in the test data
-hamby224_test <- read.csv("../data/hamby224_test.csv")
-```
-
-#  Methods
-
-## Random Forest Model
+A vector containing the features used in the random forest `rtrees` is created below.
 
@@
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
+rf_features <- rownames(bulletr::rtrees$importance)
 ```
 
-## Overview of LIME
+# Draft of LIME Procedure
 
-Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin developed LIME in response to the interpretation issue of many machine learning techniques.
-Many models used in machine learning are referred to as black box prediction models since they are complex models that may provide accurate predictions but are not able to be interpreted.
-That is, it is not possible to understand the relationship between the features and the response variable.
-Without being able to interpret the models, it becomes difficult to diagnose why a model is producing the predictions that it is.
-The developers claim that LIME allows users to check which variables are driving the predictions made by the model.
-This further allows users to determine whether their model is trustworthy.
+### Less Detailed Version
 
-LIME was designed to be a generalized algorithm that can be applied to any predictive model to return an "explanation" for an individual prediction of interest.
-This explanation is meant to convey which features from the model are driving the prediction created by the complex model.
-In the next section, I will provide a detailed description of how the LIME algorithm obtains the explanation when applied to a random forest model with numeric features.
-For now, general overview of the LIME algorithm will be explained.
+I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
+It needs a lot of work, but it is a start.
+The final version of this will end up in the technical stats paper critiquing LIME.
+The version in the firearm examiner's paper will be much simpler...
 
-Suppose that a complex model has been fit on a training dataset with $k$ features and a response variable that may either be numeric or categorical.
-This trained model will be applied to a testing dataset containing the $k$ features to obtain predictions.
-It is of interest to understand which variables played an important role in the predictions.
-LIME will be applied to one of the cases in the testing dataset to obtain an explanation.
-To create the explanation, LIME starts by approximating the distribution of each of the $k$ features in the training dataset.
-It then simulates a large data frame from these distributions.
-The simulated data are used to perform feature selection to determine the $m$ most important features.
-Then a weighted ridge regression model is fit to standardized versions of the selected $m$ features from the simulated data.
-The model assigns higher weights to observations closer to the observed case of interest.
-A linear model is used since it has a well known form and coefficients that can be interpreted.
-The coefficients from the model are extracted and used to "explain" the importance of the variables.
-Features with a larger absolute value of their coefficient are implied to play a larger role in the creation of the prediction.
+The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
+For simplicity, the steps are described as what happens to one case in the test data.
+Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
 
-The developers of LIME wrote a Python package to implement LIME, and Thomas Lin Pedersen adapted their work to create an R package called `lime`.
-This paper will use version `r packageVersion("lime")` of the R package `lime` in the analysis of the bullet matching data.
+Let
+  $$Y_{jk} = \begin{cases} 
+  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
+  0 & \mbox{otherwise}
+  \end{cases}$$
+be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
 
-## Applying LIME
+1. Distributions for each of the features in the training data are obtained. 
+    + The method that `lime` uses to obtain the distribution differs based on the feature type.
+All of the features in the Hamby datasets are numeric.
+For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
+The default number of bins is 4 (`n_bins = 4`).
 
-(this is the section where I will describe how lime was applied and which input values were used)
+2. Many ($n$) samples from each of the feature distributions are drawn.
+     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
+      * bin\_continuous = TRUE should continuous variables be binned?
+      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
+      * n\_bins = 4 number of bins if bin\_continuous is TRUE
+      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
+
+3. Predictions for the testing data using the random forest model are computed.
+     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
+Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
+
+4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
+    + The way that the similarity score is computed depends on the type of feature.
+Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
+Then, by default, the Gower distance is used to compute the similarity score.
+(using the `gower` package in R)
+
+5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
+    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
+      * forward selection with ridge regression
+      * highest weight with ridge regression
+      * LASSO model
+      * tree model
+      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
+
+6.
+A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
+If the response is categorical, the user can select how many categories and which categories they want to explain.
+  $$P(Match = TRUE) = \beta_0 + 
+  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
+  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
+  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
+For the prediction of interest, 
+  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
+7. The feature weights are extracted and used as the explanations.
+
+Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
+Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
+
+### More Detailed Version
+
+I need to install math jax to get this to work...
+
+##### Notation
+
+\begin{itemize}
+\item $x\in\mathbb{R}^d$: original representation of an instance being explained
+\begin{itemize}
+\item e.g. feature vector containing word embeddings
+\end{itemize}
+\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
+\begin{itemize}
+\item e.g. bag of words
+\end{itemize}
+\item $G$: class of potentially interpretable models
+\begin{itemize}
+\item e.g. linear models, decision trees, rule lists
+\end{itemize}
+\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
+\item $\Omega(g)$: measure of complexity of $g$
+\begin{itemize}
+\item e.g. depth of a tree, number of non-zeros in a linear model
+\end{itemize}
+\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
+\begin{itemize}
+\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
+\end{itemize}
+\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
+\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
+\end{itemize}
+
+##### Step by Step Procedure
+
+Step 1:
+
+# Application of LIME
 
@@
 
-## Development of Shiny App for Visualizing the LIME Explanations
+# Plot of Bin Frequencies
 
-# Results
+Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
+This one has been created from the lime explanations with 2 quantile bins.
+It includes all three of the chosen features for each case in the testing dataset.
+For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
 
-- show examples of using the app and what we have learned from the LIME explanations
-
-# Discussion
-
-Ideas for improvement of LIME: 
-  - change the binning method:
-    - lime is not good with linear relationships with classifiers due to the 
-    inside-outside binning - it would be better to use a cumulative approach
-  - consider interactions in the ridge regression model
-  - learn lambda in the ridge regression
-  - could add a penalty for the number of parameters in the model (or the number of bins)
-  - could start with a fine grid of bins and then go backwards and fit the models on this sampled data
-  - could try a type of ANOVA test if we can have nested models or if we can assume nesting
-  - could compute something like an R^2_adj
-  - could force the intercept to be 0.5
-  - try out the subsampling
-
-# References
+```{r fig.height = 10}
+# Plot of fequency for each bin division for 2 quantile bins
+hamby224_test_explain %>%
+  filter(situation == "2 quantile") %>%
+  ggplot(aes(x = feature_desc)) +
+  geom_bar() +
+  coord_flip() + 
+  facet_grid(set ~ .)
+```

### 2019-02-07 journals/applying LIME to bullet data journal.Rmd
started creating journal 03

--- 2019-02-05 journal/applying LIME to bullet data journal.Rmd
@@
 ```
-
-# Plots of Features
-
-## Distributions by `samesource`
-
-I created the following two plots of the training data as suggested by Heike.
-The histograms below show the distributions of the features used in the random forest `rtrees`.
-The histograms are filled by the `samesource` variable, which is the truth of whether or not the comparison is from the same barrel and land.
-The default histograms make it hard to compare the distributions of the matches and non-matches since there are many more comparisons that have `samesource == FALSE`.
-
-```{r}
-# Create plots of the feature distributions colored by samesource for the training data
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
-       title = "Hamby 173 and 252 Training Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-By setting `position = "fill"` in the `geom_histogram` function, it is easier to compare the matches and non-matches.
-<span style="color:teal"> These plots could be used in the future to hand select the bins for lime.
-Additionally, fitting a logistic regression to this data could also be used to determine the LC50, LC10, ad LC90, which could be used as the bins for lime.
-</span>
-
-```{r}
-# Create plots of the feature distributions colored by samesource for the training data
-# using the position = "fill" option
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
-       title = "Hamby 173 and 252 Training Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-The plots below have the same structure, but they are created with the Hamby 224 testing data.
-I chose to not separate the testing data by sets, but this is something that could be done later if necessary.
-
-```{r}
-# Create plots of the feature distributions colored by samesource for the testing data
-hamby224_test %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 15) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-
-# Create plots of the feature distributions colored by samesource for the testing 
-# data using the position = "fill" option
-hamby224_test %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 15) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Correlations
-
-I made these plots to look at the correlation between features in the training data within the TRUE and FALSE cases of samesource.
-The features are highly correlated for the match comparisons.
-It is clear that the variables are more correlated with the match comparisons than the non-match comparisons.
-However, there are still some variables that are relatively highly correlation with the non-match comparisons.
-
-```{r fig.height = 4, fig.width = 9}
-# Create a correlation heatmap of the match comparisons in the training data
-cor_match <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == TRUE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Match Comparisons")
-
-# Create a correlation heatmap of the non-match comparisons in the training data
-cor_nonmatch <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == FALSE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") +
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Non-Match Comparisons")
-
-# Create a title for the panel of plots
-cor_title <- ggdraw() +
-  draw_label("Correlation of Feature Variables in the Training Data", 
-             fontface = "bold", 
-             size = 16,
-             x = 0.5,
-             hjust = 0.5)
-
-# Create a joined legend for the panel of plots
-cor_legend <- get_legend(cor_match + theme(legend.position = "right"))
-
-# Create the panel of plots
-plot_grid(cor_title, 
-          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
-          ncol = 1,
-          rel_heights = c(0.25, 3))
-```
-
-The plots below show the correlations for the testing data. The patterns in the plots look really similar to ones of the training data.
-
-```{r fig.height = 4, fig.width = 9}
-# Create a correlation heatmap of the match comparisons in the training data
-cor_match_test <- hamby224_test %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == TRUE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Match Comparisons")
-
-# Create a correlation heatmap of the non-match comparisons in the training data
-cor_nonmatch_test <- hamby224_test %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == FALSE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") +
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Non-Match Comparisons")
-
-# Create a title for the panel of plots
-cor_title_test <- ggdraw() +
-  draw_label("Correlation of Feature Variables in the Testing Data", 
-             fontface = "bold", 
-             size = 16,
-             x = 0.5,
-             hjust = 0.5)
-
-# Create a joined legend for the panel of plots
-cor_legend_test <- get_legend(cor_match_test + theme(legend.position = "right"))
-
-# Create the panel of plots
-plot_grid(cor_title_test, 
-          plot_grid(cor_match_test, cor_nonmatch_test, cor_legend_test, 
-                    ncol = 3, rel_widths = c(2, 2, 0.5)),
-          ncol = 1,
-          rel_heights = c(0.25, 3))
-```
-
-# Visualizations of Explanations
-
-Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
-This one has been created from the lime explanations with 2 quantile bins.
-It includes all three of the chosen features for each case in the testing dataset.
-For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
-
-```{r fig.height = 10}
-# Plot of fequency for each bin division for 2 quantile bins
-hamby224_test_explain %>%
-  filter(situation == "2 quantile") %>%
-  ggplot(aes(x = feature_desc)) +
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
-
-The plot below is the model for the one that will be used in the app for exploring the `lime` explanations from the bullet matching data. This is the data from set 1 of the testing dataset.
-
-```{r}
-# Heatmap of rfscore for each comparison in set 1
-hamby224_test %>%
-  filter(set == "Set 1") %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-             text = paste('Bullets Compared: ', bullet1, "-", land1, 
-                          "vs", bullet2, "-", land2,
-                          '\nRandom Forest Score: ', 
-                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
-  geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet2 ~ bullet1, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank()) +
-  labs(x = "", y = "", fill = "RF Score")
-```
-
-I also wrote some code to create the above plot using individual plots instead of facets. This is included below. (It is a bit outdated compared to my newer version of the plot.)
-
-```{r}
-# Code for creating the heatmap plots using individual plots
-p1 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 1") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p2 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p3 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p4 <- ggplot() + geom_blank() + theme_classic()
-
-p5 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p6 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p7 <- ggplot() + geom_blank() + theme_classic()
-
-p8 <- ggplot() + geom_blank() + theme_classic()
-
-p9 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Questioned", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
-
-style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, 
-              nrows = 3, 
-              titleX = TRUE, 
-              titleY = TRUE, 
-              margin = 0.03),
-      hoverinfo = "skip",
-      traces = 7)
-```
-
-# Draft of LIME Procedure
-
-I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
-It needs a lot of work, but it is a start.
-The final version of this will end up in the technical stats paper critiquing LIME.
-The version in the firearm examiner's paper will be much simpler...
-
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
-
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
-
-1. Distributions for each of the features in the training data are obtained. 
-    + The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n_bins = 4`).
-
-2. Many ($n$) samples from each of the feature distributions are drawn.
-     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
-      * bin\_continuous = TRUE should continuous variables be binned?
-      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-      * n\_bins = 4 number of bins if bin\_continuous is TRUE
-      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
-
-3. Predictions for the testing data using the random forest model are computed.
-     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-
-4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-    + The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-
-5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
-    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-      * forward selection with ridge regression
-      * highest weight with ridge regression
-      * LASSO model
-      * tree model
-      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-
-6.
-A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-For the prediction of interest, 
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-7. The feature weights are extracted and used as the explanations.
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
 

### 2019-02-08 journals/03-computation_issues.Rmd
worked more on reorganizing journals

--- 2019-02-07 journals/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "03-computation_issues"
 author: "Katherine Goode"
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This journal documents some of the computation issues I have run into and my "solutions" or "conclusions".
 
@@
 # Load libraries
-library(bulletr)
+library(tidyverse)
+library(plotly)
 library(caret)
-library(cowplot)
-library(furrr)
-library(future)
-library(gretchenalbrecht)
-library(irr)
+library(randomForest)
 library(lime)
-library(plotly)
-library(purrr)
-library(randomForest)
-library(tidyverse)
-
-# Source functions
-source("../code/helper_functions.R")
-
-# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
-
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
 ```
 
-# Computation Issues
-
-## Plotly Dead Space Issue
+# Plotly Dead Space Issue
 
@@
 
-## Caret vs RandomForest
+# Caret vs RandomForest
 
@@
 
-## Comparing Furrr Times
+# Comparing Furrr Times
 
@@
 
-# New Binning Methods
-
-## Subsampled Bins
-
-One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles.
-The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`.
-By subsampling, it might allow for better locations to bin the data.
-I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.
-
-```{r eval = FALSE}
-# Code saved for future use for the sampling data
-
-# Create the data (with a set seed)
-set.seed(20181128)
-hamby173and252_train_sub <- hamby173and252_train %>%
-  filter(samesource == FALSE) %>%
-  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-# Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-# Apply lime to the subsampled training data with the specified input options
-hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
-                                                        select(-case)),
-                                         .f = run_lime, # run_lime is one of my helper functions
-                                         train = hamby173and252_train_sub %>% select(rf_features),
-                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                         rfmodel = as_classifier(rtrees),
-                                         label = "TRUE",
-                                         nfeatures = 3,
-                                         seed = TRUE) %>%
-  mutate(training_data = factor("Subsampled"))
-
-# Separate the lime and explain function results from the subsampled data
-hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-# Join the lime results from the full and subsampled training data
-hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
-```
-
-## Tree Based Bins
-
-Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins.
-That is, the divisions in the tree could be used as the bin cuts.
-This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
-(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
-
-Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
-The function is stored in the file   `helper_functions.R`.
-Here is an example using the function below with the predictor variable of ccf.
+# Session Info
 
 ```{r}
-# Example using treebink
-treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
+sessionInfo()
 ```
-
-However, there seems to be a problem with `treebink`.
-For certain variables, when a high number of bins is requested, the function returns more than the desired number of bins.
-Heike is going to look into this.
-
-She recently updated the function `treebink` to run using the tree package. Here are some comments from her about the code:
-
-"I've moved it from rpart to tree.
-I am not quite sure that the two packages are doing the exact same thing.
-They claim they do but they might be implemented a bit differently.
-What we are doing now is if there are too many splits, we look at the order in which the splits are made and roll back some of them.
-I haven't found a case that doesn't work, but obviously that doesn't show that there isn't any :)"
-
-I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
-This function is also included in the file `helper_functions.R`.
-The output from `mylime` can then be input into the `explain` function to obtain explanations.
-I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
-
-# Assessing Lime Explanations
-
-When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
-This led me to try applying LIME with a handful of input values.
-I also have tried running LIME with the tree based bins.
-Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation a handful of times.
-I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
-
-## Accuracy
-
-The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
-Each set of input values was only run once.
-
-```{r}
-# Read in the lime comparison data (the comparisons are run in the firearm examiner
-# paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
-```
-
-### Complex versus Simple Model Predictions
-
-The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
-The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and the type of bin.
-The points are colored by the $R^2$ value from the fit of the simple model.
-The lines are linear regression lines fit to the data points within a facet.
-We would hope that there is a linear relationship between these two variables.
-None of the cases show strong linear trends, but some are more linear than others.
-The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
-The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-The tree based bins do the best job with predictions above 0.6 for all number of bins.
-The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of simple model versus complex model predictions
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
-       color = "Simple Model R2")
-```
-
-The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and bin type.
-Again, the points are colored by the $R^2$ values from the simple model.
-All cases show a v-shaped trend.
-The low part of the v occurs around a random forest score of about 0.25.
-That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
-It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
-This is not the case with the quantile bins.
-It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of difference in predictions versus rfscore
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x = "Complex Model Prediction (RF Score)", 
-       y = "Difference Between Complex and Simple Model Predictions",
-       color = "Simple Model R2")
-```
-
-At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
-The plot below shows one example with the data from 3 equally spaced bins.
-There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
-This may be something to return to.
-
-```{r}
-# Plots of model "residuals"
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue") + 
-  labs(x = "Feature Value", y = "Residual")
-```
-
-### Comparing Input Values by MSE and $R^2$
-
-In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
-I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
-where $n$ is the number of observations in the testing dataset (within a set).
-Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
-
-```{r}
-# Summarizing lime results
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response, set) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set) %>%
-  ungroup()
-```
-
-The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
-
-```{r}
-# Plot of MSEs
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot below shows the average $R^2$ value for each of the input situations faceted by set.
-The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
-
-```{r}
-# Plot of R^2s
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-## Consistency with One Implementation
-
-I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
-I would like the features chosen to not depend on the number of bins used.
-Otherwise, it will be difficult to know how many bins to use.
-Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
-The code below creates a dataset that identifies the order in which the features are chosen by lime.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-chosen_features <- hamby224_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
-Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
-It calculates the degree of agreement in classification over that which would be expected by chance.
-A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
-
-I computed kappa for each bin situation separately for the top three features chosen.
-These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
-The values of kappa for the quantile bins are slight to fair agreement.
-For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
-
-```{r}
-# Computes and plots the values of kappa
-chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(set, bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, set, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  facet_grid( ~ set) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
-
-```{r fig.height = 8, fig.width = 8}
-# Plots the top feature for each case for each bin situation
-p <- ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
-```
-
-I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
-The plots are separated by set.
-
-```{r}
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-chosen_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-## Consistency Across Implementations
-
-In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
-I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-# Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
-  group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff),
-            ave_r2 = mean(model_r2))
-```
-
-The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins.
-The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
-
-```{r}
-# Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
-There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
-
-```{r}
-# Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-# Determine and plot the average and variability of the number levels for each case 
-# and input option
-hamby224_consistency <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, nbins, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels)) %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", as.character(nbins)))
-
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
-  geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was seven.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-# Determine the order that the features are chosen within a case and 
-# set of input options
-sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-```{r fig.width = 10}
-# Determine and plot the number of features chosen across the 10 reps within 
-# a set, input options, and feature level
-sensitivity_chosen %>%
-  group_by(set, situation, case) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "flood_tide", discrete = TRUE, reverse = FALSE)
-```
-
-I computed Fleiss's kappa for each sampling technique within a set across the 10 reps.
-These values are plotted below.
-Right now, the quantile methods and rfscore tree based bins seem to be the most consistent.
-However, I am not happy with some of the kappa values for cases where the next set of plots would suggest a high kappa, but the value is very low.
-I wonder if this a flaw in the Fleiss's kappa and would suggest that I use a different metric.
-
-```{r fig.width = 10}
-sensitivity_chosen %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", 
-                       nbins)) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(rep, feature) %>%
-  rename(rep1 = "1", rep2 = "2", rep3 = "3", rep4 = "4", rep5 = "5", 
-         rep6 = "6", rep7 = "7", rep8 = "8", rep9 = "9", rep10 = "10") %>%
-  group_by(set, situation, bin_situation, bins, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(rep1, rep2, rep3, rep4, rep5,
-                                          rep6, rep7, rep8, rep9, rep10), 
-                                        ncol = 10))$value,
-            nunique = length(unique(c(rep1, rep2, rep3, rep4, rep5, 
-                                      rep6, rep7, rep8, rep9, rep10)))) %>%
-  mutate(kappa = ifelse(is.nan(kappa), 1, kappa)) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) + 
-  geom_point() + 
-  geom_line(aes(linetype = chosen)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Sampling Technique", y = "Kappa", color = "Feature", linetype = "Feature")
-```
-
-The plots below need some work, but they contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-```
-
-I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
-I realized it would be helpful to view the relationship between the features and the random forest score.
-The plots below show the testing data with random forest score versus each of the features.
-The points are colored by the samesource variable.
-
-```{r}
-hamby224_test %>% 
-  select(rf_features, rfscore, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, rfscore, samesource) %>%
-  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
-  geom_point() + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Input Rankings
-
-In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
-The first table below is for set 1, and the second table below is for set 11.
-
-While using these to help me decide which input settings to use, I had a handful of thoughts:
-
-* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
-* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
-This makes me think that it would be okay to base my decision off of the results from the single rep.
-* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
-* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
-Right now, the feature plots from these explanations are not very helpful.
-I would need to adjust the intercept or something.
-
-Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
-
-```{r}
-joined_results <- hamby224_lime_results %>%
-  select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_results %>%
-              group_by(set, situation) %>%
-              summarise(mean_sensitivity_mse = mean(mse), 
-                        sd_sensitivity_mse = sd(mse)),
-            by = c("set", "situation")) %>%
-  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
-            by = c("set", "situation")) %>%
-  group_by(set) %>%
-  mutate(mse_order = dense_rank(mse),
-         ave_r2_order = dense_rank(desc(ave_r2)),
-         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
-         mean_nlevels_order = dense_rank(mean_nlevels))
-```
-
-```{r}
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 1") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 1")
-
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 11") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 11")
-```

### 2019-02-08 journals/04-new_binning_methods.Rmd
worked more on reorganizing journals

--- 2019-02-07 journals/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "04-new_binning_methods"
 author: "Katherine Goode"
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This journal contains the ideas for different binning methods that may be better than the ones currently implemented in the LIME package.
 
@@
 # Load libraries
-library(bulletr)
-library(caret)
-library(cowplot)
-library(furrr)
-library(future)
-library(gretchenalbrecht)
-library(irr)
-library(lime)
-library(plotly)
-library(purrr)
-library(randomForest)
-library(tidyverse)
 
@@
 source("../code/helper_functions.R")
-
-# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
-
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
 ```
 
-# Computation Issues
+# The Data
 
-## Plotly Dead Space Issue
+The cleaning training and testing datasets are loaded in below.
 
-I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
-
-```{r eval = FALSE}
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-# library(plotly) # version 4.8.0
-# library(ggplot2) # version 3.1.0
-# library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none")
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
+```{r}
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
 ```
 
-## Caret vs RandomForest
-
-The `lime` function in lime is set up to work with specific packages.
-For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
-I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
-It seemed to work.
-However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
-To do this, I used the iris data.
-The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
-Then the `lime` and `explain` functions are applied to both models.
-
-```{r}
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime::lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
-```
-
-To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
-I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
-Since lime is based on random permutations, I would not expect the values from the two models to be exact.
-However, I would like them to be close.
-The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
-We decided this seems like the two versions of the explanations are reasonably exchangeable.
-
-```{r}
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
-# Scatterplots of the randomForest versus caret variable values
-ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
-  geom_point() + 
-  facet_wrap( ~ variable, scales = "free") + 
-  geom_abline(intercept = 0, slope = 1)
-```
-
-## Comparing Furrr Times
-
-The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
-I ran and timed the code below to see how much faster the code was.
-Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
-
-```{r eval = FALSE}
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# Slow way
-plan(sequential)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 218.188 sec elapsed
-
-# Fast way
-plan(multiprocess)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 107.731 sec elapsed
-```
-
-# New Binning Methods
-
-## Subsampled Bins
+# Subsampled Bins
 
@@
 
-## Tree Based Bins
+# Tree Based Bins
 
@@
 
-# Assessing Lime Explanations
-
-When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
-This led me to try applying LIME with a handful of input values.
-I also have tried running LIME with the tree based bins.
-Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation a handful of times.
-I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
-
-## Accuracy
-
-The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
-Each set of input values was only run once.
+# Session Info
 
 ```{r}
-# Read in the lime comparison data (the comparisons are run in the firearm examiner
-# paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+sessionInfo()
 ```
-
-### Complex versus Simple Model Predictions
-
-The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
-The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and the type of bin.
-The points are colored by the $R^2$ value from the fit of the simple model.
-The lines are linear regression lines fit to the data points within a facet.
-We would hope that there is a linear relationship between these two variables.
-None of the cases show strong linear trends, but some are more linear than others.
-The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
-The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-The tree based bins do the best job with predictions above 0.6 for all number of bins.
-The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of simple model versus complex model predictions
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
-       color = "Simple Model R2")
-```
-
-The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and bin type.
-Again, the points are colored by the $R^2$ values from the simple model.
-All cases show a v-shaped trend.
-The low part of the v occurs around a random forest score of about 0.25.
-That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
-It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
-This is not the case with the quantile bins.
-It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of difference in predictions versus rfscore
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x = "Complex Model Prediction (RF Score)", 
-       y = "Difference Between Complex and Simple Model Predictions",
-       color = "Simple Model R2")
-```
-
-At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
-The plot below shows one example with the data from 3 equally spaced bins.
-There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
-This may be something to return to.
-
-```{r}
-# Plots of model "residuals"
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue") + 
-  labs(x = "Feature Value", y = "Residual")
-```
-
-### Comparing Input Values by MSE and $R^2$
-
-In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
-I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
-where $n$ is the number of observations in the testing dataset (within a set).
-Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
-
-```{r}
-# Summarizing lime results
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response, set) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set) %>%
-  ungroup()
-```
-
-The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
-
-```{r}
-# Plot of MSEs
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot below shows the average $R^2$ value for each of the input situations faceted by set.
-The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
-
-```{r}
-# Plot of R^2s
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-## Consistency with One Implementation
-
-I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
-I would like the features chosen to not depend on the number of bins used.
-Otherwise, it will be difficult to know how many bins to use.
-Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
-The code below creates a dataset that identifies the order in which the features are chosen by lime.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-chosen_features <- hamby224_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
-Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
-It calculates the degree of agreement in classification over that which would be expected by chance.
-A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
-
-I computed kappa for each bin situation separately for the top three features chosen.
-These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
-The values of kappa for the quantile bins are slight to fair agreement.
-For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
-
-```{r}
-# Computes and plots the values of kappa
-chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(set, bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, set, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  facet_grid( ~ set) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
-
-```{r fig.height = 8, fig.width = 8}
-# Plots the top feature for each case for each bin situation
-p <- ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
-```
-
-I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
-The plots are separated by set.
-
-```{r}
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-chosen_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-## Consistency Across Implementations
-
-In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
-I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-# Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
-  group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff),
-            ave_r2 = mean(model_r2))
-```
-
-The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins.
-The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
-
-```{r}
-# Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
-There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
-
-```{r}
-# Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-# Determine and plot the average and variability of the number levels for each case 
-# and input option
-hamby224_consistency <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, nbins, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels)) %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", as.character(nbins)))
-
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
-  geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was seven.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-# Determine the order that the features are chosen within a case and 
-# set of input options
-sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-```{r fig.width = 10}
-# Determine and plot the number of features chosen across the 10 reps within 
-# a set, input options, and feature level
-sensitivity_chosen %>%
-  group_by(set, situation, case) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "flood_tide", discrete = TRUE, reverse = FALSE)
-```
-
-I computed Fleiss's kappa for each sampling technique within a set across the 10 reps.
-These values are plotted below.
-Right now, the quantile methods and rfscore tree based bins seem to be the most consistent.
-However, I am not happy with some of the kappa values for cases where the next set of plots would suggest a high kappa, but the value is very low.
-I wonder if this a flaw in the Fleiss's kappa and would suggest that I use a different metric.
-
-```{r fig.width = 10}
-sensitivity_chosen %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", 
-                       nbins)) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(rep, feature) %>%
-  rename(rep1 = "1", rep2 = "2", rep3 = "3", rep4 = "4", rep5 = "5", 
-         rep6 = "6", rep7 = "7", rep8 = "8", rep9 = "9", rep10 = "10") %>%
-  group_by(set, situation, bin_situation, bins, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(rep1, rep2, rep3, rep4, rep5,
-                                          rep6, rep7, rep8, rep9, rep10), 
-                                        ncol = 10))$value,
-            nunique = length(unique(c(rep1, rep2, rep3, rep4, rep5, 
-                                      rep6, rep7, rep8, rep9, rep10)))) %>%
-  mutate(kappa = ifelse(is.nan(kappa), 1, kappa)) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) + 
-  geom_point() + 
-  geom_line(aes(linetype = chosen)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Sampling Technique", y = "Kappa", color = "Feature", linetype = "Feature")
-```
-
-The plots below need some work, but they contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-```
-
-I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
-I realized it would be helpful to view the relationship between the features and the random forest score.
-The plots below show the testing data with random forest score versus each of the features.
-The points are colored by the samesource variable.
-
-```{r}
-hamby224_test %>% 
-  select(rf_features, rfscore, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, rfscore, samesource) %>%
-  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
-  geom_point() + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Input Rankings
-
-In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
-The first table below is for set 1, and the second table below is for set 11.
-
-While using these to help me decide which input settings to use, I had a handful of thoughts:
-
-* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
-* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
-This makes me think that it would be okay to base my decision off of the results from the single rep.
-* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
-* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
-Right now, the feature plots from these explanations are not very helpful.
-I would need to adjust the intercept or something.
-
-Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
-
-```{r}
-joined_results <- hamby224_lime_results %>%
-  select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_results %>%
-              group_by(set, situation) %>%
-              summarise(mean_sensitivity_mse = mean(mse), 
-                        sd_sensitivity_mse = sd(mse)),
-            by = c("set", "situation")) %>%
-  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
-            by = c("set", "situation")) %>%
-  group_by(set) %>%
-  mutate(mse_order = dense_rank(mse),
-         ave_r2_order = dense_rank(desc(ave_r2)),
-         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
-         mean_nlevels_order = dense_rank(mean_nlevels))
-```
-
-```{r}
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 1") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 1")
-
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 11") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 11")
-```

### 2019-02-08 journals/05-applying_lime.Rmd
worked more on reorganizing journals

--- 2019-02-07 journals/03-applying_lime.Rmd
@@
 ---
-title: "03-applying_lime"
+title: "05-applying_lime"
 author: "Katherine Goode"
@@
 
+### One Implementation
+
+The code below applies the LIME algorithm to the bullet data for multiple different input cases.
+
 ```{r}
@@
 
+This code creates a dataframe of the bins to use in the app.
+
 ```{r}
@@
 ```
+
+This code combines the test data and the explanations.
 
@@
 
+This code creates a dataset with summaries of the explanations.
+
 ```{r}
@@
 
-# Plot of Bin Frequencies
+##### Plot of Bin Frequencies
 
@@
 ```
+
+### Multiple Implementations
+
+```{r}
+# Perform the sensitivity analysis if not already saved
+if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+
+  # Specify the number of reps and input cases
+  nreps = 10
+  noptions = 22
+
+  # Specify the inputs for the sensitivity analysis
+  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
+                                                         rep(FALSE, nreps * 2)),
+                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
+                                                        rep(TRUE, nreps * 12)),
+                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
+                                                rep(4, nreps * 2)),
+                                      use_density = c(rep(TRUE, nreps * 21), 
+                                                      rep(FALSE, nreps)),
+                                      bin_method = c(rep("quantile_bins", nreps * 5),
+                                                      rep("equally_spaced", nreps * 5),
+                                                      rep("tree", nreps * 10),
+                                                      rep("quantile_bins", nreps * 2)),
+                                      response = c(rep(NA, nreps * 10),
+                                                   rep("samesource", nreps * 5),
+                                                   rep("rfscore", nreps * 5),
+                                                   rep(NA, nreps * 2)))
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Run lime for the sensitivity analysis and organize the output
+  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
+             .f = run_lime, # run_lime is one of my helper functions
+             features = rf_features,
+             train = hamby173and252_train,
+             test = hamby224_test %>% 
+               arrange(case) %>% 
+               select(rf_features) %>% 
+               na.omit(),
+             rfmodel = as_classifier(rtrees),
+             label = "TRUE",
+             nfeatures = 3,
+             seed = FALSE) %>%
+    map_df(function(list) list$explain) %>%
+    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
+                            noptions)))
+
+  # Turn the input options into a dataframe to be saved
+  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(hamby224_sensitivity_inputs), 
+           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:(nreps * noptions)) %>%
+    select(case, bin_continuous:bin_method)
+
+  # Save the sensitivity inputs and outputs
+  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+
+}
+```
+
+```{r}
+# Join the sensativity outputs with the test data
+hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
+  full_join(hamby224_test %>% na.omit() %>% 
+                mutate(case = as.character(case)), by = "case") %>%
+    mutate(case = factor(case)) %>%
+    select(case, model_r2:feature_weight, bin_continuous:rep, 
+           set:land2, rfscore, samesource) %>%
+    mutate(diff = rfscore - model_prediction,
+         nbins = as.numeric(as.character(nbins)),
+         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                            sprintf("%.0f quantile", nbins),
+                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                   sprintf("%.0f equally spaced", nbins),
+                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                            response == "samesource",
+                                          sprintf("%.0f samesource tree", nbins),
+                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                            response == "rfscore",
+                                            sprintf("%.0f rfscore tree", nbins),
+                                            ifelse(bin_continuous == FALSE & 
+                                                   use_density == TRUE, 
+                                                   "kernel density", 
+                                                   "normal approximation"))))) %>%
+           fct_relevel("2 quantile", "3 quantile", "4 quantile",
+                       "5 quantile", "6 quantile", "2 equally spaced",
+                       "3 equally spaced", "4 equally spaced",
+                       "5 equally spaced", "6 equally spaced",
+                       "2 samesource tree", "3 samesource tree",
+                       "4 samesource tree", "5 samesource tree",
+                       "6 samesource tree")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
+                                  bin_continuous == TRUE,
+                                  "quantile",
+                                  ifelse(bin_method == "equally_spaced" & 
+                                         bin_continuous == TRUE,
+                                         "equally spaced", 
+                                         ifelse(bin_method == "tree" & 
+                                                bin_continuous == TRUE & 
+                                                response == "samesource",
+                                                "samesource tree", 
+                                                ifelse(bin_method == "tree" & 
+                                                       bin_continuous == TRUE & 
+                                                       response == "rfscore",
+                                                       "rfscore tree", 
+                                                       ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                       "kernel density", 
+                                                       "normal approximation")))))) %>%
+    mutate(bin_situation = factor(bin_situation))
+```
+
+# Session Info
+
+```{r}
+sessionInfo()
+```

### 2019-02-08 journals/06-assessing_lime_explanations.Rmd
worked more on reorganizing journals

--- 2019-02-07 journals/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "06-assessing_lime_explanations"
 author: "Katherine Goode"
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      fig.pos = "center")
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
 ```
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This journal compares the results from the different LIME implementations.
 
 ```{r}
-# Load libraries
-library(bulletr)
-library(caret)
-library(cowplot)
-library(furrr)
-library(future)
 library(gretchenalbrecht)
-library(irr)
-library(lime)
-library(plotly)
-library(purrr)
-library(randomForest)
 library(tidyverse)
 
-# Source functions
-source("../code/helper_functions.R")
-
-# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+# Load in the testing data (Hamby Data 224 Sets 1 and 11)
 hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
@@
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
+rf_features <- rownames(bulletr::rtrees$importance)
 ```
-
-# Computation Issues
-
-## Plotly Dead Space Issue
-
-I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
-
-```{r eval = FALSE}
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-# library(plotly) # version 4.8.0
-# library(ggplot2) # version 3.1.0
-# library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none")
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
-```
-
-## Caret vs RandomForest
-
-The `lime` function in lime is set up to work with specific packages.
-For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
-I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
-It seemed to work.
-However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
-To do this, I used the iris data.
-The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
-Then the `lime` and `explain` functions are applied to both models.
-
-```{r}
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime::lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
-```
-
-To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
-I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
-Since lime is based on random permutations, I would not expect the values from the two models to be exact.
-However, I would like them to be close.
-The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
-We decided this seems like the two versions of the explanations are reasonably exchangeable.
-
-```{r}
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
-# Scatterplots of the randomForest versus caret variable values
-ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
-  geom_point() + 
-  facet_wrap( ~ variable, scales = "free") + 
-  geom_abline(intercept = 0, slope = 1)
-```
-
-## Comparing Furrr Times
-
-The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
-I ran and timed the code below to see how much faster the code was.
-Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
-
-```{r eval = FALSE}
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# Slow way
-plan(sequential)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 218.188 sec elapsed
-
-# Fast way
-plan(multiprocess)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 107.731 sec elapsed
-```
-
-# New Binning Methods
-
-## Subsampled Bins
-
-One idea that I had to try to improve the lime explanations was to subsample from the training dataset before computing the quantiles.
-The proportion of observations with `samesource = FALSE` is very large in the training dataset, so that overwhelms the observations with `samesource = TRUE`.
-By subsampling, it might allow for better locations to bin the data.
-I wrote the code below to attempt to apply lime to a subsampled version of the training dataset.
-
-```{r eval = FALSE}
-# Code saved for future use for the sampling data
-
-# Create the data (with a set seed)
-set.seed(20181128)
-hamby173and252_train_sub <- hamby173and252_train %>%
-  filter(samesource == FALSE) %>%
-  slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
-  bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
-
-# Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
-
-# Apply lime to the subsampled training data with the specified input options
-hamby224_lime_explain_sub <- future_pmap(.l = as.list(hamby224_lime_inputs %>%
-                                                        select(-case)),
-                                         .f = run_lime, # run_lime is one of my helper functions
-                                         train = hamby173and252_train_sub %>% select(rf_features),
-                                         test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                         rfmodel = as_classifier(rtrees),
-                                         label = "TRUE",
-                                         nfeatures = 3,
-                                         seed = TRUE) %>%
-  mutate(training_data = factor("Subsampled"))
-
-# Separate the lime and explain function results from the subsampled data
-hamby224_lime_sub <- map(hamby224_lime_explain_sub, function(list) list$lime)
-hamby224_explain_sub <- map_df(hamby224_lime_explain_sub, function(list) list$explain)
-
-# Join the lime results from the full and subsampled training data
-hamby224_lime <- c(hamby224_lime_full, hamby224_lime_sub)
-hamby224_explain <- bind_rows(hamby224_explain_full, hamby224_explain_sub)
-```
-
-## Tree Based Bins
-
-Heike suggested the idea of using classification trees to choose the cutoffs for the lime bins.
-That is, the divisions in the tree could be used as the bin cuts.
-This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting.
-(MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
-
-Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree.
-The function is stored in the file   `helper_functions.R`.
-Here is an example using the function below with the predictor variable of ccf.
-
-```{r}
-# Example using treebink
-treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
-```
-
-However, there seems to be a problem with `treebink`.
-For certain variables, when a high number of bins is requested, the function returns more than the desired number of bins.
-Heike is going to look into this.
-
-She recently updated the function `treebink` to run using the tree package. Here are some comments from her about the code:
-
-"I've moved it from rpart to tree.
-I am not quite sure that the two packages are doing the exact same thing.
-They claim they do but they might be implemented a bit differently.
-What we are doing now is if there are too many splits, we look at the order in which the splits are made and roll back some of them.
-I haven't found a case that doesn't work, but obviously that doesn't show that there isn't any :)"
-
-I wrote the function `mylime`, which adds an option in the `lime` function from the LIME package to use Heike's function `treebink` to obtain tree based bins.
-This function is also included in the file `helper_functions.R`.
-The output from `mylime` can then be input into the `explain` function to obtain explanations.
-I was able to rerun all of the code for creating the `hamby224_test_explain` dataset with the explanations from the tree based bins included for 2 to 6 bins.
-
-# Assessing Lime Explanations
 
@@
 
-## Accuracy
+# Accuracy
 
@@
 
-## Consistency with One Implementation
+# Consistency with One Implementation
 
@@
 
-## Consistency Across Implementations
+# Consistency Across Implementations
 
@@
 I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
 
@@
 
-## Input Rankings
+# Input Rankings
 

### 2019-02-08 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked more on reorganizing journals

@@
 
-```{r}
-# Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("../data/hamby224_lime_inputs.rds")) {
-
-  # Specify the input options to use with lime
-  hamby224_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
-                                                  rep(FALSE, 2)),
-                               quantile_bins = c(rep(TRUE, 5), 
-                                                 rep(FALSE, 5), 
-                                                 rep(TRUE, 12)),
-                               nbins = c(rep(2:6, 4), 
-                                         rep(4, 2)),
-                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
-                               bin_method = c(rep("quantile_bins", 5),
-                                              rep("equally_spaced", 5),
-                                              rep("tree", 10),
-                                              rep("quantile_bins", 2)),
-                               response = c(rep(NA, 10), 
-                                            rep("samesource", 5), 
-                                            rep("rfscore", 5), 
-                                            rep(NA, 2)))
-
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Apply lime to the full training data with the specified input options
-  hamby224_lime_explain <- future_pmap(.l = hamby224_lime_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = TRUE)
-
-  # Separate the lime and explain function results from the full data
-  hamby224_lime <- map(hamby224_lime_explain, function(list) list$lime)
-  hamby224_explain <- map_df(hamby224_lime_explain, function(list) list$explain)
-
-  # Name the items in the lime list
-  names(hamby224_lime) <- map_chr(1:22, function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
-              hamby224_lime_inputs$bin_continuous[case],
-              hamby224_lime_inputs$quantile_bins[case],
-              hamby224_lime_inputs$nbins[case],
-              hamby224_lime_inputs$use_density[case],
-              hamby224_lime_inputs$bin_method[case],
-              hamby224_lime_inputs$response[case]))
-
-  # Turn the lime input options into a dataframe before saving it
-  hamby224_lime_inputs <- hamby224_lime_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_lime_inputs), 
-           dimnames = list(NULL, names(hamby224_lime_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:length(hamby224_lime_inputs$quantile_bins)) %>%
-    select(case, bin_continuous:response)
-
-  # Save the lime objects
-  saveRDS(hamby224_lime_inputs, "../data/hamby224_lime_inputs.rds")
-  saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
-  saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
-
-} else {
-
-  # Load in the lime objects
-  hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
-  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
-  hamby224_explain <- readRDS("../data/hamby224_explain.rds")
-
-}
-```
-
-```{r}
-# Create a dataframe with the bins
-if (!file.exists("../data/hamby224_bins.csv")) {
-
-  # Create a list a dataframes with the bin boundaries and bins 
-  # for the different evaluations of the lime functions
-  hamby224_bin_list <- map(hamby224_lime, create_bin_data)
-
-  # Save the bin boundaries and the bins as separate dataframes
-  hamby224_bin_boundaries <- map(hamby224_bin_list, function(m) m$boundaries)
-  hamby224_bins <- map(hamby224_bin_list, function(m) m$bins)
-
-  # Save the bin boundaries and bins
-  saveRDS(hamby224_bin_boundaries, "../data/hamby224_bin_boundaries.rds")
-  saveRDS(hamby224_bins, "../data/hamby224_bins.rds")
-
-} else {
-
-  # Load in the bin boundaries and bins
-  hamby224_bin_boundaries <- readRDS("../data/hamby224_bin_boundaries.rds")
-  hamby224_bins <- readRDS("../data/hamby224_bins.rds")
-
-}
-```
-
-```{r}
-# Create the test_explain combined data if the file does not already exist
-if(!file.exists("../data/hamby224_test_explain.rds")) {
-
-  # Join the data and the explanations and edit and add additional variables
-  # Create the feature bin labels using my function "bin_labeller"
-  hamby224_test_explain <- hamby224_test %>%
-    mutate(case = as.character(case)) %>%
-    full_join(hamby224_explain, by = "case") %>%
-    mutate(case = factor(case),
-           feature_desc = factor(feature_desc),
-           feature_bin = pmap_chr(list(feature = feature, 
-                                  feature_value = feature_value,
-                                  b_c = bin_continuous,
-                                  q_b = quantile_bins,
-                                  n_b = nbins,
-                                  u_d = use_density,
-                                  b_m = bin_method,
-                                  r_v = response),
-                            .f = bin_labeller, # bin_labeller is one of my helper functions
-                            bin_data = hamby224_bin_boundaries,
-                            case_info = hamby224_lime_inputs)) %>%
-    mutate(feature = factor(feature),
-           nbins = factor(nbins),
-           feature_number = readr::parse_number(feature_desc),
-           strictly_less = FALSE) %>%
-    arrange(nbins)
-
-  # Finish creating the strictly less than variable
-  hamby224_test_explain$strictly_less[grep("< ", hamby224_test_explain$feature_desc)] <- TRUE
-
-  # Reorder the variables of feature_desc and feature_bin for plotting purposes and
-  # create new variables of situation and bin_situation
-  hamby224_test_explain <- hamby224_test_explain %>%
-    mutate(feature_desc = reorder(feature_desc, strictly_less),
-           feature_desc = reorder(feature_desc, feature_number),
-           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
-    mutate(nbins = as.numeric(as.character(nbins)),
-           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                              sprintf("%.0f quantile", nbins),
-                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                     sprintf("%.0f equally spaced", nbins),
-                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                              response == "samesource",
-                                            sprintf("%.0f samesource tree", nbins),
-                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                              response == "rfscore",
-                                              sprintf("%.0f rfscore tree", nbins),
-                                              ifelse(bin_continuous == FALSE & 
-                                                     use_density == TRUE, 
-                                                     "kernel density", 
-                                                     "normal approximation"))))) %>%
-             fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                         "5 quantile", "6 quantile", "2 equally spaced",
-                         "3 equally spaced", "4 equally spaced",
-                         "5 equally spaced", "6 equally spaced",
-                         "2 samesource tree", "3 samesource tree",
-                         "4 samesource tree", "5 samesource tree",
-                         "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation)) %>%
-    select(situation, bin_situation, bin_continuous:response, case:feature_desc,
-           feature_bin:strictly_less, data, prediction)
-
-  # Save the combined test and explain data
-  saveRDS(hamby224_test_explain, "../data/hamby224_test_explain.rds")
-
-} else {
-
-  # Load in the data
-  hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-}
-```
-
-```{r}
-# Create the lime comparison data if the file does not already exist
-if(!file.exists("../data/hamby224_lime_comparisons.rds")) {
-
-  # Create a data frame with the interesting information relating to the different
-  # evaluations of lime and compute the difference and mean between the rf and rr
-  # model predictions
-  hamby224_lime_comparisons <- hamby224_test_explain %>%
-    select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method, response) %>%
-    slice(1) %>%
-    ungroup() %>%
-    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, response, 
-           nbins, use_density, set, case, rf_features, rfscore, model_prediction, model_r2) %>%
-    mutate(diff = rfscore - model_prediction,
-           mean = (rfscore + model_prediction) / 2)
-
-  # Save the lime comparison data frame
-  saveRDS(hamby224_lime_comparisons, "../data/hamby224_lime_comparisons.rds")
-
-} else {
-
-  # Load in the lime comparison data frame
-  hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
-
-}
-```
-
 ## Development of Shiny App for Visualizing the LIME Explanations

### 2019-02-09 journals/05-applying_lime.Rmd
worked more on journals...

@@
 
-##### Plot of Bin Frequencies
-
-Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
-This one has been created from the lime explanations with 2 quantile bins.
-It includes all three of the chosen features for each case in the testing dataset.
-For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
-
-```{r fig.height = 10}
-# Plot of fequency for each bin division for 2 quantile bins
-hamby224_test_explain %>%
-  filter(situation == "2 quantile") %>%
-  ggplot(aes(x = feature_desc)) +
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
-
 ### Multiple Implementations
@@
     mutate(bin_situation = factor(bin_situation))
+
+write.csv(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.csv",
+          row.names = FALSE)
 ```

### 2019-02-09 journals/06-assessing_lime_explanations.Rmd
worked more on journals...

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
+                      cache = TRUE)
 ```
@@
 
+hamby224_sensitivity_joined <- read.csv("../data/hamby224_sensitivity_joined.csv")
+
 # Obtain features used when fitting the rtrees random forest
@@
 I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
+
+# Visualization Ideas
+
+Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
+This one has been created from the lime explanations with 2 quantile bins.
+It includes all three of the chosen features for each case in the testing dataset.
+For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
+
+```{r fig.height = 10}
+# Plot of fequency for each bin division for 2 quantile bins
+hamby224_test_explain %>%
+  filter(situation == "2 quantile") %>%
+  ggplot(aes(x = feature_desc)) +
+  geom_bar() +
+  coord_flip() + 
+  facet_grid(set ~ .)
+```
 
@@
 
-```{r fig.height = 8, fig.width = 10}
+```{r fig.height = 8, fig.width = 10, eval = FALSE}
 hamby224_sensitivity_joined %>%

### 2019-02-09 papers/An Assessment of LIME Explanations from a Random Forest Model.Rmd
worked more on journals...

---
title: "An Assessment of LIME Explanations from a Random Forest Models"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
                      fig.pos = "center")
```

### 2019-02-11 journals/06-assessing_lime_explanations.Rmd
finished cleaning journals

@@
 # Plots the top feature for each case for each bin situation
-p <- ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
+ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
   geom_tile() + 
@@
 
-```{r fig.height = 8, fig.width = 10, eval = FALSE}
+```{r fig.height = 12, fig.width = 10}
 hamby224_sensitivity_joined %>%
@@
   ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
+  arrange(situation, desc(nlevels), case, feature) %>%
+  mutate(order = rep(rep(1:length(levels(factor(case))), each = 10), 22)) %>%
   ggplot(aes(x = order, fill = feature)) + 
@@
   coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
+  facet_wrap(situation ~ ., ncol = 4, scales = "free_y") +
   theme(legend.position = "bottom",

### 2019-02-11 journals/04-lime_algorithm_and_proposed_methods.Rmd
moved lime algorithm to journal 04

--- 2019-01-30 journal/applying LIME to bullet data journal.Rmd
@@
 ---
-title: "Applying LIME to Bullet Data Research Journal"
+title: "04-lime_algorithm_and_proposed_methods"
 author: "Katherine Goode"
@@
 
-I decided to start a journal to keep track of the work I am doing in regards to applying LIME to the Hamby bullet data.
-I want a place to store my work to use for future purposes and where I do not feel the need to "perfect" code.
-I am hoping that this will be a place where I can write drafts of code and create first versions of graphics.
-Then I can clean up and organize the code when I write the papers.
-
-Prior to this journal, I had been working on all of my ideas in the R markdown document for the firearm examiner paper, but now I am going to transfer a lot of that code to this journal.
-I am transferring them here now.
-Later I will move the necessary parts to the paper.
+This journal contains a draft of the LIME algorithm and ideas for different binning methods that may be better than the ones currently implemented in the LIME package.
 
@@
 source("../code/helper_functions.R")
-
-# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
-
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(rtrees$importance)
 ```
 
-# Plots of Features
+# The Data
 
-## Distributions by `samesource`
-
-I created the following two plots of the training data as suggested by Heike.
-The histograms below show the distributions of the features used in the random forest `rtrees`.
-The histograms are filled by the `samesource` variable, which is the truth of whether or not the comparison is from the same barrel and land.
-The default histograms make it hard to compare the distributions of the matches and non-matches since there are many more comparisons that have `samesource == FALSE`.
+The cleaning training and testing datasets are loaded in below.
 
 ```{r}
-# Create plots of the feature distributions colored by samesource for the training data
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
-       title = "Hamby 173 and 252 Training Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-By setting `position = "fill"` in the `geom_histogram` function, it is easier to compare the matches and non-matches.
-<span style="color:teal"> These plots could be used in the future to hand select the bins for lime.
-Additionally, fitting a logistic regression to this data could also be used to determine the LC50, LC10, ad LC90, which could be used as the bins for lime.
-</span>
-
-```{r}
-# Create plots of the feature distributions colored by samesource for the training data
-# using the position = "fill" option
-hamby173and252_train %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 30) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
-       title = "Hamby 173 and 252 Training Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-The plots below have the same structure, but they are created with the Hamby 224 testing data.
-I chose to not separate the testing data by sets, but this is something that could be done later if necessary.
-
-```{r}
-# Create plots of the feature distributions colored by samesource for the testing data
-hamby224_test %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(bins = 15) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-
-# Create plots of the feature distributions colored by samesource for the testing 
-# data using the position = "fill" option
-hamby224_test %>% 
-  select(rf_features, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, samesource) %>%
-  ggplot(aes(x = value, fill = samesource)) + 
-  geom_histogram(position = "fill", bins = 15) + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Correlations
-
-I made these plots to look at the correlation between features in the training data within the TRUE and FALSE cases of samesource.
-The features are highly correlated for the match comparisons.
-It is clear that the variables are more correlated with the match comparisons than the non-match comparisons.
-However, there are still some variables that are relatively highly correlation with the non-match comparisons.
-
-```{r fig.height = 4, fig.width = 9}
-# Create a correlation heatmap of the match comparisons in the training data
-cor_match <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == TRUE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Match Comparisons")
-
-# Create a correlation heatmap of the non-match comparisons in the training data
-cor_nonmatch <- hamby173and252_train %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == FALSE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") +
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Non-Match Comparisons")
-
-# Create a title for the panel of plots
-cor_title <- ggdraw() +
-  draw_label("Correlation of Feature Variables in the Training Data", 
-             fontface = "bold", 
-             size = 16,
-             x = 0.5,
-             hjust = 0.5)
-
-# Create a joined legend for the panel of plots
-cor_legend <- get_legend(cor_match + theme(legend.position = "right"))
-
-# Create the panel of plots
-plot_grid(cor_title, 
-          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
-          ncol = 1,
-          rel_heights = c(0.25, 3))
-```
-
-The plots below show the correlations for the testing data. The patterns in the plots look really similar to ones of the training data.
-
-```{r fig.height = 4, fig.width = 9}
-# Create a correlation heatmap of the match comparisons in the training data
-cor_match_test <- hamby224_test %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == TRUE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Match Comparisons")
-
-# Create a correlation heatmap of the non-match comparisons in the training data
-cor_nonmatch_test <- hamby224_test %>%
-  select(rf_features, samesource) %>%
-  filter(samesource == FALSE) %>%
-  select(-samesource) %>%
-  cor() %>%
-  reshape2::melt() %>%
-  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms")),
-         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
-                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
-  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
-  geom_tile() + 
-  scale_fill_gradient2(limits = c(-1, 1)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") +
-  labs(x = "", y = "", fill = "Correlation",
-       title = "Non-Match Comparisons")
-
-# Create a title for the panel of plots
-cor_title_test <- ggdraw() +
-  draw_label("Correlation of Feature Variables in the Testing Data", 
-             fontface = "bold", 
-             size = 16,
-             x = 0.5,
-             hjust = 0.5)
-
-# Create a joined legend for the panel of plots
-cor_legend_test <- get_legend(cor_match_test + theme(legend.position = "right"))
-
-# Create the panel of plots
-plot_grid(cor_title_test, 
-          plot_grid(cor_match_test, cor_nonmatch_test, cor_legend_test, 
-                    ncol = 3, rel_widths = c(2, 2, 0.5)),
-          ncol = 1,
-          rel_heights = c(0.25, 3))
-```
-
-# Visualizations of Explanations
-
-Heike made a plot with the structure of the one below when we began with the default settings of `lime`.
-This one has been created from the lime explanations with 2 quantile bins.
-It includes all three of the chosen features for each case in the testing dataset.
-For both sets, the cutoff of 0.275 < ccf occurs the most frequently.
-
-```{r fig.height = 10}
-# Plot of fequency for each bin division for 2 quantile bins
-hamby224_test_explain %>%
-  filter(situation == "2 quantile") %>%
-  ggplot(aes(x = feature_desc)) +
-  geom_bar() +
-  coord_flip() + 
-  facet_grid(set ~ .)
-```
-
-The plot below is the model for the one that will be used in the app for exploring the `lime` explanations from the bullet matching data. This is the data from set 1 of the testing dataset.
-
-```{r}
-# Heatmap of rfscore for each comparison in set 1
-hamby224_test %>%
-  filter(set == "Set 1") %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
-             text = paste('Bullets Compared: ', bullet1, "-", land1, 
-                          "vs", bullet2, "-", land2,
-                          '\nRandom Forest Score: ', 
-                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
-  geom_tile(aes(fill = rfscore)) +
-  facet_grid(bullet2 ~ bullet1, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank()) +
-  labs(x = "", y = "", fill = "RF Score")
-```
-
-I also wrote some code to create the above plot using individual plots instead of facets. This is included below. (It is a bit outdated compared to my newer version of the plot.)
-
-```{r}
-# Code for creating the heatmap plots using individual plots
-p1 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 1") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p2 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p3 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p4 <- ggplot() + geom_blank() + theme_classic()
-
-p5 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Known 2") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p6 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
-  theme(legend.position = "none")
-
-p7 <- ggplot() + geom_blank() + theme_classic()
-
-p8 <- ggplot() + geom_blank() + theme_classic()
-
-p9 <- hamby224_test %>%
-  filter(set == "Set 1", bullet1 == "Questioned", bullet2 == "Questioned") %>%
-  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
-  distinct() %>%
-  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
-  geom_tile(aes(fill = rfscore)) +
-  #facet_grid(bullet1 ~ bullet2, scales = "free") +
-  theme_minimal() +
-  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
-  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
-
-style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, 
-              nrows = 3, 
-              titleX = TRUE, 
-              titleY = TRUE, 
-              margin = 0.03),
-      hoverinfo = "skip",
-      traces = 7)
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
 ```
@@
 
-# Computation Issues
+# Proposed Bin Creation Methods
 
-## Plotly Dead Space Issue
-
-I found an issue with plotly. Below is the reproducible example that I sent to Carson. He was able to fix the issue, so the example below no longer has the problem.
-
-```{r eval = FALSE}
-# Example with Plotly to show dead space in heatmap
-
-# System information
-# R version 3.5.1 (2018-07-02)
-# Platform: x86_64-apple-darwin15.6.0 (64-bit)
-# Running under: macOS  10.14
-
-# Load libraries
-# library(plotly) # version 4.8.0
-# library(ggplot2) # version 3.1.0
-# library(tidyr) # version 0.8.2
-
-# Example from: https://plot.ly/r/heatmaps/ -------------------------------------------
-
-# Create dataset
-m <- matrix(rnorm(9), nrow = 3, ncol = 3)
-
-# Create plotly heatmap - no dead space to be found
-plot_ly(x = c("a", "b", "c"), y = c("d", "e", "f"), z = m, type = "heatmap")
-
-# Example using ggplotly function -----------------------------------------------------
-
-# Reshape the data for ggplot
-m_gathered <- data.frame(m) %>%
-  gather(key = column) %>%
-  mutate(row = factor(rep(c("X1", "X2", "X3"), 3))) %>%
-  select(column, row, value)
-
-# Create ggplot heatmap
-p <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile()
-
-# Apply plotly to ggplot heatmap - dead space in the middle of (X1, X1)
-ggplotly(p)
-
-# Carson's suggested fix for now
-style(ggplotly(p), hoverinfo = "skip", traces = 2)
-
-# Create ggplot heatmap without a legend
-p_nolegend <- ggplot(m_gathered, aes(x = column, y = row, fill = value)) +
-  geom_tile() +
-  theme(legend.position = "none")
-
-# Apply plotly to ggplot heatmap - the dead space is gone!
-ggplotly(p_nolegend)
-```
-
-## Caret vs RandomForest
-
-The `lime` function in lime is set up to work with specific packages.
-For example, `lime` works with a random forest model fit using the caret package, but it is not set up to work with a random forest fit using the randomForest package.
-I found a suggestion to apply the function `as_classifier` from the lime package to a model fit using randomForest in order for the `lime` function to accept the model.
-It seemed to work.
-However, I wanted to compare the lime results from a model fit using caret and the same model fit using randomForest.
-To do this, I used the iris data.
-The code below goes through the process of fitting the two models (`rf_model` and `caret_model`).
-Then the `lime` and `explain` functions are applied to both models.
-
-```{r}
-# Code for comparing the output from LIME when the model is 
-# fit with caret and randomForest
-# Last Updated: 2018/11/13
-
-## Set up -----------------------------------------------------------------------------
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-## LIME with caret --------------------------------------------------------------------
-
-# Create Random Forest model on iris data
-caret_model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-caret_explainer <- lime::lime(iris_train, caret_model)
-
-# Explain new observation
-caret_explanation <- lime::explain(iris_test, caret_explainer, n_labels = 1, n_features = 4)
-
-## LIME with randomForest -------------------------------------------------------------
-
-rf_model <- randomForest(iris_train, iris_lab)
-
-# Create an explainer object
-rf_explainer <- lime::lime(iris_train, model = as_classifier(rf_model))
-
-# Explain new observation
-rf_explanation <- lime::explain(iris_test, rf_explainer, n_labels = 1, n_features = 4)
-```
-
-To compare the lime explanations from the two models, I extracted the $R^2$ value from the simple model, the simple model intercept, the simple model prediction, the feature values, and the feature weights from both explanation datasets.
-I computed the MSE between each of these values from the two models, and I plotted them on a scatterplot.
-Since lime is based on random permutations, I would not expect the values from the two models to be exact.
-However, I would like them to be close.
-The MSEs are all close to zero, and the plots suggest that the values do an okay job of following the 1-1 line.
-We decided this seems like the two versions of the explanations are reasonably exchangeable.
-
-```{r}
-## Comparisons -----------------------------------------------------------------------
-
-# Grab the numeric caret explanation variables of interest
-caret_numeric <- caret_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "caret_value")
-
-# Grab the numeric randomForest explanation variables of interest
-rf_numeric <- rf_explanation %>%
-  select(model_r2, model_intercept, model_prediction, feature_value, feature_weight) %>%
-  gather(key = "variable", value = "rf_value")
-
-# Join the two
-lime_numeric <- caret_numeric %>%
-  mutate(rf_value = rf_numeric$rf_value, 
-         variable = factor(variable))
-
-# Look at the MSEs for the variables
-lime_numeric %>%
-  group_by(variable) %>%
-  summarise(MSE = sum((caret_value - rf_value)^2) / dim(lime_numeric)[1])
-
-# Scatterplots of the randomForest versus caret variable values
-ggplot(lime_numeric, aes(x = caret_value, y = rf_value)) + 
-  geom_point() + 
-  facet_wrap( ~ variable, scales = "free") + 
-  geom_abline(intercept = 0, slope = 1)
-```
-
-## Comparing Furrr Times
-
-The amount of time it took me to run the explain function with all of my input options was getting pretty long.
-Heike suggest that I use the furrr package, which implements the purrr functions using the speed of the future package.
-I ran and timed the code below to see how much faster the code was.
-Using the multiprocess option, the code took about half the amount of time to run (from 218.188 seconds to 108.731 seconds)!
-
-```{r eval = FALSE}
-# It took about half the time when using the function from furrr!
-
-library(tictoc)
-library(future)
-library(furrr)
-
-# Slow way
-plan(sequential)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 218.188 sec elapsed
-
-# Fast way
-plan(multiprocess)
-tictoc::tic()
-sensitivity_explain <- future_pmap(.l = as.list(sensitivity_inputs %>% 
-                                                         select(-case)),
-                                          .f = run_lime, # run_lime is one of my helper functions
-                                          train = hamby173and252_train %>% select(rf_features),
-                                          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
-                                          rfmodel = as_classifier(rtrees),
-                                          label = "TRUE",
-                                          nfeatures = 3,
-                                          seed = FALSE)
-tictoc::toc()
-# 107.731 sec elapsed
-```
-
-# New Binning Methods
-
-## Subsampled Bins
+### Subsampled Bins
 
@@
 
-## Tree Based Bins
+### Tree Based Bins
 
@@
 
-# Assessing Lime Explanations
-
-When we began looking at the explanations from `lime` with the default settings, we did not think that they made sense.
-This led me to try applying LIME with a handful of input values.
-I also have tried running LIME with the tree based bins.
-Additionally, since LIME is based on random permutations, I was curious to know how consistent the results were.
-This led me to try running each implementation a handful of times.
-I have attempted to evaluate these results by both considering the accuracy and consistency of the results.
-
-## Accuracy
-
-The figures in this section are created from the implementations of LIME on set 1 from the training data for the input options of 2 to 6 quantile bins, 2 to 6 equally spaced bins, 2 to 6 tree based bins, kernel density estimation, and normal distribution approximation.
-Each set of input values was only run once.
+# Session Info
 
 ```{r}
-# Read in the lime comparison data (the comparisons are run in the firearm examiner
-# paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+sessionInfo()
 ```
-
-### Complex versus Simple Model Predictions
-
-The plot below compares the predictions from the "simple model" (the ridge regression model) and the "complex model" (the random forest `rtrees`) on the x-axis from the lime implementations with bin estimation (`bin_continuous == TRUE`).
-The simple model predictions are on the y-axis, and the complex model predictions are on the x-axis.
-The plot is faceted by number of bins and the type of bin.
-The points are colored by the $R^2$ value from the fit of the simple model.
-The lines are linear regression lines fit to the data points within a facet.
-We would hope that there is a linear relationship between these two variables.
-None of the cases show strong linear trends, but some are more linear than others.
-The quantile bins show that the simple model never makes a prediction over 0.6, whereas the random forest model can have predictions of up to 1.
-The equally spaced bins do have probabilities that exceed 0.6, but only with 3 and 6 bins.
-The tree based bins do the best job with predictions above 0.6 for all number of bins.
-The tree bins also seem to group the simple model predictions into two categories (probably based on the samesource variable).
-I noticed that within the facets, the points are in mostly horizontal strips, and the number of strips is about the same as the number of bins from the lime implementation.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of simple model versus complex model predictions
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = model_prediction)) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  stat_smooth(method = "lm", se = FALSE, size = 0.5) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  labs(x = "Complex Model Prediction (RF Score)", y = "Simple Model Prediction",
-       color = "Simple Model R2")
-```
-
-The plot below shows the absolute value of the difference between the complex model prediction and the simple model prediction versus the complex model prediction.
-The points are faceted by number of bins and bin type.
-Again, the points are colored by the $R^2$ values from the simple model.
-All cases show a v-shaped trend.
-The low part of the v occurs around a random forest score of about 0.25.
-That is, the simple model is most accurately portraying the complex model predictions around the random forest score of 0.25.
-It gets worse near the extremes.
-However, it is interesting to note that with the equally spaced bins and the tree based bins, the absolute difference decreases near 1.
-This is not the case with the quantile bins.
-It appears that the equally spaced bins and tree based bins are able to make slightly better predictions than the quantile bins when there is a high probability of a match.
-
-```{r fig.height = 8, fig.width = 10}
-# Plot of difference in predictions versus rfscore
-hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore), set == "Set 1", bin_continuous == TRUE) %>%
-  ggplot(aes(x = rfscore, y = abs(diff))) + 
-  geom_point(aes(color = model_r2)) + 
-  facet_grid(bin_situation ~ nbins) + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x = "Complex Model Prediction (RF Score)", 
-       y = "Difference Between Complex and Simple Model Predictions",
-       color = "Simple Model R2")
-```
-
-At some point, I got the idea in my head that it would be interesting to look at the "residuals" (difference in complex and simple model predictions) by feature.
-The plot below shows one example with the data from 3 equally spaced bins.
-There are clear trends in the plots, but I am not quite sure what to make of this or how to use it.
-This may be something to return to.
-
-```{r}
-# Plots of model "residuals"
-hamby224_lime_comparisons %>%
-  filter(quantile_bins == FALSE, bin_method == "equally_spaced", nbins == "3", set == "Set 1") %>%
-  select(rf_features, diff, -case) %>%
-  gather(key = feature, value = feature_value, rf_features) %>%
-  select(feature, feature_value, diff) %>%
-  ggplot(aes(x = feature_value, y = diff)) + 
-  geom_point() + 
-  facet_wrap(~ feature, scales = "free") + 
-  geom_hline(yintercept = 0, color = "blue") + 
-  labs(x = "Feature Value", y = "Residual")
-```
-
-### Comparing Input Values by MSE and $R^2$
-
-In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
-I defined the mean squared error as
-  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
-where $n$ is the number of observations in the testing dataset (within a set).
-Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
-
-```{r}
-# Summarizing lime results
-hamby224_lime_results <- hamby224_lime_comparisons %>%
-  filter(!is.na(rfscore)) %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response, set) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  arrange(set) %>%
-  ungroup()
-```
-
-The plot below shows the mean squared errors for each of the input situations faceted by set.
-In both cases, the mean squared error with 3 equally spaced bins is low, and the MSE for the tree binning cases are also low.
-
-```{r}
-# Plot of MSEs
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot below shows the average $R^2$ value for each of the input situations faceted by set.
-The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
-The $R^2$ values for 3 equally spaced bins are in the middle, and the $R^2$ values for all of the tree based bins are the lowest.
-
-```{r}
-# Plot of R^2s
-hamby224_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-## Consistency with One Implementation
-
-I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
-I would like the features chosen to not depend on the number of bins used.
-Otherwise, it will be difficult to know how many bins to use.
-Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
-The code below creates a dataset that identifies the order in which the features are chosen by lime.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-chosen_features <- hamby224_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
-Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
-It calculates the degree of agreement in classification over that which would be expected by chance.
-A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
-
-I computed kappa for each bin situation separately for the top three features chosen.
-These values are plotted below for each set.
-For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins.
-The values of kappa for the quantile bins are slight to fair agreement.
-For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.
-
-```{r}
-# Computes and plots the values of kappa
-chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(set, bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, set, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  facet_grid( ~ set) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below.
-
-```{r fig.height = 8, fig.width = 8}
-# Plots the top feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
-  geom_tile() + 
-  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
-```
-
-I also created the plot below to visually assess the proportions of cases within a bin situation and level of feature chosen by lime (first, second, or third) that have 1 to 5 chosen features.
-The plots are separated by set.
-
-```{r}
-# Plots the proportions of number of top features chosen across number of bins for a case
-# within a binning method
-chosen_features %>%
-  group_by(set, case, bin_situation) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = bin_situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-## Consistency Across Implementations
-
-In order to assess how variable the LIME results are, I ran each of the input situations 10 times.
-I wanted to look at the variability of the MSE for each situation, and I wanted to see how consistent the choice of selected features is by LIME.
-
-```{r}
-# Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
-
-  # Specify the number of reps and input cases
-  nreps = 10
-  noptions = 22
-
-  # Specify the inputs for the sensitivity analysis
-  hamby224_sensitivity_inputs <- list(bin_continuous = c(rep(TRUE, nreps * 20),
-                                                         rep(FALSE, nreps * 2)),
-                                      quantile_bins = c(rep(c(TRUE, FALSE), each = nreps * 5), 
-                                                        rep(TRUE, nreps * 12)),
-                                      nbins = c(rep(rep(2:6, each = nreps), 4), 
-                                                rep(4, nreps * 2)),
-                                      use_density = c(rep(TRUE, nreps * 21), 
-                                                      rep(FALSE, nreps)),
-                                      bin_method = c(rep("quantile_bins", nreps * 5),
-                                                      rep("equally_spaced", nreps * 5),
-                                                      rep("tree", nreps * 10),
-                                                      rep("quantile_bins", nreps * 2)),
-                                      response = c(rep(NA, nreps * 10),
-                                                   rep("samesource", nreps * 5),
-                                                   rep("rfscore", nreps * 5),
-                                                   rep(NA, nreps * 2)))
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
-
-  # Run lime for the sensitivity analysis and organize the output
-  hamby224_sensitivity_outputs <- future_pmap(.l = hamby224_sensitivity_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = rf_features,
-             train = hamby173and252_train,
-             test = hamby224_test %>% 
-               arrange(case) %>% 
-               select(rf_features) %>% 
-               na.omit(),
-             rfmodel = as_classifier(rtrees),
-             label = "TRUE",
-             nfeatures = 3,
-             seed = FALSE) %>%
-    map_df(function(list) list$explain) %>%
-    mutate(rep = factor(rep(rep(1:nreps, each = dim(hamby224_test %>% na.omit())[1] * 3),
-                            noptions)))
-
-  # Turn the input options into a dataframe to be saved
-  hamby224_sensitivity_inputs <- hamby224_sensitivity_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(hamby224_sensitivity_inputs), 
-           dimnames = list(NULL, names(hamby224_sensitivity_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:(nreps * noptions)) %>%
-    select(case, bin_continuous:bin_method)
-
-  # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
-
-} else {
-
-  # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
-
-}
-```
-
-```{r}
-# Join the sensativity outputs with the test data
-hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
-  full_join(hamby224_test %>% na.omit() %>% 
-                mutate(case = as.character(case)), by = "case") %>%
-    mutate(case = factor(case)) %>%
-    select(case, model_r2:feature_weight, bin_continuous:rep, 
-           set:land2, rfscore, samesource) %>%
-    mutate(diff = rfscore - model_prediction,
-         nbins = as.numeric(as.character(nbins)),
-         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                            sprintf("%.0f quantile", nbins),
-                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                   sprintf("%.0f equally spaced", nbins),
-                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "samesource",
-                                          sprintf("%.0f samesource tree", nbins),
-                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                            response == "rfscore",
-                                            sprintf("%.0f rfscore tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation"))))) %>%
-           fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                       "5 quantile", "6 quantile", "2 equally spaced",
-                       "3 equally spaced", "4 equally spaced",
-                       "5 equally spaced", "6 equally spaced",
-                       "2 samesource tree", "3 samesource tree",
-                       "4 samesource tree", "5 samesource tree",
-                       "6 samesource tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "samesource",
-                                                "samesource tree", 
-                                                ifelse(bin_method == "tree" & 
-                                                       bin_continuous == TRUE & 
-                                                       response == "rfscore",
-                                                       "rfscore tree", 
-                                                       ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation")))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-```
-
-```{r}
-# Code for organizing the sensitivity analysis results
-hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
-  group_by(set, rep, situation, bin_situation, nbins) %>%
-  summarise(mse = sum((diff)^2) / length(diff),
-            ave_r2 = mean(model_r2))
-```
-
-The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set.
-There does not appear to be much variation for most of the cases.
-The largest amount of variation occurs with 4 and 5 equally spaced bins.
-There is moderate variability for 3 equally spaced bins.
-The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.
-
-```{r}
-# Plots the MSEs from the sensativity analysis
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = mse)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set.
-There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.
-
-```{r}
-# Plots the average R^2 value from the sensativity analysis 
-hamby224_sensitivity_results %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
-                       "other", as.character(nbins))) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2)) + 
-  geom_boxplot(aes(color = bin_situation)) +
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-To assess the consistency of the results, I determined the number of different features chosen by LIME as the top feature within a test case across the 10 replicates.
-I then computed the average number of different top features chosen by LIME within a input situations for each set.
-The plot below contains these values shown as the dots.
-The error bars represent one standard deviation above and below the mean.
-Note that the number of levels cannot go below 1, but the error bars go below 1.
-I have decided to ignore this for now, but I would need to come up with a better representation if I used this for something.
-
-There are a handful of situations with a mean near one and very little variation.
-However, the largest mean is around 2, which is not very high.
-This seems to suggest that LIME is relatively consistent across runs.
-
-```{r}
-# Determine and plot the average and variability of the number levels for each case 
-# and input option
-hamby224_consistency <- hamby224_sensitivity_joined %>%
-  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(set, situation, nbins, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins, case) %>%
-  summarise(nlevels = length(levels(factor(feature))),
-            count = n()) %>%
-  ungroup() %>%
-  group_by(set, situation, bin_situation, nbins) %>%
-  summarise(mean_nlevels = mean(nlevels),
-            sd_nlevels = sd(nlevels),
-            upper = mean(nlevels) + sd(nlevels),
-            lower = mean(nlevels) - sd(nlevels),
-            max = max(nlevels),
-            min = min(nlevels)) %>%
-  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
-                       "other", as.character(nbins)))
-
-hamby224_consistency %>%
-  ggplot(aes(x = situation, y = mean_nlevels)) + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
-  geom_point(aes(color = bin_situation)) + 
-  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
-  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation.
-This shows that the most different features chosen was seven.
-However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.
-
-```{r}
-# Determine the order that the features are chosen within a case and 
-# set of input options
-sensitivity_chosen <- hamby224_sensitivity_joined %>%
-  select(set, situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-```{r}
-# Determine and plot the number of features chosen across the 10 reps within 
-# a set, input options, and feature level
-sensitivity_chosen %>%
-  group_by(set, situation, case) %>%
-  summarise(first = length(levels(factor(first))),
-            second = length(levels(factor(second))),
-            third = length(levels(factor(third)))) %>%
-  gather(chosen, nfeatures, first:third) %>%
-  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
-  geom_bar(position = "stack") + 
-  facet_grid(set ~ chosen) + 
-  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
-  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
-```
-
-The plots below need some work, but they contain some interesting information.
-Right now, I am only concentrating on set 1.
-We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case.
-We can also see that different variables are selected as important depending on the number of bins.
-It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases.
-On the other hand, the quantile bins choose different first variables for the cases.
-
-The fact that different features get chosen as the top feature for different estimation techniques makes sense.
-You would expect that the number of bins would determine which features are better suited for predicting whether or not a comparison is a match.
-For example, if you look back at the feature distribution plots, you can see that ccf is the obvious choice for determining between matches and non-matches if you have to choose two equally spaced bins.
-This is the feature that lime most frequently chooses.
-You can make similar arguments for other cases as well.
-Even though different inputs select different variables, I would expect that some variables will be better at prediction than others.
-I think this is what leads some input values to better LIME explanations and lower MSEs than others.
-
-In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations.
-Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins.
-In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.
-
-```{r fig.height = 8, fig.width = 10}
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(1) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(2) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-
-hamby224_sensitivity_joined %>%
-  filter(set == "Set 1") %>%
-  droplevels() %>%
-  select(situation, case, rep, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
-  group_by(situation, case, rep) %>%
-  slice(3) %>%
-  ungroup() %>%
-  group_by(situation, case) %>%
-  mutate(nlevels = length(levels(factor(feature)))) %>%
-  ungroup() %>%
-  arrange(situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
-  ggplot(aes(x = order, fill = feature)) + 
-  geom_bar(position = "stack", width = 1) + 
-  coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 5) +
-  #facet_grid(nlevels ~ situation) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
-```
-
-I was thinking a bit more about the relationship between the top features chosen and the type of binning used.
-I realized it would be helpful to view the relationship between the features and the random forest score.
-The plots below show the testing data with random forest score versus each of the features.
-The points are colored by the samesource variable.
-
-```{r}
-hamby224_test %>% 
-  select(rf_features, rfscore, samesource) %>%
-  gather(key = feature, value = value, 1:9) %>%
-  select(feature, value, rfscore, samesource) %>%
-  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
-  geom_point() + 
-  facet_wrap( ~ feature, scales = "free") +
-  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
-       title = "Hamby 224 Testing Data") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Input Rankings
-
-In order to decide on which LIME settings to use for the firearm examiners' paper, I decided to create a table that ranks each of the 12 input settings by MSE from the single implementation, the average MSE across the 10 implementations, the average number of top features chosen across the 10 implementations, and the average $R^2$ value from the single implementation.
-The first table below is for set 1, and the second table below is for set 11.
-
-While using these to help me decide which input settings to use, I had a handful of thoughts:
-
-* Since I am still working on making sense of the variation results, and it would be nice to get the first paper out, I am thinking of basing the decision of input values entirely off of only the assessment measures from the one case.
-* Even with needing more time to think about how to understand the meaning of the results from the 10 reps, the mean MSE from these has very similar results to the MSEs from the one rep, and it does not appear that the top chosen features vary too much between the reps.
-This makes me think that it would be okay to base my decision off of the results from the single rep.
-* Both Heike and I do not think that the $R^2$ is that helpful of a measure for determining whether the LIME explanations are good, so I am not going to put much weight on it.
-* Additionally, I do not want to consider either the normal approximation or kernel density estimate since I have not figured out a good way to visualize these in the app.
-Right now, the feature plots from these explanations are not very helpful.
-I would need to adjust the intercept or something.
-
-Based on the MSEs from the single implementation of LIME, I will use 3 equally spaced bins for both the set 1 and set 11 explanations in the firearm examiner paper since it leads to the lowest MSE for both sets.
-
-```{r}
-joined_results <- hamby224_lime_results %>%
-  select(set, situation, mse, ave_r2) %>%
-  full_join(hamby224_sensitivity_results %>%
-              group_by(set, situation) %>%
-              summarise(mean_sensitivity_mse = mean(mse), 
-                        sd_sensitivity_mse = sd(mse)),
-            by = c("set", "situation")) %>%
-  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
-            by = c("set", "situation")) %>%
-  group_by(set) %>%
-  mutate(mse_order = dense_rank(mse),
-         ave_r2_order = dense_rank(desc(ave_r2)),
-         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
-         mean_nlevels_order = dense_rank(mean_nlevels))
-```
-
-```{r}
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 1") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 1")
-
-joined_results %>%
-  ungroup() %>%
-  filter(set == "Set 11") %>%
-  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
-  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
-                rownames = FALSE,
-                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
-                             "Mean R2"),
-                caption = "Results from Set 11")
-```

### 2019-02-11 journals/05-applying_lime.Rmd
moved lime algorithm to journal 04

@@
 
-This journal contains a draft of the the lime procedure, the application of lime to the bullet data, and a plot created by Heike to visualize the lime explanations.
+This journal the applications of lime to the bullet data.
 
@@
 
-# Draft of LIME Procedure
-
-### Less Detailed Version
-
-I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
-It needs a lot of work, but it is a start.
-The final version of this will end up in the technical stats paper critiquing LIME.
-The version in the firearm examiner's paper will be much simpler...
-
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
-
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
-
-1. Distributions for each of the features in the training data are obtained. 
-    + The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n_bins = 4`).
-
-2. Many ($n$) samples from each of the feature distributions are drawn.
-     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
-      * bin\_continuous = TRUE should continuous variables be binned?
-      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-      * n\_bins = 4 number of bins if bin\_continuous is TRUE
-      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
-
-3. Predictions for the testing data using the random forest model are computed.
-     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-
-4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-    + The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-
-5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
-    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-      * forward selection with ridge regression
-      * highest weight with ridge regression
-      * LASSO model
-      * tree model
-      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-
-6.
-A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-For the prediction of interest, 
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-7. The feature weights are extracted and used as the explanations.
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
-
-### More Detailed Version
-
-I need to install math jax to get this to work...
-
-##### Notation
-
-\begin{itemize}
-\item $x\in\mathbb{R}^d$: original representation of an instance being explained
-\begin{itemize}
-\item e.g. feature vector containing word embeddings
-\end{itemize}
-\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
-\begin{itemize}
-\item e.g. bag of words
-\end{itemize}
-\item $G$: class of potentially interpretable models
-\begin{itemize}
-\item e.g. linear models, decision trees, rule lists
-\end{itemize}
-\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
-\item $\Omega(g)$: measure of complexity of $g$
-\begin{itemize}
-\item e.g. depth of a tree, number of non-zeros in a linear model
-\end{itemize}
-\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
-\begin{itemize}
-\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
-\end{itemize}
-\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
-\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
-\end{itemize}
-
-##### Step by Step Procedure
-
-Step 1:
-
-# Application of LIME
-
-### One Implementation
+# One Implementation
 
@@
 
-### Multiple Implementations
+# Multiple Implementations
 

### 2019-02-11 papers/An Assessment of LIME Explanations from a Random Forest Model.Rmd
started writing description of dependency of explanations on sampling method used in stats paper

@@
 ```
+
+# Introduction
+
+# Data
+
+# Methods
+
+## LIME Algorithm
+
+**Notation**
+
+\begin{itemize}
+\item $x\in\mathbb{R}^d$: original representation of an instance being explained
+\begin{itemize}
+\item e.g. feature vector containing word embeddings
+\end{itemize}
+\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
+\begin{itemize}
+\item e.g. bag of words
+\end{itemize}
+\item $G$: class of potentially interpretable models
+\begin{itemize}
+\item e.g. linear models, decision trees, rule lists
+\end{itemize}
+\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
+\item $\Omega(g)$: measure of complexity of $g$
+\begin{itemize}
+\item e.g. depth of a tree, number of non-zeros in a linear model
+\end{itemize}
+\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
+\begin{itemize}
+\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
+\end{itemize}
+\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
+\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
+\end{itemize}
+
+**Step by Step Procedure**
+
+Step 1:
+
+## Application of LIME to Bullet Matching Data
+
+### lime R Package Perturbation Creation Methods
+
+The LIME R package allows for the following four methods to sample the perturbations based on the distributions of the features from the training data.
+
+\begin{itemize}
+\item Equally Spaced Bins
+\item Quantile Bins
+\item Normal Approximation
+\item Kernel Density Approximation
+\end{itemize}
+
+The methods of equally spaced bins and quantile bins also allow the user to specify the number of bins.
+As of now, there are no recommendations or procedures provided for how to determine which method to use.
+By default, LIME uses four quantile bins.
+It was of interest to see how the explanations from LIME varied across the four sampling methods when applied to the bullet matching data.
+The LIME algorithm was applied to each prediction from the test data obtained from the 'rtrees' random forest model for each of the sampling methods.
+For the bin based sampling methods, the algorithm was applied for 2 to 6 bins.
+That is, the LIME algorithm was applied a total of 10 times to each row in the test data with a different sampling method used each time.
+
+### Proposed Bin Creation Methods
+
+# Results
+
+## LIME Package Explanations Dependent on Sampling Method
+
+In order to assess the LIME explanations created using different sampling methods, it was of interest to compare the top three features chosen as the important predictors by lime within a case from the test data across the diferent sampling methods.
+Figure ...
+is a heatamp showing the top feature chosen by lime for each of the cases in the test data and different bin based sampling methods.
+The rows represent the cases in the test data, and the columns represent the sampling methods.
+There are twenty methods included in the plot.
+These include the equally spaced bins and quantile bins from the lime package and the random forest score tree based bins and the same source tree based bins proposed in this paper.
+The colors represent the top feature chosen by lime.
+The rows are facetted by the test set and whether or not the observation is a match or not.
+
+# Discussion

### 2019-02-12 journals/06-assessing_lime_explanations.Rmd
small changes
wrote more and worked on ordering

@@
 # Plots the top feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
+chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(first)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = situation, y = order, fill = first)) + 
   geom_tile() + 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
 
 # Plots the second feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = second)) + 
+chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(second)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = situation, y = order, fill = second)) + 
   geom_tile() + 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Second Feature")
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "Second Feature")
 
 # Plots the third feature for each case for each bin situation
-ggplot(chosen_features, aes(x = situation, y = case, fill = third)) + 
+chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(third)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = situation, y = order, fill = third)) + 
   geom_tile() + 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "Third Feature")
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "Third Feature")
 ```
@@
 ```{r}
-sessionInfo()
+devtools::session_info()
 ```

### 2019-02-12 papers/An Assessment of LIME Explanations from a Random Forest Model.Rmd
wrote more and worked on ordering

@@
 It was of interest to see how the explanations from LIME varied across the four sampling methods when applied to the bullet matching data.
-The LIME algorithm was applied to each prediction from the test data obtained from the 'rtrees' random forest model for each of the sampling methods.
-For the bin based sampling methods, the algorithm was applied for 2 to 6 bins.
-That is, the LIME algorithm was applied a total of 10 times to each row in the test data with a different sampling method used each time.
+The LIME algorithm was applied to each prediction from the test data obtained from the 'rtrees' random forest model for each of the four sampling methods.
+Within the bin based sampling methods, the algorithm was applied for 2 to 6 bins.
+It was decided to only go up to 6 bins since the more bins used the more complex the explanation becomes.
 
@@
 These include the equally spaced bins and quantile bins from the lime package and the random forest score tree based bins and the same source tree based bins proposed in this paper.
+The rows are facetted by the test set and whether or not the observation is a match or not.
+The columns are faceted by these methods, and the columns within a facet represent the number of bins.
+Each method has 2 to 6 bins.
 The colors represent the top feature chosen by lime.
-The rows are facetted by the test set and whether or not the observation is a match or not.
+
+The variables of ccf and cms immediately show up as common variables chosen across all of the sampling methods.
+However, the patterns across the number of bins withing the sampling methods are different.
+When equally spaced bins are used, the top feature chosen is consistent across all cases within a number of bins category.
+For example, ccf is almost always chosen (change to actual number) with 2 equally spaced bins, matches is almost always chosen with 3 equally spaced bins, and non_cms is always chosen for the nonmatches with 5 and 6 equally spaced bins.
+This shows that with the bullet matching data, the top feature chosen with equally spaced bins is an artifact of the number of bins used.
+With equally spaced bins, this figure sugggest that LIME is providing global explanations as opposed to local explanations.
+It would be preferable that the top feature chosen was more consistent across the number of bins and more variable across the cases.
+This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.
+
+I'm struggling what to write for the remaining three cases...
 

### 2019-02-12 journals/06-assessing_lime_explanations.Rmd
ordered plot and wrote more

@@
 
+## Fleiss's Kappa
+
 In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
@@
 ```
+
+## Tile Plots of Features Chosen
 
@@
 ```
+
+## Attempts at Arranging the Tile Plots
+
+I tried three different arrangements...
+
+```{r fig.height = 8, fig.width = 8}
+# Arranged by number of levels
+chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(first)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = situation, y = order, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
+
+# Arranged by case and then number of levels
+chosen_features %>%
+  group_by(case) %>%
+  mutate(nlevels = length(levels(factor(first)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = situation, y = order, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
+
+# No arrangement
+chosen_features %>%
+  ggplot(aes(x = situation, y = case, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
+```
+
+## Plot of Number of Features Chosen
 

### 2019-02-12 journals/06-assessing_lime_explanations.Rmd
updated journal 06 and removed caching

@@
     toc: true
-    toc_depth: 3
+    toc_depth: 2
     toc_float: true
@@
 
-This journal compares the results from the different LIME implementations.
+This journal visualizes and compares the results from the different LIME implementations.
 
@@
 
-# Accuracy
+# One Implementation
+
+## Accuracy
 
@@
 
-# Consistency with One Implementation
+## Consistency
 
@@
 
-## Fleiss's Kappa
+### Fleiss's Kappa
 
@@
 
-## Tile Plots of Features Chosen
+### Tile Plots of Features Chosen
 
@@
 
-## Attempts at Arranging the Tile Plots
+### Attempts at Arranging the Tile Plots
 
@@
 
-## Plot of Number of Features Chosen
+### Plot of Number of Features Chosen
 
@@
 
-# Consistency Across Implementations
+# Multiple Implementations
+
+## Accuracy
 
@@
 ```
+
+### Comparing MSE and $R^2$
 
@@
 ```
+
+## Consistency
+
+### Plots of Number of Features Chosen
 
@@
 
+### Fleiss's Kappa
+
 I computed Fleiss's kappa for each sampling technique within a set across the 10 reps.
@@
 ```
+
+### Tile Plots of Features Chosen
 
@@
 ```{r}
-devtools::session_info()
+sessionInfo()
 ```

### 2019-02-12 journals/00-ideas.Rmd
added an ideas journal (00)

---
title: "00-ideas"
author: "Katherine Goode"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Concerns with LIME

- We think that the model explainer needs to be close enough to the complex model that it is trying to explain in order to do a good job of providing explanations. For example, the binned regression works okay with neural networks, but it does not work well with a random forest. Maybe a tree explainer or a logistic regression explainer would work better with a random forest.

# Ideas to Try

- Could try fitting a regression with interactions and see if LIME does a good job of explaining the model.

# General Thoughts about LIME

- LIME is kind of like a jacknife technique

# Current Plan

- Write a paper that shows that LIME does not work well with random forests.

### 2019-02-21 journals/01-training_and_testing_data.Rmd
removed all observations with tank rash from the training data and started the process of rerunning all of the code

--- 2019-02-07 journals/01-cleaning_training_and_testing_data.Rmd
@@
 ---
-title: "01-cleaning training and testing data"
+title: "01-training and testing data"
 author: "Katherine Goode"
@@
 rf_features <- rownames(bulletr::rtrees$importance)
+rf_features
 ```
+
+The definitions of these features are inclued below.
+
+- ccf: 
+- cms:
+- D: 
+- matches: 
+- mismatches:
+- non_cms:
+- rough_cor: 
+- sd_D:
+- sum_peaks:
 
@@
 # Load in the Hamby 173 and 252 dataset
-hamby173and252_raw <- read.csv("../data/originals/features-hamby173and252.csv") %>%
+hamby173and252_raw <- read.csv("../data/raw/features-hamby173and252.csv") %>%
   filter(study1 != "Cary", study2 != "Cary") %>%
@@
          rf_features, samesource, rfscore)
+
 ```
+
+### Removing Bullets with Tank Rash
+
+I discovered that rhe number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.
+
+```{r}
+# Compare the dimensions of my training data and the number of predictions from rtrees
+dim(hamby173and252_train)
+dim(predict(bulletr::rtrees, type = "prob"))
+```
+
+When I talked to Heike about this, she told me that this training dataset probably still contains the four land impressions that had tank ranks and were removed before `rtrees` was fit.
+When I looked in Eric's paper, it said that the lands that were removed were the following four:
+
+- barrel 6 bullet 2-1
+- barrel 9 bullet 2-4
+- unknown bullet B-2
+- unknown bullet Q-4
+
+The code below removes any comparisons from the testing data that include one of these lands.
+
+```{r}
+# Remove the comparisons involving the four lands with tank rash
+hamby173and252_train <- hamby173and252_train %>%
+  mutate(bbl1 = barrel1:bullet1:land1,
+         bbl2 = barrel2:bullet2:land2) %>%
+  filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4") | 
+           bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4")))
+```
+
+When I look at the dimensions of my training data now and the number of predictions from `rtrees`, then agree now!
+
+```{r}
+# Compare the dimensions of my further cleaned training data and the
+# number of predictions from rtrees
+dim(hamby173and252_train)
+dim(predict(bulletr::rtrees, type = "prob"))
+```
+
+### Saving the Training Data
 
@@
 write.csv(hamby173and252_train, "../data/hamby173and252_train.csv", row.names = FALSE)
-```
-
-### Issue
-
-The number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.
-
-```{r}
-dim(predict(bulletr::rtrees, type = "prob"))
-dim(hamby173and252_train)
 ```
@@
 # Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("../data/originals/h224-set1-features.rds")
-hamby224_set11 <- readRDS("../data/originals/h224-set11-features.rds")
+hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
+hamby224_set11 <- readRDS("../data/raw/h224-set11-features.rds")
 ```
@@
 
+### Saving the Testing Data
+
 The testing data file is saved below.

### 2019-02-21 journals/02-plotting_training_and_testing_data.Rmd
worked more on reorganizing journals
removed all observations with tank rash from the training data and started the process of rerunning all of the code

@@
 
-The cleaning training and testing datasets are loaded in below.
+The cleaned training and testing datasets are loaded in below.
 
 ```{r}
-# Load in the training data (Hamby Data 173 and 252) and testing data (Hamby Data 224 Sets 1 and 11)
+# Load in the training data (Hamby Data 173 and 252)
 hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+
+# Load in the testing data (Hamby Data 224 Sets 1 and 11)
 hamby224_test <- read.csv("../data/hamby224_test.csv")

### 2019-02-21 journals/05-applying_lime.Rmd
moved old lime results to new folder for time being

@@
 # Load libraries
+library(bulletr)
+library(lime)
+library(furrr)
+library(future)
+library(randomForest)
 library(tidyverse)
+
+# Load rtrees into session
+data("rtrees")
 
@@
 ```{r}
-# Read in the Hamby 224 test data
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+
+# Load in the testing data (Hamby Data 224 Sets 1 and 11)
 hamby224_test <- read.csv("../data/hamby224_test.csv")
-
-# Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
 ```
@@
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(bulletr::rtrees$importance)
+rf_features <- rownames(rtrees$importance)
 ```

### 2019-02-21 journals/07-logistic regression.Rmd
started working on logistic regression

---
title: "07-logistic_regression"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

# Overview

I have been thinking a lot about it is difficult to determine whether LIME is providing reasonable explanations, because we cannot know what the random forest is doing. That is the point of LIME. Heike suggested that we fit a logistic regression model to the training bullet data. We can then apply LIME to the logistic regression and determine if the explanations match what we would expect based on the coefficients of the logistic regression that we can interpret. She also suggested including interactions in the logistic regression model. This journal goes through the process of fitting several logisitic regression models, applying LIME to them, and comparing the results.

```{r}
# Load libraries
library(lime)
```

# The Data

The cleaned training and testing datasets are loaded in below.

```{r}
# Load in the training data (Hamby Data 173 and 252)
hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")

# Load in the testing data (Hamby Data 224 Sets 1 and 11)
hamby224_test <- read.csv("../data/hamby224_test.csv")
```

A vector containing the features used in the random forest `rtrees` is created below that will be used when creating some of the plots in this journal.

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(bulletr::rtrees$importance)
```

# Logistic Regression Model

```{r}
# Fit a logistic regression model with only main effects
logit_main <- glm(samesource ~ ccf + rough_cor + D + sd_D + matches + mismatches + 
                    cms + non_cms + sum_peaks,
                  family = binomial(link = "logit"),
                  data = hamby173and252_train)

coef(logit_main)

logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                   model = logit_main)

logit_explain <- explain(x = hamby224_test %>% select(rf_features) %>% na.omit(), 
                         explainer = logit_lime, 
                         n_labels = 1,
                         n_features = 3)
```

### 2019-02-21 journals/07-logistic_regression.Rmd
fit logistic model

--- 2019-02-21 journals/07-logistic regression.Rmd
@@
 # Load libraries
+library(tidyverse)
 library(lime)
@@
 # Fit a logistic regression model with only main effects
-logit_main <- glm(samesource ~ ccf + rough_cor + D + sd_D + matches + mismatches + 
-                    cms + non_cms + sum_peaks,
-                  family = binomial(link = "logit"),
-                  data = hamby173and252_train)
+logit <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + matches + 
+                        mismatches + cms + non_cms + sum_peaks,
+            data = hamby173and252_train, 
+            method = "glm", 
+            family = "binomial")
 
-coef(logit_main)
+summary(logit)
 
 logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
-                   model = logit_main)
+                    model = logit)
 
@@
                           n_features = 3)
+
+plot_features(logit_explain[1:12,])
 ```

### 2019-02-22 journals/05-applying_lime.Rmd
ran the journal 05 with the updated training data and updated all of the output data from journal 05

@@
 
-This journal the applications of lime to the bullet data.
+This journal includes the code for applying lime to the random forest fit to the bullet data.
 
@@
 
-The code below applies the LIME algorithm to the bullet data for multiple different input cases.
+The code below applies the LIME algorithm to the bullet data one time for the following different input cases:
+
+- 2 to 6 quantile bins
+- 2 to 6 equally spaced bins
+- 2 to 6 tree based bins with `samesource` as the response variable
+- 2 to 6 tree based bins with `rfscore` as the response variable
+- kernel density estimation
+- normal density approximation
+
+It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists.
+The `lime` and `explain` outputs and the input settings are saved as .rds files.
 
@@
 
-This code creates a dataframe of the bins to use in the app.
+This code creates a dataframe of the bins to use in the app based on the output from the `lime` function for each of the input settings.
+The object `hamby224_bin_boundaries` contains the boundaries for the bins, and `hamby224_bins` contains nice forms of the bin intervals (i.e.
+[lower, upper)).
 
@@
            nbins = factor(nbins),
-           feature_number = readr::parse_number(feature_desc),
+           feature_number = readr::parse_number(as.character(feature_desc)),
            strictly_less = FALSE) %>%
@@
 # Multiple Implementations
+
+The code below applies the LIME algorithm to the bullet data one time for the following different input cases:
+
+- 2 to 6 quantile bins
+- 2 to 6 equally spaced bins
+- 2 to 6 tree based bins with `samesource` as the response variable
+- 2 to 6 tree based bins with `rfscore` as the response variable
+- kernel density estimation
+- normal density approximation
+
+It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists.
+The `lime` and `explain` outputs and the input settings are saved as .rds files.
 

### 2019-02-22 journals/05-applying_lime.Rmd
added more descriptions to journal 05

@@
 
-It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists.
-The `lime` and `explain` outputs and the input settings are saved as .rds files.
+It applies LIME using my function `run_lime` to specify the different input values.
+The outputs from the `lime` function are combined into a list, and the outputs from the `explain` function are combined into dataframe.
+Both are saved as .rds files.
 
@@
 
-This code combines the test data and the explanations.
+This code combines the test data and the LIME explanations into one dataframe and saves the dataframe.
 
@@
 
-This code creates a dataset with summaries of the explanations.
+This code creates and saves a dataset with summaries of the explanations.
 
@@
 
-The code below applies the LIME algorithm to the bullet data one time for the following different input cases:
+I was interested in determining how the random permutations affect ths results from LIME.
+That is, I wanted to do a sensativity analysis.
+The code below applies the LIME algorithm to the bullet data ten times for each of the following different input cases:
 
@@
 
-It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists.
-The `lime` and `explain` outputs and the input settings are saved as .rds files.
+It applies LIME using my function `run_lime` to specify the different input values.
+The outputs from the `explain` function are combined into a dataframe and saved as .rds file.
+The input values are also saved as an .rds file.
 
@@
 
+The code below joins the sensativity outputs with the test data into a dataframe. The dataframe is saved as an .rds file.
+
 ```{r}
-# Join the sensativity outputs with the test data
+# Join the sensativity outputs with the test data if not already saved
+if(!file.exists("../data/hamby224_sensitivity_joined.rds")) {
+
 hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
@@
 
-write.csv(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.csv",
-          row.names = FALSE)
+  # Save the joined test and explained dataframes
+  saveRDS(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.rds")
+
+} else {
+
+  # Load in the sensitivity inputs and outputs
+  hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
+
+}
 ```

### 2019-02-22 journals/01-training_and_testing_data.Rmd
renamed the training data in cleaning

@@
 # Cleaning the testing data
-hamby173and252_train <- hamby173and252_raw %>%
+hamby173and252_train_cleaning <- hamby173and252_raw %>%
   mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
@@
          rf_features, samesource, rfscore)
-
 ```
@@
 # Compare the dimensions of my training data and the number of predictions from rtrees
-dim(hamby173and252_train)
+dim(hamby173and252_train_cleaning)
 dim(predict(bulletr::rtrees, type = "prob"))
@@
 # Remove the comparisons involving the four lands with tank rash
-hamby173and252_train <- hamby173and252_train %>%
+hamby173and252_train <- hamby173and252_train_cleaning %>%
   mutate(bbl1 = barrel1:bullet1:land1,

### 2019-02-22 journals/06-assessing_lime_explanations.Rmd
knit journal 06 with the new training data

@@
 knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      cache = TRUE)
+                      error = FALSE, cache = TRUE)
 ```
@@
 ```{r}
+# Load libraries
 library(gretchenalbrecht)
@@
 
-hamby224_sensitivity_joined <- read.csv("../data/hamby224_sensitivity_joined.csv")
+hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
 

### 2019-02-22 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
created folders for all journals and re-knit all journals

---
title: "00-objectives_and_ideas"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This journal explains the objectives of the research project on applying LIME to the Hamby bullet data that is detailed in this series of journals.

# Objectives of the Research Project

It is the hope that this research project will result in two papers. One will focus on a statistical assessment of LIME and the other will focus on the explanation of how the application of LIME to the Hamby bullet data can help firearm examiners understand the random forest model predictions.

### Statistical Paper Assessing LIME

While applying LIME to the bullet matching dataset, we found that the explanations were not as good as we wanted them to be. This has led us to try to understand why the LIME algorithm is not working well and to propose some new methods to improve the algorithm. This paper will discuss isusses we found with the current LIME agorithm, describe our proposed approaches, and compare the results.

### Firearm Examiner's Paper

CSAFE is developing a predictive model that is able to match a bullet to the gun barrel that fired the bullet. They have acquired some sets of the data from the Hamby study. Part of this data was used to train a random forest model (`rtrees`), and the remaining portion of the data will be used as a testing dataset. CSAFE would now like to understand the predictions made by the random forest to be able to provide a better explanation of how the model works to the firearm examiners. Thus, it is of interest to apply the LIME algorithm to the predictions made by the random forest model on the testing data to see which variables LIME suggests are driving individual predictions.

# Concerns with LIME

The following are some of the concerns that we have with the current state of the LIME algorithm.

- I'm nervous about the fact that the results can change due to the permutations. Is there a way to check for consistencey? Does this only happen if you have correlated variables, or can it also happen with uncorrelated variables?
- When you have a large number of predictions to assess, would it be a good idea to focus in on the ones that have the best fitting linear model or produce the most consistent results?
- What can be done to improve the linear regression model fit? Maybe adjusting the number of bins or the kernel width would help with this.
- We think that the model explainer needs to be close enough to the complex model that it is trying to explain in order to do a good job of providing explanations. For example, the binned regression works okay with neural networks, but it does not work well with a random forest. Maybe a tree explainer or a logistic regression explainer would work better with a random forest.

# Ideas to Try

- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.

# General Thoughts about LIME

- LIME is kind of like a jacknife technique

### 2019-02-22 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-22 journals/01-training_and_testing_data.Rmd
@@
 
-This journal includes the code that is used to clean the training and testing datasets.
+This journal includes a description of the Hamby study datasets, and the code that is used to clean the Hamby training and testing datasets.
 
@@
 rf_features <- rownames(bulletr::rtrees$importance)
-rf_features
 ```
 
-The definitions of these features are inclued below.
+# Description of the Hamby Data
+
+The Hamby data is based on several test sets of bullets from the study described in the paper "The Identification of Bullets Fired from 10 Consecutively Rifled 9mm Ruger Pistol Barrels: A Research Project Involving 507 Participants from 20 Countries" by James E.
+Hamby Et.
+Al.
+In this study, sets of bullets from both "known" and "unknown" gun barrels were sent to firearm examiners around the world.
+The examiners were asked to use the known bullets to identify which barrels the unknown bullets came from.
+
+The test sets were created using 1 pistol and 10 barrels.
+Each test set contains a total of 35 bullets, which are made up of 20 known bullets and 15 unknown bullets.
+The 20 known bullets were created by firing two bullets from each of the 10 barrels.
+These are referred to as known bullets, because when they were sent to the firearm examiners, the barrel number that each bullet was fired from was listed with the bullet.
+The 15 unknown bullets were created by firing 15 bullets in some manner from the 10 barrels such that at least one unknown bullet came from each barrel and no more than three unknown bullets came from the same barrel.
+These are referred to as the unknown bullets, because when they were sent to the firearm examiners, the barrel number that the bullet was fired from was not listed with the bullet.
+A total of 240 test sets were created for the study.
+
+CSAFE has access to test sets 44, 173, and 252.
+The bullets were scanned 6 times using a high powered microscope to obtain an image of each of the 6 lands from the bullets.
+The scans for test sets 173 and 252 were done by NIST, and the scans for test set 44 was done by CSAFE.
+The data from these images were processed to obtain a signature associated with each land.
+The paper "Automatic Matching of Bullet Land Impressions" by Hare, Hofmann, and Carriquiry (https://arxiv.org/abs/1601.05788) provides more descriptions of how the signatures were obtained.
+
+CSAFE aggregated the signatures from test sets 173 and 252 and left the signatures from test set 44 separate.
+Within these two groups, pairs of lands were evaluated to determine how similar the signatures from the two lands were.
+This was done by measuring a set of variables they determined that would capture how alike the two signatures where.
+Some of these variables are described in Hare, Hofmann, and Carriquiry.
+The vignette at https://github.com/heike/bulletxtrctr/blob/master/vignettes/features.Rmd includes some additional descriptions.
+Note that it was not possible to evaluate all pairs of lands due to tank rash on some of the lands.
+The data set created from the comparisons of test sets 173 and 252 will be referred to as `hamby173and252` throughout these journals.
+Hare, Hofmann, and Carriquiry used `hamby173and252` as a training data set to fit the random forest model `rtrees`.
+The data set created from the comparisons of test sets 44 will be referred to as `hamby44` and is not used in this research project.
+
+### Variable Definitions
+
+The definitions of the variables...
 
@@
 # Load in the Hamby 173 and 252 dataset
-hamby173and252_raw <- read.csv("../data/raw/features-hamby173and252.csv") %>%
+hamby173and252_raw <- read.csv("../../data/raw/features-hamby173and252.csv") %>%
   filter(study1 != "Cary", study2 != "Cary") %>%
@@
 
-I discovered that rhe number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.
+I discovered that the number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.
 
@@
   filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4") | 
-           bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4")))
+           bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4"))) %>%
+  select(-bbl1, -bbl2)
 ```
@@
 # Save the datasets and response variables as .csv files
-write.csv(hamby173and252_train, "../data/hamby173and252_train.csv", row.names = FALSE)
+write.csv(hamby173and252_train, "../../data/hamby173and252_train.csv", row.names = FALSE)
 ```
@@
 # Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
-hamby224_set11 <- readRDS("../data/raw/h224-set11-features.rds")
+hamby224_set1 <- readRDS("../../data/raw/h224-set1-features.rds")
+hamby224_set11 <- readRDS("../../data/raw/h224-set11-features.rds")
 ```
@@
 # Save the test data as a .csv file
-write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)
+write.csv(hamby224_test, "../../data/hamby224_test.csv", row.names = FALSE)
 ```

### 2019-02-22 journals/02-plotting_training_and_testing_data/02-plotting_training_and_testing_data.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-21 journals/02-plotting_training_and_testing_data.Rmd
@@
 ---
-title: "02-plotting_features"
+title: "02-plotting_training_and_testing_data"
 author: "Katherine Goode"
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
 
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../data/hamby224_test.csv")
+hamby224_test <- read.csv("../../data/hamby224_test.csv")
 ```

### 2019-02-22 journals/03-computation_issues/03-computation_issues.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-08 journals/03-computation_issues.Rmd
@@
 # Load libraries
+library(caret)
+library(lime)
+library(plotly)
+library(randomForest)
 library(tidyverse)
-library(plotly)
-library(caret)
-library(randomForest)
-library(lime)
 ```
@@
 
+library(furrr)
+library(future)
 library(tictoc)
-library(future)
-library(furrr)
 

### 2019-02-22 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-11 journals/04-lime_algorithm_and_proposed_methods.Rmd
@@
 # Source functions
-source("../code/helper_functions.R")
+source("../../code/helper_functions.R")
 ```
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
 ```
@@
 
+# Inputs for LIME Functions
+
+The default input settings for the `lime` and `explain` functions in the lime package are described below.
+
+### `lime` function
+
+The default settings for the `lime` function are as follows.
+
+- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations.
+If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to.
+- `bins = 4`: The number of bins to divide the continuous variables into. The default is 4 bins.
+- `quantile_bins = TRUE`: If set to `TRUE`, the bins will be be based on `n_bins` quantiles. Otherwise, the bins will be spread evenly over the range of the training data.
+- `use_density = TRUE`: If `bin_continuous` is set to `FALSE` and this is set to `TRUE`, then the continuous data will be sampled using kernel density estimation.
+Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.
+
+### `explain` function
+
+For our research project, the number of labels (`n_labels`) for the response variable will be set to 1 and the number of features to include in the explanations (`n_features`) will be set to 2.
+The default values for the other options are as follows.
+
+- `n_permutations = 5000`: The number of perturbations generated for each feature.
+- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified.
+This uses forward selection if $m\le 6$ and otherwise highest weights.
+The other feature selection options are as follows.
+    - `none`: Use all features for the explanation. Not advised unless you have very few features.
+    - `forward selection`: Features are added one by one based on their improvements to a ridge regression fit of the complex model outcome.
+    - `highest weights`: The m features with highest absolute weight in a ridge regression fit of the complex model outcome are chosen.
+    - `lasso`: The m features that are least prone to shrinkage based on the regularization path of a lasso fit of the complex model outcome is chosen.
+    - `tree`: A tree is fitted with log2(m) splits, to use at max m features. It may possibly select less.
+- `dist_fun = 'gower'`: The distance function to be used for determining how close a perturbation is to the test point.
+- `kernel_width = NULL`: If `dist_fun` is not set to `gower`, then this is the kernel width that will be used in the distance function.
+
 # Proposed Bin Creation Methods
@@
 # Save the subsampled data
-write.csv(hamby173and252_train_sub, "../data/hamby173and252_train_sub.csv", row.names = FALSE)
+write.csv(hamby173and252_train_sub, "../../data/hamby173and252_train_sub.csv", row.names = FALSE)
 

### 2019-02-22 journals/05-applying_lime_to_rtrees/05-applying_lime_to_rtrees.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-22 journals/05-applying_lime.Rmd
@@
 ---
-title: "05-applying_lime"
+title: "05-applying_lime_to_rtrees"
 author: "Katherine Goode"
@@
 
-This journal includes the code for applying lime to the random forest fit to the bullet data.
+This journal includes a description of the random forest model `rtrees` fit to the bullet data by Eric and the code for applying lime to `rtrees`.
 
@@
 
-# Load rtrees into session
-data("rtrees")
-
 # Source functions
-source("../code/helper_functions.R")
+source("../../code/helper_functions.R")
 ```
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
 
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../data/hamby224_test.csv")
+hamby224_test <- read.csv("../../data/hamby224_test.csv")
+```
+
+# Description of `rtrees`
+
+The random forest model that was fit to the Hamby training dataset is discussed in the paper "Automatic Matching of Bullet Land Impressions" by E.
+Hare Et.
+Al.
+The model is available through the GitHub version of the `bulletr` package.
+The link to the GitHub repository for `bulletr` is https://github.com/CSAFE-ISU/bulletr.
+
+The random forest model is stored in the package `bulletr` as a data object called `rtrees`.
+The paper does not include many details about the model fitting process, so I looked at some of the model features, which are printed below.
+These values told me that the model was fit using the predictive features of `ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks` with 300 trees and the parameter of `mtry` set to 3, which is the "number of variables randomly sampled as candidates at each split" as explained in the `randomforest` package documentation.
+
+```{r}
+# Importance values from the random forest
+rtrees$importance
+
+# The number of trees used in the random forest
+rtrees$ntree
+
+# "Number of variables randomly sampled as candidates at each split"
+rtrees$mtry
 ```
@@
 # Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("../data/hamby224_lime_inputs.rds")) {
+if(!file.exists("../../data/hamby224_lime_inputs.rds")) {
 
@@
   # Save the lime objects
-  saveRDS(hamby224_lime_inputs, "../data/hamby224_lime_inputs.rds")
-  saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
-  saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
+  saveRDS(hamby224_lime_inputs, "../../data/hamby224_lime_inputs.rds")
+  saveRDS(hamby224_lime, "../../data/hamby224_lime.rds")
+  saveRDS(hamby224_explain, "../../data/hamby224_explain.rds")
 
@@
   # Load in the lime objects
-  hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
-  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
-  hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+  hamby224_lime_inputs <- readRDS("../../data/hamby224_lime_inputs.rds")
+  hamby224_lime <- readRDS("../../data/hamby224_lime.rds")
+  hamby224_explain <- readRDS("../../data/hamby224_explain.rds")
 
@@
 # Create a dataframe with the bins
-if (!file.exists("../data/hamby224_bins.csv")) {
+if (!file.exists("../../data/hamby224_bins.csv")) {
 
@@
   # Save the bin boundaries and bins
-  saveRDS(hamby224_bin_boundaries, "../data/hamby224_bin_boundaries.rds")
-  saveRDS(hamby224_bins, "../data/hamby224_bins.rds")
+  saveRDS(hamby224_bin_boundaries, "../../data/hamby224_bin_boundaries.rds")
+  saveRDS(hamby224_bins, "../../data/hamby224_bins.rds")
 
@@
   # Load in the bin boundaries and bins
-  hamby224_bin_boundaries <- readRDS("../data/hamby224_bin_boundaries.rds")
-  hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+  hamby224_bin_boundaries <- readRDS("../../data/hamby224_bin_boundaries.rds")
+  hamby224_bins <- readRDS("../../data/hamby224_bins.rds")
 
@@
 # Create the test_explain combined data if the file does not already exist
-if(!file.exists("../data/hamby224_test_explain.rds")) {
+if(!file.exists("../../data/hamby224_test_explain.rds")) {
 
@@
   # Save the combined test and explain data
-  saveRDS(hamby224_test_explain, "../data/hamby224_test_explain.rds")
+  saveRDS(hamby224_test_explain, "../../data/hamby224_test_explain.rds")
 
@@
   # Load in the data
-  hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+  hamby224_test_explain <- readRDS("../../data/hamby224_test_explain.rds")
 
@@
 # Create the lime comparison data if the file does not already exist
-if(!file.exists("../data/hamby224_lime_comparisons.rds")) {
+if(!file.exists("../../data/hamby224_lime_comparisons.rds")) {
 
@@
   # Save the lime comparison data frame
-  saveRDS(hamby224_lime_comparisons, "../data/hamby224_lime_comparisons.rds")
+  saveRDS(hamby224_lime_comparisons, "../../data/hamby224_lime_comparisons.rds")
 
@@
   # Load in the lime comparison data frame
-  hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+  hamby224_lime_comparisons <- readRDS("../../data/hamby224_lime_comparisons.rds")
 
@@
 # Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+if(!file.exists("../../data/hamby224_sensitivity_inputs.rds")) {
 
@@
   # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+  saveRDS(hamby224_sensitivity_inputs, "../../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../../data/hamby224_sensitivity_outputs.rds")
 
@@
   # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+  hamby224_sensitivity_inputs <- readRDS("../../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../../data/hamby224_sensitivity_outputs.rds")
 
@@
 # Join the sensativity outputs with the test data if not already saved
-if(!file.exists("../data/hamby224_sensitivity_joined.rds")) {
+if(!file.exists("../../data/hamby224_sensitivity_joined.rds")) {
 
@@
   # Save the joined test and explained dataframes
-  saveRDS(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.rds")
+  saveRDS(hamby224_sensitivity_joined, "../../data/hamby224_sensitivity_joined.rds")
 
@@
   # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
+  hamby224_sensitivity_joined <- readRDS("../../data/hamby224_sensitivity_joined.rds")
 

### 2019-02-22 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-22 journals/06-assessing_lime_explanations.Rmd
@@
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../data/hamby224_test.csv") # created in the paper
+hamby224_test <- read.csv("../../data/hamby224_test.csv") # created in the paper
 
 # Read in the test_explain data
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+hamby224_test_explain <- readRDS("../../data/hamby224_test_explain.rds")
 
-hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
+hamby224_sensitivity_joined <- readRDS("../../data/hamby224_sensitivity_joined.rds")
 
@@
 # paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+hamby224_lime_comparisons <- readRDS("../../data/hamby224_lime_comparisons.rds")
 ```

### 2019-02-22 journals/07-logistic_regression/07-logistic_regression.Rmd
created folders for all journals and re-knit all journals

--- 2019-02-21 journals/07-logistic_regression.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
+                      cache = TRUE)
 ```
@@
 # Load libraries
+library(lime)
 library(tidyverse)
-library(lime)
 ```
@@
 
-```{r}
+```{r eval = FALSE}
 # Fit a logistic regression model with only main effects

### 2019-02-25 journals/03-computation_issues/03-computation_issues.Rmd
started trying to use seriate to order the cases in the tile plots

@@
 
+# Understanding `seriation`
+
+The example below is from the paper "Getting Things in Order: An Introduction to the R Package seriation" by Hahsler, Hornik, and Buchta.
+
+```{r}
+library(seriation)
+
+data("iris")
+x <- as.matrix(iris[-5])
+x <- x[sample(seq_len(nrow(x))), ]
+d <- dist(x)
+o <- seriate(d)
+str(o)
+class(0)
+head(get_order(o), 15)
+pimage(d, main = "Random")
+pimage(d, o, main = "Reordered")
+cbind(random = criterion(d), reordered = criterion(d, o))
+
+pimage(x, main = "Random")
+o_2mode <- c(o, ser_permutation(seq_len(ncol(x))))
+pimage(x, o_2mode, main = "Reordered")
+```
+
+I wanted to learn how to use the order that is output from `seriate` to create my own plot using `ggplot`.
+I create a new dataframe below that includes the order and create two plots.
+Note that the "order" from `seriate`, which can be obtained using `get_order` is a vector with the case numbers ordered (not the order associated with a case).
+
+```{r}
+# Add a case variable (ordered by seriate order) and my own order variable to my dataframe
+x2 <- data.frame(x) %>% 
+  mutate(case = factor(1:n(), levels = get_order(o))) %>%
+  arrange(case) %>%
+  mutate(order = 1:n())
+
+# Plot ordered using the case variable
+x2 %>%
+  gather(key = variable, value = value, 1:4) %>%
+  ggplot(aes(x = variable, y = case, fill = value)) + 
+  geom_tile()
+
+# Plot ordered using the order variable
+x2 %>%
+  gather(key = variable, value = value, 1:4) %>%
+  arrange(order) %>%
+  ggplot(aes(x = variable, y = order, fill = value)) + 
+  geom_tile()
+```
+
 # Session Info

### 2019-02-25 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
started gg pres

---
title: "Applying LIME to a Random Forest Model and the Problems that Ensue"
author: "Katherine Goode"
date: "March 1, 2019"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](http://slides.yihui.name/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: center, bottom, inverse

# You only live once!

---

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---
background-image: url(`r xaringan:::karl`)
background-size: cover
class: center, bottom, inverse

# I was so happy to have discovered remark.js!

---
class: inverse, middle, center

# Using xaringan

---

# xaringan

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```

See the help page `?xaringan::moon_reader` for all possible options that you can use.

---

# remark.js vs xaringan

Some differences between using remark.js (left) and using **xaringan** (right):

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]

.footnote[[*] Not really. See next page.]

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

# HTML Widgets

I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.

Similarly, the Shiny mode (`runtime: shiny`) does not work. I might get these issues fixed in the future, but these are not of high priority to me. I never turn my presentation into a Shiny app. When I need to demonstrate more complicated examples, I just launch them separately. It is convenient to share slides with other people when they are plain HTML/JS applications.

See the next page for two HTML widgets.

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```

---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---

# Some Tips

- When you use the "Infinite Moon Reader" addin in RStudio, your R session will be blocked by default. You can click the red button on the right of the console to stop serving the slides, or use the _daemonized_ mode so that it does not block your R session. To do the latter, you can set the option

    ```r
    options(servr.daemon = TRUE)
    ```

    in your current R session, or in `~/.Rprofile` so that it is applied to all future R sessions. I do the latter by myself.

    To know more about the web server, see the [**servr**](https://github.com/yihui/servr) package.

--

- Do not forget to try the `yolo` option of `xaringan::moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        yolo: true
    ```

---

# Some Tips

- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          autoplay: 30000
    ```

--

- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          countdown: 60000
    ```

    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.

---

# Some Tips

- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.

    The title slide is set to `class: center, middle, inverse, title-slide` by default. You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          titleSlideClass: [top, left, inverse]
    ```

--

- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        seal: false
    ```

---

# Some Tips

- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.name/xaringan/incremental.html) for examples.

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          highlightLines: true
    ```

    See examples on the next page.

---

# Some Tips

.pull-left[
An example using a leading `*`:

    ```r
    if (TRUE) {
    ** message("Very important!")
    }
    ```
Output:
```r
if (TRUE) {
* message("Very important!")
}
```

This is invalid R code, so it is a plain fenced code block that is not executed.
]

.pull-right[
An example using `{{}}`:

    `r ''````{r tidy=FALSE}
    if (TRUE) {
    *{{ message("Very important!") }}
    }
    ```
Output:
```{r tidy=FALSE}
if (TRUE) {
{{ message("Very important!") }}
}
```

It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
]

---

# Some Tips

An example of using the trailing comment `#<<` to highlight lines:

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

Output:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---

# Some Tips

When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk. For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.

````md
`r ''````{r, highlight.output=c(1, 3)}
head(iris)
```
````

```{r, highlight.output=c(1, 3), echo=FALSE}
head(iris)
```

Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)

---

# Some Tips

- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).

- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.

- Then change the `chakra` option in YAML to point to this file, e.g.

    ```yaml
    output:
      xaringan::moon_reader:
        chakra: libs/remark-latest.min.js
    ```

- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally. The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.

---

# Macros

- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`. For example, before remark.js initializes the slides, you can define a macro named `scale`:

    ```js
    remark.macros.scale = function (percentage) {
      var url = this;
      return '<img src="' + url + '" style="width: ' + percentage + '" />';
    };
    ```

    Then the Markdown text

    ```markdown
    ![:scale 50%](image.jpg)
    ```

    will be translated to

    ```html
    <img src="image.jpg" style="width: 50%" />
    ```

---

# Macros (continued)

- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          beforeInit: "macros.js"
    ```

    You save your remark.js macros in the file `macros.js`.

- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.

---

# CSS

Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.

You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css). You can completely replace it with your own CSS files, or define new rules to override the default. See the help page `?xaringan::moon_reader` for more information.

---

# CSS

For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:

```css
@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
```

Then set the `css` option in the YAML metadata:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "ubuntu-mono.css"]
```

Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.

See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.

---

# Themes

Don't want to learn CSS? Okay, you can use some user-contributed themes. A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name. Below are some existing themes:

```{r}
names(xaringan:::list_css())
```

---

# Themes

To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,

```yaml
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
```

If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.name/en/2017/10/xaringan-themes).

---
class: inverse, middle, center
background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
background-size: contain

# Naruto

---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

# Sharingan

The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:

- the "Eye of Insight"

- the "Eye of Hypnotism"

I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>

.footnote[
[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.

[2] By comparison, bad presentations only put the audience to sleep.

[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
]

---

# Naruto terminology

The **xaringan** package borrowed a few terms from Naruto, such as

- [Sharingan](http://naruto.wikia.com/wiki/Sharingan) (写輪眼; the package name)

- The [moon reader](http://naruto.wikia.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)

- [Chakra](http://naruto.wikia.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)

- [Nature transformation](http://naruto.wikia.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)

- The [infinite moon reader](http://naruto.wikia.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)

- The [summoning technique](http://naruto.wikia.com/wiki/Summoning_Technique) (download remark.js from the web)

You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

### 2019-02-25 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd

@@
 library(gretchenalbrecht)
+library(seriation)
 library(tidyverse)
@@
         axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
+```
+
+Now I am trying to use the function `seriate` from the seriation package to order the cases in the plots.
+However, something is going wrong.
+It ends up adding a bunch of NAs to the dataframe after I order the cases.
+I haven't figured out what is wrong yet.
+
+```{r fig.height = 8, fig.width = 8, eval = FALSE}
+order <- chosen_features %>% 
+  filter(set == "Set 1", bin_situation == "samesource tree") %>%
+  arrange(set, case) %>%
+  select(case, nbins, first) %>%
+  spread(key = nbins, value = first) %>%
+  select(-case) %>%
+  cluster::daisy() %>%
+  seriate(method = "MDS") %>%
+  get_order()
+
+chosen_features %>% 
+  filter(set == "Set 1") %>%
+  mutate(case = factor(case)) %>%
+  ggplot(aes(x = situation, y = case, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
+
+set1 <- chosen_features %>% 
+  filter(set == "Set 1") %>%
+  mutate(case = factor(case))
+
+set12 <- chosen_features %>%
+  filter(set == "Set 1") %>%
+  mutate(case = factor(case, levels = order))
+
+order == 272
+unique(set1$case)
+unique(set12$case)
+
+sum(is.na(set1$case))
+sum(is.na(set12$case))
+
+data.frame(set1$case, set12$case) %>% View()
+
+chosen_features %>%
+  filter(set == "Set 1") %>%
+  mutate(case = factor(case, levels = order)) %>%
+  View()
+
+  ggplot(aes(x = situation, y = case, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
fixed issues with logistic regressions

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
-                      cache = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
 ```
@@
 
-# Logistic Regression Model
+# Logistic Regression Models
 
-```{r eval = FALSE}
-# Fit a logistic regression model with only main effects
-logit <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + matches + 
-                        mismatches + cms + non_cms + sum_peaks,
+### Main Effects Only
+
+The code below fits a logistic regression model to the training data using the `train` function from the caret package.
+The nine features used to fit `rtrees` are included as main effects only.
+The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+
+```{r}
+# Fit or load the logistic regression model with only main effects
+if(!file.exists("../../data/logistic_mains.rds")) {
+
+  # Fit the model
+  logistic_mains <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + 
+                                   matches + mismatches + cms + non_cms + sum_peaks,
+                                 preProcess = "scale",
                                  data = hamby173and252_train, 
@@
 
-summary(logit)
+  # Save the model
+  saveRDS(logistic_mains, "../../data/logistic_mains.rds")
 
-logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
-                    model = logit)
+} else{
 
-logit_explain <- explain(x = hamby224_test %>% select(rf_features) %>% na.omit(), 
-                          explainer = logit_lime, 
+  # Load the model
+  logistic_mains <- readRDS("../../data/logistic_mains.rds")
+
+}
+```
+
+The output from the model is shown below. The features of ccf and matches stand out as the most important features in the model.
+
+```{r}
+# Summary of the model
+summary(logistic_mains)
+```
+
+### All Two Way Interactions
+
+The code below fits a logistic regression model to the training data using the `train` function from the caret package.
+The nine features used to fit `rtrees` are included as main effects and with all two way interactions.
+The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+
+```{r}
+# Fit or load the logistic regression model with all two way interactions
+if(!file.exists("../../data/logistic_inters2.rds")) {
+
+  # Fit the model
+  logistic_inters2 <- caret::train(as.factor(samesource) ~
+                                       (ccf + rough_cor + D + sd_D + matches + 
+                                          mismatches + cms + non_cms + sum_peaks)^2,
+                                     preProcess = "scale",
+                                     data = hamby173and252_train,
+                                     method = "glm", 
+                                     family = "binomial")
+
+  # Save the model
+  saveRDS(logistic_inters2, "../../data/logistic_inters2.rds")
+
+} else{
+
+   # Load the model
+  logistic_inters2 <- readRDS("../../data/logistic_inters2.rds")
+
+}
+```
+
+The output from the model is shown below.
+
+```{r}
+# Summary of the model
+summary(logistic_inters2)
+```
+
+### All Three Way Interactions
+
+The code below fits a logistic regression model to the training data using the `train` function from the caret package.
+The nine features used to fit `rtrees` are included as main effects and with all two and three way interactions.
+The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+
+```{r eval = FALSE}
+# Fit or load the logistic regression model with all two and three way interactions
+if(!file.exists("../../data/logistic_inters3.rds")) {
+
+  # Fit the model
+  logistic_inters3 <- caret::train(as.factor(samesource) ~
+                                       (ccf + rough_cor + D + sd_D + matches + 
+                                          mismatches + cms + non_cms + sum_peaks)^3,
+                                     preProcess = "scale",
+                                     data = hamby173and252_train,
+                                     method = "glm", 
+                                     family = "binomial")
+
+  # Save the model
+  saveRDS(logistic_inters3, "../../data/logistic_inters3.rds")
+
+} else{
+
+  # Load the model
+  logistic_inters3 <- readRDS("../../data/logistic_inters3.rds")
+
+}
+```
+
+The output from the model is shown below.
+
+```{r eval = FALSE}
+# Summary of the model
+summary(logistic_inters3)
+```
+
+### Comparing the Logistic Models
+
+# Applying LIME to the Models
+
+### Main Effects Only
+
+```{r eval = FALSE}
+logistic_mains_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
+                            model = logistic_mains$finalModel)
+
+logistic_mains_explain <- explain(x = hamby224_test %>% 
+                                    select(rf_features) %>% 
+                                    na.omit(), 
+                                  explainer = logistic_mains_lime, 
                                   n_labels = 1,
@@
 
-plot_features(logit_explain[1:12,])
+plot_features(logistic_mains_explain[1:12,])
 ```
+
+### All Two Way Interactions
+
+```{r eval = FALSE}
+logistic_inters2_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
+                              model = logistic_inters2)
+
+logistic_inters2_explain <- explain(x = hamby224_test %>% 
+                                      select(rf_features) %>% 
+                                      na.omit(), 
+                                    explainer = logistic_inters2_lime, 
+                                    n_labels = 1,
+                                    n_features = 3)
+
+plot_features(logistic_inters2_explain[1:12,])
+```
+
+### All Three Way Interactions
+
+```{r eval = FALSE}
+logistic_inters3_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
+                              model = logistic_inters3)
+
+logistic_inters3_explain <- explain(x = hamby224_test %>% 
+                                      select(rf_features) %>% 
+                                      na.omit(), 
+                                    explainer = logistic_inters3_lime, 
+                                    n_labels = 1,
+                                    n_features = 3)
+
+plot_features(logistic_inters3_explain[1:12,])
+```
+
+# Session Info
+
+```{r}
+sessionInfo()
+```

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
worked more on logistic regression

@@
 # Fit or load the logistic regression model with only main effects
-if(!file.exists("../../data/logistic_mains.rds")) {
+if(!file.exists("./data/logistic_mains.rds")) {
 
@@
   # Save the model
-  saveRDS(logistic_mains, "../../data/logistic_mains.rds")
+  saveRDS(logistic_mains, "./data/logistic_mains.rds")
 
@@
   # Load the model
-  logistic_mains <- readRDS("../../data/logistic_mains.rds")
+  logistic_mains <- readRDS("./data/logistic_mains.rds")
 
@@
 # Fit or load the logistic regression model with all two way interactions
-if(!file.exists("../../data/logistic_inters2.rds")) {
+if(!file.exists("./data/logistic_inters2.rds")) {
 
@@
   # Save the model
-  saveRDS(logistic_inters2, "../../data/logistic_inters2.rds")
+  saveRDS(logistic_inters2, "./data/logistic_inters2.rds")
 
@@
    # Load the model
-  logistic_inters2 <- readRDS("../../data/logistic_inters2.rds")
+  logistic_inters2 <- readRDS("./data/logistic_inters2.rds")
 
@@
 
-```{r eval = FALSE}
+```{r}
 # Fit or load the logistic regression model with all two and three way interactions
-if(!file.exists("../../data/logistic_inters3.rds")) {
+if(!file.exists("./data/logistic_inters3.rds")) {
 
@@
   # Save the model
-  saveRDS(logistic_inters3, "../../data/logistic_inters3.rds")
+  saveRDS(logistic_inters3, "./data/logistic_inters3.rds")
 
@@
   # Load the model
-  logistic_inters3 <- readRDS("../../data/logistic_inters3.rds")
+  logistic_inters3 <- readRDS("./data/logistic_inters3.rds")
 
@@
 
-The output from the model is shown below.
-
-```{r eval = FALSE}
-# Summary of the model
-summary(logistic_inters3)
-```
+The output from this model is now shown.
 
@@
 
-```{r eval = FALSE}
-logistic_mains_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
-                            model = logistic_mains$finalModel)
+The functions `lime` and `explain` from the lime package are applied below to the logisitc regression model with only main effects.
 
-logistic_mains_explain <- explain(x = hamby224_test %>% 
+```{r}
+# Create or load the lime and explain objects for the main effects logisitic regression model
+if(!file.exists("./data/lime_explain_mains.rds")) {
+
+  # Apply lime
+  lime_mains <- lime(x = hamby173and252_train %>% select(rf_features), 
+                     model = logistic_mains)
+
+  # Apply explain
+  explain_mains <- explain(x = hamby224_test %>%
                              select(rf_features) %>% 
@@
 
-plot_features(logistic_mains_explain[1:12,])
+  # Join the lime and explain objects in a list
+  lime_explain_mains <- list(lime = lime_mains, explain = explain_mains)
+
+  # Save the lime and explain objects
+  saveRDS(lime_explain_mains, "./data/lime_explain_mains.rds")
+
+} else {
+
+  # Load the lime and explain objects
+  lime_explain_mains <- readRDS("./data/lime_explain_mains.rds")
+
+}
+```
+
+```{r}
+plot_features(lime_explain_mains$explain[1:12,])
 ```
@@
 
-```{r eval = FALSE}
-logistic_inters2_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
+```{r}
+# Create or load the lime and explain objects for the two way interaction logisitic regression model
+if(!file.exists("./data/lime_explain_inters2.rds")) {
+
+  # Apply lime
+  lime_inters2 <- lime(x = hamby173and252_train %>% select(rf_features), 
                        model = logistic_inters2)
 
-logistic_inters2_explain <- explain(x = hamby224_test %>% 
+  # Apply explain
+  explain_inters2 <- explain(x = hamby224_test %>%
                                select(rf_features) %>% 
@@
 
-plot_features(logistic_inters2_explain[1:12,])
+  # Join the lime and explain objects in a list
+  lime_explain_inters2 <- list(lime = lime_inters2, explain = explain_inters2)
+
+  # Save the lime and explain objects
+  saveRDS(lime_explain_inters2, "./data/lime_explain_inters2.rds")
+
+} else {
+
+  # Load the lime and explain objects
+  lime_explain_inters2 <- readRDS("./data/lime_explain_inters2.rds")
+
+}
+```
+
+```{r}
+plot_features(lime_explain_inters2$explain[1:12,])
 ```
@@
 
-```{r eval = FALSE}
-logistic_inters3_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
+```{r}
+# Create or load the lime and explain objects for the three way interaction logisitic regression model
+if(!file.exists("./data/lime_explain_inters3.rds")) {
+
+  # Apply lime
+  lime_inters3 <- lime(x = hamby173and252_train %>% select(rf_features), 
                        model = logistic_inters3)
 
-logistic_inters3_explain <- explain(x = hamby224_test %>% 
+  # Apply explain
+  explain_inters3 <- explain(x = hamby224_test %>%
                                select(rf_features) %>% 
@@
 
-plot_features(logistic_inters3_explain[1:12,])
+  # Join the lime and explain objects in a list
+  lime_explain_inters3 <- list(lime = lime_inters3, explain = explain_inters3)
+
+  # Save the lime and explain objects
+  saveRDS(lime_explain_inters3, "./data/lime_explain_inters3.rds")
+
+} else {
+
+  # Load the lime and explain objects
+  lime_explain_inters3 <- readRDS("./data/lime_explain_inters3.rds")
+
+}
+```
+
+```{r}
+plot_features(lime_explain_inters3$explain[1:12,])
 ```

### 2019-02-26 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
worked on pres

@@
 # Get Started
-
----
-
-# Hello World
-
-Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):
-
-```{r eval=FALSE, tidy=FALSE}
-devtools::install_github("yihui/xaringan")
-```
-
---
-
-You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.
-
-- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>
-
---
-
-- Click the `Knit` button to compile it;
-
---
-
-- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.
-
-.footnote[
-[1] 中文用户请看[这份教程](http://slides.yihui.name/xaringan/zh-CN.html)
-
-[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
-]
-
----
-background-image: url(`r xaringan:::karl`)
-background-position: 50% 50%
-class: center, bottom, inverse
-
-# You only live once!
-
----
-
-# Hello Ninja
-
-As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:
-
-1. The [remark.js](https://remarkjs.com) library;
-
-1. The **xaringan** package;
-
-Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**.
-The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).
-
----
-
-# remark.js
-
-You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to
-
-- create a new slide (Markdown syntax<sup>*</sup> and slide properties);
-
-- format a slide (e.g. text alignment);
-
-- configure the slideshow;
-
-- and use the presentation (keyboard shortcuts).
-
-It is important to be familiar with remark.js before you can understand the options in **xaringan**.
-
-.footnote[[*] It is different with Pandoc's Markdown!
-It is limited but should be enough for presentation purposes.
-Come on...
-You do not need a slide for the Table of Contents!
-Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]
-
----
-background-image: url(`r xaringan:::karl`)
-background-size: cover
-class: center, bottom, inverse
-
-# I was so happy to have discovered remark.js!
-
----
-class: inverse, middle, center
-
-# Using xaringan
-
----
-
-# xaringan
-
-Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.
-
-```yaml
----
-title: "A Cool Presentation"
-output:
-  xaringan::moon_reader:
-    yolo: true
-    nature:
-      autoplay: 30000
----
-```
-
-See the help page `?xaringan::moon_reader` for all possible options that you can use.
-
----
-
-# remark.js vs xaringan
-
-Some differences between using remark.js (left) and using **xaringan** (right):
-
-.pull-left[
-1. Start with a boilerplate HTML file;
-
-1. Plain Markdown;
-
-1. Write JavaScript to autoplay slides;
-
-1. Manually configure MathJax;
-
-1. Highlight code with `*`;
-
-1. Edit Markdown source and refresh browser to see updated slides;
-]
-
-.pull-right[
-1. Start with an R Markdown document;
-
-1. R Markdown (can embed R/other code chunks);
-
-1. Provide an option `autoplay`;
-
-1. MathJax just works;<sup>*</sup>
-
-1. Highlight code with `{{}}`;
-
-1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
-]
-
-.footnote[[*] Not really. See next page.]
-
----
-
-# Math Expressions
-
-You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:
-
-```
-$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
-```
-
-$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
-
-Limitations:
-
-1.
-The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;
-
-1. There should not be spaces after the opening `$` or before the closing `$`.
-
-1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).
-
----
-
-# R Code
-
-```{r comment='#'}
-# a boring regression
-fit = lm(dist ~ 1 + speed, data = cars)
-coef(summary(fit))
-dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
-grep('天', dojutsu, value = TRUE)
-```
-
----
-
-# R Plots
-
-```{r cars, fig.height=4, dev='svg'}
-par(mar = c(4, 4, 1, .1))
-plot(cars, pch = 19, col = 'darkgray', las = 1)
-abline(fit, lwd = 2)
-```
-
----
-
-# Tables
-
-If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,
-
-```{r}
-knitr::kable(head(iris), format = 'html')
-```
-
----
-
-# HTML Widgets
-
-I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.
-
-Similarly, the Shiny mode (`runtime: shiny`) does not work.
-I might get these issues fixed in the future, but these are not of high priority to me.
-I never turn my presentation into a Shiny app.
-When I need to demonstrate more complicated examples, I just launch them separately.
-It is convenient to share slides with other people when they are plain HTML/JS applications.
-
-See the next page for two HTML widgets.
-
----
-
-```{r out.width='100%', fig.height=6, eval=require('leaflet')}
-library(leaflet)
-leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
-```
-
----
-
-```{r eval=require('DT'), tidy=FALSE}
-DT::datatable(
-  head(iris, 10),
-  fillContainer = FALSE, options = list(pageLength = 8)
-)
-```
-
----
-
-# Some Tips
-
-- When you use the "Infinite Moon Reader" addin in RStudio, your R session will be blocked by default.
-You can click the red button on the right of the console to stop serving the slides, or use the _daemonized_ mode so that it does not block your R session.
-To do the latter, you can set the option
-
-    ```r
-    options(servr.daemon = TRUE)
-    ```
-
-    in your current R session, or in `~/.Rprofile` so that it is applied to all future R sessions. I do the latter by myself.
-
-    To know more about the web server, see the [**servr**](https://github.com/yihui/servr) package.
-
---
-
-- Do not forget to try the `yolo` option of `xaringan::moon_reader`.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        yolo: true
-    ```
-
----
-
-# Some Tips
-
-- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          autoplay: 30000
-    ```
-
---
-
-- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          countdown: 60000
-    ```
-
-    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.
-
----
-
-# Some Tips
-
-- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.
-
-    The title slide is set to `class: center, middle, inverse, title-slide` by default.
-You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          titleSlideClass: [top, left, inverse]
-    ```
-
---
-
-- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        seal: false
-    ```
-
----
-
-# Some Tips
-
-- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.name/xaringan/incremental.html) for examples.
-
-- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          highlightLines: true
-    ```
-
-    See examples on the next page.
-
----
-
-# Some Tips
-
-.pull-left[
-An example using a leading `*`:
-
-    ```r
-    if (TRUE) {
-    ** message("Very important!")
-    }
-    ```
-Output:
-```r
-if (TRUE) {
-* message("Very important!")
-}
-```
-
-This is invalid R code, so it is a plain fenced code block that is not executed.
-]
-
-.pull-right[
-An example using `{{}}`:
-
-    `r ''````{r tidy=FALSE}
-    if (TRUE) {
-    *{{ message("Very important!") }}
-    }
-    ```
-Output:
-```{r tidy=FALSE}
-if (TRUE) {
-{{ message("Very important!") }}
-}
-```
-
-It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
-]
-
----
-
-# Some Tips
-
-An example of using the trailing comment `#<<` to highlight lines:
-
-````markdown
-`r ''````{r tidy=FALSE}
-library(ggplot2)
-ggplot(mtcars) + 
-  aes(mpg, disp) + 
-  geom_point() +   #<<
-  geom_smooth()    #<<
-```
-````
-
-Output:
-
-```{r tidy=FALSE, eval=FALSE}
-library(ggplot2)
-ggplot(mtcars) + 
-  aes(mpg, disp) + 
-  geom_point() +   #<<
-  geom_smooth()    #<<
-```
-
----
-
-# Some Tips
-
-When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk.
-For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.
-
-````md
-`r ''````{r, highlight.output=c(1, 3)}
-head(iris)
-```
-````
-
-```{r, highlight.output=c(1, 3), echo=FALSE}
-head(iris)
-```
-
-Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)
-
----
-
-# Some Tips
-
-- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).
-
-- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.
-
-- Then change the `chakra` option in YAML to point to this file, e.g.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        chakra: libs/remark-latest.min.js
-    ```
-
-- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally.
-The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.
-
----
-
-# Macros
-
-- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`.
-For example, before remark.js initializes the slides, you can define a macro named `scale`:
-
-    ```js
-    remark.macros.scale = function (percentage) {
-      var url = this;
-      return '<img src="' + url + '" style="width: ' + percentage + '" />';
-    };
-    ```
-
-    Then the Markdown text
-
-    ```markdown
-    ![:scale 50%](image.jpg)
-    ```
-
-    will be translated to
-
-    ```html
-    <img src="image.jpg" style="width: 50%" />
-    ```
-
----
-
-# Macros (continued)
-
-- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          beforeInit: "macros.js"
-    ```
-
-    You save your remark.js macros in the file `macros.js`.
-
-- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.
-
----
-
-# CSS
-
-Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.
-
-You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css).
-You can completely replace it with your own CSS files, or define new rules to override the default.
-See the help page `?xaringan::moon_reader` for more information.
-
----
-
-# CSS
-
-For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:
-
-```css
-@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);
-
-.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
-```
-
-Then set the `css` option in the YAML metadata:
-
-```yaml
-output:
-  xaringan::moon_reader:
-    css: ["default", "ubuntu-mono.css"]
-```
-
-Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.
-
-See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.
-
----
-
-# Themes
-
-Don't want to learn CSS?
-Okay, you can use some user-contributed themes.
-A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name.
-Below are some existing themes:
-
-```{r}
-names(xaringan:::list_css())
-```
-
----
-
-# Themes
-
-To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,
-
-```yaml
-output:
-  xaringan::moon_reader:
-    css: [default, metropolis, metropolis-fonts]
-```
-
-If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.name/en/2017/10/xaringan-themes).
-
----
-class: inverse, middle, center
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
-background-size: contain
-
-# Naruto
-
----
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
-background-size: 100px
-background-position: 90% 8%
-
-# Sharingan
-
-The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:
-
-- the "Eye of Insight"
-
-- the "Eye of Hypnotism"
-
-I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>
-
-.footnote[
-[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.
-
-[2] By comparison, bad presentations only put the audience to sleep.
-
-[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
-]
-
----
-
-# Naruto terminology
-
-The **xaringan** package borrowed a few terms from Naruto, such as
-
-- [Sharingan](http://naruto.wikia.com/wiki/Sharingan) (写輪眼; the package name)
-
-- The [moon reader](http://naruto.wikia.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)
-
-- [Chakra](http://naruto.wikia.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)
-
-- [Nature transformation](http://naruto.wikia.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)
-
-- The [infinite moon reader](http://naruto.wikia.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)
-
-- The [summoning technique](http://naruto.wikia.com/wiki/Summoning_Technique) (download remark.js from the web)
-
-You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.
-
----
-
-class: center
-
-# Hand seals (印)
-
-Press `h` or `?` to see the possible ninjutsu you can use in remark.js.
-
-![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)
-
----
-
-class: center, middle
-
-# Thanks!
-
-Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
-
-The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

### 2019-02-26 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd
updates before meeting

@@
   filter(set == "Set 1") %>%
-  mutate(case = factor(case, levels = order)) %>%
-  View()
-
+  mutate(case = factor(case, levels = order))
   ggplot(aes(x = situation, y = case, fill = first)) + 

### 2019-02-26 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
updates before meeting

@@
 ---
-title: "Applying LIME to a Random Forest Model and the Problems that Ensue"
+title: "My Story of Applying LIME to a Random Forest Model and the Problems that Ensued"
 author: "Katherine Goode"
@@
 
-# Get Started
+## Overview
+
+1. Overview of LIME
+2. Hamby bullet matching data
+3. Applying LIME to the bullet data
+4. Issues with LIME
+5. Attempts at a Solution
+6. Future Work

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
journal 07

@@
 
+  # Set a seed
+  set.seed(20190226)
+
   # Fit the model
@@
 if(!file.exists("./data/logistic_inters2.rds")) {
+
+  # Set a seed
+  set.seed(20190226)
 
@@
 
+The results as computed by caret on the training data are shown below for the three logistic regression models.
+The accuracy shows that the models with two way interactions performs the best on the training data.
+
+```{r}
+# Results from the models
+data.frame(model = c("mains", "inters2", "inters3")) %>%
+  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results, logistic_inters3$results))
+```
+
+The AICs from the models are shown below. The model with three way interactions performs the best based on AIC.
+
+```{r}
+AIC(logistic_mains$finalModel)
+AIC(logistic_inters2$finalModel)
+AIC(logistic_inters3$finalModel)
+```
+
+I also want to know how the models perform on the test data.
+The models are used to make predictions on the test data and the MSEs are computed for each model.
+These are shown in the table below.
+The model with main effects only has the smallest MSE.
+I am guessing that the other models are overfitting.
+
+```{r}
+data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
+           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features)),
+           inters3 = predict(logistic_inters3, hamby224_test %>% select(rf_features))) %>%
+  summarise_at(vars(mains, inters2, inters3), 
+               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
+               obs = hamby224_test %>% select(samesource) %>% na.omit())
+```
+
 # Applying LIME to the Models
@@
 
+  # Set a seed
+  set.seed(20190226)
+
   # Apply lime
@@
                              na.omit(), 
-                           explainer = logistic_mains_lime, 
+                           explainer = lime_mains, 
                            n_labels = 1,
@@
                                na.omit(), 
-                             explainer = logistic_inters2_lime, 
+                             explainer = lime_inters2, 
                              n_labels = 1,
@@
                                na.omit(), 
-                             explainer = logistic_inters3_lime, 
+                             explainer = lime_inters3, 
                              n_labels = 1,

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
updates to journal 07

--- 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
@@
 }
+
+summary(logistic_mains)
 ```
@@
 
-### All Three Way Interactions
+### Comparing the Logistic Models
 
-The code below fits a logistic regression model to the training data using the `train` function from the caret package.
-The nine features used to fit `rtrees` are included as main effects and with all two and three way interactions.
-The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+The results as computed by caret on the training data are shown below for the two logistic regression models.
+The accuracy shows that the models with two way interactions performs better on the training data.
 
 ```{r}
-# Fit or load the logistic regression model with all two and three way interactions
-if(!file.exists("./data/logistic_inters3.rds")) {
-
-  # Fit the model
-  logistic_inters3 <- caret::train(as.factor(samesource) ~
-                                       (ccf + rough_cor + D + sd_D + matches + 
-                                          mismatches + cms + non_cms + sum_peaks)^3,
-                                     preProcess = "scale",
-                                     data = hamby173and252_train,
-                                     method = "glm", 
-                                     family = "binomial")
-
-  # Save the model
-  saveRDS(logistic_inters3, "./data/logistic_inters3.rds")
-
-} else{
-
-  # Load the model
-  logistic_inters3 <- readRDS("./data/logistic_inters3.rds")
-
-}
+# Results from the models
+data.frame(model = c("mains", "inters2")) %>%
+  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results))
 ```
 
-The output from this model is now shown.
+The AICs from the models are shown below. The model with two way interactions performs the best based on AIC.
 
-### Comparing the Logistic Models
+```{r}
+AIC(logistic_mains$finalModel)
+AIC(logistic_inters2$finalModel)
+```
+
+I also wanted to know how the models perform on the test data.
+The models are used to make predictions on the test data and the MSEs are computed for each model.
+These are shown in the table below.
+The model with main effects only has the smallest MSE.
+I am guessing that the other model is overfitting the data.
+
+```{r}
+data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
+           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
+  summarise_at(vars(mains, inters2), 
+               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
+               obs = hamby224_test %>% select(samesource) %>% na.omit())
+```
 
@@
 plot_features(lime_explain_mains$explain[1:12,])
-```
-
-### All Two Way Interactions
-
-```{r}
-# Create or load the lime and explain objects for the two way interaction logisitic regression model
-if(!file.exists("./data/lime_explain_inters2.rds")) {
-
-  # Apply lime
-  lime_inters2 <- lime(x = hamby173and252_train %>% select(rf_features), 
-                       model = logistic_inters2)
-
-  # Apply explain
-  explain_inters2 <- explain(x = hamby224_test %>%
-                               select(rf_features) %>% 
-                               na.omit(), 
-                             explainer = logistic_inters2_lime, 
-                             n_labels = 1,
-                             n_features = 3)
-
-  # Join the lime and explain objects in a list
-  lime_explain_inters2 <- list(lime = lime_inters2, explain = explain_inters2)
-
-  # Save the lime and explain objects
-  saveRDS(lime_explain_inters2, "./data/lime_explain_inters2.rds")
-
-} else {
-
-  # Load the lime and explain objects
-  lime_explain_inters2 <- readRDS("./data/lime_explain_inters2.rds")
-
-}
-```
-
-```{r}
-plot_features(lime_explain_inters2$explain[1:12,])
-```
-
-### All Three Way Interactions
-
-```{r}
-# Create or load the lime and explain objects for the three way interaction logisitic regression model
-if(!file.exists("./data/lime_explain_inters3.rds")) {
-
-  # Apply lime
-  lime_inters3 <- lime(x = hamby173and252_train %>% select(rf_features), 
-                       model = logistic_inters3)
-
-  # Apply explain
-  explain_inters3 <- explain(x = hamby224_test %>%
-                               select(rf_features) %>% 
-                               na.omit(), 
-                             explainer = logistic_inters3_lime, 
-                             n_labels = 1,
-                             n_features = 3)
-
-  # Join the lime and explain objects in a list
-  lime_explain_inters3 <- list(lime = lime_inters3, explain = explain_inters3)
-
-  # Save the lime and explain objects
-  saveRDS(lime_explain_inters3, "./data/lime_explain_inters3.rds")
-
-} else {
-
-  # Load the lime and explain objects
-  lime_explain_inters3 <- readRDS("./data/lime_explain_inters3.rds")
-
-}
-```
-
-```{r}
-plot_features(lime_explain_inters3$explain[1:12,])
+hamby224_test %>% filter(case == 1)
 ```

### 2019-02-26 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
more on pres and training and testing data

@@
   select(-bbl1, -bbl2)
+
+hamby173and252_train_cleaning %>%
+  mutate(id = as.character(1:n())) %>%
+  GGally::ggparcoord(columns = rf_features, order = "columns", groupColumn = id)
 ```

### 2019-02-27 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
more on pres and training and testing data
worked on gg pres

--- 2019-02-26 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
@@
 ---
-title: "Applying LIME to a Random Forest Model and the Problems that Ensue"
-author: "Katherine Goode"
-date: "March 1, 2019"
+title: "[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Clumber_Park) Applying LIME to a Random Forest Model"
+author: Katherine Goode
+date: ISU Graphics Group <div style="margin-bottom:100px;"> March 1, 2019
 output:
@@
 
-# Get Started
+# Overview
+
+.pull-left[
+### Goals for the talk
+- Explain the LIME algorithm
+- Present an application of LIME
+- Highlight problems with this application
+
+### The plan
+
+1. Explanation of LIME 
+2. Hamby bullet data
+3. Applying LIME to the bullet data
+4. Issues with LIME
+5. Attempts at a solution
+6. Future work
+]
+
+.pull-right[
+<br>
+<br>
+<img src="./images/lime_drawing.png" width = 400>
+]
+
+---
+
+class: inverse, center, middle
+
+# What is <span style="color:lime">LIME</span>?
+
+---
+
+# Motivation for LIME
+
+<br>
+
+[![](./images/blackbox.png)](https://en.wikipedia.org/wiki/Black_box)
+
+### Black Box Prediction Models
+
+- Offer great predictive ability 
+- Loss of interpretability
+- Difficult to assess trustworthiness
+
+### Enter LIME
+
+- **L**ocal **I**nterpretable **M**odel-Agnostic **E**xplanations
+- Developed by computer scientists ([Ribeiro, Singh, and Guestrin](https://arxiv.org/pdf/1602.04938.pdf))
+- Designed to assess if a black box predictive model is trustworthy
+- Produces "explanations" for individual predictions
+
+---
+
+# Meaning of LIME
+
+.pull-left[
+### <span style="color:lime">L</span>ocal
+
+- Focuses on behavior of a complex model at a local level
+
+### <span style="color:lime">I</span>nterpretable
+
+- Produces easily interpretable "explanations"
+
+### <span style="color:lime">M</span>odel-Agnostic
+
+- Works with any black-box predictor
+
+### <span style="color:lime">E</span>xplanations
+
+- Provides insight into individual predictions
+]
+
+.pull-right[
+<br>
+<br>
+.center[<img src="./images/local.png" width=300>]
+.center[<font size="4">Figure 3 in Ribeiro, Singh, and Guestrin (2016)</font>]
+<br>
+<br>
+.center[<img src="./images/image_explanation.png" width=500>]
+.center[<font size="4">Figure 4 in Ribeiro, Singh, and Guestrin (2016)</font>]
+]
+
+---
+
+# An Example <font size="3">(from Ribeiro, Singh, and Guestrin (2016))</font>
+
+.pull-left[
+### 1. Black Box Model 
+- Model predicts whether a patient has the flu
+- Apply the model to a new patient
+- Predicts that the patient has the flu
+- Can this prediction be trusted?
+]
+
+.pull-right[
+### 2. LIME
+- Apply LIME to *this* case
+- LIME returns the most important variables in *this* prediction
+- Colors indicate
+    + <span style="color:green">green</span>: evidence supporting the flu
+    + <span style="color:red">red</span>: evidence against the flu
+- Can this prediction be trusted?
+]
+
+.center[<img src="./images/example.png" width=700>]
+.center[<font size="4">Figure 1 in Ribeiro, Singh, and Guestrin (2016)</font>]
+
+---
+
+# Using LIME
+
+### Implementations of LIME
+
+- Developers created a Python package
+- Thomas Pedersen created an R package called lime
+
+![](./images/lime.png)
+
+---
+
+class: inverse, center, middle
+
+# Hamby Bullet Matching Data
+
+---
+class: inverse, center, middle
+
+# Applying LIME to the bullet data
+
+---
+class: inverse, center, middle
+
+# Issues with LIME
+
+---
+class: inverse, center, middle
+
+# Attempts at a Solution
+
+---
+class: inverse, center, middle
+
+# Future Work

### 2019-02-28 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
worked more on presentation

---
title: "[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Tilia) An Application of LIME to a Random Forest"
author: <font size="5"> Katherine Goode </font>
date: <font size="5"> ISU Graphics Group, March 1, 2019 </font>
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, eval = FALSE)
```

# Overview

.pull-left[
### Goals for the talk
- Explain the LIME algorithm
- Present an application of LIME
- Highlight problems with this application

### The plan

1. Explanation of LIME 
2. Hamby bullet data
3. Applying LIME to the bullet data
4. Issues with LIME
5. Attempts at a solution
6. Future work
]

.pull-right[
<br>
<br>
<img src="./images/lime_drawing.png" width = 400>
]

---

class: inverse, center, middle

# What is <span style="color:lime">LIME</span>?

---

# Motivation for LIME

<br>

[![](./images/blackbox.png)](https://en.wikipedia.org/wiki/Black_box)

### Black Box Prediction Models

- Offer great predictive ability 
- Loss of interpretability
- Difficult to assess trustworthiness

### Enter LIME

- **L**ocal **I**nterpretable **M**odel-Agnostic **E**xplanations
- Developed by computer scientists ([Ribeiro, Singh, and Guestrin](https://arxiv.org/pdf/1602.04938.pdf))
- Designed to assess if a black box predictive model is trustworthy
- Produces "explanations" for individual predictions

---

# Meaning of LIME

.pull-left[
### <span style="color:lime">L</span>ocal

- Focuses on behavior of a complex model at a local level

### <span style="color:lime">I</span>nterpretable

- Produces easily interpretable "explanations"

### <span style="color:lime">M</span>odel-Agnostic

- Works with any black-box predictor

### <span style="color:lime">E</span>xplanations

- Provides insight into individual predictions
]

.pull-right[
<br>
<br>
.center[<img src="./images/local.png" width=300>]
.center[<font size="4">Figure 3 in Ribeiro, Singh, and Guestrin (2016)</font>]
<br>
<br>
.center[<img src="./images/image_explanation.png" width=500>]
.center[<font size="4">Figure 4 in Ribeiro, Singh, and Guestrin (2016)</font>]
]

---

# An Example <font size="3">(from Ribeiro, Singh, and Guestrin (2016))</font>

.pull-left[
### 1. Black Box Model 
- Model predicts whether a patient has the flu
- Apply the model to a new patient
- Predicts that the patient has the flu
- Can this prediction be trusted?
]

.pull-right[
### 2. LIME
- Apply LIME to *this* case
- LIME returns the most important variables in *this* prediction
- Colors indicate
    + <span style="color:green">green</span>: evidence supporting the flu
    + <span style="color:red">red</span>: evidence against the flu
- Can this prediction be trusted?
]

.center[<img src="./images/example.png" width=700>]
.center[<font size="4">Figure 1 in Ribeiro, Singh, and Guestrin (2016)</font>]

---

# Idea of the LIME Procedure

Start with training data, complex model, and one prediction from the test data
1. Use the features in the training data to create a new dataset of many perturbations.
2. Obtain a prediction for each perturbation using the complex model.
3. Compute a similarity score between the test observation and each perturbation. 
4. Perform feature selection to choose $k$.
5. Fit a linear regression (weighted by the similarity scores) to the perturbations with the $k$ chosen features (standardized).
  $$\mbox{prediction} \sim \mbox{chosen feature 1} + \cdots + \mbox{chosen feature k}$$
6. Use the coefficients from the regression to "explain" the predictions.

| | Feature 1 | <span style="color:blue">Feature 2</span> | <span style="color:blue">Feature 3</span> | Feature 4 | Similarity Score | Prediction |
| --: | :--: | :--: | :--: | :--: | :--: | :--: |
| test observation | 2 | 4 | 2 | 10 | exact | $\hat{y}_{\mbox{obs}}$ |
| perturbation 1 | 2 | 3 | 2 | 12 | very close | $\hat{y}_1$ |
| $\vdots$ | $\vdots$ | ... | ... | ... | ... | 
| perturbation 5000  | 10 | 0 | 13 | 22 | not close | $\hat{y}_{5000}$ |

---

# Using LIME

### Implementations of LIME

- Developers created a Python package called [lime](https://github.com/marcotcr/lime)
- Thomas Pedersen created an R package also called [lime](https://github.com/thomasp85/lime)

.pull-left[
```{r eval = FALSE}
#install.packages("lime")
library(lime)
?lime
?explain
```
]

.pull-right[![](./images/lime.png)]
---

class: inverse, center, middle

# Hamby Bullet Matching Data

---
class: inverse, center, middle

# Applying LIME to the bullet data

---

# <span style="color:lime">LIME</span> Procedure with Iris Data (in R)

## Step 0: Split iris data into training and testing datasets

```{r, echo = TRUE}
# Iris dataset
iris[1:3, ]

# Split up the data set into training and testing datasets
iris_test <- iris[1:5, 1:4]
iris_train <- iris[-(1:5), 1:4]

# Create a vector with the responses for the training dataset
iris_lab <- iris[[5]][-(1:5)]
```

---

## Step 1: Fit a complex model to the training data

```{r, echo = TRUE}
# Create random forest model on iris data
library(caret)
rf_model <- train(iris_train, iris_lab, method = 'rf')

# Can use the complex model to make predictions
Pred <- predict(rf_model, iris_test)
Actual <- iris[1:5, 5]
data.frame(iris_test, Pred, Actual)
```

---

## Step 2: Obtain distributions of the variables from the training data

```{r, echo = TRUE}
# Create an explainer object
library(lime); explainer <- lime(iris_train, rf_model)

# Sepal length quantiles obtained from training data
explainer$bin_cuts$Sepal.Length

# Probability distribution for sepal length
explainer$feature_distribution$Sepal.Length
```

---

## | Histogram of Sepal Length from Training Data

```{r, fig.width = 8, fig.height = 5, fig.align = "center"}

# Histogram of sepal length from training data
ggplot(iris_train, aes(x = Sepal.Length)) +
  geom_histogram(bins = 10, color = "grey") +
  geom_vline(xintercept = explainer$bin_cuts[[1]][[1]], color = "green", size = 1) +
  geom_vline(xintercept = explainer$bin_cuts[[1]][[2]], color = "green", size = 1) +
  geom_vline(xintercept = explainer$bin_cuts[[1]][[3]], color = "green", size = 1) +
  geom_vline(xintercept = explainer$bin_cuts[[1]][[4]], color = "green", size = 1) +
  geom_vline(xintercept = explainer$bin_cuts[[1]][[5]], color = "green", size = 1) +
  labs(x = "Sepal Length", y = "Count")
```

---

## Step 3: Sample from each of the variable distributions $n$ times

Histograms of predictor variables from training data

```{r, out.width = "500px", fig.align = "center"}
knitr::include_graphics("./Graphics/training_distributions.png")
```

---

## | Histograms of $n=5000$ samples from distributions of training variables for each of the five testing cases

```{r, out.width = "550px", fig.align = "center"}
knitr::include_graphics("./Graphics/samples.png")
```

---

## Step 4: Obtain predictions for sampled values using the complex model

* For each testing case use the random forest model to make a prediction for each of the $n=5000$ samples
* In the iris data, the predictions are represented by the probability that a flower is a particular species

```{r}
perturb <- read.csv("./Data/perturb_predictions.csv")
perturb
```

---

## Step 5: Obtain similarity score between data observation and sampled values

We need to determine how similar a sampled case is to the observed case in the testing data

Case 1 from testing data:
```{r}
iris_test[1, ]
```

First sample from training data variable distributions associated with case 1 of testing data:
```{r}
perturb[1, 1:4]
```

----

LIME uses exponential kernel function
  $$\pi_{x_{obs}}(x_{sampled}) = exp\left\{\frac{−D(x_{obs}, \ x_{sampled})^2}{σ^2}\right\}$$
where

$x_{obs}$: observed data vector to predict

$x_{sampled}$: sampled data vector from distribution of training variables

$D(\cdot \ , \ \cdot)$: distance function such as euclidean distance, cosine distance, etc.  
$\sigma$: width (default set to 0.75 in `lime`)

---

## Step 6: Perform feature selection by fiting a model to the sampled data and associated predictions (weighted by the similarity scores)

* The user can specify the number of variables (features) they would like to select: $m$
* With the iris data, the following three models will be fit to perform variable selection to select $m=2$ features:

$$\mbox{P(setosa)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$
$$\mbox{P(versicolor)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$
$$\mbox{P(virginica)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$

----

* To perform variable selection `lime` supports: 
    - forward selection with ridge regression
    - highest weight with ridge regression
    - LASSO
    - tree models
    - auto: forward selection if $m\le6$, highest weight otherwise

---

## Step 7: Fit a simple model to regress the predictions on the $m$ selected predictor variables (weighted by the similarity scores)

* Currently, `lime` is programmed to use ridge regression as the "simple" model
* If the response is categorical, the user can select how many categories they want to explain
* In this example, only setosa will be explained
* If petal length and sepal length were selected as the most important features for the first case in the testing data, then the simple model is

  $$\mbox{P(Setosa)} \sim \mbox{Petal.Length} + \mbox{Sepal.Length} $$

---

## Step 8: Extract the feature weights and use them as the explanations

* Steps 3 through 8 are all performed using the `explain` function in `lime`
* Steps 3 through 7 all happen behind the scenes
* The "feature weights" that are extracted are the coefficients for the predictor variables from the ridge regression

```{r, echo = TRUE}
# Explain new observation
explanation <- explain(iris_test, explainer, n_labels = 1, 
                       n_features = 2, n_permutations = 5000,
                       feature_select = 'auto')
```

----

```{r, echo = TRUE}
explanation[1:2, 1:6]
explanation[1:2, 7:10]
explanation[1:2, 11:13]
```

---

## | Plot of explanations for predictions from random forest model trained on iris data

```{r, echo = TRUE}
plot_features(explanation)
```

---
class: inverse, center, middle

# Issues with LIME

---
class: inverse, center, middle

# Attempts at a Solution

---
class: inverse, center, middle

# Future Work

### 2019-02-28 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
finished first section of talk

@@
 .pull-left[
-### Goals for the talk
-- Explain the LIME algorithm
-- Present an application of LIME
-- Highlight problems with this application
-
 ### The plan
@@
 
-# Idea of the LIME Procedure
+# Generalized Version of the LIME Procedure
 
@@
 
-| | Feature 1 | <span style="color:blue">Feature 2</span> | <span style="color:blue">Feature 3</span> | Feature 4 | Similarity Score | Prediction |
+| | Feature 1 | <span style="color:blue">Feature 2</span> | <span style="color:blue">Feature 3</span> | Feature 4 | Similarity Score | <span style="color:blue">Prediction</span>|
 | --: | :--: | :--: | :--: | :--: | :--: | :--: |
@@
 
-.pull-left[
+![](./images/lime.png)
+
+### Key Functions in the lime R package
+
 ```{r eval = FALSE}
@@
 ```
-]
 
-.pull-right[![](./images/lime.png)]
 ---

### 2019-03-01 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd
a lot of work on pres

@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "bottom") + 
+        legend.position = "none") + 
   labs(x = "Bin Type", y = "MSE", color = "") + 
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom") + 
+        legend.position = "none") + 
   labs(x = "Bin Type", y = "Average R2", color = "") + 
@@
   coord_flip() + 
-  facet_wrap(situation ~ ., ncol = 4, scales = "free_y") +
+  facet_wrap(situation ~ ., ncol = 5, scales = "free_y") +
   theme(legend.position = "bottom",
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
+  labs(x = "Cases", y = "Rep", fill = "Feature",
+       title = "First Feature")
 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
+  labs(x = "Cases", y = "Rep", fill = "Feature",
+       title = "Second Feature")
 
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  labs(x = "cases")
+  labs(x = "Cases", y = "Rep", fill = "Feature",
+       hamby224_sensitivity_joined %>%
+  filter(set == "Set 1") %>%
+  droplevels() %>%
+  select(situation, case, rep, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
+  group_by(situation, case, rep) %>%
+  slice(3) %>%
+  ungroup() %>%
+  group_by(situation, case) %>%
+  mutate(nlevels = length(levels(factor(feature)))) %>%
+  ungroup() %>%
+  arrange(situation, desc(nlevels), case, feature) %>%
+  mutate(order = rep(rep(1:length(levels(factor(case))), each = 10), 22)) %>%
+  ggplot(aes(x = order, fill = feature)) + 
+  geom_bar(position = "stack", width = 1) + 
+  coord_flip() + 
+  facet_wrap(situation ~ ., ncol = 5, scales = "free_y") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  labs(x = "Cases", y = "Rep", fill = "Feature",
+       title = "Third Feature"))
 ```

### 2019-03-01 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
quick fix
a lot of work on pres

@@
 options(htmltools.dir.version = FALSE, eval = FALSE)
+
+# Load libraries
+library(gt)
+library(randomForest)
+library(tidyverse)
 ```
@@
 2. Hamby bullet data
-3. Applying LIME to the bullet data
-4. Issues with LIME
-5. Attempts at a solution
+3. Applying LIME to the random forest
+4. Issues with LIME and attempts at a solution
 6. Future work
@@
 
-# Generalized Version of the LIME Procedure
+# General LIME Procedure
 
 Start with training data, complex model, and one prediction from the test data
-1. Use the features in the training data to create a new dataset of many perturbations.
+1. Create perturbations based on training data.
 2. Obtain a prediction for each perturbation using the complex model.
@@
 | perturbation 1 | 2 | 3 | 2 | 12 | very close | $\hat{y}_1$ |
-| $\vdots$ | $\vdots$ | ... | ... | ... | ... | 
+| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | 
 | perturbation 5000  | 10 | 0 | 13 | 22 | not close | $\hat{y}_{5000}$ |
@@
 ---
-class: inverse, center, middle
 
-# Applying LIME to the bullet data
+# Hamby Bullet Study [<font size="3">James E. Hamby et. al. (2009)</font>](https://cdn2.hubspot.net/hub/71705/file-15668427-pdf/docs/aftespringvol41no2pages99-110.pdf)
+
+- Sets of bullets from both “known” and “unknown” gun barrels were sent to firearm examiners around the world
+- 240 total sets created
+    - 10 barrels in a set
+    - 35 bullets in a set 
+        - 20 known (2 from the same barrel)
+        - 15 unknowns (at least 1 and no more than 3 from each barrel)
+- Examiners asked to use the known bullets to identify which barrels the unknown bullets were fired from
+
+.center[<img src="./images/hamby.png" width=350>]
+.center[<font size="4">Results table from Hamby et. al. (2009)</font>]
 
@@
 
-# <span style="color:lime">LIME</span> Procedure with Iris Data (in R)
+# Automated Bullet Matching Algorithm
 
-## Step 0: Split iris data into training and testing datasets
+- CSAFE has access to some of the bullet sets
+- [Hare, Hofmann, and Carriquiry ](https://projecteuclid.org/euclid.aoas/1514430288)(2017) develop an automated algorithm to determine whether two bullets are a match
+- High definition scans of bullets used to obtain signatures associated with each land
+- Developed variables that measure how similar two signatures are
+- Fit a random forest model to predict whether two bullets were a match
 
-```{r, echo = TRUE}
-# Iris dataset
-iris[1:3, ]
+.center[<img src="./images/signatures.png" width=575>]
+.center[<font size="4">Figure from Hare, Hofmann, and Carriquiry (2017)</font>]
 
-# Split up the data set into training and testing datasets
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
+---
 
-# Create a vector with the responses for the training dataset
-iris_lab <- iris[[5]][-(1:5)]
+# Training Data
+
+#### Sets 173 and 252
+
+```{r}
+hamby173and252_train <- read.csv("./data/hamby173and252_train.csv") # 83,028 rows
+```
+
+#### Variables Identifying the Bullets
+
+```{r}
+hamby173and252_train %>% select(1:8) %>% slice(1:5)
 ```
@@
 
-## Step 1: Fit a complex model to the training data
+# Training Data
 
-```{r, echo = TRUE}
-# Create random forest model on iris data
-library(caret)
-rf_model <- train(iris_train, iris_lab, method = 'rf')
+#### Signature Similarity Features
 
-# Can use the complex model to make predictions
-Pred <- predict(rf_model, iris_test)
-Actual <- iris[1:5, 5]
-data.frame(iris_test, Pred, Actual)
+```{r}
+hamby173and252_train %>% select(9:17) %>% slice(1:5) %>% round(2)
+```
+
+#### Response and RF Score
+
+```{r}
+hamby173and252_train %>% select(18:19) %>% slice(1:5)
 ```
@@
 
-## Step 2: Obtain distributions of the variables from the training data
+# Random Forest Model
 
-```{r, echo = TRUE}
-# Create an explainer object
-library(lime); explainer <- lime(iris_train, rf_model)
+The random forest model fit to the training data in Hare, Hofmann, and Carriquiry can be found in the bulletr R package. It is called `rtrees`.
 
-# Sepal length quantiles obtained from training data
-explainer$bin_cuts$Sepal.Length
+.pull-left[
+```{r}
+# Load the bulletr library
+library(bulletr)
+```
+```{r}
+# Importance values from 
+# the random forest
+rtrees$importance
+```
+]
 
-# Probability distribution for sepal length
-explainer$feature_distribution$Sepal.Length
+.pull-right[
+```{r}
+# Number of trees
+rtrees$ntree
+
+# Number of variables randomly 
+# sampled at each split
+rtrees$mtry
+
+# Confusion matrix
+rtrees$confusion
+```
+]
+
+---
+
+# Testing Data
+
+```{r}
+hamby224_test <- read.csv("./data/hamby224_test.csv")
+glimpse(hamby224_test)
 ```
@@
 
-## | Histogram of Sepal Length from Training Data
+# Testing Data
 
-```{r, fig.width = 8, fig.height = 5, fig.align = "center"}
+#### Results from Applying `rtrees` to Hamby 224 (Sets 1 and 11)
 
-# Histogram of sepal length from training data
-ggplot(iris_train, aes(x = Sepal.Length)) +
-  geom_histogram(bins = 10, color = "grey") +
-  geom_vline(xintercept = explainer$bin_cuts[[1]][[1]], color = "green", size = 1) +
-  geom_vline(xintercept = explainer$bin_cuts[[1]][[2]], color = "green", size = 1) +
-  geom_vline(xintercept = explainer$bin_cuts[[1]][[3]], color = "green", size = 1) +
-  geom_vline(xintercept = explainer$bin_cuts[[1]][[4]], color = "green", size = 1) +
-  geom_vline(xintercept = explainer$bin_cuts[[1]][[5]], color = "green", size = 1) +
-  labs(x = "Sepal Length", y = "Count")
+<br>
+
+```{r echo = FALSE}
+data.frame(Truth = hamby224_test$samesource %>% na.omit(),
+           RF_Prediction = as.logical(predict(rtrees, hamby224_test %>%
+                                       select(ccf:sum_peaks) %>% 
+                                       na.omit()))) %>%
+  count(Truth, RF_Prediction) %>%
+  rename(Count = n) %>%
+  gt::gt()
+```
+
+<br>
+
+- Want to know which were the driving variables for individual predictions
+- Especially great when the model is wrong
+- Variable importance scores provide global interpretations
+- We want local interpretations
+
+---
+
+class: inverse, center, middle
+
+# Applying <span style="color:lime">LIME</span> to the Random Forest
+
+---
+
+# Step 0: Starting Objects
+
+**Training Data**: `hamby173and252_train`
+
+**Complex Model**: `rtrees`
+
+**Case of Interest**: case 1 from `hamby224_test`
+
+<br>
+
+```{r echo = FALSE}
+hamby224_test %>% filter(case == 1) %>% select(case:land2) %>% gt()
+```
+
+<br>
+
+```{r echo = FALSE}
+hamby224_test %>% filter(case == 1) %>% select(ccf:rfscore) %>% round(2) %>% gt()
 ```
@@
 
-## Step 3: Sample from each of the variable distributions $n$ times
+# Step 1: Create Perturbations
 
-Histograms of predictor variables from training data
+#### Estimate the feature distributions
 
-```{r, out.width = "500px", fig.align = "center"}
-knitr::include_graphics("./Graphics/training_distributions.png")
+.pull-left[
+- quantile bins (default with 4 bins)
+- equally spaced bins
+]
+.pull-right[
+- normal approximation 
+- kernel density estimation
+]
+.center[
+```{r echo = FALSE, fig.height = 4.5, fig.width = 9}
+limeout <- lime::lime(x = hamby173and252_train %>% select(ccf:sum_peaks), model = rtrees)
+ggplot(hamby173and252_train, aes(x = ccf)) + 
+  geom_histogram(bins = 30) + 
+  geom_vline(xintercept = limeout$bin_cuts$ccf[[1]], color = "green", size = 1) +
+  geom_vline(xintercept = limeout$bin_cuts$ccf[[2]], color = "green", size = 1) +
+  geom_vline(xintercept = limeout$bin_cuts$ccf[[3]], color = "green", size = 1) +
+  geom_vline(xintercept = limeout$bin_cuts$ccf[[4]], color = "green", size = 1) +
+  geom_vline(xintercept = limeout$bin_cuts$ccf[[5]], color = "green", size = 1) +
+  geom_vline(xintercept = hamby224_test %>% 
+               filter(case == 1) %>% 
+               select(ccf) %>%
+               pull(), color = "blue", size = 1) +
+  labs(x = "CCF", y = "Frequency") +
+  theme(text = element_text(size = 18))
+```
+]
+.center[<font size="4">Histogram of CCF from Training Data with LIME Quantile Bins (blue line is ccf value of case 1)</font>]
+
+---
+
+# Step 1: Create Perturbations
+
+#### Draw many samples from the estimated feature distributions to obtain the perturbations
+
+- If the a binning estimation method is used, numeric features are converted to indicator variables.
+    - 1 if in same bin as case 1
+    - 0 o.w.
+
+| | ccf same bin? | rough_cor same bin? | $\cdots$ | sum_peaks same bin?|
+| --: | :--: | :--: | :--: | :--: | 
+| case 1 | 1 | 1 | $\cdots$ | 1 |
+| perturbation 1 | 0 | 1 | $\cdots$ | 1 |
+| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |
+| perturbation 5000  | 0 | 0 | $\cdots$ | 1|
+
+- Otherwise, features are left as is.
+
+---
+
+# Step 2: Obtain Predictions
+
+#### Use the complex model to obtain a prediction for each perturbation
+
+- Use the `rtrees` model to do this
+
+<br>
+
+| | ccf same bin? | rough_cor same bin? | $\cdots$ | sum_peaks same bin?| prediction |
+| --: | :--: | :--: | :--: | :--: | :--: |
+| case 1 | 1 | 1 | $\cdots$ | 1 | not a match |
+| perturbation 1 | 0 | 1 | $\cdots$ | 1 | match |
+| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |
+| perturbation 5000  | 0 | 0 | $\cdots$ | 1 | not a match |
+
+---
+
+# Step 3: Similarity Score
+
+#### Compute a similiarity score between the test observation and each perturbation.
+
+- Default method in R package is gower distance
+    - between 0 and 1 
+    - 0 indicates exactly the same
+- Other distance metrics can be specified
+
+| | ccf same bin? | rough_cor same bin? | $\cdots$ | sum_peaks same bin?| distance | prediction |
+| --: | :--: | :--: | :--: | :--: | :--: |
+| case 1 | 1 | 1 | $\cdots$ | 1 | 0 | not a match |
+| perturbation 1 | 0 | 1 | $\cdots$ | 1 | 0.1 | match |
+| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |
+| perturbation 5000  | 0 | 0 | $\cdots$ | 1 | 0.8 | not a match |
+
+---
+
+# Step 4: Feature Selection
+
+#### Perform feature selection to choose $k$ features.
+
+- Can specify the number of features to select
+    - We have been choosing 3 features
+- Options in lime
+     - auto: forward selection if $m\le6$, highest weight otherwise (default)
+     - forward selection with ridge regression
+     - highest weight with ridge regression
+     - LASSO
+     - tree models
+- We have been using the default method
+
+$$\mbox{rf score}=\beta_0 + \beta_1 I[\mbox{ccf in same bin}] + \beta_2 I[\mbox{rough_cor in same bin}] +\cdots + \beta_9 I[\mbox{sum_peaks in same bin}]$$
+
+---
+
+# Step 5: Simple Model
+
+#### Fit a linear regression (weighted by the similarity scores) to the perturbations with the 3 chosen features.
+
+- Features are standardized
+- Currently, lime uses ridge regression as the "simple" model
+- If the response is categorical, the user can select how many categories they want to explain
+    - We have only been explaining "TRUE"
+- Example model:
+
+$$\mbox{rf score}=\beta_0 + \beta_1 I[\mbox{ccf in same bin}] + \beta_2 I[\mbox{cms in same bin}] + \beta_3 I[\mbox{matches in same bin}]$$
+
+---
+
+# Step 6: Interpret
+
+#### Use the coefficients from the regression to "explain" the predictions.
+
+- Since features are standardized, we can compare the coefficients
+- Largest $\beta_i$ is conisdered the most important
+
+---
+
+# R Code
+
+## lime Function
+
+The `lime` function estimates the feature distributions (first part of step 1).
+
+```{r}
+set.seed(20190229)
+out_lime <- lime::lime(x = hamby173and252_train %>% select(ccf:sum_peaks), 
+                      model = lime::as_classifier(rtrees))
+out_lime$bin_cuts$ccf
+out_lime$feature_distribution$ccf
 ```
@@
 
-## | Histograms of $n=5000$ samples from distributions of training variables for each of the five testing cases
+# R Code
 
-```{r, out.width = "550px", fig.align = "center"}
-knitr::include_graphics("./Graphics/samples.png")
+## explain Function
+
+The `explain` function performs the rest of the steps.
+
+```{r}
+out_explain <- lime::explain(x = hamby224_test %>% filter(case == 1) %>%
+                               select(ccf:sum_peaks),
+                             explainer = out_lime,
+                             labels = TRUE,
+                             n_features = 3)
+out_explain[,1:6]
+out_explain[,7:10]
 ```
@@
 
-## Step 4: Obtain predictions for sampled values using the complex model
+# R Code
 
-* For each testing case use the random forest model to make a prediction for each of the $n=5000$ samples
-* In the iris data, the predictions are represented by the probability that a flower is a particular species
+## R Package Plot of Explanations
 
-```{r}
-perturb <- read.csv("./Data/perturb_predictions.csv")
-perturb
+The function `plot_features` let you visualize the explanations.
+
+```{r fig.width = 10, fig.height = 5}
+lime::plot_features(out_explain)
 ```
@@
 
-## Step 5: Obtain similarity score between data observation and sampled values
+# Shiny App
 
-We need to determine how similar a sampled case is to the observed case in the testing data
+<br>
 
-Case 1 from testing data:
-```{r}
-iris_test[1, ]
-```
-
-First sample from training data variable distributions associated with case 1 of testing data:
-```{r}
-perturb[1, 1:4]
-```
-
-----
-
-LIME uses exponential kernel function
-  $$\pi_{x_{obs}}(x_{sampled}) = exp\left\{\frac{−D(x_{obs}, \ x_{sampled})^2}{σ^2}\right\}$$
-where
-
-$x_{obs}$: observed data vector to predict
-
-$x_{sampled}$: sampled data vector from distribution of training variables
-
-$D(\cdot \ , \ \cdot)$: distance function such as euclidean distance, cosine distance, etc.  
-$\sigma$: width (default set to 0.75 in `lime`)
-
----
-
-## Step 6: Perform feature selection by fiting a model to the sampled data and associated predictions (weighted by the similarity scores)
-
-* The user can specify the number of variables (features) they would like to select: $m$
-* With the iris data, the following three models will be fit to perform variable selection to select $m=2$ features:
-
-$$\mbox{P(setosa)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$
-$$\mbox{P(versicolor)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$
-$$\mbox{P(virginica)} \sim \mbox{Sepal.Length} + \mbox{Sepal.Width} + \mbox{Petal.Length} + \mbox{Petal.Width}$$
-
-----
-
-* To perform variable selection `lime` supports: 
-    - forward selection with ridge regression
-    - highest weight with ridge regression
-    - LASSO
-    - tree models
-    - auto: forward selection if $m\le6$, highest weight otherwise
-
----
-
-## Step 7: Fit a simple model to regress the predictions on the $m$ selected predictor variables (weighted by the similarity scores)
-
-* Currently, `lime` is programmed to use ridge regression as the "simple" model
-* If the response is categorical, the user can select how many categories they want to explain
-* In this example, only setosa will be explained
-* If petal length and sepal length were selected as the most important features for the first case in the testing data, then the simple model is
-
-  $$\mbox{P(Setosa)} \sim \mbox{Petal.Length} + \mbox{Sepal.Length} $$
-
----
-
-## Step 8: Extract the feature weights and use them as the explanations
-
-* Steps 3 through 8 are all performed using the `explain` function in `lime`
-* Steps 3 through 7 all happen behind the scenes
-* The "feature weights" that are extracted are the coefficients for the predictor variables from the ridge regression
-
-```{r, echo = TRUE}
-# Explain new observation
-explanation <- explain(iris_test, explainer, n_labels = 1, 
-                       n_features = 2, n_permutations = 5000,
-                       feature_select = 'auto')
-```
-
-----
-
-```{r, echo = TRUE}
-explanation[1:2, 1:6]
-explanation[1:2, 7:10]
-explanation[1:2, 11:13]
-```
-
----
-
-## | Plot of explanations for predictions from random forest model trained on iris data
-
-```{r, echo = TRUE}
-plot_features(explanation)
-```
+.center[<img src="./images/app.png" width=1100>]
 
@@
 
-# Issues with LIME
+# Issues with <span style="color:lime">LIME</span> and Attempts at a Solution
 
 ---
-class: inverse, center, middle
 
-# Attempts at a Solution
+# Initial Concerns
+
+We first applied lime using all default settings
+- explanations did not make sense
+- $R^2$ values were very low
+- predictions from the simple model were poor
+
+.center[<img src="./images/explain1.png" width=450>]
+.center[<font size="4">Example where the random forest prediction is wrong. The explanations are from from 4 quantile bins.</font>]
+
+---
+
+# More Issues
+
+Then we tried more of the feature distribution estimaton methods
+- explanations still not great
+- $R^2$ values still very low
+- predictions from the simple model still poor
+- explanations dependent on the input
+
+.center[<img src="./images/explain2.png" width=450>]
+.center[<font size="4">This is the same case with explanations are from from 3 equally spaced bins.</font>]
+
+---
+
+# New Binning Method
+
+Next we created our own way to select bins using trees
+
+```{r echo = FALSE, message = FALSE}
+source("../../code/helper_functions.R")
+```
+
+.pull-left[
+```{r}
+# Example using treebink
+treebink(
+  y = hamby173and252_train$samesource, 
+  x = hamby173and252_train$ccf, 
+  k = 5
+)
+```
+]
+.pull-right[
+.center[<img src="./images/tree.png" height = 500>]
+]
+---
+
+# Comparing Methods
+
+#### Feature distribution estimaton methods:
+
+- 2 to 5 quntile bins
+- 2 to 5 equally spaced bins
+- 2 to 5 tree based bins with `samesoure` as the response
+- 2 to 5 tree based bins with `rfscore` as the response
+- normal approximation
+- kernel density estimation
+
+#### Comparison metrics:
+
+- MSEs (rf prediction vs simple model predictions)
+- $R^2$
+- Consistency across number of bins
+- Consistency across 10 reps
+
+---
+
+# Comparing MSEs
+
+.center[<img src="./images/mse.png" width = 900>]
+
+---
+
+# Comparing $R^2$ Values
+
+.center[<img src="./images/r2.png" width = 900>]
+
+---
+
+# Comparing Consistency Across Bins
+
+.center[<img src="./images/firstfeature.png" width = 1100>]
+
+---
+
+# Comparing Consistency Across Bins
+
+.center[<img src="./images/secondfeature.png" width = 1100>]
+
+---
+
+# Comparing Consistency Across Bins
+
+.center[<img src="./images/thirdfeature.png" width = 1100>]
+
+---
+
+# Comparing Consistency Across Reps
+
+.center[<img src="./images/reps1.png" width = 1100>]
+
+---
+
+# Comparing Consistency Across Reps
+
+.center[<img src="./images/reps2.png" width = 1100>]
+
+---
+
+# Comparing Consistency Across Reps
+
+.center[<img src="./images/reps3.png" width = 1100>]
+
+---
+
+# Conclusions
+
+#### Key Observations
+
+- equally spaced bins are dependent on the nubmer of bins
+- tree based bins usually have the lowest MSEs
+- rfscore tree based bins usually have the highest $R^2$ for the binning options
+- all options results in low $R^2$ values
+    - we think that the linear regression is not similar enough to a random forest to produce good explanations
+- explanations are relatively consistent across reps for first and second features
+- non-binning methods produce very different results
 

### 2019-03-01 code/helper_functions.R

@@ -11,6 +11,10 @@
 library(tidyverse)
 library(tree)
 
+y = hamby173and252_train$samesource
+x = hamby173and252_train$ccf
+k = 5
+
 treebink <- function (y, x, k, minsize = 10) {
   
   # Set the mindev: "The within-node deviance must be at least this times 

### 2019-03-01 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
some quick updates

@@
 4. Issues with LIME and attempts at a solution
-6. Future work
+6. Conclusions and future work
 ]
@@
 
-[![](./images/blackbox.png)](https://en.wikipedia.org/wiki/Black_box)
+![](./images/blackbox.png)
 
@@
 
-### Enter LIME
+### Enter LIME...
 
@@
 
-- Default method in R package is gower distance
+- Default method in R package is Gower distance
     - between 0 and 1 
@@
 - Since features are standardized, we can compare the coefficients
-- Largest $\beta_i$ is conisdered the most important
+- Largest $\beta_i$ is considered the most important
 
@@
 
-Then we tried more of the feature distribution estimaton methods
+Then we tried more of the feature distribution estimation methods
 - explanations still not great
@@
 
-- 2 to 5 quntile bins
+- 2 to 5 quantile bins
 - 2 to 5 equally spaced bins
@@
 
+class: middle, center, inverse
+
+# Conclusions and Future Work
+
+---
+
 # Conclusions
 
-#### Key Observations
-
-- equally spaced bins are dependent on the nubmer of bins
-- tree based bins usually have the lowest MSEs
+- Equally spaced bins are dependent on the number of bins
+- Tree based bins usually have the lowest MSEs
 - rfscore tree based bins usually have the highest $R^2$ for the binning options
-- all options results in low $R^2$ values
-    - we think that the linear regression is not similar enough to a random forest to produce good explanations
-- explanations are relatively consistent across reps for first and second features
-- non-binning methods produce very different results
+- All options results in low $R^2$ values
+    - We think that the linear regression is not similar enough to a random forest to produce good explanations
+- Explanations are relatively consistent across reps for first and second features
+- Non-binning methods produce very different results
 
 ---
-class: inverse, center, middle
 
 # Future Work
+
+- Apply LIME to explain a logistic regression model
+    - We know how to interpret a logistic regression
+    - Can compare to LIME explanations
+- Run some sort of simulation to assess LIME explanations
+- Adjust and compare weighting methods and the features selection methods
+- Allow the number of bins to vary across features
+- Use a tree as the simple model
+
+---
+
+# Image Credits
+
+- slide 1: https://www.flickr.com/photos/lincolnian/300262799
+- slide 2: https://ayoqq.org/explore/lime-drawing/
+- slide 3: https://en.wikipedia.org/wiki/Black_box 
+- slide 8: https://github.com/thomasp85/lime

### 2019-03-01 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
added code to folder
edits to presentation

@@
 3. Applying LIME to the random forest
-4. Issues with LIME and attempts at a solution
+4. Issues and attempts at a solution
 6. Conclusions and future work
@@
 
-- Works with any black-box predictor
+- Works with any predictive model
 
@@
 
-Start with training data, complex model, and one prediction from the test data
-1. Create perturbations based on training data.
-2. Obtain a prediction for each perturbation using the complex model.
-3. Compute a similarity score between the test observation and each perturbation. 
-4. Perform feature selection to choose $k$.
-5. Fit a linear regression (weighted by the similarity scores) to the perturbations with the $k$ chosen features (standardized).
-  $$\mbox{prediction} \sim \mbox{chosen feature 1} + \cdots + \mbox{chosen feature k}$$
-6. Use the coefficients from the regression to "explain" the predictions.
+**Start with**: (1) training data, (2) complex model, (3) one prediction from the testing data
+1. Create perturbations from training data
+2. Input each perturbation into complex model to get predictions
+3. Compute similarity scores between test observation and each perturbation 
+4. Perform feature selection to choose $k$ features
+5. Fit a simple and interpretable model weighted by the similarity scores to the perturbations
+  $$\mbox{Example: } \mbox{prediction} \sim \mbox{feature 2} + \mbox{feature 3} \ \ \ \mbox{(with features standardized)}$$
+6. Interpret the simple model to "explain" the predictions
 
@@
 - 240 total sets created
-    - 10 barrels in a set
+    - 10 barrels used to create a set
     - 35 bullets in a set 
-        - 20 known (2 from the same barrel)
+        - 20 knowns (2 from the same barrel)
         - 15 unknowns (at least 1 and no more than 3 from each barrel)
@@
 
-- Want to know which were the driving variables for individual predictions
-- Especially great when the model is wrong
+- Want to determine the driving variables for individual predictions
+- Especially helpful when the model is wrong
 - Variable importance scores provide global interpretations
@@
 ]
-.center[<font size="4">Histogram of CCF from Training Data with LIME Quantile Bins (blue line is ccf value of case 1)</font>]
+.center[<font size="4">Histogram of CCF from training data with LIME quantile bins (blue line is ccf value of case 1)</font>]
 
@@
 
-#### Draw many samples from the estimated feature distributions to obtain the perturbations
+#### Draw many samples from the estimated feature distributions
 
-- If the a binning estimation method is used, numeric features are converted to indicator variables.
+- If a binning estimation method is used, numeric features are converted to indicator variables.
     - 1 if in same bin as case 1
@@
 
-$$\mbox{rf score}=\beta_0 + \beta_1 I[\mbox{ccf in same bin}] + \beta_2 I[\mbox{rough_cor in same bin}] +\cdots + \beta_9 I[\mbox{sum_peaks in same bin}]$$
+<br>
+
+$$\hat{\mbox{rf score}}=\hat{\beta_0} + \hat{\beta_1} I[\mbox{ccf in same bin}] + \hat{\beta_2} I[\mbox{rough_cor in same bin}] +\cdots + \hat{\beta_9} I[\mbox{sum_peaks in same bin}]$$
 
@@
 
-$$\mbox{rf score}=\beta_0 + \beta_1 I[\mbox{ccf in same bin}] + \beta_2 I[\mbox{cms in same bin}] + \beta_3 I[\mbox{matches in same bin}]$$
+<br>
+
+$$\hat{\mbox{rf score}}=\hat{\beta_0} + \hat{\beta_1} I[\mbox{ccf in same bin}] + \hat{\beta_2} I[\mbox{cms in same bin}] + \hat{\beta_3} I[\mbox{matches in same bin}]$$
 
@@
 
-We first applied lime using all default settings
-- explanations did not make sense
+We first applied lime using all default settings.
+- Explanations did not make sense
 - $R^2$ values were very low
-- predictions from the simple model were poor
+-Predictions from the simple model were poor
 
 .center[<img src="./images/explain1.png" width=450>]
-.center[<font size="4">Example where the random forest prediction is wrong. The explanations are from from 4 quantile bins.</font>]
+.center[<font size="4">Example where the random forest prediction is wrong. The explanations are from 4 quantile bins.</font>]
 
@@
 .center[<img src="./images/explain2.png" width=450>]
-.center[<font size="4">This is the same case with explanations are from from 3 equally spaced bins.</font>]
+.center[<font size="4">This is the same case with explanations from 3 equally spaced bins.</font>]
 
@@
 ```{r echo = FALSE, message = FALSE}
-source("../../code/helper_functions.R")
+source("./code/helper_functions.R")
 ```
@@
 - Tree based bins usually have the lowest MSEs
-- rfscore tree based bins usually have the highest $R^2$ for the binning options
+- `rfscore` tree based bins usually have the highest $R^2$ for the binning options
 - All options results in low $R^2$ values
@@
 - Explanations are relatively consistent across reps for first and second features
-- Non-binning methods produce very different results
+- Non-binning methods produce very different results compared to the binning methods
 
@@
 
-- Apply LIME to explain a logistic regression model
+- Apply LIME to a logistic regression model
     - We know how to interpret a logistic regression
@@
 - Run some sort of simulation to assess LIME explanations
-- Adjust and compare weighting methods and the features selection methods
+- Adjust and compare weighting methods and the feature selection methods
 - Allow the number of bins to vary across features

### 2019-03-01 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
final edits to talk

@@
 author: <font size="5"> Katherine Goode </font>
-date: <font size="5"> ISU Graphics Group, March 1, 2019 </font>
+date: <font size="5"> ISU Graphics Group - March 1, 2019 </font>
 output:
@@
 - Options in lime
-     - auto: forward selection if $m\le6$, highest weight otherwise (default)
+     - auto: forward selection if $k\le6$, highest weight otherwise (default)
      - forward selection with ridge regression
@@
 - Since features are standardized, we can compare the coefficients
-- Largest $\beta_i$ is considered the most important
+- Largest $\hat{\beta}_i$ is considered the most important
 
@@
 - $R^2$ values were very low
--Predictions from the simple model were poor
+- Predictions from the simple model were poor
 
@@
 Then we tried more of the feature distribution estimation methods
-- explanations still not great
+- Explanations still not great
 - $R^2$ values still very low
-- predictions from the simple model still poor
-- explanations dependent on the input
+- Predictions from the simple model still poor
+- Explanations dependent on the input
 
@@
 - Use a tree as the simple model
+- Find other ways to interpret random forest models
 

### 2019-03-05 journals/07-logistic_regression/07-logistic_regression.Rmd
more on logistic regression

@@
 
-The output from the model is shown below.
+The output from this model is not shown.
 
-```{r}
+```{r eval = FALSE}
 # Summary of the model
@@
 
-### Comparing the Logistic Models
+### Comparing the Two Models
 
@@
 ```{r}
-data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
+data.frame(obs = hamby224_test %>% 
+             pull(samesource) %>% na.omit(),
+           mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
            inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
-  summarise_at(vars(mains, inters2), 
-               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
-               obs = hamby224_test %>% select(samesource) %>% na.omit())
+  mutate(mains_sqerrs = (obs - as.logical(mains))^2,
+         inters2_sqerrs = (obs - as.logical(inters2))^2) %>%
+  summarise_at(vars(mains_sqerrs, inters2_sqerrs), 
+               function(x) sum(x) / length(x)) %>%
+  rename(mains_mse = mains_sqerrs, inters2_mse = inters2_sqerrs)
 ```
@@
 
-### Main Effects Only
+### Default LIME Applied to Main Effects Model
 
@@
 plot_features(lime_explain_mains$explain[1:12,])
-hamby224_test %>% filter(case == 1)
+```
+
+```{r}
+coefs <- logistic_mains$finalModel$coefficients %>% round(2)
+```
+
+The logistic regression model is
+
+$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks
+
+where $\hat{p}=P(\mbox{samesource = TRUE})$.
+
+I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.
+
+```{r}
+m = function(x) coefs[2:10] * x
+m(hamby224_test[1,] %>% select(rf_features))
+hamby224_test[1:4,] %>% select(rf_features)
+coefs
+hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
+```
+
+```{r}
+mains_test_explain <- hamby224_test %>%
+  mutate(case = as.character(case)) %>%
+  full_join(lime_explain_mains$explain, by = "case") %>%
+  mutate(case = factor(case),
+         feature = factor(feature))
+```
+
+Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).
+
+```{r}
+mains_test_explain %>%
+  na.omit() %>%
+  arrange(case, desc(abs(feature_weight))) %>%
+  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
+  select(case, set, feature, feature_order) %>%
+  spread(feature_order, feature) %>%
+  arrange(set, first, second, third) %>%
+  mutate(order = 1:n()) %>%
+  gather(feature_order, feature, 3:5) %>%
+  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
+  geom_tile() + 
+  facet_grid(set ~ ., scales = "free_y") +
+  theme_bw() +
+  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
 ```

### 2019-03-05 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
made parallel coord plots

--- 2019-02-22 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
@@
 
+It is possible that the labels that Eric was using are different from the labels in my training dataset.
+In order to check whether I removed the correct datapoints, Heike suggested that I look at a parallel coordinate plots to see if the observations that were removed stand out as being unusual compared to the rest of the data.
+The code below prepares the training data before observations were removed to be plotted.
+
+```{r}
+# Create dataset for creating the paralle coordinate plot
+par_data <- hamby173and252_train_cleaning %>%
+  mutate(bbl1 = barrel1:bullet1:land1,
+         bbl2 = barrel2:bullet2:land2) %>%
+  mutate(category = factor(ifelse(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
+                                                "Unknown:Q:4") | 
+                                      bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
+                                                  "Unknown:Q:4")),
+                           "keep", "remove"))) %>%
+  arrange(category)
+
+my_colors <- colors()[par_data %>% pull(category) %>% as.numeric() * 11]
+table(my_colors)
+```
+
+The first plot shows the observations that were kept in aquamarine and the observations that were removed in bisque.
+These observations do not seem to be weird.
+I am wondering if I removed the correct points or not.
+The second plot shows the data plotted after the observations have been removed.
+There are not obvious points that really stand out as unusual, but there is so much data it also makes it hard to tell.
+
+```{r}
+MASS::parcoord(hamby173and252_train_cleaning %>% select(ccf:sum_peaks), col = my_colors)
+MASS::parcoord(hamby173and252_train %>% select(ccf:sum_peaks))
+```
+
 ### Saving the Training Data

### 2019-03-06 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
work during meeting and presentation moved

--- 2019-02-22 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
@@
 
+It is possible that the labels that Eric was using are different from the labels in my training dataset.
+In order to check whether I removed the correct datapoints, Heike suggested that I look at a parallel coordinate plots to see if the observations that were removed stand out as being unusual compared to the rest of the data.
+The code below prepares the training data before observations were removed to be plotted.
+
+```{r}
+# Create dataset for creating the paralle coordinate plot
+par_data <- hamby173and252_train_cleaning %>%
+  mutate(bbl1 = barrel1:bullet1:land1,
+         bbl2 = barrel2:bullet2:land2) %>%
+  mutate(category = factor(ifelse(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
+                                                "Unknown:Q:4") | 
+                                      bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
+                                                  "Unknown:Q:4")),
+                           "keep", "remove"))) %>%
+  arrange(category) %>%
+  mutate(samesource_colors = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.05), 
+                                    rgb(0, 0, 0, alpha = 0.001)),
+         samesource_colors2 = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.001), 
+                                    rgb(0, 0, 0, alpha = 0.01)),
+         tankrash_colors = ifelse(category == "keep", rgb(0, 0, 1, alpha = 0.05),
+                                  rgb(0, 0, 0, alpha = 0.01)))
+```
+
+The first plot shows the observations that were kept in black and the observations that were removed in blue.
+These observations do not stand out to me.
+It is not clear if these were the ones that were suppose to be removed or not.
+The second plot shows the observations from matches plotted in red, and the third plot shows the observations from nonmatches plotted in black.
+
+```{r}
+MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$tankrash_colors)
+MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors)
+MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors2)
+```
+
 ### Saving the Training Data

### 2019-03-11 journals/07-logistic_regression/07-logistic_regression.Rmd
work during meeting and presentation moved
quick fixes and prepared lime for logisitic regression

@@
 # Load libraries
+library(furrr)
+library(future)
 library(lime)
 library(tidyverse)
+
+# Source functions
+source("../../code/helper_functions.R")
 ```
@@
 }
-
-summary(logistic_mains)
 ```
@@
 
+```{r}
+pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
+pca_results$loadings
+z1 <- pca_results$scores[,1]
+z2 <- pca_results$scores[,2]
+ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
+  geom_point()
+biplot(pca_results)
+```
+
+### All Input Options of LIME Applied to Main Effects Model
+
+The code below applies the LIME algorithm to the main effects logisitic regression model one time for the following different input cases:
+
+- 2 to 6 quantile bins
+- 2 to 6 equally spaced bins
+- 2 to 6 tree based bins with `samesource` as the response variable
+- 2 to 6 tree based bins with `rfscore` as the response variable
+- kernel density estimation
+- normal density approximation
+
+It applies LIME using my function `run_lime` to specify the different input values.
+The outputs from the `lime` function are combined into a list, and the outputs from the `explain` function are combined into dataframe.
+Both are saved as .rds files.
+
+```{r}
+# Apply the run_lime function if the lime results file does not already exist
+if(!file.exists("./data/logistic_lime_inputs.rds")) {
+
+  # Specify the input options to use with lime
+  logistic_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
+                                                  rep(FALSE, 2)),
+                               quantile_bins = c(rep(TRUE, 5), 
+                                                 rep(FALSE, 5), 
+                                                 rep(TRUE, 12)),
+                               nbins = c(rep(2:6, 4), 
+                                         rep(4, 2)),
+                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
+                               bin_method = c(rep("quantile_bins", 5),
+                                              rep("equally_spaced", 5),
+                                              rep("tree", 10),
+                                              rep("quantile_bins", 2)),
+                               response = c(rep(NA, 10), 
+                                            rep("samesource", 5), 
+                                            rep("rfscore", 5), 
+                                            rep(NA, 2)))
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Apply lime to the full training data with the specified input options
+  logistic_lime_explain <- future_pmap(.l = logistic_lime_inputs,
+             .f = run_lime, # run_lime is one of my helper functions
+             features = rf_features,
+             train = hamby173and252_train,
+             test = hamby224_test %>% 
+               arrange(case) %>% 
+               select(rf_features) %>% 
+               na.omit(),
+             rfmodel = logistic_mains,
+             label = "TRUE",
+             nfeatures = 3,
+             seed = TRUE)
+
+  # Separate the lime and explain function results from the full data
+  logistic_lime <- map(logistic_lime_explain, function(list) list$lime)
+  logistic_explain <- map_df(logistic_lime_explain, function(list) list$explain)
+
+  # Name the items in the lime list
+  names(logistic_lime) <- map_chr(1:22, function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
+              logistic_lime_inputs$bin_continuous[case],
+              logistic_lime_inputs$quantile_bins[case],
+              logistic_lime_inputs$nbins[case],
+              logistic_lime_inputs$use_density[case],
+              logistic_lime_inputs$bin_method[case],
+              logistic_lime_inputs$response[case]))
+
+  # Turn the lime input options into a dataframe before saving it
+  logistic_lime_inputs <- logistic_lime_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(logistic_lime_inputs), 
+           dimnames = list(NULL, names(logistic_lime_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:length(logistic_lime_inputs$quantile_bins)) %>%
+    select(case, bin_continuous:response)
+
+  # Save the lime objects
+  saveRDS(logistic_lime_inputs, "./data/logistic_lime_inputs.rds")
+  saveRDS(logistic_lime, "./data/logistic_lime.rds")
+  saveRDS(logistic_explain, "./data/logistic_explain.rds")
+
+} else {
+
+  # Load in the lime objects
+  logistic_lime_inputs <- readRDS("./data/logistic_lime_inputs.rds")
+  logistic_lime <- readRDS("./data/logistic_lime.rds")
+  logistic_explain <- readRDS("./data/logistic_explain.rds")
+
+}
+```
+
 # Session Info

### 2019-03-11 code/helper_functions.R

@@ -11,10 +11,6 @@
 library(tidyverse)
 library(tree)
 
-y = hamby173and252_train$samesource
-x = hamby173and252_train$ccf
-k = 5
-
 treebink <- function (y, x, k, minsize = 10) {
   
   # Set the mindev: "The within-node deviance must be at least this times 

### 2019-03-11 journals/07-logistic_regression/07-logistic_regression.Rmd
updates to journals 06 and 07

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, cache = TRUE)
 ```
@@
 library(future)
+library(gretchenalbrecht)
 library(lime)
@@
 
-```{r}
-plot_features(lime_explain_mains$explain[1:12,])
-```
-
-```{r}
-coefs <- logistic_mains$finalModel$coefficients %>% round(2)
-```
-
-The logistic regression model is
-
-$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks
-
-where $\hat{p}=P(\mbox{samesource = TRUE})$.
-
-I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.
-
-```{r}
-m = function(x) coefs[2:10] * x
-m(hamby224_test[1,] %>% select(rf_features))
-hamby224_test[1:4,] %>% select(rf_features)
-coefs
-hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
-```
-
-```{r}
-mains_test_explain <- hamby224_test %>%
-  mutate(case = as.character(case)) %>%
-  full_join(lime_explain_mains$explain, by = "case") %>%
-  mutate(case = factor(case),
-         feature = factor(feature))
-```
-
-Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).
-
-```{r}
-mains_test_explain %>%
-  na.omit() %>%
-  arrange(case, desc(abs(feature_weight))) %>%
-  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
-  select(case, set, feature, feature_order) %>%
-  spread(feature_order, feature) %>%
-  arrange(set, first, second, third) %>%
-  mutate(order = 1:n()) %>%
-  gather(feature_order, feature, 3:5) %>%
-  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
-  geom_tile() + 
-  facet_grid(set ~ ., scales = "free_y") +
-  theme_bw() +
-  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
-```
-
-```{r}
-pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
-pca_results$loadings
-z1 <- pca_results$scores[,1]
-z2 <- pca_results$scores[,2]
-ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
-  geom_point()
-biplot(pca_results)
-```
-
 ### All Input Options of LIME Applied to Main Effects Model
@@
 
+```{r}
+# Create the test_explain combined data if the file does not already exist
+if(!file.exists("./data/logistic_test_explain.rds")) {
+
+  # Join the data and the explanations and edit and add additional variables
+  logistic_test_explain <- hamby224_test %>%
+    mutate(case = as.character(case)) %>%
+    full_join(logistic_explain, by = "case") %>%
+    mutate(case = factor(case),
+           feature_desc = factor(feature_desc),
+           feature = factor(feature),
+           nbins = factor(nbins)) %>%
+    arrange(nbins) %>%
+    mutate(nbins = as.numeric(as.character(nbins)),
+           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                              sprintf("%.0f quantile", nbins),
+                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                     sprintf("%.0f equally spaced", nbins),
+                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "samesource",
+                                            sprintf("%.0f samesource tree", nbins),
+                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "rfscore",
+                                              sprintf("%.0f rfscore tree", nbins),
+                                              ifelse(bin_continuous == FALSE & 
+                                                     use_density == TRUE, 
+                                                     "kernel density", 
+                                                     "normal approximation"))))) %>%
+             fct_relevel("2 quantile", "3 quantile", "4 quantile",
+                         "5 quantile", "6 quantile", "2 equally spaced",
+                         "3 equally spaced", "4 equally spaced",
+                         "5 equally spaced", "6 equally spaced",
+                         "2 samesource tree", "3 samesource tree",
+                         "4 samesource tree", "5 samesource tree",
+                         "6 samesource tree")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
+                                  bin_continuous == TRUE,
+                                  "quantile",
+                                  ifelse(bin_method == "equally_spaced" & 
+                                         bin_continuous == TRUE,
+                                         "equally spaced", 
+                                         ifelse(bin_method == "tree" & 
+                                                bin_continuous == TRUE & 
+                                                response == "samesource",
+                                                "samesource tree", 
+                                                ifelse(bin_method == "tree" & 
+                                                       bin_continuous == TRUE & 
+                                                       response == "rfscore",
+                                                       "rfscore tree", 
+                                                       ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                       "kernel density", 
+                                                       "normal approximation")))))) %>%
+    mutate(bin_situation = factor(bin_situation))
+
+  # Save the combined test and explain data
+  saveRDS(logistic_test_explain, "./data/logistic_test_explain.rds")
+
+} else {
+
+  # Load in the data
+  logistic_test_explain <- readRDS("./data/logistic_test_explain.rds")
+
+}
+```
+
+This code creates and saves a dataset with summaries of the explanations.
+
+```{r}
+# Create the lime comparison data if the file does not already exist
+if(!file.exists("./data/logistic_lime_comparisons.rds")) {
+
+  # Create a data frame with the interesting information relating to the different
+  # evaluations of lime and compute the difference and mean between the rf and rr
+  # model predictions
+  logistic_lime_comparisons <- logistic_test_explain %>%
+    select(-data, -prediction) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method, response) %>%
+    slice(1) %>%
+    ungroup() %>%
+    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, response, 
+           nbins, use_density, set, case, rf_features, rfscore, model_prediction, model_r2) %>%
+    mutate(diff = rfscore - model_prediction,
+           mean = (rfscore + model_prediction) / 2)
+
+  # Save the lime comparison data frame
+  saveRDS(logistic_lime_comparisons, "./data/logistic_lime_comparisons.rds")
+
+} else {
+
+  # Load in the lime comparison data frame
+  logistic_lime_comparisons <- readRDS("./data/logistic_lime_comparisons.rds")
+
+}
+```
+
+# Visualizing Default LIME
+
+```{r}
+plot_features(lime_explain_mains$explain[1:12,])
+```
+
+```{r}
+coefs <- logistic_mains$finalModel$coefficients %>% round(2)
+```
+
+The logistic regression model is
+
+$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks
+
+where $\hat{p}=P(\mbox{samesource = TRUE})$.
+
+I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.
+
+```{r}
+m = function(x) coefs[2:10] * x
+m(hamby224_test[1,] %>% select(rf_features))
+hamby224_test[1:4,] %>% select(rf_features)
+coefs
+hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
+```
+
+```{r}
+mains_test_explain <- hamby224_test %>%
+  mutate(case = as.character(case)) %>%
+  full_join(lime_explain_mains$explain, by = "case") %>%
+  mutate(case = factor(case),
+         feature = factor(feature))
+```
+
+Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).
+
+```{r}
+mains_test_explain %>%
+  na.omit() %>%
+  arrange(case, desc(abs(feature_weight))) %>%
+  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
+  select(case, set, feature, feature_order) %>%
+  spread(feature_order, feature) %>%
+  arrange(set, first, second, third) %>%
+  mutate(order = 1:n()) %>%
+  gather(feature_order, feature, 3:5) %>%
+  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
+  geom_tile() + 
+  facet_grid(set ~ ., scales = "free_y") +
+  theme_bw() +
+  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
+```
+
+```{r}
+pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
+pca_results$loadings
+z1 <- pca_results$scores[,1]
+z2 <- pca_results$scores[,2]
+ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
+  geom_point()
+biplot(pca_results)
+```
+
+# Visualizing All Input Options
+
+### Comparing Input Values by MSE and $R^2$
+
+In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
+I defined the mean squared error as
+  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
+where $n$ is the number of observations in the testing dataset (within a set).
+Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
+
+```{r}
+# Summarizing lime results
+logistic_lime_results <- logistic_lime_comparisons %>%
+  filter(!is.na(rfscore)) %>%
+  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
+           bin_method, response, set) %>%
+  summarise(mse = (sum(diff^2)) / length(diff),
+            ave_r2 = mean(model_r2)) %>%
+  arrange(set) %>%
+  ungroup()
+```
+
+The plot below shows the mean squared errors for each of the input situations faceted by set.
+There is no one bin type that stands out as performing the best across all or most number of bins.
+This is unlike the results from the random forest model where the tree based bins usually performed the best.
+
+```{r}
+# Plot of MSEs
+logistic_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
+  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
+  geom_point() + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+        legend.position = "none") + 
+  labs(x = "Bin Type", y = "MSE", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+The plot below shows the average $R^2$ value for each of the input situations faceted by set.
+The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
+With the logistic regression, the equally spaced bins or the quantile bins seem to perform the best in terms of $R^2$ across the different number of bins.
+The rfscore tree based bins are not as good as they were with the random forest model.
+However, all of the $R^2$ values are still very low for all cases.
+
+```{r}
+# Plot of R^2s
+logistic_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
+  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
+  geom_point() + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") + 
+  labs(x = "Bin Type", y = "Average R2", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+## Consistency
+
+I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
+I would like the features chosen to not depend on the number of bins used.
+Otherwise, it will be difficult to know how many bins to use.
+Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
+The code below creates a dataset that identifies the order in which the features are chosen by lime.
+
+```{r}
+# Creates a dataset that creates columns of the chosen features by lime from first to third
+logistic_chosen_features <- logistic_test_explain %>%
+  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
+  filter(!is.na(rfscore)) %>%
+  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, desc(feature_weight_abs)) %>%
+  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
+  select(-feature_weight, -feature_weight_abs) %>%
+  spread(explainer, feature)
+```
+
+### Fleiss's Kappa
+
+In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
+Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
+It calculates the degree of agreement in classification over that which would be expected by chance.
+A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
+
+I computed kappa for each bin situation separately for the top three features chosen.
+These values are plotted below for each set.
+For the first feature chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the samesource tree based bins.
+
+```{r}
+# Computes and plots the values of kappa
+logistic_chosen_features %>%
+  ungroup() %>%
+  select(-situation) %>%
+  gather(key = chosen, value = feature, first:third) %>%
+  spread(nbins, feature) %>%
+  select(-case) %>%
+  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
+  group_by(set, bin_situation, chosen) %>%
+  summarise(kappa = 
+              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
+                                        ncol = 5))$value) %>%
+  arrange(chosen, set, bin_situation) %>%
+  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
+  geom_point() + 
+  geom_line() +
+  facet_grid( ~ set) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
+  labs(x = "Bin Type", y = "Kappa", color = "Feature")
+```
+
+### Tile Plots of Features Chosen
+
+I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below. The results appear to be very different from the random forest results.
+
+```{r fig.height = 8, fig.width = 8}
+# Plots the top feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(first)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "First Feature")
+
+# Plots the second feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(second)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = second)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Second Feature")
+
+# Plots the third feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(third)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = third)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Third Feature")
+```
+
 # Session Info

### 2019-03-11 journals/02-plotting_training_and_testing_data/02-plotting_training_and_testing_data.Rmd
started work (just a bit) on making a biplot
parallel coord plots

@@
 
+# Parallel Coordinate Plots
+
+Below is a parallel coordinate plot of the training dataset.
+It is facetted by `samesource` and colored by `rfscore`.
+The features are sorted by the variable importance scores (descending from left to right) from the `rtrees` model.
+It is interesting to see that the matches with low rfscores have feature values that are similar to the nonmatches.
+
+```{r fig.width = 10}
+hamby173and252_train %>%
+  mutate(case = 1:n()) %>%
+  select(case, rfscore, samesource, ccf:sum_peaks) %>%
+  mutate_at(rf_features, scale) %>%
+  gather(variable, value, 4:12) %>%
+  mutate(variable = factor(variable, levels = rf_features)) %>%
+  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
+  geom_point() + 
+  geom_line(alpha = 0.2) + 
+  facet_grid( ~ samesource) + 
+  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "Feature (sorted by rtrees variable importance)", 
+       y = "Standardized Feature Values")
+```
+
+Below is a parallel coordinate plot of the testing dataset.
+It is facetted by `samesource` and colored by `rfscore`.
+You can see a clear distinction between the trends of the feature values from the nonmatches and matches.
+It is interesting to consider the cases in set 1 that are matches but were predicted to be nonmatches by the model.
+These are the cases colored in grey, and their feature values are very different from the observations that were predicted to be matches by the model.
+The nonmatch predictions have values that are closer to the nonmatches.
+
+```{r fig.width = 10}
+hamby224_test %>%
+  na.omit() %>%
+  select(case, set, rfscore, samesource, ccf:sum_peaks) %>%
+  mutate_at(rf_features, scale) %>%
+  gather(variable, value, 5:13) %>%
+  mutate(variable = factor(variable, levels = rf_features)) %>%
+  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
+  geom_point() + 
+  geom_line(alpha = 0.5) + 
+  facet_grid(set ~ samesource) + 
+  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "Feature (sorted by rtrees variable importance)", 
+       y = "Standardized Feature Values")
+```
+
+# Biplot
+
+```{r eval = FALSE}
+pca_set1 <- princomp(x = hamby224_test %>% 
+                       filter(set == "Set 1") %>% 
+                       select(rf_features) %>% 
+                       na.omit(), 
+                     cor = TRUE)
+biplot(pca, col = hamby224_test %>% 
+                       filter(set == "Set 1") %>% 
+                       pull(rfscore))
+```
+
 # Session Info

### 2019-03-11 journals/08-iris_comparison/08-iris_comparison.Rmd
started working on iris comparison

---
title: "08-iris_comparison"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

I am interested in how lime performs on other random forest models. This journal applies all of the input lime options to a random forest model fit to the iris data.

```{r}
# Load libraries
library(caret)
library(furrr)
library(future)
library(gretchenalbrecht)

# Source functions
source("../../code/helper_functions.R")
```

# Training and Testing Data

```{r}
# Set a seed
set.seed(20190311)

# Randomly select two cases from within each of the three species of irises
selected <- c(sample(1:50, 4), sample(51:100, 4), sample(101:151, 4))

# Split up the features of the data into training and testing parts
iris_train <- iris[-selected, ]
iris_test <- iris[selected, ] %>% mutate(case = selected)
```

# Random Forest Model

```{r}
# Random forest model run on the iris data
iris_model <- train(iris_train %>% select(-Species), iris_train %>% pull(Species), method = 'rf')

# Predictions made using the random forest model on the testing data
iris_model_predict <- predict(iris_model, iris_test)

# Matrix of observed and predicted values
iris_test_obs_pred <- matrix(c(iris_test %>% pull(Species), iris_model_predict), ncol = 2, byrow = FALSE)

# Specify the column names
colnames(iris_test_obs_pred) <- c("Observed", "Predicted")

# Print the table
knitr::kable(iris_test_obs_pred, align = 'c')
```

# Apply LIME

```{r}
# Apply the run_lime function if the lime results file does not already exist
if(!file.exists("./data/iris_lime_inputs.rds")) {

  # Specify the input options to use with lime
  iris_lime_inputs <- list(bin_continuous = c(rep(TRUE, 15), 
                                                  rep(FALSE, 2)),
                               quantile_bins = c(rep(TRUE, 5), 
                                                 rep(FALSE, 5), 
                                                 rep(TRUE, 7)),
                               nbins = c(rep(2:6, 3), 
                                         rep(4, 2)),
                               use_density = c(rep(TRUE, 15), TRUE, FALSE),
                               bin_method = c(rep("quantile_bins", 5),
                                              rep("equally_spaced", 5),
                                              rep("tree", 5),
                                              rep("quantile_bins", 2)),
                               response = c(rep(NA, 10), 
                                            rep("Species", 5), 
                                            rep(NA, 2)))

  # Tell R to run the upcoming code in parallel
  plan(multiprocess)

  # Apply lime to the full training data with the specified input options
  iris_lime_explain <- future_pmap(.l = iris_lime_inputs,
             .f = run_lime, # run_lime is one of my helper functions
             features = names(iris %>% select(-Species)),
             train = iris_train,
             test = iris_test %>% select(-case, -Species),
             rfmodel = iris_model,
             label = "virginica",
             nfeatures = 3,
             seed = TRUE)

  # Separate the lime and explain function results from the full data
  iris_lime <- map(iris_lime_explain, function(list) list$lime)
  iris_explain <- map_df(iris_lime_explain, function(list) list$explain)

  # Name the items in the lime list
  names(iris_lime) <- map_chr(1:17, function(case) 
      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
              iris_lime_inputs$bin_continuous[case],
              iris_lime_inputs$quantile_bins[case],
              iris_lime_inputs$nbins[case],
              iris_lime_inputs$use_density[case],
              iris_lime_inputs$bin_method[case],
              iris_lime_inputs$response[case]))

  # Turn the lime input options into a dataframe before saving it
  iris_lime_inputs <- iris_lime_inputs %>%
    unlist() %>%
    matrix(ncol = length(iris_lime_inputs), 
           dimnames = list(NULL, names(iris_lime_inputs))) %>%
    as.data.frame() %>%
    mutate(case = 1:length(iris_lime_inputs$quantile_bins)) %>%
    select(case, bin_continuous:response)

  # Save the lime objects
  saveRDS(iris_lime_inputs, "./data/iris_lime_inputs.rds")
  saveRDS(iris_lime, "./data/iris_lime.rds")
  saveRDS(iris_explain, "./data/iris_explain.rds")

} else {

  # Load in the lime objects
  iris_lime_inputs <- readRDS("./data/iris_lime_inputs.rds")
  iris_lime <- readRDS("./data/iris_lime.rds")
  iris_explain <- readRDS("./data/iris_explain.rds")

}
```

```{r}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("./data/iris_test_explain.rds")) {

  # Join the data and the explanations and edit and add additional variables
  iris_test_explain <- iris_test %>%
    mutate(case = as.character(case),
           rfscore = predict(iris_model, iris_test, type = "prob") %>% pull(virginica)) %>%
    full_join(iris_explain, by = "case") %>%
    mutate(case = factor(case),
           feature_desc = factor(feature_desc),
           feature = factor(feature),
           nbins = factor(nbins)) %>%
    arrange(nbins) %>%
    mutate(nbins = as.numeric(as.character(nbins)),
           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                              sprintf("%.0f quantile", nbins),
                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                     sprintf("%.0f equally spaced", nbins),
                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                              response == "Species",
                                            sprintf("%.0f tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation")))) %>%
             fct_relevel("2 quantile", "3 quantile", "4 quantile",
                         "5 quantile", "6 quantile", "2 equally spaced",
                         "3 equally spaced", "4 equally spaced",
                         "5 equally spaced", "6 equally spaced",
                         "2 Species tree", "3 Species tree",
                         "4 Species tree", "5 Species tree",
                         "6 Species tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "Species",
                                                "Species tree", 
                                                ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation"))))) %>%
    mutate(bin_situation = factor(bin_situation))

  # Save the combined test and explain data
  saveRDS(iris_test_explain, "./data/iris_test_explain.rds")

} else {

  # Load in the data
  iris_test_explain <- readRDS("./data/iris_test_explain.rds")

}
```

This code creates and saves a dataset with summaries of the explanations.

```{r}
# Create the lime comparison data if the file does not already exist
if(!file.exists("./data/iris_lime_comparisons.rds")) {

  # Create a data frame with the interesting information relating to the different
  # evaluations of lime and compute the difference and mean between the rf and rr
  # model predictions
  iris_lime_comparisons <- iris_test_explain %>%
    select(-data, -prediction) %>%
    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method) %>%
    slice(1) %>%
    ungroup() %>%
    mutate(diff = rfscore - model_prediction,
           mean = (rfscore + model_prediction) / 2)

  # Save the lime comparison data frame
  saveRDS(iris_lime_comparisons, "./data/iris_lime_comparisons.rds")

} else {

  # Load in the lime comparison data frame
  iris_lime_comparisons <- readRDS("./data/iris_lime_comparisons.rds")

}
```

# Visualizing LIME Results

```{r}
# Summarizing lime results
iris_lime_results <- iris_lime_comparisons %>%
  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
           bin_method, response) %>%
  summarise(mse = (sum(diff^2)) / length(diff),
            ave_r2 = mean(model_r2)) %>%
  ungroup()
```

```{r}
# Plot of MSEs
iris_lime_results %>%
  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
  geom_point() + 
  facet_grid(~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") + 
  labs(x = "Bin Type", y = "MSE", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

```{r}
# Plot of R^2s
iris_lime_results %>%
  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
  geom_point() + 
  facet_grid( ~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") + 
  labs(x = "Bin Type", y = "Average R2", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

```{r}
# Creates a dataset that creates columns of the chosen features by lime from first to third
iris_chosen_features <- iris_test_explain %>%
  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
  filter(!is.na(rfscore)) %>%
  select(situation, bin_situation, nbins, case, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, desc(feature_weight_abs)) %>%
  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
  select(-feature_weight, -feature_weight_abs) %>%
  spread(explainer, feature)
```

```{r}
# Computes and plots the values of kappa
iris_chosen_features %>%
  ungroup() %>%
  select(-situation) %>%
  gather(key = chosen, value = feature, first:third) %>%
  spread(nbins, feature) %>%
  select(-case) %>%
  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
  group_by(bin_situation, chosen) %>%
  summarise(kappa = 
              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
                                        ncol = 5))$value) %>%
  arrange(chosen, bin_situation) %>%
  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
  geom_point() + 
  geom_line() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
  labs(x = "Bin Type", y = "Kappa", color = "Feature")
```

```{r}
# Plots the top feature for each case for each bin situation
iris_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(first)))) %>%
  ungroup() %>%
  arrange(bin_situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
  ggplot(aes(x = nbins, y = order, fill = first)) + 
  geom_tile() + 
  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "First Feature")

# Plots the second feature for each case for each bin situation
iris_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(second)))) %>%
  ungroup() %>%
  arrange(bin_situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
  ggplot(aes(x = nbins, y = order, fill = second)) + 
  geom_tile() + 
  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Second Feature")

# Plots the third feature for each case for each bin situation
iris_chosen_features %>%
  group_by(bin_situation, case) %>%
  mutate(nlevels = length(levels(factor(third)))) %>%
  ungroup() %>%
  arrange(bin_situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
  ggplot(aes(x = nbins, y = order, fill = third)) + 
  geom_tile() + 
  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Third Feature")
```

# Session Info

```{r}
sessionInfo()
```

### 2019-03-12 journals/08-iris_comparison/08-iris_comparison.Rmd
finished iris random forest comparison journal (08)

@@
 library(gretchenalbrecht)
+library(lime)
 
@@
 
+Iris is randomly split into training and testing datasets such that all of the species are represented in the testing data.
+
 ```{r}
@@
 # Randomly select two cases from within each of the three species of irises
-selected <- c(sample(1:50, 4), sample(51:100, 4), sample(101:151, 4))
+selected <- c(sample(1:50, 4), sample(51:100, 4), sample(101:150, 4))
+
+# Determine the case numbers that were not selected
+cases <- 1:150
+not_selected <- cases[!(cases %in% selected)]
 
@@
 iris_train <- iris[-selected, ]
-iris_test <- iris[selected, ] %>% mutate(case = selected)
+iris_test <- iris[selected, ] %>% mutate(case = 1:n())
 ```
@@
 
+A random forest model is fit to the iris data.
+The predictions from the model for the testing data are shown in the table below with the actual observed values.
+The model gets all of the predictions correct.
+
 ```{r}
-# Random forest model run on the iris data
-iris_model <- train(iris_train %>% select(-Species), iris_train %>% pull(Species), method = 'rf')
+# Random forest model run on the iris training data
+iris_model <- train(x = iris_train %>% select(-Species), 
+                    y = iris_train %>% pull(Species), 
+                    method = 'rf')
 
 # Predictions made using the random forest model on the testing data
-iris_model_predict <- predict(iris_model, iris_test)
+iris_model_predict <- predict(iris_model, iris_test %>% select(-Species, - case))
 
 # Matrix of observed and predicted values
-iris_test_obs_pred <- matrix(c(iris_test %>% pull(Species), iris_model_predict), ncol = 2, byrow = FALSE)
-
-# Specify the column names
-colnames(iris_test_obs_pred) <- c("Observed", "Predicted")
+iris_test_obs_pred <- data.frame(Observed = iris_test %>% pull(Species),
+                                 Predicted = iris_model_predict)
 
@@
 # Apply LIME
+
+LIME is applied using all density estimation methods with 2 to 5 bins for all of the bin based methods.
 
@@
 
+The explanations from LIME are joined with the testing data.
+Additionally, the random forest scores for the probability that a case is species virginica are added to the dataset.
+This is the only species that will be considered (for now at least).
+
 ```{r}
@@
     mutate(case = factor(case),
-           feature_desc = factor(feature_desc),
            feature = factor(feature),
@@
                          "5 equally spaced", "6 equally spaced",
-                         "2 Species tree", "3 Species tree",
-                         "4 Species tree", "5 Species tree",
-                         "6 Species tree")) %>%
+                         "2 tree", "3 tree",
+                         "4 tree", "5 tree",
+                         "6 tree")) %>%
     mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
@@
                                                 response == "Species",
-                                                "Species tree", 
+                                                "tree", 
                                                 ifelse(bin_continuous == FALSE & 
@@
 
-This code creates and saves a dataset with summaries of the explanations.
+Summaries of the explanations are computed and saved in a dataset.
 
@@
 
+All of the results in this section are in terms of the species virginica.
+
+The MSEs and average $R^2$ values are computed for each of the estimation methods.
+
 ```{r}
@@
 ```
+
+A plot of the MSEs is shown below.
 
@@
 
+A plot of the $R^2$ values is shown below. The $R^2$ values are much higher than
+
 ```{r}
@@
 
+The features chosen are sorted below.
+
 ```{r}
@@
 ```
+
+A plot of Fleiss's kappa values is shown below.
 
@@
 ```
+
+The following plots show the features chosen by each estimation method for all of the cases in the test dataset. The plots are created the by order the features are chosen (from first to third).
 

### 2019-03-15 papers/Visual Diagnostics of a Model Explainer/Visual Diagnostics of a Model Explainer Created by LIME.Rmd
updated stats paper to new name and outline added

--- 2019-02-12 papers/An Assessment of LIME Explanations from a Random Forest Model.Rmd
@@
 ---
-title: "An Assessment of LIME Explanations from a Random Forest Models"
+title: "Visual Diagnostics of a Model Explainer"
+subtitle: "Tools for the Assessment of LIME Explanations"
 author: "Katherine Goode and Heike Hofmann"
@@
 # Set knitr options
-knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      fig.pos = "center")
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE)
 ```
 
+Intended journal: ASA Data Science Journal
+
 # Introduction
+
+- main objective of a model explainer: 
+    - understand and explain model performance
+- LIME does...
+    - conceptually: models at two levels
+        1. Simple = explainer model
+        2. Complex = original "black box model"
+    - usually: model predictions, maybe with ground truth
+        - type I error
+        - type II error
+        - model is wrong in both cases
+    - explanation is also a prediction
+        - how reliable is that explanation?
+          - we will present some tools that could help answer that question
+          - we will show an example using this tools (bullet data)
+          - we will mention some possible insights about LIME that these tools have shown us
+            - explainer model generally has very low $R^2$ (probably due to binning)
+            - "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
+- Describe LIME including details on binning and linear regression in binned features and motivation for the binning
 

### 2019-03-26 journals/10-other_explainers/10-other_explainers.Rmd
worked on paper

---
title: "10-other_explainers"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

I recently started looking into new papers that cited LIME. This journal contains some information on papers with explainers developed after LIME.

# LORE (LOcal Rule-based Explanations)

This section contains my notes from reading through the paper introduction [LORE](https://arxiv.org/pdf/1805.10820.pdf).

Same idea as LIME: whole decision boundary is complex, but simpler at a local level

Difference from LIME:

(1) obtain the local data in a different way from LIME using a "genetic algorithm"
(2) better explainations (they claim)

## Method

Notation from the paper:

- $b$ = black blox predictor
- $x$ = specific instance in the data
- $y$ = predicted value from $b$ given $x$
- $c$ = interpretable predictor (a decision tree)
- $N$ = number of neighbor instances of $x$ generated using a "genetic algorithm"
- $r$ = the single rule that is a part of the local explanation
- $\Phi$ = the counterfactual rules that are a part of the local explanation
- $Z$ = generated instances with characteristics close to the ones of $x$ (note that $Z=Z_{=}\cup Z_{\not=}$)
- $Z_=$ = set of instances $z\in Z$ where $b(z)=b(x)$ 
- $Z_{\not=}$ =  set of instances $z\in Z$ where $b(z)\not=b(x)$

General Idea:

- generate neighboring instances ($Z$) to $x$ using a genetic algorithm
- fit a tree to $Z$ called $c$
- obtain the local explainer $r$ by extracting the path from the decision tree $c$ that leads to $y$ with the same conditions as $x$
- obtain the counterfactual rules $\Phi$ using the other paths from the decision tree $c$

Genetic Algorithm: Makes use of fitness functions

Fitness function = A fitness function is a particular type of objective function that is used to summarise, as a single figure of merit, how close a given design solution is to achieving the set aims. Fitness functions are used in genetic programming and genetic algorithms to guide simulations towards optimal design solutions. (from Wikipedia)

### 2019-03-26 papers/Visual Diagnostics of a Model Explainer/Visual Diagnostics of a Model Explainer Created by LIME.Rmd
worked on paper

@@
 
-- main objective of a model explainer: 
-    - understand and explain model performance
+Machine learning algorithms are have been proven to provide accurate predictions.
+However, this accuracy comes at a cost.
+With complicated algorithms, the ability to understand the mechanism in the data and the functional form of the model are lost.
+This has led for a push to be able to interpret machine learning algorithms.
+One approach to remedy this problem would be to develop a model explainer.
+The objective of such an explainer is to understand and explain model performance.
+
+LIME (locally interpretable model explanations) is one such model explainer that was developed for this purpose (reference). Conceptually, LIME
+
 - LIME does...

### 2019-03-28 papers/Visual Diagnostics of a Model Explainer/wileyNJD-AMS.Rnw
first attempt at creating an Rnw for the paper

\documentclass[AMS,STIX1COL]{WileyNJD-v2}

%\usepackage{amsmath,amsfonts}

\articletype{Article Type}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\raggedbottom

\begin{document}
\SweaveOpts{concordance=TRUE}

\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}

\author[1]{Katherine Goode*}

\author[1,2]{Heike Hofmann}

\authormark{Goode and Hofmann}

\address[1]{\orgdiv{Department of Statistics}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}

\address[2]{\orgdiv{Center for (CSAFE}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}

\corres{*Corresponding author. \email{kgoode@iastate.edus}}

\presentaddress{This is sample for present address text this is sample for present address text}

\today

\abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}

\keywords{keyword1, keyword2, keyword3, keyword4}

\jnlcitation{\cname{%
\author{Goode K.}, 
\author{H. Hofmann}, 
} (\cyear{2016}), 
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

\tableofcontents
\newpage

\maketitle

\section{Introduction}

- main objective of a model explainer: 
    - understand and explain model performance
- LIME does...
    - conceptually: models at two levels
        1. Simple = explainer model
        2. Complex = original "black box model"
    - usually: model predictions, maybe with ground truth
        - type I error
        - type II error
        - model is wrong in both cases
    - explanation is also a prediction
        - how reliable is that explanation?
          - we will present some tools that could help answer that question
          - we will show an example using this tools (bullet data)
          - we will mention some possible insights about LIME that these tools have shown us
            1. explainer model generally has very low $R^2$ (probably due to binning)
            2. "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
- Describe LIME including details on binning and linear regression in binned features and motivation for the binning

\section{Data}

\section{Methods}

\subsection{LIME Algorithm}

\paragraph{Notation}

\begin{itemize}
\item $x\in\mathbb{R}^d$: original representation of an instance being explained
\begin{itemize}
\item e.g. feature vector containing word embeddings
\end{itemize}
\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
\begin{itemize}
\item e.g. bag of words
\end{itemize}
\item $G$: class of potentially interpretable models
\begin{itemize}
\item e.g. linear models, decision trees, rule lists
\end{itemize}
\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
\item $\Omega(g)$: measure of complexity of $g$
\begin{itemize}
\item e.g. depth of a tree, number of non-zeros in a linear model
\end{itemize}
\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
\begin{itemize}
\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
\end{itemize}
\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
\end{itemize}

\paragraph{Step by Step Procedure}

Step 1:

\subsection{Application of LIME to Bullet Matching Data}

\subsubsection{lime R Package Perturbation Creation Methods}

The LIME R package allows for the following four methods to sample the perturbations based on the distributions of the features from the training data.

\begin{itemize}
\item Equally Spaced Bins
\item Quantile Bins
\item Normal Approximation
\item Kernel Density Approximation
\end{itemize}

The methods of equally spaced bins and quantile bins also allow the user to specify the number of bins. As of now, there are no recommendations or procedures provided for how to determine which method to use. By default, LIME uses four quantile bins. It was of interest to see how the explanations from LIME varied across the four sampling methods when applied to the bullet matching data. The LIME algorithm was applied to each prediction from the test data obtained from the 'rtrees' random forest model for each of the four sampling methods. Within the bin based sampling methods, the algorithm was applied for 2 to 6 bins. It was decided to only go up to 6 bins since the more bins used the more complex the explanation becomes.

\subsubsection{Proposed Bin Creation Methods}

\section{Results}

\subsection{LIME Package Explanations Dependent on Sampling Method}

In order to assess the LIME explanations created using different sampling methods, it was of interest to compare the top three features chosen as the important predictors by lime within a case from the test data across the diferent sampling methods. Figure ... is a heatamp showing the top feature chosen by lime for each of the cases in the test data and different bin based sampling methods. The rows represent the cases in the test data, and the columns represent the sampling methods. There are twenty methods included in the plot. These include the equally spaced bins and quantile bins from the lime package and the random forest score tree based bins and the same source tree based bins proposed in this paper. The rows are facetted by the test set and whether or not the observation is a match or not. The columns are faceted by these methods, and the columns within a facet represent the number of bins. Each method has 2 to 6 bins. The colors represent the top feature chosen by lime.

The variables of ccf and cms immediately show up as common variables chosen across all of the sampling methods. However, the patterns across the number of bins withing the sampling methods are different. When equally spaced bins are used, the top feature chosen is consistent across all cases within a number of bins category. For example, ccf is almost always chosen (change to actual number) with 2 equally spaced bins, matches is almost always chosen with 3 equally spaced bins, and non_cms is always chosen for the nonmatches with 5 and 6 equally spaced bins. This shows that with the bullet matching data, the top feature chosen with equally spaced bins is an artifact of the number of bins used. With equally spaced bins, this figure sugggest that LIME is providing global explanations as opposed to local explanations. It would be preferable that the top feature chosen was more consistent across the number of bins and more variable across the cases. This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.

I'm struggling what to write for the remaining three cases...

\section{Discussion}

\section{Sample for first level head}\label{sec1}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit~\citet{Rothermel1997} Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

\begin{eqnarray}
s(nT_{s}) &= &s(t)\times \sum\limits_{n=0}^{N-1} \delta (t-nT_{s}) \xleftrightarrow{\mathrm{DFT}}  S \left(\frac{m}{NT_{s}}\right) \nonumber\\
&= &\frac{1}{N} \sum\limits_{n=0}^{N-1} \sum\limits_{k=-N/2}^{N/2-1} s_{k} e^{\mathrm{j}2\pi k\Delta fnT_{s}} e^{-j\frac{2\pi}{N}mn}
\end{eqnarray}

\section{Sample for another first level head}\label{sec2}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus viverra
fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa ac
quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo~\cite{Rothermel1998} Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Example for bibliography citations cite~\citep{Elbaum2002}, cites~\cite{Allen2011,Yoo2007}

Quisque ullamcorper placerat ipsum. Cras nibh~\cite{Yoo2007,Schulz2012} Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{figure}[t]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{This is the sample figure caption.\label{fig1}}
\end{figure}

Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

\begin{figure*}
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{This is the sample figure caption.\label{fig2}}
\end{figure*}

\subsection{Example for second level head}

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit, dictum
in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam vestibulum
fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi. Pellentesque
eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut mi mi, lacinia
sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui. Mauris nibh leo,
facilisis non, adipiscing quis, ultrices a, dui.

Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam. Quisque
libero justo, consectetuer a, feugiat vitae, porttitor eu, libero. Suspendisse sed mauris vitae elit sollicitudin malesuada.

Maecenas ultricies eros sit amet ante. Ut venenatis velit. Maecenas sed mi eget dui varius euismod. Phasellus aliquet
volutpat odio. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit
amet pede ac sem eleifend consectetuer. Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
ac pretium ante justo a nulla. Curabitur tristique arcu eu metus. Vestibulum lectus. Proin mauris. Proin eu nunc eu
urna hendrerit faucibus. Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque
hendrerit ipsum dolor sed augue. Nulla nec lacus.

\begin{quote}
This is an example~\citep{Elbaum2002,Blanchard2015} for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text~\cite{Blanchard2015}. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text~\cite{Blanchard2015}. This is an example for quote text. This is an example for quote text. This is an example for quote text. 
\end{quote}

\section{Sample for next first level head}\label{sec3}

\subsection{Example for another second level head}

Suspendisse vitae elit. Aliquam arcu neque, ornare in, ullamcorper quis, commodo eu, libero. Fusce sagittis erat at
erat tristique mollis. Maecenas sapien libero, molestie et, lobortis in, sodales eget, dui. Morbi ultrices rutrum lorem.
Nam elementum ullamcorper leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
Maecenas imperdiet lacinia velit. Cras non urna. Morbi eros pede, suscipit ac, varius vel, egestas non, eros. Praesent
malesuada, diam id pretium elementum, eros sem dictum tortor, vel consectetuer odio sem sed wisi.

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

\subsection{Second level head text}

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\subsubsection{Third level head text}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
pulvinar in, cursus faucibus, augue.

\begin{boxtext}
\section*{Example of Boxtext}%
This is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext.
\end{boxtext}

\paragraph{Fourth level head text}

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\subparagraph{Fifth level head text}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
pulvinar in, cursus faucibus, augue.

Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

Nulla non mauris vitae wisi posuere convallis. Sed eu nulla nec eros scelerisque pharetra. Nullam varius. Etiam
dignissim elementum metus. Vestibulum faucibus, metus sit amet mattis rhoncus, sapien dui laoreet odio, nec ultricies
nibh augue a enim. Fusce in ligula. Quisque at magna et nulla commodo consequat. Proin accumsan imperdiet sem.
Nunc porta. Donec feugiat mi at justo. Phasellus facilisis ipsum quis ante. In ac elit eget ipsum pharetra faucibus.
Maecenas viverra nulla in massa.

Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis

\begin{center}
\begin{table*}[t]%
\caption{This is sample table caption.\label{tab1}}
\centering
\begin{tabular*}{500pt}{@{\extracolsep\fill}lccD{.}{.}{3}c@{\extracolsep\fill}}
\toprule
&\multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \multicolumn{1}{@{}l@{}}{\textbf{col4 head}}  & \textbf{col5 head}   \\
\midrule
col1 text & col2 text  & col3 text  & 12.34  & col5 text\tnote{1}   \\
col1 text & col2 text  & col3 text  & 1.62  & col5 text\tnote{2}   \\
col1 text & col2 text  & col3 text  & 51.809  & col5 text   \\
\bottomrule
\end{tabular*}
\begin{tablenotes}%%[341pt]
\item Source: Example for table source text.
\item[1] Example for a first table footnote.
\item[2] Example for a second table footnote.
\end{tablenotes}
\end{table*}
\end{center}

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{center}
\begin{table}[t]%
\centering
\caption{This is sample table caption.\label{tab2}}%
\begin{tabular*}{500pt}{@{\extracolsep\fill}lcccc@{\extracolsep\fill}}
\toprule
\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \textbf{col4 head}  & \textbf{col5 head} \\
\midrule
col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\dagger$}   \\
col1 text & col2 text  & col3 text  & col4 text  & col5 text   \\
col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\ddagger$}   \\
\bottomrule
\end{tabular*}
\begin{tablenotes}
\item Source: Example for table source text.
\item[$\dagger$] Example for a first table footnote.
\item[$\ddagger$] Example for a second table footnote.
\end{tablenotes}
\end{table}
\end{center}

Below is the example~\cite{Rothermel1998,Yoo2007,Schulz2012} for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list\footnote{This is an example for footnote.}:
\begin{itemize}
\item bulleted list entry sample bulleted list entry~\cite{Allen2011} sample list entry text. 
\item bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry.
\item bulleted list entry sample bulleted list entry~\cite{Ballen2011} bulleted list entry sample bulleted list entry~\citet{Allen2011} sample list entry text.  bulleted list entry sample bulleted list entry.
\item sample list entry text. sample list entry text.  
\end{itemize}

Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

Below is the sample for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list:\\[12pt]

\noindent\textbf{Description sample:}

\begin{description}
\item[first entry] description text. description text. description text. description text. description text. description text. description text. 
\item[second long entry] description text. description text. description text. description text. description text. description text. description text. 
\item[third entry] description text. description text. description text. description text. description text. 
\item[fourth entry] description text. description text. 
\end{description}

\noindent\textbf{Numbered list items sample:}

\begin{enumerate}[1.]
\item First level numbered list entry. sample numbered list entry.

\item First numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry.

\begin{enumerate}[a.]
\item Second level alpabetical list entry. Second level alpabetical list entry. Second level alpabetical list entry~\citet{Allen2011} Second level alpabetical list entry.

\item Second level alpabetical list entry. Second level alpabetical list entry~\citet{Schulz2012,Allen2011,Ballen2011}.

\begin{enumerate}[ii.]
\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry.

\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry~\cite{Yoo2007}.
\end{enumerate}

\item Second level alpabetical list entry. Second level alpabetical list entry~\cite{Elbaum2002}.
\end{enumerate}

\item First level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.

\item Another first level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. 
\end{enumerate}

\noindent\textbf{un-numbered list items sample:}

\begin{enumerate}[]
\item Sample unnumberd list text..
\item Sample unnumberd list text.
\item sample unnumberd list text. 
\item Sample unnumberd list text.
\end{enumerate}

\section{Examples for enunciations}\label{sec4}

\begin{theorem}[Theorem subhead]\label{thm1}
Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. 
\end{theorem}

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{proposition}
Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. 
\end{proposition}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

\begin{definition}[Definition sub head]
Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text.
\end{definition}

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

\begin{proof}
Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. 
\end{proof}

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\begin{proof}[Proof of Theorem~\ref{thm1}]
Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. 
\end{proof}

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,

\begin{sidewaystable}%[h]
\caption{Sideways table caption. For decimal alignment refer column 4 to 9 in tabular* preamble.\label{tab3}}%
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lccD{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}@{\extracolsep\fill}}%
\toprule
  & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} &\multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} \\
\midrule
  &col2 text &col3 text &0.7568&1.0530&1.2642&0.9919&1.3541&1.6108 \\
  & &col2 text &12.5701 &19.6603&25.6809&18.0689&28.4865&37.3011 \\
3 &col2 text  & col3 text &0.7426&1.0393&1.2507&0.9095&1.2524&1.4958 \\
  & &col3 text &12.8008&19.9620&26.0324&16.6347&26.0843&34.0765 \\
  & col2 text & col3 text &0.7285&1.0257&1.2374&0.8195&1.1407&1.3691\tnote{*} \\
  & & col3 text &13.0360&20.2690&26.3895&15.0812&23.4932&30.6060\tnote{\dagger} \\
\bottomrule
\end{tabular*}
\begin{tablenotes}%%[\textheight]
\item[*] First sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
\item[$\dagger$] Second sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
\end{tablenotes}
\end{sidewaystable}

\begin{sidewaysfigure}
\centerline{\includegraphics[width=542pt,height=9pc,draft]{empty}}
\caption{Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption.\label{fig3}}
\end{sidewaysfigure}

nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

\begin{algorithm}
\caption{Pseudocode for our algorithm}\label{alg1}
\begin{algorithmic}
  \For each frame
  \For water particles $f_{i}$
  \State compute fluid flow~\cite{Rothermel1997}
  \State compute fluid--solid interaction~\cite{Allen2011}
  \State apply adhesion and surface tension~\cite{Ballen2011}
  \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute virtual water film \\(see Section~\ref{sec3})
   \EndFor
   \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute growth direction vector \\(see Section~\ref{sec2})
   \EndFor
   \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute $F_{\theta}$ (see Section~\ref{sec1})
   \State compute $CE(s_{i},f_{j})$ \\(see Section~\ref{sec3})
   \If $CE(b_{i}, f_{j})$ $>$ glaze threshold
   \State $j$th water particle's phase $\Leftarrow$ ICE
   \EndIf
   \If $CE(c_{i}, f_{j})$ $>$ icicle threshold
   \State $j$th water particle's phase $\Leftarrow$ ICE
   \EndIf
   \EndFor
   \EndFor
  \EndFor
\end{algorithmic}
\end{algorithm}

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa~\cite{Rothermel1997,Elbaum2002}. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo~\cite{Elbaum2002} Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

\begin{equation}\label{eq23}
 \|\tilde{X}(k)\|^2
 =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
\end{equation}

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\begin{equation}\label{eq24}
 \|\tilde{X}(k)\|^2
 =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
\end{equation}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

\section{Conclusions}\label{sec5}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

%\backmatter

\section*{Acknowledgments}
This is acknowledgment text~\cite{Elbaum2002}. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

\subsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\subsection*{Financial disclosure}

None reported.

\subsection*{Conflict of interest}

The authors declare no potential conflict of interests.

\section*{Supporting information}

The following supporting information is available as part of the online article:

\noindent
\textbf{Figure S1.}
{500{\uns}hPa geopotential anomalies for GC2C calculated against the ERA Interim reanalysis. The period is 1989--2008.}

\noindent
\textbf{Figure S2.}
{The SST anomalies for GC2C calculated against the observations (OIsst).}

\appendix

\section{Section title of first appendix\label{app1}}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}

\subsection{Subsection title of first appendix\label{app1.1a}}

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\subsubsection{Subsection title of first appendix\label{app1.1.1a}}

\noindent\textbf{Unnumbered figure}

\begin{center}
\includegraphics[width=7pc,height=8pc,draft]{empty}
\end{center}

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.

Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

\section{Section title of second appendix\label{app2}}%

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.

Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

%== Figure 4 ==
%% Example for figure inside appendix
\begin{figure}[t]
\centerline{\includegraphics[height=10pc,width=78mm,draft]{empty}}
\caption{This is an example for appendix figure.\label{fig5}}
\end{figure}

\subsection{Subsection title of second appendix\label{app2.1a}}

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non odio.
Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce sed justo
eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin et quam.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien turpis,
fermentum vel, eleifend faucibus, vehicula eu, lacus.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

\subsubsection{Subsection title of second appendix\label{app2.1.1a}}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

\begin{center}
\begin{table}[b]%
\centering
\caption{This is an example of Appendix table showing food requirements of army, navy and airforce.\label{tab4}}%
\begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
\toprule
\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
\midrule
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text\\
\bottomrule
\end{tabular*}
\end{table}
\end{center}

Example for an equation inside appendix
\begin{equation}
\mathcal{L}\quad \mathbf{\mathcal{L}} = i \bar{\psi} \gamma^\mu D_\mu \psi - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi\label{eq25}
\end{equation}

\section{Example of another appendix section\label{app3}}%

This is sample for paragraph text this is sample for paragraph text  this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\begin{equation}
\mathcal{L} = i \bar{\psi} \gamma^\mu D_\mu \psi
    - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi
\label{eq26}
\end{equation}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

\begin{center}
\begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
\toprule
\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
\midrule
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
\bottomrule
\end{tabular*}
\end{center}

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, evehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

%\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{wileyNJD-AMS}%

\section*{Author Biography}

\begin{biography}{\includegraphics[width=60pt,height=70pt,draft]{empty}}{\textbf{Author Name.} This is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text.}
\end{biography}

\end{document}

### 2019-04-02 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
updated paper to only include necessary text and added format files so it compiles now

--- 2019-03-28 papers/Visual Diagnostics of a Model Explainer/wileyNJD-AMS.Rnw
@@
 
-\today
-
 \abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}
@@
 \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
-
-\tableofcontents
-\newpage
 
@@
 When equally spaced bins are used, the top feature chosen is consistent across all cases within a number of bins category.
-For example, ccf is almost always chosen (change to actual number) with 2 equally spaced bins, matches is almost always chosen with 3 equally spaced bins, and non_cms is always chosen for the nonmatches with 5 and 6 equally spaced bins.
+For example, ccf is almost always chosen (change to actual number) with 2 equally spaced bins, matches is almost always chosen with 3 equally spaced bins, and non\_cms is always chosen for the nonmatches with 5 and 6 equally spaced bins.
 This shows that with the bullet matching data, the top feature chosen with equally spaced bins is an artifact of the number of bins used.
@@
 This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.
-
-I'm struggling what to write for the remaining three cases...
-
-\section{Discussion}
-
-\section{Sample for first level head}\label{sec1}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit~\citet{Rothermel1997} Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
-auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
-
-\begin{eqnarray}
-s(nT_{s}) &= &s(t)\times \sum\limits_{n=0}^{N-1} \delta (t-nT_{s}) \xleftrightarrow{\mathrm{DFT}}  S \left(\frac{m}{NT_{s}}\right) \nonumber\\
-&= &\frac{1}{N} \sum\limits_{n=0}^{N-1} \sum\limits_{k=-N/2}^{N/2-1} s_{k} e^{\mathrm{j}2\pi k\Delta fnT_{s}} e^{-j\frac{2\pi}{N}mn}
-\end{eqnarray}
-
-\section{Sample for another first level head}\label{sec2}
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus viverra
-fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa ac
-quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo~\cite{Rothermel1998} Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-Example for bibliography citations cite~\citep{Elbaum2002}, cites~\cite{Allen2011,Yoo2007}
-
-Quisque ullamcorper placerat ipsum. Cras nibh~\cite{Yoo2007,Schulz2012} Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-vitae risus porta vehicula.
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis.
-Maecenas eget erat in sapien mattis porttitor.
-Vestibulum porttitor.
-Nulla facilisi.
-Sed a turpis eu lacus commodo facilisis.
-Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-\begin{figure}[t]
-\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
-\caption{This is the sample figure caption.\label{fig1}}
-\end{figure}
-
-Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
-sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
-Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
-et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-\begin{figure*}
-\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
-\caption{This is the sample figure caption.\label{fig2}}
-\end{figure*}
-
-\subsection{Example for second level head}
-
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit, dictum
-in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam vestibulum
-fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi. Pellentesque
-eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut mi mi, lacinia
-sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui. Mauris nibh leo,
-facilisis non, adipiscing quis, ultrices a, dui.
-
-Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam. Quisque
-libero justo, consectetuer a, feugiat vitae, porttitor eu, libero. Suspendisse sed mauris vitae elit sollicitudin malesuada.
-
-Maecenas ultricies eros sit amet ante. Ut venenatis velit. Maecenas sed mi eget dui varius euismod. Phasellus aliquet
-volutpat odio. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit
-amet pede ac sem eleifend consectetuer. Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
-ac pretium ante justo a nulla. Curabitur tristique arcu eu metus. Vestibulum lectus. Proin mauris. Proin eu nunc eu
-urna hendrerit faucibus. Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque
-hendrerit ipsum dolor sed augue. Nulla nec lacus.
-
-\begin{quote}
-This is an example~\citep{Elbaum2002,Blanchard2015} for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text~\cite{Blanchard2015}.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text~\cite{Blanchard2015}.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-\end{quote}
-
-\section{Sample for next first level head}\label{sec3}
-
-\subsection{Example for another second level head}
-
-Suspendisse vitae elit. Aliquam arcu neque, ornare in, ullamcorper quis, commodo eu, libero. Fusce sagittis erat at
-erat tristique mollis. Maecenas sapien libero, molestie et, lobortis in, sodales eget, dui. Morbi ultrices rutrum lorem.
-Nam elementum ullamcorper leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
-Maecenas imperdiet lacinia velit. Cras non urna. Morbi eros pede, suscipit ac, varius vel, egestas non, eros. Praesent
-malesuada, diam id pretium elementum, eros sem dictum tortor, vel consectetuer odio sem sed wisi.
-
-Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-\subsection{Second level head text}
-
-Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-\subsubsection{Third level head text}
-
-Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
-justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
-sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
-in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-Vivamus eu dolor.
-
-Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
-tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
-ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
-in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
-eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
-pulvinar in, cursus faucibus, augue.
-
-\begin{boxtext}
-\section*{Example of Boxtext}%
-This is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext.
-\end{boxtext}
-
-\paragraph{Fourth level head text}
-
-Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-\subparagraph{Fifth level head text}
-
-Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
-tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
-est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
-urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-Vivamus eu dolor.
-
-in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
-eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
-pulvinar in, cursus faucibus, augue.
-
-Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
-cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
-elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
-nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
-sed nisl eu sapien cursus rutrum.
-
-Nulla non mauris vitae wisi posuere convallis. Sed eu nulla nec eros scelerisque pharetra. Nullam varius. Etiam
-dignissim elementum metus. Vestibulum faucibus, metus sit amet mattis rhoncus, sapien dui laoreet odio, nec ultricies
-nibh augue a enim. Fusce in ligula. Quisque at magna et nulla commodo consequat. Proin accumsan imperdiet sem.
-Nunc porta. Donec feugiat mi at justo. Phasellus facilisis ipsum quis ante. In ac elit eget ipsum pharetra faucibus.
-Maecenas viverra nulla in massa.
-
-Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
-tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
-ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
-
-\begin{center}
-\begin{table*}[t]%
-\caption{This is sample table caption.\label{tab1}}
-\centering
-\begin{tabular*}{500pt}{@{\extracolsep\fill}lccD{.}{.}{3}c@{\extracolsep\fill}}
-\toprule
-&\multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
-\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \multicolumn{1}{@{}l@{}}{\textbf{col4 head}}  & \textbf{col5 head}   \\
-\midrule
-col1 text & col2 text  & col3 text  & 12.34  & col5 text\tnote{1}   \\
-col1 text & col2 text  & col3 text  & 1.62  & col5 text\tnote{2}   \\
-col1 text & col2 text  & col3 text  & 51.809  & col5 text   \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}%%[341pt]
-\item Source: Example for table source text.
-\item[1] Example for a first table footnote.
-\item[2] Example for a second table footnote.
-\end{tablenotes}
-\end{table*}
-\end{center}
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-\begin{center}
-\begin{table}[t]%
-\centering
-\caption{This is sample table caption.\label{tab2}}%
-\begin{tabular*}{500pt}{@{\extracolsep\fill}lcccc@{\extracolsep\fill}}
-\toprule
-\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \textbf{col4 head}  & \textbf{col5 head} \\
-\midrule
-col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\dagger$}   \\
-col1 text & col2 text  & col3 text  & col4 text  & col5 text   \\
-col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\ddagger$}   \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}
-\item Source: Example for table source text.
-\item[$\dagger$] Example for a first table footnote.
-\item[$\ddagger$] Example for a second table footnote.
-\end{tablenotes}
-\end{table}
-\end{center}
-
-Below is the example~\cite{Rothermel1998,Yoo2007,Schulz2012} for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list\footnote{This is an example for footnote.}:
-\begin{itemize}
-\item bulleted list entry sample bulleted list entry~\cite{Allen2011} sample list entry text. 
-\item bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry.
-\item bulleted list entry sample bulleted list entry~\cite{Ballen2011} bulleted list entry sample bulleted list entry~\citet{Allen2011} sample list entry text.
-bulleted list entry sample bulleted list entry.
-\item sample list entry text. sample list entry text.  
-\end{itemize}
-
-Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
-sed justo eu urna porta tincidunt.
-Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat.
-Morbi quis dolor.
-Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus.
-Proin
-et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-Below is the sample for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list:\\[12pt]
-
-\noindent\textbf{Description sample:}
-
-\begin{description}
-\item[first entry] description text. description text. description text. description text. description text. description text. description text. 
-\item[second long entry] description text. description text. description text. description text. description text. description text. description text. 
-\item[third entry] description text. description text. description text. description text. description text. 
-\item[fourth entry] description text. description text. 
-\end{description}
-
-\noindent\textbf{Numbered list items sample:}
-
-\begin{enumerate}[1.]
-\item First level numbered list entry. sample numbered list entry.
-
-\item First numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry.
-
-\begin{enumerate}[a.]
-\item Second level alpabetical list entry. Second level alpabetical list entry. Second level alpabetical list entry~\citet{Allen2011} Second level alpabetical list entry.
-
-\item Second level alpabetical list entry. Second level alpabetical list entry~\citet{Schulz2012,Allen2011,Ballen2011}.
-
-\begin{enumerate}[ii.]
-\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry.
-
-\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry~\cite{Yoo2007}.
-\end{enumerate}
-
-\item Second level alpabetical list entry. Second level alpabetical list entry~\cite{Elbaum2002}.
-\end{enumerate}
-
-\item First level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.
-
-\item Another first level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. 
-\end{enumerate}
-
-\noindent\textbf{un-numbered list items sample:}
-
-\begin{enumerate}[]
-\item Sample unnumberd list text..
-\item Sample unnumberd list text.
-\item sample unnumberd list text. 
-\item Sample unnumberd list text.
-\end{enumerate}
-
-\section{Examples for enunciations}\label{sec4}
-
-\begin{theorem}[Theorem subhead]\label{thm1}
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-\end{theorem}
-
-Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-vitae risus porta vehicula.
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-\begin{proposition}
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-\end{proposition}
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-vitae risus porta vehicula.
-
-\begin{definition}[Definition sub head]
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-\end{definition}
-
-Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
-sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
-Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
-et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
-
-\begin{proof}
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-\end{proof}
-
-Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-\begin{proof}[Proof of Theorem~\ref{thm1}]
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-\end{proof}
-
-Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
-justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
-sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
-in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-Pellentesque eget lectus.
-Proin eu metus.
-Sed porttitor.
-In hac habitasse platea dictumst.
-Suspendisse eu lectus.
-Ut Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor.
-Donec interdum.
-Praesent scelerisque.
-Mae-
-cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
-elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
-
-\begin{sidewaystable}%[h]
-\caption{Sideways table caption. For decimal alignment refer column 4 to 9 in tabular* preamble.\label{tab3}}%
-\begin{tabular*}{\textheight}{@{\extracolsep\fill}lccD{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}@{\extracolsep\fill}}%
-\toprule
-  & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} &\multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} \\
-\midrule
-  &col2 text &col3 text &0.7568&1.0530&1.2642&0.9919&1.3541&1.6108 \\
-  & &col2 text &12.5701 &19.6603&25.6809&18.0689&28.4865&37.3011 \\
-3 &col2 text  & col3 text &0.7426&1.0393&1.2507&0.9095&1.2524&1.4958 \\
-  & &col3 text &12.8008&19.9620&26.0324&16.6347&26.0843&34.0765 \\
-  & col2 text & col3 text &0.7285&1.0257&1.2374&0.8195&1.1407&1.3691\tnote{*} \\
-  & & col3 text &13.0360&20.2690&26.3895&15.0812&23.4932&30.6060\tnote{\dagger} \\
-\bottomrule
-\end{tabular*}
-\begin{tablenotes}%%[\textheight]
-\item[*] First sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
-\item[$\dagger$] Second sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
-\end{tablenotes}
-\end{sidewaystable}
-
-\begin{sidewaysfigure}
-\centerline{\includegraphics[width=542pt,height=9pc,draft]{empty}}
-\caption{Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption.\label{fig3}}
-\end{sidewaysfigure}
-
-nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-\begin{algorithm}
-\caption{Pseudocode for our algorithm}\label{alg1}
-\begin{algorithmic}
-  \For each frame
-  \For water particles $f_{i}$
-  \State compute fluid flow~\cite{Rothermel1997}
-  \State compute fluid--solid interaction~\cite{Allen2011}
-  \State apply adhesion and surface tension~\cite{Ballen2011}
-  \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
-   \State compute virtual water film \\(see Section~\ref{sec3})
-   \EndFor
-   \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
-   \State compute growth direction vector \\(see Section~\ref{sec2})
-   \EndFor
-   \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
-   \State compute $F_{\theta}$ (see Section~\ref{sec1})
-   \State compute $CE(s_{i},f_{j})$ \\(see Section~\ref{sec3})
-   \If $CE(b_{i}, f_{j})$ $>$ glaze threshold
-   \State $j$th water particle's phase $\Leftarrow$ ICE
-   \EndIf
-   \If $CE(c_{i}, f_{j})$ $>$ icicle threshold
-   \State $j$th water particle's phase $\Leftarrow$ ICE
-   \EndIf
-   \EndFor
-   \EndFor
-  \EndFor
-\end{algorithmic}
-\end{algorithm}
-
-Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-Integer porta neque vitae massa~\cite{Rothermel1997,Elbaum2002}. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo~\cite{Elbaum2002} Nulla nisl. Vestibulum
-sed nisl eu sapien cursus rutrum.
-
-Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
-sed nisl eu sapien cursus rutrum.
-
-\begin{equation}\label{eq23}
- \|\tilde{X}(k)\|^2
- =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
- \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
-\end{equation}
-
-Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-\begin{equation}\label{eq24}
- \|\tilde{X}(k)\|^2
- =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
- \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
-\end{equation}
-
-Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
-tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
-est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
-urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-Vivamus eu dolor.
-
-\section{Conclusions}\label{sec5}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
-auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
-
-Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
 
@@
 
-Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math.
-Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math.
-Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated.
-Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.
-All other code environments are set with normal text font.
-Refer below example:
-
-\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
-for i:=maxint to 0 do
-begin
-{ do nothing }
-end;
-Write('Case insensitive ');
-WritE('Pascal keywords.');
-\end{lstlisting}
-
-\subsection{Subsection title of first appendix\label{app1.1a}}
-
-Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-\subsubsection{Subsection title of first appendix\label{app1.1.1a}}
-
-\noindent\textbf{Unnumbered figure}
-
-\begin{center}
-\includegraphics[width=7pc,height=8pc,draft]{empty}
-\end{center}
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-\section{Section title of second appendix\label{app2}}%
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-%== Figure 4 ==
-%% Example for figure inside appendix
-\begin{figure}[t]
-\centerline{\includegraphics[height=10pc,width=78mm,draft]{empty}}
-\caption{This is an example for appendix figure.\label{fig5}}
-\end{figure}
-
-\subsection{Subsection title of second appendix\label{app2.1a}}
-
-Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non odio.
-Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce sed justo
-eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
-pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin et quam.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien turpis,
-fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
-
-\subsubsection{Subsection title of second appendix\label{app2.1.1a}}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
-auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
-
-Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-\begin{center}
-\begin{table}[b]%
-\centering
-\caption{This is an example of Appendix table showing food requirements of army, navy and airforce.\label{tab4}}%
-\begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
-\toprule
-\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
-\midrule
-col1 text & col2 text & col3 text \\
-col1 text & col2 text & col3 text \\
-col1 text & col2 text & col3 text\\
-\bottomrule
-\end{tabular*}
-\end{table}
-\end{center}
-
-Example for an equation inside appendix
-\begin{equation}
-\mathcal{L}\quad \mathbf{\mathcal{L}} = i \bar{\psi} \gamma^\mu D_\mu \psi - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi\label{eq25}
-\end{equation}
-
-\section{Example of another appendix section\label{app3}}%
-
-This is sample for paragraph text this is sample for paragraph text  this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text
-
-Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-\begin{equation}
-\mathcal{L} = i \bar{\psi} \gamma^\mu D_\mu \psi
-    - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi
-\label{eq26}
-\end{equation}
-
-Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-pellentesque felis eu massa.
-
-Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-vitae risus porta vehicula.
-
-\begin{center}
-\begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
-\toprule
-\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
-\midrule
-col1 text & col2 text & col3 text \\
-col1 text & col2 text & col3 text \\
-col1 text & col2 text & col3 text \\
-\bottomrule
-\end{tabular*}
-\end{center}
-
-Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-vitae risus porta vehicula.
-
-Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-facilisi.
-Sed a turpis eu lacus commodo facilisis.
-Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, evehicula libero dui cursus dui.
-Mauris tempor ligula sed lacus.
-Duis cursus enim ut augue.
-Cras ac magna.
-Cras nulla.
-Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
-
 %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;

### 2019-04-02 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
work on papers

@@
 
-\abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}
+\abstract[Summary]{This is sample abstract text.}
 
-\keywords{keyword1, keyword2, keyword3, keyword4}
+\keywords{LIME, black box models, interpretability, diagnostics}
 
@@
 
-- main objective of a model explainer: 
-- understand and explain model performance
-- LIME does...
-- conceptually: models at two levels
-1. Simple = explainer model
-2. Complex = original "black box model"
-- usually: model predictions, maybe with ground truth
-- type I error
-- type II error
-- model is wrong in both cases
+Machine learning algorithms have been proven to provide accurate predictions.
+However, this accuracy comes at a cost.
+With complicated algorithms, the ability to understand the mechanism in the data and the functional form of the model are lost.
+This has led for a desire to be able to interpret machine learning algorithms.
+One approach to remedy this problem would be to develop a model explainer.
+The objective of such an explainer is to understand and explain model performance.
+
+Locally interpretable model explanations (LIME) is one such model explainer that was developed for this purpose (reference).
+While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model for a single prediction of interest.
+Conceptually, LIME fits a simple interpretable model (the explainer) that is meant to capture the behavior of the complex "black box model" in a local region around the prediction.
+
+Predictive models are used in both regression and classification settings.
+For this paper, we will focus on the classification setting, and in particular, we will only discuss the case with a dichotomous response variable.
+In any case, when a predictive model is being developed, the data is usually divided into training and testing portions.
+The training data is used to fit the complex model, and the testing data is used to assess the model.
+The complex model can applied to the features in the testing data, and the resulting predictions can be compared to ground truth.
+Of interest during this assessment are the cases when the model is wrong.
+In the dichotomous response classification case, there are two ways in which the model can be wrong.
+The model can make a type I error in which..., or the model can make a type II error in which...
+
+It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
+The complex model is applied to the simulated dataset to obtain predictions.
+The observations associated with predictions are used as the response variable in a ridge regression model with the the simulated features as the predictor variable with the highest weight given to observations closest to the prediction of interest.
+Feature selection is performed to identify the most important variables in the local region.
+A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
+
 - explanation is also a prediction

### 2019-04-02 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.tex
updated paper to only include necessary text and added format files so it compiles now
work on papers

--- 2019-04-02 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+\input{visual-diagnostics-of-a-model-explainer-concordance}
 
-\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations from a Random Forest Model}
 
@@
 
-\abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}
+\abstract[Summary]{This is sample abstract text.}
 
-\keywords{keyword1, keyword2, keyword3, keyword4}
+\keywords{LIME, random forest, interpretability, diagnostics}
 
@@
 
-- main objective of a model explainer: 
-- understand and explain model performance
+Machine learning algorithms have been proven to provide accurate predictions.
+However, this accuracy comes at a cost.
+With complicated algorithms, the ability to understand the mechanism in the data and the functional form of the model are lost.
+This has led for a desire to be able to interpret machine learning algorithms.
+One approach to remedy this problem would be to develop a model explainer.
+The objective of such an explainer is to understand and explain model performance.
+
+LIME (locally interpretable model explanations) is one such model explainer that was developed for this purpose (reference). Conceptually, LIME
+
 - LIME does...

### 2019-04-02 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.tex
paper update

@@
 
-\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations from a Random Forest Model}
+\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
 
@@
 
-\keywords{LIME, random forest, interpretability, diagnostics}
+\keywords{LIME, black box models, interpretability, diagnostics}
 
@@
 
-LIME (locally interpretable model explanations) is one such model explainer that was developed for this purpose (reference). Conceptually, LIME
+Locally interpretable model explanations (LIME) is one such model explainer that was developed for this purpose (reference).
+While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model for a single prediction of interest.
+Conceptually, LIME fits a simple interpretable model (the explainer) that is meant to capture the behavior of the complex "black box model" in a local region around the prediction.
 
-- LIME does...
-  - conceptually: models at two levels
-  1. Simple = explainer model
-  2. Complex = original "black box model"
-- usually: model predictions, maybe with ground truth
-  - type I error
-  - type II error
-  - model is wrong in both cases
+Predictive models are used in both regression and classification settings.
+For this paper, we will focus on the classification setting, and in particular, we will only discuss the case with a dichotomous response variable.
+In any case, when a predictive model is being developed, the data is usually divided into training and testing portions.
+The training data is used to fit the complex model, and the testing data is used to assess the model.
+The complex model can applied to the features in the testing data, and the resulting predictions can be compared to ground truth.
+Of interest during this assessment are the cases when the model is wrong.
+In the dichotomous response classification case, there are two ways in which the model can be wrong.
+The model can make a type I error in which..., or the model can make a type II error in which...
+
+It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
+The complex model is applied to the simulated dataset to obtain predictions.
+The observations associated with predictions are used as the response variable in a ridge regression model with the the simulated features as the predictor variable with the highest weight given to observations closest to the prediction of interest.
+Feature selection is performed to identify the most important variables in the local region.
+A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
+
 - explanation is also a prediction

### 2019-04-17 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked on paper

@@
 
-%\usepackage{amsmath,amsfonts}
+\usepackage{amsmath,amsfonts}
 
@@
 
-\address[2]{\orgdiv{Center for (CSAFE}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
+\address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
 
@@
 
-\section{Data}
-
 \section{Methods}
@@
 
-\paragraph{Notation}
+The LIME algorithm is presented in the original paper in a general context that includes cases for text classification and feature recognition.
+For this paper, we are only considering a situation with a binary categorical response variable and continuous feature variables.
+The procedure below is defined in this context.
+Furthermore, the implementation of LIME used in this paper is via the lime R package, and the procedure describes the methods used by the R package.
+This deviates a bit from the original procedure described by Riberiro, Singh, and Guestrin (2016).
+We attempted to highlight these deviations.
+
+Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations.
 
 \begin{itemize}
-\item $x\in\mathbb{R}^d$: original representation of an instance being explained
-\begin{itemize}
-\item e.g. feature vector containing word embeddings
+\item $x=\left(\begin{array}{cccc}x_1 & x_2 & \hdots & x_p\end{array}\right)\in\mathbb{R}^p$: original representation of an instance being explained (e.g.
+observations from a set of $p$ continuous features for a specific case in the data) % the LIME paper uses d instead of p for the dimension
+\item $x'\in\mathbb{R}^{p'}$: vector for the interpretable representation of the instance being explained (e.g.
+a vector of indicator variables associated with the features chosen through feature selection indicating whether or not the observed value is in the bin created by LIME for the feature)
+\item $G$: class of potentially interpretable models (e.g. linear models, decision trees, rule lists)
+\item $g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$
+\item $\Omega(g)$: measure of complexity of $g$ (e.g. depth of a tree, number of non-zero coefficients in a linear model fit using LASSO)
+\item $f$: model that is being explained where $f:\mathbb{R}^p\rightarrow\mathbb{R}$ (In classification $f(x)$ is the probability that $x$ belongs to a certain class)
+\item $\pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
+\item $\mathcal{L}(f, g, \Pi_x)$: the fidelity funcions which is a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$
+\item $\xi(x)$: explanation produced by LIME where
+  $$\xi(x)=\underset{g\in G}{\arg\min} \ \mathcal{L}(f, g, \Pi_x)+\Omega(g)$$
+(i.e. want to minimize $\mathcal{L}(f, g, \Pi_x)$ and keep $\Omega(g)$ low enough to be interpretable by humans)
 \end{itemize}
-\item $x'\in\mathbb{R}^{d'}$: vector for the interpretable representation of the instance being explained
-\begin{itemize}
-\item e.g. bag of words
-\end{itemize}
-\item $G$: class of potentially interpretable models
-\begin{itemize}
-\item e.g. linear models, decision trees, rule lists
-\end{itemize}
-\item $g$: explanation model where $g:\mathbb{R}^{d'}\rightarrow\mathbb{R}$ and $g\in G$
-\item $\Omega(g)$: measure of complexity of $g$
-\begin{itemize}
-\item e.g. depth of a tree, number of non-zeros in a linear model
-\end{itemize}
-\item $f$: model that is being explained where $f:\mathbb{R}^d\rightarrow\mathbb{R}$
-\begin{itemize}
-\item note: in classification $f(x)$ is the probability that $x$ belongs to a certain class
-\end{itemize}
-\item $\Pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
-\item $\mathcal{L}(f, g, \Pi_x)$: a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\Pi_x$
-\end{itemize}
-
-\paragraph{Step by Step Procedure}
-
-Step 1:
 
@@
 \subsubsection{Proposed Bin Creation Methods}
+
+\section{Data}
 

### 2019-05-23 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked on intro to paper

@@
 
-\corres{*Corresponding author. \email{kgoode@iastate.edus}}
+\corres{*Corresponding author. \email{kgoode@iastate.edu}}
 
@@
 
-Machine learning algorithms have been proven to provide accurate predictions.
-However, this accuracy comes at a cost.
-With complicated algorithms, the ability to understand the mechanism in the data and the functional form of the model are lost.
-This has led for a desire to be able to interpret machine learning algorithms.
-One approach to remedy this problem would be to develop a model explainer.
-The objective of such an explainer is to understand and explain model performance.
+Machine learning algorithms are known to provide accurate predictions.
+(include more about the usefulness of ml algorithms).
+However, this predictive ability comes at a cost.
+These algorithms are typically very complex and have no functional form.
+As a result, the ability to directly interpret the model is lost.
 
-Locally interpretable model explanations (LIME) is one such model explainer that was developed for this purpose (reference).
+In many areas of application, the need to be able to explain the results from the model is critical.
+For example, in forensics science a machine learning model could be used to determine the probability that a shoe print found at the crime scene matches the shoe of a suspect.
+The model may return a high probability of a match, but without the ability to explain which factors in the model led to this high probability, it may be difficult for a jury to trust the results from the model when deciding whether or not to convice the suspect.
+(add sentence about Europe law) This has led to the desire to be able to interpret machine learning algorithms.
+
+One approach to remedy this problem would be to develop a model explainer that can provide insight into the model performance.
+A model explainer is a method that is separate from the model but uses the model to provide understanding into mechanism of how the model produces predictions.
+(try to think of a simple example of a model explainer)
+
+Locally interpretable model explanations (LIME) is one such model explainer (reference).
 While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model for a single prediction of interest.
-Conceptually, LIME fits a simple interpretable model (the explainer) that is meant to capture the behavior of the complex "black box model" in a local region around the prediction.
+Conceptually, LIME fits a simple model that is able to be interpreted, which is referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around a prediction of interest.
+(a good place to include an image to help with this explanation)
 
@@
 \item $\pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
-\item $\mathcal{L}(f, g, \Pi_x)$: the fidelity funcions which is a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$
+\item $\mathcal{L}(f, g, \Pi_x)$: the fidelity functions which is a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$
 \item $\xi(x)$: explanation produced by LIME where
@@
 
-In order to assess the LIME explanations created using different sampling methods, it was of interest to compare the top three features chosen as the important predictors by lime within a case from the test data across the diferent sampling methods.
+In order to assess the LIME explanations created using different sampling methods, it was of interest to compare the top three features chosen as the important predictors by lime within a case from the test data across the different sampling methods.
 Figure ...
@@
 These include the equally spaced bins and quantile bins from the lime package and the random forest score tree based bins and the same source tree based bins proposed in this paper.
-The rows are facetted by the test set and whether or not the observation is a match or not.
+The rows are faceted by the test set and whether or not the observation is a match or not.
 The columns are faceted by these methods, and the columns within a facet represent the number of bins.
@@
 This shows that with the bullet matching data, the top feature chosen with equally spaced bins is an artifact of the number of bins used.
-With equally spaced bins, this figure sugggest that LIME is providing global explanations as opposed to local explanations.
+With equally spaced bins, this figure suggest that LIME is providing global explanations as opposed to local explanations.
 It would be preferable that the top feature chosen was more consistent across the number of bins and more variable across the cases.

### 2019-05-25 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
updated intro
worked more on intro to paper - getting there...

@@
-\documentclass[AMS,STIX1COL]{WileyNJD-v2}
+\documentclass[AMS,STIX2COL]{WileyNJD-v2}
 
@@
 
-Machine learning algorithms are known to provide accurate predictions.
-(include more about the usefulness of ml algorithms).
+Machine learning models have been proven to provide accurate predictions in many areas of applications.
+Carriquiry et.
+al.
+(source) discuss improvement in various pattern recognition analyses in the forensics sciences with the use of random forests and neural networks.
+(need a source) describe the numerous ways machine learning has been used in the medical field to advance healthcare.
 However, this predictive ability comes at a cost.
-These algorithms are typically very complex and have no functional form.
+
+These models are typically complex and have no simple functional form.
 As a result, the ability to directly interpret the model is lost.
+In many areas of application such as with forensics science and healthcare, the need to be able to explain the results from the model is critical.
+For example, a machine learning model could be used to determine the probability that a shoe print found at the crime scene matches the shoe belonging to a suspect in the investigation.
+The model may return a high probability of a match, but without the ability to explain which factors in the model led to this high probability, it may be difficult for a jury to trust the results from the model when deciding whether to convict the suspect.
+(add sentence about Europe law) The importance of interpretability has led to the desire to be able to explain the output from machine learning algorithms.
 
-In many areas of application, the need to be able to explain the results from the model is critical.
-For example, in forensics science a machine learning model could be used to determine the probability that a shoe print found at the crime scene matches the shoe of a suspect.
-The model may return a high probability of a match, but without the ability to explain which factors in the model led to this high probability, it may be difficult for a jury to trust the results from the model when deciding whether or not to convice the suspect.
-(add sentence about Europe law) This has led to the desire to be able to interpret machine learning algorithms.
+One approach to remedy this problem would be to develop a model explainer that can provide insight into the performance of the complex model.
+A model explainer is a method that is separate from the model but uses the model to provide understanding into mechanism of how the model produces predictions.
+(try to think of a simple example of a model explainer) (mention some of the model explainers that have been developed recently)
 
-One approach to remedy this problem would be to develop a model explainer that can provide insight into the model performance.
-A model explainer is a method that is separate from the model but uses the model to provide understanding into mechanism of how the model produces predictions.
-(try to think of a simple example of a model explainer)
+LIME (local interpretable model explanations) is one such model explainer (reference).
+While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model at the local level for a single prediction of interest.
+Conceptually, LIME fits a simple model that can be interpreted, referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around the prediction of interest.
+(a good place to include an image to help with this explanation)
 
-Locally interpretable model explanations (LIME) is one such model explainer (reference).
-While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model for a single prediction of interest.
-Conceptually, LIME fits a simple model that is able to be interpreted, which is referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around a prediction of interest.
-(a good place to include an image to help with this explanation)
+- explanation is also a prediction/model
+  - how reliable is that explanation?
+  - also, no current recommendations for LIME algorithm input options
 
@@
 
+- we will present some tools that could help answer that question
+- we will show an example using this tools (bullet data)
+- we will mention some possible insights about LIME that these tools have shown us
+
+\section{Methods}
+
+\subsection{Overview of LIME}
+
 It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
@@
 A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
-
-- explanation is also a prediction
-  - how reliable is that explanation?
-- we will present some tools that could help answer that question
-- we will show an example using this tools (bullet data)
-- we will mention some possible insights about LIME that these tools have shown us
-1. explainer model generally has very low $R^2$ (probably due to binning)
-2. "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
-- Describe LIME including details on binning and linear regression in binned features and motivation for the binning
-
-\section{Methods}
 
@@
 \section{Results}
+
+1. explainer model generally has very low $R^2$ (probably due to binning)
+2. "local" explanations are not local but are driven by the ("global") marginal distributions of covariates
 

### 2019-05-28 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked more on intro - basically a draft of the intro is done now - need to clean up, add references, and have Heike edit

@@
 al.
-(source) discuss improvement in various pattern recognition analyses in the forensics sciences with the use of random forests and neural networks.
-(need a source) describe the numerous ways machine learning has been used in the medical field to advance healthcare.
-However, this predictive ability comes at a cost.
+(source) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model.
+Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks.
+This impressive predictive ability, however, comes at a cost.
 
-These models are typically complex and have no simple functional form.
-As a result, the ability to directly interpret the model is lost.
-In many areas of application such as with forensics science and healthcare, the need to be able to explain the results from the model is critical.
+These models are typically complex and lack a functional form, so the ability to directly interpret the model is lost.
+As a result, machine learning models often get referred to as black boxes.
+In many areas of application, such as forensics science and healthcare, the need to be able to explain the results from the model is critical.
 For example, a machine learning model could be used to determine the probability that a shoe print found at the crime scene matches the shoe belonging to a suspect in the investigation.
 The model may return a high probability of a match, but without the ability to explain which factors in the model led to this high probability, it may be difficult for a jury to trust the results from the model when deciding whether to convict the suspect.
-(add sentence about Europe law) The importance of interpretability has led to the desire to be able to explain the output from machine learning algorithms.
+(add sentence about Europe law) The need for interpretability has led to the desire to be able to explain the output from machine learning algorithms.
 
-One approach to remedy this problem would be to develop a model explainer that can provide insight into the performance of the complex model.
+One approach to remedy this problem is to develop a model explainer that can provide insight into the performance of the complex model.
 A model explainer is a method that is separate from the model but uses the model to provide understanding into mechanism of how the model produces predictions.
@@
 While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model at the local level for a single prediction of interest.
-Conceptually, LIME fits a simple model that can be interpreted, referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around the prediction of interest.
+Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around a prediction of interest.
 (a good place to include an image to help with this explanation)
 
-- explanation is also a prediction/model
-  - how reliable is that explanation?
-  - also, no current recommendations for LIME algorithm input options
+The explanation that is produced from the explainer is also a prediction or an element of a model.
+Since it is not directly extracted from the complex model, it is important to ask the question, ``How reliable is the explanation?".
+Currently, there are no recommendations for how to assess the explanations from LIME (need to check to make sure this is a true statement).
+In this paper, we will present some tools that could help answer that question for LIME.
+Additionally, we will show an example using these tools on a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
+
+\section{Methods}
 
@@
 The model can make a type I error in which..., or the model can make a type II error in which...
-
-- we will present some tools that could help answer that question
-- we will show an example using this tools (bullet data)
-- we will mention some possible insights about LIME that these tools have shown us
-
-\section{Methods}
 

### 2019-05-30 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
fixed typos

@@
 Machine learning models have been proven to provide accurate predictions in many areas of applications.
-Carriquiry et.
-al.
-(source) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model.
+Carriquiry et al.
+(2019) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model.
 Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks.

### 2019-06-03 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
small workd

@@
 Carriquiry et al.
-(2019) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model.
+(2019) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forest model.
 Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks.

### 2019-06-03 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked more on intro

@@
 
-Machine learning models have been proven to provide accurate predictions in many areas of applications.
-Carriquiry et al.
-(2019) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forest model.
-Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks.
-This impressive predictive ability, however, comes at a cost.
+Machine learning models have been proven to provide accurate predictions in a wide range of problems.
+This impressive predictive performance, however, comes at a cost.
+These models are typically complex and lack a functional form, so the ability to directly interpret the models is lost.
+This has led machine learning models be referred to as black box models.
+In many areas of application, the need to be able to explain the results from a model is critical.
+As a result, an area of research on how to explain the output from machine learning algorithms has emerged.
 
-These models are typically complex and lack a functional form, so the ability to directly interpret the model is lost.
-As a result, machine learning models often get referred to as black boxes.
-In many areas of application, such as forensics science and healthcare, the need to be able to explain the results from the model is critical.
-For example, a machine learning model could be used to determine the probability that a shoe print found at the crime scene matches the shoe belonging to a suspect in the investigation.
-The model may return a high probability of a match, but without the ability to explain which factors in the model led to this high probability, it may be difficult for a jury to trust the results from the model when deciding whether to convict the suspect.
-(add sentence about Europe law) The need for interpretability has led to the desire to be able to explain the output from machine learning algorithms.
+The forensics sciences and the heath care industry are two areas that have benefitted from machine learning but have an obvious need for explainable predictions.
+For example, Carriquiry et al.
+(2019) discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
+Yu, Beam, and Kohane (2018) describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
+In all of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings.
+If it is not possible to explain the output from a model, it becomes questionable whether the results from the model can be trusted to make important decisions.
 
-One approach to remedy this problem is to develop a model explainer that can provide insight into the performance of the complex model.
-A model explainer is a method that is separate from the model but uses the model to provide understanding into mechanism of how the model produces predictions.
+As an example, suppose that forensics examiners are trying to determine if a bullet used in a crime was fired from the gun that belongs to a suspect in the investigaion.
+A random forest model could be used to produce a probability of the bullet being fired from the gun under question.
+Even if the model may return a high probability of a match, it may be difficult for a jury to trust the results from the model when deciding whether to convict the suspect without the forensics examiners having the ability to explain which factors in the model led to this high probability.
+
+The European Union has taken the desire to provide explanations from machine learning models a step further.
+In May 2018, the General Data Protection Regulation (GDPR) went into effect (https://eugdpr.org/the-regulation/gdpr-faqs/).
+Part of the policies enforced by the regulation include the right for subjects affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
+As Goodman and Flaxman (2016) point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
+While there are different ways to interpret the ability to understand the logic behind the decisions, they claim a minimum would be to explain how the input variables relate to the predictions.
+
+One approach to remedy the problem of uninterpretable models is to develop a model explainer that can provide insight into the performance of the complex model.
+A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
 (try to think of a simple example of a model explainer) (mention some of the model explainers that have been developed recently)

### 2019-06-03 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked more on intro

@@
 As Goodman and Flaxman (2016) point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
-While there are different ways to interpret the ability to understand the logic behind the decisions, they claim a minimum would be to explain how the input variables relate to the predictions.
+While there are different ways to interpret the statement in the regulation about the ability to understand the logic behind the decisions, Goodman and Flaxman claim a minimum would be to explain how the input variables relate to the predictions.
 
@@
 A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
-(try to think of a simple example of a model explainer) (mention some of the model explainers that have been developed recently)
+Recently, a handful of model explainers have been developed (reference).
+LIME (local interpretable model explanations) is one such model explainer (reference).
 
-LIME (local interpretable model explanations) is one such model explainer (reference).
 While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model at the local level for a single prediction of interest.
@@
 
-The explanation that is produced from the explainer is also a prediction or an element of a model.
+(should probably expand on this paragraph and mention something about the only discussing the classification setting in this paper) The explanation that is produced from the explainer is also a prediction or an element of a model.
 Since it is not directly extracted from the complex model, it is important to ask the question, ``How reliable is the explanation?".

### 2019-06-06 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
worked more on paper to prepare for meeting

--- 2019-06-03 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
@@
 In May 2018, the General Data Protection Regulation (GDPR) went into effect (https://eugdpr.org/the-regulation/gdpr-faqs/).
-Part of the policies enforced by the regulation include the right for subjects affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
+The regulation includes a policy that gives the right for subjects affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
 As Goodman and Flaxman (2016) point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
-While there are different ways to interpret the ability to understand the logic behind the decisions, they claim a minimum would be to explain how the input variables relate to the predictions.
+At minimum, it will require that an explanation of how the input variables relate to the predictions.
 
@@
 Currently, there are no recommendations for how to assess the explanations from LIME (need to check to make sure this is a true statement).
-In this paper, we will present some tools that could help answer that question for LIME.
-Additionally, we will show an example using these tools on a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
+In this paper, we will present some visualizations tools that can be used to assess the explanations from LIME in classification problems.
+Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
 
@@
 
-\subsection{Application of LIME to Bullet Matching Data}
+\subsection{Implemention of LIME in R}
 
-\subsubsection{lime R Package Perturbation Creation Methods}
+(section describing the procedure that is currently used by the LIME R package)
 
@@
 
-\subsubsection{Proposed Bin Creation Methods}
+\subsection{Visualization Diagnostic Tools for LIME}
 
-\section{Data}
+\section{Application of LIME to Bullet Matching Data}
 

### 2019-06-06 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
remianders of the merge conflict

@@
 \documentclass[AMS,STIX2COL]{WileyNJD-v2}
+\usepackage{natbib}
+\usepackage{amsmath,amsfonts}
 
-\usepackage{amsmath,amsfonts}
+\usepackage{xcolor}
+\definecolor{blue}{rgb}{0.22, 0.42, 0.73}
+\definecolor{orange}{rgb}{0.94, 0.59, 0.19}
+\newcommand{\hh}[1]{\textcolor{orange}{#1}}
+\newcommand{\kg}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
 
@@
 \author{H. Hofmann}, 
-} (\cyear{2016}), 
-\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
+} (\cyear{2019}), 
+\ctitle{title}, \cjournal{journal}, \cvol{volume, number and page}.}
 
@@
 
+\hh{Generally: avoid 'can be'. Replace by 'is'.  }
+
 \section{Introduction}
 
+\hh{XXX make the intro a bit more gentle - how about something along the lines that in statistics there are two main uses for models: interpretation and prediction.
+In machine learning the focus of models is often on prediction ...
+while these models are highly predictive, this comes at the cost of interpretability.}
 Machine learning models have been proven to provide accurate predictions in a wide range of problems.
@@
 The forensics sciences and the heath care industry are two areas that have benefitted from machine learning but have an obvious need for explainable predictions.
-For example, Carriquiry et al.
-(2019) discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
+For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
 Yu, Beam, and Kohane (2018) describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
-In all of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings.
+In \hh{both} of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings.
 If it is not possible to explain the output from a model, it becomes questionable whether the results from the model can be trusted to make important decisions.
@@
 Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
+\hh{still to come: outline of the remainder of the paper.}
 
@@
 For this paper, we will focus on the classification setting, and in particular, we will only discuss the case with a dichotomous response variable.
-In any case, when a predictive model is being developed, the data is usually divided into training and testing portions.
+\hh{Accepted best practice for all}  predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
 The training data is used to fit the complex model, and the testing data is used to assess the model.
-The complex model can applied to the features in the testing data, and the resulting predictions can be compared to ground truth.
-Of interest during this assessment are the cases when the model is wrong.
+\hh{This is done to prevent overfitting and to get a more accurate assessment of the prediction error of the model.} The complex model is then applied to the features in the testing data, and the resulting predictions are compared to ground truth.
+Of \hh{particular} interest during this assessment are the cases when the model is wrong.
 In the dichotomous response classification case, there are two ways in which the model can be wrong.
@@
 Furthermore, the implementation of LIME used in this paper is via the lime R package, and the procedure describes the methods used by the R package.
-This deviates a bit from the original procedure described by Riberiro, Singh, and Guestrin (2016).
+This deviates a bit from the original procedure described by Riberio, Singh, and Guestrin (2016).
 We attempted to highlight these deviations.

### 2019-06-10 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
fixed references file

@@
 \usepackage{natbib}
+%\bibliographystyle{asa}
+
 \usepackage{amsmath,amsfonts}
@@
 For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
-Yu, Beam, and Kohane (2018) describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
+\citet{yu:2018} describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
 In \hh{both} of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings.
@@
 \section*{Acknowledgments}
-This is acknowledgment text~\cite{Elbaum2002}.
+This is acknowledgment text.
 Provide text here.
@@
 %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-\bibliography{wileyNJD-AMS}%
+\bibliography{references}%
 

### 2019-06-12 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
more work on cleaning repo

--- 2019-02-08 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
@@
                       fig.pos = "center")
-
-# Load libraries
-library(bulletr)
-library(cowplot)
-library(furrr)
-library(future)
-library(lime)
-library(purrr)
-library(randomForest)
-library(tidyverse)
-library(tree)
-
-# Source functions
-source("../code/helper_functions.R")
 ```

### 2019-06-12 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
updated after meeting
adding journals back

@@
 One will focus on a statistical assessment of LIME and the other will focus on the explanation of how the application of LIME to the Hamby bullet data can help firearm examiners understand the random forest model predictions.
+
+### Statistical Paper Presenting Visual Diagnostic Tools for LIME
+
+Write a paper that introduces some visual diagnostics for LIME to assess its performance. Key points that will be made:
+
+1. explainer model is really bad (probably due to the binning)
+2. local explanations at not local
 
@@
 - Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
+- Run a simulation to understand if LIME is working
+    - could implement a couple of local linear dependencies
+    - piece this together
+    - could include interactions in the model
+    - does lime find the local models?
+- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)
 

### 2019-06-12 journals/07-logistic_regression/07-logistic_regression.Rmd
adding journals back

@@
 library(future)
+library(glmnet)
 library(gretchenalbrecht)
+library(hierNet)
 library(lime)
@@
 
-### Comparing the Two Models
+### LASSO Model
+
+```{r}
+# Fit or load the lasso logistic regression model
+if(!file.exists("./data/logistic_lasso.rds")) {
+
+  # Set a seed
+  set.seed(20190312)
+
+  # LASSO logistic regression model
+  logistic_lasso <- cv.glmnet(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
+                              y = hamby173and252_train %>% pull(samesource) %>% as.numeric(),
+                              alpha = 1,
+                              family = "binomial")
+
+  # Tell R to run the upcoming code in parallel
+  # plan(multiprocess)
+
+  # LASSO logistic regression model with possible pairwise interactions
+  # logistic_lasso <- 
+  #   hierNet.logistic.path(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
+  #                         y = hamby173and252_train %>% pull(samesource) %>% as.numeric(), 
+  #                         lamlist = logistic_lasso$lambda)
+
+  # Save the model
+  saveRDS(logistic_lasso, "./data/logistic_lasso.rds")
+
+} else {
+
+  # Load the model
+  logistic_lasso <- readRDS("./data/logistic_lasso.rds")
+
+}
+```
+
+### Comparing the Models
 
@@
 
-I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below. The results appear to be very different from the random forest results.
+I also attempted to plot the features chosen by lime in order to visually assess the consistency.
+This plots are included below.
+The results appear to be different from the random forest results, but it is still possible to se vertical stripes that suggest a global interpretation as opposed to a local interpretation.
+However, the samesource bins do have some horizontal stipes that show what we would like to see.
+It is also interesting to note that the vertical bins are the most pronounced with the rfscore tree.
+This does not suprise me considering that these explanations are for a logistic regression and not the random forest model.
 

### 2019-06-12 journals/08-iris_comparison/08-iris_comparison.Rmd
compared to bullet
adding journals back

@@
 
-The following plots show the features chosen by each estimation method for all of the cases in the test dataset. The plots are created the by order the features are chosen (from first to third).
+The following plots show the features chosen by each estimation method for all of the cases in the test dataset.
+The plots are created the by order the features are chosen (from first to third).
+I am not seeing the same patterns that I saw with the bullet data and `rtrees`.
+Heike pointed out that you really do not need a complex model to explain this situation.
+The iris data should be easy to predict.
+Maybe I could switch to using the problem points in the iris data for the test data and see how LIME performs with these.
 

### 2019-06-12 journals/09-understanding_lime/09-understanding_lime.Rmd
adding journals back

---
title: "09-understanding_lime"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
                      cache = TRUE)
```

# Overview

```{r}
library(furrr)
library(future)
library(lime)
library(randomForest)
library(tidyverse)

# Source functions
source("../../code/helper_functions.R")
```

# The Data

The cleaned training and testing datasets are loaded in below.

```{r}
# Load in the training data (Hamby Data 173 and 252)
hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")

# Load in the testing data (Hamby Data 224 Sets 1 and 11)
hamby224_test <- read.csv("../../data/hamby224_test.csv")
```

A vector containing the features used in the random forest `rtrees` is created below that will be used when creating some of the plots in this journal.

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features_ordered <- data.frame(feature = rownames(bulletr::rtrees$importance), 
                                  MeanDecreaseGini = bulletr::rtrees$importance) %>%
  arrange(desc(MeanDecreaseGini))

top2_features <- rf_features_ordered$feature[1:2]
```

# Random Forest Model

```{r}
# Fit a random forest model with the top two most important features in the model
if(!file.exists("./data/rfmodel.rds")) {

  # Fit the random forest  
  rfmodel <- randomForest(factor(samesource) ~ rough_cor + ccf, data = hamby173and252_train)

  # Save the random forest
  saveRDS(rfmodel, "./data/rfmodel.rds")

} else {

  # Load the rf model
  rfmodel <- readRDS("./data/rfmodel.rds")
}
```

```{r}
# Create a dataset with the test data input to the random forest model 
# and the predictions from the random forest model
hamby224_test_subset <- hamby224_test %>%
  na.omit() %>%
  select(case:land2, rough_cor, ccf, samesource) %>%
  mutate(rfpred = predict(rfmodel, 
                           newdata = hamby224_test %>% select(rough_cor, ccf) %>% na.omit()),
         rfscore = predict(rfmodel, 
                           newdata = hamby224_test %>% select(rough_cor, ccf) %>% na.omit(),
                           type = "prob")[,2])
```

# Applying LIME

The functions `lime` and `explain` from the lime package are applied below to the random forest model.

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("./data/lime_explain_sub.rds")) {

  # Set a seed
  set.seed(20190315)

  # Apply lime
  lime_sub <- lime(x = hamby173and252_train %>% select(rough_cor, ccf), 
                   model = as_classifier(rfmodel))

  # Apply explain
  explain_sub <- explain(x = hamby224_test %>%
                             select(rough_cor, ccf) %>% 
                             na.omit(), 
                           explainer = lime_sub, 
                           n_labels = 1,
                           n_features = 2)

  # Join the lime and explain objects in a list
  lime_explain_sub <- list(lime = lime_sub, explain = explain_sub)

  # Save the lime and explain objects
  saveRDS(lime_explain_sub, "./data/lime_explain_sub.rds")

} else {

  # Load the lime and explain objects
  lime_explain_sub <- readRDS("./data/lime_explain_sub.rds")

}
```

```{r}
create_bin_df <- function(bin_cut) {
 data.frame(quantile = c("0%", "25%", "50%", "75%", "100%"), 
            bin_cut) 
}

bin_cuts <- purrr::map_df(lime_explain_sub$lime$bin_cuts, 
                          create_bin_df,
                          .id = "feature") %>%
  spread(key = feature, value = bin_cut)

bin_cuts
```

# Visualizations of Data, Model, and LIME

```{r}
(case1 <- lime_explain_sub$explain %>% filter(case == 1))
```

```{r}
ggplot() +
  geom_point(data = hamby173and252_train %>% filter(samesource == FALSE),
             aes(x = rough_cor, y = ccf),
             color = "darkgrey",
             alpha = 0.2) +
  geom_point(data = hamby173and252_train %>% filter(samesource == TRUE),
             aes(x = rough_cor, y = ccf),
             color = "darkorange") + 
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) +
  theme_minimal()
```

```{r}
ggplot() + 
  geom_point(data = hamby224_test_subset, 
             aes(x = rough_cor, y = ccf, color = rfscore),
             alpha = 0.5) + 
  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  geom_point(data = lime_explain_sub$explain %>% 
               filter(case == 1) %>%
               select(feature, feature_value) %>%
               spread(key = feature, value = feature_value),
             aes(x = rough_cor, y = ccf)) +
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) + 
  theme_minimal()
```

# Session Info

```{r}
sessionInfo()
```

### 2019-06-12 journals/02-plotting_training_and_testing_data/02-plotting_training_and_testing_data.Rmd
added journal 02 back

@@
 
+```{r}
+# Create a dataframe with the random forest features ordered by importance
+rf_features_ordered <- data.frame(feature = rownames(bulletr::rtrees$importance), 
+                                  MeanDecreaseGini = bulletr::rtrees$importance) %>%
+  arrange(desc(MeanDecreaseGini))
+```
+
 Below is a parallel coordinate plot of the training dataset.
@@
   gather(variable, value, 4:12) %>%
-  mutate(variable = factor(variable, levels = rf_features)) %>%
+  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
   ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
@@
   gather(variable, value, 5:13) %>%
-  mutate(variable = factor(variable, levels = rf_features)) %>%
+  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
   ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 

### 2019-06-12 README.Rmd
updated readme and paper folder names

---
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Applying LIME to Bullet Data

Repository for research project on assessing LIME by applying it to the Hamby bullet data. The contents of this respository are listed below.

### app

This folder contains files for Shiny app for visualizing the LIME explanations associated with the bullet land comparisons:

- **app.R**: code for the Shiny app

### code

This folder is a place for storing code that is used throughout the project:

- **helper_functions.R**: R script with functions that I use in the journals and will probably end up using in the papers as well

### data

This folder is a location for storing raw and created data for the project:

- **hamby173and252_train.csv**: training data that I cleaned (it should match the data used to fit `rtrees`)
- **hamby224_bin_boundaries.rds**: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
- **hamby224_bins.rds**: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
- **hamby224_explain**: the output from the `explain` function in lime from the single implementation with all of the different input options
- **hamby224_lime**: the output from the `lime` function in lime from the single implementation with all of the different input options
- **hamby224_lime_comparisons**: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
- **hamby224_lime_inputs**: LIME input settings used for the single implementation of LIME
- **hamby224_sensitivity_inputs**: LIME input settings used for the sensativity analysis of LIME
- **hamby224_sensitivity_joined.csv**: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
- **hamby224_sensitivity_outputs.rds**: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
- **hamby223_test.csv**: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
- **hamby224_test_explain.rds**: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
- raw: original data given to me by Heike
    - **features-hamby173and252.csv**
    - **h224-set1-features.rds**
    - **h224-set11-features.rds**

### journals

This folder contains folders with research journals.

- **00-objectives_and_ideas**: background of the research project, goals of the project, concerns with LIME, and ideas to try
- **01-training_and_testing_data**: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- **02-plotting_training_and_testing_data**: exploratory plots of the training and testing data
- **03-computation_issues**: documentation of some of the computation issues I ran into during the project
- **04-lime_algorithm_and_proposed_methods**: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- **05-applying_lime_to_rtrees**: application of lime and sensativity analysis for many different input options
- **06-assessing_lime_explanations**: assessment of the lime explanations
- **07-logistic_regression**: logistic regressions fit to the bullet data and application of lime to the logistic regression
- **08-iris_comparison**: applying LIME to a random forest fit to the iris data
- **09-understanding_lime**: attempts to visualize the results from LIME to understand how LIME works
- **10-other_explainers**: trying out other model explainers
- **notes from Heike.pdf**: scans of notes written by Heike for this project

### papers

This folder contains the statistics and firearm examiners papers:

- **bullet_application**: explains how LIME can be used to understand the random forest model fit to bullet matching data
- **lime_diagnostics**: explains the need to assess LIME and presents some visual diagnostic tools

### 2019-06-12 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
updated readme and paper folder names

--- 2019-06-10 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
@@
 \usepackage{xcolor}
-\definecolor{blue}{rgb}{0.22, 0.42, 0.73}
+\definecolor{purple}{rgb}{0.5, 0.0, 0.5}
 \definecolor{orange}{rgb}{0.94, 0.59, 0.19}
 \newcommand{\hh}[1]{\textcolor{orange}{#1}}
-\newcommand{\kg}[1]{\textcolor{blue}{#1}}
+\newcommand{\kg}[1]{\textcolor{purple}{#1}}
 
@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 
-\hh{XXX make the intro a bit more gentle - how about something along the lines that in statistics there are two main uses for models: interpretation and prediction.
-In machine learning the focus of models is often on prediction ...
-while these models are highly predictive, this comes at the cost of interpretability.}
-Machine learning models have been proven to provide accurate predictions in a wide range of problems.
-This impressive predictive performance, however, comes at a cost.
-These models are typically complex and lack a functional form, so the ability to directly interpret the models is lost.
-This has led machine learning models be referred to as black box models.
-In many areas of application, the need to be able to explain the results from a model is critical.
-As a result, an area of research on how to explain the output from machine learning algorithms has emerged.
+\hh{In the field of statistics, there are two main uses for models: interpretation and prediction.} \kg{Machine learning models are often used for the latter purpose.
+While these models have been proven to provide accurate predictions in a wide range of problems, this predictive ability comes at the cost of interpretability.} These models are typically complex and lack a functional form, so the ability to directly interpret the models is lost.
+\kg{This has earned machine learning models the reputation as being black boxes.
+The ability to interpret a model helps to diagnose the model and understand the predictions.} In some areas of application, the need to be able to explain the results from a model is critical.
+\kg{(These last few sentences could use some work so that the ideas are better connected from one sentence to the next.)} As a result, an area of research on how to explain the output from machine learning algorithms has emerged.
 
@@
 For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
-\citet{yu:2018} describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
-In \hh{both} of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings.
-If it is not possible to explain the output from a model, it becomes questionable whether the results from the model can be trusted to make important decisions.
+\citet{yu:2018} describe how healthcare has advanced through the use of machine learning in ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
+In \hh{both} of these cases, the decisions made based on the results of the machine learning models would greatly impact the lives of human beings.
+If it is not possible to explain the output from a model, it becomes questionable whether to trust the results from the model to make decisions.
 
 As an example, suppose that forensics examiners are trying to determine if a bullet used in a crime was fired from the gun that belongs to a suspect in the investigaion.
-A random forest model could be used to produce a probability of the bullet being fired from the gun under question.
-Even if the model may return a high probability of a match, it may be difficult for a jury to trust the results from the model when deciding whether to convict the suspect without the forensics examiners having the ability to explain which factors in the model led to this high probability.
+A random forest model could be used to produce a probability that the bullet was fired from the gun under question.
+Even if the model returns a high probability of a match, it will be difficult for a jury to trust the results from the model when deciding whether to convict the suspect without the forensics examiners having the ability to explain which factors in the model led to the high probability.
 
@@
 
-One approach to remedy the problem of uninterpretable models is to develop a model explainer that can provide insight into the performance of the complex model.
+One approach to remedy the problem of uninterpretable models is to develop a model explainer that provides insight into the performance of the complex model.
 A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
@@
 Currently, there are no recommendations for how to assess the explanations from LIME (need to check to make sure this is a true statement).
-In this paper, we will present some visualizations tools that can be used to assess the explanations from LIME in classification problems.
+\kg{I'd like to expand on this paragraph since this is really the focus of the paper.
+Then the last paragraph in the intro can outline the paper.}
+
+In this paper, we will present some visualizations tools to assess the explanations from LIME in classification problems.
 Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
@@
 
-\section{Methods}
+\section{Background}
 
@@
 
-\subsection{Visualization Diagnostic Tools for LIME}
+\section{Methods}
 
-\section{Application of LIME to Bullet Matching Data}
+\subsection{Diagnostic Tool 1}
 
-\section{Results}
+\subsection{Diagnostic Tool 2}
+
+\subsection{etc...}
+
+\section{Application}
 
@@
 2. "local" explanations are not local but are driven by the ("global") marginal distributions of covariates
-
-\subsection{LIME Package Explanations Dependent on Sampling Method}
 

### 2019-06-12 README.Rmd
updated readme and moved to do list there

@@
 
-# Applying LIME to Bullet Data
+# LIME Research
 
-Repository for research project on assessing LIME by applying it to the Hamby bullet data. The contents of this respository are listed below.
+Repository for research projects on LIME applied to the Hamby bullet data.
 
-### app
+Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/
+
+## Talking points
+
+## To Do List
+
+**Current Week**
+
+- look into bibText and add to paper
+- work on paper
+- finish journal on understanding lime (look at the RF in the local region
+  lime is considering to see if it agrees with the lime explanations)
+- think about how the argmin is accomplished by the LIME R package
+- change distance matrix in seriation to be 5-# of variables shared between two rows
+  or try using distance matrix computed on the feature values
+- fix issue with seriation
+- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
+- assess lime results on logistic regression models
+- think about how to implement a simulation with a random forest
+- add in feature selection methods to LIME input options
+- turn repetitive code into functions
+- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
+- look more into Molnar and his adviser Bernd
+- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
+- he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
+
+**Later**
+
+- look back at 601 notes from Kaiser and Hadley's removing the blindfold and
+  think about how this could be applied with random forests
+- try retriculate to apply python version of lime
+- look at 'removing the blindfold' for ideas
+- read through Heike's new function
+- think of a way to compute consistency across top two features
+- compare the simple models based on different number of bins using an F-test
+- look into literature on binning methods
+- think about why R^2 would be better for some binning methods
+- look into computing a diversity or consistency measure for the sensitivity analysis
+- create distribution visualizations bins
+- include a penalty for the number of parameters when choosing bins
+- determine the best number of bins to use for each variable
+- look at the AUC after binning
+- write a draft of the examiners paper
+- try out different weights
+- read through LIME papers again
+- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
+- try out logistic regression idea for bins (write own bin list to put in explain)
+- try out subsampling idea
+- read new paper on Anchor
+- read book Dr. Dixon lent me on sensativity analyses
+- try visualizing the features from the test data using dimension reduction and
+  coloring them by variables suggested to be important by lime
+- look into papers by Giles Hooker and Lucas Mentch
+
+## Contents
+
+Descriptions of the materials in this respository are listed below.
+
+#### app
 
@@
 
-### code
+#### code
 
@@
 
-### data
+#### data
 
@@
 
-### journals
+#### journals
 
@@
 
-### papers
+#### papers
 

### 2019-06-12 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
more work on paper

@@
 
-\hh{In the field of statistics, there are two main uses for models: interpretation and prediction.} \kg{Machine learning models are often used for the latter purpose.
-While these models have been proven to provide accurate predictions in a wide range of problems, this predictive ability comes at the cost of interpretability.} These models are typically complex and lack a functional form, so the ability to directly interpret the models is lost.
-\kg{This has earned machine learning models the reputation as being black boxes.
-The ability to interpret a model helps to diagnose the model and understand the predictions.} In some areas of application, the need to be able to explain the results from a model is critical.
-\kg{(These last few sentences could use some work so that the ideas are better connected from one sentence to the next.)} As a result, an area of research on how to explain the output from machine learning algorithms has emerged.
+\kg{Added in Heike's suggestions and made a few changes of my own to this paragraph:} In the field of statistics, there are two main uses for models: interpretation and prediction.
+Machine learning models are often used for the latter purpose.
+While these models have been proven to provide accurate predictions in a wide range of problems, this predictive ability comes at the cost of interpretability.
+These models are typically complex and lack a functional form, which makes it not possible to directly interpret the models and has earned them the reputation of being black boxes.
+The ability to interpret a model helps to diagnose the model and understand the predictions, and in some areas of application, the need to be able to explain the results from a model is critical.
 
@@
 
-One approach to remedy the problem of uninterpretable models is to develop a model explainer that provides insight into the performance of the complex model.
+\kg{Moved the last sentence from the first paragraph here:} As a result of the desire to be able to explain the predictions, an area of research has emerged on machine learning explain the output from machine learning algorithms.
+One approach that is being taken to remedy the problem of uninterpretable models is to develop a model explainer that provides insight into the performance of the complex model.
 A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
@@
 
-In this paper, we will present some visualizations tools to assess the explanations from LIME in classification problems.
-Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
-\hh{still to come: outline of the remainder of the paper.}
-
-\section{Background}
-
-Predictive models are used in both regression and classification settings.
+\kg{I moved this paragraph here, because I think this is where I was to first introdude this concept, but it need a lot of reworking to fit in with the intro, and I need to finish writing my thoughts.} Predictive models are used in both regression and classification settings.
 For this paper, we will focus on the classification setting, and in particular, we will only discuss the case with a dichotomous response variable.
@@
 The model can make a type I error in which..., or the model can make a type II error in which...
+
+In this paper, we will present some visualizations tools to assess the explanations from LIME in classification problems.
+Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
+\hh{still to come: outline of the remainder of the paper.}
+
+\section{Background}
+
+\subsection{Model Explainers}
 
@@
 \section{Application}
+
+\subsection{Iris Data (?)}
+
+\subsection{Bullet Matching Data}
 

### 2019-06-13 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
worked on intro

@@
 
-\hh{Generally: avoid 'can be'. Replace by 'is'.  }
+To check on when editing writing: 
+\begin{itemize}
+\item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
+\item \kg{words to go back and make sure I am not using too often: ability, produce}
+\end{itemize}
 
@@
 
-\kg{Added in Heike's suggestions and made a few changes of my own to this paragraph:} In the field of statistics, there are two main uses for models: interpretation and prediction.
+\kg{I added in Heike's suggestions to the first paragraph and made some changes of my own.
+I divided the first paragraph into two parts and added a discusssion on reasons why interpretability is beneficial.
+Note that I also switched the two model uses from ``interpretation and prediction" to ``inference and prediction".
+Since a key part of the paper is about being able to interpret predictive models, I thought it might be good to distinguish between interpretation and inference.
+Heike, what do you think?}\\
+\\
+In the field of statistics, there are two main uses for models: \kg{inference} and prediction.
 Machine learning models are often used for the latter purpose.
-While these models have been proven to provide accurate predictions in a wide range of problems, this predictive ability comes at the cost of interpretability.
-These models are typically complex and lack a functional form, which makes it not possible to directly interpret the models and has earned them the reputation of being black boxes.
-The ability to interpret a model helps to diagnose the model and understand the predictions, and in some areas of application, the need to be able to explain the results from a model is critical.
+While these models have been proven to perform well in a wide range of problems, their predictive accuracy comes at the cost of interpretability.
+They are often complex algorithms that are good at identifying patterns in the data but lack a functional form, so it not possible to directly interpret them.
+As a result, they produce predictions that lack an explanation, which has earned them the reputation of being black box models.
+
+The ability to interpret a model serves multiple purposes.
+When a model is first fit, interpretations help to diagnosing the model.
+If it is possible to know what variables are influencing a prediction, it can be determined if the predictions are based on reasonable variables.
+If not, appropriate adjustments to the model can be made.
+After a model has been diagnosed and found to be reasonable, the explanations for the predictions can be used to understand the underlying mechanism that produced the data and provide an argument for why the predictions should be trusted.
+In some areas of application, this ability to be able to explain the results from a model is critical.
 
@@
 \citet{yu:2018} describe how healthcare has advanced through the use of machine learning in ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
-In \hh{both} of these cases, the decisions made based on the results of the machine learning models would greatly impact the lives of human beings.
-If it is not possible to explain the output from a model, it becomes questionable whether to trust the results from the model to make decisions.
+In both of these \kg{fields}, the decisions made based on the results of the machine learning models would greatly impact \kg{people's lives}.
+If it is not possible to explain the output from a model, it becomes questionable whether to \kg{rely} on the predictions to make important decisions.
 
@@
 The European Union has taken the desire to provide explanations from machine learning models a step further.
-In May 2018, the General Data Protection Regulation (GDPR) went into effect (https://eugdpr.org/the-regulation/gdpr-faqs/).
-The regulation includes a policy that gives the right for subjects affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
-As Goodman and Flaxman (2016) point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
-At minimum, it will require that an explanation of how the input variables relate to the predictions.
+In May 2018, the General Data Protection Regulation (GDPR) went into effect \footnote{https://eugdpr.org/the-regulation/gdpr-faqs/}.
+The regulation includes a policy that gives the right for \kg{individuals} affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
+As \citet{goodman:2016} point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
+\kg{While they point out that the wording of the policy leaves room for interpretation}, they believe that, at minimum, it will require that an explanation of how the input variables relate to the predictions.
 
-\kg{Moved the last sentence from the first paragraph here:} As a result of the desire to be able to explain the predictions, an area of research has emerged on machine learning explain the output from machine learning algorithms.
-One approach that is being taken to remedy the problem of uninterpretable models is to develop a model explainer that provides insight into the performance of the complex model.
+\kg{As a result of the push (wording?) to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.} One approach that is being taken to remedy the problem of uninterpretable models is to develop model explainers that provide insight into the performance of the complex model.
 A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
@@
 Currently, there are no recommendations for how to assess the explanations from LIME (need to check to make sure this is a true statement).
-\kg{I'd like to expand on this paragraph since this is really the focus of the paper.
+\kg{LIME provides easily understandable explanations, but the current implementations of LIME are based on linear models, which are not assessed.} \kg{I'd like to expand on this paragraph since this is really the focus of the paper.
 Then the last paragraph in the intro can outline the paper.}

### 2019-06-13 README.Rmd
updated to do list

--- 2019-06-12 README.Rmd
@@
 
-# Applying LIME to Bullet Data
+# LIME Research
 
-Repository for research project on assessing LIME by applying it to the Hamby bullet data. The contents of this respository are listed below.
+Repository for research projects on LIME applied to the Hamby bullet data.
 
-### app
+Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/
+
+## Talking points
+
+## To Do List
+
+**Current Week**
+
+- finish writing and editing introduction
+- draft background section
+- fix outline of the rest of the paper now that I have a clear vision
+
+**Later**
+
+- finish journal on understanding lime (look at the RF in the local region
+  lime is considering to see if it agrees with the lime explanations)
+- think about how the argmin is accomplished by the LIME R package
+- change distance matrix in seriation to be 5-# of variables shared between two rows
+  or try using distance matrix computed on the feature values
+- fix issue with seriation
+- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
+- assess lime results on logistic regression models
+- think about how to implement a simulation with a random forest
+- add in feature selection methods to LIME input options
+- turn repetitive code into functions
+- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
+- look more into Molnar and his adviser Bernd
+- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
+- he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
+- look back at 601 notes from Kaiser and Hadley's removing the blindfold and
+  think about how this could be applied with random forests
+- try retriculate to apply python version of lime
+- look at 'removing the blindfold' for ideas
+- read through Heike's new function
+- think of a way to compute consistency across top two features
+- compare the simple models based on different number of bins using an F-test
+- look into literature on binning methods
+- think about why R^2 would be better for some binning methods
+- look into computing a diversity or consistency measure for the sensitivity analysis
+- create distribution visualizations bins
+- include a penalty for the number of parameters when choosing bins
+- determine the best number of bins to use for each variable
+- look at the AUC after binning
+- write a draft of the examiners paper
+- try out different weights
+- read through LIME papers again
+- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
+- try out logistic regression idea for bins (write own bin list to put in explain)
+- try out subsampling idea
+- read new paper on Anchor
+- read book Dr. Dixon lent me on sensativity analyses
+- try visualizing the features from the test data using dimension reduction and
+  coloring them by variables suggested to be important by lime
+- look into papers by Giles Hooker and Lucas Mentch
+
+## Contents
+
+Descriptions of the materials in this respository are listed below.
+
+#### app
 

### 2019-06-14 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
finished updates on intro and am feeling okay about where it is right now

@@
 \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
-\item \kg{words to go back and make sure I am not using too often: ability, produce}
+\item \kg{words to go back and make sure I am not using too often: ability, produce, understand}
 \end{itemize}
@@
 
-\kg{I added in Heike's suggestions to the first paragraph and made some changes of my own.
-I divided the first paragraph into two parts and added a discusssion on reasons why interpretability is beneficial.
-Note that I also switched the two model uses from ``interpretation and prediction" to ``inference and prediction".
-Since a key part of the paper is about being able to interpret predictive models, I thought it might be good to distinguish between interpretation and inference.
-Heike, what do you think?}\\
+\kg{Updates from KG:
+\begin{itemize}
+\item Added in Heike's suggestions to the first paragraph and made some changes of my own 
+\item Divided the first paragraph into two parts and added a discussion on reasons why interpretability is beneficial
+\item Switched the two model uses from ``interpretation and prediction" to ``inference and prediction" to distinguish between interpretation and inference
+\item Added most of the references (still need to add the ones about model explainers)
+\item Fixed some wordings here and there
+\item Expanded on the importance of assessing model explainers
+\item Added an outline of the rest of the paper
+\end{itemize}
+At some point, I plan to return to this section to work on the wording, but I finally have it at a point where it contains the ideas that I had intended.
+Heike, what do you think of it at this point?}\\
 \\
@@
 Machine learning models are often used for the latter purpose.
-While these models have been proven to perform well in a wide range of problems, their predictive accuracy comes at the cost of interpretability.
+While these models have been proven to perform well in a wide range of prediction problems, their accuracy comes at the cost of interpretability.
 They are often complex algorithms that are good at identifying patterns in the data but lack a functional form, so it not possible to directly interpret them.
-As a result, they produce predictions that lack an explanation, which has earned them the reputation of being black box models.
+As a result, they produce predictions that lack an explanation, which has earned them the reputation of being ``black box models".
 
-The ability to interpret a model serves multiple purposes.
-When a model is first fit, interpretations help to diagnosing the model.
-If it is possible to know what variables are influencing a prediction, it can be determined if the predictions are based on reasonable variables.
+\kg{The ability to interpret a model serves multiple purposes.
+When a model is first fit, interpretations help to diagnose the model.
+Knowing which variables influence a prediction makes it possible to determine if the predictions are based on reasonable variables.
 If not, appropriate adjustments to the model can be made.
-After a model has been diagnosed and found to be reasonable, the explanations for the predictions can be used to understand the underlying mechanism that produced the data and provide an argument for why the predictions should be trusted.
-In some areas of application, this ability to be able to explain the results from a model is critical.
+After a model has been diagnosed, the explanations for the predictions are used to understand the underlying mechanism that produced the data and provide an argument for why the predictions should be trusted.
+In some areas of application, this ability to be able to explain the results from a model is critical.}
 
-The forensics sciences and the heath care industry are two areas that have benefitted from machine learning but have an obvious need for explainable predictions.
+The forensics sciences and the heath care industry are two areas that have benefited from machine learning but have an obvious need for explainable predictions.
 For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun.
@@
 
-As an example, suppose that forensics examiners are trying to determine if a bullet used in a crime was fired from the gun that belongs to a suspect in the investigaion.
+As an example, suppose that forensics examiners are trying to determine if a bullet used in a crime was fired from the gun that belongs to a suspect in the investigation.
 A random forest model could be used to produce a probability that the bullet was fired from the gun under question.
@@
 As \citet{goodman:2016} point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
-\kg{While they point out that the wording of the policy leaves room for interpretation}, they believe that, at minimum, it will require that an explanation of how the input variables relate to the predictions.
+\kg{The wording of the policy leaves room for interpretation, but they believe that}, at minimum, it will require that an explanation of how the input variables relate to the predictions.
 
-\kg{As a result of the push (wording?) to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.} One approach that is being taken to remedy the problem of uninterpretable models is to develop model explainers that provide insight into the performance of the complex model.
-A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into mechanism of how the model produces predictions.
-Recently, a handful of model explainers have been developed (reference).
-LIME (local interpretable model explanations) is one such model explainer (reference).
+\kg{As a result of the movement to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.} One approach that is being taken is to develop model explainers that provide insight into the performance of the complex model (reference).
+A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into \kg{the process that the model goes through} to produce predictions.
+LIME (local interpretable model explanations) is one such model explainer \citep{ribeiro:2016}.
 
 While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model at the local level for a single prediction of interest.
-Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex "black box model" in a local region around a prediction of interest.
-(a good place to include an image to help with this explanation)
+\kg{It was designed to work with any model and to produce easily understandable explanations.} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
+\kg{The interpretation of the simple model is used to explain the variables that most influenced the prediction made by the complex model.}
 
-The explanation that is produced from the explainer is also a prediction or an element of a model.
-Since it is not directly extracted from the complex model, it is important to ask the question, ``How reliable is the explanation?".
-Currently, there are no recommendations for how to assess the explanations from LIME (need to check to make sure this is a true statement).
-\kg{LIME provides easily understandable explanations, but the current implementations of LIME are based on linear models, which are not assessed.} \kg{I'd like to expand on this paragraph since this is really the focus of the paper.
-Then the last paragraph in the intro can outline the paper.}
+\kg{It is important to keep in mind that the explanation produced by the explainer is not a direct interpretation of the complex model.
+Instead, it is based on a model that is trying to mimic a part of the complex model.} Thus, it is necessary to ask the question, ``How reliable is the explanation?".
+\kg{One way to answer this question is to understand how well the explainer model approximates the complex model.}
 
-\kg{I moved this paragraph here, because I think this is where I was to first introdude this concept, but it need a lot of reworking to fit in with the intro, and I need to finish writing my thoughts.} Predictive models are used in both regression and classification settings.
-For this paper, we will focus on the classification setting, and in particular, we will only discuss the case with a dichotomous response variable.
-\hh{Accepted best practice for all}  predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
+\kg{The current implementations of LIME use a linear regression model as the explainer model (references to R and Python packages).
+These implementations are relying on the assumption that the relationship between the complex model predictions and the features is linear in a local region.
+It is possible to imagine scenarios where this is not the case.
+Thus, it is important to assess this assumption in order to trust the explanations produced by LIME.
+Additionally, the implementations offer various input settings, but little work has been done to provide advice on how to specify the settings in practice (look more into this).
+An assessment of the explanations could also help to determine which settings produce the explainer model with the best approximation of the complex model.}
+
+In this paper, we will present some visualizations tools to assess the explanations from LIME.
+While predictive models are used in both regression and classification settings, we will focus on the classification setting for this paper.
+For additional simplicity, we will only discuss the case with a dichotomous response variable, but we believe that the work is adaptable for other situations.
+
+\kg{Section \ref{background} provides some background on explainer models that have been developed, a description of the LIME algorithm, and the current implementations of LIME.
+In Section \ref{methods}, we discuss ways to assess the LIME explainer model and introduces our visualization tools.
+Section \ref{application} demonstrates the use of our diagnostic tools with a logistic regression model fit to the iris data (?) and a random forest model fit to a forensics bullet matching dataset.
+To conclude, Section \ref{discussion} reviews the importance of assessing the LIME explainer model, discusses how the results from the example provide possible insights into the workings of LIME, and suggests future research directions.}
+
+\section{Background} \label{background}
+
+\kg{Just putting this here for now - needs lots of work or I may even remove it:} \hh{Accepted best practice for all} predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
 The training data is used to fit the complex model, and the testing data is used to assess the model.
@@
 The model can make a type I error in which..., or the model can make a type II error in which...
-
-In this paper, we will present some visualizations tools to assess the explanations from LIME in classification problems.
-Additionally, we will show an example using these tools on explanations from a forensics bullet matching dataset, and we will discuss how the results from the example provide some possible insights into the workings of LIME.
-\hh{still to come: outline of the remainder of the paper.}
-
-\section{Background}
 
@@
 A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
+
+(a good place to include an image to help with this explanation)
 
@@
 
-\subsection{Implemention of LIME in R}
+\subsection{Implementation of LIME in R}
 
@@
 
-\section{Methods}
+\section{Methods} \label{methods}
+
+Ways to understand if the LIME explainer is doing a good job:
+
+\begin{itemize}
+\item diagnose the explainer to make sure that it is fitting the data well
+\item compare the prediction made by the explainer to the complex model prediction
+\item visualize all explanations to understand if the explanations are local or global
+\item compare results from different input options
+\end{itemize}
 
@@
 
-\section{Application}
+\section{Application} \label{application}
 
@@
 Figure ...
-is a heatamp showing the top feature chosen by lime for each of the cases in the test data and different bin based sampling methods.
+is a heat map showing the top feature chosen by lime for each of the cases in the test data and different bin based sampling methods.
 The rows represent the cases in the test data, and the columns represent the sampling methods.
@@
 This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.
+
+\section{Discussion} \label{discussion}
 

### 2019-06-14 README.Rmd
updated to do list

@@
 
+- can I remove some of the sources from the references file that I am not going to use?
+- I finished writing and editing the introduction - what do you think?
+
 ## To Do List
 
-**Current Week**
+**Current**
 
-- finish writing and editing introduction
 - draft background section
 - fix outline of the rest of the paper now that I have a clear vision
+- read through papers giving an overview of the current explanation methods
 
@@
 
-#### app
+**app**
 
@@
 
-- **app.R**: code for the Shiny app
+- `app.R`: code for the Shiny app
 
-#### code
+**code**
 
@@
 
-- **helper_functions.R**: R script with functions that I use in the journals and will probably end up using in the papers as well
+- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well
 
-#### data
+**data**
 
@@
 
-- **hamby173and252_train.csv**: training data that I cleaned (it should match the data used to fit `rtrees`)
-- **hamby224_bin_boundaries.rds**: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
-- **hamby224_bins.rds**: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
-- **hamby224_explain**: the output from the `explain` function in lime from the single implementation with all of the different input options
-- **hamby224_lime**: the output from the `lime` function in lime from the single implementation with all of the different input options
-- **hamby224_lime_comparisons**: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
-- **hamby224_lime_inputs**: LIME input settings used for the single implementation of LIME
-- **hamby224_sensitivity_inputs**: LIME input settings used for the sensativity analysis of LIME
-- **hamby224_sensitivity_joined.csv**: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
-- **hamby224_sensitivity_outputs.rds**: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
-- **hamby223_test.csv**: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
-- **hamby224_test_explain.rds**: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
+- `hamby173and252_train.csv`: training data that I cleaned (it should match the data used to fit `rtrees`)
+- `hamby224_bin_boundaries.rds`: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
+- `hamby224_bins.rds`: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
+- `hamby224_explain`: the output from the `explain` function in lime from the single implementation with all of the different input options
+- `hamby224_lime`: the output from the `lime` function in lime from the single implementation with all of the different input options
+- `hamby224_lime_comparisons`: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
+- `hamby224_lime_inputs`: LIME input settings used for the single implementation of LIME
+- `hamby224_sensitivity_inputs`: LIME input settings used for the sensativity analysis of LIME
+- `hamby224_sensitivity_joined.csv`: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
+- `hamby224_sensitivity_outputs.rds`: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
+- `hamby223_test.csv`: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
+- `hamby224_test_explain.rds`: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
 - raw: original data given to me by Heike
-    - **features-hamby173and252.csv**
-    - **h224-set1-features.rds**
-    - **h224-set11-features.rds**
+    - `features-hamby173and252.csv`
+    - `h224-set1-features.rds`
+    - `h224-set11-features.rds`
 
-#### journals
+**journals**
 
@@
 
-- **00-objectives_and_ideas**: background of the research project, goals of the project, concerns with LIME, and ideas to try
-- **01-training_and_testing_data**: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
-- **02-plotting_training_and_testing_data**: exploratory plots of the training and testing data
-- **03-computation_issues**: documentation of some of the computation issues I ran into during the project
-- **04-lime_algorithm_and_proposed_methods**: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
-- **05-applying_lime_to_rtrees**: application of lime and sensativity analysis for many different input options
-- **06-assessing_lime_explanations**: assessment of the lime explanations
-- **07-logistic_regression**: logistic regressions fit to the bullet data and application of lime to the logistic regression
-- **08-iris_comparison**: applying LIME to a random forest fit to the iris data
-- **09-understanding_lime**: attempts to visualize the results from LIME to understand how LIME works
-- **10-other_explainers**: trying out other model explainers
-- **notes from Heike.pdf**: scans of notes written by Heike for this project
+- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
+- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
+- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
+- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
+- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
+- `05-applying_lime_to_rtrees`: application of lime and sensativity analysis for many different input options
+- `06-assessing_lime_explanations`: assessment of the lime explanations
+- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
+- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
+- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
+- `10-other_explainers`: trying out other model explainers
+- `notes from Heike.pdf`: scans of notes written by Heike for this project
 
-#### papers
+**papers**
 
@@
 
-- **bullet_application**: explains how LIME can be used to understand the random forest model fit to bullet matching data
-- **lime_diagnostics**: explains the need to assess LIME and presents some visual diagnostic tools
+- `bullet_application`: explains how LIME can be used to understand the random forest model fit to bullet matching data
+- `lime_diagnostics`: explains the need to assess LIME and presents some visual diagnostic tools

### 2019-06-18 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
minor edits

@@
 \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
+\item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
 \item \kg{words to go back and make sure I am not using too often: ability, produce, understand}
@@
 \\
-In the field of statistics, there are two main uses for models: \kg{inference} and prediction.
+In the field of statistics, there are two main uses for models: inference and prediction.
 Machine learning models are often used for the latter purpose.
@@
 \citet{yu:2018} describe how healthcare has advanced through the use of machine learning in ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes.
-In both of these \kg{fields}, the decisions made based on the results of the machine learning models would greatly impact \kg{people's lives}.
-If it is not possible to explain the output from a model, it becomes questionable whether to \kg{rely} on the predictions to make important decisions.
+In both of these fields, the decisions made based on the results of the machine learning models can greatly impact people's lives.
+If it is not possible to explain the output from a model, it becomes questionable whether to rely on the predictions to make important decisions.
 
@@
 In May 2018, the General Data Protection Regulation (GDPR) went into effect \footnote{https://eugdpr.org/the-regulation/gdpr-faqs/}.
-The regulation includes a policy that gives the right for \kg{individuals} affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
-As \citet{goodman:2016} point out, this regulation will have a great effect on the way that machine learning algorithms are used to make decisions.
-\kg{The wording of the policy leaves room for interpretation, but they believe that}, at minimum, it will require that an explanation of how the input variables relate to the predictions.
+The regulation includes a policy that gives the right for individuals affected by decisions made via automated algorithms to understand the logic behind the decisions being made.
+As \citet{goodman:2016} point out, this regulation has a great effect on the way that machine learning algorithms are used to make decisions.
+The wording of the policy leaves room for interpretation, but \hh{the authors} believe that, at a minimum, \hh{the regulations} will require that an explanation of how the input variables relate to the predictions be provided.
 
-\kg{As a result of the movement to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.} One approach that is being taken is to develop model explainers that provide insight into the performance of the complex model (reference).
-A model explainer is a method that is separate from the model but uses the model and output from the model to provide understanding into \kg{the process that the model goes through} to produce predictions.
-LIME (local interpretable model explanations) is one such model explainer \citep{ribeiro:2016}.
+As a result of the movement to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.
+One approach that is being taken is to develop model explainers that provide insight into the performance of the complex model (reference).
+A model explainer is a method that is separate from the model but uses the model and output from the model to shed light on the process that the model goes through to produce predictions.
+LIME (local interpretable model\hh{-agnostic} explanations) is one such model explainer \citep{ribeiro:2016}.
 
-While some model explainers are focused on understanding a model at the global level, LIME was designed to explain the model at the local level for a single prediction of interest.
-\kg{It was designed to work with any model and to produce easily understandable explanations.} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
-\kg{The interpretation of the simple model is used to explain the variables that most influenced the prediction made by the complex model.}
+While some model explainers are focused on understanding a model at the global level, LIME is designed to explain the model locally for a single prediction of interest.
+\hh{Additionally, LIME} was designed to work with any model and to produce easily understandable explanations.
+\hh{XXX a citation might be good here for local and agnostic} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
+The interpretation of the simple model is then used to explain the variables that most influenced the prediction made by the complex model.
 
-\kg{It is important to keep in mind that the explanation produced by the explainer is not a direct interpretation of the complex model.
-Instead, it is based on a model that is trying to mimic a part of the complex model.} Thus, it is necessary to ask the question, ``How reliable is the explanation?".
-\kg{One way to answer this question is to understand how well the explainer model approximates the complex model.}
+\hh{At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the  black box model, a simpler explainer model is added.
+To be able to trust in the explanation it is imperative to check that the explainer model is reliable and does not over-simplify the black-box model.
+}
+It is important to keep in mind that the explanation produced by the explainer is not a direct interpretation of the complex model.
+Instead, it is based on a model that is trying to mimic a part of the complex model.
+Thus, it is necessary to ask the question, ``How reliable is the explanation?".
+One way to answer this question is to understand how well the explainer model approximates the complex model.
 
-\kg{The current implementations of LIME use a linear regression model as the explainer model (references to R and Python packages).
+The current implementations of LIME use a linear regression model as the explainer model (references to R and Python packages).
 These implementations are relying on the assumption that the relationship between the complex model predictions and the features is linear in a local region.
-It is possible to imagine scenarios where this is not the case.
+\hh{XXX don't get into a discussion of locally not linear models.
+From theory we know that every function can be approximated locally by a linear function.
+From a practical point of view the local area might be too small to be relevant.}
+\kg{It is possible to imagine scenarios where this is not the case.
 Thus, it is important to assess this assumption in order to trust the explanations produced by LIME.
@@
 
-\kg{Section \ref{background} provides some background on explainer models that have been developed, a description of the LIME algorithm, and the current implementations of LIME.
+Section \ref{background} provides some background on explainer models that have been developed, a description of the LIME algorithm, and the current implementations of LIME.
 In Section \ref{methods}, we discuss ways to assess the LIME explainer model and introduces our visualization tools.
-Section \ref{application} demonstrates the use of our diagnostic tools with a logistic regression model fit to the iris data (?) and a random forest model fit to a forensics bullet matching dataset.
-To conclude, Section \ref{discussion} reviews the importance of assessing the LIME explainer model, discusses how the results from the example provide possible insights into the workings of LIME, and suggests future research directions.}
+Section \ref{application} demonstrates the use of our diagnostic tools with a logistic regression model fit to the iris data (?
+\hh{urgh.
+but we can decide on that later} ) and a random forest model fit to a forensics bullet matching dataset.
+To conclude, Section \ref{discussion} reviews the importance of assessing the LIME explainer model, discusses how the results from the example provide possible insights into the workings of LIME, and suggests future research directions.
 

### 2019-06-21 README.Rmd
added talking point to readme and lime image
updated to do list

@@
 
-# LIME Research
+# LIME Research <img align="right" height="200" src="./figures/lime.png">
 
@@
 
+- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
+- is it okay if I change the repo name to "lime-research"?
 - can I remove some of the sources from the references file that I am not going to use?
@@
 - draft background section
-- fix outline of the rest of the paper now that I have a clear vision
 - read through papers giving an overview of the current explanation methods
+- create first draft of JSM poster
 
@@
 
-- finish journal on understanding lime (look at the RF in the local region
-  lime is considering to see if it agrees with the lime explanations)
-- think about how the argmin is accomplished by the LIME R package
+- LIME diganostics  
+    - turn repetitive code into functions
+    - try out different weights
     - change distance matrix in seriation to be 5-# of variables shared between two rows
-  or try using distance matrix computed on the feature values
-- fix issue with seriation
+    - try using distance matrix computed on the feature value with seriation
+    - add in feature selection methods to LIME input options
+    - think of a way to compute consistency across top two features
+    - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
+    - he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
+    - compare the simple models based on different number of bins using an F-test
+    - look into computing a diversity or consistency measure for the sensitivity analysis
+    - include a penalty for the number of parameters when choosing bins
+    - look at the AUC after binning
+    - compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
+    - try visualizing the features from the test data using dimension reduction and
+  coloring them by variables suggested to be important by lime
+- explainer models
+    - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
+    - look more into Molnar and his adviser Bernd
+- understanding LIME
+    - read through LIME papers again
+    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
     - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
     - assess lime results on logistic regression models
-- think about how to implement a simulation with a random forest
-- add in feature selection methods to LIME input options
-- turn repetitive code into functions
-- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
-- look more into Molnar and his adviser Bernd
-- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
-- he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
-- look back at 601 notes from Kaiser and Hadley's removing the blindfold and
-  think about how this could be applied with random forests
+    - think about how the argmin is accomplished by the LIME R package
     - try retriculate to apply python version of lime
-- look at 'removing the blindfold' for ideas
-- read through Heike's new function
-- think of a way to compute consistency across top two features
-- compare the simple models based on different number of bins using an F-test
     - look into literature on binning methods
     - think about why R^2 would be better for some binning methods
-- look into computing a diversity or consistency measure for the sensitivity analysis
-- create distribution visualizations bins
-- include a penalty for the number of parameters when choosing bins
+    - read new paper on Anchor
+- simulation with RF
+    - think about how to implement a simulation with a random forest
+    - look back at 601 notes from Kaiser for model assessment
+    - look at Hadley's 'removing the blindfold' for ideas
+    - read book Dr. Dixon lent me on sensativity analyses
+- possible improvements to LIME
     - determine the best number of bins to use for each variable
-- look at the AUC after binning
-- write a draft of the examiners paper
-- try out different weights
-- read through LIME papers again
-- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
-- try out logistic regression idea for bins (write own bin list to put in explain)
     - try out subsampling idea
-- read new paper on Anchor
-- read book Dr. Dixon lent me on sensativity analyses
-- try visualizing the features from the test data using dimension reduction and
-  coloring them by variables suggested to be important by lime
+- random forests confidence intervals
     - look into papers by Giles Hooker and Lucas Mentch
+    - Dr. Nettleton paper
 

### 2019-06-25 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
small changes to intro

@@
 
-\kg{Updates from KG:
-\begin{itemize}
-\item Added in Heike's suggestions to the first paragraph and made some changes of my own 
-\item Divided the first paragraph into two parts and added a discussion on reasons why interpretability is beneficial
-\item Switched the two model uses from ``interpretation and prediction" to ``inference and prediction" to distinguish between interpretation and inference
-\item Added most of the references (still need to add the ones about model explainers)
-\item Fixed some wordings here and there
-\item Expanded on the importance of assessing model explainers
-\item Added an outline of the rest of the paper
-\end{itemize}
-At some point, I plan to return to this section to work on the wording, but I finally have it at a point where it contains the ideas that I had intended.
-Heike, what do you think of it at this point?}\\
-\\
 In the field of statistics, there are two main uses for models: inference and prediction.
@@
 
-\kg{The ability to interpret a model serves multiple purposes.
+The ability to interpret a model serves multiple purposes.
 When a model is first fit, interpretations help to diagnose the model.
@@
 After a model has been diagnosed, the explanations for the predictions are used to understand the underlying mechanism that produced the data and provide an argument for why the predictions should be trusted.
-In some areas of application, this ability to be able to explain the results from a model is critical.}
+In some areas of application, this ability to be able to explain the results from a model is critical.
 
@@
 As \citet{goodman:2016} point out, this regulation has a great effect on the way that machine learning algorithms are used to make decisions.
-The wording of the policy leaves room for interpretation, but \hh{the authors} believe that, at a minimum, \hh{the regulations} will require that an explanation of how the input variables relate to the predictions be provided.
+The wording of the policy leaves room for interpretation, but the authors believe that, at a minimum, the regulations will require that an explanation of how the input variables relate to the predictions be provided.
 
@@
 A model explainer is a method that is separate from the model but uses the model and output from the model to shed light on the process that the model goes through to produce predictions.
-LIME (local interpretable model\hh{-agnostic} explanations) is one such model explainer \citep{ribeiro:2016}.
+LIME (local interpretable model-agnostic explanations) is one such model explainer \citep{ribeiro:2016}.
 
@@
 These implementations are relying on the assumption that the relationship between the complex model predictions and the features is linear in a local region.
-\hh{XXX don't get into a discussion of locally not linear models.
-From theory we know that every function can be approximated locally by a linear function.
-From a practical point of view the local area might be too small to be relevant.}
-\kg{It is possible to imagine scenarios where this is not the case.
-Thus, it is important to assess this assumption in order to trust the explanations produced by LIME.
+It is important to assess this assumption in the local region of interest in order to trust the explanations produced by LIME.
 Additionally, the implementations offer various input settings, but little work has been done to provide advice on how to specify the settings in practice (look more into this).
-An assessment of the explanations could also help to determine which settings produce the explainer model with the best approximation of the complex model.}
+An assessment of the explanations could also help to determine which settings produce the explainer model with the best approximation of the complex model.
 

### 2019-06-25 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
couple of edits

@@
 
+\hh{It does this -- XX references :) }
 It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
-The complex model is applied to the simulated dataset to obtain predictions.
-The observations associated with predictions are used as the response variable in a ridge regression model with the the simulated features as the predictor variable with the highest weight given to observations closest to the prediction of interest.
-Feature selection is performed to identify the most important variables in the local region.
+\hh{more on how the data is simulated - that's an important step.} The complex model is then applied to the simulated dataset to obtain predictions.
+The observations associated with predictions are used as the response variable in a ridge regression model with the  simulated features as the predictor variable with the highest weight given to observations closest to the prediction of interest.
+\hh{more on the weights} Feature selection is performed to identify the most important variables in the local region.
 A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
@@
 The procedure below is defined in this context.
-Furthermore, the implementation of LIME used in this paper is via the lime R package, and the procedure describes the methods used by the R package.
-This deviates a bit from the original procedure described by Riberio, Singh, and Guestrin (2016).
-We attempted to highlight these deviations.
+Furthermore, \hh{in this paper we are relying on the LIME implementation in R \citep{lime}.
+This implementation deviates at times from the original implementation by \citet{riberio}.
+Whenever the implementations differ, we will} highlight these deviations.
 
@@
 observations from a set of $p$ continuous features for a specific case in the data) % the LIME paper uses d instead of p for the dimension
-\item $x'\in\mathbb{R}^{p'}$: vector for the interpretable representation of the instance being explained (e.g.
+\item $x'\in\mathbb{R}^{p'}$: \hh{what is $p'$ ?
+shouldn't $p$ and $p'$ be the same?
+I thought that you were trying to say that $x'$ explains $x$?} vector for the interpretable representation of the instance being explained (e.g.
 a vector of indicator variables associated with the features chosen through feature selection indicating whether or not the observed value is in the bin created by LIME for the feature)
-\item $G$: class of potentially interpretable models (e.g. linear models, decision trees, rule lists)
+\item $G$: class of potentially \hh{why potentially?} interpretable models (e.g. linear models, decision trees, rule lists)
 \item $g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$

### 2019-06-25 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
small edits during meeting

@@
 observations from a set of $p$ continuous features for a specific case in the data) % the LIME paper uses d instead of p for the dimension
-\item $x'\in\mathbb{R}^{p'}$: \hh{what is $p'$ ?
-shouldn't $p$ and $p'$ be the same?
-I thought that you were trying to say that $x'$ explains $x$?} vector for the interpretable representation of the instance being explained (e.g.
+\item $x'\in\mathbb{R}^{p'}$: \hh{where $1 \le p' \le p$}  vector for the interpretable representation of the instance being explained (e.g.
 a vector of indicator variables associated with the features chosen through feature selection indicating whether or not the observed value is in the bin created by LIME for the feature)
-\item $G$: class of potentially \hh{why potentially?} interpretable models (e.g. linear models, decision trees, rule lists)
-\item $g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$
+\item $G$: class of potentially interpretable models (e.g. linear models, decision trees, rule lists) \hh{in our case, we will use ridge regression}
+\item $g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$ \hh{ do we need $\{0,1\}^{p'}$?}
 \item $\Omega(g)$: measure of complexity of $g$ (e.g. depth of a tree, number of non-zero coefficients in a linear model fit using LASSO)

### 2019-06-25 README.Rmd
updated talking points

@@
 - adding a random noise variable to the model to see if LIME ever chooses it as an important variable
-- is it okay if I change the repo name to "lime-research"?
 - can I remove some of the sources from the references file that I am not going to use?
-- I finished writing and editing the introduction - what do you think?
 

### 2019-08-05 README.Rmd
updated questions
updated discussion points
added a talking point
added item to discuss

@@
 
+- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
+- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
+- opinions on saving pdf files to github - if no - what to do?
 - adding a random noise variable to the model to see if LIME ever chooses it as an important variable
 - can I remove some of the sources from the references file that I am not going to use?
+- have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
 

### 2019-08-05 README.Rmd
added another talking point

--- 2019-06-25 README.Rmd
@@
 
+- see email from Shar
+- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
+- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
+- opinions on saving pdf files to github - if no - what to do?
 - adding a random noise variable to the model to see if LIME ever chooses it as an important variable
 - can I remove some of the sources from the references file that I am not going to use?
+- have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
 

### 2019-08-06 README.Rmd
prepared for meeting with Heike

--- 2019-06-25 README.Rmd
@@
 
-- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
-- can I remove some of the sources from the references file that I am not going to use?
+JSM
+
+- Lots of "enthusiasm" about interpreting random forest models from individuals who stopped by the poster (the next presenter had to ask me to leave)
+- Many people seemed to agree that just using the default values of LIME will not be enough to necessarily capture the local trend
+- Shapley values were mentioned several times
+- See email from Shar (references and possible collaborator)
+- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
+- Saw Andrew - he has invited me to give a talk at Lawrence this winter
+- I updated my website while at JSM
+- I realized that I left the CSAFE logo off the poster. Should I always include this to acknowledge that there were the source of funding for the dataset?
+
+SAMSI
+
+- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
+- Opinions on saving pdf files to github - if no - what to do?
+
+NCCC
+
+- Adding a random noise variable to the model to see if LIME ever chooses it as an important variable
+
+Paper
+
+- Can I remove some of the sources from the references file that I am not going to use?
+- Have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
+- What are your recommendations for going forward in the month of August? 
+- Should we start talking about a date for my oral prelim?
 
@@
 - read through papers giving an overview of the current explanation methods
-- create first draft of JSM poster
 

### 2019-08-06 README.Rmd
updated talking points after meeting

--- 2019-08-05 README.Rmd
@@
 
-- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
-- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
-- opinions on saving pdf files to github - if no - what to do?
-- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
-- can I remove some of the sources from the references file that I am not going to use?
-- have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
+- Can I remove some of the sources from the references file that I am not going to use?
 
@@
 
-- draft background section
+- work on first draft of paper
 - read through papers giving an overview of the current explanation methods
-- create first draft of JSM poster
 

### 2019-08-06 README.Rmd
added MAPLE

@@
     - look more into Molnar and his adviser Bernd
+    - look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
 - understanding LIME

### 2019-08-08 papers/lime_diagnostics/code/figure-creation.Rmd
worked on paper

---
title: "Figure Creation"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Overview

This document contains the code for creating figures to be included in the LIME diagnostic paper.

```{r}
# Load packages
library(cowplot)
library(gower)
library(graphics)
library(tidyverse)
```

# Conceptual Depiction of LIME

```{r}
# Generate data
set.seed(20190624)
lime_data <- data.frame(feature1 = sort(runif(250, 0, 1)),
                      feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
  mutate(prediction = if_else(feature1 >= 0 & feature1 < 0.1, (0.3 * feature1) + rnorm(n(), 0, 0.01), 
                      if_else(feature1 >= 0.1 & feature1 < 0.3, rbeta(n(), 1, 0.5), 
                      if_else(feature1 >= 0.3 & feature1 < 0.5, sin(pi* feature1) + rnorm(n(), 0, 0.5),
                      if_else(feature1 >= 0.5 & feature1 < 0.8, -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
                      if_else(feature1 >= 0.8 & feature1 < 0.9, 0.5 + runif(n(), -0.5, 0.5), 
                              0.5 + rnorm(n(), 0, 0.3)))))))

# Specify a prediction of interest
prediction_of_interest <- data.frame(feature1 = 0.07,
                                feature2 = 200,
                                prediction = 0.05, 
                                color = factor("Prediction of Interest"))

# Compute the distance between the prediction of interest 
lime_data$distance <- (1 - gower_dist(x = prediction_of_interest, y = lime_data))^20

# Fit the interpretable explainer model
lime_explainer <- lm(prediction ~ feature1 + feature2, data = lime_data, weights = distance)

# Predictions versus feature 1
plot_feature1 <- ggplot(lime_data, aes(x = feature1, y = prediction, size = distance)) + 
  geom_abline(intercept = coef(lime_explainer)[[1]] + coef(lime_explainer)[[3]]*prediction_of_interest$feature2, 
              slope = coef(lime_explainer)[[2]], 
              size = 1) +
  geom_point() + 
  geom_point(data = prediction_of_interest,
             mapping = aes(x = feature1, y = prediction),
             color = "#EFB084",
             size = 5) +
  theme_linedraw(base_family = "Times") +
  labs(x = "Feature 1", 
       y = "Black-Box Prediction") + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none")

# Predictions versus feature 2
plot_feature2 <- ggplot(lime_data, aes(x = feature2, y = prediction, size = distance)) +
  geom_abline(intercept = coef(lime_explainer)[[1]] + coef(lime_explainer)[[2]]*prediction_of_interest$feature1,
              slope = coef(lime_explainer)[[3]],
              size = 1) +
  geom_point() +
  geom_point(data = prediction_of_interest,
             mapping = aes(x = feature2, y = prediction),
             color = "#EFB084",
             size = 5) +
  theme_linedraw(base_family = "Times") +
  labs(x = "Feature 2",
       y = "Black-Box Prediction") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none")

# Join the two feature plots
lime_plots <- plot_grid(plot_feature1, plot_feature2)

# Create a plot to extract a legend for the prediction of interest
lime_legend_plot <- ggplot(prediction_of_interest, aes(x = feature1, y = prediction, color = color)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("#EFB084")) +
  theme_classic(base_family = "Times") +
  labs(color = "") +
  theme(legend.position = "bottom")

# Extract the legend
lime_legend <- get_legend(lime_legend_plot)

# Join the title, plots, legend, and caption into one figure
lime_concept <- plot_grid(lime_plots, lime_legend,
                         ncol = 1,
                         rel_heights = c(0.9, 0.1))

# Preview the plot
lime_concept

# Save the plot
ggsave(filename = "../figures/lime_concept.png",
       plot = lime_concept,
       height = 4, width = 8)
```

### 2019-08-08 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
worked on paper

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE, echo = FALSE}
 
@@
 While these models have been proven to perform well in a wide range of prediction problems, their accuracy comes at the cost of interpretability.
-They are often complex algorithms that are good at identifying patterns in the data but lack a functional form, so it not possible to directly interpret them.
+They are often complex algorithms that are good at identifying patterns in the data but lack a functional form \kg{XXX Is it okay for me to make this statement about the functional form?}, so it not possible to directly interpret them.
 As a result, they produce predictions that lack an explanation, which has earned them the reputation of being ``black box models".
@@
 
-The European Union has taken the desire to provide explanations from machine learning models a step further.
+The European Union has taken the desire to provide explanations for machine learning model predictions a step further.
 In May 2018, the General Data Protection Regulation (GDPR) went into effect \footnote{https://eugdpr.org/the-regulation/gdpr-faqs/}.
@@
 
-While some model explainers are focused on understanding a model at the global level, LIME is designed to explain the model locally for a single prediction of interest.
-\hh{Additionally, LIME} was designed to work with any model and to produce easily understandable explanations.
-\hh{XXX a citation might be good here for local and agnostic} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
+While some model explainers are focused on understanding a model at the global level, LIME is designed provide a local explanations by focusing on a single prediction of interest.
+Additionally, LIME was designed to work with any model and to produce easily understandable explanations.
+\citep{ribeiro:2016} \hh{XXX a citation might be good here for local and agnostic} \kg{Is it okay to include the same reference to the original LIME paper again?} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
 The interpretation of the simple model is then used to explain the variables that most influenced the prediction made by the complex model.
+Figure \ref{fig:limeconcept} provides a visualization of this conceptual understanding of LIME.
 
-\hh{At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the  black box model, a simpler explainer model is added.
-To be able to trust in the explanation it is imperative to check that the explainer model is reliable and does not over-simplify the black-box model.
-}
-It is important to keep in mind that the explanation produced by the explainer is not a direct interpretation of the complex model.
+\begin{figure}
+\begin{center}
+\includegraphics[width=3.25in]{figures/lime_concept.png}
+\caption{\kg{XXX This caption is getting too long.
+Will probably need to move some of this to the body of the text.} These figures show the predictions from a hypothetical black-box model plotted against the two features used to fit the black-box model.
+The orange point represent one prediction that is of interest to explain.
+The size of the points represent the proximity to the prediction of interest.
+The black lines represent the explainer model which is a weighted linear regression model in this case fit with the black-box predictions as the response variable and Feature 1 and Feature 2 as the covariates in the model where the proximity values used as the weights in the model.
+The image on the left shows that there is a complex relationship between black-box predictions and Feature 1.
+Here the explainer model is plotted with Feature 2 set to be the observed value of Feature 2 for the prediction of interest.
+The explainer model does a good job of capturing the relationship in the local region around the prediction of interest.
+The image on the right shows that there is no relationship between the black-box predictions and Feature 2 in either the global sense or local region around the prediction of interest.
+Here the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a slope of approximately 0.
+This explainer model would indicate that Feature 1 is driving the prediction made by the black box model for the prediction of interest.}
+\label{fig:limeconcept}
+\end{center}
+\end{figure}
+
+\kg{XXX Rework this paragraph so that it flows better} \hh{At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the black box model, a simpler explainer model is added.
+To be able to trust in the explanation it is imperative to check that the explainer model is reliable and does not over-simplify the black-box model.} The explanation produced by the explainer is not a direct interpretation of the complex model.
 Instead, it is based on a model that is trying to mimic a part of the complex model.
@@
 In Section \ref{methods}, we discuss ways to assess the LIME explainer model and introduces our visualization tools.
-Section \ref{application} demonstrates the use of our diagnostic tools with a logistic regression model fit to the iris data (?
-\hh{urgh.
-but we can decide on that later} ) and a random forest model fit to a forensics bullet matching dataset.
+Section \ref{application} demonstrates the use of our diagnostic tools with a random forest model fit to a forensics bullet matching dataset (\kg{I went ahead and excluded the idea of including the iris data}).
 To conclude, Section \ref{discussion} reviews the importance of assessing the LIME explainer model, discusses how the results from the example provide possible insights into the workings of LIME, and suggests future research directions.
 
-\section{Background} \label{background}
+\section{Background on LIME} \label{background}
 
-\kg{Just putting this here for now - needs lots of work or I may even remove it:} \hh{Accepted best practice for all} predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
+%\kg{Just putting this here for now - needs lots of work or I may even remove it:} \hh{Accepted best practice for all} predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
 The training data is used to fit the complex model, and the testing data is used to assess the model.
@@
 
-\subsection{Model Explainers}
+LIME was developed in 2017 by Ribeiro, Singh, and Guestrin.
+The authors were interested in developing a model explainer method that produced easily understandable explanations for individual predictions made by any predictive model \citep{ribeiro:2016}.
+It was initially implemented in a Python package\footnote{https://github.com/marcotcr/lime} by the original authors and was later adapted to an R package by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}.
 
-\subsection{Overview of LIME}
+The LIME algorithm is presented in the original paper in a general context that accounts for cases such as text classification and feature recognition.
+For this paper, we are only considering the tabular data situation with a binary categorical response variable and continuous feature variables.
+As a result, the following subsections are written in terms of this context.
 
-\hh{It does this -- XX references :) }
+\subsection{Overview}
+
+The
+
+\hh{It does this -- XX references :)}
 It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
@@
 
-(a good place to include an image to help with this explanation)
-
 \subsection{LIME Algorithm}
 
-The LIME algorithm is presented in the original paper in a general context that includes cases for text classification and feature recognition.
-For this paper, we are only considering a situation with a binary categorical response variable and continuous feature variables.
-The procedure below is defined in this context.
 Furthermore, \hh{in this paper we are relying on the LIME implementation in R \citep{lime}.
@@
 \section{Application} \label{application}
-
-\subsection{Iris Data (?)}
 

### 2019-08-09 papers/lime_diagnostics/code/figure-creation.Rmd
added lime concept figures - worked on intro - started lime procedure

@@
 # Conceptual Depiction of LIME
+
+### Good Fit
 
@@
 # Join the two feature plots
-lime_plots <- plot_grid(plot_feature1, plot_feature2)
+lime_plots <- plot_grid(plot_feature1, plot_feature2, ncol = 1)
 
@@
        plot = lime_concept,
-       height = 4, width = 8)
+       height = 6, width = 4)
 ```
+
+### Poor Fit
+
+```{r}
+# Compute the distance between the prediction of interest 
+lime_data$distance_bad <- (1 - gower_dist(x = prediction_of_interest, y = lime_data))^1
+
+# Fit the interpretable explainer model
+lime_explainer_bad <- lm(prediction ~ feature1 + feature2, data = lime_data, weights = distance_bad)
+
+# Predictions versus feature 1
+plot_feature1_bad <- ggplot(lime_data, aes(x = feature1, y = prediction, size = distance_bad)) + 
+  geom_point() + 
+  geom_abline(intercept = coef(lime_explainer_bad)[[1]] + coef(lime_explainer_bad)[[3]]*prediction_of_interest$feature2, 
+              slope = coef(lime_explainer_bad)[[2]], 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             color = "#EFB084",
+             size = 6) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Predictions versus feature 2
+plot_feature2_bad <- ggplot(lime_data, aes(x = feature2, y = prediction, size = distance_bad)) + 
+  geom_point() + 
+  geom_abline(intercept = coef(lime_explainer_bad)[[1]] + coef(lime_explainer_bad)[[2]]*prediction_of_interest$feature1, 
+              slope = coef(lime_explainer_bad)[[3]], 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             color = "#EFB084",
+             size = 6) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Join the two bad feature plots
+lime_plots_bad <- plot_grid(plot_feature1_bad, plot_feature2_bad, ncol = 1)
+
+# Join the title, plots, legend, and caption into one figure
+lime_figure_bad <- plot_grid(lime_plots_bad, lime_legend,
+                         ncol = 1, 
+                         rel_heights = c(0.9, 0.1))
+
+# View the figure
+lime_figure_bad
+
+# Save the plot
+ggsave(filename = "../figures/lime_figure_bad.png",
+       plot = lime_figure_bad,
+       height = 6, width = 4)
+```

### 2019-08-09 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
added lime concept figures - worked on intro - started lime procedure

@@
 \documentclass[AMS,STIX2COL]{WileyNJD-v2}
+
+% Packages
+\usepackage{amsmath,amsfonts}
 \usepackage{natbib}
@@
 
-\usepackage{amsmath,amsfonts}
-
+% Colors for comments by authors
 \usepackage{xcolor}
@@
 
-\articletype{Article Type}%
-
+% Set up for ASA dat science journal
+\articletype{Article Type}
 \received{26 April 2016}
@@
 \accepted{6 June 2016}
-
 \raggedbottom
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE, echo = FALSE}
 
+% R code chunk options
+\SweaveOpts{concordance = TRUE, echo = FALSE}
+
+% Paper header (title and authors)
 \title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
-
 \author[1]{Katherine Goode*}
-
 \author[1,2]{Heike Hofmann}
-
 \authormark{Goode and Hofmann}
-
 \address[1]{\orgdiv{Department of Statistics}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
-
 \address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
-
 \corres{*Corresponding author. \email{kgoode@iastate.edu}}
-
 \presentaddress{This is sample for present address text this is sample for present address text}
 
+% Abstract and keywords
 \abstract[Summary]{This is sample abstract text.}
+\keywords{LIME, black-box models, interpretability, diagnostics}
 
-\keywords{LIME, black box models, interpretability, diagnostics}
-
-\jnlcitation{\cname{%
-\author{Goode K.}, 
-\author{H. Hofmann}, 
-} (\cyear{2019}), 
-\ctitle{title}, \cjournal{journal}, \cvol{volume, number and page}.}
+% Citation information
+\jnlcitation{
+\cname{\author{Goode K.}, \author{H. Hofmann}, } 
+\cyear{2019}, 
+\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}, 
+\cjournal{Stat Anal Data Min: The ASA Data Sci Journal}, 
+\cvol{volume, number and page}.}
 
@@
 
+\kg{*** I added some subsections to the introduction, because it was getting so long.
+What do you think?
+Would it be better to make the introduction shorter and move the details to a separate section?}
+
 In the field of statistics, there are two main uses for models: inference and prediction.
@@
 While these models have been proven to perform well in a wide range of prediction problems, their accuracy comes at the cost of interpretability.
-They are often complex algorithms that are good at identifying patterns in the data but lack a functional form \kg{XXX Is it okay for me to make this statement about the functional form?}, so it not possible to directly interpret them.
-As a result, they produce predictions that lack an explanation, which has earned them the reputation of being ``black box models".
+They are often complex algorithms that are good at identifying patterns in the data but lack a functional form \kg{*** Is it okay for me to make this statement about the functional form?}, so it not possible to directly interpret them.
+As a result, they produce predictions that lack an explanation, which has earned them the reputation of being ``black-box models".
+
+\subsection{The Importance of Explanability}
 
@@
 
+\subsection{Explainer Models}
+
 As a result of the movement to produce explainable predictions, an area of research has emerged focusing on developing ways to explain output from machine learning algorithms.
@@
 Additionally, LIME was designed to work with any model and to produce easily understandable explanations.
-\citep{ribeiro:2016} \hh{XXX a citation might be good here for local and agnostic} \kg{Is it okay to include the same reference to the original LIME paper again?} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black box model" in a local region around a prediction of interest.
+\citep{ribeiro:2016} \hh{XXX a citation might be good here for local and agnostic} \kg{Is it okay to include the same reference to the original LIME paper again?} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black-box model" in a local region around a prediction of interest.
 The interpretation of the simple model is then used to explain the variables that most influenced the prediction made by the complex model.
-Figure \ref{fig:limeconcept} provides a visualization of this conceptual understanding of LIME.
 
-\begin{figure}
+\begin{figure}[t!]
 \begin{center}
 \includegraphics[width=3.25in]{figures/lime_concept.png}
-\caption{\kg{XXX This caption is getting too long.
-Will probably need to move some of this to the body of the text.} These figures show the predictions from a hypothetical black-box model plotted against the two features used to fit the black-box model.
-The orange point represent one prediction that is of interest to explain.
-The size of the points represent the proximity to the prediction of interest.
-The black lines represent the explainer model which is a weighted linear regression model in this case fit with the black-box predictions as the response variable and Feature 1 and Feature 2 as the covariates in the model where the proximity values used as the weights in the model.
-The image on the left shows that there is a complex relationship between black-box predictions and Feature 1.
-Here the explainer model is plotted with Feature 2 set to be the observed value of Feature 2 for the prediction of interest.
-The explainer model does a good job of capturing the relationship in the local region around the prediction of interest.
-The image on the right shows that there is no relationship between the black-box predictions and Feature 2 in either the global sense or local region around the prediction of interest.
-Here the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a slope of approximately 0.
-This explainer model would indicate that Feature 1 is driving the prediction made by the black box model for the prediction of interest.}
+\caption{Conceptual depiction of LIME.
+The black lines represent a weighted linear regression model being used as the explainer model for a hypothetical black-box model fit with two features.
+The explainer model suggests that Feature 1 is driving the prediction made by the black-box model for the case of interest since it has captured the slope in the local region around the prediction of interest.}
 \label{fig:limeconcept}
@@
 
-\kg{XXX Rework this paragraph so that it flows better} \hh{At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the black box model, a simpler explainer model is added.
-To be able to trust in the explanation it is imperative to check that the explainer model is reliable and does not over-simplify the black-box model.} The explanation produced by the explainer is not a direct interpretation of the complex model.
-Instead, it is based on a model that is trying to mimic a part of the complex model.
-Thus, it is necessary to ask the question, ``How reliable is the explanation?".
-One way to answer this question is to understand how well the explainer model approximates the complex model.
+Figure \ref{fig:limeconcept} provides a visualization of this conceptual understanding of LIME.
+These figures show the predictions from a hypothetical black-box model plotted against the two features used to fit the black-box model.
+The orange point represent one prediction that is of interest to explain.
+The size of the points represent the proximity to the prediction of interest measured using the Gower distance metric \kg{(reference and add exponent value?)}.
+The black lines represent the explainer model which is a weighted linear regression model in this case fit with the black-box predictions as the response variable and Feature 1 and Feature 2 as the covariates in the model where the proximity values used as the weights in the model.
+The top image shows that there is a complex relationship between black-box predictions and Feature 1.
+Here the explainer model is plotted with Feature 2 set to be the observed value of Feature 2 for the prediction of interest.
+The explainer model does a good job of capturing the relationship in the local region around the prediction of interest.
+The bottom shows that there is no relationship between the black-box predictions and Feature 2 in either the global sense or local region around the prediction of interest.
+Here the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a slope of approximately 0.
+This explainer model would indicate that Feature 1 is driving the prediction made by the black-box model for the prediction of interest.
+
+\subsection{Motivation for Diagnosing LIME}
+
+At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the black-box model, a simpler explainer model is added.
+To be able to trust in the explanation it is imperative to check that the explainer model is reliable and does not over-simplify the black-box model.
 
@@
 
+Figure \ref{fig:limebadapprox} provides an example where the explainer model is doing a poor job of approximating the complex model.
+The plots were created using the same data as Figure \ref{fig:limeconcept}, but the Gower distance metric was adjusted \kg{(add exponent value)}, so that observations further away from the prediction of interest are given larger weights.
+In this case, the explainer model is doing a poor job of capturing the relationship between the black-box predictions and the feature for both Feature 1 and Feature 2.
+However, the magnitude of the slope of the line in the bottom figure appears to be larger than .
+As a result, this explainer model would return an explanation that Feature 2 is driving the prediction made by the black-box model for the case of interest, which is not an accurate explanation.
+
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=3.25in]{figures/lime_figure_bad.png}
+\caption{A second version of explainer model applied to the data from Figure \ref{fig:limeconcept}.
+The model explainer is refit using an adjusted distance measure.
+It leads to an explainer model that is doing a poor job of approximating the complex model in the local region around the prediction of interest for both features.}
+\label{fig:limebadapprox}
+\end{center}
+\end{figure}
+
+In the scenario depicted in Figure \ref{fig:limeconcept}, the distance metric was adjusted until the explainer models produced a good local approximation of the complex model.
+For Figure \ref{fig:limebadapprox}, the default setting for distance measures was used by the LIME R package.
+Without these images, it would not be obvious that the explainer model used in Figure \ref{fig:limebadapprox} is a poor local approximation.
+
+\subsection{Overview of Paper}
+
 In this paper, we will present some visualizations tools to assess the explanations from LIME.
@@
 
-Section \ref{background} provides some background on explainer models that have been developed, a description of the LIME algorithm, and the current implementations of LIME.
-In Section \ref{methods}, we discuss ways to assess the LIME explainer model and introduces our visualization tools.
-Section \ref{application} demonstrates the use of our diagnostic tools with a random forest model fit to a forensics bullet matching dataset (\kg{I went ahead and excluded the idea of including the iris data}).
+Section \ref{background} provides some background on the LIME algorithm and the current implementations of LIME.
+In Section \ref{methods}, we discuss ways to assess the LIME explainer model and introduce our visualization tools.
+Section \ref{application} demonstrates the use of our diagnostic tools with a random forest model fit to a forensics bullet matching dataset (\kg{***I went ahead and excluded the idea of including the iris data}).
 To conclude, Section \ref{discussion} reviews the importance of assessing the LIME explainer model, discusses how the results from the example provide possible insights into the workings of LIME, and suggests future research directions.
@@
 
-%\kg{Just putting this here for now - needs lots of work or I may even remove it:} \hh{Accepted best practice for all} predictive models is \hh{that during the model fitting process}, the data is divided into training and testing portions.
-The training data is used to fit the complex model, and the testing data is used to assess the model.
-\hh{This is done to prevent overfitting and to get a more accurate assessment of the prediction error of the model.} The complex model is then applied to the features in the testing data, and the resulting predictions are compared to ground truth.
-Of \hh{particular} interest during this assessment are the cases when the model is wrong.
-In the dichotomous response classification case, there are two ways in which the model can be wrong.
-The model can make a type I error in which..., or the model can make a type II error in which...
-
-LIME was developed in 2017 by Ribeiro, Singh, and Guestrin.
+LIME was developed in 2016 by \citet{ribeiro:2016}.
 The authors were interested in developing a model explainer method that produced easily understandable explanations for individual predictions made by any predictive model \citep{ribeiro:2016}.
@@
 As a result, the following subsections are written in terms of this context.
+Furthermore, in this paper we are relying on the LIME implementation in R \citep{lime}.
+This implementation deviates at times from the original implementation by \citet{ribeiro:2016}.
+Whenever the implementations differ, we will highlight these deviations.
 
-\subsection{Overview}
+\subsection{LIME Procedure in the Context of Tabular Data with a Dichotomous Response Variable}
 
-The
+\kg{***Need to clean up the notation.} Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x=\left(\begin{array}{cccc}x_1 & x_2 & \hdots & x_p\end{array}\right)\in\mathbb{R}^p$ be the observation of interest.
+Furthermore, let $\textbf{y}$ be a vector of length $n$ of response values and $y\in\{0, 1\}$ be the observed response value associated with $x$.
+Suppose that $f$ is a classification model where $f:\mathbb{R}^p\rightarrow[0,1]$ that is applied to $\textbf{X}$ and $\textbf{y}$.
+Let the predictions made by $f$ applied to $\textbf{X}$ be denoted as $\hat{\textbf{y}}$.
+It is of interest to explain the prediction made by $f$ when $f$ is applied to $x$.
+Note that $f(x)$ is equal to the probability that $y=1$.
+Given this setup, the LIME procedure is as follows.
 
-\hh{It does this -- XX references :)}
-It does this by using the features from the training data to simulate a new dataset on which the simple model is fit.
+\begin{enumerate}
+\item Generate a new dataset $\textbf{X}^*$ of size $m$ by $p$ using the observed values in $\textbf{X}$.
+There are various ways to simulate the new dataset, and the methods currently used by the LIME R package will be described in more detail in Section \ref{r package}.
+
+\item Apply a transformation $T$ to $\textbf{X}^*$ that results in an interpretable representation.
+The transformation that is applied will depend on the simulation method used.
+Section \ref{r package} will discuss the transformations used by the LIME R package.
+Let $T(\textbf{X}^*)=\textbf{X}'$.
+Furthermore, apply $T$ to $x$ to obtain $T(x)=x'$.
+\noindent\kg{***I need to check if the predictions are made before or after the transformation.}
+
+\item Apply $f$ to $\textbf{X}'$ to obtain a vector of predictions $\hat{\textbf{y}}'$ of length $m$.
+Let the prediction made by $f$ when applied to the transformed case of interested be denoted as $f(x')=y'$.
+
+\item Compute a proximity measure between $x$ and $\textbf{x}'_i$ for each $i\in 1,...,m$ denoted by $\pi_x(\textbf{x}'_i)$.
+
+\item Identify a class of potentially interpretable models such as linear models or decision trees.
+Denote this class of models by $G:\mathbb{R}^p\rightarrow[0,1]$.
+Section \ref{r package} describes the class of interpretable models used by the R package.
+
+\item Apply the class of models $G$ to $\textbf{X}$...
+\end{enumerate}
+
+\kg{Somehow I need to mesh the procedure peformed by the R package and the description of LIME described in the original paper.
+The place where I left off in the procedure above is where the two start to disagree.
+Here are my old ``notes" on the LIME algorithm based on the paper:}
+
+\begin{itemize}
+\item \kg{$G$: class of potentially interpretable models (e.g. linear models, decision trees, rule lists) \hh{in our case, we will use ridge regression}}
+\item \kg{$g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$ \hh{ do we need $\{0,1\}^{p'}$?}}
+\item \kg{$\Omega(g)$: measure of complexity of $g$ (e.g. depth of a tree, number of non-zero coefficients in a linear model fit using LASSO)}
+\item \kg{$\mathcal{L}(f, g, \Pi_x)$: the fidelity functions which is a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$}
+\item \kg{$\xi(x)$: explanation produced by LIME where
+  $$\xi(x)=\underset{g\in G}{\arg\min} \ \mathcal{L}(f, g, \Pi_x)+\Omega(g)$$
+(i.e. want to minimize $\mathcal{L}(f, g, \Pi_x)$ and keep $\Omega(g)$ low enough to be interpretable by humans)}
+\end{itemize}
+
+\hh{XX references :)} Features from the training data are used to simulate a new dataset on which the simple model is fit.
 \hh{more on how the data is simulated - that's an important step.} The complex model is then applied to the simulated dataset to obtain predictions.
@@
 
-\subsection{LIME Algorithm}
-
-Furthermore, \hh{in this paper we are relying on the LIME implementation in R \citep{lime}.
-This implementation deviates at times from the original implementation by \citet{riberio}.
-Whenever the implementations differ, we will} highlight these deviations.
-
-Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations.
-
-\begin{itemize}
-\item $x=\left(\begin{array}{cccc}x_1 & x_2 & \hdots & x_p\end{array}\right)\in\mathbb{R}^p$: original representation of an instance being explained (e.g.
-observations from a set of $p$ continuous features for a specific case in the data) % the LIME paper uses d instead of p for the dimension
-\item $x'\in\mathbb{R}^{p'}$: \hh{where $1 \le p' \le p$}  vector for the interpretable representation of the instance being explained (e.g.
-a vector of indicator variables associated with the features chosen through feature selection indicating whether or not the observed value is in the bin created by LIME for the feature)
-\item $G$: class of potentially interpretable models (e.g. linear models, decision trees, rule lists) \hh{in our case, we will use ridge regression}
-\item $g$: explanation model where $g:\{0,1\}^{p'}\rightarrow\mathbb{R}$ and $g\in G$ \hh{ do we need $\{0,1\}^{p'}$?}
-\item $\Omega(g)$: measure of complexity of $g$ (e.g. depth of a tree, number of non-zero coefficients in a linear model fit using LASSO)
-\item $f$: model that is being explained where $f:\mathbb{R}^p\rightarrow\mathbb{R}$ (In classification $f(x)$ is the probability that $x$ belongs to a certain class)
-\item $\pi_x(z)$: proximity measure between an instance $z$ to $x$ which defines a locality around $x$
-\item $\mathcal{L}(f, g, \Pi_x)$: the fidelity functions which is a measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$
-\item $\xi(x)$: explanation produced by LIME where
-  $$\xi(x)=\underset{g\in G}{\arg\min} \ \mathcal{L}(f, g, \Pi_x)+\Omega(g)$$
-(i.e. want to minimize $\mathcal{L}(f, g, \Pi_x)$ and keep $\Omega(g)$ low enough to be interpretable by humans)
-\end{itemize}
-
-\subsection{Implementation of LIME in R}
-
-(section describing the procedure that is currently used by the LIME R package)
+\subsection{Implementation of LIME in R} \label{r package}
 
@@
 It was decided to only go up to 6 bins since the more bins used the more complex the explanation becomes.
+
+\kg{make sure to include an output figure of a LIME explanation here}
 
@@
 \subsection{Bullet Matching Data}
+
+Of \hh{particular} interest during this assessment are the cases when the model is wrong.
 
@@
 
-%\backmatter
+% Backmatter of Paper
 
 \section*{Acknowledgments}
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
+
+This is acknowledgment text. Provide text here.
 
@@
 
-\noindent
-\textbf{Figure S1.}
-{500{\uns}hPa geopotential anomalies for GC2C calculated against the ERA Interim reanalysis. The period is 1989--2008.}
-
-\noindent
-\textbf{Figure S2.}
-{The SST anomalies for GC2C calculated against the observations (OIsst).}
-
 \appendix
@@
 %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-\bibliography{references}%
+\bibliography{references}
 
@@
 
-\begin{biography}{\includegraphics[width=60pt,height=70pt,draft]{empty}}{\textbf{Author Name.} This is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text.}
+\begin{biography}
+{\includegraphics[width=60pt,height=70pt,draft]{empty}}
+{\textbf{Author Name.} This is sample author biography text this is sample author biography text}
 \end{biography}

### 2019-08-10 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
added in overview of last steps (may change)
commented out in progress writing

@@
 \usepackage{natbib}
+\usepackage{xcolor}
 %\bibliographystyle{asa}
 
-% Colors for comments by authors
-\usepackage{xcolor}
+% Commands
 \definecolor{purple}{rgb}{0.5, 0.0, 0.5}
@@
 \newcommand{\kg}[1]{\textcolor{purple}{#1}}
+\newcommand{\comment}[1]{}
 
-% Set up for ASA dat science journal
+% Set up for ASA data science journal
 \articletype{Article Type}
@@
 
-\item Apply the class of models $G$ to $\textbf{X}$...
+\item Perform feature selection...
+
+\item Fit explainer model
+
+\item Interpret
+
 \end{enumerate}
@@
 
-\hh{XX references :)} Features from the training data are used to simulate a new dataset on which the simple model is fit.
+\hh{XX references :)} \comment{Features from the training data are used to simulate a new dataset on which the simple model is fit.
 \hh{more on how the data is simulated - that's an important step.} The complex model is then applied to the simulated dataset to obtain predictions.
@@
 \hh{more on the weights} Feature selection is performed to identify the most important variables in the local region.
-A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.
+A final ridge regression model is fit with the selected features, and the coefficients of the model are used to interpret the behavior of the complex model.}
 
@@
 
-The LIME R package allows for the following four methods to sample the perturbations based on the distributions of the features from the training data.
+\comment{The LIME R package allows for the following four methods to sample the perturbations based on the distributions of the features from the training data.
 
@@
 Within the bin based sampling methods, the algorithm was applied for 2 to 6 bins.
-It was decided to only go up to 6 bins since the more bins used the more complex the explanation becomes.
+It was decided to only go up to 6 bins since the more bins used the more complex the explanation becomes.}
 
@@
 
-Ways to understand if the LIME explainer is doing a good job:
+\comment{Ways to understand if the LIME explainer is doing a good job:
 
@@
 \item compare results from different input options
-\end{itemize}
+\end{itemize}}
 
@@
 
-Of \hh{particular} interest during this assessment are the cases when the model is wrong.
+\comment{Of \hh{particular} interest during this assessment are the cases when the model is wrong.
 
@@
 It would be preferable that the top feature chosen was more consistent across the number of bins and more variable across the cases.
-This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.
+This would suggest that the top feature chosen is dependent on the feature values associated with a particular case and not just on which feature is the best explainer when $b$ number of bins are used.}
 

### 2019-08-10 README.Rmd
added thought to readme

@@
 
+- I am thinking about moving the paper to a new repository and then renaming this repository as LIME-research-journals and using it more as a place to try stuff out
 - Can I remove some of the sources from the references file that I am not going to use?

### 2019-08-13 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
worked on procedure in paper

@@
 
-# The Data
+# LIME Procedure
 
-The cleaning training and testing datasets are loaded in below.
+### Original Paper
 
-```{r}
-# Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
-```
+*Note: Most of the text in this section is copied from the original paper.*
 
-# Draft of LIME Procedure
+| Notation | Original Paper Definition | My Interpretation (in terms of a data table) |
+| -------- | ------------------------- | ------------------------- |
+| $x\in\mathbb{R}^d$ | Original representation of an instance being explained | Vector of observed features for one observation e.g. $(x_1, x_2,...,x_d)$ where $\textbf{X}$ is an $n$ by $d$ matrix | 
+| $f:\mathbb{R}^d→\mathbb{R}$ | The model being explained...In classification, $f(x)$ is the probability (or a binary indicator) that $x$ belongs to a certain class.
+| This is a random forest in our case.
+|
+| $x'\in\{0,1\}^{d'}$ | A binary vector for interpretable representation (where interpretable explanations are defined as "use a representation that is understandable by humans") | Varies based on the simulation method used - note that $1\le d' \le d$ since it is possible that feature selection may be performed to choose a smaller set of variables than originally in $x$ (One example: vector of indicator variables that indicate whether the observed value falls in the same bin as the instance being explained e.g.
+$x'_i = I[x_i\in \mbox{same variable } i \mbox{ bin as the instance being explained}]$) | In our example, this is the random forest model.
+|
+|$G$ | A class of potentially interpretable models, such as linear models, decision trees, or falling rule lists |  <span style="color:blue"> I'm not sure what is considered $G$ in the R package - the fitting of the final ridge regression model or the ridge regression model used for feature selection?
+</span>|
+| $g$ | An explanation as a model...can be readily presented to the user with visual or textual artifacts...The domain of $g$ is $\{0,1\}^{d′}$, i.e.
+$g$ acts over absence/presence of the interpretable components | This could be a ridge regression model with the form $f(x) \sim x'_1 + x'_2 + \cdots + x'_{d'}$ |
+| $\Omega(g)$ | A measure of complexity of the explanation $g\in G$.
+For example, for decision trees $\Omega(g)$ may be the depth of the tree, while for linear models, $\Omega(g)$ may be the number of non-zero weights.
+| Seemingly, this is based on how the weights are assigned to the data points.
+|
+| $\pi_x(z)$ | A proximity measure between an instance $z$ to $x$, so as to define locality around $x$. | This could be the Gower distance. |
+| $\mathcal{L}(f,g,\pi_x)$ | A measure of how unfaithful $g$ is in approximating $f$ in the locality defined by $\pi_x$.
+| <span style="color:blue"> Does the LIME R package ever consider this?
+</span> |
+
+**Goal of LIME**: In order to ensure both interpretability and local fidelity, we must minimize $\mathcal{L}(f,g,\pi_x)$ while having $\Omega(g)$ below enough to be interpretable by humans.
+The explanation produced by LIME is obtained by the following:
+  $$\xi(x) = \underset{g∈G}{\arg\min} \ \mathcal{L}(f,g,\pi_x) + \Omega(g)$$
+This  formulation  can  be  used  with  different  explanation families $G$, fidelity functions $\mathcal{L}$, and complexity measures $\Omega$.
+Here we focus on sparse linear models as explanations, and on performing the search using perturbations.
+
+**Procedure**: We want to minimize the locality-aware loss $\mathcal{L}(f,g, \pi_x)$ without making any assumptions about $f$, since we want the explainer to be model-agnostic.
+
+1. In order to learn the local behavior of $f$ as the interpretable inputs vary, we approximate $\mathcal{L}(f,g,\pi_x)$ by drawing samples, weighted by $\pi_x$. 
+2. We sample instances around $x'$ by drawing nonzero elements of $x'$ uniformly at random (where the number of such draws is also uniformly sampled).
+3.
+Given a perturbed sample $z'\in\{0,1\}^{d′}$ (which contains a fraction of the nonzero elements of $x'$), we recover the sample in the original representation $z\in\mathbb{R}^d$ and obtain $f(z)$, which is used as a label for the explanation model.
+4. Given this data set $\mathcal{Z}$ of perturbed samples with the associated labels, we optimize $\mathcal{L}(f,g,\pi_x) + \Omega(g)$ to get an explanation $\xi(x)$.
+
+It is worth noting that our method is fairly robust to sampling noise since the samples are weighted by $\pi_x$.
+
+### R Package (Draft)
 
@@
 
+### The Data
+
+The cleaning training and testing datasets are loaded in below.
+
+```{r}
+# Load in the training data (Hamby Data 173 and 252)
+hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
+```
+
 ### Subsampled Bins

### 2019-08-13 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
worked on procedure in paper

@@
 
-\kg{***Need to clean up the notation.} Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x=\left(\begin{array}{cccc}x_1 & x_2 & \hdots & x_p\end{array}\right)\in\mathbb{R}^p$ be the observation of interest.
+\kg{***Need to clean up the notation.
+Should I use the same notation as the original paper?} Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x=\left(\begin{array}{cccc}x_1 & x_2 & \hdots & x_p\end{array}\right)\in\mathbb{R}^p$ be the observation of interest.
 Furthermore, let $\textbf{y}$ be a vector of length $n$ of response values and $y\in\{0, 1\}$ be the observed response value associated with $x$.
@@
 
+\item Apply $f$ to $\textbf{X}^*$ to obtain a vector of predictions $\hat{\textbf{y}}'$ of length $m$.
+Let the prediction made by $f$ when applied to the transformed case of interested be denoted as $f(x')=\hat{y}'$.
+
 \item Apply a transformation $T$ to $\textbf{X}^*$ that results in an interpretable representation.
@@
 Furthermore, apply $T$ to $x$ to obtain $T(x)=x'$.
-\noindent\kg{***I need to check if the predictions are made before or after the transformation.}
-
-\item Apply $f$ to $\textbf{X}'$ to obtain a vector of predictions $\hat{\textbf{y}}'$ of length $m$.
-Let the prediction made by $f$ when applied to the transformed case of interested be denoted as $f(x')=y'$.
 

### 2019-08-13 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
couple of edits

@@
 % R code chunk options
-\SweaveOpts{concordance = TRUE, echo = FALSE}
+%\SweaveOpts{concordance = TRUE, echo = FALSE}
 
@@
 While these models have been proven to perform well in a wide range of prediction problems, their accuracy comes at the cost of interpretability.
-They are often complex algorithms that are good at identifying patterns in the data but lack a functional form \kg{*** Is it okay for me to make this statement about the functional form?}, so it not possible to directly interpret them.
-As a result, they produce predictions that lack an explanation, which has earned them the reputation of being ``black-box models".
+They are often complex algorithms that are good at identifying patterns in the data but \hh{often} lack a functional form, \hh{making it impossible} to directly interpret them.
+As a result, they \hh{HH: who is they - make that explicit.
+always.} produce predictions that lack an explanation, which has earned them the reputation of being ``black-box models".
+\hh{HH: I would make the claim that the need for explanations goes even deeper.
+Even if a functional form exists, such as in a linear model, there are situations where the model gets complicated enough to be not or not easily interpretable.
+Only very good natured three-way interactions in a logistic regression are interpretable.
+For the other ones more work is needed than most audiences would be capable of.
+Explainer models can be used in those situations as well.}
 
@@
 Additionally, LIME was designed to work with any model and to produce easily understandable explanations.
-\citep{ribeiro:2016} \hh{XXX a citation might be good here for local and agnostic} \kg{Is it okay to include the same reference to the original LIME paper again?} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black-box model" in a local region around a prediction of interest.
+\citep{ribeiro:2016} \hh{XXX a citation might be good here for local and agnostic} \kg{Is it okay to include the same reference to the original LIME paper again?} \hh{sure} Conceptually, LIME fits a simple interpretable model, referred to as the explainer, that is meant to capture the behavior of the complex ``black-box model" in a local region around a prediction of interest.
 The interpretation of the simple model is then used to explain the variables that most influenced the prediction made by the complex model.
@@
 
+\hh{I think it would make sense to combine figures 1 and 2 into one big, two-column spread figure with the two explainer models shown side by side. }
+\hh{Include a legend in the plot for the size of points.
+It would also be nice to change the points from black to something a bit lighter - maybe grey30?
+- and add a bit of alpha blending to them.
+That will allow you to still see the overall structure, but show the underlying 2d density somewhat.
+It also increases the contrast to the black lines of the explainer model.
+}
 Figure \ref{fig:limeconcept} provides a visualization of this conceptual understanding of LIME.
 These figures show the predictions from a hypothetical black-box model plotted against the two features used to fit the black-box model.
-The orange point represent one prediction that is of interest to explain.
-The size of the points represent the proximity to the prediction of interest measured using the Gower distance metric \kg{(reference and add exponent value?)}.
-The black lines represent the explainer model which is a weighted linear regression model in this case fit with the black-box predictions as the response variable and Feature 1 and Feature 2 as the covariates in the model where the proximity values used as the weights in the model.
+The orange point \hh{It's better not to refer to colors in the text.
+Why don't you double encode with shape and refer to the shape of that special point.
+We do not know how color is going to be publicized and it's painful to find all the textual references.} represent one prediction that is of interest to explain.
+The size of the points represent the proximity to the prediction of interest measured using the Gower distance metric \kg{(reference and add exponent value?)} \hh{yes}.
+The black lines represent the  explainer model which in this case  is a weighted linear regression model fit with the black-box predictions as the response variable and Features 1 and 2 as the covariates in the model with proximity values used as  weights in the model.
 The top image shows that there is a complex relationship between black-box predictions and Feature 1.
 Here the explainer model is plotted with Feature 2 set to be the observed value of Feature 2 for the prediction of interest.
-The explainer model does a good job of capturing the relationship in the local region around the prediction of interest.
-The bottom shows that there is no relationship between the black-box predictions and Feature 2 in either the global sense or local region around the prediction of interest.
-Here the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a slope of approximately 0.
-This explainer model would indicate that Feature 1 is driving the prediction made by the black-box model for the prediction of interest.
+The explainer model captures the relationship in the local region around the prediction of interest well.
+The bottom figure shows that there is no relationship between the black-box predictions and Feature 2 in either the global sense or in a local region around the prediction of interest.
+Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a slope of approximately 0.
+Taken together, this explainer model would indicate that Feature 1 is driving the prediction made by the black-box model for the prediction of interest.
 
@@
 
-The current implementations of LIME use a linear regression model as the explainer model (references to R and Python packages).
+The current implementations of LIME use a linear regression model as the explainer model \citep{lime} (references to R and Python packages) \hh{for which models?
+LIME uses neural networks for image analyses}.
 These implementations are relying on the assumption that the relationship between the complex model predictions and the features is linear in a local region.
-It is important to assess this assumption in the local region of interest in order to trust the explanations produced by LIME.
+\hh{HH: be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion).
+The question is how big the error is.
+} It is important to assess this assumption in the local region of interest in order to trust the explanations produced by LIME.
+\hh{The next sentence is muddying the waters - by being able to doagnose explainer models we will be able to assess the different settings offered in the implementations.
+Let's bring those up later.
+}
 Additionally, the implementations offer various input settings, but little work has been done to provide advice on how to specify the settings in practice (look more into this).
@@
 In the scenario depicted in Figure \ref{fig:limeconcept}, the distance metric was adjusted until the explainer models produced a good local approximation of the complex model.
-For Figure \ref{fig:limebadapprox}, the default setting for distance measures was used by the LIME R package.
+\hh{HH: excellent!
+What are the respective R squares?} For Figure \ref{fig:limebadapprox}, the default setting for distance measures was used by the LIME R package.
 Without these images, it would not be obvious that the explainer model used in Figure \ref{fig:limebadapprox} is a poor local approximation.

### 2019-08-13 README.Rmd
worked on procedure in paper
work from Tuesday before meeting

--- 2019-08-06 README.Rmd
@@
 
+- Paper:
     - Can I remove some of the sources from the references file that I am not going to use?
+    - Can we talk about how best to present the LIME algorithm and some of the terms from the original paper that do not make sense in the context of the R package?
+    - Subsections in the introduction?
+    - See other comments in the paper
+    - I am thinking about moving the paper to a new repository and then renaming this repository as LIME-research-journals and using it more as a place to try stuff out
+- Graphics Group:
+    - schedule
+    - current list of volunteers
+- Sandia Internship:
+    - email from Danny
 

### 2019-08-13 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
work from Tuesday before meeting

@@
 ---
-title: "04-lime_algorithm_and_proposed_methods"
+title: "Lime Algorithm and Proposed Methods"
 author: "Katherine Goode"
@@
 
-This journal contains a draft of the LIME algorithm and ideas for different binning methods that may be better than the ones currently implemented in the LIME package.
+This journal contains a description of the LIME procedure from the original paper, my write-up of the LIME algorithm used in the R package, and ideas for different binning methods that may be better than the ones currently implemented in the R package.
 
 ```{r}
-# Load libraries
-
 # Source functions
@@
 
-# LIME Procedure
+# Original Paper
 
-### Original Paper
+Here, I have copied in the section of the original paper that describes LIME and put it in a more orgainzed format.
+I have also added in some comments explaining my interpretation of the text and questions where I am not sure what is meant by the text.
+
+### Notation
 
@@
 </span> |
+| $z'\in\{0,1\}^{d′}$ | A perturbed sample...(which contains a fraction of the nonzero elements of $x′$) | <span style="color:blue"> It appears that they are creating the perturbations in a different way than the R package.
+</span> |
+| $z\in\mathbb{R}^d$ | The sample in the original representation | <span style="color:blue"> Again, this seems to be different than the R package. </span> |
+| $f(z)$ | Used as a label for the explanation model | This is the application of the complex model to the perturbed sample. |
+| $\mathcal{Z}$ | Data set...of perturbed samples with the associated labels | This is the full simulated dataset of perturbations and complex model predictions. |
+| $\xi(x)$ | The explanation produced by LIME...$\underset{g∈G}{\arg\min} \ \mathcal{L}(f,g,\pi_x) + \Omega(g)$ | The output from the explanation model which is found through an optimiation process. |
 
-**Goal of LIME**: In order to ensure both interpretability and local fidelity, we must minimize $\mathcal{L}(f,g,\pi_x)$ while having $\Omega(g)$ below enough to be interpretable by humans.
+### Goal of LIME
+
+In order to ensure both interpretability and local fidelity, we must minimize $\mathcal{L}(f,g,\pi_x)$ while having $\Omega(g)$ below enough to be interpretable by humans.
 The explanation produced by LIME is obtained by the following:
@@
 
-**Procedure**: We want to minimize the locality-aware loss $\mathcal{L}(f,g, \pi_x)$ without making any assumptions about $f$, since we want the explainer to be model-agnostic.
+### Procedure
 
-1. In order to learn the local behavior of $f$ as the interpretable inputs vary, we approximate $\mathcal{L}(f,g,\pi_x)$ by drawing samples, weighted by $\pi_x$. 
-2. We sample instances around $x'$ by drawing nonzero elements of $x'$ uniformly at random (where the number of such draws is also uniformly sampled).
-3.
-Given a perturbed sample $z'\in\{0,1\}^{d′}$ (which contains a fraction of the nonzero elements of $x'$), we recover the sample in the original representation $z\in\mathbb{R}^d$ and obtain $f(z)$, which is used as a label for the explanation model.
-4. Given this data set $\mathcal{Z}$ of perturbed samples with the associated labels, we optimize $\mathcal{L}(f,g,\pi_x) + \Omega(g)$ to get an explanation $\xi(x)$.
+We want to minimize the locality-aware loss $\mathcal{L}(f,g, \pi_x)$ without making any assumptions about $f$, since we want the explainer to be model-agnostic.
+
+| Step Number | Paper Description | My Interpretation |
+| :----: | ----------------- | ----------------- |
+| 1 | In order to learn the local behavior of $f$ as the interpretable inputs vary, we approximate $\mathcal{L}(f,g,\pi_x)$ by drawing samples, weighted by $\pi_x$.
+| <span style="color:blue"> I don't understand how drawing these samples approximates $\mathcal{L}(f,g,\pi_x)$ </span> |
+| 2 | We sample instances around $x'$ by drawing nonzero elements of $x'$ uniformly at random (where the number of such draws is also uniformly sampled).| <span style="color:blue"> What is meant by drawing elements of $x'$?
+Is this different than what the R package is doing?
+</span> I'm wondering if the idea is that $x'=(x'_1, x'_2,...,x'_{d'})=(1, 1, ...., 1)$, and then a sample is taken such as $z'=(0, x'_2, 0, 0, x'_5,...,x'_{d'}) =(0, 1, 0, 0, 1, ..., 1)$.
+<span style="color:blue"> However, this doesn't really make sense in terms of why $d'$ is different from $d$ </span> |
+| 3 | Given a perturbed sample $z'\in\{0,1\}^{d′}$ (which contains a fraction of the nonzero elements of $x'$), we recover the sample in the original representation $z\in\mathbb{R}^d$ and obtain $f(z)$, which is used as a label for the explanation model.
+| <span style="color:blue"> How is the original sample recovered?
+</span> Maybe based on my example in the last step $z=(0, x_2, 0, 0, x_5, ..., x_d)$|
+| 4 | Given this data set $\mathcal{Z}$ of perturbed samples with the associated labels, we optimize $\mathcal{L}(f,g,\pi_x) + \Omega(g)$ to get an explanation $\xi(x)$.
+| <span style="color:blue"> Where is this done in the R package?
+</span> |
 
 It is worth noting that our method is fairly robust to sampling noise since the samples are weighted by $\pi_x$.
+<span style="color:blue"> Okay - but this will really depend on how $\pi_x$ is chosen </span>
 
-### R Package (Draft)
+...let $G$ be the class of linear models, such that $g(z′)=w_g\cdot z′$.
+<span style="color:blue"> (What is $w_g$?
+Is this suppose to be a linear model where $w_g$ are the coefficients?) </span> We use the locally weighted square loss as $\mathcal{L}$...where we let
+  $$\pi_x(z)=exp(−D(x,z)^2/\sigma^2)$$ 
+be an exponential kernel defined on some distance function $D$ (e.g. cosine distance for text, $L2$ distancef or images) with width $\sigma$.
+  $$\mathcal{L}(f,g,\pi_x)=\sum_{z, z'\in\mathcal{Z}}\pi_x(z)\left(f(z)-g(z')\right)^2$$
+
+### Comment on Faithfulness
+
+...our choice of $G$ (sparse linear models) means that if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation.
+However, we can estimate the faithfulness of the explanation on $\mathcal{Z}$, and present this information to the user.
+This estimate of faithfulness can also be used for selecting an appropriate family of explanations from a set of multiple interpretable model classes, thus adapting to the given dataset and the classifier.
+We leave such exploration for future work, as linear explanations work quite well for multiple black-box models in our experiments.
+
+# R Package
+
+### Procedure (Draft)
 
@@
 
-# Inputs for LIME Functions
+### Function Inputs
 
@@
 
-### `lime` function
+##### `lime` function
 
@@
 
-### `explain` function
+##### `explain` function
 

### 2019-08-13 papers/lime_diagnostics/code/figure-creation.Rmd
work from Tuesday before meeting

@@
 ```
+
+# Second Attempt
+
+```{r}
+# Generate data
+set.seed(20190624)
+all_observations <- data.frame(case = factor("Other", levels = c("Other", "Prediction of Interest")),
+                        feature1 = sort(runif(250, 0, 1)),
+                        feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+  mutate(prediction = if_else(feature1 >= 0 & feature1 < 0.1, (0.3 * feature1) + rnorm(n(), 0, 0.01), 
+                      if_else(feature1 >= 0.1 & feature1 < 0.3, rbeta(n(), 1, 0.5), 
+                      if_else(feature1 >= 0.3 & feature1 < 0.5, sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                      if_else(feature1 >= 0.5 & feature1 < 0.8, -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                      if_else(feature1 >= 0.8 & feature1 < 0.9, 0.5 + runif(n(), -0.5, 0.5), 
+                              0.5 + rnorm(n(), 0, 0.3)))))))
+```
+
+```{r}
+# Specify a prediction of interest
+prediction_of_interest <- data.frame(case = factor("Prediction of Interest", 
+                                                   levels = c("Other", "Prediction of Interest")),
+                                     feature1 = 0.07,
+                                     feature2 = 200,
+                                     prediction = 0.05)
+```
+
+```{r}
+lime_data <- bind_rows(all_observations, prediction_of_interest)
+```
+
+```{r}
+# Compute the distance between the prediction of interest 
+lime_data$distance <- (1 - gower_dist(x = prediction_of_interest, y = lime_data))^20
+lime_data$distance_bad <- (1 - gower_dist(x = prediction_of_interest, y = lime_data))^1
+
+# Fit the interpretable explainer models
+lime_explainer <- lm(prediction ~ feature1 + feature2, data = lime_data, weights = distance)
+lime_explainer_bad <- lm(prediction ~ feature1 + feature2, data = lime_data, weights = distance_bad)
+```
+
+```{r}
+lime_data_gathered <- lime_data %>%
+  gather(key = feature, value = value, 2:3) %>%
+  gather(key = distance_case, value = distance_value, 3:4)
+```
+
+```{r}
+ggplot(data = lime_data_gathered, 
+       mapping = aes(x = value, 
+                     y = prediction, 
+                     size = distance_value,
+                     shape = case)) + 
+  geom_point(alpha = 0.5) + 
+  geom_abline(data = lime_data_gathered %>% 
+                filter(feature == "feature1", distance_case == "distance"),
+              intercept = coef(lime_explainer)[[1]] +
+                coef(lime_explainer)[[3]]*prediction_of_interest$feature2, 
+              slope = coef(lime_explainer)[[2]], 
+              size = 1) +
+  #stat_smooth(data = lime_data_gathered %>% filter(feature == "feature2")) +
+  facet_grid(distance_case ~ feature, scales = "free") + 
+  theme_bw()
+```

### 2019-08-13 papers/lime_diagnostics/visual-diagnostics-of-a-model-explainer.Rnw
work from Tuesday before meeting

@@
 While these models have been proven to perform well in a wide range of prediction problems, their accuracy comes at the cost of interpretability.
-They are often complex algorithms that are good at identifying patterns in the data but \hh{often} lack a functional form, \hh{making it impossible} to directly interpret them.
-As a result, they \hh{HH: who is they - make that explicit.
-always.} produce predictions that lack an explanation, which has earned them the reputation of being ``black-box models".
+Machine learning models are generally complex algorithms that are good at identifying patterns in the data but \hh{often} lack a functional form, which makes it impossible to directly interpret them \kg{***Should I change this them?}.
+As a result, machine learning learning models produce predictions that lack an explanation, which has earned them \kg{***What about this one?} the reputation of being ``black-box models".
 \hh{HH: I would make the claim that the need for explanations goes even deeper.
@@
 
+\kg{While reading through the original paper again, I rediscovered this quote.
+This may be something to reference or quote in this section: ``...our choice of $G$ (sparse linear models) means that if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation.
+However, we can estimate the faithfulness of the explanation on $\mathcal{Z}$, and present this information to the user.
+This estimate of faithfulness can also be used for selecting an appropriate family of explanations from a set of multiple interpretable model classes, thus adapting to the given dataset and the classifier.
+We leave such exploration for future work, as linear explanations work quite well for multiple black-box models in our experiments."}
+
 At a conceptual level, explainer models add another level of complexity to predictive models: in trying to explain the black-box model, a simpler explainer model is added.
@@
 The current implementations of LIME use a linear regression model as the explainer model \citep{lime} (references to R and Python packages) \hh{for which models?
-LIME uses neural networks for image analyses}.
+LIME uses neural networks for image analyses} \kg{I think that it is actualy using ridge regression for all cases - even images}.
 These implementations are relying on the assumption that the relationship between the complex model predictions and the features is linear in a local region.

### 2019-08-13 code/app.R
moved app to the code folder

@@ -14,10 +14,10 @@ library(gridExtra)
 ## ------------------------------------------------------------------------------------
 
 # Input data
-hamby224_test <- read.csv("../data/hamby224_test.csv")
-hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
-hamby224_bins <- readRDS("../data/hamby224_bins.rds")
-hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
+hamby224_test <- read.csv("../../data/hamby224_test.csv")
+hamby224_test_explain <- readRDS("../../data/hamby224_test_explain.rds")
+hamby224_bins <- readRDS("../../data/hamby224_bins.rds")
+hamby224_lime_inputs <- readRDS("../../data/hamby224_lime_inputs.rds")
 
 ## ------------------------------------------------------------------------------------
 ## Functions

### 2019-08-14 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
updated journals after data folder movement

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
+knitr::opts_chunk$set(echo = TRUE, 
+                      message = FALSE,
+                      warning = FALSE, 
+                      eval = TRUE, 
                       cache = TRUE)
@@
 # Load in the Hamby 173 and 252 dataset
-hamby173and252_raw <- read.csv("../../data/raw/features-hamby173and252.csv") %>%
+hamby173and252_raw <- read.csv("../../../data/raw/features-hamby173and252.csv") %>%
   filter(study1 != "Cary", study2 != "Cary") %>%
@@
 
-```{r}
+```{r eval = FALSE}
 # Save the datasets and response variables as .csv files
@@
 # Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("../../data/raw/h224-set1-features.rds")
-hamby224_set11 <- readRDS("../../data/raw/h224-set11-features.rds")
+hamby224_set1 <- readRDS("../../../data/raw/h224-set1-features.rds")
+hamby224_set11 <- readRDS("../../../data/raw/h224-set11-features.rds")
 ```
@@
 
-```{r}
+```{r eval = FALSE}
 # Save the test data as a .csv file

### 2019-08-14 README.Rmd
updated readme

--- 2019-08-06 README.Rmd
@@
 ## Talking points
-
-- Can I remove some of the sources from the references file that I am not going to use?
 
@@
 
-**app**
-
-This folder contains files for Shiny app for visualizing the LIME explanations associated with the bullet land comparisons:
-
-- `app.R`: code for the Shiny app
-
 **code**
@@
 
+- `app.R`: code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
 - `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well
 
-**data**
+**figures**
 
-This folder is a location for storing raw and created data for the project:
+This folder contains static images:
 
-- `hamby173and252_train.csv`: training data that I cleaned (it should match the data used to fit `rtrees`)
-- `hamby224_bin_boundaries.rds`: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
-- `hamby224_bins.rds`: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
-- `hamby224_explain`: the output from the `explain` function in lime from the single implementation with all of the different input options
-- `hamby224_lime`: the output from the `lime` function in lime from the single implementation with all of the different input options
-- `hamby224_lime_comparisons`: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
-- `hamby224_lime_inputs`: LIME input settings used for the single implementation of LIME
-- `hamby224_sensitivity_inputs`: LIME input settings used for the sensativity analysis of LIME
-- `hamby224_sensitivity_joined.csv`: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
-- `hamby224_sensitivity_outputs.rds`: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
-- `hamby223_test.csv`: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
-- `hamby224_test_explain.rds`: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
-- raw: original data given to me by Heike
-    - `features-hamby173and252.csv`
-    - `h224-set1-features.rds`
-    - `h224-set11-features.rds`
+- `lime.png`: fun picture of a lime to use in the readme
 
@@
 - `10-other_explainers`: trying out other model explainers
+
+**main**
+
+The documents contained in the top folder are as follows:
+
+- `.gitattributes`: attributes relating to git
+- `.gitignore`: files to ignore
 - `notes from Heike.pdf`: scans of notes written by Heike for this project
-
-**papers**
-
-This folder contains the statistics and firearm examiners papers:
-
-- `bullet_application`: explains how LIME can be used to understand the random forest model fit to bullet matching data
-- `lime_diagnostics`: explains the need to assess LIME and presents some visual diagnostic tools
+- `README`: document containing to do list and contents of this repository

### 2019-08-14 README.Rmd
updated to do list after meeting yesterday

@@
 
+- Graphics Group
+    - email list (should I be added as an admin?)
+
 ## To Do List
@@
 
-- work on first draft of paper
+- keep the LIME procedure at a higher level in the paper
+- check for ridge regression model in Python code
+- compute generalized $R^2$ for my images
+- change to computing the $\mathcal{L}$ metric from the paper
+- check if Python package outputs the locality metric
+- add figure descriptions in both caption and text
+- move sentence on various settings to back of paper
+- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
+- get rid of current implementation in text (change to original paper and mention doing this for model agnostic reasons)
+- add an assert_that statement in the code to check if the LIME package is changing
+- first draft of paper due two weeks into the semester (September 10)
 - read through papers giving an overview of the current explanation methods

### 2019-08-14 README.Rmd
made small changes to the paper

--- 2019-08-14 README.Rmd
@@
 
+- Graphics Group
+    - email list (should I be added as an admin?)
+
 ## To Do List
+
+*First draft of paper due two weeks into the semester (Tuesday, September 10)*
 
@@
 
-- work on first draft of paper
+- keep the LIME procedure at a higher level in the paper
+- check for ridge regression model in Python code
+- compute generalized $R^2$ for my images
+- change to computing the $\mathcal{L}$ metric from the paper
+- check if Python package outputs the locality metric
+- add figure descriptions in both caption and text
+- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
+- add an assert_that statement in the code to check if the LIME package is changing
 - read through papers giving an overview of the current explanation methods

### 2019-08-20 README.Rmd
updates since last meeting

--- 2019-08-14 README.Rmd
@@
 
+- Paper
+    - I found ridge regression models in Python code (see journal 04)
+    - Show the plots using the ridge regression in journal 09
+    - What should I do about computing the generalized R2 value?
+    - Show this paper: https://arxiv.org/pdf/1806.07498.pdf
+    - Can you help to show me your vision with the minipage format?
+    - I could not find a locality metric output from Python.
+There was a section in their vignettes that seemed to be referring to some sort of assessment about the models, but I'm not sure what was happening.
+https://marcotcr.github.io/lime/tutorials/Tutorial%20-%20continuous%20and%20categorical%20features.html
+- Graphics Group
+    - email list (should I be added as an admin?)
+    - send out another email and plan for first week?
+    - updates on schedule since last meeting
+
 ## To Do List
+
+*First draft of paper due two weeks into the semester (Tuesday, September 10)*
 
@@
 
-- work on first draft of paper
+- keep the LIME procedure at a higher level in the paper
+- change to computing the $\mathcal{L}$ metric from the paper
+- add figure descriptions in both caption and text
+- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
+- add an assert_that statement in the code to check if the LIME package is changing
 - read through papers giving an overview of the current explanation methods
@@
 
-- LIME diganostics  
+- LIME diagnostics  
     - turn repetitive code into functions
@@
     - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
-    - he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
+    - he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
     - compare the simple models based on different number of bins using an F-test
@@
     - look at Hadley's 'removing the blindfold' for ideas
-    - read book Dr. Dixon lent me on sensativity analyses
+    - read book Dr. Dixon lent me on sensitivity analyses
 - possible improvements to LIME
@@
 
-Descriptions of the materials in this respository are listed below.
+Descriptions of the materials in this repository are listed below.
 
@@
 - `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
-- `05-applying_lime_to_rtrees`: application of lime and sensativity analysis for many different input options
+- `05-applying_lime_to_rtrees`: application of lime and sensitivity analysis for many different input options
 - `06-assessing_lime_explanations`: assessment of the lime explanations

### 2019-08-20 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
updates since last meeting

@@
 
+# Python Package
+
+I have not spent a lot of time going through the Python package code, but I wanted to check to see if it uses a ridge regression for the feature selection and the explainer model.
+This [article](https://towardsdatascience.com/how-to-perform-lasso-and-ridge-regression-in-python-3b3b75541ad8) describes that ridge regression can be fit in Python using the sklearn "package".
+These images below of the code from the Python lime [GitHub repository](https://github.com/marcotcr/lime/blob/master/lime/lime_base.py) seem to imply that it is using ridge regression for both of these steps.
+
+![](../../figures/python-ridge1.png)
+
+![](../../figures/python-ridge2.png)
+
+![](../../figures/python-ridge3.png)
+
 # Proposed Bin Creation Methods
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
 ```

### 2019-08-20 journals/09-understanding_lime/09-understanding_lime.Rmd
updates since last meeting

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
-                      cache = TRUE)
+knitr::opts_chunk$set(echo = TRUE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      eval = TRUE)
 ```
@@
 
+This journal is a place where I create visuals to try to understand how lime works.
+
 ```{r}
+library(cowplot)
 library(furrr)
 library(future)
+library(glmnet)
+library(gower)
 library(lime)
@@
 
-# The Data
+# Generated Data
+
+The images in this section were created using simulated data that I knew had a local trend around the point of interest.
+I consider both a linear regression and a ridge regression as the explainer model.
+
+### Data and Model
+
+This code generates the data and predictions from a hypothetical complex model.
+
+```{r}
+# Generate features and predictions from a hypothetical complex model
+set.seed(20190624)
+lime_data <- data.frame(feature1 = sort(runif(250, 0, 1)),
+                        feature2 = sample(x = 1:250, 
+                                          size = 250, 
+                                          replace = FALSE)) %>%
+  mutate(prediction = if_else(feature1 >= 0 & feature1 < 0.1, 
+                              (0.3 * feature1) + rnorm(n(), 0, 0.01), 
+                      if_else(feature1 >= 0.1 & feature1 < 0.3, 
+                              rbeta(n(), 1, 0.5), 
+                      if_else(feature1 >= 0.3 & feature1 < 0.5, 
+                              sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                      if_else(feature1 >= 0.5 & feature1 < 0.8, 
+                              -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                      if_else(feature1 >= 0.8 & feature1 < 0.9, 
+                              0.5 + runif(n(), -0.5, 0.5), 
+                              0.5 + rnorm(n(), 0, 0.3)))))))
+```
+
+```{r}
+# Specify a prediction of interest
+prediction_of_interest <- data.frame(feature1 = 0.07, 
+                                     feature2 = 200,
+                                     prediction = 0.05, 
+                                     color = factor("Prediction of Interest"))
+```
+
+```{r}
+# Compute the distance between the prediction of interest and 
+# all other observations
+lime_data$distance <- (1 - gower_dist(x = prediction_of_interest, 
+                                      y = lime_data))^20
+```
+
+### Linear Regression Explainer
+
+These visualizations are based on a weighted linear regression model used as the explainer.
+
+```{r}
+# Fit the interpretable explainer model (weighted linear regression)
+linear_explainer <- lm(formula = prediction ~ feature1 + feature2, 
+                       data = lime_data, 
+                       weights = distance)
+```
+
+```{r}
+# Extract the coefficients from the explainer
+linear_b0 <- coef(linear_explainer)[[1]]
+linear_b1 <- coef(linear_explainer)[[2]]
+linear_b2 <- coef(linear_explainer)[[3]]
+```
+
+```{r}
+# Predictions versus feature 1
+linear_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 +
+                linear_b2*prediction_of_interest$feature2, 
+              slope = linear_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Predictions versus feature 1
+linear_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 + 
+                linear_b1*prediction_of_interest$feature1,
+              slope = linear_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Plot that creates a size legend
+size_legend_plot <- lime_data %>%
+  gather(key = feature, value = value, 1:2) %>%
+  ggplot(mapping = aes(x = value, 
+                       y = prediction,
+                       size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) +
+  labs(size = "Weight") +
+  theme_linedraw(base_family = "Times") +
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Extract the legend
+size_legend <- get_legend(size_legend_plot)
+```
+
+```{r}
+# Join the two feature plots
+lime_linear_plots <- plot_grid(linear_plot_feature1, 
+                               linear_plot_feature2, 
+                               size_legend,
+                               ncol = 3, 
+                               rel_widths = c(0.4, 0.4, 0.1))
+```
+
+```{r}
+# Create a plot to extract a legend for the prediction of interest
+lime_legend_plot <- ggplot(data = prediction_of_interest, 
+                           mapping = aes(x = feature1, 
+                                         y = prediction, 
+                                         fill = color)) +
+  geom_point(size = 5, shape = 23) +
+  scale_fill_manual(values = c("#EFB084")) +
+  theme_classic(base_family = "Times") +
+  labs(fill = "") +
+  theme(legend.position = "bottom")
+
+# Extract the legend
+lime_legend <- get_legend(lime_legend_plot)
+```
+
+```{r}
+# Join the title, plots, legend, and caption into one figure
+lime_linear_concept <- plot_grid(lime_linear_plots, lime_legend,
+                         ncol = 1,
+                         rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is doing a good job of capturing the local trend.
+
+```{r}
+# View the plot
+lime_linear_concept
+```
+
+### Ridge Regression Explainer
+
+```{r}
+# Fits the explainer model (weighted ridge regression)
+ridge_explainer <- glmnet(x = lime_data %>% 
+                            select(feature1, feature2) %>%
+                            as.matrix(), 
+                          y = lime_data %>% pull(prediction),
+                          weights = lime_data$distance,
+                          family = "gaussian", 
+                          alpha = 0, 
+                          lambda = 1, 
+                          standardize = FALSE)
+```
+
+```{r}
+# Extract the coefficients from the explainer
+ridge_b0 <- ridge_explainer$a0[[1]]
+ridge_b1 <- ridge_explainer$beta[1,1]
+ridge_b2 <- ridge_explainer$beta[2,1]
+```
+
+```{r}
+# Predictions versus feature 1
+ridge_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 +
+                ridge_b2*prediction_of_interest$feature2, 
+              slope = ridge_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Predictions versus feature 2
+ridge_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 + 
+                ridge_b1*prediction_of_interest$feature1,
+              slope = ridge_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Join the two feature plots
+lime_ridge_plots <- plot_grid(ridge_plot_feature1, 
+                              ridge_plot_feature2, 
+                              size_legend,
+                              ncol = 3,
+                              rel_widths = c(0.4, 0.4, 0.1))
+```
+
+```{r}
+# Join the title, plots, legend, and caption into one figure
+lime_ridge_concept <- plot_grid(lime_ridge_plots, 
+                                lime_legend,
+                                ncol = 1,
+                                rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is **not** doing a good job of capturing the local trend.
+
+```{r}
+# Preview the plot
+lime_ridge_concept
+```
+
+# Bullet Data
+
+### The Data
 
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
 
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../../data/hamby224_test.csv")
+hamby224_test <- read.csv("../../../data/hamby224_test.csv")
 ```
@@
 
-# Random Forest Model
+### Random Forest Model
 
@@
 
-# Applying LIME
+### Applying LIME
 
@@
 
-```{r}
+```{r eval = FALSE}
 # Create or load the lime and explain objects for the main effects logisitic regression model
@@
 
-```{r}
+```{r eval = FALSE}
 create_bin_df <- function(bin_cut) {
@@
 
-# Visualizations of Data, Model, and LIME
+### Visualizations of Data, Model, and LIME
 
-```{r}
+```{r eval = FALSE}
 (case1 <- lime_explain_sub$explain %>% filter(case == 1))
@@
 
-```{r}
+```{r eval = FALSE}
 ggplot() +
@@
 
-```{r}
+```{r eval = FALSE}
 ggplot() + 

### 2019-08-24 README.Rmd
worked on organizing journals

@@
 - Paper
-    - I found ridge regression models in Python code (see journal 04)
-    - Show the plots using the ridge regression in journal 09
-    - What should I do about computing the generalized R2 value?
-    - Show this paper: https://arxiv.org/pdf/1806.07498.pdf
-    - Can you help to show me your vision with the minipage format?
-    - I could not find a locality metric output from Python.
-There was a section in their vignettes that seemed to be referring to some sort of assessment about the models, but I'm not sure what was happening.
-https://marcotcr.github.io/lime/tutorials/Tutorial%20-%20continuous%20and%20categorical%20features.html
+    - Can you re-explain your vision with the minipage format?
+- Internship
+    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
 - Graphics Group
     - email list (should I be added as an admin?)
-    - send out another email and plan for first week?
-    - updates on schedule since last meeting
+    - emailed Min (waiting for a response)
+    - show updated schedule
+    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
 
@@
 
+- finish organizing journals and update contents in readme
+- send out an email about graphics group plan for the first week
+- finish reading new paper
+- set up meeting with Danny on Friday once Heike sends me her availability
+- add generalized R2 values to plots
+- code up Laugel et al's work
+- point out differences and similarities from the other paper (such as normal sampling)
 - keep the LIME procedure at a higher level in the paper

### 2019-08-24 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
worked on organizing journals

@@
 ---
-title: "00-objectives_and_ideas"
+title: "Objectives and Ideas"
 author: "Katherine Goode"
@@
 
-# Overview
+This journal explains the objectives and ideas for the research project on applying LIME to the Hamby bullet data that is detailed in this series of journals.
 
-This journal explains the objectives of the research project on applying LIME to the Hamby bullet data that is detailed in this series of journals.
+# Objectives
 
-# Objectives of the Research Project
+### Overall
 
-It is the hope that this research project will result in two papers.
-One will focus on a statistical assessment of LIME and the other will focus on the explanation of how the application of LIME to the Hamby bullet data can help firearm examiners understand the random forest model predictions.
+- Understand how LIME works
+- Consider ways to improvement LIME
+- Apply LIME (or some improved version of LIME) to interpret the random forest model fit to the Hamby bullet data
 
-### Statistical Paper Presenting Visual Diagnostic Tools for LIME
+### Possible Papers
 
-Write a paper that introduces some visual diagnostics for LIME to assess its performance. Key points that will be made:
+Here are ideas for possible papers.
 
-1. explainer model is really bad (probably due to the binning)
-2. local explanations at not local
+**Statistical Paper Presenting Visual Diagnostic Tools for LIME**
 
-### Statistical Paper Assessing LIME
+This paper would assess the explainations produced by LIME. It would introduce some visual diagnostics for LIME to assess its performance. Key points that will be made:
 
-While applying LIME to the bullet matching dataset, we found that the explanations were not as good as we wanted them to be.
-This has led us to try to understand why the LIME algorithm is not working well and to propose some new methods to improve the algorithm.
-This paper will discuss isusses we found with the current LIME agorithm, describe our proposed approaches, and compare the results.
+1. Explainer model is really bad (probably due to the binning)
+2. Local explanations at not local
 
-### Firearm Examiner's Paper
+**Statistical Paper Assessing LIME**
+
+This paper would be an explanation of how the application of LIME to the Hamby bullet data can help firearm examiners understand the random forest model predictions.
+When we first applied LIME to the bullet matching dataset, we found that the explanations were not as good as we wanted them to be.
+This has led us to try to understand why the LIME algorithm is not working well.
+We even tried some new sampling methods to improve the algorithm.
+They mde a bit of improvement, but the improvements could be much better.
+This paper could discuss isusses we found with the current LIME agorithm, describe our proposed approaches, and compare the results.
+
+**Firearm Examiner's Paper**
 
@@
 
-# Concerns with LIME
+# Concerns
 
@@
 
-# General Thoughts about LIME
+# General Thoughts
 

### 2019-08-24 journals/01-hamby_data_and_rtrees/01-hamby_data_and_rtrees.Rmd
worked on organizing journals

--- 2019-08-14 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
@@
 ---
-title: "01-training and testing data"
+title: "Hamby Data and `rtrees`"
 author: "Katherine Goode"
@@
     toc_float: true
+    code_folding: hide
 ---
@@
 
-# Overview
-
-This journal includes a description of the Hamby study datasets, and the code that is used to clean the Hamby training and testing datasets.
+This journal includes a description of the Hamby datasets and the random forest model `rtrees` that will be used in this research project.
+Additionally, the specification and cleaning of the training and testing datasets are documented, and some initial visualizations of the random forest model are included.
 
@@
 # Load libraries
-library(tidyverse)
+library(bulletr)
+library(cowplot)
 library(plotly)
 library(randomForest)
+library(tidyverse)
 ```
 
-Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the bulletr library.
-I create such a vector below to use in this journal.
+# Hamby Data
 
-```{r}
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(bulletr::rtrees$importance)
-```
-
-# Description of the Hamby Data
+### Description
 
@@
 
-### Variable Definitions
+Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the bulletr library.
+I created such a vector to use in this journal, and this vector is printed below.
+It includes nine features.
 
-The definitions of the variables...
+```{r}
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(bulletr::rtrees$importance)
+rf_features
+```
+
+At some point, I would like to write down definitions of all the features.
 
@@
 
-# Training Data
+### Training Data
 
@@
 
-### The Raw Data
+**Raw Data**
 
@@
 
-### Considering the Number of Rows in the Raw Data
+**Number of Rows**
 
@@
 
-### Understanding the Missing Observations
+**Missing Observations**
 
@@
 
-### Cleaning the Trainng Data
+**Data Cleaning**
 
@@
 
-### Removing Bullets with Tank Rash
+**Removing Bullets with Tank Rash**
 
@@
 
-### Saving the Training Data
+**Saving the Data**
 
@@
 
-# Testing Data
+### Testing Data
 
-### The Raw Data
+**Raw Data**
 
@@
 
-### Cleaning the Testing Data
+**Data Cleaning**
 
@@
 
-### Saving the Testing Data
+**Saving the Data**
 
@@
 
+### Plots of Features
+
+##### Distributions by `samesource`
+
+I created the following two plots of the training data as suggested by Heike.
+The histograms below show the distributions of the features used in the random forest `rtrees`.
+The histograms are filled by the `samesource` variable, which is the truth of whether or not the comparison is from the same barrel and land.
+The default histograms make it hard to compare the distributions of the matches and non-matches since there are many more comparisons that have `samesource == FALSE`.
+
+```{r}
+# Create plots of the feature distributions colored by samesource for the training data
+hamby173and252_train %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
+       title = "Hamby 173 and 252 Training Data") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+By setting `position = "fill"` in the `geom_histogram` function, it is easier to compare the matches and non-matches.
+<span style="color:teal"> These plots could be used in the future to hand select the bins for lime.
+Additionally, fitting a logistic regression to this data could also be used to determine the LC50, LC10, ad LC90, which could be used as the bins for lime.
+</span>
+
+```{r}
+# Create plots of the feature distributions colored by samesource for the training data
+# using the position = "fill" option
+hamby173and252_train %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(position = "fill", bins = 30) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
+       title = "Hamby 173 and 252 Training Data") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+The plots below have the same structure, but they are created with the Hamby 224 testing data.
+I chose to not separate the testing data by sets, but this is something that could be done later if necessary.
+
+```{r}
+# Create plots of the feature distributions colored by samesource for the testing data
+hamby224_test %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(bins = 15) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Frequency", fill = "Same Source?",
+       title = "Hamby 224 Testing Data") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+# Create plots of the feature distributions colored by samesource for the testing 
+# data using the position = "fill" option
+hamby224_test %>% 
+  select(rf_features, samesource) %>%
+  gather(key = feature, value = value, 1:9) %>%
+  select(feature, value, samesource) %>%
+  ggplot(aes(x = value, fill = samesource)) + 
+  geom_histogram(position = "fill", bins = 15) + 
+  facet_wrap( ~ feature, scales = "free") +
+  labs(x = "Variable Value", y = "Proportion", fill = "Same Source?",
+       title = "Hamby 224 Testing Data") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+##### Correlations
+
+I made these plots to look at the correlation between features in the training data within the TRUE and FALSE cases of samesource.
+The features are highly correlated for the match comparisons.
+It is clear that the variables are more correlated with the match comparisons than the non-match comparisons.
+However, there are still some variables that are relatively highly correlation with the non-match comparisons.
+
+```{r fig.height = 4, fig.width = 9}
+# Create a correlation heatmap of the match comparisons in the training data
+cor_match <- hamby173and252_train %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == TRUE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") + 
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Match Comparisons")
+
+# Create a correlation heatmap of the non-match comparisons in the training data
+cor_nonmatch <- hamby173and252_train %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == FALSE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") +
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Non-Match Comparisons")
+
+# Create a title for the panel of plots
+cor_title <- ggdraw() +
+  draw_label("Correlation of Feature Variables in the Training Data", 
+             fontface = "bold", 
+             size = 16,
+             x = 0.5,
+             hjust = 0.5)
+
+# Create a joined legend for the panel of plots
+cor_legend <- get_legend(cor_match + theme(legend.position = "right"))
+
+# Create the panel of plots
+plot_grid(cor_title, 
+          plot_grid(cor_match, cor_nonmatch, cor_legend, ncol = 3, rel_widths = c(2, 2, 0.5)),
+          ncol = 1,
+          rel_heights = c(0.25, 3))
+```
+
+The plots below show the correlations for the testing data. The patterns in the plots look really similar to ones of the training data.
+
+```{r fig.height = 4, fig.width = 9}
+# Create a correlation heatmap of the match comparisons in the training data
+cor_match_test <- hamby224_test %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == TRUE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") + 
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Match Comparisons")
+
+# Create a correlation heatmap of the non-match comparisons in the training data
+cor_nonmatch_test <- hamby224_test %>%
+  select(rf_features, samesource) %>%
+  filter(samesource == FALSE) %>%
+  select(-samesource) %>%
+  cor() %>%
+  reshape2::melt() %>%
+  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms")),
+         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
+                                        "D", "sd_D", "mismatches", "non_cms"))) %>%
+  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
+  geom_tile() + 
+  scale_fill_gradient2(limits = c(-1, 1)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") +
+  labs(x = "", y = "", fill = "Correlation",
+       title = "Non-Match Comparisons")
+
+# Create a title for the panel of plots
+cor_title_test <- ggdraw() +
+  draw_label("Correlation of Feature Variables in the Testing Data", 
+             fontface = "bold", 
+             size = 16,
+             x = 0.5,
+             hjust = 0.5)
+
+# Create a joined legend for the panel of plots
+cor_legend_test <- get_legend(cor_match_test + theme(legend.position = "right"))
+
+# Create the panel of plots
+plot_grid(cor_title_test, 
+          plot_grid(cor_match_test, cor_nonmatch_test, cor_legend_test, 
+                    ncol = 3, rel_widths = c(2, 2, 0.5)),
+          ncol = 1,
+          rel_heights = c(0.25, 3))
+```
+
+# Random Forest: `rtrees`
+
+### Description
+
+The random forest model that was fit to the Hamby training dataset is discussed in the paper "Automatic Matching of Bullet Land Impressions" by E.
+Hare Et.
+Al.
+The model is available through the GitHub version of the `bulletr` package.
+The link to the GitHub repository for `bulletr` is https://github.com/CSAFE-ISU/bulletr.
+
+The random forest model is stored in the package `bulletr` as a data object called `rtrees`.
+The paper does not include many details about the model fitting process, so I looked at some of the model features, which are printed below.
+These values told me that the model was fit using the predictive features of `ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks` with 300 trees and the parameter of `mtry` set to 3, which is the "number of variables randomly sampled as candidates at each split" as explained in the `randomforest` package documentation.
+
+```{r}
+# Importance values from the random forest
+rtrees$importance
+
+# The number of trees used in the random forest
+rtrees$ntree
+
+# "Number of variables randomly sampled as candidates at each split"
+rtrees$mtry
+```
+
+### Visualizations
+
+##### Random Forest Scores
+
+**Facet Version**
+
+The plot below is the model for the one that will be used in the app for exploring the `lime` explanations from the bullet matching data. This is the data from set 1 of the testing dataset.
+
+```{r}
+# Heatmap of rfscore for each comparison in set 1
+hamby224_test %>%
+  filter(set == "Set 1") %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
+             text = paste('Bullets Compared: ', bullet1, "-", land1, 
+                          "vs", bullet2, "-", land2,
+                          '\nRandom Forest Score: ', 
+                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
+  geom_tile(aes(fill = rfscore)) +
+  facet_grid(bullet2 ~ bullet1, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank()) +
+  labs(x = "", y = "", fill = "RF Score")
+```
+
+**Individual Plots Version**
+
+I also wrote some code to create the above plot using individual plots instead of facets. This is included below. (It is a bit outdated compared to my newer version of the plot.)
+
+```{r}
+# Code for creating the heatmap plots using individual plots
+p1 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 1") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p2 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Known 2") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p3 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 1", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p4 <- ggplot() + geom_blank() + theme_classic()
+
+p5 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Known 2") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p6 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Known 2", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score") + 
+  theme(legend.position = "none")
+
+p7 <- ggplot() + geom_blank() + theme_classic()
+
+p8 <- ggplot() + geom_blank() + theme_classic()
+
+p9 <- hamby224_test %>%
+  filter(set == "Set 1", bullet1 == "Questioned", bullet2 == "Questioned") %>%
+  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
+  distinct() %>%
+  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2)) +
+  geom_tile(aes(fill = rfscore)) +
+  #facet_grid(bullet1 ~ bullet2, scales = "free") +
+  theme_minimal() +
+  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5, limits = c(0,1)) +
+  labs(x = "Land 1", y = "Land 2", fill = "RF Score")
+
+style(subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, 
+              nrows = 3, 
+              titleX = TRUE, 
+              titleY = TRUE, 
+              margin = 0.03),
+      hoverinfo = "skip",
+      traces = 7)
+```
+
+##### Parallel Coordinate Plots
+
+```{r}
+# Create a dataframe with the random forest features ordered by importance
+rf_features_ordered <- data.frame(feature = rownames(bulletr::rtrees$importance), 
+                                  MeanDecreaseGini = bulletr::rtrees$importance) %>%
+  arrange(desc(MeanDecreaseGini))
+```
+
+Below is a parallel coordinate plot of the training dataset.
+It is facetted by `samesource` and colored by `rfscore`.
+The features are sorted by the variable importance scores (descending from left to right) from the `rtrees` model.
+It is interesting to see that the matches with low rfscores have feature values that are similar to the nonmatches.
+
+```{r fig.width = 10}
+hamby173and252_train %>%
+  mutate(case = 1:n()) %>%
+  select(case, rfscore, samesource, ccf:sum_peaks) %>%
+  mutate_at(rf_features, scale) %>%
+  gather(variable, value, 4:12) %>%
+  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
+  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
+  geom_point() + 
+  geom_line(alpha = 0.2) + 
+  facet_grid( ~ samesource) + 
+  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "Feature (sorted by rtrees variable importance)", 
+       y = "Standardized Feature Values")
+```
+
+Below is a parallel coordinate plot of the testing dataset.
+It is facetted by `samesource` and colored by `rfscore`.
+You can see a clear distinction between the trends of the feature values from the nonmatches and matches.
+It is interesting to consider the cases in set 1 that are matches but were predicted to be nonmatches by the model.
+These are the cases colored in grey, and their feature values are very different from the observations that were predicted to be matches by the model.
+The nonmatch predictions have values that are closer to the nonmatches.
+
+```{r fig.width = 10}
+hamby224_test %>%
+  na.omit() %>%
+  select(case, set, rfscore, samesource, ccf:sum_peaks) %>%
+  mutate_at(rf_features, scale) %>%
+  gather(variable, value, 5:13) %>%
+  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
+  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
+  geom_point() + 
+  geom_line(alpha = 0.5) + 
+  facet_grid(set ~ samesource) + 
+  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  labs(x = "Feature (sorted by rtrees variable importance)", 
+       y = "Standardized Feature Values")
+```
+
+##### Biplot
+
+```{r eval = FALSE}
+pca_set1 <- princomp(x = hamby224_test %>% 
+                       filter(set == "Set 1") %>% 
+                       select(rf_features) %>% 
+                       na.omit(), 
+                     cor = TRUE)
+biplot(pca, col = hamby224_test %>% 
+                       filter(set == "Set 1") %>% 
+                       pull(rfscore))
+```
+
 # Session Info

### 2019-08-24 journals/02-understanding_lime/02-understanding_lime.Rmd
worked on organizing journals

--- 2019-08-20 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
@@
 ---
-title: "Lime Algorithm and Proposed Methods"
+title: "Understanding LIME"
 author: "Katherine Goode"
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, cache = TRUE)
 ```
-
-# Overview
 
@@
 ```{r}
+# Load packages
+library(cowplot)
+library(furrr)
+library(future)
+library(glmnet)
+library(gower)
+library(lime)
+library(randomForest)
+library(tidyverse)
+
 # Source functions
@@
 We leave such exploration for future work, as linear explanations work quite well for multiple black-box models in our experiments.
+
+# Concept Visualizations
+
+The images in this section were created using simulated data that I knew had a local trend around the point of interest.
+I consider both a linear regression and a ridge regression as the explainer model.
+
+### Data and Model
+
+This code generates the data and predictions from a hypothetical complex model.
+
+```{r}
+# Generate features and predictions from a hypothetical complex model
+set.seed(20190624)
+lime_data <- data.frame(feature1 = sort(runif(250, 0, 1)),
+                        feature2 = sample(x = 1:250, 
+                                          size = 250, 
+                                          replace = FALSE)) %>%
+  mutate(prediction = if_else(feature1 >= 0 & feature1 < 0.1, 
+                              (0.3 * feature1) + rnorm(n(), 0, 0.01), 
+                      if_else(feature1 >= 0.1 & feature1 < 0.3, 
+                              rbeta(n(), 1, 0.5), 
+                      if_else(feature1 >= 0.3 & feature1 < 0.5, 
+                              sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                      if_else(feature1 >= 0.5 & feature1 < 0.8, 
+                              -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                      if_else(feature1 >= 0.8 & feature1 < 0.9, 
+                              0.5 + runif(n(), -0.5, 0.5), 
+                              0.5 + rnorm(n(), 0, 0.3)))))))
+```
+
+```{r}
+# Specify a prediction of interest
+prediction_of_interest <- data.frame(feature1 = 0.07, 
+                                     feature2 = 200,
+                                     prediction = 0.05, 
+                                     color = factor("Prediction of Interest"))
+```
+
+```{r}
+# Compute the distance between the prediction of interest and 
+# all other observations
+lime_data$distance <- (1 - gower_dist(x = prediction_of_interest, 
+                                      y = lime_data))^20
+```
+
+### Linear Regression Explainer
+
+These visualizations are based on a weighted linear regression model used as the explainer.
+
+```{r}
+# Fit the interpretable explainer model (weighted linear regression)
+linear_explainer <- lm(formula = prediction ~ feature1 + feature2, 
+                       data = lime_data, 
+                       weights = distance)
+```
+
+```{r}
+# Extract the coefficients from the explainer
+linear_b0 <- coef(linear_explainer)[[1]]
+linear_b1 <- coef(linear_explainer)[[2]]
+linear_b2 <- coef(linear_explainer)[[3]]
+```
+
+```{r}
+# Predictions versus feature 1
+linear_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 +
+                linear_b2*prediction_of_interest$feature2, 
+              slope = linear_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Predictions versus feature 1
+linear_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 + 
+                linear_b1*prediction_of_interest$feature1,
+              slope = linear_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Plot that creates a size legend
+size_legend_plot <- lime_data %>%
+  gather(key = feature, value = value, 1:2) %>%
+  ggplot(mapping = aes(x = value, 
+                       y = prediction,
+                       size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) +
+  labs(size = "Weight") +
+  theme_linedraw(base_family = "Times") +
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Extract the legend
+size_legend <- get_legend(size_legend_plot)
+```
+
+```{r}
+# Join the two feature plots
+lime_linear_plots <- plot_grid(linear_plot_feature1, 
+                               linear_plot_feature2, 
+                               size_legend,
+                               ncol = 3, 
+                               rel_widths = c(0.4, 0.4, 0.1))
+```
+
+```{r}
+# Create a plot to extract a legend for the prediction of interest
+lime_legend_plot <- ggplot(data = prediction_of_interest, 
+                           mapping = aes(x = feature1, 
+                                         y = prediction, 
+                                         fill = color)) +
+  geom_point(size = 5, shape = 23) +
+  scale_fill_manual(values = c("#EFB084")) +
+  theme_classic(base_family = "Times") +
+  labs(fill = "") +
+  theme(legend.position = "bottom")
+
+# Extract the legend
+lime_legend <- get_legend(lime_legend_plot)
+```
+
+```{r}
+# Join the title, plots, legend, and caption into one figure
+lime_linear_concept <- plot_grid(lime_linear_plots, lime_legend,
+                         ncol = 1,
+                         rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is doing a good job of capturing the local trend.
+
+```{r}
+# View the plot
+lime_linear_concept
+```
+
+### Ridge Regression Explainer
+
+```{r}
+# Fits the explainer model (weighted ridge regression)
+ridge_explainer <- glmnet(x = lime_data %>% 
+                            select(feature1, feature2) %>%
+                            as.matrix(), 
+                          y = lime_data %>% pull(prediction),
+                          weights = lime_data$distance,
+                          family = "gaussian", 
+                          alpha = 0, 
+                          lambda = 1, 
+                          standardize = FALSE)
+```
+
+```{r}
+# Extract the coefficients from the explainer
+ridge_b0 <- ridge_explainer$a0[[1]]
+ridge_b1 <- ridge_explainer$beta[1,1]
+ridge_b2 <- ridge_explainer$beta[2,1]
+```
+
+```{r}
+# Predictions versus feature 1
+ridge_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 +
+                ridge_b2*prediction_of_interest$feature2, 
+              slope = ridge_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Predictions versus feature 2
+ridge_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 + 
+                ridge_b1*prediction_of_interest$feature1,
+              slope = ridge_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+```
+
+```{r}
+# Join the two feature plots
+lime_ridge_plots <- plot_grid(ridge_plot_feature1, 
+                              ridge_plot_feature2, 
+                              size_legend,
+                              ncol = 3,
+                              rel_widths = c(0.4, 0.4, 0.1))
+```
+
+```{r}
+# Join the title, plots, legend, and caption into one figure
+lime_ridge_concept <- plot_grid(lime_ridge_plots, 
+                                lime_legend,
+                                ncol = 1,
+                                rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is **not** doing a good job of capturing the local trend.
+
+```{r}
+# Preview the plot
+lime_ridge_concept
+```
 

### 2019-08-24 journals/03-applying_lime_logistic/03-applying_lime_logistic.Rmd
worked on organizing journals

--- 2019-06-12 journals/07-logistic_regression/07-logistic_regression.Rmd
@@
 ---
-title: "07-logistic_regression"
+title: "Applying Lime to a Logisitic Regression"
 author: "Katherine Goode"
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, cache = TRUE)
+knitr::opts_chunk$set(echo = TRUE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      eval = TRUE, 
+                      cache = TRUE)
 ```
@@
 
-I have been thinking a lot about it is difficult to determine whether LIME is providing reasonable explanations, because we cannot know what the random forest is doing.
+I have been thinking a lot about it is difficult to determine whether LIME is xproviding reasonable explanations, because we cannot know what the random forest is doing.
 That is the point of LIME.
@@
 library(gretchenalbrecht)
-library(hierNet)
 library(lime)

### 2019-08-24 journals/03-applying_lime_rtrees/03-applying_lime_rtrees.Rmd
worked on organizing journals

--- 2019-02-22 journals/05-applying_lime.Rmd
@@
 ---
-title: "05-applying_lime"
+title: "Applying lime to `rtrees`"
 author: "Katherine Goode"
@@
 # Load in the training data (Hamby Data 173 and 252)
-hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")
+hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
 
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../data/hamby224_test.csv")
+hamby224_test <- read.csv("../../../data/hamby224_test.csv")
 ```
@@
 # Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("../data/hamby224_lime_inputs.rds")) {
+if(!file.exists("../../../data/hamby224_lime_inputs.rds")) {
 
@@
   # Save the lime objects
-  saveRDS(hamby224_lime_inputs, "../data/hamby224_lime_inputs.rds")
-  saveRDS(hamby224_lime, "../data/hamby224_lime.rds")
-  saveRDS(hamby224_explain, "../data/hamby224_explain.rds")
+  saveRDS(hamby224_lime_inputs, "../../../data/hamby224_lime_inputs.rds")
+  saveRDS(hamby224_lime, "../../../data/hamby224_lime.rds")
+  saveRDS(hamby224_explain, "../../../data/hamby224_explain.rds")
 
@@
   # Load in the lime objects
-  hamby224_lime_inputs <- readRDS("../data/hamby224_lime_inputs.rds")
-  hamby224_lime <- readRDS("../data/hamby224_lime.rds")
-  hamby224_explain <- readRDS("../data/hamby224_explain.rds")
+  hamby224_lime_inputs <- readRDS("../../../data/hamby224_lime_inputs.rds")
+  hamby224_lime <- readRDS("../../../data/hamby224_lime.rds")
+  hamby224_explain <- readRDS("../../../data/hamby224_explain.rds")
 
@@
 # Create a dataframe with the bins
-if (!file.exists("../data/hamby224_bins.csv")) {
+if (!file.exists("../../../data/hamby224_bins.csv")) {
 
@@
   # Save the bin boundaries and bins
-  saveRDS(hamby224_bin_boundaries, "../data/hamby224_bin_boundaries.rds")
-  saveRDS(hamby224_bins, "../data/hamby224_bins.rds")
+  saveRDS(hamby224_bin_boundaries, "../../../data/hamby224_bin_boundaries.rds")
+  saveRDS(hamby224_bins, "../../../data/hamby224_bins.rds")
 
@@
   # Load in the bin boundaries and bins
-  hamby224_bin_boundaries <- readRDS("../data/hamby224_bin_boundaries.rds")
-  hamby224_bins <- readRDS("../data/hamby224_bins.rds")
+  hamby224_bin_boundaries <- readRDS("../../../data/hamby224_bin_boundaries.rds")
+  hamby224_bins <- readRDS("../../../data/hamby224_bins.rds")
 
@@
 # Create the test_explain combined data if the file does not already exist
-if(!file.exists("../data/hamby224_test_explain.rds")) {
+if(!file.exists("../../../data/hamby224_test_explain.rds")) {
 
@@
   # Save the combined test and explain data
-  saveRDS(hamby224_test_explain, "../data/hamby224_test_explain.rds")
+  saveRDS(hamby224_test_explain, "../../../data/hamby224_test_explain.rds")
 
@@
   # Load in the data
-  hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
+  hamby224_test_explain <- readRDS("../../../data/hamby224_test_explain.rds")
 
@@
 # Create the lime comparison data if the file does not already exist
-if(!file.exists("../data/hamby224_lime_comparisons.rds")) {
+if(!file.exists("../../../data/hamby224_lime_comparisons.rds")) {
 
@@
   # Save the lime comparison data frame
-  saveRDS(hamby224_lime_comparisons, "../data/hamby224_lime_comparisons.rds")
+  saveRDS(hamby224_lime_comparisons, "../../../data/hamby224_lime_comparisons.rds")
 
@@
   # Load in the lime comparison data frame
-  hamby224_lime_comparisons <- readRDS("../data/hamby224_lime_comparisons.rds")
+  hamby224_lime_comparisons <- readRDS("../../../data/hamby224_lime_comparisons.rds")
 
@@
 # Perform the sensitivity analysis if not already saved
-if(!file.exists("../data/hamby224_sensitivity_inputs.rds")) {
+if(!file.exists("../../../data/hamby224_sensitivity_inputs.rds")) {
 
@@
   # Save the sensitivity inputs and outputs
-  saveRDS(hamby224_sensitivity_inputs, "../data/hamby224_sensitivity_inputs.rds")
-  saveRDS(hamby224_sensitivity_outputs, "../data/hamby224_sensitivity_outputs.rds")
+  saveRDS(hamby224_sensitivity_inputs, "../../../data/hamby224_sensitivity_inputs.rds")
+  saveRDS(hamby224_sensitivity_outputs, "../../../data/hamby224_sensitivity_outputs.rds")
 
@@
   # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_inputs <- readRDS("../data/hamby224_sensitivity_inputs.rds")
-  hamby224_sensitivity_outputs <- readRDS("../data/hamby224_sensitivity_outputs.rds")
+  hamby224_sensitivity_inputs <- readRDS("../../../data/hamby224_sensitivity_inputs.rds")
+  hamby224_sensitivity_outputs <- readRDS("../../../data/hamby224_sensitivity_outputs.rds")
 
@@
 # Join the sensativity outputs with the test data if not already saved
-if(!file.exists("../data/hamby224_sensitivity_joined.rds")) {
+if(!file.exists("../../../data/hamby224_sensitivity_joined.rds")) {
 
@@
   # Save the joined test and explained dataframes
-  saveRDS(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.rds")
+  saveRDS(hamby224_sensitivity_joined, "../../../data/hamby224_sensitivity_joined.rds")
 
@@
   # Load in the sensitivity inputs and outputs
-  hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
+  hamby224_sensitivity_joined <- readRDS("../../../data/hamby224_sensitivity_joined.rds")
 

### 2019-08-24 journals/04-assessing_lime/04-assessing_lime.Rmd
worked on organizing journals

--- 2019-03-01 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd
@@
 ---
-title: "06-assessing_lime_explanations"
+title: "Assessing Lime"
 author: "Katherine Goode"
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
-                      error = FALSE, cache = TRUE)
+knitr::opts_chunk$set(echo = TRUE, 
+                      eval = TRUE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      error = FALSE, 
+                      cache = TRUE)
 ```
@@
 library(gretchenalbrecht)
-library(seriation)
+#library(seriation)
 library(tidyverse)
@@
 # Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../../data/hamby224_test.csv") # created in the paper
+hamby224_test <- read.csv("../../../data/hamby224_test.csv") # created in the paper
 
 # Read in the test_explain data
-hamby224_test_explain <- readRDS("../../data/hamby224_test_explain.rds")
+hamby224_test_explain <- readRDS("../../../data/hamby224_test_explain.rds")
 
-hamby224_sensitivity_joined <- readRDS("../../data/hamby224_sensitivity_joined.rds")
+hamby224_sensitivity_joined <- readRDS("../../../data/hamby224_sensitivity_joined.rds")
 
@@
 # paper since they will be discussed in the paper)
-hamby224_lime_comparisons <- readRDS("../../data/hamby224_lime_comparisons.rds")
+hamby224_lime_comparisons <- readRDS("../../../data/hamby224_lime_comparisons.rds")
 ```
@@
 
+# My LIME
+
+### Random Forest Model
+
+```{r}
+# Fit a random forest model with the top two most important features in the model
+if(!file.exists("./data/rfmodel.rds")) {
+
+  # Fit the random forest  
+  rfmodel <- randomForest(factor(samesource) ~ rough_cor + ccf, data = hamby173and252_train)
+
+  # Save the random forest
+  saveRDS(rfmodel, "./data/rfmodel.rds")
+
+} else {
+
+  # Load the rf model
+  rfmodel <- readRDS("./data/rfmodel.rds")
+}
+```
+
+```{r}
+# Create a dataset with the test data input to the random forest model 
+# and the predictions from the random forest model
+hamby224_test_subset <- hamby224_test %>%
+  na.omit() %>%
+  select(case:land2, rough_cor, ccf, samesource) %>%
+  mutate(rfpred = predict(rfmodel, 
+                           newdata = hamby224_test %>% select(rough_cor, ccf) %>% na.omit()),
+         rfscore = predict(rfmodel, 
+                           newdata = hamby224_test %>% select(rough_cor, ccf) %>% na.omit(),
+                           type = "prob")[,2])
+```
+
+### Applying LIME
+
+The functions `lime` and `explain` from the lime package are applied below to the random forest model.
+
+```{r eval = FALSE}
+# Create or load the lime and explain objects for the main effects logisitic regression model
+if(!file.exists("./data/lime_explain_sub.rds")) {
+
+  # Set a seed
+  set.seed(20190315)
+
+  # Apply lime
+  lime_sub <- lime(x = hamby173and252_train %>% select(rough_cor, ccf), 
+                   model = as_classifier(rfmodel))
+
+  # Apply explain
+  explain_sub <- explain(x = hamby224_test %>%
+                             select(rough_cor, ccf) %>% 
+                             na.omit(), 
+                           explainer = lime_sub, 
+                           n_labels = 1,
+                           n_features = 2)
+
+  # Join the lime and explain objects in a list
+  lime_explain_sub <- list(lime = lime_sub, explain = explain_sub)
+
+  # Save the lime and explain objects
+  saveRDS(lime_explain_sub, "./data/lime_explain_sub.rds")
+
+} else {
+
+  # Load the lime and explain objects
+  lime_explain_sub <- readRDS("./data/lime_explain_sub.rds")
+
+}
+```
+
+```{r eval = FALSE}
+create_bin_df <- function(bin_cut) {
+ data.frame(quantile = c("0%", "25%", "50%", "75%", "100%"), 
+            bin_cut) 
+}
+
+bin_cuts <- purrr::map_df(lime_explain_sub$lime$bin_cuts, 
+                          create_bin_df,
+                          .id = "feature") %>%
+  spread(key = feature, value = bin_cut)
+
+bin_cuts
+```
+
+### Visualizations of Data, Model, and LIME
+
+```{r eval = FALSE}
+(case1 <- lime_explain_sub$explain %>% filter(case == 1))
+```
+
+```{r eval = FALSE}
+ggplot() +
+  geom_point(data = hamby173and252_train %>% filter(samesource == FALSE),
+             aes(x = rough_cor, y = ccf),
+             color = "darkgrey",
+             alpha = 0.2) +
+  geom_point(data = hamby173and252_train %>% filter(samesource == TRUE),
+             aes(x = rough_cor, y = ccf),
+             color = "darkorange") + 
+  geom_vline(xintercept = bin_cuts$rough_cor) + 
+  geom_hline(yintercept = bin_cuts$ccf) +
+  theme_minimal()
+```
+
+```{r eval = FALSE}
+ggplot() + 
+  geom_point(data = hamby224_test_subset, 
+             aes(x = rough_cor, y = ccf, color = rfscore),
+             alpha = 0.5) + 
+  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
+  geom_point(data = lime_explain_sub$explain %>% 
+               filter(case == 1) %>%
+               select(feature, feature_value) %>%
+               spread(key = feature, value = feature_value),
+             aes(x = rough_cor, y = ccf)) +
+  geom_vline(xintercept = bin_cuts$rough_cor) + 
+  geom_hline(yintercept = bin_cuts$ccf) + 
+  theme_minimal()
+```
+
 # Session Info

### 2019-08-24 journals/05-iris_comparison/05-iris_comparison.Rmd
worked on organizing journals

--- 2019-06-12 journals/08-iris_comparison/08-iris_comparison.Rmd
@@
 ---
-title: "08-iris_comparison"
+title: "Iris Comparison"
 author: "Katherine Goode"

### 2019-08-24 journals/06-other_explainers/06-other_explainers.Rmd
worked on organizing journals

--- 2019-03-26 journals/10-other_explainers/10-other_explainers.Rmd
@@
 ---
-title: "10-other_explainers"
+title: "Other Explainers"
 author: "Katherine Goode"

### 2019-08-24 journals/07-computation_issues/07-computation_issues.Rmd
worked on organizing journals

--- 2019-02-25 journals/03-computation_issues/03-computation_issues.Rmd
@@
 ---
-title: "03-computation_issues"
+title: "Computation Issues"
 author: "Katherine Goode"

### 2019-08-24 journals/03-applying_lime_logistic/03-applying_lime_logistic.Rmd
updated journals after organization

@@
                       warning = FALSE, 
-                      eval = TRUE, 
-                      cache = TRUE)
+                      eval = TRUE)
 ```
@@
   # Save the model
-  saveRDS(logistic_mains, "./data/logistic_mains.rds")
+  saveRDS(logistic_mains, "../../../data/logistic_mains.rds")
 
@@
   # Load the model
-  logistic_mains <- readRDS("./data/logistic_mains.rds")
+  logistic_mains <- readRDS("../../../data/logistic_mains.rds")
 
@@
 # Fit or load the logistic regression model with all two way interactions
-if(!file.exists("./data/logistic_inters2.rds")) {
+if(!file.exists("../../../data/logistic_inters2.rds")) {
 
@@
   # Save the model
-  saveRDS(logistic_inters2, "./data/logistic_inters2.rds")
+  saveRDS(logistic_inters2, "../../../data/logistic_inters2.rds")
 
@@
   # Load the model
-  logistic_inters2 <- readRDS("./data/logistic_inters2.rds")
+  logistic_inters2 <- readRDS("../../../data/logistic_inters2.rds")
 
@@
 # Fit or load the lasso logistic regression model
-if(!file.exists("./data/logistic_lasso.rds")) {
+if(!file.exists("../../../data/logistic_lasso.rds")) {
 
@@
   # Save the model
-  saveRDS(logistic_lasso, "./data/logistic_lasso.rds")
+  saveRDS(logistic_lasso, "../../../data/logistic_lasso.rds")
 
@@
   # Load the model
-  logistic_lasso <- readRDS("./data/logistic_lasso.rds")
+  logistic_lasso <- readRDS("../../../data/logistic_lasso.rds")
 
@@
 # Create or load the lime and explain objects for the main effects logisitic regression model
-if(!file.exists("./data/lime_explain_mains.rds")) {
+if(!file.exists("../../../data/lime_explain_mains.rds")) {
 
@@
   # Apply lime
-  lime_mains <- lime(x = hamby173and252_train %>% select(rf_features), 
+  lime_mains <- lime(x = hamby173and252_train %>%
+                       select(rf_features), 
                      model = logistic_mains)
@@
   # Save the lime and explain objects
-  saveRDS(lime_explain_mains, "./data/lime_explain_mains.rds")
+  saveRDS(lime_explain_mains, "../../../data/lime_explain_mains.rds")
 
@@
   # Load the lime and explain objects
-  lime_explain_mains <- readRDS("./data/lime_explain_mains.rds")
+  lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")
 
@@
 # Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("./data/logistic_lime_inputs.rds")) {
+if(!file.exists("../../../data/logistic_lime_inputs.rds")) {
 
@@
   # Save the lime objects
-  saveRDS(logistic_lime_inputs, "./data/logistic_lime_inputs.rds")
-  saveRDS(logistic_lime, "./data/logistic_lime.rds")
-  saveRDS(logistic_explain, "./data/logistic_explain.rds")
+  saveRDS(logistic_lime_inputs, "../../../data/logistic_lime_inputs.rds")
+  saveRDS(logistic_lime, "../../../data/logistic_lime.rds")
+  saveRDS(logistic_explain, "../../../data/logistic_explain.rds")
 
@@
   # Load in the lime objects
-  logistic_lime_inputs <- readRDS("./data/logistic_lime_inputs.rds")
-  logistic_lime <- readRDS("./data/logistic_lime.rds")
-  logistic_explain <- readRDS("./data/logistic_explain.rds")
+  logistic_lime_inputs <- readRDS("../../../data/logistic_lime_inputs.rds")
+  logistic_lime <- readRDS("../../../data/logistic_lime.rds")
+  logistic_explain <- readRDS("../../../data/logistic_explain.rds")
 
@@
 # Create the test_explain combined data if the file does not already exist
-if(!file.exists("./data/logistic_test_explain.rds")) {
+if(!file.exists("../../../data/logistic_test_explain.rds")) {
 
@@
   # Save the combined test and explain data
-  saveRDS(logistic_test_explain, "./data/logistic_test_explain.rds")
+  saveRDS(logistic_test_explain, "../../../data/logistic_test_explain.rds")
 
@@
   # Load in the data
-  logistic_test_explain <- readRDS("./data/logistic_test_explain.rds")
+  logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")
 
@@
 # Create the lime comparison data if the file does not already exist
-if(!file.exists("./data/logistic_lime_comparisons.rds")) {
+if(!file.exists("../../../data/logistic_lime_comparisons.rds")) {
 
@@
   # Save the lime comparison data frame
-  saveRDS(logistic_lime_comparisons, "./data/logistic_lime_comparisons.rds")
+  saveRDS(logistic_lime_comparisons, "../../../data/logistic_lime_comparisons.rds")
 
@@
   # Load in the lime comparison data frame
-  logistic_lime_comparisons <- readRDS("./data/logistic_lime_comparisons.rds")
+  logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")
 

### 2019-08-24 journals/04-assessing_lime/04-assessing_lime.Rmd
updated journals after organization

@@
 library(gretchenalbrecht)
+library(lime)
 #library(seriation)
 library(tidyverse)
+library(randomForest)
+
+# Load in the training data 
+hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
 
@@
 # Fit a random forest model with the top two most important features in the model
-if(!file.exists("./data/rfmodel.rds")) {
+if(!file.exists("../../../data/rfmodel.rds")) {
 
@@
   # Save the random forest
-  saveRDS(rfmodel, "./data/rfmodel.rds")
+  saveRDS(rfmodel, "../../../data/rfmodel.rds")
 
@@
   # Load the rf model
-  rfmodel <- readRDS("./data/rfmodel.rds")
+  rfmodel <- readRDS("../../../data/rfmodel.rds")
 }
@@
 
-```{r eval = FALSE}
+```{r}
 # Create or load the lime and explain objects for the main effects logisitic regression model
-if(!file.exists("./data/lime_explain_sub.rds")) {
+if(!file.exists("../../../data/lime_explain_sub.rds")) {
 
@@
   # Save the lime and explain objects
-  saveRDS(lime_explain_sub, "./data/lime_explain_sub.rds")
+  saveRDS(lime_explain_sub, "../../../data/lime_explain_sub.rds")
 
@@
   # Load the lime and explain objects
-  lime_explain_sub <- readRDS("./data/lime_explain_sub.rds")
+  lime_explain_sub <- readRDS("../../../data/lime_explain_sub.rds")
 
@@
 
-```{r eval = FALSE}
+```{r}
 create_bin_df <- function(bin_cut) {
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 (case1 <- lime_explain_sub$explain %>% filter(case == 1))
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 ggplot() +
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 ggplot() + 

### 2019-08-27 README.Rmd
added talking point

@@
     - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
+    - How to include an image in the preview of a post in blogdown?
 

### 2019-08-27 README.Rmd
finished organizing journals

--- 2019-08-24 README.Rmd
@@
     - Can you re-explain your vision with the minipage format?
+    - I cannot get LIME to work on my computer anymore...
 - Internship
@@
 - Graphics Group
+    - show updated schedule
     - email list (should I be added as an admin?)
-    - emailed Min (waiting for a response)
-    - show updated schedule
     - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
+    - How to include an image in the preview of a post in blogdown?
+    - Are you still available to talk next week?
 
@@
 
-- finish organizing journals and update contents in readme
-- send out an email about graphics group plan for the first week
 - finish reading new paper
-- set up meeting with Danny on Friday once Heike sends me her availability
 - add generalized R2 values to plots
@@
 - `lime.png`: fun picture of a lime to use in the readme
+- `python-ridge1`, `python-ridge2`, and `python-ridge3`: screen shots of the python LIME package showing the use of a ridge regression as the explainer
 
@@
 - `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
-- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
-- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
-- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
-- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
-- `05-applying_lime_to_rtrees`: application of lime and sensitivity analysis for many different input options
-- `06-assessing_lime_explanations`: assessment of the lime explanations
-- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
-- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
-- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
-- `10-other_explainers`: trying out other model explainers
+- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
+- `02-understanding_lime`: explanation of LIME procedure
+- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
+- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
+- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
+- `06-other_explainers`: trying out other model explainers
+- `07-computation_issues`: documentation of some of the computation issues I ran into during the project
 

### 2019-08-27 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
finished organizing journals

--- 2019-08-24 journals/01-hamby_data_and_rtrees/01-hamby_data_and_rtrees.Rmd
@@
     toc_float: true
-    code_folding: hide
 ---
@@
 
-This journal includes a description of the Hamby datasets and the random forest model `rtrees` that will be used in this research project.
-Additionally, the specification and cleaning of the training and testing datasets are documented, and some initial visualizations of the random forest model are included.
+This journal includes a description of the Hamby datasets and models fit to the data.
+The specification and cleaning of the training and testing datasets are documented, and some initial visualizations of the random forest model are included.
+The models included are the random forest model `rtrees` and several logistic regression models.
 
@@
 library(cowplot)
+library(glmnet)
 library(plotly)
@@
 
+# Logistic Regressions
+
+I have been thinking a lot about it is difficult to determine whether LIME is providing reasonable explanations, because we cannot know what the random forest is doing.
+That is the point of LIME.
+Heike suggested that we fit a logistic regression model to the training bullet data.
+We can then apply LIME to the logistic regression and determine if the explanations match what we would expect based on the coefficients of the logistic regression that we can interpret.
+She also suggested including interactions in the logistic regression model.
+This section includes code for fitting several logisitic regression models.
+
+### Main Effects Only
+
+The code below fits a logistic regression model to the training data using the `train` function from the caret package.
+The nine features used to fit `rtrees` are included as main effects only.
+The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+
+```{r}
+# Fit or load the logistic regression model with only main effects
+if(!file.exists("../../../data/logistic_mains.rds")) {
+
+  # Set a seed
+  set.seed(20190226)
+
+  # Fit the model
+  logistic_mains <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + 
+                                   matches + mismatches + cms + non_cms + sum_peaks,
+                                 preProcess = "scale",
+                                 data = hamby173and252_train, 
+                                 method = "glm", 
+                                 family = "binomial")
+
+  # Save the model
+  saveRDS(logistic_mains, "../../../data/logistic_mains.rds")
+
+} else{
+
+  # Load the model
+  logistic_mains <- readRDS("../../../data/logistic_mains.rds")
+
+}
+```
+
+The output from the model is shown below. The features of ccf and matches stand out as the most important features in the model.
+
+```{r}
+# Summary of the model
+summary(logistic_mains)
+```
+
+### All Two Way Interactions
+
+The code below fits a logistic regression model to the training data using the `train` function from the caret package.
+The nine features used to fit `rtrees` are included as main effects and with all two way interactions.
+The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.
+
+```{r}
+# Fit or load the logistic regression model with all two way interactions
+if(!file.exists("../../../data/logistic_inters2.rds")) {
+
+  # Set a seed
+  set.seed(20190226)
+
+  # Fit the model
+  logistic_inters2 <- caret::train(as.factor(samesource) ~
+                                       (ccf + rough_cor + D + sd_D + matches + 
+                                          mismatches + cms + non_cms + sum_peaks)^2,
+                                     preProcess = "scale",
+                                     data = hamby173and252_train,
+                                     method = "glm", 
+                                     family = "binomial")
+
+  # Save the model
+  saveRDS(logistic_inters2, "../../../data/logistic_inters2.rds")
+
+} else{
+
+  # Load the model
+  logistic_inters2 <- readRDS("../../../data/logistic_inters2.rds")
+
+}
+```
+
+The output from this model is not shown.
+
+```{r eval = FALSE}
+# Summary of the model
+summary(logistic_inters2)
+```
+
+### LASSO Model
+
+```{r}
+# Fit or load the lasso logistic regression model
+if(!file.exists("../../../data/logistic_lasso.rds")) {
+
+  # Set a seed
+  set.seed(20190312)
+
+  # LASSO logistic regression model
+  logistic_lasso <- cv.glmnet(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
+                              y = hamby173and252_train %>% pull(samesource) %>% as.numeric(),
+                              alpha = 1,
+                              family = "binomial")
+
+  # Tell R to run the upcoming code in parallel
+  # plan(multiprocess)
+
+  # LASSO logistic regression model with possible pairwise interactions
+  # logistic_lasso <- 
+  #   hierNet.logistic.path(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
+  #                         y = hamby173and252_train %>% pull(samesource) %>% as.numeric(), 
+  #                         lamlist = logistic_lasso$lambda)
+
+  # Save the model
+  saveRDS(logistic_lasso, "../../../data/logistic_lasso.rds")
+
+} else {
+
+  # Load the model
+  logistic_lasso <- readRDS("../../../data/logistic_lasso.rds")
+
+}
+```
+
+### Comparing the Models
+
+The results as computed by caret on the training data are shown below for the two logistic regression models.
+The accuracy shows that the models with two way interactions performs better on the training data.
+
+```{r}
+# Results from the models
+data.frame(model = c("mains", "inters2")) %>%
+  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results))
+```
+
+The AICs from the models are shown below. The model with two way interactions performs the best based on AIC.
+
+```{r}
+AIC(logistic_mains$finalModel)
+AIC(logistic_inters2$finalModel)
+```
+
+I also wanted to know how the models perform on the test data.
+The models are used to make predictions on the test data and the MSEs are computed for each model.
+These are shown in the table below.
+The model with main effects only has the smallest MSE.
+I am guessing that the other model is overfitting the data.
+
+```{r}
+data.frame(obs = hamby224_test %>% 
+             pull(samesource) %>% na.omit(),
+           mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
+           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
+  mutate(mains_sqerrs = (obs - as.logical(mains))^2,
+         inters2_sqerrs = (obs - as.logical(inters2))^2) %>%
+  summarise_at(vars(mains_sqerrs, inters2_sqerrs), 
+               function(x) sum(x) / length(x)) %>%
+  rename(mains_mse = mains_sqerrs, inters2_mse = inters2_sqerrs)
+```
+
 # Session Info

### 2019-08-27 journals/03-applying_lime/03-applying_lime.Rmd
finished organizing journals

--- 2019-08-24 journals/03-applying_lime_rtrees/03-applying_lime_rtrees.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      eval = TRUE)
 ```
@@
 
-This journal includes a description of the random forest model `rtrees` fit to the bullet data by Eric and the code for applying lime to `rtrees`.
+This journal includes code for applying lime to various models (`rtrees` and logisitic regression with main effects only).
 
@@
 library(future)
+library(gretchenalbrecht)
 library(randomForest)
@@
 ```
-
-# Data
 
@@
 
-# One Implementation
+# Random Forest
+
+### One Implementation
 
@@
 
-# Multiple Implementations
+### Multiple Implementations
 
@@
 
+# Logistic Regression
+
+```{r}
+# Load the model
+logistic_mains <- readRDS("../../../data/logistic_mains.rds")
+```
+
+### One Implementataion
+
+The functions `lime` and `explain` from the lime package are applied below to the logisitc regression model with only main effects.
+
+```{r}
+# Create or load the lime and explain objects for the main effects logisitic regression model
+if(!file.exists("../../../data/lime_explain_mains.rds")) {
+
+  # Set a seed
+  set.seed(20190226)
+
+  # Apply lime
+  lime_mains <- lime(x = hamby173and252_train %>%
+                       select(rf_features), 
+                     model = logistic_mains)
+
+  # Apply explain
+  explain_mains <- explain(x = hamby224_test %>%
+                             select(rf_features) %>% 
+                             na.omit(), 
+                           explainer = lime_mains, 
+                           n_labels = 1,
+                           n_features = 3)
+
+  # Join the lime and explain objects in a list
+  lime_explain_mains <- list(lime = lime_mains, explain = explain_mains)
+
+  # Save the lime and explain objects
+  saveRDS(lime_explain_mains, "../../../data/lime_explain_mains.rds")
+
+} else {
+
+  # Load the lime and explain objects
+  lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")
+
+}
+```
+
+### Multiple Implementations
+
+The code below applies the LIME algorithm to the main effects logisitic regression model one time for the following different input cases:
+
+- 2 to 6 quantile bins
+- 2 to 6 equally spaced bins
+- 2 to 6 tree based bins with `samesource` as the response variable
+- 2 to 6 tree based bins with `rfscore` as the response variable
+- kernel density estimation
+- normal density approximation
+
+It applies LIME using my function `run_lime` to specify the different input values.
+The outputs from the `lime` function are combined into a list, and the outputs from the `explain` function are combined into dataframe.
+Both are saved as .rds files.
+
+```{r}
+# Apply the run_lime function if the lime results file does not already exist
+if(!file.exists("../../../data/logistic_lime_inputs.rds")) {
+
+  # Specify the input options to use with lime
+  logistic_lime_inputs <- list(bin_continuous = c(rep(TRUE, 20), 
+                                                  rep(FALSE, 2)),
+                               quantile_bins = c(rep(TRUE, 5), 
+                                                 rep(FALSE, 5), 
+                                                 rep(TRUE, 12)),
+                               nbins = c(rep(2:6, 4), 
+                                         rep(4, 2)),
+                               use_density = c(rep(TRUE, 20), TRUE, FALSE),
+                               bin_method = c(rep("quantile_bins", 5),
+                                              rep("equally_spaced", 5),
+                                              rep("tree", 10),
+                                              rep("quantile_bins", 2)),
+                               response = c(rep(NA, 10), 
+                                            rep("samesource", 5), 
+                                            rep("rfscore", 5), 
+                                            rep(NA, 2)))
+
+  # Tell R to run the upcoming code in parallel
+  plan(multiprocess)
+
+  # Apply lime to the full training data with the specified input options
+  logistic_lime_explain <- future_pmap(.l = logistic_lime_inputs,
+             .f = run_lime, # run_lime is one of my helper functions
+             features = rf_features,
+             train = hamby173and252_train,
+             test = hamby224_test %>% 
+               arrange(case) %>% 
+               select(rf_features) %>% 
+               na.omit(),
+             rfmodel = logistic_mains,
+             label = "TRUE",
+             nfeatures = 3,
+             seed = TRUE)
+
+  # Separate the lime and explain function results from the full data
+  logistic_lime <- map(logistic_lime_explain, function(list) list$lime)
+  logistic_explain <- map_df(logistic_lime_explain, function(list) list$explain)
+
+  # Name the items in the lime list
+  names(logistic_lime) <- map_chr(1:22, function(case) 
+      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
+              logistic_lime_inputs$bin_continuous[case],
+              logistic_lime_inputs$quantile_bins[case],
+              logistic_lime_inputs$nbins[case],
+              logistic_lime_inputs$use_density[case],
+              logistic_lime_inputs$bin_method[case],
+              logistic_lime_inputs$response[case]))
+
+  # Turn the lime input options into a dataframe before saving it
+  logistic_lime_inputs <- logistic_lime_inputs %>%
+    unlist() %>%
+    matrix(ncol = length(logistic_lime_inputs), 
+           dimnames = list(NULL, names(logistic_lime_inputs))) %>%
+    as.data.frame() %>%
+    mutate(case = 1:length(logistic_lime_inputs$quantile_bins)) %>%
+    select(case, bin_continuous:response)
+
+  # Save the lime objects
+  saveRDS(logistic_lime_inputs, "../../../data/logistic_lime_inputs.rds")
+  saveRDS(logistic_lime, "../../../data/logistic_lime.rds")
+  saveRDS(logistic_explain, "../../../data/logistic_explain.rds")
+
+} else {
+
+  # Load in the lime objects
+  logistic_lime_inputs <- readRDS("../../../data/logistic_lime_inputs.rds")
+  logistic_lime <- readRDS("../../../data/logistic_lime.rds")
+  logistic_explain <- readRDS("../../../data/logistic_explain.rds")
+
+}
+```
+
+```{r}
+# Create the test_explain combined data if the file does not already exist
+if(!file.exists("../../../data/logistic_test_explain.rds")) {
+
+  # Join the data and the explanations and edit and add additional variables
+  logistic_test_explain <- hamby224_test %>%
+    mutate(case = as.character(case)) %>%
+    full_join(logistic_explain, by = "case") %>%
+    mutate(case = factor(case),
+           feature_desc = factor(feature_desc),
+           feature = factor(feature),
+           nbins = factor(nbins)) %>%
+    arrange(nbins) %>%
+    mutate(nbins = as.numeric(as.character(nbins)),
+           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
+                              sprintf("%.0f quantile", nbins),
+                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
+                                     sprintf("%.0f equally spaced", nbins),
+                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "samesource",
+                                            sprintf("%.0f samesource tree", nbins),
+                                            ifelse(bin_continuous == TRUE & bin_method == "tree" &
+                                              response == "rfscore",
+                                              sprintf("%.0f rfscore tree", nbins),
+                                              ifelse(bin_continuous == FALSE & 
+                                                     use_density == TRUE, 
+                                                     "kernel density", 
+                                                     "normal approximation"))))) %>%
+             fct_relevel("2 quantile", "3 quantile", "4 quantile",
+                         "5 quantile", "6 quantile", "2 equally spaced",
+                         "3 equally spaced", "4 equally spaced",
+                         "5 equally spaced", "6 equally spaced",
+                         "2 samesource tree", "3 samesource tree",
+                         "4 samesource tree", "5 samesource tree",
+                         "6 samesource tree")) %>%
+    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
+                                  bin_continuous == TRUE,
+                                  "quantile",
+                                  ifelse(bin_method == "equally_spaced" & 
+                                         bin_continuous == TRUE,
+                                         "equally spaced", 
+                                         ifelse(bin_method == "tree" & 
+                                                bin_continuous == TRUE & 
+                                                response == "samesource",
+                                                "samesource tree", 
+                                                ifelse(bin_method == "tree" & 
+                                                       bin_continuous == TRUE & 
+                                                       response == "rfscore",
+                                                       "rfscore tree", 
+                                                       ifelse(bin_continuous == FALSE & 
+                                                       use_density == TRUE, 
+                                                       "kernel density", 
+                                                       "normal approximation")))))) %>%
+    mutate(bin_situation = factor(bin_situation))
+
+  # Save the combined test and explain data
+  saveRDS(logistic_test_explain, "../../../data/logistic_test_explain.rds")
+
+} else {
+
+  # Load in the data
+  logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")
+
+}
+```
+
+This code creates and saves a dataset with summaries of the explanations.
+
+```{r}
+# Create the lime comparison data if the file does not already exist
+if(!file.exists("../../../data/logistic_lime_comparisons.rds")) {
+
+  # Create a data frame with the interesting information relating to the different
+  # evaluations of lime and compute the difference and mean between the rf and rr
+  # model predictions
+  logistic_lime_comparisons <- logistic_test_explain %>%
+    select(-data, -prediction) %>%
+    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method, response) %>%
+    slice(1) %>%
+    ungroup() %>%
+    select(situation, bin_situation, bin_method, bin_continuous, quantile_bins, response, 
+           nbins, use_density, set, case, rf_features, rfscore, model_prediction, model_r2) %>%
+    mutate(diff = rfscore - model_prediction,
+           mean = (rfscore + model_prediction) / 2)
+
+  # Save the lime comparison data frame
+  saveRDS(logistic_lime_comparisons, "../../../data/logistic_lime_comparisons.rds")
+
+} else {
+
+  # Load in the lime comparison data frame
+  logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")
+
+}
+```
+
 # Session Info

### 2019-08-27 journals/04-assessing_lime/04-assessing_lime.Rmd
finished organizing journals

@@
 library(lime)
+library(randomForest)
 #library(seriation)
 library(tidyverse)
-library(randomForest)
-
-# Load in the training data 
+
+# Load in the training and testing data 
 hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
-
-# Load in the testing data (Hamby Data 224 Sets 1 and 11)
-hamby224_test <- read.csv("../../../data/hamby224_test.csv") # created in the paper
-
-# Read in the test_explain data
+hamby224_test <- read.csv("../../../data/hamby224_test.csv")
+
+# Read in the lime explanations
 hamby224_test_explain <- readRDS("../../../data/hamby224_test_explain.rds")
-
 hamby224_sensitivity_joined <- readRDS("../../../data/hamby224_sensitivity_joined.rds")
@@
 
-# Visualization Ideas
+# Random Forest
+
+### Bar Charts of Bins
 
@@
 
-# One Implementation
-
-## Accuracy
+### One Implementation
+
+##### Accuracy
 
@@
 
-### Complex versus Simple Model Predictions
+**Complex versus Simple Model Predictions**
 
@@
 
-### Comparing Input Values by MSE and $R^2$
+**Comparing Input Values by MSE and $R^2$**
 
@@
 
-## Consistency
+##### Consistency
 
@@
 
-### Fleiss's Kappa
+**Fleiss's Kappa**
 
@@
 
-### Tile Plots of Features Chosen
+**Tile Plots of Features Chosen**
 
@@
 
-### Attempts at Arranging the Tile Plots
+**Attempts at Arranging the Tile Plots**
 
@@
 
-### Plot of Number of Features Chosen
+**Plot of Number of Features Chosen**
 
@@
 
-# Multiple Implementations
-
-## Accuracy
+### Multiple Implementations
+
+##### Accuracy
 
@@
 
-### Comparing MSE and $R^2$
+**Comparing MSE and $R^2$**
 
@@
 
-## Consistency
-
-### Plots of Number of Features Chosen
+##### Consistency
+
+**Plots of Number of Features Chosen**
 
@@
 
-# Input Rankings
+### Rankings
 
@@
 
-# My LIME
-
-### Random Forest Model
+# Simpler Random Forest
+
+### Model
 
@@
 
-### Visualizations of Data, Model, and LIME
+### Visualizations
 
@@
 
+# Logistic Regression
+
+```{r}
+# Load the model
+logistic_mains <- readRDS("../../../data/logistic_mains.rds")
+
+# Read in the LIME explanations for the logistic regression
+lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")
+
+# Read in the LIME comparisons for the logistic regression
+logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")
+
+# Read in the combined test data and explanations
+logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")
+```
+
+### Visualizing Default LIME
+
+```{r}
+plot_features(lime_explain_mains$explain[1:12,])
+```
+
+```{r}
+coefs <- logistic_mains$finalModel$coefficients %>% round(2)
+```
+
+The logistic regression model is
+
+$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks
+
+where $\hat{p}=P(\mbox{samesource = TRUE})$.
+
+I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.
+
+```{r}
+m = function(x) coefs[2:10] * x
+m(hamby224_test[1,] %>% select(rf_features))
+hamby224_test[1:4,] %>% select(rf_features)
+coefs
+hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
+```
+
+```{r}
+mains_test_explain <- hamby224_test %>%
+  mutate(case = as.character(case)) %>%
+  full_join(lime_explain_mains$explain, by = "case") %>%
+  mutate(case = factor(case),
+         feature = factor(feature))
+```
+
+Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).
+
+```{r}
+mains_test_explain %>%
+  na.omit() %>%
+  arrange(case, desc(abs(feature_weight))) %>%
+  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
+  select(case, set, feature, feature_order) %>%
+  spread(feature_order, feature) %>%
+  arrange(set, first, second, third) %>%
+  mutate(order = 1:n()) %>%
+  gather(feature_order, feature, 3:5) %>%
+  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
+  geom_tile() + 
+  facet_grid(set ~ ., scales = "free_y") +
+  theme_bw() +
+  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
+```
+
+```{r}
+pca_results <- princomp(hamby224_test %>% select(rf_features) %>% na.omit())
+pca_results$loadings
+z1 <- pca_results$scores[,1]
+z2 <- pca_results$scores[,2]
+ggplot(data.frame(z1, z2), aes(x = z1, y = z2)) + 
+  geom_point()
+biplot(pca_results)
+```
+
+### One Implementation
+
+##### Accuracy
+
+**Comparing Input Values by MSE and $R^2$**
+
+In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations.
+I defined the mean squared error as
+  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
+where $n$ is the number of observations in the testing dataset (within a set).
+Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.
+
+```{r}
+# Summarizing lime results
+logistic_lime_results <- logistic_lime_comparisons %>%
+  filter(!is.na(rfscore)) %>%
+  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
+           bin_method, response, set) %>%
+  summarise(mse = (sum(diff^2)) / length(diff),
+            ave_r2 = mean(model_r2)) %>%
+  arrange(set) %>%
+  ungroup()
+```
+
+The plot below shows the mean squared errors for each of the input situations faceted by set.
+There is no one bin type that stands out as performing the best across all or most number of bins.
+This is unlike the results from the random forest model where the tree based bins usually performed the best.
+
+```{r}
+# Plot of MSEs
+logistic_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
+  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
+  geom_point() + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+        legend.position = "none") + 
+  labs(x = "Bin Type", y = "MSE", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+The plot below shows the average $R^2$ value for each of the input situations faceted by set.
+The results are very similar for each set, and the highest $R^2$ values occur for 2 quantile bins.
+With the logistic regression, the equally spaced bins or the quantile bins seem to perform the best in terms of $R^2$ across the different number of bins.
+The rfscore tree based bins are not as good as they were with the random forest model.
+However, all of the $R^2$ values are still very low for all cases.
+
+```{r}
+# Plot of R^2s
+logistic_lime_results %>%
+  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
+  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
+  geom_point() + 
+  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none") + 
+  labs(x = "Bin Type", y = "Average R2", color = "") + 
+  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
+```
+
+##### Consistency
+
+I wanted to look at the consistency of features chosen by lime across the number of bins within different bin types.
+I would like the features chosen to not depend on the number of bins used.
+Otherwise, it will be difficult to know how many bins to use.
+Additionally, it would be nice if the features chosen differed across cases, so that the explanations are based on the locality of the observation and not general across all locations.
+The code below creates a dataset that identifies the order in which the features are chosen by lime.
+
+```{r}
+# Creates a dataset that creates columns of the chosen features by lime from first to third
+logistic_chosen_features <- logistic_test_explain %>%
+  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
+  filter(!is.na(rfscore)) %>%
+  select(set, situation, bin_situation, nbins, case, samesource, feature, feature_weight) %>%
+  mutate(feature_weight_abs = abs(feature_weight)) %>%
+  arrange(situation, case, desc(feature_weight_abs)) %>%
+  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
+  select(-feature_weight, -feature_weight_abs) %>%
+  spread(explainer, feature)
+```
+
+**Fleiss's Kappa**
+
+In order to access consistency, I have decided to compute Fleiss' kappa for each of the bin types.
+Fleiss' kappa is often used to assess the consistency across raters for any number of raters and with nominal ratings.
+It calculates the degree of agreement in classification over that which would be expected by chance.
+A description of how it is computed can be found on the wikipedia site: https://en.wikipedia.org/wiki/Fleiss%27_kappa
+
+I computed kappa for each bin situation separately for the top three features chosen.
+These values are plotted below for each set.
+For the first feature chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the samesource tree based bins.
+
+```{r}
+# Computes and plots the values of kappa
+logistic_chosen_features %>%
+  ungroup() %>%
+  select(-situation) %>%
+  gather(key = chosen, value = feature, first:third) %>%
+  spread(nbins, feature) %>%
+  select(-case) %>%
+  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
+  group_by(set, bin_situation, chosen) %>%
+  summarise(kappa = 
+              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
+                                        ncol = 5))$value) %>%
+  arrange(chosen, set, bin_situation) %>%
+  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
+  geom_point() + 
+  geom_line() +
+  facet_grid( ~ set) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
+  labs(x = "Bin Type", y = "Kappa", color = "Feature")
+```
+
+**Tile Plots of Features Chosen**
+
+I also attempted to plot the features chosen by lime in order to visually assess the consistency.
+This plots are included below.
+The results appear to be different from the random forest results, but it is still possible to se vertical stripes that suggest a global interpretation as opposed to a local interpretation.
+However, the samesource bins do have some horizontal stipes that show what we would like to see.
+It is also interesting to note that the vertical bins are the most pronounced with the rfscore tree.
+This does not suprise me considering that these explanations are for a logistic regression and not the random forest model.
+
+```{r fig.height = 8, fig.width = 8}
+# Plots the top feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(first)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = first)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "First Feature")
+
+# Plots the second feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(second)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = second)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Second Feature")
+
+# Plots the third feature for each case for each bin situation
+logistic_chosen_features %>%
+  group_by(bin_situation, case) %>%
+  mutate(nlevels = length(levels(factor(third)))) %>%
+  ungroup() %>%
+  arrange(bin_situation, set, samesource, desc(nlevels), case) %>%
+  mutate(order = rep(rep(1:length(unique(case)), each = 5, 4))) %>%
+  ggplot(aes(x = nbins, y = order, fill = third)) + 
+  geom_tile() + 
+  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
+  theme_bw() + 
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) + 
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
+  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Third Feature")
+```
+
 # Session Info

### 2019-08-27 journals/06-literature_review/06-literature_review.Rmd
read and took notes on defining locality paper

---
title: "Literature Review"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This journal contains some information on papers relating to LIME.

# Locality Assumption

I'm finding that I am not the only person discovering issues with the local assumption made by LIME.

### Laugel et al (2018)

***Defining Locality for Surrogates in Post-hoc Interpretablity***

This paper is interested in "the importance of defining the right locality, the neighborhood on which a local sur-rogate is trained, in order to approximate accurately the local black-box decision boundary." They propose a new method for sampling around the pertrubations that is not necessarily centered at the prediction of interest.

**Notation**

| notation | definition | 
| -------- | ---------------------- |
| $\mathcal{X}$ | feature space |
| $b:\mathcal{X}\rightarrow\mathcal{Y}$ | black-box classifier | 
| $b(x)$ | prediction made by $b$ where $x\in\mathcal{X}$ | 
| $X$ | training set used to train $b$ |
| $s_x$ | surrogate model that can approximate the local decision boundary of $b$ from which explanations are extracted | 
| $X_{s_x}$ | training set sampled from the feature space | 
| $Y_{s_x}$ | "labels" associated with $X_{s_x}$ and computed as $Y_{s_x}=b(X_{s_x})$ | 
| $\mathcal{V}_x$ | neighborhood around $x$ | 
| $Acc$ | a measure of accuracy (such as the AUC score) |
| $LocalFid(x, s_x)$ | measure of local fidelity of $s_x$ to $b$ | | $r_{fid}$ | radius of the fidelity hypersphere used when determining the neighborhood $\mathcal{V}_x$ |
| $x_{border}$ | the closest decision boundary of $b$ to $x$ (determined as $b(x_{border})\not=b(x)$) |
| $\mathcal{S}$ | hypersphere used to sample training instances in LS procedure | 
| $r_{s_x}$ | radius of $\mathcal{S}$ |

**Steps in a Surrogate Model Explanation**

1. "Sample the feature space to generate a training set"
2. "A surrogate model can be fit using [the training set] in order to approximate the local decision boundary of $b$" (the surrogate can be adjusted for complexity and locality)
3. "Explanations are extracted from the surrogate $s_x$"

**Comments Relating to LIME**

- It appears that they only consider the normal approximation sampling method used by LIME ("Regarding the sampling step (1), a set of instances $X_{s_x}$ is drawn following a normal distribution with the same mean and standard  deviation  as  the  original  feature  space $\mathcal{X}$, independently from the instance $x$ of the prediction $b(x)$ to explain.")
- They also mention that LIME uses ridge regression
- The figure below shows the paper's conceptual depiction of LIME where the linear decision boundaries are based on a label of 0.5. That is
  $$s_x(a)=0.5=\hat{\beta}_0+\hat{\beta}_1\mbox{F0}+\hat{\beta}_2\mbox{F1} \ \ \ \Rightarrow \ \ \  \mbox{F1}=\left(\frac{0.5-\hat{\beta}_0}{\hat{\beta}_2}\right)-\left(\frac{\hat{\beta}_1}{\hat{\beta}_2}\right)\mbox{F0}=\hat{\alpha}_0+\hat{\alpha}_2\mbox{F0}$$
- The figure shows how the decision boundaries are not good local approximations.

![](../../figures/laugel-lime-concept.png)

**Proposed Locality Metric**

The authors propose the following definition for *Local Fidelity* as "the fidelity of $s_x$ to $b$ withing a neighborhood $\mathcal{V}_x$ around $x$ as
  $$LocalFid(x,s_x)=Acc_{x_i\in\mathcal{V}_x}(b(x_i), s_x(x_i))$$
where $Acc$ is a measure of accuracy (such as the AUC score) calculated over instances generated uniformly in $\mathcal{V}_x$." 
*Note: This is similar to the locality metric proposed in the original paper. Again, it is comparing the black-box model prediction to the explainer model prediction.*

They define the $\mathcal{V}_x$ of $x$ using a $l_2$-hypersphere of radius $r_{f_{id}}$ centered on $x$. They say, "This intuitive definition of locality allows us to make the radius $r_{fid}$ of the fidelity hypersphere a proxy for the degree of locality considered. Since the radius value is heavily linked to the dimension and density of the input space $\mathcal{X}$,$r_{fid}$ will be expressed in the rest of the paper as a percentage of the maximum distance between the instances of the dataset andv $x$, whose prediction is being interpreted." <span style="color:blue"> I don't really understand their definition of $r_{fid}$. </span>

You can also compute this value for all observations in a dataset and then compute the mean and standard deviation to get a feel for how the local fidelity compares across the whole dataset.

The figure below shows their locality metric computed for a specific $r_{fid}$ <span style="color:blue"> (they do not explain how they chose this value) </span>. The image shows that LIME has a more difficult time with the local approximation in the regions where a local approximation is more important. They say, "LIME has trouble approximating areas where the local decision boundary of the black-box classifier $b$ differs from the decision boundary approximating the whole dataset (ie.features with a local influence vs. features with a global influence)."

![](../../figures/laugel-locality-metric.png)

**Proposed Local Surrogate (LS) Sampling Method**

The general idea is that instead of sampling across the whole feature space and then weighting the samples, a local region containing the closest decision boundary will be found and samples will only be drawn in this region.

Steps:

1. Detect the closest decision boundary of $b$ by looking for the closest instance $x_{border}$ such that $b(x_{border})\not=b(x)$. (Done using the *GrowingSpheres* (Laugel et al, 2018) algorithm.)
2. Sample training instances uniformly in a hypersphere $\mathcal{S}$ of radius $r_{s_x}$ centered on $x_{border}$. <span style="color:blue"> How will the radius be determined? </span>
3. Fit $s_x$ to this new data, which to learn the closest decision border to $x$.

*Comment: I feel like this will only work well if there is an observation from the other class "close" to the case of interest.*

**References to Look Into**

- Craven and Shavlik (1996): show that "increasing the density of instances is beneficial for the surrogate accuracy"
- Hara and Hayashi (2016): general info on surrogate models

# Other Explainer Models

### LORE (LOcal Rule-based Explanations)

This section contains my notes from reading through the paper introduction [LORE](https://arxiv.org/pdf/1805.10820.pdf).

Same idea as LIME: whole decision boundary is complex, but simpler at a local level

Difference from LIME:

(1) obtain the local data in a different way from LIME using a "genetic algorithm"
(2) better explainations (they claim)

## Method

Notation from the paper:

- $b$ = black blox predictor
- $x$ = specific instance in the data
- $y$ = predicted value from $b$ given $x$
- $c$ = interpretable predictor (a decision tree)
- $N$ = number of neighbor instances of $x$ generated using a "genetic algorithm"
- $r$ = the single rule that is a part of the local explanation
- $\Phi$ = the counterfactual rules that are a part of the local explanation
- $Z$ = generated instances with characteristics close to the ones of $x$ (note that $Z=Z_{=}\cup Z_{\not=}$)
- $Z_=$ = set of instances $z\in Z$ where $b(z)=b(x)$ 
- $Z_{\not=}$ =  set of instances $z\in Z$ where $b(z)\not=b(x)$

General Idea:

- generate neighboring instances ($Z$) to $x$ using a genetic algorithm
- fit a tree to $Z$ called $c$
- obtain the local explainer $r$ by extracting the path from the decision tree $c$ that leads to $y$ with the same conditions as $x$
- obtain the counterfactual rules $\Phi$ using the other paths from the decision tree $c$

Genetic Algorithm: Makes use of fitness functions

Fitness function = A fitness function is a particular type of objective function that is used to summarise, as a single figure of merit, how close a given design solution is to achieving the set aims. Fitness functions are used in genetic programming and genetic algorithms to guide simulations towards optimal design solutions. (from Wikipedia)

# Session Info

```{r}
sessionInfo()
```

### 2019-08-27 README.Rmd
updated to do list

@@
     - Can you re-explain your vision with the minipage format?
-    - I cannot get LIME to work on my computer anymore...
+    - Sometimes LIME doesn't work on my computer anymore...
+    - Explain the details of the locality paper to Heike (ask about the radius definition)
 - Internship
@@
 
-- finish reading new paper
-- add generalized R2 values to plots
-- code up Laugel et al's work
-- point out differences and similarities from the other paper (such as normal sampling)
-- keep the LIME procedure at a higher level in the paper
-- change to computing the $\mathcal{L}$ metric from the paper
-- add figure descriptions in both caption and text
 - go back through LIME procedure and update with new understanding (such as d' can be larger than d)
 - add an assert_that statement in the code to check if the LIME package is changing
+- point out differences and similarities from the other paper (such as normal sampling)
+- code up Laugel et al's work
 - read through papers giving an overview of the current explanation methods
@@
 - `05-iris_comparison`: applying LIME to a random forest fit to the iris data
-- `06-other_explainers`: trying out other model explainers
+- `06-literature_review`: notes on papers relating to LIME
 - `07-computation_issues`: documentation of some of the computation issues I ran into during the project

### 2019-08-28 README.Rmd
added a talking point
added to talking points
updated to do list

@@
 - Paper
+    - I reorganized my work into three repos and consolidated the journals
     - Can you re-explain your vision with the minipage format?
@@
     - Explain the details of the locality paper to Heike (ask about the radius definition)
+    - Should I make the LIME procedure more general?
 - Internship
     - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
+    - See list of activites for Fall 2019
 - Graphics Group
@@
     - Are you still available to talk next week?
+    - Cookies for tomorrow?
 

### 2019-09-03 README.Rmd
worked on detailing the functions in the lime r package

@@
     - Sometimes LIME doesn't work on my computer anymore...
-    - Explain the details of the locality paper to Heike (ask about the radius definition)
-    - Should I make the LIME procedure more general?
-- Internship
-    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
-    - See list of activites for Fall 2019
+    - Read the locality paper in detail and added to journal
+    - Updated LIME procedure and R package function notes
 - Graphics Group
-    - show updated schedule
+    - title and abstract
+    - preview image
     - email list (should I be added as an admin?)
-    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
-    - How to include an image in the preview of a post in blogdown?
-    - Are you still available to talk next week?
-    - Cookies for tomorrow?
+    - treats?
 
@@
 - read through papers giving an overview of the current explanation methods
+
+**Oral Prelim**
+
+- schedule
+    - can be anytime during the semester 
+    - just needs to be 6 months before final defense
+    - schedule when it gets closer to the time 
+    - schedule 3 or 4 weeks in advance
+    - send prelim materials to committee 2 weeks in advance
+- materials
+    - Chapter 0 (complete)
+        - lit review
+        - research statement: "this is what this thesis will investigate"
+    - Chatper 1 (as close to submission as possible)
+        - LIME and shortcomings
+        - Dr. Dixon likes to give feedback before submission
+    - Chapter 2 (draft)
+        - Diagnostics for RF
+    - Chapter 3 (some idea)
+        - Diagnostics for Bayesian Neural Networks
+        - Could switch to chapter 2 if more complete
+    - Conclusion (not needed)
 

### 2019-09-03 journals/02-understanding_lime/02-understanding_lime.Rmd
worked on detailing the functions in the lime r package

--- 2019-08-20 journals/04-lime_algorithm_and_proposed_methods/04-lime_algorithm_and_proposed_methods.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
+knitr::opts_chunk$set(echo = TRUE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      eval = TRUE)
 ```
 
-# Overview
+This journal contains information from the work I did to understand LIME.
+This includes a description of the LIME procedure from the original paper, a description of the functions in the in the *lime* R package, information about the Python *lime* package, and ideas for new binning methods.
 
-This journal contains a description of the LIME procedure from the original paper, my write-up of the LIME algorithm used in the R package, and ideas for different binning methods that may be better than the ones currently implemented in the R package.
+```{r packages and sourced functions}
+# Load packages
+library(assertthat)
+library(cowplot)
+library(furrr)
+library(future)
+library(glmnet)
+library(gower)
+library(lime)
+library(randomForest)
+library(tidyverse)
 
-```{r}
 # Source functions
@@
 |
-| $x'\in\{0,1\}^{d'}$ | A binary vector for interpretable representation (where interpretable explanations are defined as "use a representation that is understandable by humans") | Varies based on the simulation method used - note that $1\le d' \le d$ since it is possible that feature selection may be performed to choose a smaller set of variables than originally in $x$ (One example: vector of indicator variables that indicate whether the observed value falls in the same bin as the instance being explained e.g.
+| $x'\in\{0,1\}^{d'}$ | A binary vector for interpretable representation (where interpretable explanations are defined as "use a representation that is understandable by humans") | Varies based on the simulation method used.
+It is unclear to us how the size of $d$ compares to $d'$.
+We think they left it vague, so that it could fit any situation ($d<d'$, $d=d'$, or $d>d'$) (One example of converting to an interpretable representation would be a conversion to a vector of indicator variables that indicate whether the observed value falls in the same bin as the instance being explained e.g.
 $x'_i = I[x_i\in \mbox{same variable } i \mbox{ bin as the instance being explained}]$) | In our example, this is the random forest model.
@@
 
+# Concept Visualizations
+
+The images in this section were created using simulated data that I knew had a local trend around the point of interest.
+I consider both a linear regression and a ridge regression as the explainer model.
+
+### Data and Model
+
+This code generates the data and predictions from a hypothetical complex model.
+
+```{r}
+# Generate features and predictions from a hypothetical complex model
+set.seed(20190624)
+lime_data <- data.frame(feature1 = sort(runif(250, 0, 1)),
+                        feature2 = sample(x = 1:250, 
+                                          size = 250, 
+                                          replace = FALSE)) %>%
+  mutate(prediction = if_else(feature1 >= 0 & feature1 < 0.1, 
+                              (0.3 * feature1) + rnorm(n(), 0, 0.01), 
+                      if_else(feature1 >= 0.1 & feature1 < 0.3, 
+                              rbeta(n(), 1, 0.5), 
+                      if_else(feature1 >= 0.3 & feature1 < 0.5, 
+                              sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                      if_else(feature1 >= 0.5 & feature1 < 0.8, 
+                              -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                      if_else(feature1 >= 0.8 & feature1 < 0.9, 
+                              0.5 + runif(n(), -0.5, 0.5), 
+                              0.5 + rnorm(n(), 0, 0.3)))))))
+
+# Specify a prediction of interest
+prediction_of_interest <- data.frame(feature1 = 0.07, 
+                                     feature2 = 200,
+                                     prediction = 0.05, 
+                                     color = factor("Prediction of Interest"))
+
+# Compute the distance between the prediction of interest and 
+# all other observations
+lime_data$distance <- (1 - gower_dist(x = prediction_of_interest, 
+                                      y = lime_data))^20
+```
+
+### Linear Regression Explainer
+
+These visualizations are based on a weighted linear regression model used as the explainer.
+
+```{r}
+# Fit the interpretable explainer model (weighted linear regression)
+linear_explainer <- lm(formula = prediction ~ feature1 + feature2, 
+                       data = lime_data, 
+                       weights = distance)
+
+# Extract the coefficients from the explainer
+linear_b0 <- coef(linear_explainer)[[1]]
+linear_b1 <- coef(linear_explainer)[[2]]
+linear_b2 <- coef(linear_explainer)[[3]]
+
+# Predictions versus feature 1
+linear_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 +
+                linear_b2*prediction_of_interest$feature2, 
+              slope = linear_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Predictions versus feature 1
+linear_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = linear_b0 + 
+                linear_b1*prediction_of_interest$feature1,
+              slope = linear_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Plot that creates a size legend
+size_legend_plot <- lime_data %>%
+  gather(key = feature, value = value, 1:2) %>%
+  ggplot(mapping = aes(x = value, 
+                       y = prediction,
+                       size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) +
+  labs(size = "Weight") +
+  theme_linedraw(base_family = "Times") +
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Extract the legend
+size_legend <- get_legend(size_legend_plot)
+
+# Join the two feature plots
+lime_linear_plots <- plot_grid(linear_plot_feature1, 
+                               linear_plot_feature2, 
+                               size_legend,
+                               ncol = 3, 
+                               rel_widths = c(0.4, 0.4, 0.1))
+
+# Create a plot to extract a legend for the prediction of interest
+lime_legend_plot <- ggplot(data = prediction_of_interest, 
+                           mapping = aes(x = feature1, 
+                                         y = prediction, 
+                                         fill = color)) +
+  geom_point(size = 5, shape = 23) +
+  scale_fill_manual(values = c("#EFB084")) +
+  theme_classic(base_family = "Times") +
+  labs(fill = "") +
+  theme(legend.position = "bottom")
+
+# Extract the legend
+lime_legend <- get_legend(lime_legend_plot)
+
+# Join the title, plots, legend, and caption into one figure
+lime_linear_concept <- plot_grid(lime_linear_plots, lime_legend,
+                         ncol = 1,
+                         rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is doing a good job of capturing the local trend.
+
+```{r}
+# View the plot
+lime_linear_concept
+```
+
+### Ridge Regression Explainer
+
+```{r}
+# Fits the explainer model (weighted ridge regression)
+ridge_explainer <- glmnet(x = lime_data %>% 
+                            select(feature1, feature2) %>%
+                            as.matrix(), 
+                          y = lime_data %>% pull(prediction),
+                          weights = lime_data$distance,
+                          family = "gaussian", 
+                          alpha = 0, 
+                          lambda = 1, 
+                          standardize = FALSE)
+
+# Extract the coefficients from the explainer
+ridge_b0 <- ridge_explainer$a0[[1]]
+ridge_b1 <- ridge_explainer$beta[1,1]
+ridge_b2 <- ridge_explainer$beta[2,1]
+
+# Predictions versus feature 1
+ridge_plot_feature1 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature1, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 +
+                ridge_b2*prediction_of_interest$feature2, 
+              slope = ridge_b1, 
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature1, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 1", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Predictions versus feature 2
+ridge_plot_feature2 <- ggplot(data = lime_data,
+                        mapping = aes(x = feature2, 
+                                      y = prediction, 
+                                      size = distance)) + 
+  geom_point(color = "grey30",
+             alpha = 0.75) + 
+  geom_abline(intercept = ridge_b0 + 
+                ridge_b1*prediction_of_interest$feature1,
+              slope = ridge_b2,
+              size = 1) +
+  geom_point(data = prediction_of_interest,
+             mapping = aes(x = feature2, y = prediction),
+             fill = "#EFB084",
+             color = "black",
+             size = 5, 
+             shape = 23) +
+  theme_linedraw(base_family = "Times") +
+  labs(x = "Feature 2", 
+       y = "Black-Box Prediction") + 
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
+
+# Join the two feature plots
+lime_ridge_plots <- plot_grid(ridge_plot_feature1, 
+                              ridge_plot_feature2, 
+                              size_legend,
+                              ncol = 3,
+                              rel_widths = c(0.4, 0.4, 0.1))
+
+# Join the title, plots, legend, and caption into one figure
+lime_ridge_concept <- plot_grid(lime_ridge_plots, 
+                                lime_legend,
+                                ncol = 1,
+                                rel_heights = c(0.9, 0.1))
+```
+
+This example shows that the explainer model is **not** doing a good job of capturing the local trend.
+
+```{r}
+# Preview the plot
+lime_ridge_concept
+```
+
 # R Package
 
-### Procedure (Draft)
+The version of the `lime` packge that is considered here is `r packageVersion("lime")` (version when I first wrote this section: 0.5.0).
+I am only considering the `data.frame` versions of the functions.
 
-I wrote this up to start thinking about how to describe the procedure that the `lime` R package uses to implement the LIME algorithm.
-It needs a lot of work, but it is a start.
-The final version of this will end up in the technical stats paper critiquing LIME.
-The version in the firearm examiner's paper will be much simpler...
+### `lime` function
 
-The steps below explain the procedure that the R package is using to apply the LIME algorithm to the bullet matching predictions on the Hamby 224 clone dataset made by the random forest model from Hare.
-For simplicity, the steps are described as what happens to one case in the test data.
-Thus, the steps (2) through (7) are repeated for each observation in the testing dataset.
+**Inputs**
 
-Let
-  $$Y_{jk} = \begin{cases} 
-  1 & \mbox{ if bullets } j \mbox{ and } k \mbox{ were fired from the same gun barrel }\\
-  0 & \mbox{otherwise}
-  \end{cases}$$
-be the response variable in the training dataset, and $X_1,...,X_9$ correspond to the nine features in the training dataset. Let $X'_1,...,X'_9$ be the
+- `x`: The training data used to fit the model to be explained
+- `model`: The model to explain.
+- `preprocess = NULL`: Function to transform a character vector to the format expected from the model.
+- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations.
+If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to.
+- `n_bins = 4`: The number of bins to use if `bin_continuous = TRUE`.
+- `quantile_bins = TRUE`: Should quantile bins be used if `bin_continuous = TRUE? (Otherwise, equally spaced bins will be used.)
+- `use_density = TRUE`: This option is only considered if `bin_continuous` is set to `FALSE`.
+In that situation, if `use_density = TRUE`, then the continuous data will be sampled using kernel density estimation.
+Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.
 
-1. Distributions for each of the features in the training data are obtained. 
-    + The method that `lime` uses to obtain the distribution differs based on the feature type.
-All of the features in the Hamby datasets are numeric.
-For numeric features, the default option in `lime` (`quantile_bins = TRUE`) computes the quantiles of each feature based on the number of bins selected.
-The default number of bins is 4 (`n_bins = 4`).
+**Procedure**
 
-2. Many ($n$) samples from each of the feature distributions are drawn.
-     + To do this, `lime` has several options (mostly quoted from `lime` package for now):
-      * bin\_continuous = TRUE should continuous variables be binned?
-      * quantile\_bins = TRUE should the ins for n\_bins be based on quantiles or spread evenly
-      * n\_bins = 4 number of bins if bin\_continuous is TRUE
-      * use\_density = TRUE if bin\_continuous is FALSE, should continuous data be sampled using kernel density estimation (if not, then will assume normal for continuous variable)
+1. If `preprocess` is NULL, then set it to the identity function. Either way, check to make sure that it is a function.
+2. Create an explainer object.
+3. Determine the type of each of the features (e.g. integer, numeric, etc.). If any of the variables are constants, a warning is returned. If the feature type is unknown, an error is returned.
+4.
+Create bins for numeric and intger type variables.
+If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles.
+Otherwise, `n_bins` equally spaced bins are created.
+If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning.
+Using standard binning instead.") and $n_bins$ equally spaced bins are returned.
+5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
+    - Integer: nothing
+    - Numeric: If `bin_continuous`, then determine the
+    proportion of observations in each bin. If
+    `use_density=TRUE`, then kernel a kernel density
+    approximation is used to estimate the distribution.
+    Otherwise, the mean and standard deviation of each 
+    of the features is computed.
+    - Character: nothing
+    - Logical: nothing
+    - Factor: Determine the proportion in each category.
+6. Assign some attributes to the explainer object, and return the explainer object.
+
+```{r lime function}
+# Print the lime function (and check to see if there have been any changes)
+if(!file.exists("../../../data/lime_functions/lime_v0.5.0.rds")) {
+  saveRDS(object = getAnywhere(lime.data.frame),
+          file = "../../../data/lime_functions/lime_v0.5.0.rds")
+} else {
+  lime_v0.5.0 <- readRDS("../../../data/lime_functions/lime_v0.5.0.rds")  
+  if(assert_that(are_equal(lime_v0.5.0, getAnywhere(lime.data.frame)))){
+    getAnywhere(lime.data.frame)
+  } 
+}
+```
+
+### `explain` function
+
+**Inputs**
+
+- `x`: The new observations to explain (with the same format as used when creating the explainer).
+- `explainer`: This is the object output from the `lime` function.
+- `labels = NULL`: The specific labels (classes) to explain in case the model is a classifier. For classifiers either this or `n_labels` must be given.
+- `n_labels = NULL`: The number of labels to explain. If this is given for classifiers, the top `n_label` classes will be explained.
+- `n_features`: The number of features to use for each explanation. (i.e. The number of features to select during feature selection.)
+- `n_permutations = 5000`: The number of perturbations generated for each feature.
+- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified. 
+    - `auto`: If `n_features` $\le 6$, uses `forward_selection`.
+    Otherwise, `highest_weights` is used. 
+    - `none`: Use all features for the explanation. Not advised
+    unless you have very few features.
+    - `forward_selection`: Add one feature at a time until
+    `n_features` is reached, based on quality of a ridge 
+    regression model.
+    - `highest_weights`: The `n_features` with highest absolute
+    weight in a ridge regression fit of the complex model outcome
+    are chosen.
+    - `lasso_path`: Fit a lasso model and choose the `n_features`
+    whose lars path converge to zero the latest.
+    - `tree`: Fit a tree to select `n_features` (which needs to be
+    a power of 2). It requires last version of *XGBoost*.
+- `dist_fun = 'gower'`: The distance function to use for calculating the distance from the observation to the permutations.
+If `dist_fun = 'gower'` (default) it will use `gower::gower_dist()`.
+Otherwise it will be forwarded to `stats::dist()`.
+- `kernel_width = NULL`:The width of the exponential kernel that will be used to convert the distance to a similarity in case `dist_fun != 'gower'`.
+- `gower_pow = 1`: A modifier for gower distance. The calculated distance will be raised to the power of this value.
+
+**Procedure**
+
+1. Check to make sure that the `explainer` is an object output from the `lime` function. 
+2.
+Determine the type of the model that is contained within the explainer function (using the [`model_type`](#model_type) function), and determine the type of output that should be produced by `explain` based on the model type (using the [`output_type`](#output_type) function).
+3.
+If the model type is regression, check to make sure both `labels` and `n_labels` are set to NULL.
+Otherwsie, return a warning saying that labels and n_labels are ignored with explaining regression models.
+Then set `n_lables` to 1 and `labels` to NULL.
+4. Check to make sure that only `labels` or `n_labels` is specified and the other is NULL. If not, output a warning saying that you must choose between one or the other.
+5. Return an error if `n_features` or `n_permutations` are not specified as counts.
+6.
+If the kernel width has not been specified, then compute it as the square root of the number of columns of the testing dataframe multiplied by 0.75.
+Then create a kernel function that will be used to weight the perturbations based on the specified kernel width using the function [`exp_kernel`](#exp_kernel).
+The formula used by `exp_kernel` is
+  $$f(x, w)=\sqrt{\exp\left(\frac{-(x^2)}{w}\right)}$$
+where $w$ is the kernel width.
+7.
+Makes use of the [`permute_cases`](#permute_cases) function for data frames in the lime package.
+This is the function that creates the perturbations.
+One perturnabiton is created for each of the `n_permuations` specified.
 
@@
 
-### Function Inputs
+```{r explain function}
+# Print the explain function (and check to see if there have been any changes)
+if(!file.exists("../../../data/lime_functions/explain_v0.5.0.rds")) {
+  saveRDS(object = getAnywhere(explain.data.frame),
+          file = "../../../data/lime_functions/explain_v0.5.0.rds")
+} else {
+  explain_v0.5.0 <- readRDS("../../../data/lime_functions/explain_v0.5.0.rds")  
+  if(assert_that(are_equal(explain_v0.5.0, getAnywhere(explain.data.frame)))){
+    getAnywhere(explain.data.frame)
+  } 
+}
+```
 
-The default input settings for the `lime` and `explain` functions in the lime package are described below.
+### `model_type` helper {#model_type}
 
-##### `lime` function
+The *lime* package provides a variety of functions for extracting the model type from the complex model to be explained.
+These are shown below.
+Here is information from the package documentation about models supported by *lime*.
 
-The default settings for the `lime` function are as follows.
+> Out of the box, lime supports the following model objects:
+>
+> - train from caret
+> - WrappedModel from mlr
+> - xgb.Booster from xgboost
+> - H2OModel from h2o
+> - keras.engine.training.Model from keras
+> - lda from MASS (used for low-dependency examples)
+>
+> If your model is not one of the above you'll need to implement support yourself.
+If the model has a predict interface mimicking that of predict.train() from caret, it will be enough to wrap your model in as_classifier()/as_regressor() to gain support.
+Otherwise you'll need need to implement a predict_model() method and potentially a model_type() method (if the latter is omitted the model should be wrapped in as_classifier()/as_regressor(), everytime it is used in lime()).
 
-- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations.
-If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to.
-- `bins = 4`: The number of bins to divide the continuous variables into. The default is 4 bins.
-- `quantile_bins = TRUE`: If set to `TRUE`, the bins will be be based on `n_bins` quantiles. Otherwise, the bins will be spread evenly over the range of the training data.
-- `use_density = TRUE`: If `bin_continuous` is set to `FALSE` and this is set to `TRUE`, then the continuous data will be sampled using kernel density estimation.
-Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.
+```{r model type}
+getAnywhere(model_type)
+getAnywhere(model_type.default)
+getAnywhere(model_type.lime_classifier)
+getAnywhere(model_type.lime_regressor)
+getAnywhere(model_type.train)
+getAnywhere(model_type.model_fit)
+getAnywhere(model_type.WrappedModel)
+getAnywhere(model_type.xgb.Booster)
+getAnywhere(model_type.lda)
+getAnywhere(model_type.keras.engine.training.Model)
+getAnywhere(model_type.H2OModel)
+getAnywhere(model_type.ranger)
+```
 
-##### `explain` function
+### `output_type` helper {#output_type}
 
-For our research project, the number of labels (`n_labels`) for the response variable will be set to 1 and the number of features to include in the explanations (`n_features`) will be set to 2.
-The default values for the other options are as follows.
+```{r output type}
+getAnywhere(output_type)
+```
 
-- `n_permutations = 5000`: The number of perturbations generated for each feature.
-- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified.
-This uses forward selection if $m\le 6$ and otherwise highest weights.
-The other feature selection options are as follows.
-    - `none`: Use all features for the explanation. Not advised unless you have very few features.
-    - `forward selection`: Features are added one by one based on their improvements to a ridge regression fit of the complex model outcome.
-    - `highest weights`: The m features with highest absolute weight in a ridge regression fit of the complex model outcome are chosen.
-    - `lasso`: The m features that are least prone to shrinkage based on the regularization path of a lasso fit of the complex model outcome is chosen.
-    - `tree`: A tree is fitted with log2(m) splits, to use at max m features. It may possibly select less.
-- `dist_fun = 'gower'`: The distance function to be used for determining how close a perturbation is to the test point.
-- `kernel_width = NULL`: If `dist_fun` is not set to `gower`, then this is the kernel width that will be used in the distance function.
+### `exp_kernel` helper {#exp_kernel}
+
+```{r exp_kernel}
+# Print the exp_kernel function (and check to see if there have been any changes)
+if(!file.exists("../../../data/lime_functions/exp_kernel_v0.5.0.rds")) {
+  saveRDS(object = getAnywhere(exp_kernel),
+          file = "../../../data/lime_functions/exp_kernel_v0.5.0.rds")
+  getAnywhere(exp_kernel)
+} else {
+  exp_kernel_v0.5.0 <- readRDS("../../../data/lime_functions/exp_kernel_v0.5.0.rds")  
+  if(assert_that(are_equal(exp_kernel_v0.5.0, getAnywhere(exp_kernel)))){
+    getAnywhere(exp_kernel)
+  } 
+}
+```
+
+### `permute_cases` helper {#permute_cases}
+
+**Procedure**
+
+1. Compute the number of rows as the number of predictions to be explained times the number of permutations.
+2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
+    - numeric variable and the feature distribution contains all NAs: the observed cases get repeated `n_permutations` times
+    - numeric variable and `bin_continuous = TRUE`: 
+    sample from 1:number of bin cuts with replacement for
+    nrows times using the probability from the variable 
+    distribution sample from a uniform(0,1) distribution
+    and then multiply by the difference in bin cuts of
+    the appropriate bin and add the quantile associated
+    with the bin
+    - numeric variable, `bin_continuous = FALSE`, and `use_density = TRUE`: 
+    - numeric variable, `bin_continuous = FALSE`, and `use_density = FALSE`: randomly sample from a normal distribution, multiply by the sd of the feature distribution, and add the mean 
+    - character variable: sample from the names of the levels in the variable based on the probability of the variable distribution
+    - logical variable: 
+    - factor variable: sample from the names of the levels in the variable based on the probability of the variable distribution and convert the samples to factors 
+    - date: 
+    - integer variable: round the permutations to the nearest integer
+3. Give the permutations the same name as the variables
+4. Add the cases back into the data frame of the permutations
+5. Return the permutations.
+
+```{r}
+if(!file.exists("../../../data/lime_functions/permute_cases_v0.5.0.rds")) {
+  saveRDS(object = getAnywhere(permute_cases.data.frame),
+          file = "../../../data/lime_functions/permute_cases_v0.5.0.rds")
+  getAnywhere(permute_cases.data.frame)
+} else {
+  permute_cases_v0.5.0 <- readRDS("../../../data/lime_functions/permute_cases_v0.5.0.rds")  
+  if(assert_that(are_equal(permute_cases_v0.5.0, getAnywhere(permute_cases.data.frame)))){
+    getAnywhere(permute_cases.data.frame)
+  } 
+}
+```
 

### 2019-09-04 README.Rmd
updates after meeting

@@
 
-- Paper
-    - I reorganized my work into three repos and consolidated the journals
-    - Can you re-explain your vision with the minipage format?
-    - Sometimes LIME doesn't work on my computer anymore...
-    - Read the locality paper in detail and added to journal
-    - Updated LIME procedure and R package function notes
 - Graphics Group
-    - title and abstract
-    - preview image
-    - email list (should I be added as an admin?)
-    - treats?
+    - email list
 
@@
 - read through papers giving an overview of the current explanation methods
+- check to see if there a paper showing how ridge regression is affected by sample size changes
+- try fitting the ridge regression with the observed data only to see how it compares to the model fit with the ridge regression
 

### 2019-09-05 journals/02-understanding_lime/02-understanding_lime.Rmd
worked on LIME procedure

@@
     toc_float: true
+    theme: cerulean
+    highlight: textmate
 ---
@@
 
-# Original Paper
+# Original Paper {.tabset}
 
-Here, I have copied in the section of the original paper that describes LIME and put it in a more orgainzed format.
+Here, I have copied in the section of the original paper that describes LIME and put it in a more organized format.
 I have also added in some comments explaining my interpretation of the text and questions where I am not sure what is meant by the text.
@@
 | $\mathcal{Z}$ | Data set...of perturbed samples with the associated labels | This is the full simulated dataset of perturbations and complex model predictions. |
-| $\xi(x)$ | The explanation produced by LIME...$\underset{g∈G}{\arg\min} \ \mathcal{L}(f,g,\pi_x) + \Omega(g)$ | The output from the explanation model which is found through an optimiation process. |
+| $\xi(x)$ | The explanation produced by LIME...$\underset{g∈G}{\arg\min} \ \mathcal{L}(f,g,\pi_x) + \Omega(g)$ | The output from the explanation model which is found through an optimization process.
+|
 
@@
   $$\pi_x(z)=exp(−D(x,z)^2/\sigma^2)$$ 
-be an exponential kernel defined on some distance function $D$ (e.g. cosine distance for text, $L2$ distancef or images) with width $\sigma$.
+be an exponential kernel defined on some distance function $D$ (e.g. cosine distance for text, $L2$ distance or images) with width $\sigma$.
   $$\mathcal{L}(f,g,\pi_x)=\sum_{z, z'\in\mathcal{Z}}\pi_x(z)\left(f(z)-g(z')\right)^2$$
@@
 
-The version of the `lime` packge that is considered here is `r packageVersion("lime")` (version when I first wrote this section: 0.5.0).
+This section describes the procedure the the *lime* R package implements.
+The version of the `lime` package that is considered here is `r packageVersion("lime")`.
+The version considered when I first wrote this section was 0.5.0.
 I am only considering the `data.frame` versions of the functions.
+In order to determine if any of the functions that I am interested in have changed since I wrote the description, I created the function below that allows me to check if anything has changed in the function.
+If nothing has changed, it then prints the function.
 
-### `lime` function
+```{r}
+# Function for checking for changes in a function and printing the current version
+func_check <- function(func_name, version){
 
-**Inputs**
+  # Specify the path to where the function will be stored
+  file_path <- paste0("../../../data/lime_functions/", func_name, "_v", version, ".rds")
+
+  # Save the file if it does not exist, otherwise load the function and check 
+  # to make sure they have been no changes
+  if(!file.exists(file_path)) {
+    saveRDS(object = getAnywhere(func_name), file = file_path)
+  } else {
+    saved_func <- readRDS(file_path)
+    assertthat::assert_that(assertthat::are_equal(saved_func,
+                                                  getAnywhere(func_name)))
+  }
+
+  # Print the function
+  getAnywhere(func_name)
+
+}
+```
+
+## Main Functions
+
+### `lime.data.frame` {.tabset}
+
+#### Inputs
 
@@
 
-**Procedure**
+#### Procedure
 
@@
 4.
-Create bins for numeric and intger type variables.
+Create bins for numeric and inter type variables.
 If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles.
@@
 If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning.
-Using standard binning instead.") and $n_bins$ equally spaced bins are returned.
+Using standard binning instead.") and `n_bins` equally spaced bins are returned.
 5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
@@
 
-```{r lime function}
+#### Function
+
+```{r}
 # Print the lime function (and check to see if there have been any changes)
-if(!file.exists("../../../data/lime_functions/lime_v0.5.0.rds")) {
-  saveRDS(object = getAnywhere(lime.data.frame),
-          file = "../../../data/lime_functions/lime_v0.5.0.rds")
-} else {
-  lime_v0.5.0 <- readRDS("../../../data/lime_functions/lime_v0.5.0.rds")  
-  if(assert_that(are_equal(lime_v0.5.0, getAnywhere(lime.data.frame)))){
-    getAnywhere(lime.data.frame)
-  } 
-}
+func_check("lime.data.frame", "0.5.0")
 ```
 
-### `explain` function
+### `explain.data.frame` {.tabset}
 
-**Inputs**
+#### Inputs
 
@@
 
-**Procedure**
+#### Procedure
 
-1. Check to make sure that the `explainer` is an object output from the `lime` function. 
+1. Check to make sure that `explainer` is an object output from the `lime` function.
+
+        assertthat::assert_that(is.data_frame_explainer(explainer))
+
 2.
 Determine the type of the model that is contained within the explainer function (using the [`model_type`](#model_type) function), and determine the type of output that should be produced by `explain` based on the model type (using the [`output_type`](#output_type) function).
+
+        m_type <- model_type(explainer)  
+        o_type <- output_type(explainer)
+
 3.
 If the model type is regression, check to make sure both `labels` and `n_labels` are set to NULL.
-Otherwsie, return a warning saying that labels and n_labels are ignored with explaining regression models.
+Otherwise, return a warning saying that labels and n_labels are ignored with explaining regression models.
 Then set `n_lables` to 1 and `labels` to NULL.
+
+        if (m_type == "regression") {
+          if (!is.null(labels) || !is.null(n_labels)) {
+            warning("\"labels\" and \"n_labels\" arguments are ignored 
+              when explaining regression models")
+          }
+          n_labels <- 1
+          labels <- NULL
+        }
+
 4. Check to make sure that only `labels` or `n_labels` is specified and the other is NULL. If not, output a warning saying that you must choose between one or the other.
+
+        assert_that(is.null(labels) + is.null(n_labels) == 1, 
+          msg = "You need to choose between labels and n_labels parameters.")
+
 5. Return an error if `n_features` or `n_permutations` are not specified as counts.
+
+        assert_that(is.count(n_features))
+        assert_that(is.count(n_permutations))
+
 6.
@@
 where $w$ is the kernel width.
+
+        if (is.null(kernel_width)) {
+          kernel_width <- sqrt(ncol(x)) * 0.75
+        }
+        kernel <- exp_kernel(kernel_width)
+
 7.
@@
 This is the function that creates the perturbations.
-One perturnabiton is created for each of the `n_permuations` specified.
+One perturbation is created for each of the `n_permuations` specified.
 
-3. Predictions for the testing data using the random forest model are computed.
+        case_perm <- permute_cases(x, n_permutations, explainer$feature_distribution, 
+          explainer$bin_continuous, explainer$bin_cuts, explainer$use_density)
+
+---------
+
+- Predictions for the testing data using the random forest model are computed.
      + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
@@
 
-4. Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
+- Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
     + The way that the similarity score is computed depends on the type of feature.
@@
 
-5. Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
+- Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
     + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
@@
 
-6.
-A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
+- A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
 If the response is categorical, the user can select how many categories and which categories they want to explain.
@@
   $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-7. The feature weights are extracted and used as the explanations.
+- The feature weights are extracted and used as the explanations.
 
@@
 
-```{r explain function}
+#### Function
+
+```{r}
 # Print the explain function (and check to see if there have been any changes)
-if(!file.exists("../../../data/lime_functions/explain_v0.5.0.rds")) {
-  saveRDS(object = getAnywhere(explain.data.frame),
-          file = "../../../data/lime_functions/explain_v0.5.0.rds")
-} else {
-  explain_v0.5.0 <- readRDS("../../../data/lime_functions/explain_v0.5.0.rds")  
-  if(assert_that(are_equal(explain_v0.5.0, getAnywhere(explain.data.frame)))){
-    getAnywhere(explain.data.frame)
-  } 
-}
+func_check("explain.data.frame", "0.5.0")
 ```
 
-### `model_type` helper {#model_type}
+## Helper Functions
+
+### `model_type` {#model_type .tabset}
+
+#### Info
 
 The *lime* package provides a variety of functions for extracting the model type from the complex model to be explained.
-These are shown below.
+The function `model_type` is an overarching function that leads to the specific functions for determining the model type.
+The specific functions vary based on what package was used to fit the model.
+
 Here is information from the package documentation about models supported by *lime*.
 
-> Out of the box, lime supports the following model objects:
->
-> - train from caret
-> - WrappedModel from mlr
-> - xgb.Booster from xgboost
-> - H2OModel from h2o
-> - keras.engine.training.Model from keras
-> - lda from MASS (used for low-dependency examples)
->
-> If your model is not one of the above you'll need to implement support yourself.
+    Out of the box, lime supports the following model objects:
+      - train from caret
+      - WrappedModel from mlr
+      - xgb.Booster from xgboost
+      - H2OModel from h2o
+      - keras.engine.training.Model from keras
+      - lda from MASS (used for low-dependency examples)
+    If your model is not one of the above you'll need to implement support yourself.
 If the model has a predict interface mimicking that of predict.train() from caret, it will be enough to wrap your model in as_classifier()/as_regressor() to gain support.
@@
 
-```{r model type}
+#### Function
+
+```{r}
+getAnywhere(model_type)
+```
+
+#### Model Specific Functions
+
+```{r}
 getAnywhere(model_type)
@@
 
-### `output_type` helper {#output_type}
+### `output_type` {#output_type .tabset}
 
-```{r output type}
-getAnywhere(output_type)
+#### Inputs
+
+- `x`: the model that is stored in the `explainer` object
+
+#### Procedure
+
+1.
+Identifies which model type the model is.
+If it is a classification model, then the output type is set to "prob".
+If it is a regression model, then the output type is set to "raw".
+If neither of these, then an error is returned saying that the model type that was input is not supported by the package.
+
+        switch(model_type(x), 
+              classification = "prob", 
+              regression = "raw", 
+              stop(model_type(x), " models are not supported yet", call. = FALSE))
+
+#### Function
+
+```{r}
+# Print the explain function (and check to see if there have been any changes)
+func_check("output_type", "0.5.0")
 ```
 
-### `exp_kernel` helper {#exp_kernel}
+### `exp_kernel` {#exp_kernel .tabset}
+
+#### Inputs
+
+- `width`: kernel width
+
+#### Procedure
+
+1. Create a function for computing an exponential kernel.
+
+        function(x) sqrt(exp(-(x^2)/(width^2)))
+
+#### Function
 
@@
 
-### `permute_cases` helper {#permute_cases}
+### `permute_cases` {#permute_cases .tabset}
 
-**Procedure**
+#### Inputs
+
+#### Procedure
 
 1. Compute the number of rows as the number of predictions to be explained times the number of permutations.
+
+        nrows <- nrow(cases) * n_permutations
+
 2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
@@
 5. Return the permutations.
+
+#### Function
 

### 2019-09-06 README.Rmd
finished documenting the LIME R package in journal 02

@@
     - email list
+    - what should we do about gganimate/Halloween?
 
@@
 
-- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
-- add an assert_that statement in the code to check if the LIME package is changing
-- point out differences and similarities from the other paper (such as normal sampling)
 - code up Laugel et al's work

### 2019-09-06 journals/02-understanding_lime/02-understanding_lime.Rmd
finished documenting the LIME R package in journal 02

@@
 
-# Original Paper {.tabset}
+# Original Paper
 
@@
 
-### Notation
+## Notation
 
@@
 
-### Goal of LIME
+## Goal of LIME
 
@@
 
-### Procedure
+## Procedure
 
@@
 
-### Comment on Faithfulness
+## Comment on Faithfulness
 
@@
 
+# R Package
+
+This section describes the procedure the the *lime* R package implements.
+The version of the `lime` package that is considered here is `r packageVersion("lime")`.
+The version considered when I first wrote this section was 0.5.0.
+I am only considering the `data.frame` versions of the functions.
+In order to determine if any of the functions that I am interested in have changed since I wrote the description, I created the function below that allows me to check if anything has changed in the function.
+If nothing has changed, it then prints the function.
+
+```{r}
+# Function for checking for changes in a function and printing the current version
+func_check <- function(func_name, version){
+
+  # Specify the path to where the function will be stored
+  file_path <- paste0("../../../data/lime_functions/", func_name, "_v", version, ".rds")
+
+  # Save the file if it does not exist, otherwise load the function and check 
+  # to make sure they have been no changes
+  if(!file.exists(file_path)) {
+    saveRDS(object = getAnywhere(func_name), file = file_path)
+  } else {
+    saved_func <- readRDS(file_path)
+    assertthat::assert_that(assertthat::are_equal(saved_func,
+                                                  getAnywhere(func_name)))
+  }
+
+  # Print the function
+  getAnywhere(func_name)
+
+}
+```
+
+## Main Functions
+
+### `lime.data.frame` {.tabset}
+
+#### Inputs
+
+- `x`: The training data used to fit the model to be explained
+- `model`: The model to explain.
+- `preprocess = NULL`: Function to transform a character vector to the format expected from the model.
+- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations.
+If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to.
+- `n_bins = 4`: The number of bins to use if `bin_continuous = TRUE`.
+- `quantile_bins = TRUE`: Should quantile bins be used if `bin_continuous = TRUE? (Otherwise, equally spaced bins will be used.)
+- `use_density = TRUE`: This option is only considered if `bin_continuous` is set to `FALSE`.
+In that situation, if `use_density = TRUE`, then the continuous data will be sampled using kernel density estimation.
+Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.
+
+#### Procedure
+
+1. If `preprocess` is NULL, then set it to the identity function. Either way, check to make sure that it is a function.
+
+        if (is.null(preprocess)) 
+          preprocess <- function(x) x
+        assert_that(is.function(preprocess))
+
+2. Create an explainer object.
+
+        explainer <- c(as.list(environment()), list(...))
+        explainer$x <- NULL
+
+3. Determine the type of each of the features (e.g. integer, numeric, etc.). If any of the variables are constants, a warning is returned. If the feature type is unknown, an error is returned.
+
+        explainer$feature_type <- setNames(sapply(x, function(f) {
+          if (is.integer(f)) {
+            if (length(unique(f)) == 1) 
+                 "constant"
+             else "integer"
+          }
+          else if (is.numeric(f)) {
+            if (length(unique(f)) == 1) 
+                 "constant"
+            else "numeric"
+          }
+          else if (is.character(f)) {
+            "character"
+          }
+          else if (is.factor(f)) {
+            "factor"
+          }
+          else if (is.logical(f)) {
+            "logical"
+          }
+          else if (inherits(f, "Date") || inherits(f, "POSIXt")) {
+            "date_time"
+          }
+          else {
+            stop("Unknown feature type", call. = FALSE)
+          }
+        }), names(x))
+        if (any(explainer$feature_type == "constant")) {
+          warning("Data contains numeric columns with zero variance", 
+            call. = FALSE)
+        }
+
+4.
+Create bins for numeric and inter type variables.
+If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles.
+Otherwise, `n_bins` equally spaced bins are created.
+If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning.
+Using standard binning instead.") and `n_bins` equally spaced bins are returned.
+
+        explainer$bin_cuts <- setNames(lapply(seq_along(x), function(i) {
+          if (explainer$feature_type[i] %in% c("numeric", "integer")) {
+            if (quantile_bins) {
+              bins <- quantile(x[[i]], seq(0, 1, length.out = n_bins + 
+                1), na.rm = TRUE)
+              bins <- bins[!duplicated(bins)]
+              if (length(bins) < 3) {
+                warning(names(x)[i], " does not contain enough variance to use
+                quantile binning. Using standard binning instead.", 
+                  call. = FALSE)
+                d_range <- range(x[[i]], na.rm = TRUE)
+                bins <- seq(d_range[1], d_range[2], length.out = n_bins + 1)
+              }
+              bins
+            }
+            else {
+              d_range <- range(x[[i]], na.rm = TRUE)
+              seq(d_range[1], d_range[2], length.out = n_bins + 1)
+            }
+          }
+        }), names(x))
+
+5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
+    - Integer: nothing
+    - Numeric: If `bin_continuous`, then determine the
+    proportion of observations in each bin. If
+    `use_density=TRUE`, then kernel a kernel density
+    approximation is used to estimate the distribution.
+    Otherwise, the mean and standard deviation of each 
+    of the features is computed.
+    - Character: nothing
+    - Logical: nothing
+    - Factor: Determine the proportion in each category.
+
+          explainer$feature_distribution <- setNames(lapply(seq_along(x),
+              function(i) {
+                switch(explainer$feature_type[i], 
+                  integer = , 
+                  numeric = if (bin_continuous) {
+                    table(cut(x[[i]], unique(explainer$bin_cuts[[i]]), 
+                      labels = FALSE, include.lowest = TRUE))/nrow(x)
+                  } else if (use_density) {
+                    density(x[[i]])
+                  } else {
+                   c(mean = mean(x[[i]], na.rm = TRUE), sd = sd(x[[i]], 
+                     na.rm = TRUE))
+                  }, character = , logical = , factor = table(x[[i]])/nrow(x), 
+                   NA)
+            }), names(x))
+
+6. Assign some attributes to the explainer object, and return the explainer object.
+
+        structure(explainer, class = c("data_frame_explainer", "explainer", 
+          "list"))
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("lime.data.frame", "0.5.0")
+```
+
+### `explain.data.frame` {.tabset}
+
+#### Inputs
+
+- `x`: The new observations to explain (with the same format as used when creating the explainer).
+- `explainer`: This is the object output from the `lime` function.
+- `labels = NULL`: The specific labels (classes) to explain in case the model is a classifier. For classifiers either this or `n_labels` must be given.
+- `n_labels = NULL`: The number of labels to explain. If this is given for classifiers, the top `n_label` classes will be explained.
+- `n_features`: The number of features to use for each explanation. (i.e. The number of features to select during feature selection.)
+- `n_permutations = 5000`: The number of perturbations generated for each feature.
+- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified. 
+    - `auto`: If `n_features` $\le 6$, uses `forward_selection`.
+    Otherwise, `highest_weights` is used. 
+    - `none`: Use all features for the explanation. Not advised
+    unless you have very few features.
+    - `forward_selection`: Add one feature at a time until
+    `n_features` is reached, based on quality of a ridge 
+    regression model.
+    - `highest_weights`: The `n_features` with highest absolute
+    weight in a ridge regression fit of the complex model outcome
+    are chosen.
+    - `lasso_path`: Fit a lasso model and choose the `n_features`
+    whose lars path converge to zero the latest.
+    - `tree`: Fit a tree to select `n_features` (which needs to be
+    a power of 2). It requires last version of *XGBoost*.
+- `dist_fun = 'gower'`: The distance function to use for calculating the distance from the observation to the permutations.
+If `dist_fun = 'gower'` (default) it will use `gower::gower_dist()`.
+Otherwise it will be forwarded to `stats::dist()`.
+- `kernel_width = NULL`:The width of the exponential kernel that will be used to convert the distance to a similarity in case `dist_fun != 'gower'`.
+- `gower_pow = 1`: A modifier for gower distance. The calculated distance will be raised to the power of this value.
+
+#### Procedure
+
+1. Check to make sure that `explainer` is an object output from the `lime` function.
+
+        assertthat::assert_that(is.data_frame_explainer(explainer))
+
+2.
+Determine the type of the model that is contained within the explainer function (using the [`model_type`](#model_type) function), and determine the type of output that should be produced by `explain` based on the model type (using the [`output_type`](#output_type) function).
+
+        m_type <- model_type(explainer)  
+        o_type <- output_type(explainer)
+
+3.
+If the model type is regression, check to make sure both `labels` and `n_labels` are set to NULL.
+Otherwise, return a warning saying that labels and n_labels are ignored with explaining regression models.
+Then set `n_lables` to 1 and `labels` to NULL.
+
+        if (m_type == "regression") {
+          if (!is.null(labels) || !is.null(n_labels)) {
+            warning("\"labels\" and \"n_labels\" arguments are ignored 
+              when explaining regression models")
+          }
+          n_labels <- 1
+          labels <- NULL
+        }
+
+4. Check to make sure that only `labels` or `n_labels` is specified and the other is NULL. If not, output a warning saying that you must choose between one or the other.
+
+        assert_that(is.null(labels) + is.null(n_labels) == 1, 
+          msg = "You need to choose between labels and n_labels parameters.")
+
+5. Return an error if `n_features` or `n_permutations` are not specified as counts.
+
+        assert_that(is.count(n_features))
+        assert_that(is.count(n_permutations))
+
+6.
+If the kernel width has not been specified, then compute it as the square root of the number of columns of the testing dataframe multiplied by 0.75.
+Then create a kernel function that will be used to weight the perturbations based on the specified kernel width using the function [`exp_kernel`](#exp_kernel).
+The formula used by `exp_kernel` is
+  $$f(x, w)=\sqrt{\exp\left(\frac{-(x^2)}{w}\right)}$$
+where $w$ is the kernel width.
+
+        if (is.null(kernel_width)) {
+          kernel_width <- sqrt(ncol(x)) * 0.75
+        }
+        kernel <- exp_kernel(kernel_width)
+
+7.
+Makes use of the [`permute_cases`](#permute_cases) function for data frames in the lime package.
+This is the function that creates the perturbations.
+One perturbation is created for each of the `n_permuations` specified.
+
+        case_perm <- permute_cases(x, n_permutations, explainer$feature_distribution, 
+          explainer$bin_continuous, explainer$bin_cuts, explainer$use_density)
+
+8. Obtains predictions for all of the permutated data points based on the original model using the [`predict_model`](#predict_model) function.
+
+        case_res <- predict_model(explainer$model, 
+          explainer$preprocess(case_perm),
+          type = o_type, ...)
+        case_res <- set_labels(case_res, explainer$model)
+
+9. Creates indicies for each of the perturbations and dividing them into groups based on which new prediction case they correspond to
+
+        case_ind <- split(seq_len(nrow(case_perm)), rep(seq_len(nrow(x)), each = n_permutations))
+
+10. Fill in the results obejct
+
+        res <- lapply(seq_along(case_ind), function(ind) {
+
+11. Create a vector of indicies for one of the observations
+
+        i <- case_ind[[ind]]
+
+12.
+If the distance function is specified to be "gower", then compute the distance between the case of interest and each observation in the permuted dataset.
+These distances get raised to whatever the specified `gower_pow` is.
+Then these values are subtracted from one so that observations closer to the case of interest have a higher "weight" associated with them.
+
+        if (dist_fun == "gower") {
+          sim <- 1 - (gower_dist(case_perm[i[1], , drop = FALSE], 
+            case_perm[i, , drop = FALSE]))^gower_pow
+        }
+
+13.
+Turns the factor and character variables into numeric variables and determines whether a permutation falls into the test data bin if bins_continuous is set to TRUE.
+This uses the [`numerify`](#numerify) function.
+
+        perms <- numerify(case_perm[i, ], explainer$feature_type, explainer$bin_continuous, explainer$bin_cuts)
+
+14.
+If the distance is not set to "gower", then distance between the case of interest and the permutations is computed using the kernel function.
+This also makes use of the [`feature_scale`](#feature_scale) function.
+
+        if (dist_fun != "gower") {
+          sim <- kernel(c(0, dist(feature_scale(perms, explainer$feature_distribution, 
+            explainer$feature_type, explainer$bin_continuous), 
+            method = dist_fun)[seq_len(n_permutations - 1)]))
+        }
+
+15. Perform feature selection and fit a model to the permutations using these important variables using the function [`model_permutations`](#model_permutations).
+
+        res <- model_permutations(as.matrix(perms), case_res[i, , drop = FALSE], sim, labels, n_labels, n_features, feature_select)
+
+16. Finish filling in the rest of the results object with information about bins and such. This makes use of the [`describe_feature`](#describe_feature) function.
+
+        res$feature_value <- unlist(case_perm[i[1], res$feature])
+        res$feature_desc <- describe_feature(res$feature, case_perm[i[1], ], explainer$feature_type, 
+          explainer$bin_continuous, explainer$bin_cuts)
+        guess <- which.max(abs(case_res[i[1], ]))
+        res$case <- rownames(x)[ind]
+        res$label_prob <- unname(as.matrix(case_res[i[1], ]))[match(res$label, colnames(case_res))]
+        res$data <- list(as.list(case_perm[i[1], ]))
+        res$prediction <- list(as.list(case_res[i[1], ]))
+        res$model_type <- m_type
+        res
+
+17. Join the results and assign names to the columns
+
+        res <- do.call(rbind, res)
+        res <- res[, c('model_type', 'case', 'label', 'label_prob', 'model_r2', 
+                       'model_intercept', 'model_prediction', 'feature', 'feature_value', 
+                       'feature_weight', 'feature_desc', 'data', 'prediction')]
+        if (m_type == 'regression') {
+          res$label <- NULL
+          res$label_prob <- NULL
+          res$prediction <- unlist(res$prediction)
+        }
+
+18. Return the results object
+
+        res
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("explain.data.frame", "0.5.0")
+```
+
+## Helper Functions
+
+These are listed in the order that they are used.
+
+### `model_type` {#model_type .tabset}
+
+#### Inputs
+
+- `x`: the model that is stored in the `explainer` object
+
+#### Procedure
+
+1. The function `model_type` is an overarching function that leads to the specific functions for determining the model type.
+
+        model_type <- function (x, ...) {
+                    UseMethod("model_type")
+                  }
+
+    The specific functions vary based on what package was used to fit the model. Here is information from the package documentation about models supported by *lime*.
+
+        Out of the box, lime supports the following model objects:
+            - train from caret
+            - WrappedModel from mlr
+            - xgb.Booster from xgboost
+            - H2OModel from h2o
+            - keras.engine.training.Model from keras
+            - lda from MASS (used for low-dependency examples)
+        If your model is not one of the above you'll need to implement support yourself.
+If the model has a predict interface mimicking that of predict.train() from caret, it will be enough to wrap your model in as_classifier()/as_regressor() to gain support.
+Otherwise you'll need need to implement a predict_model() method and potentially a model_type() method (if the latter is omitted the model should be wrapped in as_classifier()/as_regressor(), everytime it is used in lime()).
+
+2. Apply the model specific function to determine the model type.
+
+    - **default**
+
+          stop("The class of model must have a model_type method. See ?model_type to get an overview of models supported out of the box", call. = FALSE)
+
+    - **lime classifier**
+
+            "classification"
+
+    - **lime regressor**
+
+            "regression"
+
+    - **train**
+
+            tolower(x$modelType)
+
+    - **model fit**
+
+            x$spec$mode
+
+    - **Wrapped Model**
+
+            switch(x$learner$type, classif = "classification", regr = "regression", 
+              surv = "survival", cluster = "clustering", multilabel = "multilabel")
+
+    - **xgb Booster**
+
+            obj <- x$params$objective
+            if (is.null(obj)) 
+              return("regression")
+            if (is.function(obj)) 
+              stop("Unsupported model type", call. = FALSE)
+            type <- strsplit(obj, ":")[[1]][1]
+            switch(type, reg = "regression", binary = "classification", 
+              multi = "classification", stop("Unsupported model type", 
+              call. = FALSE))
+
+    - **lda**
+
+            "classification"
+
+    - **keras**
+
+            if (!requireNamespace("keras", quietly = TRUE)) {
+              stop("The keras package is required for predicting keras models")
+            }
+            num_layers <- length(x$layers)
+            if (keras::get_config(keras::get_layer(x, index = num_layers))$activation == "linear") {
+              "regression"
+            }
+            else {
+              "classification"
+            }
+
+    - **ranger**
+
+            ranger_model_class <- x$treetype
+            if (ranger_model_class == "Probability estimation" || ranger_model_class == "Classification") {
+              return("classification")
+            }
+            else if (ranger_model_class == "Regression") {
+              return("regression")
+            }
+            else {
+              stop(paste0("ranger model class \"", ranger_model_class, 
+                "\" is not currently supported."))
+            }
+
+#### Function
+
+```{r}
+func_check("model_type", "0.5.0")
+func_check("model_type", "0.5.0")
+func_check("model_type.default", "0.5.0")
+func_check("model_type.lime_classifier", "0.5.0")
+func_check("model_type.lime_regressor", "0.5.0")
+func_check("model_type.train", "0.5.0")
+func_check("model_type.model_fit", "0.5.0")
+func_check("model_type.WrappedModel", "0.5.0")
+func_check("model_type.xgb.Booster", "0.5.0")
+func_check("model_type.lda", "0.5.0")
+func_check("model_type.keras.engine.training.Model", "0.5.0")
+func_check("model_type.H2OModel", "0.5.0")
+func_check("model_type.ranger", "0.5.0")
+```
+
+### `output_type` {#output_type .tabset}
+
+#### Inputs
+
+- `x`: the model that is stored in the `explainer` object
+
+#### Procedure
+
+1.
+Identifies which model type the model is.
+If it is a classification model, then the output type is set to "prob".
+If it is a regression model, then the output type is set to "raw".
+If neither of these, then an error is returned saying that the model type that was input is not supported by the package.
+
+        switch(model_type(x), 
+              classification = "prob", 
+              regression = "raw", 
+              stop(model_type(x), " models are not supported yet", call. = FALSE))
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("output_type", "0.5.0")
+```
+
+### `exp_kernel` {#exp_kernel .tabset}
+
+#### Inputs
+
+- `width`: kernel width
+
+#### Procedure
+
+1. Create a function for computing an exponential kernel.
+
+        function(x) sqrt(exp(-(x^2)/(width^2)))
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("exp_kernel", "0.5.0")
+```
+
+### `permute_cases` {#permute_cases .tabset}
+
+#### Inputs
+
+- `cases`: the object `x` from `explain.data.frame` (new obs to explain)
+- `n_permutations`: the object `n_permutations` from `explain.data.frame` (number of perturbations)
+- `feature_distribution`: the object `explainer$feature_distribution` (the distribution of each feature computed from `lime.data.frame`)
+- `bin_continuous`: the object `explainer$bin_continuous` determined from `lime.data.frame`
+- `bin_cuts`: the object `explainer$bin_cuts` determined from `lime.data.frame`
+- `use_density`: the object `explainer$use_density` determined from `lime.data.frame`
+
+#### Procedure
+
+1. Compute the number of rows as the number of predictions to be explained times the number of permutations.
+
+        nrows <- nrow(cases) * n_permutations
+
+2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
+
+        perm <- as.data.frame(lapply(seq_along(cases), function(i) {
+
+    - **numeric variable and feature distribution contains all NAs**: the observed cases get repeated `n_permutations` times
+
+            perms <- if (is.numeric(cases[[i]]) && identical(is.na(feature_distribution[[i]]), TRUE)) {
+            rep(cases[[i]], each = n_permutations)
+            }
+
+    - **numeric variable and `bin_continuous = TRUE`**: 
+    sample from 1:number of bin cuts with replacement for
+    nrows times using the probability from the variable 
+    distribution sample from a uniform(0,1) distribution
+    and then multiply by the difference in bin cuts of
+    the appropriate bin and add the quantile associated
+    with the bin
+
+            else if (is.numeric(cases[[i]]) && bin_continuous) {
+              bin <- sample(seq_along(feature_distribution[[i]]), 
+                nrows, TRUE, as.numeric(feature_distribution[[i]]))
+              diff(bin_cuts[[i]])[bin] * runif(nrows) + bin_cuts[[i]][bin]
+            }
+
+    - **numeric variable, `bin_continuous = FALSE`, and `use_density = TRUE`**:
+
+            else if (is.numeric(cases[[i]]) && use_density) {
+              width <- diff(feature_distribution[[i]]$x[c(1, 2)])/2
+              sample(feature_distribution[[i]]$x, nrows, TRUE, 
+                feature_distribution[[i]]$y) + runif(nrows, -width, width)
+            }
+
+    - **numeric variable, `bin_continuous = FALSE`, and `use_density = FALSE`**: randomly sample from a normal distribution, multiply by the sd of the feature distribution, and add the mean
+
+            else if (is.numeric(cases[[i]])) {
+               rnorm(nrows) * feature_distribution[[i]]["sd"] + 
+                   feature_distribution[[i]]["mean"]
+            }
+
+    - **character variable**: sample from the names of the levels in the variable based on the probability of the variable distribution
+
+            else if (is.character(cases[[i]])) {
+               sample(names(feature_distribution[[i]]), nrows, TRUE, 
+                   as.numeric(feature_distribution[[i]]))
+            }
+
+    - **logical variable**:
+
+            else if (is.logical(cases[[i]])) {
+               sample(as.logical(names(feature_distribution[[i]])), 
+                   nrows, TRUE, as.numeric(feature_distribution[[i]]))
+            }
+
+    - **factor variable**: sample from the names of the levels in the variable based on the probability of the variable distribution and convert the samples to factors
+
+            else if (is.factor(cases[[i]])) {
+              x <- sample(names(feature_distribution[[i]]), nrows, 
+                TRUE, as.numeric(feature_distribution[[i]]))
+              factor(x, levels = names(feature_distribution[[i]]))
+            }
+
+    - **date**:
+
+            else if (inherits(cases[[i]], "Date") || inherits(cases[[i]], "POSIXt")) {
+              rep(cases[[i]], each = n_permutations)
+            }
+
+    - **integer variable**: round the permutations to the nearest integer
+
+            if (is.integer(cases[[i]])) {
+              as.integer(round(perms))
+            }
+
+    - **other**:
+
+            } else {
+              perms
+            }
+            }), stringsAsFactors = FALSE)
+
+3. Give the permutations the same name as the variables
+
+        names(perm) <- names(cases)
+
+4. Add the cases back into the data frame of the permutations
+
+        perm[seq.int(1, by = n_permutations, length.out = nrow(cases)), ] <- cases
+
+5. Return the permutations.
+
+        perm
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("permute_cases.data.frame", "0.5.0")
+```
+
+### `predict_model` {#predict_model .tabset}
+
+#### Inputs
+
+- `x`: a model
+- `newdata`: the new observations to predict
+- `type`: either `'raw'` to indicate predicted values, or `'prob'` to indicate class probabilities
+
+#### Procedure
+
+1. Determine which `predict_model` function to use based on the model type
+
+        predict_model <- function(x, newdata, type, ...) {
+          UseMethod('predict_model')
+        }
+
+2. Make predictions appropriately based on the model type
+
+    - **Default**
+
+            predict_model.default <- function(x, newdata, type, ...) {
+              p <- predict(x, newdata = newdata, type = type, ...)
+              if (type == 'raw') 
+                p <- data.frame(Response = p, stringsAsFactors = FALSE)
+              as.data.frame(p)
+            }
+
+    - **Model Fit** (?)
+
+            predict_model.model_fit <- function (x, newdata, type, ...) {
+              if (type == "raw") 
+                type <- "numeric"
+                p <- predict(x, new_data = newdata, type = type, ...)
+              if (type == "raw") {
+                p <- data.frame(Response = p[[1]], stringsAsFactors = FALSE)
+              }
+              else if (type == "prob") {
+                names(p) <- sub(".pred_", "", names(p))
+              }
+              p
+            }
+
+    - **Wrapped Model**
+
+            predict_model.WrappedModel <- function (x, newdata, type, ...) {
+              if (!requireNamespace("mlr", quietly = TRUE)) {
+                stop("mlr must be available when working with WrappedModel models")
+              }
+              p <- predict(x, newdata = newdata, ...)
+              switch(type, raw = data.frame(Response = mlr::getPredictionResponse(p), 
+                stringsAsFactors = FALSE), prob = mlr::getPredictionProbabilities(p, 
+                p$task.desc$class.levels), stop("Type must be either \"raw\" or \"prob\"", 
+              call. = FALSE))
+            }
+
+    - **xbg Booster**
+
+            predict_model.xgb.Booster <- function (x, newdata, type, ...) {
+              if (!requireNamespace("xgboost", quietly = TRUE)) {
+                stop("The xgboost package is required for predicting xgboost models")
+              }
+              if (is.data.frame(newdata)) {
+                newdata <- xgboost::xgb.DMatrix(as.matrix(newdata))
+              }
+              p <- data.frame(predict(x, newdata = newdata, reshape = TRUE, ...), 
+                stringsAsFactors = FALSE)
+              if (type == "raw") {
+                names(p) <- "Response"
+              }
+              else if (type == "prob") {
+                if (ncol(p) == 1) {
+                  names(p) = "1"
+                  p[["0"]] <- 1 - p[["1"]]
+                }
+                else {
+                  names(p) <- as.character(seq_along(p))
+                }
+              }
+              p
+            }
+
+    - **lda**
+
+            predict_model.lda <- function(x, newdata, type, ...) {
+              res <- predict(x, newdata = newdata, ...)
+              switch(
+              type,
+              raw = data.frame(Response = res$class, stringsAsFactors = FALSE),
+              prob = as.data.frame(res$posterior, check.names = FALSE)
+              )
+            }
+
+    - **keras**
+
+            predict_model.keras.engine.training.Model <- function (x, newdata, type, ...) {
+              if (!requireNamespace("keras", quietly = TRUE)) {
+                stop("The keras package is required for predicting keras models")
+              }
+              res <- predict(x, as.array(newdata))
+              if (type == "raw") {
+                data.frame(Response = res[, 1])
+              }
+              else {
+                if (ncol(res) == 1) {
+                res <- cbind(1 - res, res)
+              }
+              colnames(res) <- as.character(seq_len(ncol(res)))
+              as.data.frame(res, check.names = FALSE)
+              }
+            }
+
+    - **H2O Model**
+
+            predict_model.H2OModel <- ## function (x, newdata, type, ...) {
+               if (!requireNamespace("h2o", quietly = TRUE)) {
+                   stop("The h2o package is required for predicting h2o models")
+               }
+               pred <- h2o::h2o.predict(x, h2o::as.h2o(newdata))
+               h2o_model_class <- class(x)[[1]]
+               if (h2o_model_class %in% c("H2OBinomialModel", "H2OMultinomialModel")) {
+                   return(as.data.frame(pred[, -1]))
+               }
+               else if (h2o_model_class == "H2ORegressionModel") {
+                   ret <- as.data.frame(pred[, 1])
+                   names(ret) <- "Response"
+                   return(ret)
+               }
+               else {
+                   stop("This h2o model is not currently supported.")
+               }
+           }
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("predict_model", "0.5.0")
+func_check("predict_model.default", "0.5.0")
+func_check("predict_model.model_fit", "0.5.0")
+func_check("predict_model.WrappedModel", "0.5.0")
+func_check("predict_model.xgb.Booster", "0.5.0")
+func_check("predict_model.lda", "0.5.0")
+func_check("predict_model.keras.engine.training.Model", "0.5.0")
+func_check("predict_model.H2OModel", "0.5.0")
+func_check("predict_model.ranger", "0.5.0")
+```
+
+### `numerify` {#numerify .tabset}
+
+#### Inputs
+
+- `x`: object `case_perm` with the perturbed values 
+- `type`: the `explainer$feature_type` object 
+- `bin_continuous`: the value of `explainer$bin_continuous` 
+- `bin_cuts`: the value of `explainer$bin_cuts`
+
+#### Procedure
+
+1. Apply the function below to each observation in the perturbed dataset.
+
+        setNames(as.data.frame(lapply(seq_along(x), function(i) {
+
+2. If the variable is a character, factor, or logical change it to a numeric variable.
+
+        if (type[i] %in% c("character", "factor", "logical")) {
+          as.numeric(x[[i]] == x[[i]][1])
+        }
+
+3.
+If the variable is some other type and `bin_continuous=TRUE`, then put the bin cuts into a variable called cuts, set the first and last bin cuts to -inf and inf, respectively, determine which bin each permutation falls into, and determine whether a permution falls into the test data observation bin of interest.
+
+        else {
+          if (bin_continuous) {
+            cuts <- bin_cuts[[i]]
+            cuts[1] <- -Inf
+            cuts[length(cuts)] <- Inf
+            xi <- cut(x[[i]], unique(cuts), include.lowest = T)
+            as.numeric(xi == xi[1])
+
+4. If the variable is some other type and `bin_continuous=FALSE`, then just return the permutations.
+
+          } else {
+            x[[i]]
+          }
+        }
+        }), stringsAsFactors = FALSE), names(x))
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("numerify", "0.5.0")
+```
+
+### `feature_scale` {#feature_scale .tabset}
+
+#### Inputs
+
+- `x` = `perms`
+- `distribution` = `explainer$feature_distribution`
+- `type` = `explainer$feature_type`
+- `bin_continuous` = `explainer$bin_continuous`
+
+#### Procedure
+
+Scales the distribuiton of the numeric permutions if bin_continuous was set to FALSE.
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("feature_scale", "0.5.0")
+```
+
+### `model_permutations` {#model_permutations .tabset}
+
+#### Inputs
+
+- `x`: the `as.matrix(perms)` object with the perturbations
+- `y`: `case_res[i, , drop = FALSE]`
+- `weights`: the weights `sim`
+- `labels`: the `labels` object
+- `n_labels`: the `n_labels` object
+- `n_features`: the `n_features` object
+- `feature_method`: the `feature_select` object
+
+#### Procedure
+
+1. If all of the weights are 0 (no difference from the case of interest), then return an error.
+
+        if (all(weights[-1] == 0)) {
+          stop("All permutations have no similarity to the original observation. 
+          Try setting bin_continuous to TRUE and/or increase kernel_size", 
+          call. = FALSE)
+        }
+
+2. Create labels if `n_labels` is not NULL.
+
+        if (!is.null(n_labels)) {
+          labels <- names(y)[order(as.data.frame(y)[1, ], decreasing = TRUE)[seq_len(n_labels)]]
+        }
+
+3. Something about missing values (?)
+
+        x <- x[, colSums(is.na(x)) == 0 & apply(x, 2, var) != 0, drop = FALSE]
+
+4. If the response has the same value for all permutations, then an error is returned.
+
+        res <- lapply(labels, function(label) {
+          if (length(unique(y[[label]])) == 1) {
+            stop("Response is constant across permutations. Please check your model", 
+            call. = FALSE)
+        }
+
+5. Select which variables are important for the model using the [`select_features`](#select_features) function.
+
+        features <- select_features(feature_method, x, y[[label]], weights, n_features)
+
+6. `glmnet` does not allow `n_features=1`, so in this case the model must be fit separately. This is done by 
+creating a matrix with a column of 1s for the intercept and the selected variables for the other columns, fiting a model with the probability as the response and the selected variables as the predictors, computing the r2 values, and extracting the intercept, non-intercept coefficients, and model prediction for the case of interest.
+
+        if (length(features) == 1) {
+          x_fit = cbind("(Intercept)" = rep(1, nrow(x)), x[, features, drop = FALSE])
+          fit <- glm.fit(x = x_fit, y = y[[label]],  weights = weights, family = gaussian())
+          r2 <- 1 - fit$deviance/fit$null.deviance
+          coefs <- coef(fit)
+          intercept <- coefs[1]
+          coefs <- coefs[-1]
+          model_pred <- fit$fitted.values[1]
+
+7. When `n_features` > 1, fit the ridge regression model using `glmnet` when the order of the observations shuffled, and extract the same items as in Step 6.
+
+        } else {
+          shuffle_order <- sample(length(y[[label]])) # glm is sensitive to the order of the examples
+          fit <- glmnet(x[shuffle_order, features], y[[label]][shuffle_order], weights = weights[shuffle_order], 
+            alpha = 0, lambda = 0.001)
+          r2 <- fit$dev.ratio
+          coefs <- coef(fit)
+          intercept <- coefs[1, 1]
+          coefs <- coefs[-1, 1]
+          model_pred <- predict(fit, x[1, features, drop = FALSE])[1]
+        }
+
+8. Finally, put the values from above into a data frame.
+
+        data.frame(
+          label = label,
+          feature = names(coefs),
+          feature_weight = unname(coefs),
+          model_r2 = r2,
+          model_intercept = intercept,
+          model_prediction = model_pred,
+          stringsAsFactors = FALSE
+        )
+        })
+
+10. Bind all of the results associated with different cases.
+
+        do.call(rbind, res)
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("model_permutations", "0.5.0")
+```
+
+### `select_features` {#select_features .tabset}
+
+#### Inputs
+
+- `method`: `feature_method`
+- `x`: `x`
+- `y`: `y[[label]]`
+- `weights`: `weights`
+- `n_features`: `n_features`
+
+#### Procedure
+
+Performs features selection using the specified method. Note that this is based on a handful of other [functions](#select) including the `feature_selection_method`.
+
+        if (n_features >= ncol(x)) {
+          return(seq_len(ncol(x)))
+        }
+        method <- match.arg(method, feature_selection_method())
+        switch(
+          method,
+          auto = if (n_features <= 6) {
+            select_features("forward_selection", x, y, weights, n_features)
+          } else {
+            select_features("highest_weights", x, y, weights, n_features)
+          },
+          none = seq_len(nrow(x)),
+          forward_selection = select_f_fs(x, y, weights, n_features),
+          highest_weights = select_f_hw(x, y, weights, n_features),
+          lasso_path = select_f_lp(x, y, weights, n_features),
+          tree = select_tree(x, y, weights, n_features),
+          stop("Method not implemented", call. = FALSE)
+        )
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("select_features", "0.5.0")
+func_check("feature_selection_method", "0.5.0")
+```
+
+### `select_` {#select .tabset}
+
+#### Options
+
+- Forward selection: `select_f_fs`
+- Heighest weights: `select_f_hw`
+- Lasso path: `select_f_lp`
+- Tree: `select_tree`
+
+#### `select_f_fs`
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("select_f_fs", "0.5.0")
+```
+
+#### `select_f_hw`
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("select_f_hw", "0.5.0")
+```
+
+#### `select_f_lp`
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("select_f_lp", "0.5.0")
+```
+
+#### `select_tree`
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("select_tree", "0.5.0")
+```
+
+### `describe_feature` {#describe_feature .tabset}
+
+#### Inputs
+
+- `feature` = `res$feature`
+- `case` = `case_perm[i[1], ]`
+- `type` = `explainer$feature_type`
+- `bin_continuous` = `explainer$bin_continuous`
+- `bin_cuts` = `explainer$bin_cuts`
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("describe_feature", "0.5.0")
+```
+
+# Python Package
+
+I have not spent a lot of time going through the Python package code, but I wanted to check to see if it uses a ridge regression for the feature selection and the explainer model.
+This [article](https://towardsdatascience.com/how-to-perform-lasso-and-ridge-regression-in-python-3b3b75541ad8) describes that ridge regression can be fit in Python using the sklearn "package".
+These images below of the code from the Python lime [GitHub repository](https://github.com/marcotcr/lime/blob/master/lime/lime_base.py) seem to imply that it is using ridge regression for both of these steps.
+
+![](../../figures/python-ridge1.png)
+
+![](../../figures/python-ridge2.png)
+
+![](../../figures/python-ridge3.png)
+
 # Concept Visualizations
@@
 
-### Data and Model
+## Data and Model
 
@@
 
-### Linear Regression Explainer
+## Linear Regression Explainer
 
@@
 
-### Ridge Regression Explainer
+## Ridge Regression Explainer
 
@@
 
-# R Package
-
-This section describes the procedure the the *lime* R package implements.
-The version of the `lime` package that is considered here is `r packageVersion("lime")`.
-The version considered when I first wrote this section was 0.5.0.
-I am only considering the `data.frame` versions of the functions.
-In order to determine if any of the functions that I am interested in have changed since I wrote the description, I created the function below that allows me to check if anything has changed in the function.
-If nothing has changed, it then prints the function.
-
-```{r}
-# Function for checking for changes in a function and printing the current version
-func_check <- function(func_name, version){
-
-  # Specify the path to where the function will be stored
-  file_path <- paste0("../../../data/lime_functions/", func_name, "_v", version, ".rds")
-
-  # Save the file if it does not exist, otherwise load the function and check 
-  # to make sure they have been no changes
-  if(!file.exists(file_path)) {
-    saveRDS(object = getAnywhere(func_name), file = file_path)
-  } else {
-    saved_func <- readRDS(file_path)
-    assertthat::assert_that(assertthat::are_equal(saved_func,
-                                                  getAnywhere(func_name)))
-  }
-
-  # Print the function
-  getAnywhere(func_name)
-
-}
-```
-
-## Main Functions
-
-### `lime.data.frame` {.tabset}
-
-#### Inputs
-
-- `x`: The training data used to fit the model to be explained
-- `model`: The model to explain.
-- `preprocess = NULL`: Function to transform a character vector to the format expected from the model.
-- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations.
-If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to.
-- `n_bins = 4`: The number of bins to use if `bin_continuous = TRUE`.
-- `quantile_bins = TRUE`: Should quantile bins be used if `bin_continuous = TRUE? (Otherwise, equally spaced bins will be used.)
-- `use_density = TRUE`: This option is only considered if `bin_continuous` is set to `FALSE`.
-In that situation, if `use_density = TRUE`, then the continuous data will be sampled using kernel density estimation.
-Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.
-
-#### Procedure
-
-1. If `preprocess` is NULL, then set it to the identity function. Either way, check to make sure that it is a function.
-2. Create an explainer object.
-3. Determine the type of each of the features (e.g. integer, numeric, etc.). If any of the variables are constants, a warning is returned. If the feature type is unknown, an error is returned.
-4.
-Create bins for numeric and inter type variables.
-If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles.
-Otherwise, `n_bins` equally spaced bins are created.
-If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning.
-Using standard binning instead.") and `n_bins` equally spaced bins are returned.
-5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
-    - Integer: nothing
-    - Numeric: If `bin_continuous`, then determine the
-    proportion of observations in each bin. If
-    `use_density=TRUE`, then kernel a kernel density
-    approximation is used to estimate the distribution.
-    Otherwise, the mean and standard deviation of each 
-    of the features is computed.
-    - Character: nothing
-    - Logical: nothing
-    - Factor: Determine the proportion in each category.
-6. Assign some attributes to the explainer object, and return the explainer object.
-
-#### Function
-
-```{r}
-# Print the lime function (and check to see if there have been any changes)
-func_check("lime.data.frame", "0.5.0")
-```
-
-### `explain.data.frame` {.tabset}
-
-#### Inputs
-
-- `x`: The new observations to explain (with the same format as used when creating the explainer).
-- `explainer`: This is the object output from the `lime` function.
-- `labels = NULL`: The specific labels (classes) to explain in case the model is a classifier. For classifiers either this or `n_labels` must be given.
-- `n_labels = NULL`: The number of labels to explain. If this is given for classifiers, the top `n_label` classes will be explained.
-- `n_features`: The number of features to use for each explanation. (i.e. The number of features to select during feature selection.)
-- `n_permutations = 5000`: The number of perturbations generated for each feature.
-- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified. 
-    - `auto`: If `n_features` $\le 6$, uses `forward_selection`.
-    Otherwise, `highest_weights` is used. 
-    - `none`: Use all features for the explanation. Not advised
-    unless you have very few features.
-    - `forward_selection`: Add one feature at a time until
-    `n_features` is reached, based on quality of a ridge 
-    regression model.
-    - `highest_weights`: The `n_features` with highest absolute
-    weight in a ridge regression fit of the complex model outcome
-    are chosen.
-    - `lasso_path`: Fit a lasso model and choose the `n_features`
-    whose lars path converge to zero the latest.
-    - `tree`: Fit a tree to select `n_features` (which needs to be
-    a power of 2). It requires last version of *XGBoost*.
-- `dist_fun = 'gower'`: The distance function to use for calculating the distance from the observation to the permutations.
-If `dist_fun = 'gower'` (default) it will use `gower::gower_dist()`.
-Otherwise it will be forwarded to `stats::dist()`.
-- `kernel_width = NULL`:The width of the exponential kernel that will be used to convert the distance to a similarity in case `dist_fun != 'gower'`.
-- `gower_pow = 1`: A modifier for gower distance. The calculated distance will be raised to the power of this value.
-
-#### Procedure
-
-1. Check to make sure that `explainer` is an object output from the `lime` function.
-
-        assertthat::assert_that(is.data_frame_explainer(explainer))
-
-2.
-Determine the type of the model that is contained within the explainer function (using the [`model_type`](#model_type) function), and determine the type of output that should be produced by `explain` based on the model type (using the [`output_type`](#output_type) function).
-
-        m_type <- model_type(explainer)  
-        o_type <- output_type(explainer)
-
-3.
-If the model type is regression, check to make sure both `labels` and `n_labels` are set to NULL.
-Otherwise, return a warning saying that labels and n_labels are ignored with explaining regression models.
-Then set `n_lables` to 1 and `labels` to NULL.
-
-        if (m_type == "regression") {
-          if (!is.null(labels) || !is.null(n_labels)) {
-            warning("\"labels\" and \"n_labels\" arguments are ignored 
-              when explaining regression models")
-          }
-          n_labels <- 1
-          labels <- NULL
-        }
-
-4. Check to make sure that only `labels` or `n_labels` is specified and the other is NULL. If not, output a warning saying that you must choose between one or the other.
-
-        assert_that(is.null(labels) + is.null(n_labels) == 1, 
-          msg = "You need to choose between labels and n_labels parameters.")
-
-5. Return an error if `n_features` or `n_permutations` are not specified as counts.
-
-        assert_that(is.count(n_features))
-        assert_that(is.count(n_permutations))
-
-6.
-If the kernel width has not been specified, then compute it as the square root of the number of columns of the testing dataframe multiplied by 0.75.
-Then create a kernel function that will be used to weight the perturbations based on the specified kernel width using the function [`exp_kernel`](#exp_kernel).
-The formula used by `exp_kernel` is
-  $$f(x, w)=\sqrt{\exp\left(\frac{-(x^2)}{w}\right)}$$
-where $w$ is the kernel width.
-
-        if (is.null(kernel_width)) {
-          kernel_width <- sqrt(ncol(x)) * 0.75
-        }
-        kernel <- exp_kernel(kernel_width)
-
-7.
-Makes use of the [`permute_cases`](#permute_cases) function for data frames in the lime package.
-This is the function that creates the perturbations.
-One perturbation is created for each of the `n_permuations` specified.
-
-        case_perm <- permute_cases(x, n_permutations, explainer$feature_distribution, 
-          explainer$bin_continuous, explainer$bin_cuts, explainer$use_density)
-
----------
-
-- Predictions for the testing data using the random forest model are computed.
-     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match.
-Since the random forest is a classification model, `lime` is set to return the prediction probabilities.
-
-- Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
-    + The way that the similarity score is computed depends on the type of feature.
-Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point.
-Then, by default, the Gower distance is used to compute the similarity score.
-(using the `gower` package in R)
-
-- Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
-    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
-      * forward selection with ridge regression
-      * highest weight with ridge regression
-      * LASSO model
-      * tree model
-      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise
-
-- A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores.
-If the response is categorical, the user can select how many categories and which categories they want to explain.
-  $$P(Match = TRUE) = \beta_0 + 
-  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
-  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
-  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
-For the prediction of interest, 
-  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
-- The feature weights are extracted and used as the explanations.
-
-Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all.
-Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.
-
-#### Function
-
-```{r}
-# Print the explain function (and check to see if there have been any changes)
-func_check("explain.data.frame", "0.5.0")
-```
-
-## Helper Functions
-
-### `model_type` {#model_type .tabset}
-
-#### Info
-
-The *lime* package provides a variety of functions for extracting the model type from the complex model to be explained.
-The function `model_type` is an overarching function that leads to the specific functions for determining the model type.
-The specific functions vary based on what package was used to fit the model.
-
-Here is information from the package documentation about models supported by *lime*.
-
-    Out of the box, lime supports the following model objects:
-      - train from caret
-      - WrappedModel from mlr
-      - xgb.Booster from xgboost
-      - H2OModel from h2o
-      - keras.engine.training.Model from keras
-      - lda from MASS (used for low-dependency examples)
-    If your model is not one of the above you'll need to implement support yourself.
-If the model has a predict interface mimicking that of predict.train() from caret, it will be enough to wrap your model in as_classifier()/as_regressor() to gain support.
-Otherwise you'll need need to implement a predict_model() method and potentially a model_type() method (if the latter is omitted the model should be wrapped in as_classifier()/as_regressor(), everytime it is used in lime()).
-
-#### Function
-
-```{r}
-getAnywhere(model_type)
-```
-
-#### Model Specific Functions
-
-```{r}
-getAnywhere(model_type)
-getAnywhere(model_type.default)
-getAnywhere(model_type.lime_classifier)
-getAnywhere(model_type.lime_regressor)
-getAnywhere(model_type.train)
-getAnywhere(model_type.model_fit)
-getAnywhere(model_type.WrappedModel)
-getAnywhere(model_type.xgb.Booster)
-getAnywhere(model_type.lda)
-getAnywhere(model_type.keras.engine.training.Model)
-getAnywhere(model_type.H2OModel)
-getAnywhere(model_type.ranger)
-```
-
-### `output_type` {#output_type .tabset}
-
-#### Inputs
-
-- `x`: the model that is stored in the `explainer` object
-
-#### Procedure
-
-1.
-Identifies which model type the model is.
-If it is a classification model, then the output type is set to "prob".
-If it is a regression model, then the output type is set to "raw".
-If neither of these, then an error is returned saying that the model type that was input is not supported by the package.
-
-        switch(model_type(x), 
-              classification = "prob", 
-              regression = "raw", 
-              stop(model_type(x), " models are not supported yet", call. = FALSE))
-
-#### Function
-
-```{r}
-# Print the explain function (and check to see if there have been any changes)
-func_check("output_type", "0.5.0")
-```
-
-### `exp_kernel` {#exp_kernel .tabset}
-
-#### Inputs
-
-- `width`: kernel width
-
-#### Procedure
-
-1. Create a function for computing an exponential kernel.
-
-        function(x) sqrt(exp(-(x^2)/(width^2)))
-
-#### Function
-
-```{r exp_kernel}
-# Print the exp_kernel function (and check to see if there have been any changes)
-if(!file.exists("../../../data/lime_functions/exp_kernel_v0.5.0.rds")) {
-  saveRDS(object = getAnywhere(exp_kernel),
-          file = "../../../data/lime_functions/exp_kernel_v0.5.0.rds")
-  getAnywhere(exp_kernel)
-} else {
-  exp_kernel_v0.5.0 <- readRDS("../../../data/lime_functions/exp_kernel_v0.5.0.rds")  
-  if(assert_that(are_equal(exp_kernel_v0.5.0, getAnywhere(exp_kernel)))){
-    getAnywhere(exp_kernel)
-  } 
-}
-```
-
-### `permute_cases` {#permute_cases .tabset}
-
-#### Inputs
-
-#### Procedure
-
-1. Compute the number of rows as the number of predictions to be explained times the number of permutations.
-
-        nrows <- nrow(cases) * n_permutations
-
-2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
-    - numeric variable and the feature distribution contains all NAs: the observed cases get repeated `n_permutations` times
-    - numeric variable and `bin_continuous = TRUE`: 
-    sample from 1:number of bin cuts with replacement for
-    nrows times using the probability from the variable 
-    distribution sample from a uniform(0,1) distribution
-    and then multiply by the difference in bin cuts of
-    the appropriate bin and add the quantile associated
-    with the bin
-    - numeric variable, `bin_continuous = FALSE`, and `use_density = TRUE`: 
-    - numeric variable, `bin_continuous = FALSE`, and `use_density = FALSE`: randomly sample from a normal distribution, multiply by the sd of the feature distribution, and add the mean 
-    - character variable: sample from the names of the levels in the variable based on the probability of the variable distribution
-    - logical variable: 
-    - factor variable: sample from the names of the levels in the variable based on the probability of the variable distribution and convert the samples to factors 
-    - date: 
-    - integer variable: round the permutations to the nearest integer
-3. Give the permutations the same name as the variables
-4. Add the cases back into the data frame of the permutations
-5. Return the permutations.
-
-#### Function
-
-```{r}
-if(!file.exists("../../../data/lime_functions/permute_cases_v0.5.0.rds")) {
-  saveRDS(object = getAnywhere(permute_cases.data.frame),
-          file = "../../../data/lime_functions/permute_cases_v0.5.0.rds")
-  getAnywhere(permute_cases.data.frame)
-} else {
-  permute_cases_v0.5.0 <- readRDS("../../../data/lime_functions/permute_cases_v0.5.0.rds")  
-  if(assert_that(are_equal(permute_cases_v0.5.0, getAnywhere(permute_cases.data.frame)))){
-    getAnywhere(permute_cases.data.frame)
-  } 
-}
-```
-
-# Python Package
-
-I have not spent a lot of time going through the Python package code, but I wanted to check to see if it uses a ridge regression for the feature selection and the explainer model.
-This [article](https://towardsdatascience.com/how-to-perform-lasso-and-ridge-regression-in-python-3b3b75541ad8) describes that ridge regression can be fit in Python using the sklearn "package".
-These images below of the code from the Python lime [GitHub repository](https://github.com/marcotcr/lime/blob/master/lime/lime_base.py) seem to imply that it is using ridge regression for both of these steps.
-
-![](../../figures/python-ridge1.png)
-
-![](../../figures/python-ridge2.png)
-
-![](../../figures/python-ridge3.png)
-
 # Proposed Bin Creation Methods
 
-### The Data
+## The Data
 
@@
 
-### Subsampled Bins
+## Subsampled Bins
 
@@
 
-### Tree Based Bins
+## Tree Based Bins
 

### 2019-09-06 README.Rmd
started adding some code that demonstrates how the internal lime functions work

@@
     - what should we do about gganimate/Halloween?
+- LIME
+    - I made a mistake when I told you that the full test dataset gets included in the ridge regression model (only the case of interest in included)
 
@@
 
-- code up Laugel et al's work
+- finish going through code with the explain function
+- write procedure section of LIME paper
+- draft the rest of the paper
 - read through papers giving an overview of the current explanation methods
-- check to see if there a paper showing how ridge regression is affected by sample size changes
-- try fitting the ridge regression with the observed data only to see how it compares to the model fit with the ridge regression
 

### 2019-09-06 journals/02-understanding_lime/02-understanding_lime.Rmd
started adding some code that demonstrates how the internal lime functions work

@@
 
+In order to run the *lime* functions, here I load the bullet data to apply the code to.
+
+```{r}
+# Load in the bullet training and testing data
+hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")
+hamby224_test <- read.csv("../../../data/hamby224_test.csv")
+
+# Obtain features used when fitting the rtrees random forest
+rf_features <- rownames(bulletr::rtrees$importance)
+```
+
 ## Main Functions
@@
 
-8. Obtains predictions for all of the permutated data points based on the original model using the [`predict_model`](#predict_model) function.
+8. Obtains predictions for all of the permutated data points based on the original model using the [`predict_model`](#predict_model) function. Use the function [`set_labels`](#set_labels.)
 
@@
 func_check("explain.data.frame", "0.5.0")
+```
+
+#### Implementation
+
+```{r}
+library(randomForest)
+x <- hamby224_test %>% 
+  arrange(case) %>%
+  select(rf_features) %>% 
+  na.omit()
+explainer <- lime:::lime.data.frame(x = hamby173and252_train %>%
+                                      select(rf_features), 
+                                    y = hamby173and252_train %>%
+                                      select(samesource), 
+                                    model = as_classifier(bulletr::rtrees))
+label = TRUE
+n_labels = NULL
+n_features = 3
+n_permutations = 5000
+feature_select = 'auto'
+dist_fun = "gower"
+kernel_width = NULL
+gower_pow = 1
+```
+
+```{r}
+assertthat::assert_that(lime:::is.data_frame_explainer(explainer))
+```
+
+```{r}
+#m_type <- lime:::model_type(explainer)
+o_type <- lime:::output_type(explainer)
+```
+
+```{r}
+assert_that(is.null(labels) + is.null(n_labels) == 1, 
+   msg = "You need to choose between labels and n_labels parameters.")
+```
+
+```{r}
+assert_that(is.count(n_features))
+assert_that(is.count(n_permutations))
+```
+
+```{r}
+if (is.null(kernel_width)) {
+   kernel_width <- sqrt(ncol(x)) * 0.75
+}
+kernel <- lime:::exp_kernel(kernel_width)
+```
+
+```{r}
+case_perm <- lime:::permute_cases.data.frame(x,
+                                             n_permutations,
+                                             explainer$feature_distribution,
+                                             explainer$bin_continuous,
+                                             explainer$bin_cuts,
+                                             explainer$use_density)
+head(case_perm)
+```
+
+```{r}
+case_res <- lime:::predict_model(explainer$model, 
+                                 explainer$preprocess(case_perm),
+                                 type = o_type)
+case_res <- lime:::set_labels(case_res, explainer$model)
+head(case_res)
+```
+
+```{r}
+case_ind <- split(seq_len(nrow(case_perm)), rep(seq_len(nrow(x)), each = n_permutations))
+case_ind[[1]][1:10]
+case_ind[[2]][1:10]
+case_ind[[3]][1:10]
+```
+
+```{r}
+str(seq_along(case_ind))
+```
+
+```{r}
+i <- case_ind[[1]]
+str(i)
+```
+
+```{r}
+if (dist_fun == "gower") {
+  sim <- 1 - (gower_dist(case_perm[i[1], , drop = FALSE], 
+    case_perm[i, , drop = FALSE]))^gower_pow
+}
+str(sim)
+```
+
+```{r}
+perms <- lime:::numerify(case_perm[i, ], 
+                         explainer$feature_type, 
+                         explainer$bin_continuous,
+                         explainer$bin_cuts)
+head(perms)
+```
+
+```{r}
+# error?
+# res <- lime:::model_permutations(as.matrix(perms), 
+#                                  case_res[i, , drop = FALSE], 
+#                                  sim, 
+#                                  labels, 
+#                                  n_labels, 
+#                                  n_features, 
+#                                  feature_select)
 ```
@@
 
-2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
+2.
+Create the perturbations based on the type of variable and using the feature distribution determined by the lime function.
+The cases are as follows.
+The function does this process one variable at a time where a case represents on variable.
 
@@
 
-    - **integer variable**: round the permutations to the nearest integer
+3. If the variable in the original dataset is an integer, then convert the perturbations to integers.
 
@@
           as.integer(round(perms))
-            }
-
-    - **other**:
-
         } else {
@@
         }
-            }), stringsAsFactors = FALSE)
-
-3. Give the permutations the same name as the variables
+
+4. Give the permutations the same name as the variables.
 
@@
 
-4. Add the cases back into the data frame of the permutations
+5. Add the cases back into the data frame of the permutations, so that the case of interest gets inserted at the beginning of each set of perturbations.
 
@@
 
-5. Return the permutations.
+6. Return the permutations.
 
         perm
+
+The final `perm` will look like...
+
+| Case | Obs | 
+| ---- | --------- | 
+| 1 | 1st case of interest | 
+| 1 | perturbation 1,1 | 
+| 1 | perturbation 1,2 |
+| ... | ... | 
+| 1 | perturbation 1,m |
+| 2 | 2nd case of interest | 
+| 2 | perturbation 2,1 | 
+| 2 | perturbation 2,2 |
+| ... | ... | 
+| 2 | perturbation 2,m |
+| ... | ... | 
+| n | nth case of interest | 
+| n | perturbation n,1 | 
+| n | perturbation n,2 |
+| ... | ... | 
+| n | perturbation n,m |
 
@@
 func_check("permute_cases.data.frame", "0.5.0")
+```
+
+#### Implementation
+
+```{r}
+cases = x
+n_permutations = n_permutations
+feature_distribution = explainer$feature_distribution
+bin_continuous = explainer$bin_continuous
+bin_cuts = explainer$bin_cuts
+use_density = explainer$use_density
+```
+
+```{r}
+nrows <- nrow(cases) * n_permutations
+```
+
+```{r}
+seq <- seq_along(cases)
+seq
+```
+
+```{r}
+i <- seq[1]
+# Case when is.numeric(cases[[i]]) && bin_continuous
+bin <- sample(seq_along(feature_distribution[[i]]), nrows, TRUE,
+              as.numeric(feature_distribution[[i]]))
+head(bin)
+perms <- diff(bin_cuts[[i]])[bin] * runif(nrows) + bin_cuts[[i]][bin]
+head(perms)
+```
+
+```{r}
+if (is.integer(cases[[i]])) {
+    perms <- as.integer(round(perms))
+  } else {
+    perms <- perms
+  }
+head(perms)
+```
+
+```{r}
+perm <- as.data.frame(lapply(seq_along(cases), function(i) {
+         perms <- if (is.numeric(cases[[i]]) && bin_continuous) {
+             bin <- sample(seq_along(feature_distribution[[i]]), 
+                 nrows, TRUE, as.numeric(feature_distribution[[i]]))
+             diff(bin_cuts[[i]])[bin] * runif(nrows) + bin_cuts[[i]][bin]
+         }
+         if (is.integer(cases[[i]])) {
+             as.integer(round(perms))
+         }
+         else {
+             perms
+         }
+}), stringsAsFactors = FALSE)
+names(perm) <- names(cases)
+head(perm)
+```
+
+```{r}
+# The first row gets replaced with the case of interest for each set of perturbations
+perm[seq.int(1, by = n_permutations, length.out = nrow(cases)), ] <- cases
+head(perm)
 ```
@@
 func_check("predict_model.ranger", "0.5.0")
+```
+
+### `set_labels` {#set_labels .tabset}
+
+#### Inputs
+
+- `res` = the predictions (`case_res`)
+- `model` = `explainer$model`
+
+#### Function
+
+```{r}
+# Print the function (and check to see if there have been any changes)
+func_check("set_labels", "0.5.0")
 ```

### 2019-09-10 README.Rmd
updated discussion points

@@
 - Graphics Group
-    - email list
     - what should we do about gganimate/Halloween?
+    - treats?
 - LIME
     - I made a mistake when I told you that the full test dataset gets included in the ridge regression model (only the case of interest in included)
+    - Show updated journal on LIME (added a lot to document the package)
+    - What did you think of my additions to section 2 of the paper?
+    - New goal for 1st draft of paper: next Wednesday (9/18)
 

### 2019-09-10 README.Rmd
updated to do list

@@
 
-- finish going through code with the explain function
-- write procedure section of LIME paper
-- draft the rest of the paper
-- read through papers giving an overview of the current explanation methods
+- draft methods section of the paper
+- draft data example section of paper
+- draft discussion section of paper
+- draft appendices
 
@@
 - explainer models
+    - read through papers giving an overview of the current explanation methods
     - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)

### 2019-09-11 README.Rmd
added to to do list
updates after meeting

@@
 
-- Graphics Group
-    - what should we do about gganimate/Halloween?
-    - treats?
-- LIME
-    - I made a mistake when I told you that the full test dataset gets included in the ridge regression model (only the case of interest in included)
-    - Show updated journal on LIME (added a lot to document the package)
-    - What did you think of my additions to section 2 of the paper?
-    - New goal for 1st draft of paper: next Wednesday (9/18)
-
 ## To Do List
 
-*First draft of paper due two weeks into the semester (Tuesday, September 10)*
+*First draft of paper due Wednesday, September 18)*
 
@@
     - Dr. Nettleton paper
+- random forest interpretations
+    - read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/
 

### 2019-09-13 README.Rmd
updated readme

@@
 
-Repository for research projects on LIME applied to the Hamby bullet data.
+Repository for research projects on LIME
 
@@
 
-**Current**
-
 - draft methods section of the paper
@@
 
-**Oral Prelim**
+## Oral Prelim
 
-- schedule
+**Schedule**
+
 - can be anytime during the semester 
@@
 - send prelim materials to committee 2 weeks in advance
-- materials
+
+**Materials**
+
 - Chapter 0 (complete)
@@
 
-**Later**
+## Ideas
 
-- LIME diagnostics  
+**LIME diagnostics**
+
 - turn repetitive code into functions
@@
 coloring them by variables suggested to be important by lime
-- explainer models
+
+**Explainer Models**
+
 - read through papers giving an overview of the current explanation methods
@@
 - look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
-- understanding LIME
-    - read through LIME papers again
-    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
+
+**Understanding LIME**
+
+- edit details in understanding LIME journal
+- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
 - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
 - assess lime results on logistic regression models
-    - think about how the argmin is accomplished by the LIME R package
 - try retriculate to apply python version of lime
@@
 - read new paper on Anchor
-- simulation with RF
+
+**Possible Improvements to LIME**
+
+- determine the best number of bins to use for each variable
+- try out subsampling idea
+
+**Simulation with RF**
+
 - think about how to implement a simulation with a random forest
@@
 - read book Dr. Dixon lent me on sensitivity analyses
-- possible improvements to LIME
-    - determine the best number of bins to use for each variable
-    - try out subsampling idea
-- random forests confidence intervals
+
+**Random Forests Confidence Intervals**
+
 - look into papers by Giles Hooker and Lucas Mentch
 - Dr. Nettleton paper
-- random forest interpretations
+
+**Random Forest Interpretations**
+
 - read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/
 
-## Contents
+## Repository Contents
 

### 2019-09-13 README.Rmd
small updates to journal and readme

@@
 ## Talking points
+
+- Sometimes LIME does not want to run in R
+
+```{r error = TRUE, message = FALSE}
+library(caret)
+library(lime)
+
+# Split up the data set
+iris_test <- iris[1:5, 1:4]
+iris_train <- iris[-(1:5), 1:4]
+iris_lab <- iris[[5]][-(1:5)]
+
+# Create Random Forest model on iris data
+model <- train(iris_train, iris_lab, method = 'rf')
+
+# Create an explainer object
+explainer <- lime(iris_train, model)
+
+# Explain new observation
+explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
+```
 

### 2019-09-13 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
small updates to journal and readme

@@
 library(cowplot)
+library(GGally)
 library(glmnet)
@@
   theme(legend.position = "bottom")
+```
+
+##### Feature Interactions
+
+```{r}
+hamby224_test %>%
+  select(rf_features, samesource) %>%
+  ggpairs(mapping = aes(color = samesource), 
+          columns = rf_features)
 ```

### 2019-09-19 README.Rmd
updated example in readme

--- 2019-09-13 README.Rmd
@@
 ## Talking points
+
+- Should I write the code in a package or just save the functions in a folder in the paper repository?
+- Sometimes LIME does not want to run in R with the bullet data
+
+```{r error = TRUE, message = FALSE}
+library(lime)
+
+# Split up the data set
+iris_test <- iris[1:5, 1:4]
+iris_train <- iris[-(1:5), 1:4]
+iris_lab <- iris[[5]][-(1:5)]
+
+# Create Random Forest model on iris data
+#model <- caret::train(iris_train, iris_lab, method = 'rf')
+model <- randomForest::randomForest(iris_train, iris_lab)
+
+# Create an explainer object
+explainer <- lime(iris_train, as_classifier(model))
+
+# Explain new observation
+explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
+```
 

### 2019-09-21 README.Rmd
added to discussion points

@@
 - Should I write the code in a package or just save the functions in a folder in the paper repository?
-- Sometimes LIME does not want to run in R with the bullet data
+- MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
+- How to handle the issue of accessing the perturbations?
+- Do we want to think of a metric that is stand alone? - not just for comparisons
+- Sometimes LIME does not want to run in R with the bullet data - this example works but I'm running into issues with the package...I don't really understand how the predict_model functions work
 

### 2019-09-25 README.Rmd
added talking points about graphics group
updated notes after meeting

--- 2019-09-13 README.Rmd
@@
 
-- Sometimes LIME does not want to run in R
+**LIME**
 
-```{r error = TRUE, message = FALSE}
-library(caret)
-library(lime)
-
-# Split up the data set
-iris_test <- iris[1:5, 1:4]
-iris_train <- iris[-(1:5), 1:4]
-iris_lab <- iris[[5]][-(1:5)]
-
-# Create Random Forest model on iris data
-model <- train(iris_train, iris_lab, method = 'rf')
-
-# Create an explainer object
-explainer <- lime(iris_train, model)
-
-# Explain new observation
-explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
-```
+- What names should I give to the diagnostic plots?
+- Color themes for the paper?
+- Metrics:
+    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
+    - Do we want to think of a metric that is stand alone? - not just for comparisons
 
 ## To Do List
-
-*First draft of paper due Wednesday, September 18)*
 

### 2019-10-08 README.Rmd
added Q's to readme
updated readme with questions for Heike

@@
 
+- Completed: 
+    - connected limeaid to my forked version of lime
+    - added sine example and analysis of default LIME explanations to paper
+    - started section on heatmap plot
+- What do you think of my work on the methods section so far?
+- Should we schedule my oral prelim, or should we keep waiting until I get closer to finishing the paper?
 - What names should I give to the diagnostic plots?
 - Color themes for the paper?
+- Could you help me with the interpretation of the default LIME explanations?
 - Metrics:
@@
     - Do we want to think of a metric that is stand alone? - not just for comparisons
+
+**Sandia**
+
+- I had a phone interview with them
+- Did you get an email from them for a reference?
+
+**Graphics Group**
+
+- treats for Yihui's talk?
 

### 2019-10-16 README.Rmd
added another talking point
updated list of questions
updated readme

--- 2019-09-25 README.Rmd
@@
 
+**Sandia**
+
+- Memo about full time
+
 **LIME**
 
+- What do you think of the new version of the plot that I created?
+- Should we schedule my oral prelim, or should we keep waiting until I get closer to finishing the paper?
 - What names should I give to the diagnostic plots?
-- Color themes for the paper?
+- Could you help me with the interpretation of the default LIME explanations?
 - Metrics:
@@
 
+**Graphics Group**
+
+- Did you have any resources for gganimate? (check out my slides so far)
+- Treats for tomorrow?
+
 ## To Do List
 
-- draft methods section of the paper
-- draft data example section of paper
-- draft discussion section of paper
-- draft appendices
+- draft paper
 

### 2019-10-22 README.Rmd
one more update to talking points
updated to do list
added to questions for tomorrow

--- 2019-09-25 README.Rmd
@@
 
+- Can we talk about the LIME assumptions?
 - What names should I give to the diagnostic plots?
-- Color themes for the paper?
+- Could you help me with the interpretation of the default LIME explanations?
 - Metrics:
@@
 
+**Graphics Group**
+
+- Treats?
+
+**Sandia**
+
 ## To Do List
 
-- draft methods section of the paper
-- draft data example section of paper
-- draft discussion section of paper
-- draft appendices
+- draft paper
+- start organizing literature review paper
 

### 2019-10-26 README.Rmd
updated talking points

@@
 
-- Can we talk about the LIME assumptions?
-- What names should I give to the diagnostic plots?
-- Could you help me with the interpretation of the default LIME explanations?
-- Metrics:
-    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
-    - Do we want to think of a metric that is stand alone? - not just for comparisons
-
 **Graphics Group**
-
-- Treats?
 
@@
 - start organizing literature review paper
+- set up dissertation R markdown document
 

### 2019-11-08 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
created some partial dependence plots

@@
     toc: true
-    toc_depth: 3
+    toc_depth: 5
     toc_float: true
@@
 library(cowplot)
+library(ggConvexHull) #devtools::install_github("cmartin/ggConvexHull")
 library(GGally)
+library(ggpcp)
 library(glmnet)
@@
   theme_minimal() + 
-  scale_fill_distiller(palette = "GnBu", direction = 1)
+  scale_fill_distiller(palette = "GnBu", direction = 1) + 
+  theme(legend.position = "bottom")
 
@@
 
-```{r fig.width = 10}
+```{r fig.width = 14}
 hamby173and252_train %>%
-  mutate(case = 1:n()) %>%
-  select(case, rfscore, samesource, ccf:sum_peaks) %>%
-  mutate_at(rf_features, scale) %>%
-  gather(variable, value, 4:12) %>%
-  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
-  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
-  geom_point() + 
-  geom_line(alpha = 0.2) + 
-  facet_grid( ~ samesource) + 
+  na.omit() %>%
+  ggplot(aes(color = rfscore)) + 
+  geom_pcp(aes(vars = vars(as.vector(rf_features_ordered$feature))), alpha = 0.1) + 
+  facet_grid(. ~ samesource) + 
   scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
@@
 
-```{r fig.width = 10}
+```{r fig.width = 14}
 hamby224_test %>%
   na.omit() %>%
-  select(case, set, rfscore, samesource, ccf:sum_peaks) %>%
-  mutate_at(rf_features, scale) %>%
-  gather(variable, value, 5:13) %>%
-  mutate(variable = factor(variable, levels = rf_features_ordered$feature)) %>%
-  ggplot(aes(x = variable, y = value, group = case, color = rfscore)) + 
-  geom_point() + 
-  geom_line(alpha = 0.5) + 
-  facet_grid(set ~ samesource) + 
+  ggplot(aes(color = rfscore)) + 
+  geom_pcp(aes(vars = vars(as.vector(rf_features_ordered$feature))), alpha = 0.1) + 
+  facet_grid(. ~ samesource) + 
   scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) + 
@@
        y = "Standardized Feature Values") 
+```
+
+##### Partial Dependence Plots
+
+I tried using the package `pdp`, but I got the following error.
+
+```{r error = TRUE}
+library(pdp)
+partial(object = rtrees, pred.var = "rough_cor", plot = TRUE, plot.engine = "ggplot2")
+```
+
+Then I tried creating some plots myself.
+
+```{r}
+# Specify the number of breaks in the grid
+n <- 100000
+
+# Create a prediction grid
+set.seed(20191108)
+simulated_data <- hamby173and252_train %>%
+  select(rf_features) %>%
+  gather(variable, value) %>%
+  group_by(variable) %>%
+  summarise(min = min(value),
+            max = max(value)) %>%
+  rowwise() %>%
+  mutate(samples = list(runif(n, min, max))) %>%
+  select(variable, samples) %>%
+  unnest() %>%
+  mutate(case = rep(1:n, 9)) %>%
+  spread(variable, samples) %>%
+  select(-case)
+
+simulated_data$rfpred <- predict(rtrees, newdata = simulated_data, type = "prob")[,2]
+```
+
+```{r}
+simulated_data %>%
+  gather(key = variable, value = value, rf_features) %>%
+  ggplot(aes(x = value, y = rfpred, color = rfpred)) + 
+  geom_point() + 
+  facet_wrap(. ~ variable, scales = "free_x") + 
+  scale_color_viridis_c("rfpred", option = "A", limits = c(0, 1))
+```
+
+```{r}
+ggplot() + 
+  stat_summary_2d(data = simulated_data,
+                  mapping = aes(x = ccf, y = rough_cor, z = rfpred), 
+                  bins = 75, 
+                  fun = mean) + 
+  scale_fill_viridis_c("rfpred", option = "A", limits = c(0, 1)) + 
+  geom_convexhull(data = hamby173and252_train, 
+                  mapping = aes(x = ccf, y = rough_cor), 
+                  alpha = 0, 
+                  color = "black")
+```
+
+```{r}
+ggplot() + 
+  stat_summary_2d(data = simulated_data,
+                  mapping = aes(x = ccf, y = matches, z = rfpred), 
+                  bins = 75, 
+                  fun = mean) + 
+  scale_fill_viridis_c("rfpred", option = "A", limits = c(0, 1)) + 
+  geom_convexhull(data = hamby173and252_train, 
+                  mapping = aes(x = ccf, y = matches), 
+                  alpha = 0, 
+                  color = "black")
 ```

### 2019-11-18 journals/02-understanding_lime/02-understanding_lime.Rmd
added implementation for feature_select

@@
 
+#### Implementation
+
+```{r}
+# Set up and implementation
+x <- hamby224_test %>% 
+  arrange(case) %>%
+  select(rf_features) %>% 
+  na.omit()
+explainer <- lime:::lime.data.frame(x = hamby173and252_train %>%
+                                      select(rf_features), 
+                                    y = hamby173and252_train %>%
+                                      select(samesource), 
+                                    model = as_classifier(bulletr::rtrees))
+label = TRUE
+n_labels = NULL
+n_features = 3
+n_permutations = 5000
+feature_select = 'auto'
+dist_fun = "gower"
+kernel_width = NULL
+gower_pow = 1
+o_type <- lime:::output_type(explainer)
+if (is.null(kernel_width)) {
+   kernel_width <- sqrt(ncol(x)) * 0.75
+}
+kernel <- lime:::exp_kernel(kernel_width)
+case_perm <- lime:::permute_cases.data.frame(x,
+                                             n_permutations,
+                                             explainer$feature_distribution,
+                                             explainer$bin_continuous,
+                                             explainer$bin_cuts,
+                                             explainer$use_density)
+case_res <- lime:::predict_model(explainer$model, 
+                                 explainer$preprocess(case_perm),
+                                 type = o_type)
+case_res <- lime:::set_labels(case_res, explainer$model)
+case_ind <- split(seq_len(nrow(case_perm)), rep(seq_len(nrow(x)), each = n_permutations))
+i <- case_ind[[1]]
+if (dist_fun == "gower") {
+  sim <- 1 - (gower_dist(case_perm[i[1], , drop = FALSE], 
+    case_perm[i, , drop = FALSE]))^gower_pow
+}
+perms <- lime:::numerify(case_perm[i, ], 
+                         explainer$feature_type, 
+                         explainer$bin_continuous,
+                         explainer$bin_cuts)
+
+# Running the function
+lime:::select_f_fs(x = as.matrix(perms), 
+                   y = case_res[i, , drop = FALSE][[label]], 
+                   weights = sim, 
+                   n_features = n_features)
+```
+
+```{r}
+# One implementation of the inside of select_f_fs
+
+# Input values
+x = as.matrix(perms)
+y = case_res[i, , drop = FALSE][[label]]
+weights = sim
+n_features = n_features
+
+# Creates a vector where to store the selected features
+features <- c()
+
+#for (i in seq_len(n_features)) {
+
+# My code to run this loop
+seq_len(n_features)
+loopi <- 1
+
+# Settings
+max <- -1e+05
+best <- 0
+
+seq_len(ncol(x))
+
+for (loopj in seq_len(ncol(x))) {
+
+#if (loopj %in% features)
+#  next
+
+if (length(features) == 0) {
+
+  x_fit = cbind(`(Intercept)` = rep(1, nrow(x)), x[, loopj, drop = FALSE])
+  print(head(x_fit))
+
+  fit <- glm.fit(x = x_fit, y = y, weights = weights, family = gaussian())
+
+  r2 <- 1 - fit$deviance/fit$null.deviance
+  print(r2)
+
+  } else {
+
+    x_fit = x[, c(features, loopj), drop = FALSE]
+    print(head(x_fit))
+    fit <- glmnet(x_fit,
+                  y, weights = weights, alpha = 0, lambda = 0)
+
+    r2 <- fit$dev.ratio
+    print(r2)
+  }
+
+if (is.finite(r2) && r2 > max) {
+  max <- r2
+  best <- loopj
+  print(max)
+}
+
+}
+
+if (best == 0) {
+             stop("Failed to select features with forward selection. Please choose another feature selector",
+                 call. = FALSE)
+}
+
+features <- c(features, best)
+
+#}
+
+features
+```
+
 ### `describe_feature` {#describe_feature .tabset}

### 2020-05-20 journals/08-logistic_regression/08-logistic_regression.Rmd
added an example with a logistic regression model and sine data

---
title: "LIME Applied to a Logistic Regression"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE, 
                      eval = TRUE,
                      cache = TRUE, 
                      fig.width = 12)
```

This journal includes LIME examples with a logistic regression model fit to the sine data.

```{r}
library(caret)
library(cowplot)
library(lime)
library(limeaid)
```

# Data

Prepare the sine data

```{r}
# Prepare training and testing data
x_train = sine_data_train[c("x1", "x2", "x3")]
y_train = factor(sine_data_train$y)
x_test = sine_data_test[1:5, c("x1", "x2", "x3")]
```

# Logistic Regression Models

## Main Effects Only

Logistic regression model: y ~ x1 + x2 + x3

```{r}
# Fit the model
lrm <- caret::train(
  as.factor(y) ~ x1 + x2 + x3,
  preProcess = "scale",
  data = sine_data_train,
  method = "glm",
  family = "binomial"
)

lrm$finalModel
```

## All Interactions

Logistic regression model: y ~ x1 * x2 * x3

```{r}
# Fit the model
lri <- caret::train(
  as.factor(y) ~ x1 * x2 * x3,
  preProcess = "scale",
  data = sine_data_train,
  method = "glm",
  family = "binomial"
)

lri$finalModel
```

# Apply LIME

Apply LIME with 3 quantile bins, 4 quantile bins, and kernel density to both models

```{r}
# Run apply_lime
resm <- apply_lime(
  train = x_train,
  test = x_test,
  model = lrm,
  label = "1",
  n_features = 2,
  sim_method = c('quantile_bins',
                 'kernel_density'),
  nbins = 3:4,
  return_perms = TRUE
)

# Run apply_lime
resi <- apply_lime(
  train = x_train,
  test = x_test,
  model = lri,
  label = "1",
  n_features = 2,
  sim_method = c('quantile_bins',
                 'kernel_density'),
  nbins = 3:4,
  return_perms = TRUE
)
```

# Exlanation Visualizations

Plot the LIME explanation plot and my EOI plot for each prediction in the test data and each implementation of LIME

```{r}
# Plot the explanation of interest
join_plots <- function(id, exp) {
  p1 <- lime::plot_features(exp$explain[id:(id+1),])
  p2 <- eoi_plot(exp$explain[id:(id+1),])
  plot_grid(p1, p2)
}
```

## Main Effects Only

### 3 quantile bins

```{r}
purrr::map(.x = seq(1, 9, 2), .f = join_plots, exp = resm)
```

### 4 quantile bins

```{r}
purrr::map(.x = seq(11, 19, 2), .f = join_plots, exp = resm)
```

### kernel density

```{r}
purrr::map(.x = seq(21, 29, 2), .f = join_plots, exp = resm)
```

## All Interactions

### 3 quantile bins

```{r}
purrr::map(.x = seq(1, 9, 2), .f = join_plots, exp = resi)
```

### 4 quantile bins

```{r}
purrr::map(.x = seq(11, 19, 2), .f = join_plots, exp = resi)
```

### kernel density

```{r}
purrr::map(.x = seq(21, 29, 2), .f = join_plots, exp = resi)
```

### 2020-09-07 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
updates for preparing paper for submission

@@
 # Load libraries
-library(bulletr)
+library(bulletxtrctr)
 library(cowplot)
@@
 
-Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the bulletr library.
+Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the `bulletxtrctr` library.
 I created such a vector to use in this journal, and this vector is printed below.
@@
 # Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(bulletr::rtrees$importance)
+rf_features <- rownames(bulletxtrctr::rtrees$importance)
 rf_features
@@
          land2 = factor(land2),
-         rfscore = predict(bulletr::rtrees, hamby173and252_raw %>%
+         rfscore = predict(bulletxtrctr::rtrees, hamby173and252_raw %>%
                              select(rf_features), 
@@
 dim(hamby173and252_train_cleaning)
-dim(predict(bulletr::rtrees, type = "prob"))
+dim(predict(bulletxtrctr::rtrees, type = "prob"))
 ```
@@
 dim(hamby173and252_train)
-dim(predict(bulletr::rtrees, type = "prob"))
+dim(predict(bulletxtrctr::rtrees, type = "prob"))
 ```
@@
 
-```{r eval = FALSE}
+```{r}
 # Save the datasets and response variables as .csv files
-write.csv(hamby173and252_train, "../../data/hamby173and252_train.csv", row.names = FALSE)
+write.csv(hamby173and252_train, "../../../data/hamby173and252_train.csv", row.names = FALSE)
 ```
@@
   mutate(case = factor(1:length(study))) %>%
-  select(case, study:samesource)
+  select(case, study, set, bullet1, land1, bullet2, land2, ccf:sum_peaks, samesource, rfscore)
 ```
@@
 
-```{r eval = FALSE}
+```{r}
 # Save the test data as a .csv file
-write.csv(hamby224_test, "../../data/hamby224_test.csv", row.names = FALSE)
+write.csv(hamby224_test, "../../../data/hamby224_test.csv", row.names = FALSE)
+```
+
+**Data for LIME Diagnostics Paper**
+
+The code below takes the dataset `hamby224_test` and makes some formatting adjustments to prepare it to be used in the LIME diagnostics paper, so that it matches the training dataset published by Heike that was used to fit `rtrees`.
+
+```{r}
+# Change format of dataset to be used in the paper
+paper_bullet_test_data <- 
+  hamby224_test %>%
+  mutate(study = str_remove(study, " "),
+         set = str_remove(set, " "),
+         bullet1 = str_replace(bullet1, "Known ", "B"),
+         bullet2 = str_replace(bullet2, "Known ", "B"),
+         bullet1 = str_replace(bullet1, "Questioned", "BUnk"),
+         bullet2 = str_replace(bullet2, "Questioned", "BUnk"),
+         land1 = str_replace(land1, "Land ", "L"),
+         land2 = str_replace(land2, "Land ", "L")) %>%
+  mutate(land_id1 = paste(study, set, bullet1, land1, sep = "-"),
+         land_id2 = paste(study, set, bullet2, land2, sep = "-")) %>%
+  select(-study, -set, -bullet1, -land1, -bullet2, -land2) %>%
+  select(case, land_id1, land_id2, everything())
+
+# ave the file to the folder where the LIME diagnostics paper is stored
+write.csv(paper_bullet_test_data , "../../../diagnostics-paper/data-bullet-test.csv", row.names = FALSE)
 ```
@@
 Al.
-The model is available through the GitHub version of the `bulletr` package.
-The link to the GitHub repository for `bulletr` is https://github.com/CSAFE-ISU/bulletr.
-
-The random forest model is stored in the package `bulletr` as a data object called `rtrees`.
+The model is available through the GitHub version of the `bulletxtrctr` package.
+The link to the GitHub repository for `bulletxtrctr` is https://github.com/heike/bulletxtrctr.
+
+The random forest model is stored in the package `bulletxtrctr` as a data object called `rtrees`.
 The paper does not include many details about the model fitting process, so I looked at some of the model features, which are printed below.
@@
 # Create a dataframe with the random forest features ordered by importance
-rf_features_ordered <- data.frame(feature = rownames(bulletr::rtrees$importance), 
-                                  MeanDecreaseGini = bulletr::rtrees$importance) %>%
+rf_features_ordered <- data.frame(feature = rownames(bulletxtrctr::rtrees$importance), 
+                                  MeanDecreaseGini = bulletxtrctr::rtrees$importance) %>%
   arrange(desc(MeanDecreaseGini))

### 2020-09-12 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
removed code for saving data to paper repo (since I've moved that code elsewhere now)

@@
 
-**Data for LIME Diagnostics Paper**
-
-The code below takes the dataset `hamby224_test` and makes some formatting adjustments to prepare it to be used in the LIME diagnostics paper, so that it matches the training dataset published by Heike that was used to fit `rtrees`.
-
-```{r}
-# Change format of dataset to be used in the paper
-paper_bullet_test_data <- 
-  hamby224_test %>%
-  mutate(study = str_remove(study, " "),
-         set = str_remove(set, " "),
-         bullet1 = str_replace(bullet1, "Known ", "B"),
-         bullet2 = str_replace(bullet2, "Known ", "B"),
-         bullet1 = str_replace(bullet1, "Questioned", "BUnk"),
-         bullet2 = str_replace(bullet2, "Questioned", "BUnk"),
-         land1 = str_replace(land1, "Land ", "L"),
-         land2 = str_replace(land2, "Land ", "L")) %>%
-  mutate(land_id1 = paste(study, set, bullet1, land1, sep = "-"),
-         land_id2 = paste(study, set, bullet2, land2, sep = "-")) %>%
-  select(-study, -set, -bullet1, -land1, -bullet2, -land2) %>%
-  select(case, land_id1, land_id2, everything())
-
-# ave the file to the folder where the LIME diagnostics paper is stored
-write.csv(paper_bullet_test_data , "../../../diagnostics-paper/data-bullet-test.csv", row.names = FALSE)
-```
-
 ### Plots of Features

### 2020-09-17 README.Rmd
updated talking points
updated talking points after meeting
added files for comparing random forest models to rtrees

@@
 Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/
-
-## Talking points
-
-**LIME**
-
-**Graphics Group**
-
-**Sandia**
-
-## To Do List
-
-- draft paper
-- start organizing literature review paper
-- set up dissertation R markdown document
-
-## Oral Prelim
-
-**Schedule**
-
-- can be anytime during the semester 
-- just needs to be 6 months before final defense
-- schedule when it gets closer to the time 
-- schedule 3 or 4 weeks in advance
-- send prelim materials to committee 2 weeks in advance
-
-**Materials**
-
-- Chapter 0 (complete)
-    - lit review
-    - research statement: "this is what this thesis will investigate"
-- Chatper 1 (as close to submission as possible)
-    - LIME and shortcomings
-    - Dr. Dixon likes to give feedback before submission
-- Chapter 2 (draft)
-    - Diagnostics for RF
-- Chapter 3 (some idea)
-    - Diagnostics for Bayesian Neural Networks
-    - Could switch to chapter 2 if more complete
-- Conclusion (not needed)
 
@@
 - `07-computation_issues`: documentation of some of the computation issues I ran into during the project
+- `08-logistic_regression`: examples of applying LIME to explain logistic regression models
+- `09-refitting-rtrees`: examples where I retrain the rtrees model with the "current" version of the training data and compare the results
 

### 2020-09-17 journals/09-refitting-rtrees/09-refitting-rtrees.Rmd
added files for comparing random forest models to rtrees

---
title: "Comparing `rtrees` to my models"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  cache = FALSE
)
```

This journal contains the results from 100 new random forests to the bullet training data observations where `flag == FALSE`.

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(purrr)
library(randomForest)
library(tidyr)
```

# Data

Load the prepared training data which only has observations with `flag == FALSE` (prepared in the LIME diagnostics paper repository):

```{r}
bullet_train <- read.csv("../../../diagnostics-paper/data/bullet-train.csv")
```

Load the random forest `rtrees` from the `bulletxtrctr` package and the random forest model I recently fit using the `bullet_train` data in the paper:

```{r}
rtrees <- bulletxtrctr::rtrees
paper_rf <- readRDS("../../../diagnostics-paper/data/bullet-rf.rds")
```

Extract the features used to fit `rtrees`:

```{r}
bullet_features <- rownames(bulletxtrctr::rtrees$importance)
bullet_features
```

# `rtrees` versus paper model

The code below was used to fit the random forest in the paper but is not run here:

```{r eval = FALSE}
set.seed(20160104)
bullet_rf <-
  randomForest(
    y = factor(bullet_train$samesource),
    x = bullet_train %>% select(all_of(bullet_features)),
    ntree = bulletxtrctr::rtrees$ntree,
    mtry = bulletxtrctr::rtrees$mtry
  )
```

Confusion matrices from the two models:

```{r}
rtrees$confusion
paper_rf$confusion
```

Variable importance values:

```{r}
vi = data.frame(
  features = rownames(rtrees$importance),
  rtrees = rtrees$importance[, 1],
  paper = paper_rf$importance[, 1]
)
```

# New Random Forests

Randomly select 100 seeds (using a random seed):

```{r}
set.seed(20200917)
seeds = sample(x = 10000000:100000000, size = 100, replace = FALSE)
seeds
```

Function for fitting random forests to mimic rtrees with different seeds:

```{r}
fit_rf <- function(seed) {
  set.seed(seed)
  bullet_rf <-
    randomForest(
      y = factor(bullet_train$samesource),
      x = bullet_train %>% select(all_of(bullet_features)),
      ntree = bulletxtrctr::rtrees$ntree,
      mtry = bulletxtrctr::rtrees$mtry
    )  
}
```

Fit 100 new random forests and save or load:

```{r}
# Fit (and save) or load random forests
bullet_rfs_file = "../../../data/bullet_rfs.rds"
if (!file.exists(bullet_rfs_file)) {
  bullet_rfs = map(.x = seeds, .f = fit_rf)
  saveRDS(object = bullet_rfs, file = bullet_rfs_file)
} else {
  bullet_rfs = readRDS(bullet_rfs_file)
}
```

Function for extracting the confusion matrices from the model and put in a nice data frame:

```{r}
extract_confus <- function(model) {
  data.frame(model$confusion) %>%
  rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>%
  mutate(observed = rownames(model$confusion)) %>%
  pivot_wider(names_from = observed, values_from = everything())  
}
```

Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:

```{r}
extract_importance <- function(model) {
  data.frame(model$importance) %>%
    mutate(features = rownames(model$importance)) %>%
    arrange(desc(MeanDecreaseGini)) %>%
    mutate(rank = 1:n()) %>%
    rename("importance" = "MeanDecreaseGini") %>%
    select(features, importance, rank)
}
```

Extract the confusion matrices and importance values from all random forest models:

```{r}
res_confus <- map_df(.x = bullet_rfs, .f = extract_confus, .id = "rf_model_id")
res_importance <- map_df(.x = bullet_rfs, .f = extract_importance, .id = "rf_model_id")
```

# Visualizations of Results

## Class Errors

Obtain the class errors from `rtrees` and the paper random forest:

```{r}
comparison_values <-
  data.frame(
    model = c("paper", "rtrees"),
    class_error_true = c(paper_rf$confusion[2, 3], rtrees$confusion[2, 3]),
    class_error_false = c(paper_rf$confusion[1, 3], rtrees$confusion[1, 3])
  )
```

Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true):

```{r fig.width = 10, fig.height = 4.5}
hist_true <- 
  res_confus %>%
  ggplot(aes(x = class_error_TRUE)) +
  geom_histogram() +
  geom_vline(data = comparison_values,
             mapping = aes(xintercept = class_error_true, color = model))

hist_false <- 
  res_confus %>%
  ggplot(aes(x = class_error_FALSE)) +
  geom_histogram() +
  geom_vline(data = comparison_values,
             mapping = aes(xintercept = class_error_false, color = model))

plot_grid(hist_true, hist_false)
```

Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models:

```{r}
ggplot() +
  geom_point(data = res_confus,
             mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) +
  geom_point(
    data = comparison_values,
    mapping = aes(x = class_error_false, y = class_error_true, color = model)
  )
```

## Variable Importance

Prepare variable importance from `rtrees` and paper models for plotting:

```{r}
vi_ranks <- 
  vi %>%
  arrange(desc(rtrees)) %>%
  mutate(rtrees_rank = 1:n()) %>% 
  arrange(desc(paper)) %>%
  mutate(paper_rank = 1:n()) %>%
  select(-rtrees, -paper) %>%
  pivot_longer(names_to = "rf_model_id", values_to = "rank", cols = -features)
```

Tile plot showing the variable importance ranks for each model showing variability across newly trained models and some agreement (ex: rough_cor and ccf) and some disagreement (ex: sum_peaks and non_cms) with `rtrees`:

```{r fig.width = 10, fig.height = 4.5}
rtrees_var_order <-
  vi_ranks %>%
  filter(rf_model_id == "rtrees_rank") %>%
  arrange(desc(rank)) %>%
  pull(features)

tile_org <-
  vi_ranks %>%
  mutate(
    rank = factor(rank, levels = 1:9),
    features = factor(features, levels = rtrees_var_order), 
    rf_model_id = factor(rf_model_id, levels = c("rtrees_rank", "paper_rank"))
  ) %>%
  ggplot(aes(x = rf_model_id, y = features, fill = rank)) +
  geom_tile() +
  scale_fill_brewer(palette = "RdYlBu")

tile_new <-
  res_importance %>%
  mutate(
    rank = factor(rank, levels = 1:9),
    features = factor(features, levels = rtrees_var_order)
  ) %>%
  ggplot(aes(x = rf_model_id, y = features, fill = rank)) +
  geom_tile() +
  scale_fill_brewer(palette = "RdYlBu")

plot_grid(tile_org, tile_new)
```

Box plot of ranks across the models with colored points added for the `rtrees` and paper model variable importance ranks (features ordered by `rtrees` variable importance):

```{r}
res_importance %>%
  mutate(features = factor(features, levels = rtrees_var_order)) %>%
  ggplot() +
  geom_boxplot(aes(x = rank, y = features)) +
  geom_jitter(
    data = vi_ranks,
    mapping = aes(x = rank, y = features, color = rf_model_id),
    width = 0,
    height = 0.2
  )
```

Features versus variable importance ranks for new models (black lines and points) and `rtrees` and paper model (features ordered by `rtrees` variable importance):

```{r}
res_importance %>%
  mutate(
    rank = factor(rank, levels = 1:9),
    features = factor(features, levels = rtrees_var_order)
  ) %>%
  ggplot(aes(x = rank, y = features, group = rf_model_id)) +
  geom_line(alpha = 0.2, size = 2) +
  geom_point(alpha = 0.2, size = 3) +
  geom_line(
    data = vi_ranks,
    mapping = aes(
      x = rank,
      y = features,
      group = rf_model_id,
      color = rf_model_id
    )
  ) +
  geom_jitter(
    data = vi_ranks,
    mapping = aes(x = rank, y = features, color = rf_model_id),
    width = 0.1,
    height = 0
  ) +
  labs(title = "new random forest lines and points created with alpha shading")
```

### 2020-09-25 journals/10-comparing-rfs/10-comparing-rfs.Rmd
heike's code and trying with other data

---
title: "10-compring-rfs"
author: "Katherine Goode"
date: "9/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(randomForest)
library(stringr)

CCFs_withlands = read.csv("../../../diagnostics-paper/data/raw/CCFs_withlands.csv")

includes <-
  setdiff(
    names(CCFs_withlands),
    c(
      "compare_id",
      "profile1_id",
      "profile2_id",
      "study.x",
      "study.y",
      "barrel.x",
      "barrel.y",
      "bullet.x",
      "bullet.y",
      "land.x",
      "land.y",
      "land_id.x",
      "land_id.y",
      "signature_length",
      "lag",
      "overlap"
    )
  )

set.seed(20170222)
rtrees3 <-
  randomForest(factor(match) ~ ., data = CCFs_withlands[, includes], ntree = 300)

set.seed(20140501)
rtrees2 <-
  randomForest(factor(match) ~ ., data = CCFs_withlands[, includes], ntree = 300)

# plot votes in a scatterplot
plot(rtrees2$votes, rtrees3$votes)
plot(rtrees2$votes[,2], bulletxtrctr::rtrees$votes[,2])
plot(rtrees3$votes[,2], bulletxtrctr::rtrees$votes[,2])

plot(sort(rtrees2$votes[,2]), sort(bulletxtrctr::rtrees$votes[,2]))
plot(sort(rtrees3$votes[,2]), sort(bulletxtrctr::rtrees$votes[,2]))
```

```{r}
hamby_comparisons = read.csv("../../../diagnostics-paper/data/raw/hamby-comparisons.csv") %>%
  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
  select(-bbl1, -bbl2) %>%
  select(-lag, -abs_lag, -overlap, -signature_length, -flag) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())

set.seed(20170222)
rtrees4 <-
  randomForest(
    factor(samesource) ~ .,
    data = hamby_comparisons %>% select(samesource, rownames(bulletr::rtrees$importance)),
    ntree = 300
  )

set.seed(20140501)
rtrees5 <-
  randomForest(
    factor(samesource) ~ .,
    data = hamby_comparisons %>% select(samesource, rownames(bulletr::rtrees$importance)),
    ntree = 300
  )

# plot votes in a scatterplot
plot(rtrees4$votes, rtrees5$votes)
plot(rtrees4$votes, bulletxtrctr::rtrees$votes)
plot(rtrees5$votes, bulletxtrctr::rtrees$votes)

plot(sort(rtrees4$votes), sort(bulletxtrctr::rtrees$votes))
plot(sort(rtrees5$votes), sort(bulletxtrctr::rtrees$votes))
```

### 2020-09-25 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
everything is a mess right now, but pushing this so it doesn't get lost

@@
   filter(study1 != "Cary", study2 != "Cary") %>%
-  mutate(study1 = factor(study1), 
-         study2 = factor(study2))
+  mutate(study1 = factor(study1), study2 = factor(study2))
 ```
@@
 See the R code and output below.
-Note that `hamby173` is currently incorrectly labelled as `hamby44`.
+Note that `hamby173` is currently incorrectly labeled as `hamby44`.
 Both test sets have less than but close to 22,155 rows.
@@
 ```{r}
-# Summary of the number of observations in the Hamby173and252 datase
+# Summary of the number of observations in the Hamby173and252 database
 table(hamby173and252_raw$study1, hamby173and252_raw$study2)
@@
 For the comparisons across studies, the cases with less than expected are also due to tank rash.
-For some reason, the comparisons between bullets 1 from Hamby 173 and Hamby 252, the cells are being colored grey even though they have 36 observations.
+For some reason, the comparisons between bullets 1 from Hamby 173 and Hamby 252, the cells are being colored gray even though they have 36 observations.
 I am not sure why this is...
@@
 # Determine the letters associated with the unknown bullets
-letters <- levels(hamby173and252_raw$barrel1)[11:length(levels(hamby173and252_raw$barrel1))]
+all_barrel_labels <-
+  unique(c(
+    as.character(hamby173and252_raw$barrel1),
+    as.character(hamby173and252_raw$barrel2)
+  ))
+letters <- all_barrel_labels[!(all_barrel_labels %in% 1:10)]
+letters
+
+#letters <- levels(hamby173and252_raw$barrel1)[11:length(levels(hamby173and252_raw$barrel1))]
 
 # Cleaning the testing data
-hamby173and252_train_cleaning <- hamby173and252_raw %>%
+hamby173and252_train_cleaning <- 
+  hamby173and252_raw %>%
   mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
-         study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
-         bullet1 = factor(ifelse(barrel1 %in% letters,
-                                 as.character(barrel1),
-                                 as.character(bullet1))),
-         barrel1 = factor(ifelse(barrel1 %in% letters, 
-                                 as.character("Unknown"), 
-                                 as.character(barrel1))),
-         bullet2 = factor(ifelse(barrel2 %in% letters,
-                                 as.character(barrel2),
-                                 as.character(bullet2))),
-         barrel2 = factor(ifelse(barrel2 %in% letters, 
-                                 as.character("Unknown"), 
-                                 as.character(barrel2))),
-         land1 = factor(land1),
-         land2 = factor(land2),
+         study2 = fct_recode(study2, "Hamby173" = "Hamby44")) %>%
+  mutate(across(is.factor, as.character)) %>%
+  mutate(bullet1 = ifelse(barrel1 %in% letters, barrel1, bullet1),
+         barrel1 = ifelse(barrel1 %in% letters, "Unknown", barrel1),
+         bullet2 = ifelse(barrel2 %in% letters, barrel2, bullet2),
+         barrel2 = ifelse(barrel2 %in% letters, "Unknown", barrel2),
+         land1 = as.character(land1),
+         land2 = as.character(land2),
          rfscore = predict(bulletxtrctr::rtrees, hamby173and252_raw %>%
@@
 hamby173and252_train <- hamby173and252_train_cleaning %>%
-  mutate(bbl1 = barrel1:bullet1:land1,
-         bbl2 = barrel2:bullet2:land2) %>%
+  mutate(bbl1 = paste(barrel1, bullet1, land1, sep = ":"),
+         bbl2 = paste(barrel2, bullet2, land2, sep = ":")) %>%
   filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4") | 
@@
 ```{r}
-# Create dataset for creating the paralle coordinate plot
+# Create dataset for creating the parallel coordinate plot
 par_data <- hamby173and252_train_cleaning %>%
-  mutate(bbl1 = barrel1:bullet1:land1,
-         bbl2 = barrel2:bullet2:land2) %>%
+  mutate(bbl1 = paste(barrel1, bullet1, land1, sep = ":"),
+         bbl2 = paste(barrel2, bullet2, land2, sep = ":")) %>%
   mutate(category = factor(ifelse(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
@@
 It is not clear if these were the ones that were suppose to be removed or not.
-The second plot shows the observations from matches plotted in red, and the third plot shows the observations from nonmatches plotted in black.
+The second plot shows the observations from matches plotted in red, and the third plot shows the observations from non-matches plotted in black.
 
@@
 Below is a parallel coordinate plot of the training dataset.
-It is facetted by `samesource` and colored by `rfscore`.
+It is faceted by `samesource` and colored by `rfscore`.
 The features are sorted by the variable importance scores (descending from left to right) from the `rtrees` model.
@@
 Below is a parallel coordinate plot of the testing dataset.
-It is facetted by `samesource` and colored by `rfscore`.
+It is faceted by `samesource` and colored by `rfscore`.
 You can see a clear distinction between the trends of the feature values from the nonmatches and matches.
 It is interesting to consider the cases in set 1 that are matches but were predicted to be nonmatches by the model.
-These are the cases colored in grey, and their feature values are very different from the observations that were predicted to be matches by the model.
+These are the cases colored in gray, and their feature values are very different from the observations that were predicted to be matches by the model.
 The nonmatch predictions have values that are closer to the nonmatches.
@@
 She also suggested including interactions in the logistic regression model.
-This section includes code for fitting several logisitic regression models.
+This section includes code for fitting several logistic regression models.
 

### 2020-09-25 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
everything is a mess right now, but pushing this so it doesn't get lost

---
title: "Identifying `rtrees` Training Data"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  cache = FALSE, 
  dpi = 300
)
```

This journal contains work to identify the data used to train `rtrees` (contained in both `bulletr` and `bulletxtrctr`). We recently discovered some discrepancies between `rtrees` and the training data we were using (`hamby-comparisons.csv`, previously `features-hamby173and252.csv`). Unfortunately, the original work by Eric is not well documented, so it is difficult to know for sure which dataset was used to train the model. However, Eric recently pointed us to some [code](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R), which he believes was used to train `rtrees`. Heike was able to rerun part of the code to extract data from the CSAFE database that was created by the first part of the code (scans to features). The new data (`CCFs_withlands`) contains the same number of rows the number of predictions associated with `rtrees`. I have gathered all of our work trying to determine that `CCFs_withlands` is the data used to train `rtrees` in this journal.

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(purrr)
library(randomForest)
library(tidyr)
```

# Raw Datasets

This section contains code for loading and performing initial comparisons of the raw datasets.

## Load Data

Load the data provided by Heike and CSAFE that we have been using and believed to be the training data for rtrees:

```{r}
hamby_comparisons <- read.csv("../../../data/raw/hamby-comparisons.csv")
```

Load the data extracted (on 2020-09-23) from the CSAFE database and corresponds to the [R script](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R) Eric believes to be the one used to train `rtrees`.

```{r}
CCFs_withlands <- read.csv("../../../data/raw/CCFs_withlands.csv")
```

Obtain the features used to train `rtrees` for use throughout this journal:

```{r}
rtrees_features <- rownames(bulletxtrctr::rtrees$importance)
```

## Initial Comparisons

Dimensions of the raw datasets:

```{r}
dim(hamby_comparisons)
dim(CCFs_withlands)
```

Note that `CCFs_withlands` has the same number of rows as the number of predictions associated with `rtrees`:

```{r}
length(bulletxtrctr::rtrees$predicted)
```

Comparing summaries of the distributions of the features used to train `rtrees` from the two datasets. Note that I even remove the observations in `hamby_comparisons` known to have tank rash (`flag == FALSE`). The main differences are seen with the distributions of `D` (distance) and `sd_D` (standard deviation of distance).

```{r}
summary(hamby_comparisons %>% filter(flag == FALSE) %>% select(all_of(rtrees_features)))
summary(CCFs_withlands %>% select(all_of(rtrees_features)))
```

Comparing visualizations of the distributions of the features used to train `rtrees` from the two datasets to again see the differences in distributions of `D` and `sd_D`:

```{r fig.width = 10, fig.height = 3}
bind_rows(
  hamby_comparisons %>%
    filter(flag == FALSE) %>%
    select(all_of(rtrees_features)) %>%
    pivot_longer(cols = everything()) %>%
    mutate(dataset = "hamby_comparisons"),
  CCFs_withlands %>% select(all_of(rtrees_features)) %>%
    pivot_longer(cols = everything()) %>%
    mutate(dataset = "CCFs_withlands")
) %>%
  ggplot(aes(x = value, fill = dataset)) + 
  geom_histogram() +
  facet_grid(dataset ~ name)
```

<!-- New data plot: -->

<!-- ```{r} -->
<!-- preds <- -->
<!--   data.frame( -->
<!--     oob = predict(bulletxtrctr::rtrees, type = "prob")[, 2], -->
<!--     all_data = predict( -->
<!--       bulletxtrctr::rtrees, -->
<!--       ccfs_withlands_raw %>% select(all_of(rf_features)), -->
<!--       type = "prob" -->
<!--     )[, 2] -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- preds %>%  -->
<!--   ggplot(aes(x = all_data, y = oob)) +  -->
<!--   geom_point() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- preds %>% -->
<!--   mutate(obs = 1:n()) %>% -->
<!--   pivot_longer(cols = -obs) %>% -->
<!--   ggplot(aes(x = value, fill = name)) +  -->
<!--   geom_density(alpha = 0.5) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- preds %>%  -->
<!--   mutate(diff = oob - all_data) %>% -->
<!--   ggplot(aes(x = diff)) +  -->
<!--   geom_histogram() -->
<!-- ``` -->
<!-- # Data -->

<!-- Load the prepared training data which only has observations with `flag == FALSE` (prepared in the LIME diagnostics paper repository): -->

<!-- ```{r} -->
<!-- bullet_train <- read.csv("../../../diagnostics-paper/data/bullet-train.csv") -->
<!-- ``` -->

<!-- Load the random forest `rtrees` from the `bulletxtrctr` package and the random forest model I recently fit using the `bullet_train` data in the paper: -->

<!-- ```{r} -->
<!-- rtrees <- bulletxtrctr::rtrees -->
<!-- paper_rf <- readRDS("../../../diagnostics-paper/data/bullet-rf.rds") -->
<!-- ``` -->

<!-- Extract the features used to fit `rtrees`: -->

<!-- ```{r} -->
<!-- bullet_features <- rownames(bulletxtrctr::rtrees$importance) -->
<!-- bullet_features -->
<!-- ``` -->

<!-- # `rtrees` versus paper model -->

<!-- The code below was used to fit the random forest in the paper but is not run here: -->

<!-- ```{r eval = FALSE} -->
<!-- set.seed(20160104) -->
<!-- bullet_rf <- -->
<!--   randomForest( -->
<!--     y = factor(bullet_train$samesource), -->
<!--     x = bullet_train %>% select(all_of(bullet_features)), -->
<!--     ntree = bulletxtrctr::rtrees$ntree, -->
<!--     mtry = bulletxtrctr::rtrees$mtry -->
<!--   ) -->
<!-- ``` -->

<!-- Confusion matrices from the two models: -->

<!-- ```{r} -->
<!-- rtrees$confusion -->
<!-- paper_rf$confusion -->
<!-- ``` -->

<!-- Variable importance values: -->

<!-- ```{r} -->
<!-- vi = data.frame( -->
<!--   features = rownames(rtrees$importance), -->
<!--   rtrees = rtrees$importance[, 1], -->
<!--   paper = paper_rf$importance[, 1] -->
<!-- ) -->
<!-- ``` -->

<!-- # New Random Forests -->

<!-- Randomly select 100 seeds (using a random seed):  -->

<!-- ```{r} -->
<!-- set.seed(20200917) -->
<!-- seeds = sample(x = 10000000:100000000, size = 100, replace = FALSE) -->
<!-- seeds -->
<!-- ``` -->

<!-- Function for fitting random forests to mimic rtrees with different seeds: -->

<!-- ```{r} -->
<!-- fit_rf <- function(seed) { -->
<!--   set.seed(seed) -->
<!--   bullet_rf <- -->
<!--     randomForest( -->
<!--       y = factor(bullet_train$samesource), -->
<!--       x = bullet_train %>% select(all_of(bullet_features)), -->
<!--       ntree = bulletxtrctr::rtrees$ntree, -->
<!--       mtry = bulletxtrctr::rtrees$mtry -->
<!--     )   -->
<!-- } -->
<!-- ``` -->

<!-- Fit 100 new random forests and save or load: -->

<!-- ```{r} -->
<!-- # Fit (and save) or load random forests -->
<!-- bullet_rfs_file = "../../../data/bullet_rfs.rds" -->
<!-- if (!file.exists(bullet_rfs_file)) { -->
<!--   bullet_rfs = map(.x = seeds, .f = fit_rf) -->
<!--   saveRDS(object = bullet_rfs, file = bullet_rfs_file) -->
<!-- } else { -->
<!--   bullet_rfs = readRDS(bullet_rfs_file) -->
<!-- } -->
<!-- ``` -->

<!-- Function for extracting the confusion matrices from the model and put in a nice data frame: -->

<!-- ```{r} -->
<!-- extract_confus <- function(model) { -->
<!--   data.frame(model$confusion) %>% -->
<!--   rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>% -->
<!--   mutate(observed = rownames(model$confusion)) %>% -->
<!--   pivot_wider(names_from = observed, values_from = everything())   -->
<!-- } -->
<!-- ``` -->

<!-- Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:  -->

<!-- ```{r} -->
<!-- extract_importance <- function(model) { -->
<!--   data.frame(model$importance) %>% -->
<!--     mutate(features = rownames(model$importance)) %>% -->
<!--     arrange(desc(MeanDecreaseGini)) %>% -->
<!--     mutate(rank = 1:n()) %>% -->
<!--     rename("importance" = "MeanDecreaseGini") %>% -->
<!--     select(features, importance, rank) -->
<!-- } -->
<!-- ``` -->

<!-- Extract the confusion matrices and importance values from all random forest models: -->

<!-- ```{r} -->
<!-- res_confus <- map_df(.x = bullet_rfs, .f = extract_confus, .id = "rf_model_id") -->
<!-- res_importance <- map_df(.x = bullet_rfs, .f = extract_importance, .id = "rf_model_id") -->
<!-- ``` -->

<!-- # Visualizations of Results -->

<!-- ## Class Errors -->

<!-- Obtain the class errors from `rtrees` and the paper random forest: -->

<!-- ```{r} -->
<!-- comparison_values <- -->
<!--   data.frame( -->
<!--     model = c("paper", "rtrees"), -->
<!--     class_error_true = c(paper_rf$confusion[2, 3], rtrees$confusion[2, 3]), -->
<!--     class_error_false = c(paper_rf$confusion[1, 3], rtrees$confusion[1, 3]) -->
<!--   ) -->
<!-- ``` -->

<!-- Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true): -->

<!-- ```{r fig.width = 10, fig.height = 4.5} -->
<!-- hist_true <-  -->
<!--   res_confus %>% -->
<!--   ggplot(aes(x = class_error_TRUE)) + -->
<!--   geom_histogram() + -->
<!--   geom_vline(data = comparison_values, -->
<!--              mapping = aes(xintercept = class_error_true, color = model)) -->

<!-- hist_false <-  -->
<!--   res_confus %>% -->
<!--   ggplot(aes(x = class_error_FALSE)) + -->
<!--   geom_histogram() + -->
<!--   geom_vline(data = comparison_values, -->
<!--              mapping = aes(xintercept = class_error_false, color = model)) -->

<!-- plot_grid(hist_true, hist_false) -->
<!-- ``` -->

<!-- Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models: -->

<!-- ```{r} -->
<!-- ggplot() + -->
<!--   geom_point(data = res_confus, -->
<!--              mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) + -->
<!--   geom_point( -->
<!--     data = comparison_values, -->
<!--     mapping = aes(x = class_error_false, y = class_error_true, color = model) -->
<!--   ) -->
<!-- ``` -->

<!-- ## Variable Importance  -->

<!-- Prepare variable importance from `rtrees` and paper models for plotting: -->

<!-- ```{r} -->
<!-- vi_ranks <-  -->
<!--   vi %>% -->
<!--   arrange(desc(rtrees)) %>% -->
<!--   mutate(rtrees_rank = 1:n()) %>%  -->
<!--   arrange(desc(paper)) %>% -->
<!--   mutate(paper_rank = 1:n()) %>% -->
<!--   select(-rtrees, -paper) %>% -->
<!--   pivot_longer(names_to = "rf_model_id", values_to = "rank", cols = -features) -->
<!-- ``` -->

<!-- Tile plot showing the variable importance ranks for each model showing variability across newly trained models and some agreement (ex: rough_cor and ccf) and some disagreement (ex: sum_peaks and non_cms) with `rtrees`: -->

<!-- ```{r fig.width = 10, fig.height = 4.5} -->
<!-- rtrees_var_order <- -->
<!--   vi_ranks %>% -->
<!--   filter(rf_model_id == "rtrees_rank") %>% -->
<!--   arrange(desc(rank)) %>% -->
<!--   pull(features) -->

<!-- tile_org <- -->
<!--   vi_ranks %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order),  -->
<!--     rf_model_id = factor(rf_model_id, levels = c("rtrees_rank", "paper_rank")) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
<!--   geom_tile() + -->
<!--   scale_fill_brewer(palette = "RdYlBu") -->

<!-- tile_new <- -->
<!--   res_importance %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
<!--   geom_tile() + -->
<!--   scale_fill_brewer(palette = "RdYlBu") -->

<!-- plot_grid(tile_org, tile_new) -->
<!-- ``` -->

<!-- Box plot of ranks across the models with colored points added for the `rtrees` and paper model variable importance ranks (features ordered by `rtrees` variable importance): -->

<!-- ```{r} -->
<!-- res_importance %>% -->
<!--   mutate(features = factor(features, levels = rtrees_var_order)) %>% -->
<!--   ggplot() + -->
<!--   geom_boxplot(aes(x = rank, y = features)) + -->
<!--   geom_jitter( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
<!--     width = 0, -->
<!--     height = 0.2 -->
<!--   ) -->
<!-- ``` -->

<!-- Features versus variable importance ranks for new models (black lines and points) and `rtrees` and paper model (features ordered by `rtrees` variable importance): -->

<!-- ```{r} -->
<!-- res_importance %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rank, y = features, group = rf_model_id)) + -->
<!--   geom_line(alpha = 0.2, size = 2) + -->
<!--   geom_point(alpha = 0.2, size = 3) + -->
<!--   geom_line( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes( -->
<!--       x = rank, -->
<!--       y = features, -->
<!--       group = rf_model_id, -->
<!--       color = rf_model_id -->
<!--     ) -->
<!--   ) + -->
<!--   geom_jitter( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
<!--     width = 0.1, -->
<!--     height = 0 -->
<!--   ) + -->
<!--   labs(title = "new random forest lines and points created with alpha shading") -->
<!-- ``` -->

### 2020-09-25 journals/10-comparing-rfs/10-comparing-rfs.Rmd
everything is a mess right now, but pushing this so it doesn't get lost

@@
 plot(rtrees2$votes, rtrees3$votes)
-plot(rtrees2$votes[,2], bulletxtrctr::rtrees$votes[,2])
-plot(rtrees3$votes[,2], bulletxtrctr::rtrees$votes[,2])
+plot(rtrees2$votes, bulletxtrctr::rtrees$votes)
+plot(rtrees3$votes, bulletxtrctr::rtrees$votes)
 
@@
 plot(sort(rtrees3$votes[,2]), sort(bulletxtrctr::rtrees$votes[,2]))
+
+bulletxtrctr::rtrees$confusion
+rtrees2$confusion
+rtrees3$confusion
 ```

### 2020-09-25 journals/11-training-rtrees-with-CCFs_withlands/11-training-rtrees-with-CCFs_withlands.Rmd
everything is a mess right now, but pushing this so it doesn't get lost

--- 2020-09-25 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
@@
 ---
-title: "Identifying `rtrees` Training Data"
+title: "Experiments with rtrees using `CCFs_withlands` data"
 author: "Katherine Goode"
@@
   eval = TRUE,
-  cache = FALSE, 
-  dpi = 300
+  cache = FALSE
 )
@@
 
-This journal contains work to identify the data used to train `rtrees` (contained in both `bulletr` and `bulletxtrctr`).
-We recently discovered some discrepancies between `rtrees` and the training data we were using (`hamby-comparisons.csv`, previously `features-hamby173and252.csv`).
-Unfortunately, the original work by Eric is not well documented, so it is difficult to know for sure which dataset was used to train the model.
-However, Eric recently pointed us to some [code](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R), which he believes was used to train `rtrees`.
-Heike was able to rerun part of the code to extract data from the CSAFE database that was created by the first part of the code (scans to features).
-The new data (`CCFs_withlands`) contains the same number of rows the number of predictions associated with `rtrees`.
-I have gathered all of our work trying to determine that `CCFs_withlands` is the data used to train `rtrees` in this journal.
+This journal contains the results from 100 new random forests to the bullet training data observations where `flag == FALSE`.
 
@@
 
-# Raw Datasets
+# Data
 
-This section contains code for loading and performing initial comparisons of the raw datasets.
-
-## Load Data
-
-Load the data provided by Heike and CSAFE that we have been using and believed to be the training data for rtrees:
+Load the data Heike extracted from the CSAFE database (on 9/23) which we currently believe is the correct training data for `rtrees`:
 
 ```{r}
-hamby_comparisons <- read.csv("../../../data/raw/hamby-comparisons.csv")
+CCFs_withlands <- read.csv("../../../diagnostics-paper/data/raw/CCFs_withlands.csv")
 ```
 
-Load the data extracted (on 2020-09-23) from the CSAFE database and corresponds to the [R script](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R) Eric believes to be the one used to train `rtrees`.
+Load the random forest `rtrees` from the `bulletxtrctr` package:
 
 ```{r}
-CCFs_withlands <- read.csv("../../../data/raw/CCFs_withlands.csv")
+rtrees <- bulletxtrctr::rtrees
 ```
 
-Obtain the features used to train `rtrees` for use throughout this journal:
+Extract the features used to fit `rtrees`:
 
 ```{r}
-rtrees_features <- rownames(bulletxtrctr::rtrees$importance)
+bullet_features <- rownames(bulletxtrctr::rtrees$importance)
+bullet_features
 ```
 
-## Initial Comparisons
+# Random Forests
 
-Dimensions of the raw datasets:
+Randomly select a large amount of seeds (using a random seed):
 
 ```{r}
-dim(hamby_comparisons)
-dim(CCFs_withlands)
+set.seed(20200925)
+seeds = sample(x = 10000000:100000000, size = 250, replace = FALSE)
+seeds
 ```
 
-Note that `CCFs_withlands` has the same number of rows as the number of predictions associated with `rtrees`:
+Function for fitting random forests to mimic rtrees with different seeds:
 
 ```{r}
-length(bulletxtrctr::rtrees$predicted)
+fit_rf <- function(seed) {
+  set.seed(seed)
+  bullet_rf <-
+    randomForest(
+      y = factor(CCFs_withlands$match),
+      x = CCFs_withlands %>% select(all_of(bullet_features)),
+      ntree = bulletxtrctr::rtrees$ntree,
+      mtry = bulletxtrctr::rtrees$mtry
+    )  
+}
 ```
 
-Comparing summaries of the distributions of the features used to train `rtrees` from the two datasets.
-Note that I even remove the observations in `hamby_comparisons` known to have tank rash (`flag == FALSE`).
-The main differences are seen with the distributions of `D` (distance) and `sd_D` (standard deviation of distance).
+Fit 100 new random forests and save or load:
 
 ```{r}
-summary(hamby_comparisons %>% filter(flag == FALSE) %>% select(all_of(rtrees_features)))
-summary(CCFs_withlands %>% select(all_of(rtrees_features)))
+# Fit (and save) or load random forests
+CCFs_withlands_rfs_file = "../../../data/CCFs_withlands_rfs.rds"
+if (!file.exists(CCFs_withlands_rfs_file)) {
+  CCFs_withlands_rfs = map(.x = seeds, .f = fit_rf)
+  saveRDS(object = CCFs_withlands_rfs, file = CCFs_withlands_rfs_file)
+} else {
+  CCFs_withlands_rfs = readRDS(CCFs_withlands_rfs_file)
+}
 ```
 
-Comparing visualizations of the distributions of the features used to train `rtrees` from the two datasets to again see the differences in distributions of `D` and `sd_D`:
+Function for extracting the confusion matrices from the model and put in a nice data frame:
 
-```{r fig.width = 10, fig.height = 3}
-bind_rows(
-  hamby_comparisons %>%
-    filter(flag == FALSE) %>%
-    select(all_of(rtrees_features)) %>%
-    pivot_longer(cols = everything()) %>%
-    mutate(dataset = "hamby_comparisons"),
-  CCFs_withlands %>% select(all_of(rtrees_features)) %>%
-    pivot_longer(cols = everything()) %>%
-    mutate(dataset = "CCFs_withlands")
-) %>%
-  ggplot(aes(x = value, fill = dataset)) + 
-  geom_histogram() +
-  facet_grid(dataset ~ name)
+```{r}
+extract_confus <- function(model) {
+  data.frame(model$confusion) %>%
+  rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>%
+  mutate(observed = rownames(model$confusion)) %>%
+  pivot_wider(names_from = observed, values_from = everything())  
+}
 ```
 
-<!-- New data plot: -->
+Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:
 
-<!-- ```{r} -->
-<!-- preds <- -->
-<!--   data.frame( -->
-<!--     oob = predict(bulletxtrctr::rtrees, type = "prob")[, 2], -->
-<!--     all_data = predict( -->
-<!--       bulletxtrctr::rtrees, -->
-<!--       ccfs_withlands_raw %>% select(all_of(rf_features)), -->
-<!--       type = "prob" -->
-<!--     )[, 2] -->
-<!--   ) -->
-<!-- ``` -->
+```{r}
+extract_importance <- function(model) {
+  data.frame(model$importance) %>%
+    mutate(features = rownames(model$importance)) %>%
+    arrange(desc(MeanDecreaseGini)) %>%
+    mutate(rank = 1:n()) %>%
+    rename("importance" = "MeanDecreaseGini") %>%
+    select(features, importance, rank)
+}
+```
 
-<!-- ```{r} -->
-<!-- preds %>%  -->
-<!--   ggplot(aes(x = all_data, y = oob)) +  -->
-<!--   geom_point() -->
-<!-- ``` -->
+Extract the confusion matrices and importance values from all random forest models:
 
-<!-- ```{r} -->
-<!-- preds %>% -->
-<!--   mutate(obs = 1:n()) %>% -->
-<!--   pivot_longer(cols = -obs) %>% -->
-<!--   ggplot(aes(x = value, fill = name)) +  -->
-<!--   geom_density(alpha = 0.5) -->
-<!-- ``` -->
+```{r}
+res_confus <- map_df(.x = CCFs_withlands_rfs, .f = extract_confus, .id = "rf_model_id")
+res_importance <- map_df(.x = CCFs_withlands_rfs, .f = extract_importance, .id = "rf_model_id")
+```
 
-<!-- ```{r} -->
-<!-- preds %>%  -->
-<!--   mutate(diff = oob - all_data) %>% -->
-<!--   ggplot(aes(x = diff)) +  -->
-<!--   geom_histogram() -->
-<!-- ``` -->
-<!-- # Data -->
+# Visualizations of Results
 
-<!-- Load the prepared training data which only has observations with `flag == FALSE` (prepared in the LIME diagnostics paper repository): -->
+## Class Errors
 
-<!-- ```{r} -->
-<!-- bullet_train <- read.csv("../../../diagnostics-paper/data/bullet-train.csv") -->
-<!-- ``` -->
+Obtain the class errors from `rtrees` and the paper random forest:
 
-<!-- Load the random forest `rtrees` from the `bulletxtrctr` package and the random forest model I recently fit using the `bullet_train` data in the paper: -->
+```{r}
+comparison_values <-
+  data.frame(
+    model = "rtrees",
+    class_error_true = rtrees$confusion[2, 3],
+    class_error_false = rtrees$confusion[1, 3]
+  )
+```
 
-<!-- ```{r} -->
-<!-- rtrees <- bulletxtrctr::rtrees -->
-<!-- paper_rf <- readRDS("../../../diagnostics-paper/data/bullet-rf.rds") -->
-<!-- ``` -->
+Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true):
 
-<!-- Extract the features used to fit `rtrees`: -->
+```{r fig.width = 10, fig.height = 4.5}
+hist_true <- 
+  res_confus %>%
+  ggplot(aes(x = class_error_TRUE)) +
+  geom_histogram() +
+  geom_vline(data = comparison_values,
+             mapping = aes(xintercept = class_error_true, color = model))
 
-<!-- ```{r} -->
-<!-- bullet_features <- rownames(bulletxtrctr::rtrees$importance) -->
-<!-- bullet_features -->
-<!-- ``` -->
+hist_false <- 
+  res_confus %>%
+  ggplot(aes(x = class_error_FALSE)) +
+  geom_histogram() +
+  geom_vline(data = comparison_values,
+             mapping = aes(xintercept = class_error_false, color = model))
 
-<!-- # `rtrees` versus paper model -->
+plot_grid(hist_true, hist_false)
+```
 
-<!-- The code below was used to fit the random forest in the paper but is not run here: -->
+Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models:
 
-<!-- ```{r eval = FALSE} -->
-<!-- set.seed(20160104) -->
-<!-- bullet_rf <- -->
-<!--   randomForest( -->
-<!--     y = factor(bullet_train$samesource), -->
-<!--     x = bullet_train %>% select(all_of(bullet_features)), -->
-<!--     ntree = bulletxtrctr::rtrees$ntree, -->
-<!--     mtry = bulletxtrctr::rtrees$mtry -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- Confusion matrices from the two models: -->
-
-<!-- ```{r} -->
-<!-- rtrees$confusion -->
-<!-- paper_rf$confusion -->
-<!-- ``` -->
-
-<!-- Variable importance values: -->
-
-<!-- ```{r} -->
-<!-- vi = data.frame( -->
-<!--   features = rownames(rtrees$importance), -->
-<!--   rtrees = rtrees$importance[, 1], -->
-<!--   paper = paper_rf$importance[, 1] -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- # New Random Forests -->
-
-<!-- Randomly select 100 seeds (using a random seed):  -->
-
-<!-- ```{r} -->
-<!-- set.seed(20200917) -->
-<!-- seeds = sample(x = 10000000:100000000, size = 100, replace = FALSE) -->
-<!-- seeds -->
-<!-- ``` -->
-
-<!-- Function for fitting random forests to mimic rtrees with different seeds: -->
-
-<!-- ```{r} -->
-<!-- fit_rf <- function(seed) { -->
-<!--   set.seed(seed) -->
-<!--   bullet_rf <- -->
-<!--     randomForest( -->
-<!--       y = factor(bullet_train$samesource), -->
-<!--       x = bullet_train %>% select(all_of(bullet_features)), -->
-<!--       ntree = bulletxtrctr::rtrees$ntree, -->
-<!--       mtry = bulletxtrctr::rtrees$mtry -->
-<!--     )   -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Fit 100 new random forests and save or load: -->
-
-<!-- ```{r} -->
-<!-- # Fit (and save) or load random forests -->
-<!-- bullet_rfs_file = "../../../data/bullet_rfs.rds" -->
-<!-- if (!file.exists(bullet_rfs_file)) { -->
-<!--   bullet_rfs = map(.x = seeds, .f = fit_rf) -->
-<!--   saveRDS(object = bullet_rfs, file = bullet_rfs_file) -->
-<!-- } else { -->
-<!--   bullet_rfs = readRDS(bullet_rfs_file) -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Function for extracting the confusion matrices from the model and put in a nice data frame: -->
-
-<!-- ```{r} -->
-<!-- extract_confus <- function(model) { -->
-<!--   data.frame(model$confusion) %>% -->
-<!--   rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>% -->
-<!--   mutate(observed = rownames(model$confusion)) %>% -->
-<!--   pivot_wider(names_from = observed, values_from = everything())   -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:  -->
-
-<!-- ```{r} -->
-<!-- extract_importance <- function(model) { -->
-<!--   data.frame(model$importance) %>% -->
-<!--     mutate(features = rownames(model$importance)) %>% -->
-<!--     arrange(desc(MeanDecreaseGini)) %>% -->
-<!--     mutate(rank = 1:n()) %>% -->
-<!--     rename("importance" = "MeanDecreaseGini") %>% -->
-<!--     select(features, importance, rank) -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Extract the confusion matrices and importance values from all random forest models: -->
-
-<!-- ```{r} -->
-<!-- res_confus <- map_df(.x = bullet_rfs, .f = extract_confus, .id = "rf_model_id") -->
-<!-- res_importance <- map_df(.x = bullet_rfs, .f = extract_importance, .id = "rf_model_id") -->
-<!-- ``` -->
-
-<!-- # Visualizations of Results -->
-
-<!-- ## Class Errors -->
-
-<!-- Obtain the class errors from `rtrees` and the paper random forest: -->
-
-<!-- ```{r} -->
-<!-- comparison_values <- -->
-<!--   data.frame( -->
-<!--     model = c("paper", "rtrees"), -->
-<!--     class_error_true = c(paper_rf$confusion[2, 3], rtrees$confusion[2, 3]), -->
-<!--     class_error_false = c(paper_rf$confusion[1, 3], rtrees$confusion[1, 3]) -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true): -->
-
-<!-- ```{r fig.width = 10, fig.height = 4.5} -->
-<!-- hist_true <-  -->
-<!--   res_confus %>% -->
-<!--   ggplot(aes(x = class_error_TRUE)) + -->
-<!--   geom_histogram() + -->
-<!--   geom_vline(data = comparison_values, -->
-<!--              mapping = aes(xintercept = class_error_true, color = model)) -->
-
-<!-- hist_false <-  -->
-<!--   res_confus %>% -->
-<!--   ggplot(aes(x = class_error_FALSE)) + -->
-<!--   geom_histogram() + -->
-<!--   geom_vline(data = comparison_values, -->
-<!--              mapping = aes(xintercept = class_error_false, color = model)) -->
-
-<!-- plot_grid(hist_true, hist_false) -->
-<!-- ``` -->
-
-<!-- Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models: -->
-
-<!-- ```{r} -->
-<!-- ggplot() + -->
-<!--   geom_point(data = res_confus, -->
-<!--              mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) + -->
-<!--   geom_point( -->
-<!--     data = comparison_values, -->
-<!--     mapping = aes(x = class_error_false, y = class_error_true, color = model) -->
-<!--   ) -->
-<!-- ``` -->
+```{r}
+ggplot() +
+  geom_point(data = res_confus,
+             mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) +
+  geom_point(
+    data = comparison_values,
+    mapping = aes(x = class_error_false, y = class_error_true, color = model)
+  )
+```
 

### 2020-09-26 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
still a mess but did some more work

@@
 Heike was able to rerun part of the code to extract data from the CSAFE database that was created by the first part of the code (scans to features).
-The new data (`CCFs_withlands`) contains the same number of rows the number of predictions associated with `rtrees`.
+The new data (`CCFs_withlands.csv`) contains the same number of rows the number of predictions associated with `rtrees`.
 I have gathered all of our work trying to determine that `CCFs_withlands` is the data used to train `rtrees` in this journal.
@@
 library(randomForest)
+library(stringr)
 library(tidyr)
@@
 ```{r}
-hamby_comparisons <- read.csv("../../../data/raw/hamby-comparisons.csv")
+hamby_comparisons_raw <- read.csv("../../../data/raw/hamby-comparisons.csv")
 ```
@@
 ```{r}
-CCFs_withlands <- read.csv("../../../data/raw/CCFs_withlands.csv")
+CCFs_withlands_raw <- read.csv("../../../data/raw/CCFs_withlands.csv")
 ```
@@
 ```{r}
-dim(hamby_comparisons)
-dim(CCFs_withlands)
+dim(hamby_comparisons_raw)
+dim(CCFs_withlands_raw)
 ```
@@
 Comparing summaries of the distributions of the features used to train `rtrees` from the two datasets.
-Note that I even remove the observations in `hamby_comparisons` known to have tank rash (`flag == FALSE`).
-The main differences are seen with the distributions of `D` (distance) and `sd_D` (standard deviation of distance).
+Note that the main differences are seen with the distributions of `D` (distance) and `sd_D` (standard deviation of distance):
 
 ```{r}
-summary(hamby_comparisons %>% filter(flag == FALSE) %>% select(all_of(rtrees_features)))
-summary(CCFs_withlands %>% select(all_of(rtrees_features)))
+summary(hamby_comparisons_raw %>% select(all_of(rtrees_features)))
+summary(CCFs_withlands_raw %>% select(all_of(rtrees_features)))
+```
+
+This result is even true when the observations in `hamby_comparisons` known to have tank rash (`flag == FALSE`) are removed.
+This seems to suggest that the units of `D` and `sd_D` changed from `CCFs_withlands`:
+
+```{r}
+summary(hamby_comparisons_raw %>% filter(flag == FALSE) %>% select(all_of(rtrees_features)))
 ```
@@
 bind_rows(
-  hamby_comparisons %>%
+  hamby_comparisons_raw %>%
     filter(flag == FALSE) %>%
@@
     mutate(dataset = "hamby_comparisons"),
-  CCFs_withlands %>% select(all_of(rtrees_features)) %>%
+  CCFs_withlands_raw %>% select(all_of(rtrees_features)) %>%
     pivot_longer(cols = everything()) %>%
@@
 ```
+
+# Data Cleaning
+
+There are discrepancies in the naming conventions of the two datasets. This section contains the code that identifies the differences and cleans the data.
+
+## Extracting Variables of Interest
+
+The following variables are contained in the raw versions of the data.
+Note that they have different variables and different names.
+For our analysis, we only need the variables identifying the lands, the features used to train `rtrees`, the ground truth for whether or not the bullets are a match, and variables flagging bullets with tank rash.
+
+```{r}
+names(hamby_comparisons_raw)
+names(CCFs_withlands_raw)
+```
+
+The code below separates the land id variables in `hamby_comparisons_raw` into separate columns for study, barrel, bullet, and land and selects only the variables of interest.
+
+```{r}
+hamby_comparisons_select <- 
+  hamby_comparisons_raw %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2")) %>%
+  select(
+    study1,
+    barrel1,
+    bullet1,
+    land1,
+    study2,
+    barrel2,
+    bullet2,
+    land2,
+    all_of(rtrees_features),
+    same_source,
+    flag
+  )
+```
+
+The code below renames some of the variables in `CCFs_withlands_raw`, selects only the variables of interest, and converts all land labels to characters.
+
+```{r}
+CCFs_withlands_select <- 
+  CCFs_withlands_raw %>%
+  rename(
+    "study1" = "study.x",
+    "barrel1" = "barrel.x",
+    "bullet1" = "bullet.x",
+    "land1" = "land.x",
+    "study2" = "study.y",
+    "barrel2" = "barrel.y",
+    "bullet2" = "bullet.y",
+    "land2" = "land.y",
+    "same_source"= "match"
+  ) %>%
+  select(
+    study1,
+    barrel1,
+    bullet1,
+    land1,
+    study2,
+    barrel2,
+    bullet2,
+    land2,
+    all_of(rtrees_features),
+    same_source
+  ) %>%
+  mutate(across(c(bullet1, land1, bullet2, land2), as.character))
+```
+
+Check to make sure the structures of the two datasets agree:
+
+```{r}
+hamby_comparisons_select %>% str()
+CCFs_withlands_select %>% str()
+```
+
+## Matching Labels
+
+The function below extracts the labels from the two datasets for a given variable name `var` and creates a plot to show the discrepancies between `hamby_comparison_select` and `CCFs_withlands_select`.
+
+```{r}
+plot_labels <- function(var, ccf_data) {
+
+  # Extract the labels
+  hc_labels <-
+    unique(c(
+      hamby_comparisons_select %>% pull(paste0(var, "1")),
+      hamby_comparisons_select %>% pull(paste0(var, "2"))
+    ))
+  ccfwl_labels <-
+    unique(c(
+      ccf_data %>% pull(paste0(var, "1")),
+      ccf_data %>% pull(paste0(var, "2"))
+    ))
+
+  # Plot the labels
+  data.frame(data = c(
+    rep("hamby comparisons", length(hc_labels)),
+    rep("CCFs with lands", length(ccfwl_labels))
+  ),
+  labels = c(hc_labels, ccfwl_labels)) %>%
+    ggplot(aes(x = labels, y = data)) +
+    geom_tile() +
+    labs(x = "", y = "", title = paste("Comparing labels in variable:", var))  
+}
+```
+
+The plots below show that the following changes need to be made to `CCFs_withlands_select` in order to match with `hamby_comparison_select`: 
+  - study label of `Hamby44` needs to be changed to `Hamby173`
+  - lettered barrels need to be changed to `BrUnk` and `Br` needs to be added to other barrels
+  - barrel letters need to be made the bullet label and `B` needs to be added to all bullets
+  - `L` needs to be added to lands
+
+```{r fig.width = 14, fig.height = 2.5}
+plot_labels(var = "study", ccf_data = CCFs_withlands_select)
+plot_labels(var = "barrel", ccf_data = CCFs_withlands_select)
+plot_labels(var = "bullet", ccf_data = CCFs_withlands_select)
+plot_labels(var = "land", ccf_data = CCFs_withlands_select)
+```
+
+Determine the letters in the `CCFs_withlands_select` unkown barrels:
+
+```{r}
+all_barrel_labels <-
+  unique(c(
+    as.character(CCFs_withlands_select$barrel1),
+    as.character(CCFs_withlands_select$barrel2)
+  ))
+letters <- all_barrel_labels[!(all_barrel_labels %in% 1:10)]
+letters
+```
+
+Clean `CCFs_withlands_select` so the labels match `bullet_train_raw`:
+
+```{r}
+CCFs_withlands_labelled <- 
+  CCFs_withlands_select %>%
+  mutate(
+    study1 = ifelse(study1 == "Hamby44", "Hamby173", study1),
+    study2 = ifelse(study2 == "Hamby44", "Hamby173", study2),
+    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
+    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
+    ) %>%
+  mutate(
+    barrel1 = paste0("Br", barrel1),
+    bullet1 = paste0("B", bullet1),
+    land1 = paste0("L", land1),
+    barrel2 = paste0("Br", barrel2),
+    bullet2 = paste0("B", bullet2),
+    land2 = paste0("L", land2)
+  )
+```
+
+The plots below show that the labels are now in agreement:
+
+```{r fig.width = 14, fig.height = 2.5}
+plot_labels(var = "study", ccf_data = CCFs_withlands_labelled)
+plot_labels(var = "barrel", ccf_data = CCFs_withlands_labelled)
+plot_labels(var = "bullet", ccf_data = CCFs_withlands_labelled)
+plot_labels(var = "land", ccf_data = CCFs_withlands_labelled)
+```
+
+## Final Touches
+
+Create the land ids for both datasets:
+
+```{r}
+hamby_comparisons <-
+  hamby_comparisons_select %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, all_of(rtrees_features), same_source, flag)
+
+CCFs_withlands <-
+  CCFs_withlands_labelled %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, all_of(rtrees_features), same_source)
+```
+
+The structures of the cleaned data:
+
+```{r}
+hamby_comparisons %>% str()
+CCFs_withlands %>% str()
+```
+
+# Land ID Differences
+
+This section considers the differences in bullets included in the two datasets. The code below extracts the unique land IDs from the two datasets:
+
+```{r}
+hamby_comparisons_ids = unique(c(hamby_comparisons$land_id1, hamby_comparisons$land_id2))
+CCFs_withlands_ids = unique(c(CCFs_withlands$land_id1, CCFs_withlands$land_id2))
+```
+
+Below are the number of bullets contained in each of the datasets. There are less in `CCFs_withlands` than `hamby_comparisons`:
+
+```{r}
+length(hamby_comparisons_ids)
+length(CCFs_withlands_ids)
+```
+
+Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons`:
+
+```{r}
+CCFs_withlands_ids[!(CCFs_withlands_ids %in% hamby_comparisons_ids)]
+```
+
+Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands`:
+
+```{r}
+hamby_comparisons_ids[!(hamby_comparisons_ids %in% CCFs_withlands_ids)]
+```
+
+# Comparisons to rtrees
+
+## Dimensions
+
+One of the aspects which led to the realization that the `hamby-comparisons` data is not the training data for `rtrees` is that the number of observations in the data do not agree with the number of predictions in the `rtrees` model.
+The number of observations used to train `rtrees` is the following:
+
+```{r}
+length(bulletxtrctr::rtrees$predicted)
+```
+
+Here are the dimensions of the `hamby_comparisons` data which does not agree with the number of observations used to train `rtrees`:
+
+```{r}
+hamby_comparisons %>% dim()
+```
+
+Even with the observations removed that are known to have tank rash (`flag != FALSE`), the dimensions of the `hamby_comparisons` data do not agree with `rtrees`:
+
+```{r}
+hamby_comparisons %>% filter(flag == FALSE) %>% dim()
+```
+
+In the Hare, Hofmann, and Carriquiry (2017), they describe removing four land impressions that were flagged for quality assessment:
+
+- Barrel 6 Bullet 2-1
+- Barrel 9 Bullet 2-4
+- Unknown Bullet B-2
+- Unknown Bullet Q-4
+
+These lands should correspond to Hamby 252.
+However, it is possible to obtain the same number of observations as used to train `rtrees` by filtering out observations in `hamby_comparisons` using these barrel, bullet, and land combinations without specifying the study (that is removing observations from both Hamby 173 and Hamby 252).
+
+```{r}
+hamby_comparisons_filtered <- 
+  hamby_comparisons %>%
+  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
+         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
+  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
+           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
+  select(-bbl1, -bbl2)
+hamby_comparisons_filtered %>% dim()
+```
+
+While it is possible to use `hamby_comparisons` to get to the same number of observations as `rtrees`, it is only a guess as to how the bullets were removed.
+On the other hand, the number of rows in `CCFs_withlands` already has the same number of rows as `rtrees`:
+
+```{r}
+CCFs_withlands %>% dim()
+```
+
+# Old Code
+
+<!-- The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`: -->
+
+<!-- ```{r} -->
+<!-- bullet_train_eric_filter <-  -->
+<!--   bullet_train_raw %>% -->
+<!--   separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>% -->
+<!--   separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>% -->
+<!--   filter(study1 != "Hamby173" | bullet1 != "BE") %>% -->
+<!--   filter(study2 != "Hamby173" | bullet2 != "BE") -->
+
+<!-- # Eric's code for reference: -->
+<!-- # filter(study.y != "Hamby44" | barrel.y != "E") %>% -->
+<!-- # filter(study.x != "Hamby44" | barrel.x != "E") %>% -->
+<!-- ``` -->
+
+<!-- Here, the dimensions to not agree with the number of observations in `rtrees`: -->
+
+<!-- ```{r} -->
+<!-- dim(bullet_train_eric_filter) -->
+<!-- length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1] -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- bullet_train_eric_filter_v2 <- -->
+<!--   bullet_train_raw %>% -->
+<!--   mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"), -->
+<!--          bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>% -->
+<!--   filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") |  -->
+<!--            bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>% -->
+<!--   select(-bbl1, -bbl2) %>% -->
+<!--   separate(col = "land_id1", -->
+<!--            into = c("study1", "barrel1", "bullet1", "land1")) %>% -->
+<!--   separate(col = "land_id2", -->
+<!--            into = c("study2", "barrel2", "bullet2", "land2")) %>% -->
+<!--   filter(study1 != "Hamby173" | bullet1 != "BE") %>% -->
+<!--   filter(study2 != "Hamby173" | bullet2 != "BE") -->
+
+<!-- dim(bullet_train_eric_filter_v2) -->
+<!-- length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter_v2)[1] -->
+<!-- ``` -->
+
+<!-- Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data: -->
+
+<!-- ```{r} -->
+<!-- rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2] -->
+
+<!-- new_pred = predict(bulletxtrctr::rtrees,  -->
+<!--                    bullet_train_filtered %>%  -->
+<!--                      select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2] -->
+
+<!-- new_pred_full = predict(bulletxtrctr::rtrees,  -->
+<!--                         bullet_train_raw %>% -->
+<!--                           select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2] -->
+<!-- ``` -->
+
+<!-- Plot comparing the two predictions (we discovered that the `predict` function from random forest returns different results when applied to only the model (out-of-bag predictions) and the training data (regular predictions), so this is not a good way to test for agreement between training data and models): -->
+
+<!-- ```{r} -->
+<!-- data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred)) %>% -->
+<!--   ggplot(aes(rtrees_pred, new_pred)) +  -->
+<!--   geom_point() -->
+<!-- ``` -->
+
+<!-- Plot showing distributions of predictions from `rtrees` and new predictions made on full training data (same comment here as above about not being able to use this to determine if we have the correct training data for the model): -->
+
+<!-- ```{r} -->
+<!-- data.frame(data = c(rep("rtrees", length(rtrees_pred)),  -->
+<!--                     rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>% -->
+<!--   ggplot(aes(x = pred, fill = data)) +  -->
+<!--   geom_density(alpha = 0.75) -->
+<!-- ``` -->
+
+<!-- Comparison to the data Eric Hare said was used to fit `rtrees` which has half the number of observations as the number of rtrees predictions:  -->
+
+<!-- ```{r} -->
+<!-- eric <- read.csv("https://raw.githubusercontent.com/erichare/imaging-paper/master/data/data-25-25/bullet-stats.csv") -->
+<!-- dim(eric) -->
+<!-- ``` -->
 
@@
 <!-- ``` -->
+
+# Session Info
+
+```{r}
+sessionInfo()
+```

### 2020-09-28 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
working on documenting the comparisons of two trainin datasets

@@
   ) %>%
-  mutate(across(c(bullet1, land1, bullet2, land2), as.character))
+  mutate(across(c(barrel1, bullet1, land1, barrel2, bullet2, land2), as.character))
 ```
@@
 
-Determine the letters in the `CCFs_withlands_select` unkown barrels:
+Determine the letters in the `CCFs_withlands_select` unknown barrels:
 
@@
     study2 = ifelse(study2 == "Hamby44", "Hamby173", study2),
-    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    bullet1 = ifelse(barrel1 %in% letters, barrel1, bullet1),
     barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
-    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    bullet2 = ifelse(barrel2 %in% letters, barrel2, bullet2),
     barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
@@
 CCFs_withlands %>% str()
+```
+
+```{r}
+length(unique(c(CCFs_withlands$land_id1, CCFs_withlands$land_id2)))
 ```
@@
 
+The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
+
+```{r}
+bullet_train_eric_filter <-
+  hamby_comparisons %>%
+  separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
+  filter(study2 != "Hamby173" | bullet2 != "BE")
+
+# Eric's code for reference:
+# filter(study.y != "Hamby44" | barrel.y != "E") %>%
+# filter(study.x != "Hamby44" | barrel.x != "E") %>%
+```
+
+Again, the dimensions do not agree with the number of observations in `rtrees`:
+
+```{r}
+dim(bullet_train_eric_filter)
+length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1]
+```
+
 In the Hare, Hofmann, and Carriquiry (2017), they describe removing four land impressions that were flagged for quality assessment:
@@
 
+Note that if the code used in Eric Hare's [R script](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R), which he thinks may be the code used to train `rtrees`), is used to filter `CCFs_withlands`, the number of rows does not change!
+
+```{r}
+CCFs_withlands %>%
+  separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
+  filter(study2 != "Hamby173" | bullet2 != "BE") %>% dim()
+```
+
+## Predictions
+
+It is not possible to directly compare the internal predictions from `rtrees` (`predict(bulletxtrctr::rtrees, type = "prob")[,2])`) to those obtained by using `rtrees` to make predictions on the `hamby_comparisons` and `CCFs_withlands` data, because those obtained using the `predict` function from `randomForest` are the out-of-bag (OOB) predictions.
+The predictions obtained by using the `predict` function from `randomForest` to obtain predictions on a new dataset are created using all the training data.
+From the documentation for `randomForest:::predict.randomForest`:
+
+> `newdata`: a data frame or matrix containing new data. (Note: If not given, the out-of-bag prediction in object is returned.
+
+This was determined by Heike based on the following code.
+She pointed out, "Have a look at the code below - we would expect a line of identity in the last plot.
+Sorting values also does not help (that would help in case the observations got re-ordered internally in some way).
+"
+
+```{r}
+x1 <- rnorm(1000)
+x2 <- rnorm(1000)
+x3 <- rnorm(1000)
+z <- rbinom(1000,1, 0.4)
+
+dframe <- data.frame(x1,x2,x3,z)
+
+rf1 <- randomForest(factor(z)~x1+x2+x3, data = dframe)
+
+dframe$predict <- predict(rf1, newdata=dframe, type="prob")[,2]
+dframe$rfscore <- predict(rf1, type="prob")[,2]
+
+dframe %>% 
+  ggplot(aes(x = predict, y = rfscore)) + geom_point()
+```
+
+However, we may still gain some insights by comparing the distributions of the predictions.
+The code below extracts the predictions on the training data from `rtrees` and uses `rtrees` to make predictions on `hamby_comparisons` and `CCFs_withlands`:
+
+```{r}
+rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
+hc_pred = predict(bulletxtrctr::rtrees, hamby_comparisons %>% select(rtrees_features), type = "prob")[,2]
+ccfwl_pred = predict(bulletxtrctr::rtrees, CCFs_withlands %>% select(rtrees_features), type = "prob")[,2]
+
+all_pred <-
+  data.frame(
+    dataset = c(
+      rep("internal", length(rtrees_pred)),
+      rep("Hamby comparisons", length(hc_pred)),
+      rep("CCFs with lands", length(ccfwl_pred))
+    ),
+    pred = c(rtrees_pred, hc_pred, ccfwl_pred)
+  )
+```
+
+Plot showing distributions of three set of predictions from `rtrees`: (light blue) internal predictions from `rtrees`, (blue) predictions obtained by applying `rtrees` to the observations in the `CCFs_withlands` data, and (purple) predictions obtained by applying `rtrees` to the observations in the `hamby_comparisons` data.
+Note that even though the internal predictions from `rtrees` are OOB and those computed using `CCFs_withlands` are not OOB, the distributions are very similar.
+On the other hand, the predictions from `hamby_comparions` are very different.
+This provides evidence that `rtrees` was trained on `CCFs_withlands`, and the change in units of `D` and `sd_D` in `hamby_comparisons` is apparent by the much different distribution of predictions from `rtrees`:
+
+```{r}
+all_pred %>%
+  ggplot(aes(x = pred, fill = dataset, color = dataset)) +
+  geom_density(alpha = 0.5, size = 1) +
+  scale_fill_manual(values = c("blue", "purple", "lightblue")) + 
+  scale_color_manual(values = c("blue", "purple", "lightblue")) +
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  labs(x = "rtrees predictions",
+       y = "Density",
+       fill = "Data predictions computed on",
+       color = "Data predictions computed on")
+```
+The four plots below show direct comparisons of predictions between the internal `rtrees` predictions and those computed on `hamby_comparisons` and `CCFs_withlands` using `rtrees`.
+There are two versions of the plots for each of the possible training datasets.
+One plots the predictions without adjusting the order of the predictions in any way.
+The other plot sorts the predictions from lowest to highest (for a dataset) in case it helps to see a direct relationship.
+None of the figures show a 1-to-1 relationship, but notice that the plot with the title "Comparing internal to CCFs with lands (not sorted)" looks very similar to the one created by Heike with the example data and random forest.
+This is additional evidence that `CCFs_withlands` was used to train `rtrees` since even without sorting the predictions, the relationship between the OOB and new predictions is very similar to an example where we know the same training data was used.
+
+```{r fig.width = 12, fig.height = 10}
+plot_grid(
+  all_pred %>%
+    filter(dataset != "CCFs with lands") %>%
+    group_by(dataset) %>%
+    mutate(case = 1:n()) %>%
+    pivot_wider(names_from = "dataset", values_from = "pred") %>%
+    ggplot(aes(x = `Hamby comparisons`, y = internal)) +
+    geom_point() + 
+    theme(aspect.ratio = 1) +
+    labs(title = "Comparing internal to Hamby Comparisons (not sorted)"),
+  all_pred %>%
+    filter(dataset != "CCFs with lands") %>%
+    group_by(dataset) %>%
+    arrange(pred) %>%
+    mutate(case = 1:n()) %>%
+    pivot_wider(names_from = "dataset", values_from = "pred") %>%
+    ggplot(aes(x = `Hamby comparisons`, y = internal)) +
+    geom_point() + 
+    theme(aspect.ratio = 1) +
+    labs(title = "Comparing internal to Hamby Comparisons (sorted)"),
+  all_pred %>%
+    filter(dataset != "Hamby comparisons") %>%
+    group_by(dataset) %>%
+    mutate(case = 1:n()) %>%
+    pivot_wider(names_from = "dataset", values_from = "pred") %>%
+    ggplot(aes(x = `CCFs with lands`, y = internal)) +
+    geom_point() + 
+    theme(aspect.ratio = 1) +
+    labs(title = "Comparing internal to CCFs with lands (not sorted)"), 
+  all_pred %>%
+    filter(dataset != "Hamby comparisons") %>%
+    group_by(dataset) %>%
+    arrange(pred) %>%
+    mutate(case = 1:n()) %>%
+    pivot_wider(names_from = "dataset", values_from = "pred") %>%
+    ggplot(aes(x = `CCFs with lands`, y = internal)) +
+    geom_point() + 
+    theme(aspect.ratio = 1) +
+    labs(title = "Comparing internal to CCFs with lands (sorted)")
+)
+```
+
 # Old Code
-
-<!-- The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`: -->
-
-<!-- ```{r} -->
-<!-- bullet_train_eric_filter <-  -->
-<!--   bullet_train_raw %>% -->
-<!--   separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>% -->
-<!--   separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>% -->
-<!--   filter(study1 != "Hamby173" | bullet1 != "BE") %>% -->
-<!--   filter(study2 != "Hamby173" | bullet2 != "BE") -->
-
-<!-- # Eric's code for reference: -->
-<!-- # filter(study.y != "Hamby44" | barrel.y != "E") %>% -->
-<!-- # filter(study.x != "Hamby44" | barrel.x != "E") %>% -->
-<!-- ``` -->
-
-<!-- Here, the dimensions to not agree with the number of observations in `rtrees`: -->
-
-<!-- ```{r} -->
-<!-- dim(bullet_train_eric_filter) -->
-<!-- length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1] -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- bullet_train_eric_filter_v2 <- -->
-<!--   bullet_train_raw %>% -->
-<!--   mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"), -->
-<!--          bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>% -->
-<!--   filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") |  -->
-<!--            bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>% -->
-<!--   select(-bbl1, -bbl2) %>% -->
-<!--   separate(col = "land_id1", -->
-<!--            into = c("study1", "barrel1", "bullet1", "land1")) %>% -->
-<!--   separate(col = "land_id2", -->
-<!--            into = c("study2", "barrel2", "bullet2", "land2")) %>% -->
-<!--   filter(study1 != "Hamby173" | bullet1 != "BE") %>% -->
-<!--   filter(study2 != "Hamby173" | bullet2 != "BE") -->
-
-<!-- dim(bullet_train_eric_filter_v2) -->
-<!-- length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter_v2)[1] -->
-<!-- ``` -->
-
-<!-- Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data: -->
-
-<!-- ```{r} -->
-<!-- rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2] -->
-
-<!-- new_pred = predict(bulletxtrctr::rtrees,  -->
-<!--                    bullet_train_filtered %>%  -->
-<!--                      select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2] -->
-
-<!-- new_pred_full = predict(bulletxtrctr::rtrees,  -->
-<!--                         bullet_train_raw %>% -->
-<!--                           select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2] -->
-<!-- ``` -->
-
-<!-- Plot comparing the two predictions (we discovered that the `predict` function from random forest returns different results when applied to only the model (out-of-bag predictions) and the training data (regular predictions), so this is not a good way to test for agreement between training data and models): -->
-
-<!-- ```{r} -->
-<!-- data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred)) %>% -->
-<!--   ggplot(aes(rtrees_pred, new_pred)) +  -->
-<!--   geom_point() -->
-<!-- ``` -->
-
-<!-- Plot showing distributions of predictions from `rtrees` and new predictions made on full training data (same comment here as above about not being able to use this to determine if we have the correct training data for the model): -->
-
-<!-- ```{r} -->
-<!-- data.frame(data = c(rep("rtrees", length(rtrees_pred)),  -->
-<!--                     rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>% -->
-<!--   ggplot(aes(x = pred, fill = data)) +  -->
-<!--   geom_density(alpha = 0.75) -->
-<!-- ``` -->
-
-<!-- Comparison to the data Eric Hare said was used to fit `rtrees` which has half the number of observations as the number of rtrees predictions:  -->
-
-<!-- ```{r} -->
-<!-- eric <- read.csv("https://raw.githubusercontent.com/erichare/imaging-paper/master/data/data-25-25/bullet-stats.csv") -->
-<!-- dim(eric) -->
-<!-- ``` -->
-
-<!-- New data plot: -->
-
-<!-- ```{r} -->
-<!-- preds <- -->
-<!--   data.frame( -->
-<!--     oob = predict(bulletxtrctr::rtrees, type = "prob")[, 2], -->
-<!--     all_data = predict( -->
-<!--       bulletxtrctr::rtrees, -->
-<!--       ccfs_withlands_raw %>% select(all_of(rf_features)), -->
-<!--       type = "prob" -->
-<!--     )[, 2] -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- preds %>%  -->
-<!--   ggplot(aes(x = all_data, y = oob)) +  -->
-<!--   geom_point() -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- preds %>% -->
-<!--   mutate(obs = 1:n()) %>% -->
-<!--   pivot_longer(cols = -obs) %>% -->
-<!--   ggplot(aes(x = value, fill = name)) +  -->
-<!--   geom_density(alpha = 0.5) -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- preds %>%  -->
-<!--   mutate(diff = oob - all_data) %>% -->
-<!--   ggplot(aes(x = diff)) +  -->
-<!--   geom_histogram() -->
-<!-- ``` -->
-<!-- # Data -->
-
-<!-- Load the prepared training data which only has observations with `flag == FALSE` (prepared in the LIME diagnostics paper repository): -->
-
-<!-- ```{r} -->
-<!-- bullet_train <- read.csv("../../../diagnostics-paper/data/bullet-train.csv") -->
-<!-- ``` -->
-
-<!-- Load the random forest `rtrees` from the `bulletxtrctr` package and the random forest model I recently fit using the `bullet_train` data in the paper: -->
 

### 2020-09-28 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
added next section to work on

@@
 
-# Old Code
-
-<!-- ```{r} -->
-<!-- rtrees <- bulletxtrctr::rtrees -->
-<!-- paper_rf <- readRDS("../../../diagnostics-paper/data/bullet-rf.rds") -->
-<!-- ``` -->
-
-<!-- Extract the features used to fit `rtrees`: -->
-
-<!-- ```{r} -->
-<!-- bullet_features <- rownames(bulletxtrctr::rtrees$importance) -->
-<!-- bullet_features -->
-<!-- ``` -->
-
-<!-- # `rtrees` versus paper model -->
-
-<!-- The code below was used to fit the random forest in the paper but is not run here: -->
-
-<!-- ```{r eval = FALSE} -->
-<!-- set.seed(20160104) -->
-<!-- bullet_rf <- -->
-<!--   randomForest( -->
-<!--     y = factor(bullet_train$samesource), -->
-<!--     x = bullet_train %>% select(all_of(bullet_features)), -->
-<!--     ntree = bulletxtrctr::rtrees$ntree, -->
-<!--     mtry = bulletxtrctr::rtrees$mtry -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- Confusion matrices from the two models: -->
-
-<!-- ```{r} -->
-<!-- rtrees$confusion -->
-<!-- paper_rf$confusion -->
-<!-- ``` -->
-
-<!-- Variable importance values: -->
-
-<!-- ```{r} -->
-<!-- vi = data.frame( -->
-<!--   features = rownames(rtrees$importance), -->
-<!--   rtrees = rtrees$importance[, 1], -->
-<!--   paper = paper_rf$importance[, 1] -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- # New Random Forests -->
-
-<!-- Randomly select 100 seeds (using a random seed):  -->
-
-<!-- ```{r} -->
-<!-- set.seed(20200917) -->
-<!-- seeds = sample(x = 10000000:100000000, size = 100, replace = FALSE) -->
-<!-- seeds -->
-<!-- ``` -->
-
-<!-- Function for fitting random forests to mimic rtrees with different seeds: -->
-
-<!-- ```{r} -->
-<!-- fit_rf <- function(seed) { -->
-<!--   set.seed(seed) -->
-<!--   bullet_rf <- -->
-<!--     randomForest( -->
-<!--       y = factor(bullet_train$samesource), -->
-<!--       x = bullet_train %>% select(all_of(bullet_features)), -->
-<!--       ntree = bulletxtrctr::rtrees$ntree, -->
-<!--       mtry = bulletxtrctr::rtrees$mtry -->
-<!--     )   -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Fit 100 new random forests and save or load: -->
-
-<!-- ```{r} -->
-<!-- # Fit (and save) or load random forests -->
-<!-- bullet_rfs_file = "../../../data/bullet_rfs.rds" -->
-<!-- if (!file.exists(bullet_rfs_file)) { -->
-<!--   bullet_rfs = map(.x = seeds, .f = fit_rf) -->
-<!--   saveRDS(object = bullet_rfs, file = bullet_rfs_file) -->
-<!-- } else { -->
-<!--   bullet_rfs = readRDS(bullet_rfs_file) -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Function for extracting the confusion matrices from the model and put in a nice data frame: -->
-
-<!-- ```{r} -->
-<!-- extract_confus <- function(model) { -->
-<!--   data.frame(model$confusion) %>% -->
-<!--   rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>% -->
-<!--   mutate(observed = rownames(model$confusion)) %>% -->
-<!--   pivot_wider(names_from = observed, values_from = everything())   -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:  -->
-
-<!-- ```{r} -->
-<!-- extract_importance <- function(model) { -->
-<!--   data.frame(model$importance) %>% -->
-<!--     mutate(features = rownames(model$importance)) %>% -->
-<!--     arrange(desc(MeanDecreaseGini)) %>% -->
-<!--     mutate(rank = 1:n()) %>% -->
-<!--     rename("importance" = "MeanDecreaseGini") %>% -->
-<!--     select(features, importance, rank) -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- Extract the confusion matrices and importance values from all random forest models: -->
-
-<!-- ```{r} -->
-<!-- res_confus <- map_df(.x = bullet_rfs, .f = extract_confus, .id = "rf_model_id") -->
-<!-- res_importance <- map_df(.x = bullet_rfs, .f = extract_importance, .id = "rf_model_id") -->
-<!-- ``` -->
-
-<!-- # Visualizations of Results -->
-
-<!-- ## Class Errors -->
-
-<!-- Obtain the class errors from `rtrees` and the paper random forest: -->
-
-<!-- ```{r} -->
-<!-- comparison_values <- -->
-<!--   data.frame( -->
-<!--     model = c("paper", "rtrees"), -->
-<!--     class_error_true = c(paper_rf$confusion[2, 3], rtrees$confusion[2, 3]), -->
-<!--     class_error_false = c(paper_rf$confusion[1, 3], rtrees$confusion[1, 3]) -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true): -->
-
-<!-- ```{r fig.width = 10, fig.height = 4.5} -->
-<!-- hist_true <-  -->
-<!--   res_confus %>% -->
-<!--   ggplot(aes(x = class_error_TRUE)) + -->
-<!--   geom_histogram() + -->
-<!--   geom_vline(data = comparison_values, -->
-<!--              mapping = aes(xintercept = class_error_true, color = model)) -->
-
-<!-- hist_false <-  -->
-<!--   res_confus %>% -->
-<!--   ggplot(aes(x = class_error_FALSE)) + -->
-<!--   geom_histogram() + -->
-<!--   geom_vline(data = comparison_values, -->
-<!--              mapping = aes(xintercept = class_error_false, color = model)) -->
-
-<!-- plot_grid(hist_true, hist_false) -->
-<!-- ``` -->
-
-<!-- Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models: -->
-
-<!-- ```{r} -->
-<!-- ggplot() + -->
-<!--   geom_point(data = res_confus, -->
-<!--              mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) + -->
-<!--   geom_point( -->
-<!--     data = comparison_values, -->
-<!--     mapping = aes(x = class_error_false, y = class_error_true, color = model) -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- ## Variable Importance  -->
-
-<!-- Prepare variable importance from `rtrees` and paper models for plotting: -->
-
-<!-- ```{r} -->
-<!-- vi_ranks <-  -->
-<!--   vi %>% -->
-<!--   arrange(desc(rtrees)) %>% -->
-<!--   mutate(rtrees_rank = 1:n()) %>%  -->
-<!--   arrange(desc(paper)) %>% -->
-<!--   mutate(paper_rank = 1:n()) %>% -->
-<!--   select(-rtrees, -paper) %>% -->
-<!--   pivot_longer(names_to = "rf_model_id", values_to = "rank", cols = -features) -->
-<!-- ``` -->
-
-<!-- Tile plot showing the variable importance ranks for each model showing variability across newly trained models and some agreement (ex: rough_cor and ccf) and some disagreement (ex: sum_peaks and non_cms) with `rtrees`: -->
-
-<!-- ```{r fig.width = 10, fig.height = 4.5} -->
-<!-- rtrees_var_order <- -->
-<!--   vi_ranks %>% -->
-<!--   filter(rf_model_id == "rtrees_rank") %>% -->
-<!--   arrange(desc(rank)) %>% -->
-<!--   pull(features) -->
-
-<!-- tile_org <- -->
-<!--   vi_ranks %>% -->
-<!--   mutate( -->
-<!--     rank = factor(rank, levels = 1:9), -->
-<!--     features = factor(features, levels = rtrees_var_order),  -->
-<!--     rf_model_id = factor(rf_model_id, levels = c("rtrees_rank", "paper_rank")) -->
-<!--   ) %>% -->
-<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
-<!--   geom_tile() + -->
-<!--   scale_fill_brewer(palette = "RdYlBu") -->
-
-<!-- tile_new <- -->
-<!--   res_importance %>% -->
-<!--   mutate( -->
-<!--     rank = factor(rank, levels = 1:9), -->
-<!--     features = factor(features, levels = rtrees_var_order) -->
-<!--   ) %>% -->
-<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
-<!--   geom_tile() + -->
-<!--   scale_fill_brewer(palette = "RdYlBu") -->
-
-<!-- plot_grid(tile_org, tile_new) -->
-<!-- ``` -->
-
-<!-- Box plot of ranks across the models with colored points added for the `rtrees` and paper model variable importance ranks (features ordered by `rtrees` variable importance): -->
-
-<!-- ```{r} -->
-<!-- res_importance %>% -->
-<!--   mutate(features = factor(features, levels = rtrees_var_order)) %>% -->
-<!--   ggplot() + -->
-<!--   geom_boxplot(aes(x = rank, y = features)) + -->
-<!--   geom_jitter( -->
-<!--     data = vi_ranks, -->
-<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
-<!--     width = 0, -->
-<!--     height = 0.2 -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- Features versus variable importance ranks for new models (black lines and points) and `rtrees` and paper model (features ordered by `rtrees` variable importance): -->
-
-<!-- ```{r} -->
-<!-- res_importance %>% -->
-<!--   mutate( -->
-<!--     rank = factor(rank, levels = 1:9), -->
-<!--     features = factor(features, levels = rtrees_var_order) -->
-<!--   ) %>% -->
-<!--   ggplot(aes(x = rank, y = features, group = rf_model_id)) + -->
-<!--   geom_line(alpha = 0.2, size = 2) + -->
-<!--   geom_point(alpha = 0.2, size = 3) + -->
-<!--   geom_line( -->
-<!--     data = vi_ranks, -->
-<!--     mapping = aes( -->
-<!--       x = rank, -->
-<!--       y = features, -->
-<!--       group = rf_model_id, -->
-<!--       color = rf_model_id -->
-<!--     ) -->
-<!--   ) + -->
-<!--   geom_jitter( -->
-<!--     data = vi_ranks, -->
-<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
-<!--     width = 0.1, -->
-<!--     height = 0 -->
-<!--   ) + -->
-<!--   labs(title = "new random forest lines and points created with alpha shading") -->
-<!-- ``` -->
+# Training New Random Forests
 

### 2020-09-29 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
working on condensing journals

@@
 
+## Try Old Seeds
+
+The seeds used were selected by Heike based on ones she believes were used at the time of training `rtrees`.
+
+Code for training random forest models based on the random forest fit in Eric's code found [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R), which is believed to be the code used to train the original `rtrees`.
+
+```{r}
+set.seed(20140501)
+rtrees2 <-
+  randomForest(
+    factor(same_source) ~ ., 
+    data = CCFs_withlands %>% select(rtrees_features, same_source), 
+    ntree = 300
+  )
+
+set.seed(20170222)
+rtrees3 <-
+  randomForest(
+    factor(same_source) ~ ., 
+    data = CCFs_withlands %>% select(rtrees_features, same_source), 
+    ntree = 300
+  )
+```
+
+```{r}
+set.seed(20170222)
+rtrees4 <-
+  randomForest(
+    factor(same_source) ~ .,
+    data = hamby_comparisons_filtered %>% select(rtrees_features, same_source),
+    ntree = 300
+  )
+
+set.seed(20140501)
+rtrees5 <-
+  randomForest(
+    factor(same_source) ~ .,
+    data = hamby_comparisons_filtered %>% select(rtrees_features, same_source),
+    ntree = 300
+  )
+```
+
+```{r}
+plot(rtrees2$votes, rtrees3$votes)
+plot(rtrees2$votes, bulletxtrctr::rtrees$votes)
+plot(rtrees3$votes, bulletxtrctr::rtrees$votes)
+```
+
+```{r}
+plot(rtrees4$votes, rtrees5$votes)
+plot(rtrees4$votes, bulletxtrctr::rtrees$votes)
+plot(rtrees5$votes, bulletxtrctr::rtrees$votes)
+```
+
+```{r}
+plot(sort(rtrees2$votes), sort(bulletxtrctr::rtrees$votes))
+plot(sort(rtrees3$votes), sort(bulletxtrctr::rtrees$votes))
+plot(sort(rtrees4$votes), sort(bulletxtrctr::rtrees$votes))
+plot(sort(rtrees5$votes), sort(bulletxtrctr::rtrees$votes))
+```
+
+```{r}
+bulletxtrctr::rtrees$confusion
+rtrees2$confusion
+rtrees3$confusion
+rtrees4$confusion
+rtrees5$confusion
+```
+
+## Distribution Across Seeds
+
+Randomly select 100 seeds (using a random seed):
+
+```{r}
+#set.seed(20200917)
+set.seed(20200925)
+seeds = sample(x = 10000000:100000000, size = 250, replace = FALSE)
+seeds
+```
+
+Function for fitting random forests to mimic rtrees with different seeds:
+
+```{r}
+fit_rf <- function(seed, data) {
+  set.seed(seed)
+  bullet_rf <-
+    randomForest(
+      y = factor(data$same_source),
+      x = data %>% select(all_of(rtrees_features)),
+      ntree = bulletxtrctr::rtrees$ntree,
+      mtry = bulletxtrctr::rtrees$mtry
+    )
+  return(bullet_rf)
+}
+```
+
+Fit 250 new random forests and save or load:
+
+```{r}
+rfs_hamby_comparison_file = "../../../data/rfs_hamby_comparison.rds"
+if (!file.exists(rfs_hamby_comparison_file)) {
+  rfs_hamby_comparison = map(.x = seeds, .f = fit_rf, data = hamby_comparisons_filtered)
+  saveRDS(object = bullet_rfs, file = rfs_hamby_comparison_file)
+} else {
+  rfs_hamby_comparison = readRDS(rfs_hamby_comparison_file)
+}
+
+rfs_CCFs_withlands_file = "../../../data/rfs_CCFs_withlands.rds"
+if (!file.exists(rfs_CCFs_withlands_file)) {
+  rfs_CCFs_withlands = map(.x = seeds, .f = fit_rf, data = CCFs_withlands)
+  saveRDS(object = rfs_CCFs_withlands, file = rfs_CCFs_withlands_file)
+} else {
+  rfs_CCFs_withlands = readRDS(rfs_CCFs_withlands_file)
+}
+```
+
+Function for extracting the confusion matrices from the model and put in a nice data frame:
+
+```{r}
+extract_confus <- function(model) {
+  data.frame(model$confusion) %>%
+    rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>%
+    mutate(observed = rownames(model$confusion)) %>%
+    pivot_wider(names_from = observed, values_from = everything())  
+}
+```
+
+Extract the confusion matrices and importance values from all random forest models:
+
+```{r}
+hamby_comparison_confus <-
+  map_df(.x = hamby_comparison_rfs, .f = extract_confus, .id = "rf_model_id")
+CCFs_withlands_confus <-
+  map_df(.x = CCFs_withlands_rfs, .f = extract_confus, .id = "rf_model_id")
+```
+
+Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:
+
+```{r}
+extract_importance <- function(model) {
+  data.frame(model$importance) %>%
+    mutate(features = rownames(model$importance)) %>%
+    arrange(desc(MeanDecreaseGini)) %>%
+    mutate(rank = 1:n()) %>%
+    rename("importance" = "MeanDecreaseGini") %>%
+    select(features, importance, rank)
+}
+```
+
+```{r}
+hamby_comparison_importance <-
+  map_df(.x = hamby_comparison_rfs, .f = extract_importance, .id = "rf_model_id")
+CCFs_withlands_importance <-
+  map_df(.x = CCFs_withlands_rfs, .f = extract_importance, .id = "rf_model_id")
+```
+
+### Visualizations of Class Errors
+
+Obtain the class errors from `rtrees` and the paper random forest:
+
+```{r}
+rtrees_values <-
+  data.frame(
+    model = "rtrees",
+    class_error_true = rtrees$confusion[2, 3],
+    class_error_false = rtrees$confusion[1, 3]
+  )
+```
+
+Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true):
+
+```{r fig.width = 10, fig.height = 4.5}
+hist_true_hc <-
+  hamby_comparison_confus %>%
+  ggplot(aes(x = class_error_TRUE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_true, color = model))
+
+hist_false_hc <- 
+  CCFs_withlands_confus %>%
+  ggplot(aes(x = class_error_FALSE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_false, color = model))
+
+hist_true_ccfwl <-
+  CCFs_withlands_confus %>%
+  ggplot(aes(x = class_error_TRUE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_true, color = model))
+
+hist_false_ccfwl <- 
+  CCFs_withlands_confus %>%
+  ggplot(aes(x = class_error_FALSE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_false, color = model))
+
+plot_grid(hist_true_hc, hist_false_hc, hist_true_ccfwl, hist_false_ccfwl)
+```
+
+# LIME Explanation Comparison
+
 # Session Info

### 2020-09-29 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
added text descriptions and code for visualizations (currently waiting for all 500 new random forests to train)

--- 2020-09-28 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
@@
 The new data (`CCFs_withlands.csv`) contains the same number of rows the number of predictions associated with `rtrees`.
-I have gathered all of our work trying to determine that `CCFs_withlands` is the data used to train `rtrees` in this journal.
+I have gathered all of our work trying to determine that `CCFs_withlands` is the data (or very similar to the data) used to train `rtrees` in this journal.
 
@@
   filter(study1 != "Hamby173" | bullet1 != "BE") %>%
-  filter(study2 != "Hamby173" | bullet2 != "BE") %>% dim()
+  filter(study2 != "Hamby173" | bullet2 != "BE") %>% 
+  dim()
 ```
@@
 
+In this section, we retrain various random forest models using both the Hamby comparison and CCFs with lands data.
+Then we compare the results from the retrained models to `rtrees` to check for similarity.
+The results show that the retrained models on the CCFs with lands data are very similar to `rtrees` while the model trained on the Hamby comparison data are very different.
+It should be noted that all models trained in this section on the Hamby comparison data used the observations in the filtered version of the dataset (`hamby_comparisons_filtered`) so that the number of observations match `rtrees` and since this was the data we were previously using in the LIME diagnostics paper.
+
+## Old Seeds
+
+Unfortunately, the seed that was used to train `rtrees` was lost or the changes in the way the random number generation is done in R has changed has made it not possible to reproduce `rtrees`.
+However, Heike has two seeds that were used around the time of training `rtrees`
+The seeds used were selected by Heike based on ones she believes were used at the time of training `rtrees`: 20140501 and 20170222.
+Note that 20170222 is also the seed used in Eric's [code](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R).
+
+Below, four random forest models are trained using the seeds suggested by Heike.
+The code used to fit the models is based on Eric's [code](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R), which is believed to be the code used to train the original `rtrees`.
+The first two random forest are fit using `CCFs_withlands`, and the third and fourth models are fit using `hamby_comparisons_filtered`:
+
+```{r}
+rtrees2_file = "../../../data/rfs_rtrees2.rds"
+if (!file.exists(rtrees2_file)) {
+  set.seed(20140501)
+  rtrees2 <-
+    randomForest(
+      factor(same_source) ~ ., 
+      data = CCFs_withlands %>% select(rtrees_features, same_source), 
+      ntree = 300
+    )
+  saveRDS(object = rtrees2, file = rtrees2_file)
+}
+
+rtrees3_file = "../../../data/rfs_rtrees3.rds"
+if (!file.exists(rtrees3_file)) {
+  set.seed(20170222)
+  rtrees3 <-
+    randomForest(
+      factor(same_source) ~ ., 
+      data = CCFs_withlands %>% select(rtrees_features, same_source), 
+      ntree = 300
+    )
+  saveRDS(object = rtrees3, file = rtrees3_file)
+}
+
+rtrees4_file = "../../../data/rfs_rtrees4.rds"
+if (!file.exists(rtrees4_file)) {
+  set.seed(20140501)
+  rtrees4 <-
+    randomForest(
+      factor(same_source) ~ .,
+      data = hamby_comparisons_filtered %>% select(rtrees_features, same_source),
+      ntree = 300
+    )
+  saveRDS(object = rtrees4, file = rtrees4_file)
+}
+
+rtrees5_file = "../../../data/rfs_rtrees5.rds"
+if (!file.exists(rtrees5_file)) {
+  set.seed(20170222)
+  rtrees5 <-
+    randomForest(
+      factor(same_source) ~ .,
+      data = hamby_comparisons_filtered %>% select(rtrees_features, same_source),
+      ntree = 300
+    )
+  saveRDS(object = rtrees5, file = rtrees5_file)
+} 
+```
+
+Load the saved versions of the models:
+
+```{r}
+rtrees2 <- readRDS(rtrees2_file)
+rtrees3 <- readRDS(rtrees3_file)
+rtrees4 <- readRDS(rtrees4_file)
+rtrees5 <- readRDS(rtrees5_file)
+```
+
+Extract the votes from each of the newly trained random forest models and `rtrees` and prepare the dataframe for plotting:
+
+```{r}
+rtrees_votes <-
+  data.frame(
+    rtrees = bulletxtrctr::rtrees$votes,
+    rtrees2 = rtrees2$votes,
+    rtrees3 = rtrees3$votes,
+    rtrees4 = rtrees4$votes,
+    rtrees5 = rtrees5$votes
+  ) %>%
+  mutate(obs = 1:n()) %>%
+  pivot_longer(cols = -obs) %>%
+  separate(name, c("model", "label")) %>%
+  pivot_wider(names_from = model, values_from = value)
+```
+
+Plots comparing the votes from `rtrees` to those from the newly trained models.
+The top row contains the comparisons with the random forests trained on `CCFs_withlands`.
+Note that the first two plots comparing the `CCFs_withlands` newly trained random forest vote to `rtrees` looks very similar to the third plots which compares the votes from the two newly trained random forests on `CCFs_withlands`.
+This suggests that even though all three models are trained using different seeds, the training data is the same.
+On the other hand, the bottom row of plots are created using the votes from the random forests trained on `hamby_comparisons_filtered`, and the two plots comparing the votes to `rtrees` look very different from the third plot comparing the votes from the two newly trained models.
+This suggests that the `hamby_comparisons_filtered` was not the training data for `rtrees`, or at least, the observations are not ordered the same in the dataset.
+
+```{r fig.width = 12, fig.height = 5}
+plot_grid(
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees, y = rtrees2, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees2 votes",
+         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20140501"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees, y = rtrees3, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees3 votes",
+         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20170222"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees2, y = rtrees3, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees2 votes",
+         title = "Both retrained RFs on Hamby comparison data"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees, y = rtrees4, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees4 votes",
+         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20140501"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees, y = rtrees5, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees5 votes",
+         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20170222"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = rtrees4, y = rtrees5, color = label
+    )) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees5 votes",
+         title = "Both retrained RFs on CCFs with lands data"),
+  nrow = 2
+)
+```
+
+To address the issue that the observations in `CCFs_withlands` and `hamby_comparisons` may not be ordered the same way as the training data for `rtrees`, the set of plots are recreated by first ordering all votes.
+If the training data and seed are the same as those used to train `rtrees`, we would expect a 1-to-1 relationship.
+1-to-1 lines are included in the plots, and none of the votes result in an exact 1-to-1 relationship.
+
+```{r fig.width = 12, fig.height = 5}
+plot_grid(
+  rtrees_votes %>%
+    ggplot(aes(
+      x = sort(rtrees), y = sort(rtrees2), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees2 votes",
+         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20140501"),
+
+  rtrees_votes%>%
+    ggplot(aes(
+      x = sort(rtrees), y = sort(rtrees3), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees3 votes",
+         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20170222"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = sort(rtrees2), y = sort(rtrees3), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees2 votes",
+         title = "Both retrained RFs on Hamby comparison data"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = sort(rtrees), y = sort(rtrees4), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees4 votes",
+         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20140501"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = sort(rtrees), y = sort(rtrees5), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees5 votes",
+         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20170222"),
+
+  rtrees_votes %>%
+    ggplot(aes(
+      x = sort(rtrees4), y = sort(rtrees5), color = label
+    )) +
+    geom_abline(slope = 1, intercept = 0) +
+    geom_point(shape = 1) +
+    labs(x = "rtrees votes",
+         y = "rtrees5 votes",
+         title = "Both retrained RFs on CCFs with lands data"),
+  nrow = 2
+)
+```
+
+The confusion matrices from `rtrees` and the four newly trained random forests (note that the models trained using `CCFs_withlands` result in much more similar confusion matrices to `rtrees` than the models trained using `hamby_comparisons_filtered`):
+
+```{r}
+bulletxtrctr::rtrees$confusion
+rtrees2$confusion
+rtrees3$confusion
+rtrees4$confusion
+rtrees5$confusion
+```
+
+## Distribution Across Seeds
+
+To better understand how the random forests trained on `CCFs_withlands` and `hamby_comparisons` compare to `rtrees`, we compare the true and false class errors from `rtrees` to the distributions of the class errors by train 250 new random forests using different seeds.
+
+### Training the Random Forests
+
+Randomly select 100 seeds (using a random seed):
+
+```{r}
+set.seed(20200925)
+seeds = sample(x = 10000000:100000000, size = 250, replace = FALSE)
+seeds
+```
+
+Function for fitting random forests to mimic rtrees with different seeds:
+
+```{r}
+fit_rf <- function(seed, dataset) {
+  set.seed(seed)
+  randomForest(
+    y = factor(dataset$same_source),
+    x = dataset %>% select(all_of(rtrees_features)),
+    ntree = bulletxtrctr::rtrees$ntree,
+    mtry = bulletxtrctr::rtrees$mtry
+  )
+}
+```
+
+Fit 250 new random forests on `hamby_comparisons_filtered` and `CCFs_withlands` using the seeds generated above:
+
+```{r}
+rfs_hc_file = "../../../data/rfs_hamby_comparison.rds"
+if (!file.exists(rfs_hc_file)) {
+  saveRDS(
+    object = map(.x = seeds, .f = fit_rf, dataset = hamby_comparisons_filtered),
+    file = rfs_hc_file
+  )
+} 
+rfs_ccfwl_file = "../../../data/rfs_CCFs_withlands.rds"
+if (!file.exists(rfs_ccfwl_file)) {
+  saveRDS(
+    object = map(.x = seeds, .f = fit_rf, dataset = CCFs_withlands),
+    file = rfs_ccfwl_file
+  )
+}
+```
+
+Load the saved versions of the random forest models:
+
+```{r}
+rfs_hamby_comparison = readRDS(rfs_hc_file)
+rfs_CCFs_withlands = readRDS(rfs_ccfwl_file)
+```
+
+### Extracting Model Results
+
+Function for extracting the confusion matrices from the model and put in a nice data frame:
+
+```{r}
+extract_confus <- function(model) {
+  data.frame(model$confusion) %>%
+    rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>%
+    mutate(observed = rownames(model$confusion)) %>%
+    pivot_wider(names_from = observed, values_from = everything())  
+}
+```
+
+Extract the confusion matrices and importance values from all random forest models:
+
+```{r}
+hamby_comparison_confus <-
+  map_df(.x = rfs_hamby_comparison, .f = extract_confus, .id = "rf_model_id")
+CCFs_withlands_confus <-
+  map_df(.x = rfs_CCFs_withlands, .f = extract_confus, .id = "rf_model_id")
+```
+
+Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:
+
+```{r}
+extract_importance <- function(model) {
+  data.frame(model$importance) %>%
+    mutate(features = rownames(model$importance)) %>%
+    arrange(desc(MeanDecreaseGini)) %>%
+    mutate(rank = 1:n()) %>%
+    rename("importance" = "MeanDecreaseGini") %>%
+    select(features, importance, rank)
+}
+```
+
+Extract the feature importance from the new models:
+
+```{r}
+hamby_comparison_importance <-
+  map_df(.x = rfs_hamby_comparison, .f = extract_importance, .id = "rf_model_id")
+CCFs_withlands_importance <-
+  map_df(.x = rfs_CCFs_withlands, .f = extract_importance, .id = "rf_model_id")
+```
+
+Extract the feature importance from `rtrees`:
+
+```{r}
+rtrees_importance <- 
+  data.frame(features = rownames(bulletxtrctr::rtrees$importance),
+             bulletxtrctr::rtrees$importance) %>%
+  arrange(desc(MeanDecreaseGini)) %>%
+  mutate(rank = 1:n(),
+         rf_model_id = "rtrees") %>%
+  rename("importance" = "MeanDecreaseGini") %>%
+  select(rf_model_id, features, importance, rank)
+```
+
+### Class Error Distributions
+
+Obtain the class errors from `rtrees` and the paper random forest:
+
+```{r}
+rtrees_values <-
+  data.frame(
+    model = "rtrees",
+    class_error_true = bulletxtrctr::rtrees$confusion[2, 3],
+    class_error_false = bulletxtrctr::rtrees$confusion[1, 3]
+  )
+```
+
+Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true):
+
+```{r fig.width = 10, fig.height = 4.5}
+hist_true_hc <-
+  hamby_comparison_confus %>%
+  ggplot(aes(x = class_error_TRUE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_true, color = model))
+
+hist_false_hc <- 
+  hamby_comparison_confus %>%
+  ggplot(aes(x = class_error_FALSE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_false, color = model))
+
+hist_true_ccfwl <-
+  CCFs_withlands_confus %>%
+  ggplot(aes(x = class_error_TRUE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_true, color = model))
+
+hist_false_ccfwl <- 
+  CCFs_withlands_confus %>%
+  ggplot(aes(x = class_error_FALSE)) +
+  geom_histogram() +
+  geom_vline(data = rtrees_values,
+             mapping = aes(xintercept = class_error_false, color = model))
+
+plot_grid(hist_true_hc, hist_false_hc, hist_true_ccfwl, hist_false_ccfwl)
+```
+
+### Comparing Feature Importance
+
+Heatmap depicting feature importance across models:
+
+```{r fig.width = 12, fig.height = 5}
+plot_grid(
+  bind_rows(rtrees_importance, hamby_comparison_importance) %>%
+    mutate(
+      rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
+      rank = factor(rank, levels = 1:9),
+      features = factor(features, levels = rev(rtrees_importance$features))
+    ) %>%
+    ggplot(aes(x = rf_model_id, y = features, fill = rank)) +
+    geom_tile() +
+    scale_fill_brewer(palette = "RdYlBu") + 
+    theme_bw() +
+    labs(
+      x = "Random Forest Model", 
+      y = "Feature", 
+      title = "Comparing rtrees importance to random forests fit using Hamby comparisons data"
+    ),
+
+  bind_rows(rtrees_importance, CCFs_withlands_importance) %>%
+    mutate(
+      rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
+      rank = factor(rank, levels = 1:9),
+      features = factor(features, levels = rev(rtrees_importance$features))
+    ) %>%
+    ggplot(aes(x = rf_model_id, y = features, fill = rank)) +
+    geom_tile() +
+    scale_fill_brewer(palette = "RdYlBu") + 
+    theme_bw() +
+    labs(
+      x = "Random Forest Model", 
+      y = "Feature", 
+      title = "Comparing rtrees importance to random forests fit using CCFs with lands data"
+    )
+)
+```
+
+```{r fig.width = 12, fig.height = 5}
+plot_grid(
+  bind_rows(rtrees_importance, hamby_comparison_importance) %>%
+    mutate(
+      rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
+      rank = factor(rank, levels = 1:9),
+      features = factor(features, levels = rev(rtrees_importance$features)),
+      rtrees_ind = ifelse(rf_model_id == "rtrees", "rtrees", "Hamby Comparison")
+    ) %>%
+    ggplot(aes(x = rank, y = features, group = rf_model_id, color = rtrees_ind)) +
+    geom_point(alpha = 0.5, shape = 1) + 
+    geom_line(alpha = 0.5) +
+    scale_color_manual(values = c("grey50", "blue")) +
+    theme_bw() +
+    labs(
+      x = "Random Forest Model", 
+      y = "Feature", 
+      title = "Comparing rtrees importance to random forests fit using Hamby comparisons data"
+    ), 
+    bind_rows(rtrees_importance, CCFs_withlands_importance) %>%
+    mutate(
+      rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
+      rank = factor(rank, levels = 1:9),
+      features = factor(features, levels = rev(rtrees_importance$features)),
+      rtrees_ind = ifelse(rf_model_id == "rtrees", "rtrees", "CCFs with lands")
+    ) %>%
+    ggplot(aes(x = rank, y = features, group = rf_model_id, color = rtrees_ind)) +
+    geom_point(alpha = 0.5, shape = 1) + 
+    geom_line(alpha = 0.5) +
+    scale_color_manual(values = c("grey50", "blue")) +
+    theme_bw() +
+    labs(
+      x = "Random Forest Model", 
+      y = "Feature", 
+      title = "Comparing rtrees importance to random forests fit using CCFs with lands data"
+    )
+)
+```
+
+# LIME Explanation Comparison
+
 # Session Info

### 2020-09-29 README.Rmd
updating readme

@@
 
-Repository for research projects on LIME
+Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository. For easy viewing of the journals, use these links:
 
-Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/
-
-## Ideas
-
-**LIME diagnostics**
-
-- turn repetitive code into functions
-- try out different weights
-- change distance matrix in seriation to be 5-# of variables shared between two rows
-- try using distance matrix computed on the feature value with seriation
-- add in feature selection methods to LIME input options
-- think of a way to compute consistency across top two features
-- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
-- he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
-- compare the simple models based on different number of bins using an F-test
-- look into computing a diversity or consistency measure for the sensitivity analysis
-- include a penalty for the number of parameters when choosing bins
-- look at the AUC after binning
-- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
-- try visualizing the features from the test data using dimension reduction and
-coloring them by variables suggested to be important by lime
-
-**Explainer Models**
-
-- read through papers giving an overview of the current explanation methods
-- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
-- look more into Molnar and his adviser Bernd
-- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
-
-**Understanding LIME**
-
-- edit details in understanding LIME journal
-- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
-- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
-- assess lime results on logistic regression models
-- try retriculate to apply python version of lime
-- look into literature on binning methods
-- think about why R^2 would be better for some binning methods
-- read new paper on Anchor
-
-**Possible Improvements to LIME**
-
-- determine the best number of bins to use for each variable
-- try out subsampling idea
-
-**Simulation with RF**
-
-- think about how to implement a simulation with a random forest
-- look back at 601 notes from Kaiser for model assessment
-- look at Hadley's 'removing the blindfold' for ideas
-- read book Dr. Dixon lent me on sensitivity analyses
-
-**Random Forests Confidence Intervals**
-
-- look into papers by Giles Hooker and Lucas Mentch
-- Dr. Nettleton paper
-
-**Random Forest Interpretations**
-
-- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/
+0. [Objectives and Ideas]()
+1. [Information on Hamby Data and Models]()
+2. [Understanding LIME]()
+3. [Applying LIME to Hamby Data]()
+4. [Assessing LIME on Hamby Data]()
+5. [Applying and Assessing LIME on Iris Data]()
+6. [Notes on Readings]()
+7. [Computational Issues]()
+8. [LIME Applied to Logistic Regression]()
+9. [Identifying `rtrees` Training Data]()
+10. [LIME Variability Across Hamby Data and Models]()
 

### 2020-09-29 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
updating readme

@@
 - Apply LIME (or some improved version of LIME) to interpret the random forest model fit to the Hamby bullet data
+
+### Ideas
+
+**LIME diagnostics**
+
+- turn repetitive code into functions
+- try out different weights
+- change distance matrix in seriation to be 5-# of variables shared between two rows
+- try using distance matrix computed on the feature value with seriation
+- add in feature selection methods to LIME input options
+- think of a way to compute consistency across top two features
+- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
+- he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
+- compare the simple models based on different number of bins using an F-test
+- look into computing a diversity or consistency measure for the sensitivity analysis
+- include a penalty for the number of parameters when choosing bins
+- look at the AUC after binning
+- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
+- try visualizing the features from the test data using dimension reduction and
+coloring them by variables suggested to be important by lime
+- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
+- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)
+
+**Explainer Models**
+
+- read through papers giving an overview of the current explanation methods
+- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
+- look more into Molnar and his adviser Bernd
+- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
+
+**Understanding LIME**
+
+- Run a simulation to understand if LIME is working
+    - could implement a couple of local linear dependencies
+    - piece this together
+    - could include interactions in the model
+    - does lime find the local models?
+- edit details in understanding LIME journal
+- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
+- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
+- assess lime results on logistic regression models
+- try reticulate R package to apply python version of lime
+- look into literature on binning methods
+- think about why R^2 would be better for some binning methods
+- read new paper on Anchor
+
+**Possible Improvements to LIME**
+
+- determine the best number of bins to use for each variable
+- try out subsampling idea
+
+**Simulation with RF**
+
+- think about how to implement a simulation with a random forest
+- look back at 601 notes from Kaiser for model assessment
+- look at Hadley's 'removing the blindfold' for ideas
+- read book Dr. Dixon lent me on sensitivity analyses
+
+**Random Forests Confidence Intervals**
+
+- look into papers by Giles Hooker and Lucas Mentch
+- Dr. Nettleton paper
+
+**Random Forest Interpretations**
+
+- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/
 
@@
 
-# Ideas to Try
-
-- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
-- Run a simulation to understand if LIME is working
-    - could implement a couple of local linear dependencies
-    - piece this together
-    - could include interactions in the model
-    - does lime find the local models?
-- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)
-
 # General Thoughts

### 2020-09-29 README.Rmd
working on updating repo

@@
 
-0. [Objectives and Ideas]()
-1. [Information on Hamby Data and Models]()
-2. [Understanding LIME]()
-3. [Applying LIME to Hamby Data]()
-4. [Assessing LIME on Hamby Data]()
-5. [Applying and Assessing LIME on Iris Data]()
-6. [Notes on Readings]()
-7. [Computational Issues]()
-8. [LIME Applied to Logistic Regression]()
-9. [Identifying `rtrees` Training Data]()
-10. [LIME Variability Across Hamby Data and Models]()
+0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
+1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
+2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
+3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
+4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
+5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
+6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
+7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
+8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
+9. [Identifying `rtrees` Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
+10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-LIME-hamby-variability/10-LIME-hamby-variability.html)
 

### 2020-09-29 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
working on updating repo

@@
     toc: true
-    toc_depth: 3
+    toc_depth: 5
     toc_float: true
+    theme: cerulean
+    highlight: textmate
 ---

### 2020-09-29 journals/06-literature_review/06-literature_review.Rmd
updates after meeting
working on updating repo

@@
 
+*Heike metioned that the sampling method they are doing is similar to what an SVM is doing.*
+
 **References to Look Into**

### 2020-09-29 README.Rmd
update name

@@
 9. [Identifying `rtrees` Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
-10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-LIME-hamby-variability/10-LIME-hamby-variability.html)
+10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-LIME_hamby_variability.html)
 

### 2020-09-29 old-journals/bullet data/journals/02-cleaning and exploratory analyses.Rmd
added old journals

---
title: "Cleaning and Exploring the Hamby Data"
author: "Katherine Goode"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
                      fig.align = "center")
```

# Overview

In this journal, I explore the two Hamby datasets, clean and combine them into one data frame, and create the training and testing datasets that will be used when LIME is applied. I start by familiarizing myself with what variables are in the datasets and attempt to understand some of the inconsistencies in the data that I have come across. Then I clean the datasets and combine them into one data frame. Finally, I create the forms of the training and testing datasets that are required by the `lime` R package that include the numeric features that were used to fit the random forest. I also create some plots to explore the features in the training and testing datasets.

The following R libraries will be used in this journal

\vspace{0.25cm}

```{r}
# Load libraries
library(tidyverse)
library(plotly)
```

# Familiarizing Myself with the Datasets

The Hamby datasets are loaded in below. Note that when the `hamby173and252` dataset is read in, the studies called "Cary" are excluded. The data file contains rows based on bullet scans from a different study. These rows are no longer being included since Heike has found the study they came from to be poorly executed.

\vspace{0.25cm}

```{r}
# Load in the Hamby 173 and 252 dataset
hamby173and252 <- read.csv("../data/features-hamby173and252.csv") %>%
  filter(study1 != "Cary", study2 != "Cary")

# Load in the Hamby 44 dataset
hamby44 <- read.csv("../data/features-hamby44.csv")
```

## Comparing Variables in the Two Datasets

The datasets `hamby173and252` and `hamby44` contain variables that identify which bullet and barrel each land is associated with and variables that compare the similarity of the two signatures. However, the versions of these datasets that I have now do not match in terms of variables. Some variables are in both datasets, and some variables are only in one of the datasets. The following code creates the figure shown below that contains all of the variable names and indicates if the variable is in a dataset by a turquoise square.

\vspace{0.25cm}

```{r}
# Create a dataframe with the names of the variables from both datasets
hamby_vars <- data.frame(vars = factor(c(names(hamby173and252), names(hamby44)))) %>%
  distinct() %>%
  arrange(vars)

# Create variables that indicate whether a variable is in a dataset
hamby_vars$hamby173and252 <- hamby_vars$vars %in% names(hamby173and252)
hamby_vars$hamby44 <- hamby_vars$vars %in% names(hamby44)

# Reformat the data to be plotted
hamby_vars_gathered <- hamby_vars %>% 
  gather(key = dataset, value = contained, 2:3) %>%
  filter(contained == TRUE)
```

```{r fig.height = 2.5, fig.width = 10}
# Plot the variables in the datasets
ggplot(hamby_vars_gathered, aes(x = vars, y = dataset)) +
  geom_tile(aes(fill = contained), fill = "mediumturquoise") + 
  labs(x = "Variable", y = "Dataset", fill = "Contained in Dataset?") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

\vspace{0.25cm}

Note that both datasets contain a variable that indicates whether the two lands are a match or not based on the random forest score, but the variables have different names in the two datasets. In `hamby173and252` this variables is called `match`, and in `hamby44`, this variable is called `samesource`.

## Considering the Number of Rows in Each Dataset

If we include symmetric comparisons, each set of test bullets should result in a dataset with
  $$(35 \mbox{ bullets} \times 6 \mbox{ lands})^2=44100 \mbox{ rows},$$
where a row would contain information on a pair of lands. If we do not include the symmetric comparisons, then the dataset should have
  $$\frac{(44100 \mbox{ rows} - (35 \mbox{ bullets} \times 6))}{2} + (35 \mbox{ bullets} \times 6) = 22155 \mbox{ rows}.$$
However, when I looked at the dimension of the datasets, neither of these seem to be the case. See the R code and output below. Note that `hamby173` is currently incorrectly labelled as `hamby44`. All three test sets have less than 44,100 rows. `hamby44` is close, and when I checked with Heike, she said that when we created the dataset, she chose to include the symmetric comparisons. `hamby173` and `hamby252` are much are closer to 22,155 rows, which suggests that these do no include symmetric comparisons. When I checked with Heike, she confirmed that this is the case. This table also shows that there are comparisons across `hamby173` and `hamby252`. These missing observations will be explored more in the section.

\vspace{0.25cm}

```{r}
# Summary of the number of observations in the Hamby173and252 datase
table(hamby173and252$study1, hamby173and252$study2)

# Determine the dimensions of hamby44
dim(hamby44)
```

## Understanding the Missing Observations

I wanted to better understand why the number of rows in the datasets were less than what I expected. The plots below attempt to figure this out.

The plot below considers the number of observations within a barrel and bullet comparison for the known bullets in the `hamby44` dataset. I would expect there to be (6 lands) x (6 lands) = 36 observations within a cell. Most of the cells have 36 observations, but the diagonal for the cases that compare the lands from the same barrel and bullet are missing 6 observations. The next plot gets at this issue. We also can see that there is something wrong with barrel 9. Heike said that the bullets from barrel 9 had tank rash, which caused some of the lands to be excluded.

\vspace{0.25cm}

```{r}
countplot44 <- hamby44 %>%
  filter(barrel1 != "Unk", barrel2 != "Unk") %>%
  group_by(barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  labs(title = "Number of Observations per Barrel-Bullet Pair in Hamby 44")

ggplotly(countplot44, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

\vspace{0.25cm}

The plot below considers the match responses for the land comparisons with barrel 1 and bullet 1 from `hamby44`. I was expecting the 6 missing observations to be the matches, but that does not seem to be the case based on this plot. I found this to be the same for other bullets that I considered. Heike said that the six missing observations should be the matches, which means that something is wrong with the `samesource` variable.

\vspace{0.25cm}

```{r}
hamby44 %>%
  filter(barrel1 == 1, bullet1 == 1, barrel2 == 1, bullet2 == 1) %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = samesource)) +
  theme_bw() +
  labs(title = "Matches for Each Pair of Lands for Barrel 1 and Bullet 1 in Hamby 44")
```

\vspace{0.25cm}

This is the same plot as the previous one, but the colors represent the random forest score. The scores do not seem to match up with the previous plot.

\vspace{0.25cm}

```{r}
hamby44 %>%
  filter(barrel1 == 1, bullet1 == 1, barrel2 == 1, bullet2 == 1) %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = rfscore)) +
  theme_bw() +
  labs(title = "RF Score for Each Pair of Lands for Barrel 1 and Bullet 1 in Hamby 44")
```

\vspace{0.25cm}

The plot below considers the match responses for the land comparisons with barrel 9 and bullet 2 from `hamby44`. There are additional missing observations here due to the tank rash, which appears to be on land 3.

\vspace{0.25cm}

```{r}
hamby44 %>%
  filter(barrel1 == 9, bullet1 == 2, barrel2 == 9, bullet2 == 2) %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = samesource)) +
  theme_bw() +
  labs(title = "Matches for Each Pair of Lands for Barrel 9 and Bullet 2 in Hamby 44")
```

\vspace{0.25cm}

I started to create the same plots for the `hamby173and252` data. When I did this, I discovered that the barrels are not labelled the same between the two datasets. Heike said that the unknown bullets in the `hamby44` dataset are given letters in the bullet column. See the additional code below.

\vspace{0.25cm}

```{r}
# The levels of these do not agree...
summary(hamby173and252$barrel1)
summary(hamby44$barrel1)
```

```{r}
# The bullet levels
levels(factor(hamby173and252$bullet1))
levels(factor(hamby44$bullet1))
```

\vspace{0.25cm}

The plot below considers the number of observations within a barrel and bullet comparison from the Hamby 173 test set data. We can see that the observations on the lower diagonals are missing, and a handful of cases have less than 36 observations. This is due to observations in the upper diagonal corresponding exactly to the ones below the diagonal, so the repeats are excluded from the data. The diagonal also is lower, because none of the repeats from the symmetric comparisons of lands are included. The rows or columns with less than 36 observations are missing values due to tank rash.

\vspace{0.25cm}

```{r}
countplot173 <- hamby173and252 %>%
  filter(study1 == "Hamby44", study2 == "Hamby44") %>%
  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
  group_by(barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  labs(title = "Number of Observations per Barrel-Bullet Pair in Hamby 173")

ggplotly(countplot173, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

\vspace{0.25cm}

This plot considers the number of observations within a barrel and bullet comparison from the Hamby 252 test set data. Again, the observations on the lower diagonals are missing, and a handful of cases have less than 36 observations. This is due to the same reason as with Hamby 173.

\vspace{0.25cm}

```{r}
countplot252 <- hamby173and252 %>%
  filter(study1 == "Hamby252", study2 == "Hamby252") %>%
  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
  group_by(barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  labs(title = "Number of Observations per Barrel-Bullet Pair in Hamby 252")

ggplotly(countplot252, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

\vspace{0.25cm}

Finally, this plot considers the number of observations within a barrel and bullet comparison from the cases where `study1` and `study2` are not equal. That is, these are the cases that compare across `hamby173` and `hamby252`. Again, the observations on the lower diagonals are missing. Here, some cases have less than 36 observations and other have more than 36 observations. The cases with more than 36 observations are due to both test sets having the same numbered barrels but different bullets, and the cases with less than expected are due to tank rash.

\vspace{0.25cm}

```{r}
countplot173and252 <- hamby173and252 %>%
  filter(study1 != study2) %>%
  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
  group_by(barrel1, barrel2, bullet1, bullet2) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = barrel1, y = barrel2)) +
  geom_tile(aes(fill = count)) + 
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  labs(title = "Number of Observations per Barrel-Bullet Pair in Comparisons of 
       Hamby 173 and 252")

ggplotly(countplot173and252, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

\vspace{0.25cm}

Below are plots of the match values associated with the land comparisons within barrel 1 and bullet 1 from `hamby173and252`. Both of these plots only have observations on the upper diagonal since the symmetric cases are not included.

\vspace{0.25cm}

```{r}
hamby173and252 %>%
  filter(study1 == "Hamby44", study2 == "Hamby44") %>%
  filter(barrel1 == 1, bullet1 == 1, barrel2 == 1, bullet2 == 1) %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = match)) +
  theme_bw() +
  labs(title = "Matches for Each Pair of Lands for Barrel 1 and Bullet 1 in Hamby 173")
```

```{r}
hamby173and252 %>%
  filter(study1 == "Hamby252", study2 == "Hamby252") %>%
  filter(barrel1 == 1, bullet1 == 1, barrel2 == 1, bullet2 == 1) %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = match)) +
  theme_bw() +
  labs(title = "Matches for Each Pair of Lands for Barrel 1 and Bullet 1 in Hamby 252")
```

# Cleaning the Data

After working with the data, I have found some issues that I have mentioned in the journals. The code below cleans the `hamby173and252` and `hamby44` data files and joins them based on the variables that both datasets share. However, I did include the random forest prediction probability variable from `hamby44` that was not in `hamby173and252`. The cleaned data is exported as a .csv file.

\vspace{0.25cm}

```{r}
# Create a vector of the features in both datasets
features <- hamby_vars %>% 
  filter(hamby173and252 == TRUE, hamby44 == TRUE) %>%
  pull(vars) %>%
  as.character()

# Clean the data from test sets 173 and 252
hamby173and252_cleaning <- hamby173and252 %>%
  mutate(study1 = factor(study1),
         study2 = factor(study2)) %>%
  mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
         study2 = fct_recode(study2, "Hamby173" = "Hamby44")) %>%
  rename(samesource = match) %>%
  select(features, samesource, study1, study2)

# Determine the unknown bullet letters in the hamby173and252 data
letters <- levels(hamby173and252_cleaning$barrel1)[11:length(
  levels(hamby173and252_cleaning$barrel1))]

# Adjust the barrel1 and bullet1 names for the known case
hamby173and252_cleaning_known1 <- hamby173and252_cleaning %>%
  filter(!barrel1 %in% letters) %>%
  mutate(bullet1 = factor(bullet1)) %>%
  select(barrel1, barrel2, bullet1, bullet2, 5:21)

# Adjust the barrel1 and bullet1 names for the unknown case
hamby173and252_cleaning_unknown1 <- hamby173and252_cleaning %>%
  filter(barrel1 %in% letters) %>%
  mutate(bullet1 = barrel1) %>%
  select(barrel1, barrel2, bullet1, bullet2, 5:21) %>%
  mutate(barrel1 = factor("Unk"))

# Join the two parts
hamby173and252_cleaning_still <- bind_rows(hamby173and252_cleaning_known1,
                                           hamby173and252_cleaning_unknown1)

# Adjust the barrel2 and bullet2 names for the known case
hamby173and252_cleaning_known2 <- hamby173and252_cleaning_still %>%
  filter(!barrel2 %in% letters) %>%
  mutate(bullet2 = factor(bullet2)) %>%
  select(barrel1, barrel2, bullet1, bullet2, 5:21)

# Adjust the barrel2 and bullet2 names for the unknown case
hamby173and252_cleaning_unknown2 <- hamby173and252_cleaning_still %>%
  filter(barrel2 %in% letters) %>%
  mutate(bullet2 = barrel2) %>%
  select(barrel1, barrel2, bullet1, bullet2, 5:21) %>%
  mutate(barrel2 = factor("Unk"))

# Join the two parts
hamby173and252_cleaned <- bind_rows(hamby173and252_cleaning_known2,
                                    hamby173and252_cleaning_unknown2)

# Clean the data from test sets 44
hamby44_cleaned <- hamby44 %>% 
  select(features, rfscore, samesource) %>%
  mutate(study1 = "Hamby44", study2 = "Hamby44")

# Bind the cleaned dataframes
hamby_cleaned <- bind_rows(hamby173and252_cleaned, hamby44_cleaned) %>%
  select(study1, barrel1, bullet1, land1, 
         study2, barrel2, bullet2, land2,
         ccf, cms, D, lag, matches, mismatches, non_cms, overlap, 
         rough_cor, sd_D, signature_length, sum_peaks, rfscore, samesource) %>%
  mutate(study1 = factor(study1),
         barrel1 = factor(barrel1),
         bullet1 = factor(bullet1),
         land1 = factor(land1),
         study2 = factor(study2),
         barrel2 = factor(barrel2),
         bullet2 = factor(bullet2),
         land2 = factor(land2))

# Export the cleaned data as a .csv file
write.csv(hamby_cleaned, "../data/features_cleaned.csv", row.names = FALSE)
```

\vspace{0.25cm}

Below is a summary of the structure of the cleaned hamby data.

\vspace{0.25cm}

```{r}
# Structure of the cleaned hamby data
str(hamby_cleaned)
```

# Creating the Training and Testing Datasets

Prior to applying LIME to the random forest model and the testing data, I need to recreate the training data that was used to fit the random forest model and create a matching testing dataset. The training data is created from the Hamby 173 and 252 test sets, and the testing data is created from the Hamby 44 test set. Based on the information learned in the previous journal about the random forest model `rtrees` that was used by Eric, the features of `ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks` need to be included in the training and testing datasets. Additionally, variables describing the pair of bullets in a row are included. The code below creates these two datasets and saves them as .csv files. The response variables of `samesource` are put in separate data frames along with the identification variables. These datasets are also saved as .csv files.

\vspace{0.25cm}

```{r}
# Create a vector of the random forest features to be included
rf_features <- c("ccf", "rough_cor", "D", "sd_D", "matches", 
                 "mismatches", "cms", "non_cms", "sum_peaks")

# Create the training dataset
hamby_train <- hamby_cleaned %>% 
  filter(study1 %in% c("Hamby173", "Hamby252")) %>%
  select(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2, 
         rf_features, samesource)

# Create the testing dataset
hamby_test <- hamby_cleaned %>% 
  filter(study1 %in% c("Hamby44")) %>% 
  select(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2, 
         rf_features, rfscore, samesource)

# Save the datasets and response variables as .csv files
write.csv(hamby_train, "../data/hamby_train.csv", row.names = FALSE)
write.csv(hamby_test, "../data/hamby_test.csv", row.names = FALSE)
```

# Exploring the Random Forest Features

I was interested in exploring the numeric features from the datasets to better understand them. The code below goes through the process of creating histograms for all of the numeric variables that compare two signatures for both the training and testing datasets. The distributions of the features look really similar when comparing the training and testing datasets.

\vspace{0.25cm}

```{r}
# Function for checking if a variable is type dbl
check_dbl <- function(x) type_sum(x) == "dbl"
```

```{r}
# Subset the Hamby 173 and 252 dataset to only contain the double variables
hamby_train_numeric <- hamby_train %>% 
  select_if(check_dbl) %>%
  select(sort(names(.)))

# Gather the data to use for plotting
hamby_train_numeric_gathered <- hamby_train_numeric %>%
  gather(key = "variable", value = "measurement")

# Plot histograms of the variables
ggplot(hamby_train_numeric_gathered, aes(x = measurement)) + 
  geom_histogram(bins = 30) + 
  facet_wrap( ~ variable, scales = "free") +
  theme_bw() + 
  labs(title = "Histograms of the Numeric Variables in the Hamby 173 and 252 Data", 
       x = "Count", y = "Measurement")
```

```{r}
# Subset the Hamby 44 dataset to only contain the double variables
hamby_test_numeric <- hamby_test %>% 
  select_if(check_dbl) %>%
  select(sort(names(.)), -rfscore)

# Gather the data to use for plotting
hamby_test_numeric_gathered <- hamby_test_numeric %>%
  gather(key = "variable", value = "measurement")

# Plot histograms of the variables
ggplot(hamby_test_numeric_gathered, aes(x = measurement)) + 
  geom_histogram(bins = 30) + 
  facet_wrap( ~ variable, scales = "free", ncol = 3) +
  theme_bw() + 
  labs(title = "Histograms of the Numeric Variables in the Hamby 44 Data",
       x = "Count", y = "Measurement")
```

\vspace{0.25cm}

Correlations are computed below between all pairs of variables that were used to fit the random forest `rtrees` within both the training or testing datasets. These are plotted in heat maps shown below using `plotly` to make them interactive.

\vspace{0.25cm}

```{r fig.width = 5, fig.height = 5}
# Compute a correlation matrix of the numeric variables
cormat_train <- cor(hamby_train_numeric)

# Melt the matrix for plotting purposes
melted_cormat_train <- reshape2::melt(cormat_train) %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")))

# Create a heatmap of the correlation matrix
plotcor_train <- ggplot(data = melted_cormat_train, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() + 
  scale_fill_gradient2() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x = "", y = "", fill = "Correlation",
       title = "Correlations of Numeric Variables in the Hamby 173 and 252 Data")

# Plot the correlation heatmap as an interactive plotly object
ggplotly(plotcor_train, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

```{r fig.width = 5, fig.height = 5}
# Compute a correlation matrix of the numeric variables
cormat_test <- cor(hamby_test_numeric)

# Melt the matrix for plotting purposes
melted_cormat_test <- reshape2::melt(cormat_test) %>%
  mutate(Var1 = factor(Var1, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")),
         Var2 = factor(Var2, levels = c("ccf", "cms", "matches", "rough_cor", "sum_peaks",
                                        "D", "sd_D", "mismatches", "non_cms")))

# Create a heatmap of the correlation matrix
plotcor_test <- ggplot(data = melted_cormat_test, aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() + 
  scale_fill_gradient2() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x = "", y = "", fill = "Correlation",
       title = "Correlations of Numeric Variables in the Hamby 44 Data")

# Plot the correlation heatmap as an interactive plotly object
ggplotly(plotcor_test, width = 600, height = 500) %>%
  shiny::div(align = "center")
```

### 2020-09-29 old-journals/bullet data/journals/03-applying LIME.Rmd
added old journals

---
title: "Applying LIME to the Bullet Data"
author: "Katherine Goode"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = FALSE)
```

# Overview

The journal goes through the process applying the `lime` and `explain` functions from the `lime` R package to the random forest model fit to the bullet training data.

The following R libraries will be used.

\vspace{0.25cm}

```{r}
# Load libraries
library(tidyverse)
library(lime)
library(randomForest)
library(bulletr)
```

# Applying LIME to Comparisons within Barrels 1 and 2 of the Testing Data

The training and testing datasets are loaded in below. To start, I am only going to obtain explanations for a small subset of the testing data. For now, I have subset the data to only contain the comparisons of lands within barrels 1 and 2. This leads to a dataset with 552 observations.

\vspace{0.25cm}

```{r}
# Load in the training data
hamby_train <- read.csv("../data/hamby_train.csv")

# Load in the testing data
hamby_test <- read.csv("../data/hamby_test.csv")

# Subset the testing data to only contain the comparisons within barrels 1 and 2
hamby_test_barrels1and2 <- hamby_test %>% filter(barrel1 %in% c(1, 2), barrel2 %in% c(1, 2))

# Save the subset data for later use
write.csv(hamby_test_barrels1and2, "../data/hamby_test_barrels1and2.csv", row.names = FALSE)
```

\vspace{0.25cm}

When the functions from `lime` are applied to the bullet data, only the features used to fit the random forest model `rtrees` should be included. Thus, a vector containing the random forest features is created below.

\vspace{0.25cm}

```{r}
# Create a vector of the random forest features to be included
rf_features <- c("ccf", "rough_cor", "D", "sd_D", "matches", 
                 "mismatches", "cms", "non_cms", "sum_peaks")

```

\vspace{0.25cm}

The code below applies the LIME algorithm to the random forest model `rtrees` and the bullet testing data using the `lime` R package. First, a seed is set, so that the same results are returned each time the code in this journal is run since the LIME algorithm creates random permutations. Next, the `lime` function with default settings from the `lime` package is applied to the training data and random forest model to obtain what I will refer to as the "lime" object. The default settings for the `lime` function are as follows.

- `bin_continuous = TRUE`: If set to `TRUE`, the continuous variables will be binned when making the explanations. If they are not binned, then perturbations will be obtained by either simulating using kernel density estimation or a normal distribution depending on what the option of `use_density` is set to. 
- `bins = 4`: The number of bins to divide the continuous variables into. The default is 4 bins.
- `quantile_bins = TRUE`: If set to `TRUE`, the bins will be be based on `n_bins` quantiles. Otherwise, the bins will be spread evenly over the range of the training data.
- `use_density = TRUE`: If `bin_continuous` is set to `FALSE` and this is set to `TRUE`, then the continuous data will be sampled using kernel density estimation. Otherwise, it will be assumed that the continuous features follow a normal distribution and samples will be drawn from a normal distribution with the mean and standard deviation set to the sample mean and standard deviation associated with the feature.

The "lime" object is saved as an .rds file.

\vspace{0.25cm}

```{r}
# Set a seed
set.seed(84902)

# Apply the lime function from the lime package
# Note that the as_classifier must be added since rtrees is from the
# randomForest package and not fit using caret or one of the other 
# available models specified in the lime package. Additionally, the
# randomForest package must be loaded in order to run the functions
# from the lime package.
hamby_lime <- lime::lime(x = hamby_train %>% select(rf_features),
                         model = as_classifier(rtrees))

# Save the lime object
saveRDS(hamby_lime, "../data/hamby_lime.rds")
```

\vspace{0.25cm}

Next, the `explain` function is applied to the testing data and "lime" object to obtain the "explain" object. The number of labels (`n_labels`) for the response variable is set to 1, the number of features to include in the explanations (`n_features`) is set to 2, and the remaining options are set to the default values. These default values are as follows.

- `n_permutations = 5000`: The number of perturbations generated for each feature.
- `feature_select = 'auto'`: This is the feature selection method for choosing the number of features specified. This uses forward selection if $m\le 6$ and otherwise highest weights. The other feature selection options are as follows.
    - `none`: Use all features for the explanation. Not advised unless you have very few features.
    - `forward selection`: Features are added one by one based on their improvements to a ridge regression fit of the complex model outcome.
    - `highest weights`: The m features with highest absolute weight in a ridge regression fit of the complex model outcome are chosen.
    - `lasso`: The m features that are least prone to shrinkage based on the regularization path of a lasso fit of the complex model outcome is chosen.
    - `tree`: A tree is fitted with log2(m) splits, to use at max m features. It may possibly select less.
- `dist_fun = 'gower'`: The distance function to be used for determining how close a perturbation is to the test point.
- `kernel_width = NULL`: If `dist_fun` is not set to `gower`, then this is the kernel width that will be used in the distance function.

The "explain" object is saved as .rds files.

\vspace{0.25cm}

```{r}
# Set a seed
set.seed(84902)

# Apply the explain function from the lime package
hamby_explain_barrels1and2 <- lime::explain(hamby_test_barrels1and2 %>% select(rf_features), 
                                       hamby_lime, 
                                       n_labels = 1, 
                                       n_features = 3)

# Save the explain object
saveRDS(hamby_explain_barrels1and2, "../data/hamby_explain_barrels1and2.rds")
```

### 2020-09-29 old-journals/bullet data/journals/05-LIME conclusions.Rmd
added old journals

---
title: "Conclusions from Applying LIME to the Hamby Bullet Data"
author: "Katherine Goode"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This journal contains some of my concluding thoughts from going through the process of applying LIME to the Hamby bullet data.

# Conclusions

- I was concerned that the $R^2$ values were too low, and I was thinking that we may need to make some corrections to the LIME specificiations. Heike thinks that as long as the LIME results make sense we should be okay to ignore the low $R^2$ values. She thinks that the variables that should be important most of the time would be `ccf` and `matches`.
- Heike thinks that the variables that LIME is showing as being important are what she would expect.

# Concerns with LIME

- It would be nice if LIME output the model AIC in addition to the $R^2$ value.
- I would like a way to check if the results LIME produces are trustworthy. How can this be done? Is the $R^2$ value enough?
- I'm nervous about the fact that the results can change due to the permutations. Is there a way to check for consistencey? Does this only happen if you have correlated variables, or can it also happen with uncorrelated variables?
- When you have a large number of predictions to assess, would it be a good idea to focus in on the ones that have the best fitting linear model or produce the most consistent results?
- What can be done to improve the linear regression model fit? Maybe adjusting the number of bins or the kernel width would help with this.

# Future Work

- When writing the paper, we will need to redo this process with the updated version of the random forest model.
- The new random forest model will be fit using some different Hamby test set data. Possibly Hamby 44 and Hamby 244. 
- The new random forest will also use the updated features.
- I need to add interactivity to the plots of the plots of the land comparisons with the random forest prediction probabilities.
- I need to figure out why the LIME probabilities do not match the random forest scores.

### 2020-09-29 old-journals/bullet data/journals/Heike_first example of lime with bullet data.Rmd
added old journals

---
title: "Testing Lime"
author: "Heike Hofmann"
date: "10/7/2017"
output: pdf_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures-lime/',
  echo=TRUE
)
options(knitr.table.format = "latex")

library(tidyverse)
library(scales)
library(multidplyr)
library(bulletr)
library(gridExtra)
library(kableExtra)
```

```{r read}
hamby <- read.csv("data/features-hamby.csv.gz") %>% filter(study1 != "Cary", study2 != "Cary")
library(caret)
library(lime)

# Split up the data set
idx <- createDataPartition(hamby$match, p = 0.1, list=FALSE)

hamby_test <- hamby[idx,]
hamby_train <- hamby[-idx,]

# Create Random Forest model on hamby data
vars <- c("ccf", "rough_cor", "lag", "D", "sd_D", "overlap", "cms", "non_cms", "sum_peaks")
model <- train(hamby_train %>% select(one_of(vars)), factor(hamby_train$match), method = 'rf')
saveRDS(model, file="lime-data/model.rds")

# Create an explainer object
explainer <- lime(hamby_train %>% select(one_of(vars)), model)
saveRDS(explainer, file="lime-data/explainer.rds")

# Explain new observation
explanation <- explain(hamby_test %>% select(one_of(vars)), explainer, n_labels = 1, n_features = 9)
explanation$truth <- rep(hamby_test$match,each=9)
plot_features(explanation[1:9,])
saveRDS(explanation, file="lime-data/explanation.rds")
```

```{r second}
newGrid = expand.grid(mtry = 4:6)
second <- train(hamby_train %>% select(one_of(vars)), factor(hamby_train$match), method = 'rf', tuneGrid = newGrid)
saveRDS(second, file="lime-data/model-second.rds") # mtry=4 seems to work the best (by a very small margin, but there's not that much room for improvement anyway)
```

### 2020-09-29 old-journals/bullet data/journals/Heike_matching.Rmd
added old journals

---
title: "Re-scanning: Hamby-44"
author: "Heike Hofmann, CSAFE"
date: "8/19/2017"
output: html_document
bibliography: ../references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  fig.width=8, fig.height=8)

sam_boot <- function(n = 1000, values, observed, m = 6) {
  res <- replicate(n, {
    X = base::sample(x = values, size = m, replace = FALSE)
    mean(X, na.rm=TRUE)
  })
  list(pval=sum(res>=observed)/n, samples = res)
}
```
## Study Setup

## Results:

All lands are processed using the fully automated matching algorithm described in [@aoas, @bulletr], resulting in all land-to-land comparisons of known and unknown LEAs. 
Bullet-by-bullet comparisons are based on Sequence Average Maximums (SAMs) [@sam] of land-by-land comparisons of maximized cross-correlation (sam_ccf) and scores from the random forest (sam_rf).

## Checking for consistency

```{r dataload, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
library(pander)
features <- read.csv("data/features.csv")
f2 <- features

f2nest <- f2 %>% filter(!(barrel1==barrel2 & bullet1 == bullet2)) %>% group_by( bullet2, barrel1, barrel2, bullet1) %>%  nest()

rotate <- function(x, lag) {
  n <- length(x)
  rep(x, 2)[lag+1:n]
}

f3nest <- f2nest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
    dt = xtabs(ccf ~land1+land2, data=d)
    drow <- dim(dt)[2]
    1:drow %>% purrr::map_dbl(.f=function(i) {
      mean(diag(dt[,rotate(1:drow,i)]))
    }) %>% max()
  }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    dt = xtabs(rfscore ~land1+land2, data=d)
    drow <- dim(dt)[2]
    1:drow %>% purrr::map_dbl(.f=function(i) {
      mean(diag(dt[,rotate(1:drow,i)]))
    }) %>% max()
  })#,
#  KM = data %>% purrr::map_lgl(.f=function(d) { any(d$KM) })
)

f3nest <- f3nest %>% mutate(
  bulletland2 = paste( barrel2, bullet2, sep="-"),
  bulletland1 = paste( barrel1, bullet1, sep="-")
)

```

### Checking consistency: knowns against knowns

```{r, echo=FALSE, fig.cap="Bullet-to-bullet summary of all test fires. Two test fires are available for each of ten barrels. We expect to see orange tiles (high rf values) on the diagonal and grey tiles everywhere else.", fig.width=7, fig.height=6.5}
knowns <- f3nest %>% filter(barrel1!="Unk", barrel2!="Unk") 
knowns %>% ggplot(aes(x = bullet1, y = bullet2, fill=sam_rf)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.35) +
  facet_grid(barrel1~barrel2)
```

```{r, echo=FALSE, fig.cap="Land-to-land overview for test fires from the same barrels. We expect to see one diagonal line of six orange tiles in each of the squares.", fig.width=8, fig.height =6}
knowns %>% filter(barrel1==barrel2) %>% unnest(data) %>% 
  mutate(land1 = gsub("and ", "", land1), land2 = gsub("and ", "", land2)) %>%
  ggplot(aes(x = land1, y = land2, fill=rfscore)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.35) +
  facet_wrap(~barrel1)

```

### Checking unknowns against unknowns

```{r, echo=FALSE, fig.cap="Bullet-to-bullet overview of all pairwise comparisons of questioned bullets. Fifteen bullets are questioned in Hamby-44. It is known that all fires come from the same ten barrels. We would therefore expect at least five matches between questioned bullets.", fig.width=8, fig.height=8}
unknowns <- f3nest %>% filter(barrel1=="Unk", barrel2 == "Unk")

library(seriation)
dt <- matrix(xtabs(I(sam_rf*(sam_rf>.35))~bulletland1+bulletland2, data=unknowns), ncol=length(unique(unknowns$bulletland1)))
order <- seriate(dt, method="PCA_angle")
unknowns <- unknowns %>% mutate(
  bulletland1 = factor(bulletland1),
  bulletland2 = factor(bulletland2)
)
unknowns <- unknowns %>% mutate(
  bulletland1 = factor(bulletland1, levels=levels(unknowns$bulletland1)[order[[1]]]),
  bulletland2 = factor(bulletland2, levels= levels(unknowns$bulletland2)[order[[2]]])
)

unknowns %>% ggplot(aes(x = bullet1, y = bullet2, fill=sam_rf)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.35) 
```

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Land-to-land overviews between any two questioned bullets that show a score high enough for matching (0.375). If the bullets are indeed a match, we would like to see a matching sequence in the tiles."}
unknowns %>% filter(sam_rf > 0.375) %>% unnest(data) %>% 
  mutate(land1 = gsub("and ", "", land1), land2 = gsub("and ", "", land2)) %>%
  ggplot(aes(x = land1, y = land2, fill=rfscore)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.35) +
  facet_wrap(~bullet1+bullet2)

```

## Results from matching

```{r, echo=FALSE, fig.width=10, fig.height=7.5, fig.cap="Bullet-to-bullet overview of questioned bullets (along y axis) and all known fires from the ten barrels. We want to see one barrel match for each questioned bullet (i.e. both test fires should show a match, and only one barrel should match)."}
questioned <- f3nest %>% filter(barrel1!="Unk", barrel2=="Unk") 
questioned <- questioned %>% mutate(
  bullet2 = factor(bullet2, 
                   levels=rev(c("K", "S", "O", "L", "P", "J", "I", "H", "Y", "G", "X", "U", "E", "F", "T")))
)
questioned %>% 
  ggplot(aes(x = bullet1, y = bullet2, fill=sam_rf)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.3) +
  facet_grid(.~barrel1)
```

```{r, echo=FALSE, fig.width=10, fig.height=8, fig.cap="Land-to-land overview of all pairs of questioned bullets and known test fires. For each match, we want to see q matching sequence in the tiles."}
questioned %>% unnest(data) %>%
  mutate(land1 = gsub("and ", "", land1), land2 = gsub("and ", "", land2)) %>%
  ggplot(aes(x = land1, y = land2, fill=rfscore)) + geom_tile() +
  scale_fill_gradient2(low="darkgrey", high="darkorange", midpoint=.3) +
  facet_grid(bullet2~barrel1+bullet1)
```

## References

### 2020-09-29 old-journals/iris data/journals/examples with lime applied to iris data.Rmd
added old journals

---
title: "Examples with the `lime` R package applied to a Random Forest Model fit to the Iris Data"
author: "Katherine Goode"
date: "Last Updated: 2018/04/18"
output:
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Overview

This document contains examples that apply the LIME algorithm to a random forest model fit to the iris data. These examples are both meant to better understand how the R package `lime` implements the LIME algorithm and to explore whether the explanations returned by `lime` are reasonable. The first example verifies how the ridge regression function is fit within the `lime` package. The next example considers plots of the perturbation created by `lime` in order to visually inspect if the default method in LIME does a good job of selecting the important local predictors. The last example compares the fit of the ridge regression model when different feature selection methods are used.

# Set Up for Examples

## Loading Packages, Sourcing Code, and Setting a Seed

The code below loads the R packages that will be used and sources the code from the `lime` R package and functions I have written. My functions include my version of the `lime` explain.data.frame, which exports the perturbations and numerified perturbations along with the explanation table. I have also written functions for plotting the perturbations. Additionally, a seed is set since some of the procedures in these examples involve randomization. This will allow for replication of the examples.

\vspace{0.5cm}

```{r}
# Load libraries
library(R.utils)
library(caret)
library(tidyverse)
library(knitr)

# Source in code from the lime R package
sourceDirectory("../../../LIME R Package/R")

# Source in the functions I have written
sourceDirectory("../../my functions")

# Set a seed for any randomization that occurs in the example to maintain consistency
set.seed(174920)
```

## Training and Testing Data

The code below splits the iris data into training and testing parts. To do this, two cases are selected randomly from within each of the three species of irises. These cases are put in the testing data, and the other cases are made into the training data. For both the training and testing data, the features are put in a data frame, and the response variables are put in separate vectors.

\vspace{0.5cm}

```{r}
# Randomly select two cases from within each of the three species of irises
selected <- c(sample(1:50, 2), sample(51:100, 2), sample(101:151, 2))

# Split up the features of the data into training and testing parts
iris_train <- iris[-selected, 1:4]
iris_test <- iris[selected, 1:4]

# Grab the response variables from both the training and testing data
iris_train_response <- iris[[5]][-selected]
iris_test_response <- iris[[5]][selected]
```

## Random Forest Model

A random forest model is fit to the training data using the `caret` package with all of the default settings. All four features (`Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`) from the iris data are put in the random forest model. The model is then used to make predictions on the testing data. The predictions are compared to the actual observed species for the test cases. The table below contains the observed species and predicted species from the test data, and we see that the models gets all of the predictions correct. However, we will use `lime` to see which features were key in making these predictions to see if the predictions are based on features that make sense.

\vspace{0.5cm}

```{r}
# Random forest model run on the iris data
iris_model <- train(iris_train, iris_train_response, method = 'rf')

# Predictions made using the random forest model on the testing data
iris_model_predict <- predict(iris_model, iris_test)

# Matrix of observed and predicted values
iris_test_obs_pred <- matrix(c(iris_test_response, iris_model_predict), 
                             ncol = 2, byrow = FALSE)

# Specify the column names
colnames(iris_test_obs_pred) <- c("Observed", "Predicted")

# Print the table
kable(iris_test_obs_pred, align = 'c')
```

## LIME Functions

The LIME algorithm is applied to the model now. First, the `lime` function from the R package is run on the iris training data and random forest model. All of the default settings are used, which are as follows.

\vspace{0.25cm}

\begin{itemize}
\item \texttt{bin\_continuous = TRUE}: If set to `TRUE`, the continuous variables will be binned when making the explanations. If they are not binned, then perturbations will be obtained by simulating from a normal distribution with sample mean and standard deviation associated with the feature.
\item \texttt{bins = 4}: The number of bins to divide the continuous variables into. The defualt is 4 bins.
\item \texttt{quantile\_bins = TRUE}: If set to `TRUE`, the bins will be be based on `n\_bins` quantiles. Otherwise, the bins will be spread evenly over the range.
of the training data
\end{itemize}

\vspace{0.25cm}

Next, my version of the `explain` function for dataframes is applied to the testing data and the `lime` "explainer" object. The number of labels for the response variable is set to 3 (for the three species of irises), the number of features to include in the explanations is set to 2, and the remaining options are set to the default values. These default values are as follows.

\vspace{0.25cm}

\begin{itemize}
\item \texttt{n\_permutations = 5000}: The number of perturbations generated for each feature.
\item \texttt{feature\_select = 'auto'}: This is the feature selection method for choosing the number of features specified. In the vignette for the \texttt{lime} package, Thomas describes the options as follows.
\begin{itemize}
\item \texttt{none}: Use all features for the explanation. Not advised unless you have very few features.
\item \texttt{forward selection}: Features are added one by one based on their improvements to a ridge regression fit of the complex model outcome.
\item \texttt{highest weights}: The m features with highest absolute weight in a ridge regression fit of the complex model outcome are chosen.
\item \texttt{lasso}: The m features that are least prone to shrinkage based on the regularization path of a lasso fit of the complex model outcome is chosen.
\item \texttt{tree}: A tree is fitted with log2(m) splits, to use at max m features. It may possibly select less.
\item \texttt{auto}: Uses forward selection if m <= 6 and otherwise highest weights.
\end{itemize}
The default is set to \texttt{auto}.
\item \texttt{dist\_fun = 'gower'}: The distance function to be used for determining how close a perturbation is to the test point. The default is set to `gower`.
\item \texttt{kernel\_width = NULL}: If `dist\_fun` is not set to `gower`, then this is the kernel width that will be used in the distance function. If set to `NULL`, which is the default, the default method within \texttt{lime} is used.
\end{itemize}

\vspace{0.25cm}

The output from the `my_explain.data.frame` contains a list with three objects. The first contains the `lime` explanations, the second is the perturbations, and the thrid is the numerified perturbations. These three objects are separated and given the names of `iris_explanation`, `iris_perturb`, and `iris_perturb_numerified`, respectively.

\vspace{0.5cm}

```{r}
# Run the lime function on the iris data and random forest model with 4 bins
iris_explainer <- lime.data.frame(iris_train, iris_model)

# Run the explain function for data frames on the iris data
iris_explanation_list <- my_explain.data.frame(iris_test, iris_explainer,
                                               n_labels = 3, n_features = 2)

# Create a separate data frame for the explanations
iris_explanation <- iris_explanation_list$explanations

# Create a separate data frame for the perturbations
iris_perturb <- iris_explanation_list$perturb

# Create a separate data frame for the numerified perturbations
iris_perturb_numerified <- iris_explanation_list$perturb_numerified 
```

# Examples

## Verifying the Ridge Regression Procedure

I wanted to verify that I understood how the ridge regression model was being fit by the `lime` package. To start, I selected the pertrubations and response probability of setosa associated with the first test case. Then I fit a ridge regression model with a response variable of the probability of the perturbation being setosa and predictor variables of the simulated perturbations for the two features selected by feature selection. I set $\lambda=0.001$, which is what `lime` does. Then I extracted the coefficients from the ridge regression model and compared these to the coefficients from `lime`. These are included in the table below. I discovered that they did not agree, which told me that my initial understanding of how `lime` fit the ridge regression model was not correct.

\vspace{0.5cm}

```{r}
# Select only explanations associated with the first case and outcome of setosa
iris_explain_sub <- iris_explanation %>% 
  filter(label == "setosa") %>%
  slice(1:2)

# Put perturbations for the selected features from the first test case into 
# a data frame 
iris_perturb_sub <- iris_perturb %>% 
  filter(Test_Case == iris_explain_sub$case) %>% 
  select(iris_explain_sub$feature, setosa, Weight)

# Fit the ridge regression model as I understand it...
rr1 <- glmnet(as.matrix(iris_perturb_sub[,1:2]), iris_perturb_sub$setosa, 
              weights = iris_perturb_sub$Weight, alpha = 0, lambda = 0.001)

# Matrix with coefficients from my ridge regression model and from the lime 
# ridge regression model
coefs1 <- matrix(c(rr1$a0, rr1$beta[1], rr1$beta[2],
                   iris_explain_sub$model_intercept[1],
                   iris_explain_sub$feature_weight), 
                 nrow = 3, byrow = FALSE)

# Label the rows and columns of the matrix
rownames(coefs1) <- c("beta0", "beta1", "beta2")
colnames(coefs1) <- c("My Ridge Regression", "LIME Ridge Regression")

# Print the coefficients in a table
kable(coefs1, align = 'c')
```

\vspace{0.5cm}

I remembered that `lime` creates numerified pertrubations, which assign a 0 or a 1 to the observation based on whether or not it falls into the same bin as the observed case. I wondered if `lime` used these values as the features. I fit a new ridge regression model using the numerified perturbations from the selected features as the predictor variables in the model. I compared the coefficients from my model to the one fit by `lime`. These are shown in the table below. They agree this time! Thus, `lime` is using the numerified perturbations when it fits the ridge regression model.

\vspace{0.5cm}

```{r}
# Select the numerified perturbations associated with test case 1, and select
# only the chosen features
iris_perturb_numerified_sub <- iris_perturb_numerified %>%
  filter(Test_Case == iris_explain_sub$case) %>% 
  select(iris_explain_sub$feature)

# Fit the ridge regression again with the numerified perturbations instead of 
# the regular perturbations
rr2 <- glmnet(as.matrix(iris_perturb_numerified_sub), iris_perturb_sub$setosa, 
              weights = iris_perturb_sub$Weight, alpha = 0, lambda = 0.001)

# Matrix with coefficients from my ridge regression model and from the lime 
# ridge regression model
coefs2 <- matrix(c(rr2$a0, rr2$beta[1], rr2$beta[2],
                   iris_explain_sub$model_intercept[1],
                   iris_explain_sub$feature_weight), 
                 nrow = 3, byrow = FALSE)

# Label the rows and columns of the matrix
rownames(coefs2) <- c("beta0", "beta1", "beta2")
colnames(coefs2) <- c("My Ridge Regression", "LIME Ridge Regression")

# Print the coefficients in a table
kable(coefs2, align = 'c')
```

\vspace{0.5cm}

I do not understand why `lime` has chosen to use the numerified perturbations instead of the regular perturbations when fitting the ridge regression models. Someone did ask about this on the GitHub page for `lime`. The question was a follows.

\begin{quote}
For continuous variables with bin\_continuous=TRUE, it seems like the data set used for the regression (and for the computation of weights) consists of zeroes and ones only, where the value in row i for variable j is 1 if the bin for this variable in this row is equal to the bin for the same variable in the observation vector and 0 otherwise. Is this correct? If yes, doesn't one then discard a lot of information, since there obviously is a larger distance between e.g. bins 1 and 5 than there is between bins 1 and 2?
\end{quote}

Thomas answered the question as follows.

\begin{quote}
This is correct - the explanation looks into whether the bin significantly affects the model. I guess the reason that it is done this way is to ease interpretation at the cost of a potentially worse local fit..
\end{quote}

The link to where this disucssion can be found is https://github.com/thomasp85/lime/issues/68. This answer helps a bit in understanding why this was done, but I do not feel like it is satistfactory. I would still like to look more into this. I have two main questions that I would like to try to answer.

\begin{itemize}
\item How can the model coefficients be interpred since the numerified perturbations are used?
\item How are the `lime` explanations affected by using the numerified perturbations instead of the regular perturbations?
\end{itemize}

## Plots of Perturbations with Default `lime` Settings

In order to better understand how `lime` works, I wanted to create some visualizations of the perturbations created by `lime`. I was interested in visualizing the distributions of the pertrubations and how they compared to the original data. I was also interested in looking at the relationship between the pertrubations and the probability that the perturbation fell in a specific species response category. This is the relationship that the ridge regression that `lime` fits is trying to capture and use to determine which features are most influnential in determining the predictions made by the model.

To access these visualizations, I created two functions. The function `plot_perturbs` plots the top two features chosen by the default settings in `lime` for both the perturbations and the original data. The perturbations are colored by the response that the model predicts for the perturbation. This plot allows one to visualize the regions of the feature space that the model predicts to be a certain response. I was hoping that this type of plot would help to identify whether the two chosen variables lead to a clear region in which the model predicts one way or the other. More details about what the plots shows will be described in Section \@ref(plotperturb).

The other function, `plot_probs`, creates two plots corresponding to the top two features chosen by the default settings in `lime`. The plot shows the probability that a perturbation will be the associated response on the y axis and the value of the feature on the x-axis. These plots were meant to visualize whether there is a linear relationship between the probability, which is used as the response in the ridge regression, and the feature value. However, keep in mind that the ridge regression uses the numerified value of the feature instead of the raw value. More details about the plot will be included in Section \@ref(plotprob)

### Plots of Perturbations and Original Data {#plotperturb}

Each plot created using `plot_perturbs` corresponds to one observation (case) in the test data. This point is represented by a black dot in the plot. The ring of color around the black dot represents the species that the random forest predicts the test case to be. The larger dots represent the observed training data. The color of the point represents the true species associated with the observation. The smaller points in the plots represent the perturbations created by `lime`. The color of the small point represents the species that the random forest predicts the perturbation to be. The shade of the color of the small points is the weight assigned to the perturbation by `lime`, which signifies how "close" or how "similar" the perturbation is to the test case of interest. Darker shades indicate that the perturbation is "close" to the test case. The perturbations with higher weights will be more influential in the ridge regression model that is fit to determine which features are important. The variable on the x-axis is the feature selected by the default settings in `lime` as the most important feature in the predictive model. The variable on the y-axis is the second most important feature selected by the default settings in `lime`.

The plot shown below corresponds to the first observation in the `Iris` test data. This point falls in the cluster of training data points that belong to the species setosa. The model predicts that this test point has a species of setosa, and the model makes the right prediction.

\vspace{0.5cm}

```{r fig.width = 5.5, fig.height = 4, fig.align = 'center'}
# Test Case 1: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[1],
              resp_category = 'setosa', 
              separate = FALSE)

# Test Case 2: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[2],
              resp_category = 'setosa', 
              separate = FALSE)

# Test Case 3: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[3],
              resp_category = 'versicolor', 
              separate = FALSE)

# Test Case 4: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[4],
              resp_category = 'versicolor', 
              separate = FALSE)

# Test Case 5: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[5],
              resp_category = 'virginica', 
              separate = FALSE)

# Test Case 6: Plot of the selected features perturbations with predictions
# and observed training data
plot_perturbs(train = iris_train, 
              response = iris_train_response,
              perturb = iris_perturb, 
              explain = iris_explanation, 
              test_case = unique(iris_explanation$case)[6],
              resp_category = 'virginica', 
              separate = FALSE)
```

### Plots of Probabilities and Perturbations {#plotprob}

\vspace{0.5cm}

```{r fig.width = 10, fig.height = 5, fig.align = 'center'}
# Test Case 1: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[1],
           resp_category = 'setosa')

# Test Case 2: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[2],
           resp_category = 'setosa')

# Test Case 3: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[3],
           resp_category = 'versicolor')

# Test Case 4: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[4],
           resp_category = 'versicolor')

# Test Case 5: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[5],
           resp_category = 'virginica')

# Test Case 6: Plots of the probabilities versus the selected features of the 
# perturbations with predictions and observed training data
plot_probs(train = iris_train, 
           response = iris_train_response, 
           perturb = iris_perturb, 
           explain = iris_explanation, 
           test_case = unique(iris_explanation$case)[6],
           resp_category = 'virginica')
```

## Comparing Feature Selection Methods in `lime`

Since the plots above led me to believe that LIME was not doing a great job of selecting the important features, I wanted to compare the feature selection methods. I noticed that the $R^2$ value seemed low for the ridge regressions that `lime` was fitting, and I was curious to know if a different feature selection method would lead to a higher $R^2$ value and more reasonable features chosen by `lime`. I also wanted to compare the $R^2$ values bewteen ridge regressions fit using the numerified perturbations (like `lime` does) and fit using the actual perturbations. The first section below considers the numerified perturbations, and the the following section considers the actual pertrubations.

### Feature Selection with Numerified Perturbations

I ran my version of the `explain` function with all six options for feature selection. I fit the ridge regression models using the original code from `lime` that uses the numerified perturbations as the predictor variables in the model.

\vspace{0.5cm}

```{r}
## Auto Selection
iris_auto <- my_explain.data.frame(iris_test, iris_explainer, 
                                   n_labels = 3, n_features = 2,
                                   feature_select = 'auto')
iris_explain_auto <- iris_auto$explanations

## Forward Selection
iris_forward <- my_explain.data.frame(iris_test, iris_explainer, 
                                      n_labels = 3, n_features = 2,
                                      feature_select = 'forward_selection')
iris_explain_forward <- iris_forward$explanations

## Heighest Weights
iris_heighest <- my_explain.data.frame(iris_test, iris_explainer, 
                                       n_labels = 3, n_features = 2,
                                       feature_select = 'highest_weights')
iris_explain_heighest <- iris_heighest$explanations

## LASSO
iris_lasso <- my_explain.data.frame(iris_test, iris_explainer, 
                                    n_labels = 3, n_features = 2,
                                    feature_select = 'lasso')
iris_explain_lasso <- iris_lasso$explanations

## Tree
iris_tree <- my_explain.data.frame(iris_test, iris_explainer, 
                                   n_labels = 3, n_features = 2,
                                  feature_select = 'tree')
iris_explain_tree <- iris_tree$explanations
```

\vspace{0.5cm}

I extracted the $R^2$ values from all of the ridge regression models. This includes models for all 6 cases and 3 species labels. Thus, there were a total 18 $R^2$ values per feature selection method.

\vspace{0.5cm}

```{r}
# Create a data frame with all of the R2 values from the different feature selection
# methods
r2 <- data.frame(case = iris_explain_auto$case,
                 label = iris_explain_auto$label,
                 label_prob = iris_explain_auto$label_prob,
                 auto = iris_explain_auto$model_r2,
                 forward = iris_explain_forward$model_r2,
                 heighest = iris_explain_heighest$model_r2,
                 LASSO = iris_explain_lasso$model_r2,
                 tree = iris_explain_tree$model_r2)

# Only keep the unique rows
r2 <- unique(r2)

# Gather the dataset
r2_gathered <- r2 %>% gather(method, r2, 4:8)

# Reorder the levels of the case variable
r2_gathered$case <- factor(r2_gathered$case, 
                           levels(r2_gathered$case)[c(2, 1, 6, 5, 3, 4)])

# Rename the levels of the case variable
levels(r2_gathered$case) <- c("119 (virginica)", "113 (virginica)", 
                              "79 (versicolor)", "63 (versicolor)",
                              "29 (setosa)", "3 (setosa)")
```

\vspace{0.5cm}

The plot below shows the $R^2$ values for each method associated with a case and facetted by a species label. Within each case and within each species label, the $R^2$ values are the highest for the feature selection methods of highest, LASSO, and tree. This suggests that these three feature selection methods lead to the best linear fit with the iris perturbations. Within the species facets, the cases which have a true species corresponding to the label have the highest $R^2$ values of the cases for both setosa and virginica. This suggests that the cases with a model fit with a response variable corresponding to the true species of the case leads to a higher $R^2$ for both setosa and virginica. It appears that it is hard to find a linear relationship for any feature selection method with the species of versicolor.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 14, fig.height = 4.5}
# Tile plot of feature selection method and case colored by r2 facetted by label
ggplot(r2_gathered, aes(x = method, y = case)) +
  geom_tile(aes(fill = r2)) +
  facet_wrap(~label) +
  labs(x = "Feature Selection Method", y = "Case", fill = expression(R^2))
```

\vspace{0.5cm}

The boxplots below show the distribution of $R^2$ values within a feature selection method for each of the species. This further shows that the $R^2$ values tend to be higher for the feature selection methods of highest, LASSO, and tree for all three methods. These plots also highlight how the $R^2$ values are much more variable for the species of setosa and virginica than the species of versicolor. All of the $R^2$ values for versicolor are low.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 12 , fig.height = 3.5}
# Plot the R2 values in boxplots by the feature selection method
ggplot(r2_gathered, aes(x = method, y = r2)) + 
  geom_boxplot() + 
  facet_wrap(~label) + 
  labs(x = "Feature Selection Method", y = expression(R^2)) +
  theme(text = element_text(size = 10))
```

\vspace{0.5cm}

I also wanted to see how the $R^2$ values compared for just the true species labels. I subsetted the data to only contain the $R^2$ values from models fit with a response of the probability from the true species.

\vspace{0.5cm}

```{r}
# Create a data frame with only the true species labels
r2_true <- r2 %>%
  group_by(case) %>%
  filter(label_prob == max(label_prob))

# Gather the dataset
r2_true_gathered <- r2_true %>% gather(method, r2, 4:8)

# Reorder the levels of the case variable
r2_true_gathered$case <- factor(r2_true_gathered$case, 
                           levels(r2_true_gathered$case)[c(2, 1, 6, 5, 3, 4)])

# Rename the levels of the case variable
levels(r2_true_gathered$case) <- c("119 (virginica)", "113 (virginica)", 
                                   "79 (versicolor)", "63 (versicolor)",
                                   "29 (setosa)", "3 (setosa)")
```

\vspace{0.5cm}

Again, a tile plot shows the $R^2$ value for each feature selection method within a case. The feature selection methods of heighest, LASSO, and tree have the highest $R^2$ values, especially for the cases with a true species of setosa and virginica. The boxplots show a similar message.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 12, fig.height = 3.75}
tile <- ggplot(r2_true_gathered, aes(x = method, y = case)) +
  geom_tile(aes(fill = r2)) + 
  labs(x = "Feature Selection Method", y = "Case", fill = expression(R^2))

# Plot the R2 values in boxplots by the feature selection method
box <- ggplot(r2_true_gathered, aes(x = method, y = r2)) + 
  geom_boxplot() +
  labs(x = "Feature Selection Method", y = expression(R^2))

cowplot::plot_grid(tile, box)
```

### Feature Selection with Actual Perturbations

Next, I ran my version of the `explain` function with all six options for feature selection. This time, I added an option in my `explain` function that allowed the ridge regression to be fit using the actual pertrubations as the predictor variables instead of the numerified perturbations.

\vspace{0.5cm}

```{r}
## Auto Selection (with actual perturbations)
iris_auto_v2 <- my_explain.data.frame(iris_test, iris_explainer, 
                                      n_labels = 3, n_features = 2,
                                      feature_select = 'auto', 
                                      rr_predictors = "perturb")
iris_explain_auto_v2 <- iris_auto_v2$explanations

## Forward Selection (with actual perturbations)
iris_forward_v2 <- my_explain.data.frame(iris_test, iris_explainer, 
                                         n_labels = 3, n_features = 2,
                                         feature_select = 'forward_selection', 
                                         rr_predictors = "perturb")
iris_explain_forward_v2 <- iris_forward_v2$explanations

## Heighest Weights (with actual perturbations)
iris_heighest_v2 <- my_explain.data.frame(iris_test, iris_explainer,
                                          n_labels = 3, n_features = 2,
                                          feature_select = 'highest_weights', 
                                          rr_predictors = "perturb")
iris_explain_heighest_v2 <- iris_heighest_v2$explanations

## LASSO (with actual perturbations)
iris_lasso_v2 <- my_explain.data.frame(iris_test, iris_explainer, 
                                       n_labels = 3, n_features = 2,
                                       feature_select = 'lasso',
                                       rr_predictors = "perturb")
iris_explain_lasso_v2 <- iris_lasso_v2$explanations

## Tree (with actual perturbations)
iris_tree_v2 <- my_explain.data.frame(iris_test, iris_explainer, 
                                      n_labels = 3, n_features = 2,
                                      feature_select = 'tree', 
                                      rr_predictors = "perturb")
iris_explain_tree_v2 <- iris_tree_v2$explanations
```

\vspace{0.5cm}

I extracted the $R^2$ values from the ridge regressions fit with a response of one of the species and the pertrubations as the predictors for each case and each of the feature selection methods. For some reason, the tree method is not creating a model for the same number of cases as the other methods. I am not sure why this is. For now, I have exculded the tree feature selection method, and I will try to fix this later.

\vspace{0.5cm}

```{r}
# Create a data frame with all of the R2 values from the different feature selection
# methods
r2_v2 <- data.frame(case = iris_explain_auto_v2$case,
                    label = iris_explain_auto_v2$label,
                    label_prob = iris_explain_auto_v2$label_prob,
                    auto = iris_explain_auto_v2$model_r2,
                    forward = iris_explain_forward_v2$model_r2,
                    heighest = iris_explain_heighest_v2$model_r2,
                    LASSO = iris_explain_lasso_v2$model_r2)
                    #tree = iris_explain_tree_v2$model_r2)

# Only keep the unique rows
r2_v2 <- unique(r2_v2)

# Gather the dataset
r2_v2_gathered <- r2_v2 %>% gather(method, r2, 4:7)

# Reorder the levels of the case variable
r2_v2_gathered$case <- factor(r2_v2_gathered$case, 
                           levels(r2_v2_gathered$case)[c(2, 1, 6, 5, 3, 4)])

# Rename the levels of the case variable
levels(r2_v2_gathered$case) <- c("119 (virginica)", "113 (virginica)", 
                              "79 (versicolor)", "63 (versicolor)",
                              "29 (setosa)", "3 (setosa)")
```

\vspace{0.5cm}

The tile plots below depict the $R^2$ values from the ridge regression models for each case and feature selection method within each of the three species responses. With the species of setosa and virginica, the $R^2$ values are higher for the methods of highest and LASSO. For the species of versicolor, all of the $R^2$ values are very low and similar. It appears to be hard to find a linear relationship for versicolor. Unlike the $R^2$ values from the ridge regressions fit with the numerified perturbations, the $R^2$ values do no vary much between cases within a species and feature selection method. I am not sure why this is.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 14, fig.height = 4.5}
# Tile plot of feature selection method and case colored by r2 facetted by label
ggplot(r2_v2_gathered, aes(x = method, y = case)) +
  geom_tile(aes(fill = r2)) +
  facet_wrap(~label) +
  labs(x = "Feature Selection Method", y = "Case", fill = expression(R^2))
```

\vspace{0.5cm}

The box plots below make it clear that there is much less variation in $R^2$ values within a species and feature selection method. Thess plots also highlight that when the ridge regression models are fit to the perturbations, there is a clear difference in $R^2$ values between the methods of auto and forward and the methods of highest and LASSO for the species of setosa and virginica. The boxplots from the numerified pertrubations showed overlap between the feature selection methods.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 12 , fig.height = 3.5}
# Plot the R2 values in boxplots by the feature selection method
ggplot(r2_v2_gathered, aes(x = method, y = r2)) + 
  geom_boxplot() + 
  facet_wrap(~label) + 
  labs(x = "Feature Selection Method", y = expression(R^2)) +
  theme(text = element_text(size = 10))
```

\vspace{0.5cm}

I also decided to look at the $R^2$ values only from models fit to a case with the true species. The code below extracts these cases from the dataframe with all of the $R^2$ values.

\vspace{0.5cm}

```{r}
# Create a data frame with only the true species labels
r2_v2_true <- r2_v2 %>%
  group_by(case) %>%
  filter(label_prob == max(label_prob))

# Gather the dataset
r2_v2_true_gathered <- r2_v2_true %>% gather(method, r2, 4:7)

# Reorder the levels of the case variable
r2_v2_true_gathered$case <- factor(r2_v2_true_gathered$case, 
                           levels(r2_v2_true_gathered$case)[c(2, 1, 6, 5, 3, 4)])

# Rename the levels of the case variable
levels(r2_v2_true_gathered$case) <- c("119 (virginica)", "113 (virginica)", 
                                   "79 (versicolor)", "63 (versicolor)",
                                   "29 (setosa)", "3 (setosa)")
```

\vspace{0.5cm}

A tile plot and box plots of the $R^2$ values are shown below. The tile plot highlights the difference between the methods of auto and forward and the methods of highest and LASSO for the species of setosa and virginica. There is little difference between the method within the species of versicolor. The boxplots show more variation when the true cases from the three species are combined.

\vspace{0.5cm}

```{r echo = FALSE, fig.align = 'center', fig.width = 12, fig.height = 3.75}
tile_v2 <- ggplot(r2_v2_true_gathered, aes(x = method, y = case)) +
  geom_tile(aes(fill = r2)) + 
  labs(x = "Feature Selection Method", y = "Case", fill = expression(R^2))

# Plot the R2 values in boxplots by the feature selection method
box_v2 <- ggplot(r2_v2_true_gathered, aes(x = method, y = r2)) + 
  geom_boxplot() +
  labs(x = "Feature Selection Method", y = expression(R^2))

cowplot::plot_grid(tile_v2, box_v2)
```

### 2020-09-29 old-journals/iris data/journals/visualizing setosa predictions on a grid.R

@@ -1,0 +1,185 @@
+## Purpose: Visualize predictions from the iris data for setosa and 
+##          compare to LIME explanations
+## Created: 2017/11/15
+## Last Edited: 2018/01/14
+
+# Load libraries
+library(caret)
+library(lime)
+library(tidyverse)
+
+# Split up iris data set into training and testing data
+iris_test <- iris[1:5, 1:4]
+iris_train <- iris[-(1:5), 1:4]
+iris_lab <- iris[[5]][-(1:5)]
+
+## --------------------------------------------------------------------------------
+## Model with only 2 predictors
+## --------------------------------------------------------------------------------
+
+# Select only petal width and sepal width from the training data
+iris_train_subset <- iris_train %>%
+  select(Petal.Width, Sepal.Width)
+
+# Select only petal width and sepal width from the testing data
+iris_test_subset <- iris_test %>%
+  select(Petal.Width, Sepal.Width)
+
+# Fit a random forest to the subset data
+rf_model_subset <- train(iris_train_subset, iris_lab, method = 'rf')
+
+# Scatterplot of petal width versus sepal width colored by species with testing 
+# points in black
+ggplot(iris_train_subset, aes(x = Petal.Width, y = Sepal.Width)) + 
+  geom_point(aes(color = iris_lab)) +
+  geom_point(data = iris_test_subset, aes(x = Petal.Width, y = Sepal.Width))
+
+# Create a sequence of values for the x axis
+x_min <- min(iris_train$Petal.Width)
+x_max <- max(iris_train$Petal.Width)
+x_axis <- seq(from = x_min, to = x_max, by = 0.05)
+
+# Create a sequence of values for the y axis
+y_min <- min(iris_train$Sepal.Width)
+y_max <- max(iris_train$Sepal.Width)
+y_axis <- seq(from = y_min, to = y_max, by = 0.05)
+
+# Create a grid of the x and y axis values
+grid_subset <- expand.grid(x_axis, y_axis)
+
+# Rename the data set and change the variable names
+iris_grid_subset <- grid_subset %>%
+  rename(Petal.Width = Var1, 
+         Sepal.Width = Var2)
+
+# Make predictions for all of the values in the grid 
+predictions_subset <- predict(rf_model_subset, iris_grid_subset)
+
+# Add predictions to dataset
+iris_grid_subset$Pred <- predictions_subset
+
[…]

### 2020-09-29 old-journals/iris data/journals/visualizing versicolor and virginica predictions on a grid.R

@@ -1,0 +1,185 @@
+## Purpose: Visualize predictions from the iris data for versicolor and virginica and
+##          compare to LIME explanations
+## Created: 2018/01/14
+## Last Edited: 2018/01/14
+
+# Load libraries
+library(caret)
+library(lime)
+library(tidyverse)
+
+# Split up iris data set into training and testing data
+iris_test <- iris[c(58, 70, 106, 119, 124), 1:4]
+iris_train <- iris[-c(58, 70, 106, 119, 124), 1:4]
+iris_lab <- iris[[5]][-c(58, 70, 106, 119, 124)]
+
+## --------------------------------------------------------------------------------
+## Model with only 2 predictors
+## --------------------------------------------------------------------------------
+
+# Select only petal width and sepal width from the training data
+iris_train_subset <- iris_train %>%
+  select(Petal.Width, Sepal.Width)
+
+# Select only petal width and sepal width from the testing data
+iris_test_subset <- iris_test %>%
+  select(Petal.Width, Sepal.Width)
+
+# Fit a random forest to the subset data
+rf_model_subset <- train(iris_train_subset, iris_lab, method = 'rf')
+
+# Scatterplot of petal width versus sepal width colored by species with testing 
+# points in black
+ggplot(iris_train_subset, aes(x = Petal.Width, y = Sepal.Width)) + 
+  geom_point(aes(color = iris_lab)) +
+  geom_point(data = iris_test_subset, aes(x = Petal.Width, y = Sepal.Width))
+
+# Create a sequence of values for the x axis
+x_min <- min(iris_train$Petal.Width)
+x_max <- max(iris_train$Petal.Width)
+x_axis <- seq(from = x_min, to = x_max, by = 0.05)
+
+# Create a sequence of values for the y axis
+y_min <- min(iris_train$Sepal.Width)
+y_max <- max(iris_train$Sepal.Width)
+y_axis <- seq(from = y_min, to = y_max, by = 0.05)
+
+# Create a grid of the x and y axis values
+grid_subset <- expand.grid(x_axis, y_axis)
+
+# Rename the data set and change the variable names
+iris_grid_subset <- grid_subset %>%
+  rename(Petal.Width = Var1, 
+         Sepal.Width = Var2)
+
+# Make predictions for all of the values in the grid 
+predictions_subset <- predict(rf_model_subset, iris_grid_subset)
+
[…]

### 2020-09-29 old-journals/my functions/case_selector.R

@@ -1,0 +1,33 @@
+## Purpose: Function for selecting training data and explanations for 
+##          a specified test case
+## Created: 2018/02/13
+## Last Edited: 2018/02/13
+
+# Load necessary libraries
+library(tidyverse)
+
+# Function for selecting training data and explanations for a specific test case
+case_selector <- function(train, response, perturb, explain, test_case, 
+                          resp_category = NULL){
+  
+  # Select only the rows of features for the test case of interest
+  sub_explain <- explain %>% 
+    filter(case == test_case, label == resp_category)
+  
+  # Select variables chosen by LIME from the training data
+  sub_train <- train %>%
+    select(sub_explain$feature)
+  
+  # Add the response variable to the sub_train data frame
+  sub_train$response <- response
+  
+  # Subset the perturbations based on the testing point and grab selected 
+  # features, predictions, weights, and prediction probability
+  sub_perturb <- perturb %>%
+    filter(Test_Case == test_case) %>%
+    select(resp_category, sub_explain$feature, Prediction, Weight)
+  
+  # Put the sub training and perturbation data is a list to return
+  return(list(sub_train = sub_train, sub_perturb = sub_perturb))
+  
+}

### 2020-09-29 old-journals/my functions/my_explain.data.frame.R

@@ -1,0 +1,222 @@
+## Purpose: Add comments to the LIME function explain.data.frame and make
+##          adjustments to it so it outputs the perturbations, predictions
+##          for the perturbations based on the model, weights, and the
+##          numerified perturbations
+## Created: 2018/02/13
+## Last Edited: 2018/02/13
+
+# Load necessary libraries 
+library(assertthat)
+library(glmnet)
+
+# My adjusted explain.data.frame function with comments -- I started comments 
+# with "Added by KG" before each of the lines of code that I added to the
+# function
+my_explain.data.frame <- function(x, explainer, labels = NULL, n_labels = NULL,
+                               n_features, n_permutations = 5000,
+                               feature_select = 'auto', dist_fun = 'euclidean',
+                               kernel_width = NULL, rr_predictors = "numerified",
+                               ...) {
+  
+  # Make sure that the object explainer is of the type data_frame_explainer - 
+  # if not, then the function will stop
+  assert_that(is.data_frame_explainer(explainer))
+  
+  # Determine the type of the model that is contained within the explainer function
+  m_type <- model_type(explainer)
+  
+  # Determine the output type based on the type of the model in the explainer
+  o_type <- output_type(explainer)
+  
+  # If the model type is regression, then set n_lables to 1 and labels to NULL
+  # also if the model is a regression and labels or n_labels are not set to NULL, 
+  # then output a warning saying that labels and n_labels are ignored with 
+  # explaining regression models
+  if (m_type == 'regression') {
+    if (!is.null(labels) || !is.null(n_labels)) {
+      warning('"labels" and "n_labels" arguments are ignored when explaining 
+              regression models')
+    }
+    n_labels <- 1
+    labels <- NULL
+  }
+  
+  # If both labels and n_labels are specified or neither are specified, then 
+  # output a warning saying that we must choose between one or the other
+  assert_that(is.null(labels) + is.null(n_labels) == 1, 
+              msg = "You need to choose between labels and n_labels parameters.")
+  
+  # Stop function if n_features is not specified (as a numeric object) and 
+  # output a warning saying this is the case
+  assert_that(is.count(n_features))
+  
+  # Stop funtion if n_perumtations is not specified (as a numeric object) and 
+  # output a warning saying this is the case
+  assert_that(is.count(n_permutations))
+  
+  # If kernel width has not been specified, then compute it as the square root
[…]

### 2020-09-29 old-journals/my functions/plot_perturbs.R

@@ -1,0 +1,73 @@
+## Purpose: Function for plotting LIME perturbations
+## Created: 2018/02/13
+## Last Edited: 2018/03/01
+
+# Load necessary libraries
+library(tidyverse)
+library(wesanderson)
+library(cowplot)
+
+# Function for plotting the perturbations
+plot_perturbs <- function(train, response, perturb, explain, test_case, 
+                         resp_category = NULL, separate = TRUE){
+  
+  # Use the case selector function to obtain the training data (with response) and 
+  # perturbations that correspond to the test case of interest, the features 
+  # selected by LIME, and response category of interest
+  case_data <- case_selector(train, response, perturb, explain, test_case, resp_category)
+  
+  # Obtain names of two most important variables chosen by lime for the
+  # perturbation dataset
+  Var1 <- names(case_data$sub_perturb)[2]
+  Var2 <- names(case_data$sub_perturb)[3]
+  
+  # Plot of the perturbations for the two chosen variables colored by prediction
+  # with alpha value based on weight
+  perturb_plot <- ggplot(case_data$sub_perturb, aes_string(x = Var1, y = Var2)) + 
+    geom_point(aes(color = Prediction, alpha = Weight)) +
+    geom_point(data = case_data$sub_perturb[1,], 
+               aes_string(x = Var1, y = Var2, color = "Prediction"), 
+               size = 3, fill = "black", pch = 21) +
+    scale_color_manual(values = wes_palette("Darjeeling")) +
+    scale_fill_manual(values = wes_palette("Darjeeling")) +
+    labs(x = Var1, y = Var2) +
+    theme_bw()
+  
+  # Plot of raw data for the two chosen variables colored by response
+  raw_plot <- ggplot(data = case_data$sub_train, aes_string(x = Var1, y = Var2)) +
+    geom_point(aes(fill = response), color = "black", size = 3, pch = 21) + 
+    geom_point(data = case_data$sub_perturb[1,], 
+               aes_string(x = Var1, y = Var2, color = "Prediction"), 
+               size = 3, fill = "black", pch = 21) +
+    scale_color_manual(values = wes_palette("Darjeeling")) +
+    scale_fill_manual(values = wes_palette("Darjeeling")) +
+    labs(x = Var1, y = Var2) +
+    theme_bw()
+  
+  # Plot of perturbations and raw data for the two chosen variables colored
+  # by prediction and response, respectively
[…]

### 2020-09-29 old-journals/my functions/plot_probs.R

@@ -1,0 +1,51 @@
+## Purpose: Function for plotting probabilities vs. LIME perturbations
+## Created: 2018/02/18
+## Last Edited: 2018/02/28
+
+# Load necessary libraries
+library(tidyverse)
+library(wesanderson)
+library(cowplot)
+
+# Function for plotting the probabilities
+plot_probs <- function(train, response, perturb, explain, test_case, resp_category = NULL){
+  
+  # Use the case selector function to obtain the training data (with response) and 
+  # perturbations that correspond to the test case of interest, the features 
+  # selected by LIME, and response category of interest
+  case_data <- case_selector(train, response, perturb, explain, 
+                             test_case, resp_category)
+  
+  # Obtain names of the response variable and the wo most important variables chosen by 
+  # LIME for the perturbation dataset
+  Response <- names(case_data$sub_perturb)[1]
+  ResponseSafe <- paste0("`",Response,"`")
+  Var1 <- names(case_data$sub_perturb)[2]
+  Var2 <- names(case_data$sub_perturb)[3]
+  
+  # Plot of probabilities vs feature 1 perturbations colored by prediction
+  feature1 <- ggplot(case_data$sub_perturb, aes_string(x = Var1, y = ResponseSafe)) +
+    geom_point(aes(alpha = Weight, color = Prediction)) +
+    geom_point(data = case_data$sub_perturb[1,], 
+                 aes_string(x = Var1, y = ResponseSafe, color = "Prediction"), 
+                 size = 3, fill = "black", pch = 21) +
+    scale_fill_manual(values = wes_palette("Darjeeling")) +
+    scale_color_manual(values = wes_palette("Darjeeling")) + 
+    labs(x = Var1, y = Response) +
+    theme_bw()
+  
+  # Plot of probabilities vs feature 2 perturbations colored by prediction
+  feature2 <- ggplot(case_data$sub_perturb, aes_string(x = Var2, y = ResponseSafe)) +
+    geom_point(aes(color = Prediction, alpha = Weight)) +
+    geom_point(data = case_data$sub_perturb[1,], 
+               aes_string(x = Var2, y = ResponseSafe, color = "Prediction"), 
+               size = 3, fill = "black", pch = 21) +
+    scale_fill_manual(values = wes_palette("Darjeeling")) +
+    scale_color_manual(values = wes_palette("Darjeeling")) + 
+    labs(x = Var2, y = Response) +
+    theme_bw()
+  
[…]

### 2020-09-29 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
removed cache and re-knit

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, 
+knitr::opts_chunk$set(
+  echo = TRUE,
   message = FALSE,
@@
   eval = TRUE,
-                      cache = TRUE)
+  cache = FALSE
+)
 ```
@@
 
-When I look at the dimensions of my training data now and the number of predictions from `rtrees`, then agree now!
+When I look at the dimensions of my training data now and the number of predictions from `rtrees`, they agree now!
 

### 2020-09-29 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
updated and reknit

@@
 We even tried some new sampling methods to improve the algorithm.
-They mde a bit of improvement, but the improvements could be much better.
-This paper could discuss isusses we found with the current LIME agorithm, describe our proposed approaches, and compare the results.
+They made a bit of improvement, but the improvements could be much better.
+This paper could discuss isusses we found with the current LIME algorithm, describe our proposed approaches, and compare the results.
 
@@
 - I'm nervous about the fact that the results can change due to the permutations.
-Is there a way to check for consistencey?
+Is there a way to check for consistency?
 Does this only happen if you have correlated variables, or can it also happen with uncorrelated variables?
@@
 
-- LIME is kind of like a jacknife technique
+- LIME is kind of like a jackknife technique

### 2020-09-29 journals/08-logistic_regression/08-logistic_regression.Rmd
small updates

@@
   eval = TRUE,
-                      cache = TRUE, 
-                      fig.width = 12)
+  cache = FALSE,
+  fig.width = 12
+)
 ```
@@
   p1 <- lime::plot_features(exp$explain[id:(id+1),])
-  p2 <- eoi_plot(exp$explain[id:(id+1),])
+  p2 <- limeaid::plot_explain_scatter(exp$explain[id:(id+1),])
   plot_grid(p1, p2)

### 2020-09-29 journals/10-lime_hamby_variability/10-lime_hamby_variability.Rmd
added journal for comparing lime explanations across models

---
title: "LIME Variability Across Hamby Data and Model"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  cache = FALSE
)
```

We have finally identified the data that was most likely used to train `rtrees` (`CCFs_withlands`). This data is different from the one we previously believed to be the one that trained `rtrees` (`hamby_comparisons`; previously called `features-hamby173and252.csv`). It is of interest to keep a record of how the LIME explanations on a testing dataset (Hamby 224 sets 1 and 11) vary across the various training datasets and models. This journal applies LIME to various versions of a random forest trained on the Hamby bullet signature comparisons data.

```{r}
library(dplyr)
library(forcats)
library(ggplot2)
library(gretchenalbrecht)
library(limeaid)
```

# Data

Load the filtered version of the `hamby_comparisons` data: 
  - LEAs with tank rash in Eric's paper filtered out
  - Contains same number of rows as `rtrees`
  - Prepared in journal [09-identifying-rtrees-training-data.Rmd](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)

```{r}
hamby_comparisons_filtered <- read.csv("../../../data/hamby_comparisons_filtered.csv")
```

Load the cleaned version of the `CCFs_withlands` data (prepared in [09-identifying-rtrees-training-data.Rmd](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)):

```{r}
CCFs_withlands_clean <- read.csv("../../../data/CCFs_withlands_clean.csv")
```

Load the bullet testing data using in the LIME diagnostics paper (prepared in https://github.com/goodekat/LIME-diagnostics-paper/blob/master/code/01-raw-file-compression.Rmd):

```{r}
bullet_test <- read.csv("../../../diagnostics-paper/data/bullet-test.csv")
```

Obtain the features used to train `rtrees` for use throughout this journal:

```{r}
rtrees_features <- rownames(bulletxtrctr::rtrees$importance)
```

# Apply LIME

## rtrees with hamby_comparisons

Wrong training data for `rtrees`

```{r}
# Create a file path
file_rtrees_hc_explanations = "../../../data/rtrees_explanations_hc.rds"

# Implement and save or load LIME explanations
if (!file.exists(file_rtrees_hc_explanations)) {

  # Apply LIME
  rtrees_hc_explanations <- apply_lime(
    train = hamby_comparisons_filtered %>% select(all_of(rtrees_features)),
    test = bullet_test %>% select(all_of(rtrees_features)),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)

  # Save the explanations
  saveRDS(object = rtrees_hc_explanations, file = file_rtrees_hc_explanations)

} else {

  # Load the explanations
  rtrees_hc_explanations <- readRDS(file_rtrees_hc_explanations)

}
```

## rtrees with CCFs_withlands

Probably the training data for `rtrees`

```{r}
# Create a file path
file_rtrees_ccfwl_explanations = "../../../data/rtrees_explanations_ccfwl.rds"

# Implement and save or load LIME explanations
if (!file.exists(file_rtrees_ccfwl_explanations)) {

  # Apply LIME
  rtrees_ccfwl_explanations <- apply_lime(
    train = CCFs_withlands_clean %>% select(all_of(rtrees_features)),
    test = bullet_test %>% select(all_of(rtrees_features)),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)

  # Save the explanations
  saveRDS(object = rtrees_ccfwl_explanations, file = file_rtrees_ccfwl_explanations)

} else {

  # Load the explanations
  rtrees_ccfwl_explanations <- readRDS(file_rtrees_ccfwl_explanations)

}
```

## New RF with CCFs_withlands

Using the data that was probably used to train `rtrees` to train a new random forest (see the [Rnw of the LIME diagnostics paper](https://github.com/goodekat/LIME-diagnostics-paper/blob/master/paper.Rnw) for the code):

```{r}
bullet_explain <- readRDS("../../../diagnostics-paper/data/bullet-explain.rds")
```

# Feature Heatmaps

## rtrees with hamby_comparisons

```{r fig.width = 12, fig.height = 12}
# Create a feature heatmap
plot_feature_heatmap(
  rtrees_hc_explanations$explain %>%
    mutate(
      label = as.factor(label),
      feature = fct_recode(
        feature,
        "Rough Correlation" = "rough_cor",
        "Consecutively Matching Striae" = "cms",
        "Distance" = "D",
        "Matches" = "matches",
        "Mismatches" = "mismatches",
        "Non-Consecutively Matching Striae" = "non_cms",
        "Cross Correlation Function" = "ccf",
        "Sum of Peaks" = "sum_peaks",
        "Distance Standard Deviation" = "sd_D"
      )
    ),
  facet_var = bullet_test %>%
    mutate(samesource = fct_recode(
      factor(samesource),
      "Match" = "TRUE",
      "Non-Match" = "FALSE"
    )) %>%
    pull(samesource),
  order_method = "PCA"
) +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  scale_color_gretchenalbrecht(palette = "last_rays",
                               discrete = TRUE,
                               reverse = TRUE) +
  theme_bw() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_rect(color = "white", fill = "white"),
    strip.text.y.right = element_text(angle = 0),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(nrow = 3)) +
  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
```

## rtrees with CCFs_withlands

```{r fig.width = 12, fig.height = 12}
# Create a feature heatmap
plot_feature_heatmap(
  rtrees_ccfwl_explanations$explain %>%
    mutate(
      label = as.factor(label),
      feature = fct_recode(
        feature,
        "Rough Correlation" = "rough_cor",
        "Consecutively Matching Striae" = "cms",
        "Distance" = "D",
        "Matches" = "matches",
        "Mismatches" = "mismatches",
        "Non-Consecutively Matching Striae" = "non_cms",
        "Cross Correlation Function" = "ccf",
        "Sum of Peaks" = "sum_peaks",
        "Distance Standard Deviation" = "sd_D"
      )
    ),
  facet_var = bullet_test %>%
    mutate(samesource = fct_recode(
      factor(samesource),
      "Match" = "TRUE",
      "Non-Match" = "FALSE"
    )) %>%
    pull(samesource),
  order_method = "PCA"
) +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  scale_color_gretchenalbrecht(palette = "last_rays",
                               discrete = TRUE,
                               reverse = TRUE) +
  theme_bw() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_rect(color = "white", fill = "white"),
    strip.text.y.right = element_text(angle = 0),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(nrow = 3)) +
  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
```

## New RF with CCFs_withlands

```{r fig.width = 12, fig.height = 12}
# Create a feature heatmap
plot_feature_heatmap(
  bullet_explain %>%
    mutate(
      label = as.factor(label),
      feature = fct_recode(
        feature,
        "Rough Correlation" = "rough_cor",
        "Consecutively Matching Striae" = "cms",
        "Distance" = "D",
        "Matches" = "matches",
        "Mismatches" = "mismatches",
        "Non-Consecutively Matching Striae" = "non_cms",
        "Cross Correlation Function" = "ccf",
        "Sum of Peaks" = "sum_peaks",
        "Distance Standard Deviation" = "sd_D"
      )
    ),
  facet_var = bullet_test %>%
    mutate(samesource = fct_recode(
      factor(samesource),
      "Match" = "TRUE",
      "Non-Match" = "FALSE"
    )) %>%
    pull(samesource),
  order_method = "PCA"
) +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  scale_color_gretchenalbrecht(palette = "last_rays",
                               discrete = TRUE,
                               reverse = TRUE) +
  theme_bw() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_rect(color = "white", fill = "white"),
    strip.text.y.right = element_text(angle = 0),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(nrow = 3)) +
  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
```

# Assessment Metric Plots

## rtrees with hamby_comparisons

```{r}
plot_metrics(
  rtrees_hc_explanations$explain %>% mutate(label = as.factor(label)),
  add_lines = TRUE,
  line_alpha = 0.75
) +
  theme_bw() +
  theme(
    strip.background = element_rect(color = "white", fill = "white"),
    strip.placement = "outside"
  )
```

## rtrees with CCFs_withlands

```{r}
plot_metrics(
  rtrees_ccfwl_explanations$explain %>% mutate(label = as.factor(label)),
  add_lines = TRUE,
  line_alpha = 0.75
) +
  theme_bw() +
  theme(
    strip.background = element_rect(color = "white", fill = "white"),
    strip.placement = "outside"
  )
```

## New RF with CCFs_withlands

```{r}
plot_metrics(
  bullet_explain %>% mutate(label = as.factor(label)),
  add_lines = TRUE,
  line_alpha = 0.75
) +
  theme_bw() +
  theme(
    strip.background = element_rect(color = "white", fill = "white"),
    strip.placement = "outside"
  )
```

# Session Info

```{r}
sessionInfo()
```

### 2020-09-29 README.Rmd
fixed link

@@
 8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
-9. [Identifying `rtrees` Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
-10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-LIME_hamby_variability.html)
+9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
+10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)
 

### 2020-09-29 journals/09-identifying_rtrees_training_rdata/09-identifying_rtrees_training_data.Rmd
renamed files to match other journals

--- 2020-09-29 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
@@
   cache = FALSE, 
-  dpi = 300
+  dpi = 500
 )
@@
 
-```{r}
-length(unique(c(CCFs_withlands$land_id1, CCFs_withlands$land_id2)))
+Save the cleaned data:
+
+```{r}
+write.csv(x = hamby_comparisons, file = "../../../data/hamby_comparisons_clean.csv", row.names = FALSE)
+write.csv(x = CCFs_withlands, file = "../../../data/CCFs_withlands_clean.csv", row.names = FALSE)
 ```
@@
 
+Save the cleaned and filtered data:
+
+```{r}
+write.csv(x = hamby_comparisons_filtered , file = "../../../data/hamby_comparisons_filtered.csv", row.names = FALSE)
+```
+
 While it is possible to use `hamby_comparisons` to get to the same number of observations as `rtrees`, it is only a guess as to how the bullets were removed.
@@
 rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
-hc_pred = predict(bulletxtrctr::rtrees, hamby_comparisons %>% select(rtrees_features), type = "prob")[,2]
-ccfwl_pred = predict(bulletxtrctr::rtrees, CCFs_withlands %>% select(rtrees_features), type = "prob")[,2]
+hc_pred = predict(bulletxtrctr::rtrees, hamby_comparisons %>% select(all_of(rtrees_features)), type = "prob")[,2]
+ccfwl_pred = predict(bulletxtrctr::rtrees, CCFs_withlands %>% select(all_of(rtrees_features)), type = "prob")[,2]
 
@@
 
-```{r fig.width = 12, fig.height = 5}
+```{r fig.width = 15, fig.height = 8}
 plot_grid(
@@
          y = "rtrees2 votes",
-         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20140501"),
+         title = "Retrained RF on Hamby comparison data \nversus rtrees; Seed 20140501"),
 
@@
          y = "rtrees3 votes",
-         title = "Retrained RF on Hamby comparison data versus rtrees; Seed 20170222"),
+         title = "Retrained RF on Hamby comparison data \nversus rtrees; Seed 20170222"),
 
@@
          y = "rtrees2 votes",
-         title = "Both retrained RFs on Hamby comparison data"),
+         title = "Both retrained RFs on Hamby \ncomparison data"),
 
@@
          y = "rtrees4 votes",
-         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20140501"),
+         title = "Retrained RF on CCFs with lands data \nversus rtrees; Seed 20140501"),
 
@@
          y = "rtrees5 votes",
-         title = "Retrained RF on CCFs with lands data versus rtrees; Seed 20170222"),
+         title = "Retrained RF on CCFs with lands data \nversus rtrees; Seed 20170222"),
 
@@
          y = "rtrees5 votes",
-         title = "Both retrained RFs on CCFs with lands data"),
+         title = "Both retrained RFs on CCFs with \nlands data"),
   nrow = 2
@@
 hamby_comparison_importance <-
-  map_df(.x = rfs_hamby_comparison, .f = extract_importance, .id = "rf_model_id")
+  map_df(.x = rfs_hamby_comparison, .f = extract_importance, .id = "rf_model_id") %>%
+  mutate(scenario = "Hamby Comparisons")
 CCFs_withlands_importance <-
-  map_df(.x = rfs_CCFs_withlands, .f = extract_importance, .id = "rf_model_id")
+  map_df(.x = rfs_CCFs_withlands, .f = extract_importance, .id = "rf_model_id") %>%
+  mutate(scenario = "CCFs with lands")
 ```
@@
   mutate(rank = 1:n(),
-         rf_model_id = "rtrees") %>%
+         rf_model_id = "rtrees", 
+         scenario = "rtrees") %>%
   rename("importance" = "MeanDecreaseGini") %>%
-  select(rf_model_id, features, importance, rank)
+  select(rf_model_id, features, importance, rank, scenario)
 ```
@@
 
-Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true):
+Histograms of the class errors (true and false) show that the rtrees class errors are in the tails of the distributions of the class errors from the models trained on the `hamby_comparisons` data  but closer to the center of the class error distributions from the models trained on the `CCFs_withlands` data:
 
@@
   ggplot(aes(x = class_error_TRUE)) +
-  geom_histogram() +
+  geom_histogram(bins = 20) +
   geom_vline(data = rtrees_values,
@@
   ggplot(aes(x = class_error_FALSE)) +
-  geom_histogram() +
+  geom_histogram(bins = 20) +
   geom_vline(data = rtrees_values,
@@
 
-Heatmap depicting feature importance across models:
-
-```{r fig.width = 12, fig.height = 5}
-plot_grid(
-  bind_rows(rtrees_importance, hamby_comparison_importance) %>%
+Heatmap depicting feature importance across models (note that `rtrees` importance ranks for `D` and `non_cms` are more similar to random forests trained using `CCFs_withlands` than `hamby_comparisons`):
+
+```{r fig.width = 15, fig.height = 5}
+bind_rows(rtrees_importance, hamby_comparison_importance, CCFs_withlands_importance) %>%
     mutate(
+      scenario = factor(scenario, levels = c("rtrees", "Hamby Comparisons", "CCFs with lands")),
       rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
@@
     geom_tile() +
+    facet_grid(. ~ scenario, scales = "free_x") +
     scale_fill_brewer(palette = "RdYlBu") + 
@@
       y = "Feature", 
-      title = "Comparing rtrees importance to random forests fit using Hamby comparisons data"
-    ),
-
-  bind_rows(rtrees_importance, CCFs_withlands_importance) %>%
-    mutate(
-      rf_model_id = factor(rf_model_id, levels = c("rtrees", 1:length(seeds))),
-      rank = factor(rank, levels = 1:9),
-      features = factor(features, levels = rev(rtrees_importance$features))
-    ) %>%
-    ggplot(aes(x = rf_model_id, y = features, fill = rank)) +
-    geom_tile() +
-    scale_fill_brewer(palette = "RdYlBu") + 
-    theme_bw() +
-    labs(
-      x = "Random Forest Model", 
-      y = "Feature", 
-      title = "Comparing rtrees importance to random forests fit using CCFs with lands data"
-    )
-)
-```
-
-```{r fig.width = 12, fig.height = 5}
+      title = "Comparing Feature Importance to rtrees"
+    )
+```
+
+Plots of features versus importance ranks (importance ranks vary more in the middle of the features for the models trained using `hamby_comparisons` and near the tail end of the features for the models trained using `CCFs_withlands`):
+
+```{r fig.width = 15, fig.height = 5}
 plot_grid(
@@
     ) %>%
-    ggplot(aes(x = rank, y = features, group = rf_model_id, color = rtrees_ind)) +
-    geom_point(alpha = 0.5, shape = 1) + 
-    geom_line(alpha = 0.5) +
-    scale_color_manual(values = c("grey50", "blue")) +
+    arrange(desc(rf_model_id)) %>%
+    ggplot(
+      aes(
+        x = rank,
+        y = features,
+        group = rf_model_id,
+        color = rtrees_ind,
+        size = rtrees_ind,
+        alpha = rtrees_ind
+      )
+    ) +
+    geom_line() +
+    scale_color_manual(values = c("black", "purple")) +
     theme_bw() +
@@
       y = "Feature", 
-      title = "Comparing rtrees importance to random forests fit using Hamby comparisons data"
+      title = "Comparing rtrees importance to random forests fit \nusing Hamby comparisons data"
     ), 
@@
     ) %>%
-    ggplot(aes(x = rank, y = features, group = rf_model_id, color = rtrees_ind)) +
-    geom_point(alpha = 0.5, shape = 1) + 
-    geom_line(alpha = 0.5) +
-    scale_color_manual(values = c("grey50", "blue")) +
+    arrange(desc(rf_model_id)) %>%
+    ggplot(
+      aes(
+        x = rank,
+        y = features,
+        group = rf_model_id,
+        color = rtrees_ind,
+        size = rtrees_ind,
+        alpha = rtrees_ind
+      )
+    ) +
+    geom_line() +
+    scale_color_manual(values = c("black", "purple")) +
     theme_bw() +
-    labs(
-      x = "Random Forest Model", 
+    labs(x = "Random Forest Model",
          y = "Feature",
-      title = "Comparing rtrees importance to random forests fit using CCFs with lands data"
-    )
-)
-```
-
-# LIME Explanation Comparison
+         title = "Comparing rtrees importance to random forests fit \nusing CCFs with lands data")
+)
+```
 

### 2020-09-29 README.Rmd
changed link to match file name

@@
 8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
-9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
+9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.html)
 10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)

### 2020-09-29 journals/05-iris_comparison/05-iris_comparison.Rmd
updated this journal (old code didn't run)

@@
 library(caret)
+library(e1071)
 library(furrr)
@@
 library(gretchenalbrecht)
-library(lime)
+library(limeaid)
 
@@
 ```{r}
-# Apply the run_lime function if the lime results file does not already exist
-if(!file.exists("./data/iris_lime_inputs.rds")) {
+# Create a file path
+file_iris_explanations = "../../../data/iris_explanations.rds"
 
-  # Specify the input options to use with lime
-  iris_lime_inputs <- list(bin_continuous = c(rep(TRUE, 15), 
-                                                  rep(FALSE, 2)),
-                               quantile_bins = c(rep(TRUE, 5), 
-                                                 rep(FALSE, 5), 
-                                                 rep(TRUE, 7)),
-                               nbins = c(rep(2:6, 3), 
-                                         rep(4, 2)),
-                               use_density = c(rep(TRUE, 15), TRUE, FALSE),
-                               bin_method = c(rep("quantile_bins", 5),
-                                              rep("equally_spaced", 5),
-                                              rep("tree", 5),
-                                              rep("quantile_bins", 2)),
-                               response = c(rep(NA, 10), 
-                                            rep("Species", 5), 
-                                            rep(NA, 2)))
+# Implement and save or load LIME explanations
+if (!file.exists(file_iris_explanations)) {
 
-  # Tell R to run the upcoming code in parallel
-  plan(multiprocess)
+  # Apply LIME
+  iris_explanations <-
+    apply_lime(
+      train = iris_train %>% select(names(iris %>% select(-Species))),
+      test = iris_test %>% select(-case, -Species),
+      model = iris_model,
+      label = "virginica",
+      n_features = 3,
+      sim_method = c('quantile_bins', 'equal_bins'),
+      nbins = 2:6,
+      feature_select = "auto",
+      dist_fun = "gower",
+      kernel_width = NULL,
+      gower_pow = c(0.5, 1, 10),
+      return_perms = FALSE,
+      all_fs = FALSE,
+      seed = 20190914
+    )
 
-  # Apply lime to the full training data with the specified input options
-  iris_lime_explain <- future_pmap(.l = iris_lime_inputs,
-             .f = run_lime, # run_lime is one of my helper functions
-             features = names(iris %>% select(-Species)),
-             train = iris_train,
-             test = iris_test %>% select(-case, -Species),
-             rfmodel = iris_model,
-             label = "virginica",
-             nfeatures = 3,
-             seed = TRUE)
-
-  # Separate the lime and explain function results from the full data
-  iris_lime <- map(iris_lime_explain, function(list) list$lime)
-  iris_explain <- map_df(iris_lime_explain, function(list) list$explain)
-
-  # Name the items in the lime list
-  names(iris_lime) <- map_chr(1:17, function(case) 
-      sprintf("case: bin_continuous = %s, quantile_bins = %s, nbins = %0.f, use_density = %s, bin_method = %s, response = %s",
-              iris_lime_inputs$bin_continuous[case],
-              iris_lime_inputs$quantile_bins[case],
-              iris_lime_inputs$nbins[case],
-              iris_lime_inputs$use_density[case],
-              iris_lime_inputs$bin_method[case],
-              iris_lime_inputs$response[case]))
-
-  # Turn the lime input options into a dataframe before saving it
-  iris_lime_inputs <- iris_lime_inputs %>%
-    unlist() %>%
-    matrix(ncol = length(iris_lime_inputs), 
-           dimnames = list(NULL, names(iris_lime_inputs))) %>%
-    as.data.frame() %>%
-    mutate(case = 1:length(iris_lime_inputs$quantile_bins)) %>%
-    select(case, bin_continuous:response)
-
-  # Save the lime objects
-  saveRDS(iris_lime_inputs, "./data/iris_lime_inputs.rds")
-  saveRDS(iris_lime, "./data/iris_lime.rds")
-  saveRDS(iris_explain, "./data/iris_explain.rds")
+  # Save the explanations
+  saveRDS(object = iris_explanations, file = file_iris_explanations)
 
@@
 
-  # Load in the lime objects
-  iris_lime_inputs <- readRDS("./data/iris_lime_inputs.rds")
-  iris_lime <- readRDS("./data/iris_lime.rds")
-  iris_explain <- readRDS("./data/iris_explain.rds")
-
-}
-```
-
-The explanations from LIME are joined with the testing data.
-Additionally, the random forest scores for the probability that a case is species virginica are added to the dataset.
-This is the only species that will be considered (for now at least).
-
-```{r}
-# Create the test_explain combined data if the file does not already exist
-if(!file.exists("./data/iris_test_explain.rds")) {
-
-  # Join the data and the explanations and edit and add additional variables
-  iris_test_explain <- iris_test %>%
-    mutate(case = as.character(case),
-           rfscore = predict(iris_model, iris_test, type = "prob") %>% pull(virginica)) %>%
-    full_join(iris_explain, by = "case") %>%
-    mutate(case = factor(case),
-           feature = factor(feature),
-           nbins = factor(nbins)) %>%
-    arrange(nbins) %>%
-    mutate(nbins = as.numeric(as.character(nbins)),
-           situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
-                              sprintf("%.0f quantile", nbins),
-                              ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
-                                     sprintf("%.0f equally spaced", nbins),
-                                     ifelse(bin_continuous == TRUE & bin_method == "tree" &
-                                              response == "Species",
-                                            sprintf("%.0f tree", nbins),
-                                            ifelse(bin_continuous == FALSE & 
-                                                   use_density == TRUE, 
-                                                   "kernel density", 
-                                                   "normal approximation")))) %>%
-             fct_relevel("2 quantile", "3 quantile", "4 quantile",
-                         "5 quantile", "6 quantile", "2 equally spaced",
-                         "3 equally spaced", "4 equally spaced",
-                         "5 equally spaced", "6 equally spaced",
-                         "2 tree", "3 tree",
-                         "4 tree", "5 tree",
-                         "6 tree")) %>%
-    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
-                                  bin_continuous == TRUE,
-                                  "quantile",
-                                  ifelse(bin_method == "equally_spaced" & 
-                                         bin_continuous == TRUE,
-                                         "equally spaced", 
-                                         ifelse(bin_method == "tree" & 
-                                                bin_continuous == TRUE & 
-                                                response == "Species",
-                                                "tree", 
-                                                ifelse(bin_continuous == FALSE & 
-                                                       use_density == TRUE, 
-                                                       "kernel density", 
-                                                       "normal approximation"))))) %>%
-    mutate(bin_situation = factor(bin_situation))
-
-  # Save the combined test and explain data
-  saveRDS(iris_test_explain, "./data/iris_test_explain.rds")
-
-} else {
-
-  # Load in the data
-  iris_test_explain <- readRDS("./data/iris_test_explain.rds")
-
-}
-```
-
-Summaries of the explanations are computed and saved in a dataset.
-
-```{r}
-# Create the lime comparison data if the file does not already exist
-if(!file.exists("./data/iris_lime_comparisons.rds")) {
-
-  # Create a data frame with the interesting information relating to the different
-  # evaluations of lime and compute the difference and mean between the rf and rr
-  # model predictions
-  iris_lime_comparisons <- iris_test_explain %>%
-    select(-data, -prediction) %>%
-    group_by(case, bin_continuous, quantile_bins, nbins, use_density, bin_method) %>%
-    slice(1) %>%
-    ungroup() %>%
-    mutate(diff = rfscore - model_prediction,
-           mean = (rfscore + model_prediction) / 2)
-
-  # Save the lime comparison data frame
-  saveRDS(iris_lime_comparisons, "./data/iris_lime_comparisons.rds")
-
-} else {
-
-  # Load in the lime comparison data frame
-  iris_lime_comparisons <- readRDS("./data/iris_lime_comparisons.rds")
+  # Load the explanations
+  iris_explanations <- readRDS(file_iris_explanations)
 
@@
 
-The MSEs and average $R^2$ values are computed for each of the estimation methods.
+## Feature Heatmap
 
 ```{r}
-# Summarizing lime results
-iris_lime_results <- iris_lime_comparisons %>%
-  group_by(situation, bin_situation, bin_continuous, quantile_bins, nbins, use_density, 
-           bin_method, response) %>%
-  summarise(mse = (sum(diff^2)) / length(diff),
-            ave_r2 = mean(model_r2)) %>%
-  ungroup()
+plot_feature_heatmap(iris_explanations$explain, order_method = "PCA") +
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  scale_color_gretchenalbrecht(palette = "last_rays", discrete = TRUE, reverse = TRUE) +
+  theme_bw() +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.text.y.right = element_text(angle = 0),
+    legend.position = "bottom"
+  ) +
+  guides(fill = guide_legend(nrow = 3)) +
+  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
 ```
 
-A plot of the MSEs is shown below.
+## Assessment Metric Plot
 
 ```{r}
-# Plot of MSEs
-iris_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = mse, color = bin_situation)) +
-  geom_point() + 
-  facet_grid(~ bins, scales = "free_x", space = "free_x") + 
+plot_metrics(
+  iris_explanations$explain,
+  add_lines = TRUE,
+  line_alpha = 0.75
+) +
   theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-        legend.position = "none") + 
-  labs(x = "Bin Type", y = "MSE", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-A plot of the $R^2$ values is shown below. The $R^2$ values are much higher than
-
-```{r}
-# Plot of R^2s
-iris_lime_results %>%
-  mutate(bins = ifelse(nbins == 4 & bin_continuous == FALSE, "other", nbins)) %>%
-  ggplot(aes(x = bin_situation, y = ave_r2, color = bin_situation)) +
-  geom_point() + 
-  facet_grid( ~ bins, scales = "free_x", space = "free_x") + 
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none") + 
-  labs(x = "Bin Type", y = "Average R2", color = "") + 
-  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
-```
-
-The features chosen are sorted below.
-
-```{r}
-# Creates a dataset that creates columns of the chosen features by lime from first to third
-iris_chosen_features <- iris_test_explain %>%
-  filter(!(bin_situation %in% c("kernel density", "normal approximation"))) %>%
-  filter(!is.na(rfscore)) %>%
-  select(situation, bin_situation, nbins, case, feature, feature_weight) %>%
-  mutate(feature_weight_abs = abs(feature_weight)) %>%
-  arrange(situation, case, desc(feature_weight_abs)) %>%
-  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
-  select(-feature_weight, -feature_weight_abs) %>%
-  spread(explainer, feature)
-```
-
-A plot of Fleiss's kappa values is shown below.
-
-```{r}
-# Computes and plots the values of kappa
-iris_chosen_features %>%
-  ungroup() %>%
-  select(-situation) %>%
-  gather(key = chosen, value = feature, first:third) %>%
-  spread(nbins, feature) %>%
-  select(-case) %>%
-  rename(bins2 = "2", bins3 = "3", bins4 = "4", bins5 = "5", bins6 = "6") %>%
-  group_by(bin_situation, chosen) %>%
-  summarise(kappa = 
-              irr::kappam.fleiss(matrix(c(bins2, bins3, bins4, bins5, bins6), 
-                                        ncol = 5))$value) %>%
-  arrange(chosen, bin_situation) %>%
-  ggplot(aes(x = bin_situation, y = kappa, color = chosen, group = chosen)) +
-  geom_point() + 
-  geom_line() +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-  scale_color_gretchenalbrecht(palette = "pink_cloud", discrete = TRUE) +
-  labs(x = "Bin Type", y = "Kappa", color = "Feature")
-```
-
-The following plots show the features chosen by each estimation method for all of the cases in the test dataset.
-The plots are created the by order the features are chosen (from first to third).
-I am not seeing the same patterns that I saw with the bullet data and `rtrees`.
-Heike pointed out that you really do not need a complex model to explain this situation.
-The iris data should be easy to predict.
-Maybe I could switch to using the problem points in the iris data for the test data and see how LIME performs with these.
-
-```{r}
-# Plots the top feature for each case for each bin situation
-iris_chosen_features %>%
-  group_by(bin_situation, case) %>%
-  mutate(nlevels = length(levels(factor(first)))) %>%
-  ungroup() %>%
-  arrange(bin_situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
-  ggplot(aes(x = nbins, y = order, fill = first)) + 
-  geom_tile() + 
-  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "First Feature")
-
-# Plots the second feature for each case for each bin situation
-iris_chosen_features %>%
-  group_by(bin_situation, case) %>%
-  mutate(nlevels = length(levels(factor(second)))) %>%
-  ungroup() %>%
-  arrange(bin_situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
-  ggplot(aes(x = nbins, y = order, fill = second)) + 
-  geom_tile() + 
-  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Second Feature")
-
-# Plots the third feature for each case for each bin situation
-iris_chosen_features %>%
-  group_by(bin_situation, case) %>%
-  mutate(nlevels = length(levels(factor(third)))) %>%
-  ungroup() %>%
-  arrange(bin_situation, desc(nlevels), case) %>%
-  mutate(order = rep(rep(1:length(unique(case)), each = 5, 3))) %>%
-  ggplot(aes(x = nbins, y = order, fill = third)) + 
-  geom_tile() + 
-  facet_grid( ~ bin_situation, scales = "free", space = "free_y") + 
-  theme_bw() + 
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) + 
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
-  labs(x = "Number of Bins", y = "Test Case", fill = "Feature", title = "Third Feature")
+  theme(
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.placement = "outside"
+  )
 ```

### 2020-09-30 README.Rmd
trying out a different image
updated figure and contents in repo

@@
 
-# LIME Research <img align="right" height="200" src="./figures/lime.png">
+# LIME Research <img align="right" height="200" src="https://i.pinimg.com/originals/de/18/33/de18338e3313edd97d8156d987244e74.jpg">
 
@@
 
-**code**
+[**code**](code/)
 
-This folder is a place for storing code that is used throughout the project:
+Place for storing R code used in the research journals:
 
-- `app.R`: code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
-- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well
+- [app.R](code/app.R): code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
+- [helper_functions.R](code/helper_functions.R): R script with functions that I use in the journals
 
-**figures**
+[**figures**](figures)
 
-This folder contains static images:
+Contains static images:
 
-- `lime.png`: fun picture of a lime to use in the readme
-- `python-ridge1`, `python-ridge2`, and `python-ridge3`: screen shots of the python LIME package showing the use of a ridge regression as the explainer
+- [laugel-lime-concept.png](figures/laugel-lime-concept.png) and [laugel-locality-metric](figures/laugel-locality-metric.png): figures from the Laugel et al. (2018) paper
+- [python-ridge1](figures/python-ridge1.png), [python-ridge2](figures/python-ridge2.png), and [python-ridge3](figures/python-ridge3.png): screen shots of the python LIME package showing the use of a ridge regression as the explainer
 
-**journals**
+[**journals**](journals)
 
@@
 
-- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
-- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
-- `02-understanding_lime`: explanation of LIME procedure
-- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
-- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
-- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
-- `06-literature_review`: notes on papers relating to LIME
-- `07-computation_issues`: documentation of some of the computation issues I ran into during the project
-- `08-logistic_regression`: examples of applying LIME to explain logistic regression models
-- `09-refitting-rtrees`: examples where I retrain the rtrees model with the "current" version of the training data and compare the results
+- [00-objectives_and_ideas](journals/00-objectives_and_ideas): background of the research project, goals of the project, concerns with LIME, and ideas to try
+- [01-hamby_data_and_models](journals/01-hamby_data_and_models)***: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
+- [02-understanding_lime](journals/02-understanding_lime): work done to understand the LIME algorithm
+- [03-applying_lime](journals/03-applying_lime)***: applications of LIME to the models fit to the Hamby data
+- [04-assessing_lime](journals/04-assessing_lime)***: visual diagnostics for assessing the lime explanations
+- [05-iris_comparison](journals/05-iris_comparison): applying LIME to a random forest fit to the iris data and assessing the explanations
+- [06-literature_review](journals/06-literature_review/): notes on papers relating to LIME
+- [07-computation_issues](journals/07-computation_issues/): documentation of some of the computation issues I ran into during the project
+- [08-logistic_regression](journals/08-logistic_regression): examples of applying and diagnosing LIME with logistic regression models fit to the sine data
+- [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data/): examples where I retrain the rtrees model with the "current" version of the training data and compare the results
+- [10-lime_hamby_variability](journals/10-lime_hamby_variability/): investigating variability between LIME explanations using diagnostic figures for random forest models trained on the Hamby bullet data
+
+*** **Note: We have realized that the training dataset for the `rtrees` model is not the one used in this file.
+See: [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data)**
+
+[**old-journals**](old-journals)
+
+Contain materials from my earliest research journals relating to the LIME project.
+It is likely that the code in these files will not run.
+However, the knit versions of the R markdown documents may still be useful.
 
@@
 
-- `.gitattributes`: attributes relating to git
-- `.gitignore`: files to ignore
-- `notes from Heike.pdf`: scans of notes written by Heike for this project
-- `README`: document containing to do list and contents of this repository
+- [.gitignore](.gitignore): files to ignore
+- [notes from Heike.pdf](notes from Heike.pdf): scans of notes written by Heike for this project
+- [README.md](README.md) and [README.Rmd](README.Rmd): this README and the R markdown document used to generate this README

### 2020-09-30 README.Rmd
small updates

@@
 - [01-hamby_data_and_models](journals/01-hamby_data_and_models)***: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
-- [02-understanding_lime](journals/02-understanding_lime): work done to understand the LIME algorithm
+- [02-understanding_lime](journals/02-understanding_lime)***: work done to understand the LIME algorithm
 - [03-applying_lime](journals/03-applying_lime)***: applications of LIME to the models fit to the Hamby data
@@
 - [06-literature_review](journals/06-literature_review/): notes on papers relating to LIME
-- [07-computation_issues](journals/07-computation_issues/): documentation of some of the computation issues I ran into during the project
+- [07-computation_issues](journals/07-computation_issues/)***: documentation of some of the computation issues I ran into during the project
 - [08-logistic_regression](journals/08-logistic_regression): examples of applying and diagnosing LIME with logistic regression models fit to the sine data
@@
 
-*** **Note: We have realized that the training dataset for the `rtrees` model is not the one used in this file.
-See: [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data)**
+*** **Note**: We have realized that the training dataset for the `rtrees` model is not the one used in these files.
+See [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data) for more details on the correct dataset.
+The correct data is used in the LIME diagnostics paper.
+For time reasons, the results in these journals have not been updated.
 

### 2020-09-30 README.Rmd
a few more small updates

@@
 
-This folder contains folders with research journals.
+Contains folders with research journals:
 
@@
 
-Contain materials from my earliest research journals relating to the LIME project.
+Contains materials from my earliest research journals relating to the LIME project.
 It is likely that the code in these files will not run.
-However, the knit versions of the R markdown documents may still be useful.
+However, the knit versions of the R markdown documents may still be useful, so I included them in the repository.
 
@@
 
-The documents contained in the top folder are as follows:
+Files contained in the main folder of the repository:
 

### 2020-09-30 old-journals/bullet data/01-objectives and background.Rmd
moved some files around a bit

--- 2019-03-06 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
@@
 ---
-title: "01-training and testing data"
+title: "Objectives and Background for Applying LIME to the Hamby Bullet Data"
 author: "Katherine Goode"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-output:
-  html_document:
-    toc: true
-    toc_depth: 3
-    toc_float: true
+date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
+output: html_document
 ---
 
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
-                      cache = TRUE)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = TRUE)
 ```
@@
 
-This journal includes a description of the Hamby study datasets, and the code that is used to clean the Hamby training and testing datasets.
+This journal explains the objectives of the project on applying LIME to the Hamby bullet data that is detailed in this series of journals.
+It also provides some background material on the study including a description of the Hamby data and the random forest model that was fit to the training portion of the Hamby data.
+References are provided that contain additional details on the Hamby data and the random forest model.
 
-```{r}
-# Load libraries
-library(tidyverse)
-library(plotly)
-library(randomForest)
-```
+# Objectives
 
-Both the training and the testing data will require the use of a vector of the names of the features used in the `rtrees` random forest included in the bulletr library.
-I create such a vector below to use in this journal.
+CSAFE is developing a predictive model that is able to match a bullet to the gun barrel that fired the bullet.
+They have acquired some sets of the data from the Hamby study.
+This data will be referred to as the Hamby data throughout this journal series.
+Part of this data was used to train a random forest model, and the remaining portion of the data will be used as a testing dataset.
+CSAFE would now like to understand the predictions made by the random forest to be able to provide a better explanation of how the model works to the firearm examiners.
+Thus, it is of interest to apply the LIME algorithm to the predictions made by the random forest model on the testing data to see which variables LIME suggests are driving the predictions.
+This journal series goes through the process of applying LIME to the predictions made by the random forest model and considering the results produced by LIME.
 
-```{r}
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(bulletr::rtrees$importance)
-```
+# Background
 
-# Description of the Hamby Data
+## Description of the Hamby Data
 
@@
 CSAFE aggregated the signatures from test sets 173 and 252 and left the signatures from test set 44 separate.
-Within these two groups, pairs of lands were evaluated to determine how similar the signatures from the two lands were.
+Within these two groups, pairs of lands were evaluated to determine how similar the signuatrues from the two lands were.
 This was done by measuring a set of variables they determined that would capture how alike the two signatures where.
@@
 Note that it was not possible to evaluate all pairs of lands due to tank rash on some of the lands.
-The data set created from the comparisons of test sets 173 and 252 will be referred to as `hamby173and252` throughout these journals.
-Hare, Hofmann, and Carriquiry used `hamby173and252` as a training data set to fit the random forest model `rtrees`.
-The data set created from the comparisons of test sets 44 will be referred to as `hamby44` and is not used in this research project.
+The next journal further explores and explains the number of comparisons that were done.
+The dataset created from the comparisons of test sets 173 and 252 will be referred to as `hamby173and252` throughout these journals, and the dataset created from the comparisons of test sets 44 will be referred to as `hamby44`.
 
-### Variable Definitions
+Hare, Hofmann, and Carriquiry used `hamby173and252` as a training dataset to fit a random forest model.
+The next section describes this model.
+The dataset `hamby44` has been used as a testing dataset by CSAFE.
+In this journal series, the features from `hamby44` will be input in the random forest to obtain predictions, and LIME will be applied to these predictions.
 
-The definitions of the variables...
+## Description of the Random Forest Model
 
-- ccf: 
-- cms:
-- D: 
-- matches: 
-- mismatches:
-- non_cms:
-- rough_cor: 
-- sd_D:
-- sum_peaks:
+The random forest model that was fit to the Hamby training dataset is discussed in the paper "Automatic Matching of Bullet Land Impressions" by E.
+Hare Et.
+Al.
+The model is available through the GitHub version of the `bulletr` package.
+The link to the GitHub repository for `bulletr` is https://github.com/CSAFE-ISU/bulletr.
 
-# Training Data
-
-This was originally a part of a journal entry that I wrote in my 'Case Studies with LIME' repository.
-I took the code that I used to clean the training dataset from that entry and updated it in this entry.
-It should still produce essentially the same dataset (with some possible changes to the level names of some of the barrels due to a 'factor' issue).
-The dataset that gets saved from this journal is the one that I am using for this research project.
-
-### The Raw Data
-
-The dataset loaded in below is the original Hamby 172 and 252 dataset that Heike gave to me.
-Note that when the `hamby173and252` dataset is read in, the studies called "Cary" are excluded.
-The data file contains rows based on bullet scans from a different study.
-These rows are no longer being included since Heike has found the study they came from to be poorly executed.
+The `bulletr` package is loaded below.
+The random forest model is stored in the package as a data object called `rtrees`.
+The paper does not include many details about the model fitting process, so I looked at some of the model features, which are printed below.
+These values told me that the model was fit using the predictive features of `ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks` with 300 trees and the parameter of `mtry` set to 3, which is the "number of variables randomly sampled as candidates at each split" as explained in the `randomforest` package documentation.
+This is the random forest model that will be used throughout this journal series.
 
 ```{r}
-# Load in the Hamby 173 and 252 dataset
-hamby173and252_raw <- read.csv("../../data/raw/features-hamby173and252.csv") %>%
-  filter(study1 != "Cary", study2 != "Cary") %>%
-  mutate(study1 = factor(study1), 
-         study2 = factor(study2))
+# Load the library
+library(bulletr)
+
+# Importance values from the random forest
+rtrees$importance
+
+# The number of trees used in the random forest
+rtrees$ntree
+
+# "Number of variables randomly sampled as candidates at each split"
+rtrees$mtry
 ```
-
-### Considering the Number of Rows in the Raw Data
-
-If we include symmetric comparisons, each set of test bullets should result in a dataset with
-  $$(35 \mbox{ bullets} \times 6 \mbox{ lands})^2=44100 \mbox{ rows},$$
-where a row would contain information on a pair of lands. If we do not include the symmetric comparisons, then the dataset should have
-  $$\frac{(44100 \mbox{ rows} - (35 \mbox{ bullets} \times 6))}{2} + (35 \mbox{ bullets} \times 6) = 22155 \mbox{ rows}.$$
-However, when I looked at the dimension of the datasets, neither of these seem to be the case.
-See the R code and output below.
-Note that `hamby173` is currently incorrectly labelled as `hamby44`.
-Both test sets have less than but close to 22,155 rows.
-This suggests that these do not include symmetric comparisons.
-When I checked with Heike, she confirmed that this is the case.
-This table also shows that there are comparisons across `hamby173` and `hamby252`.
-These missing observations will be explored more in the next section.
-
-```{r}
-# Summary of the number of observations in the Hamby173and252 datase
-table(hamby173and252_raw$study1, hamby173and252_raw$study2)
-```
-
-### Understanding the Missing Observations
-
-The plot below considers the number of observations within a barrel and bullet comparison from all known cases in the Hamby 173 and 252 data.
-We can see that the observations on the lower diagonals are missing in all cases which confirms that the symmetric comparisons were not included in the data.
-Additionally, a handful of cases have less than 36 observations.
-For the comparisons within the Hamby 173 or Hamby 252 study, the cells on the diagonals are less than 36, because none of the repeats from the symmetric comparisons of lands are included.
-The cells above the diagonal with less than 36 observations are missing some observations due to tank rash.
-For the comparisons across studies, the cases with less than expected are also due to tank rash.
-For some reason, the comparisons between bullets 1 from Hamby 173 and Hamby 252, the cells are being colored grey even though they have 36 observations.
-I am not sure why this is...
-
-```{r}
-# Create the plot to look at number of comparisons within the known bullets
-countplot <- hamby173and252_raw %>%
-  filter(barrel1 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
-         barrel2 %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>%
-  group_by(study1, study2, barrel1, barrel2, bullet1, bullet2) %>%
-  summarise(count = n()) %>%
-  ggplot(aes(x = barrel1, y = barrel2)) +
-  geom_tile(aes(fill = count)) + 
-  facet_grid(study1 + bullet1 ~ study2 + bullet2, scales = "free") +
-  theme_minimal() + 
-  scale_fill_distiller(palette = "GnBu", direction = 1)
-
-# Make the plot interactive
-ggplotly(countplot, width = 800, height = 700) %>%
-  shiny::div(align = "center")
-```
-
-### Cleaning the Trainng Data
-
-The code below cleans the training data. The cleaning involves:
-
-- correcting the study 173 labels
-- adjusting the bullet and barrel values for the unknowns
-- renaming the match variable as samesource
-- selecting the desired variables
-
-```{r}
-# Determine the letters associated with the unknown bullets
-letters <- levels(hamby173and252_raw$barrel1)[11:length(levels(hamby173and252_raw$barrel1))]
-
-# Cleaning the testing data
-hamby173and252_train_cleaning <- hamby173and252_raw %>%
-  mutate(study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
-         study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
-         bullet1 = factor(ifelse(barrel1 %in% letters,
-                                 as.character(barrel1),
-                                 as.character(bullet1))),
-         barrel1 = factor(ifelse(barrel1 %in% letters, 
-                                 as.character("Unknown"), 
-                                 as.character(barrel1))),
-         bullet2 = factor(ifelse(barrel2 %in% letters,
-                                 as.character(barrel2),
-                                 as.character(bullet2))),
-         barrel2 = factor(ifelse(barrel2 %in% letters, 
-                                 as.character("Unknown"), 
-                                 as.character(barrel2))),
-         land1 = factor(land1),
-         land2 = factor(land2),
-         rfscore = predict(bulletr::rtrees, hamby173and252_raw %>%
-                             select(rf_features), 
-                           type = "prob")[,2]) %>%
-  rename(samesource = match) %>%
-  select(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2,
-         rf_features, samesource, rfscore)
-```
-
-### Removing Bullets with Tank Rash
-
-I discovered that the number of rtrees predictions does not match the length of my training data. I need to ask Heike about this.
-
-```{r}
-# Compare the dimensions of my training data and the number of predictions from rtrees
-dim(hamby173and252_train_cleaning)
-dim(predict(bulletr::rtrees, type = "prob"))
-```
-
-When I talked to Heike about this, she told me that this training dataset probably still contains the four land impressions that had tank ranks and were removed before `rtrees` was fit.
-When I looked in Eric's paper, it said that the lands that were removed were the following four:
-
-- barrel 6 bullet 2-1
-- barrel 9 bullet 2-4
-- unknown bullet B-2
-- unknown bullet Q-4
-
-The code below removes any comparisons from the testing data that include one of these lands.
-
-```{r}
-# Remove the comparisons involving the four lands with tank rash
-hamby173and252_train <- hamby173and252_train_cleaning %>%
-  mutate(bbl1 = barrel1:bullet1:land1,
-         bbl2 = barrel2:bullet2:land2) %>%
-  filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4") | 
-           bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2", "Unknown:Q:4"))) %>%
-  select(-bbl1, -bbl2)
-```
-
-When I look at the dimensions of my training data now and the number of predictions from `rtrees`, then agree now!
-
-```{r}
-# Compare the dimensions of my further cleaned training data and the
-# number of predictions from rtrees
-dim(hamby173and252_train)
-dim(predict(bulletr::rtrees, type = "prob"))
-```
-
-It is possible that the labels that Eric was using are different from the labels in my training dataset.
-In order to check whether I removed the correct datapoints, Heike suggested that I look at a parallel coordinate plots to see if the observations that were removed stand out as being unusual compared to the rest of the data.
-The code below prepares the training data before observations were removed to be plotted.
-
-```{r}
-# Create dataset for creating the paralle coordinate plot
-par_data <- hamby173and252_train_cleaning %>%
-  mutate(bbl1 = barrel1:bullet1:land1,
-         bbl2 = barrel2:bullet2:land2) %>%
-  mutate(category = factor(ifelse(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
-                                                "Unknown:Q:4") | 
-                                      bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
-                                                  "Unknown:Q:4")),
-                           "keep", "remove"))) %>%
-  arrange(category) %>%
-  mutate(samesource_colors = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.05), 
-                                    rgb(0, 0, 0, alpha = 0.001)),
-         samesource_colors2 = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.001), 
-                                    rgb(0, 0, 0, alpha = 0.01)),
-         tankrash_colors = ifelse(category == "keep", rgb(0, 0, 1, alpha = 0.05),
-                                  rgb(0, 0, 0, alpha = 0.01)))
-```
-
-The first plot shows the observations that were kept in black and the observations that were removed in blue.
-These observations do not stand out to me.
-It is not clear if these were the ones that were suppose to be removed or not.
-The second plot shows the observations from matches plotted in red, and the third plot shows the observations from nonmatches plotted in black.
-
-```{r}
-MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$tankrash_colors)
-MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors)
-MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors2)
-```
-
-### Saving the Training Data
-
-The cleaned data is saved and used as the training dataset for the rest of this research project.
-
-```{r}
-# Save the datasets and response variables as .csv files
-write.csv(hamby173and252_train, "../../data/hamby173and252_train.csv", row.names = FALSE)
-```
-
-# Testing Data
-
-### The Raw Data
-
-The original data files given to me by Heike are loaded in below. For now, we are working with only sets 1 and 11 from the Hamby 224 study. She may provide me with more in the future.
-
-```{r}
-# Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("../../data/raw/h224-set1-features.rds")
-hamby224_set11 <- readRDS("../../data/raw/h224-set11-features.rds")
-```
-
-### Cleaning the Testing Data
-
-The code below cleans the data from both sets 1 and 11. This involves:
-
-- selecting the desired variables
-- renaming the bullet and land variables
-- creating study and set variables
-- re-coding the bullet and land names
-
-```{r}
-# Clean the Hamby 224 set 1 data
-hamby224_set1_cleaned <- hamby224_set1 %>%
-  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-  rename(bullet1 = bulletA,
-         bullet2 = bulletB, 
-         land1 = landA,
-         land2 = landB) %>%
-  mutate(study = factor("Hamby 224"), 
-         set = factor("Set 1"),
-         bullet1 = recode(factor(bullet1), 
-                          "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-         bullet2 = recode(factor(bullet2), 
-                          "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
-         land1 = recode(factor(land1), 
-                        "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
-                        "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
-         land2 = recode(factor(land2), 
-                        "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
-                        "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
-  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
-
-# Clean the Hamby 224 set 11 data
-hamby224_set11_cleaned <- hamby224_set11 %>%
-  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
-  rename(bullet1 = bulletA,
-         bullet2 = bulletB, 
-         land1 = landA,
-         land2 = landB) %>%
-  mutate(study = factor("Hamby 224"), 
-         set = factor("Set 11"),
-         bullet1 = recode(factor(bullet1), 
-                          "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
-                          "Bullet I" = "Questioned"),
-         bullet2 = recode(factor(bullet2), 
-                          "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
-                          "Bullet I" = "Questioned")) %>%
-  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
-```
-
-The cleaned data from sets 1 and 11 are combined below into the testing dataset. Rows are added for the missing comparisons from the Hamby 224 study, and some additional cleaning is done.
-
-```{r}
-# Create a dataset with all combinations of lands and bullets comparisons for each set
-combinations <- data.frame(set = factor(rep(c("Set 1", "Set 11"), each = 324)),
-                    expand.grid(land1 = factor(c("Land 1", "Land 2", "Land 3", 
-                                                 "Land 4", "Land 5", "Land 6")),
-                                land2 = factor(c("Land 1", "Land 2", "Land 3", 
-                                                 "Land 4", "Land 5", "Land 6")),
-                                bullet1 = factor(c("Known 1", "Known 2", "Questioned")),
-                                bullet2 = factor(c("Known 1", "Known 2", "Questioned"))))
-
-# Join the two cleaned Hamby 224 sets into one testing set
-hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
-                                            hamby224_set11_cleaned)) %>%
-  mutate(set = factor(set),
-         bullet1 = factor(bullet1),
-         bullet2 = factor(bullet2),
-         land1 = factor(land1),
-         land2 = factor(land2)) %>%
-  right_join(combinations, by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
-  filter(!(bullet1 == "Questioned" & bullet2 == "Known 1"),
-         !(bullet1 == "Questioned" & bullet2 == "Known 2"),
-         !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
-  arrange(rfscore) %>%
-  mutate(case = factor(1:length(study))) %>%
-  select(case, study:samesource)
-```
-
-### Saving the Testing Data
-
-The testing data file is saved below.
-
-```{r}
-# Save the test data as a .csv file
-write.csv(hamby224_test, "../../data/hamby224_test.csv", row.names = FALSE)
-```
-
-# Session Info
-
-```{r}
-sessionInfo()
-```

### 2020-09-30 old-journals/bullet data/04-LIME results.Rmd
moved some files around a bit

---
title: "Results from LIME Applied to the Bullet Data"
author: "Katherine Goode"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE, eval = TRUE)
```

# Overview

This document explores the explanations resulting from the `lime` R package applied to the bullet data. Different visualizations are made in an attempt to be able to comprehend the many explanations created.

The following R libraries will be used.

\vspace{0.25cm}

```{r}
# Load libraries
library(tidyverse)
library(lime)
library(randomForest)
library(bulletr)
```

# Comparisons within `hamby44` of Barrel 1 and Barrel 2

For now, only explanations have been made on the comparisons between the lands from barrel 1 and barrel 2 in the `hamby44` test data.

## Combining the Data and Explanations

The code below reads in the subset of the test data and the LIME explanations that accompany the data, and they are joined into one data frame. Additionally, variable types are adjusted as need be, and some additional variables are added. These new variables are the interaction between barrel and bullet, which will be used for plotting, and my own computation of the random forest prediction score from `rtrees` to compare with the one in the data frame that I was given.

\vspace{0.25cm}

```{r}
# Load in the test data and explanations for barrels 1 and 2
hamby_test_barrels1and2 <- read.csv("../data/hamby_test_barrels1and2.csv")
hamby_explain_barrels1and2 <- readRDS("../data/hamby_explain_barrels1and2.rds")

# Add a case variable to the test data
hamby_test_barrels1and2 <- hamby_test_barrels1and2 %>%
  mutate(case = as.character(1:dim(hamby_test_barrels1and2)[1])) %>%
  select(case, study1:samesource)

# Create a vector of the random forest features to be included
rf_features <- c("ccf", "rough_cor", "D", "sd_D", "matches", 
                 "mismatches", "cms", "non_cms", "sum_peaks")

# Join the data and the explanations and edit and add additional variables
hamby_barrels1and2 <- full_join(hamby_test_barrels1and2, hamby_explain_barrels1and2, 
                                by = "case") %>%
  mutate(case = factor(case),
         barrel1 = factor(barrel1),
         bullet1 = factor(bullet1),
         land1 = factor(land1),
         barrel2 = factor(barrel2),
         bullet2 = factor(bullet2),
         land2 = factor(land2)) %>%
  mutate(barrelbullet1 = barrel1:bullet1, 
         barrelbullet2 = barrel2:bullet2, 
         mypred = rep(predict(rtrees, hamby_test_barrels1and2 %>% select(rf_features), 
                                type = "prob")[,2], each = 3)) %>%
  select(case:bullet1, barrelbullet1, land1:bullet2, barrelbullet2, land2:rfscore, 
         mypred, samesource:prediction)

# The structure of the joined data
str(hamby_barrels1and2 %>% select(-c(prediction, data)))
```

## Plotting the Data and Explanations

### Plot of $R^2$ from LIME Local Models

Before looking at the plots of the explanations, first consider the $R^2$ values for the local models fit by `lime`. The plot below shows the $R^2$ value for the local models fit for each of the land to land comparisons. The plot shows that the $R^2$ values are pretty low. This is an indicator that some of the default settings in `lime` should be adjusted to improve the local model fit. For example, the kernel width could be decreased to try to make the fit more local.

\vspace{0.25cm}

```{r}
# Plot of r2 values
hamby_barrels1and2 %>%
  select(case, land1, land2, barrelbullet1, barrelbullet2, model_r2) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = model_r2)) + 
  facet_grid(barrelbullet1 ~ barrelbullet2) + 
  theme_bw()
```

### Feature Plots Produced by `lime`

The plots below shows the explanations produced by `lime` for the first eight cases in the `hamby_test_barrels1and2` dataset.

\vspace{0.25cm}

```{r}
cases_of_interest <- hamby_test_barrels1and2 %>%
  filter(barrel1 == barrel2, bullet1 != bullet2, land1 == land2) %>%
  pull(case)

plot_features(hamby_explain_barrels1and2[1:12,])
plot_features(hamby_explain_barrels1and2[13:24,])
```

### Plots of Random Forest Prediction Probabilities

The plots below show the random forest score from the original data, my computed random forest score, 1 minus the label probability from `lime`, the model prediction probability from `lime`, and the same source variable from the original data for the comparisons of lands between barrel 1 and barrel 2. The plot with my calculated prediction probabilities matches the random forest score from the data given to me. However, they do not agree with the probability output by `lime`, the label probabilities, or the `samesource` variable. I will need to look more into this. Note that the `samesource` variable is incorrect, so that plot should be ignored.

\vspace{0.25cm}

```{r}
# Plot of the random forest score already in the data
ggplot(hamby_barrels1and2, aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = rfscore)) +
  facet_grid(barrelbullet1 ~ barrelbullet2) +
  theme_bw()

# Plot of the random forest score calculated by myself
ggplot(hamby_barrels1and2, aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = mypred)) + 
  facet_grid(barrelbullet1 ~ barrelbullet2) + 
  theme_bw()

# Plot of the random forest score calculated by lime
ggplot(hamby_barrels1and2, aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = 1 - label_prob)) + 
  facet_grid(barrelbullet1 ~ barrelbullet2) + 
  theme_bw()

# Plot of the prediction probability calculated by the simple model in lime
ggplot(hamby_barrels1and2, aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = model_prediction)) + 
  facet_grid(barrelbullet1 ~ barrelbullet2) + 
  theme_bw()

# Plot of the samesource variable
ggplot(hamby_barrels1and2, aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = samesource)) + 
  facet_grid(barrelbullet1 ~ barrelbullet2) + 
  theme_bw()
```

\vspace{0.25cm}

Below are computations to check how similar the prediction probabilities are. These varify the claims I made above after looking at the plots.

\vspace{0.25cm}

```{r}
# Comparing the random forest score and my calculated probability
sum(hamby_barrels1and2$rfscore - hamby_barrels1and2$mypred)

# Comparing the random forest score and 1 minus the lime label probability
sum(hamby_barrels1and2$rfscore - (1 - hamby_barrels1and2$label_prob))

# Comparing the random forest score and the lime model prediction
sum(hamby_barrels1and2$rfscore - hamby_barrels1and2$model_prediction)
```

### Plots of LIME Explanations

Below is a plot created by `lime` that shows all of the explanations for the comparisons between barrel 1 and barrel 2.

\vspace{0.25cm}

```{r}
lime::plot_explanations(hamby_explain_barrels1and2)
```

\vspace{0.25cm}

I tried to recreate the above plot myself. This plot is shown below.

\vspace{0.25cm}

```{r}
ggplot(hamby_barrels1and2, aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(. ~ label)
```

\vspace{0.25cm}

I also created a plot that only includes the maximum absolute value of the feature weight within a case.

\vspace{0.25cm}

```{r}
hamby_barrels1and2_max <- hamby_barrels1and2 %>%
  group_by(case) %>%
  filter(row_number(feature_weight) == n())

ggplot(hamby_barrels1and2_max, aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(. ~ label)
```

\vspace{0.25cm}

I also wanted to try improving the plot by faceting by the features. This plot is included below.

\vspace{0.25cm}

```{r}
ggplot(hamby_barrels1and2, aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free")
```

\vspace{0.25cm}

The plots below separate the above plot so that each plot only contains the explanations within a barrel to barrel comparison.

\vspace{0.25cm}

```{r}
hamby_barrels1and2 %>%
  filter(barrel1 == "1", barrel2 == "1") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90))

hamby_barrels1and2 %>%
  filter(barrel1 == "1", barrel2 == "2") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90))

hamby_barrels1and2 %>%
  filter(barrel1 == "2", barrel2 == "1") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90))

hamby_barrels1and2 %>%
  filter(barrel1 == "2", barrel2 == "2") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r include = FALSE, eval = FALSE}
characters <- strsplit(hamby_barrels1and2$feature_desc, " ")
mymax <- characters %>% lapply(length) %>% unlist %>% max
new_characters <- characters %>% lapply(function(x) c(x, rep(NA, mymax-length(x))))
as.data.frame(matrix(unlist(new_characters), ncol = 5, byrow = TRUE))
```

```{r include = FALSE, eval = FALSE}
## OLD CODE

# Load in the LIME explanations
hamby_explain5000 <- readRDS("../data/hamby_explain5000.rds")

lime::plot_features(hamby_explain5000[1:(4*2),])
lime::plot_explanations(hamby_explain5000)

ggplot(hamby_explain5000, aes(x = feature_value, y = feature_weight)) +
  geom_point() + 
  facet_grid(feature ~ .)

# Need to create a variable for the truth
# ggplot(hamby_explain5000, aes(x = feature_value, y = feature_weight)) +
#   geom_point(aes(color = truth)) + 
#   facet_grid(feature ~ .)

# ggplot(hamby_explain5000, aes(x = feature_weight)) +
#   geom_histogram(bins = 30, aes(fill = truth)) + 
#   facet_grid(feature ~ truth)

ggplot(hamby_explain5000, aes(x = case, y = feature_weight)) +
  geom_point(aes(color = feature))

ggplot(hamby_explain5000, aes(x = case, y = feature_weight)) +
  geom_point(aes(color = feature))

ggplot(hamby_explain5000, aes(x = case, y = abs(feature_weight))) +
  geom_point(aes(color = feature))

# Compute the number of cases explained
(num_cases <- dim(hamby_explain5000)[1] / 2)

# Subset the data to only have the rows with the maximum feature weight for
# each case
hamby_explain5000_max <- hamby_explain5000 %>%
  group_by(case) %>%
  top_n(1, feature_weight)

# Change feature to a factor variable
hamby_explain5000_max$feature <- as.factor(hamby_explain5000_max$feature)

# Check to make sure the number of cases in this new dataset are the same as
# the original
length(unique(hamby_explain5000_max$case))

# Create a dataset with only the rows for largest feature weights for each
# of the cases
hamby_explain5000_max <- hamby_explain5000_max %>%
  arrange(by = feature_weight)

# Number of times each feature is the top explanation
summary(hamby_explain5000_max$feature)

ggplot(hamby_explain5000_max, aes(x = case, y = feature_weight)) +
  geom_point(aes(color = feature))

# ggplot(hamby_explain5000_max, aes(x = case, y = feature_weight)) +
#   geom_point(aes(color = feature)) +
#   facet_grid(truth ~ .)

# ggplot(hamby_explain5000_max, aes(x = feature_value, y = feature_weight)) +
#   geom_point(aes(color = truth), alpha = 0.5) +
#   facet_grid(feature ~ truth)
```

### 2020-09-30 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
final clean up before making repo public

@@
 
-- turn repetitive code into functions
-- try out different weights
-- change distance matrix in seriation to be 5-# of variables shared between two rows
-- try using distance matrix computed on the feature value with seriation
 - add in feature selection methods to LIME input options
@@
 - compare the simple models based on different number of bins using an F-test
-- look into computing a diversity or consistency measure for the sensitivity analysis
 - include a penalty for the number of parameters when choosing bins
@@
 coloring them by variables suggested to be important by lime
-- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
-- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)
+- could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable
+- come up with a test to compare between global and local explanations
 
@@
   - does lime find the local models?
-- edit details in understanding LIME journal
-- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
 - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
-- assess lime results on logistic regression models
 - try reticulate R package to apply python version of lime
@@
 
-### Possible Papers
-
-Here are ideas for possible papers.
-
-**Statistical Paper Presenting Visual Diagnostic Tools for LIME**
-
-This paper would assess the explainations produced by LIME. It would introduce some visual diagnostics for LIME to assess its performance. Key points that will be made:
-
-1. Explainer model is really bad (probably due to the binning)
-2. Local explanations at not local
-
-**Statistical Paper Assessing LIME**
-
-This paper would be an explanation of how the application of LIME to the Hamby bullet data can help firearm examiners understand the random forest model predictions.
-When we first applied LIME to the bullet matching dataset, we found that the explanations were not as good as we wanted them to be.
-This has led us to try to understand why the LIME algorithm is not working well.
-We even tried some new sampling methods to improve the algorithm.
-They made a bit of improvement, but the improvements could be much better.
-This paper could discuss isusses we found with the current LIME algorithm, describe our proposed approaches, and compare the results.
-
-**Firearm Examiner's Paper**
-
-CSAFE is developing a predictive model that is able to match a bullet to the gun barrel that fired the bullet.
-They have acquired some sets of the data from the Hamby study.
-Part of this data was used to train a random forest model (`rtrees`), and the remaining portion of the data will be used as a testing dataset.
-CSAFE would now like to understand the predictions made by the random forest to be able to provide a better explanation of how the model works to the firearm examiners.
-Thus, it is of interest to apply the LIME algorithm to the predictions made by the random forest model on the testing data to see which variables LIME suggests are driving individual predictions.
-
 # Concerns

### 2020-09-30 journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.Rmd
final clean up before making repo public

--- 2020-09-29 journals/09-identifying_rtrees_training_rdata/09-identifying_rtrees_training_data.Rmd
@@
 
-```{r fig.width = 10, fig.height = 3}
+```{r}
 bind_rows(
@@
   ggplot(aes(x = value, fill = dataset)) + 
-  geom_histogram() +
-  facet_grid(dataset ~ name)
+  geom_histogram(position = "dodge") +
+  facet_wrap(. ~ name, scales = "free") + 
+  theme(legend.position = "bottom")
 ```
@@
     dataset = c(
-      rep("internal", length(rtrees_pred)),
+      rep("Internal (OOB)", length(rtrees_pred)),
       rep("Hamby comparisons", length(hc_pred)),
@@
     pivot_wider(names_from = "dataset", values_from = "pred") %>%
-    ggplot(aes(x = `Hamby comparisons`, y = internal)) +
+    ggplot(aes(x = `Hamby comparisons`, y = `Internal (OOB)`)) +
     geom_point() + 
@@
     pivot_wider(names_from = "dataset", values_from = "pred") %>%
-    ggplot(aes(x = `CCFs with lands`, y = internal)) +
+    ggplot(aes(x = `CCFs with lands`, y = `Internal (OOB)`)) +
     geom_point() + 
@@
   geom_vline(data = rtrees_values,
-             mapping = aes(xintercept = class_error_true, color = model))
+             mapping = aes(xintercept = class_error_true, color = model)) + 
+    labs(title = "Models Trained on Hamby Comparison Data")
 
@@
   geom_vline(data = rtrees_values,
-             mapping = aes(xintercept = class_error_false, color = model))
+             mapping = aes(xintercept = class_error_false, color = model)) + 
+    labs(title = "Models Trained on Hamby Comparison Data")
 
@@
   geom_vline(data = rtrees_values,
-             mapping = aes(xintercept = class_error_true, color = model))
+             mapping = aes(xintercept = class_error_true, color = model)) +
+  labs(title = "Models Trained on CCFs with Lands Data")
 
@@
   geom_vline(data = rtrees_values,
-             mapping = aes(xintercept = class_error_false, color = model))
+             mapping = aes(xintercept = class_error_false, color = model)) +
+  labs(title = "Models Trained on CCFs with Lands Data")
 
 plot_grid(hist_true_hc, hist_false_hc, hist_true_ccfwl, hist_false_ccfwl)
+```
+
+Plots of true versus false class errors:
+
+```{r fig.width = 10, fig.height = 4.5}
+plot_grid(
+  ggplot() +
+    geom_point(data = hamby_comparison_confus, aes(x = class_error_FALSE, y = class_error_TRUE)) +
+    geom_point(
+      data = rtrees_values,
+      aes(x = class_error_false, y = class_error_true, color = model)
+    ) + 
+    labs(title = "Models Trained on Hamby Comparison Data") + 
+    theme(legend.position = "bottom"),
+  ggplot() +
+    geom_point(data = CCFs_withlands_confus, aes(x = class_error_FALSE, y = class_error_TRUE)) +
+    geom_point(
+      data = rtrees_values,
+      aes(x = class_error_false, y = class_error_true, color = model)
+    ) + 
+    labs(title = "Models Trained on CCFs with Lands Data") + 
+    theme(legend.position = "bottom")
+)
 ```
@@
     labs(
-      x = "Random Forest Model", 
+      x = "Feature Importance Rank",
       y = "Feature", 
@@
     theme_bw() +
-    labs(x = "Random Forest Model",
+    labs(x = "Feature Importance Rank",
          y = "Feature",

### 2020-09-30 journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.Rmd
last few small changes

@@
 
-Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons`:
+Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons` (Heike identified that Hamby173-Br3-B2-L1 has damage on the bullet, but she is not sure why Hamby173-BrUnk-BM-L4 was left out):
 
@@
 
-Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands`:
+Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands` (Heike confirmed that bullet E is known to have issues):
 

### 2020-10-07 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
moved ideas to other journal

@@
 
-**Explainer Models**
-
-- read through papers giving an overview of the current explanation methods
-- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
-- look more into Molnar and his adviser Bernd
-- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
-
 **Understanding LIME**
@@
 
-**Simulation with RF**
-
-- think about how to implement a simulation with a random forest
-- look back at 601 notes from Kaiser for model assessment
-- look at Hadley's 'removing the blindfold' for ideas
-- read book Dr. Dixon lent me on sensitivity analyses
-
-**Random Forests Confidence Intervals**
-
-- look into papers by Giles Hooker and Lucas Mentch
-- Dr. Nettleton paper
-
-**Random Forest Interpretations**
-
-- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/
-
 # Concerns

### 2020-12-16 journals/11-gower_exponent_examples/11-gower-exponent-examples.Rmd
added some journals for understanding the gower exponent

---
title: "Gower Exponent Examples"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: cerulean
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This document contains an example that demonstrates the effect an exponent has on the similarity computation between a prediction of interest and another observation.

```{r}
# Load libraries
library(dplyr)
library(ggplot2)
library(tidyr)
```

In the *lime* R package, the similarity between the prediction of interest (*poi*) and another observation (*obs*) is computed as:

> 1 - (Gower distance(*poi*, *obs*)^(exponent))

where the "exponent" is specified by the user.

The code below creates an example dataset that computes similarities based on various exponents from the same distances.

```{r}
# Prepare an example dataset
dist_data <-
  data.frame(distance = seq(0, 1, length.out = 100)) %>%
  mutate(
    sim0.1 = 1 - ((distance) ^ 0.1),
    sim0.25 = 1 - ((distance) ^ 0.25),
    sim0.5 = 1 - ((distance) ^ 0.5),
    sim1 = 1 - ((distance) ^ 1),
    sim10 = 1 - ((distance) ^ 10),
    sim15 = 1 - ((distance) ^ 15),
    sim5 = 1 - ((distance) ^ 5)
  ) %>%
  pivot_longer(names_to = "exponent",
               values_to = "similarity",
               cols = -distance) %>%
  mutate(exponent = stringr::str_remove(exponent, "sim")) %>%
  mutate(exponent = factor(
    exponent,
    levels = c("0.1", "0.25", "0.5", "1", "5", "10", "15")
  ))

# Print the head of the data
head(dist_data)
```

The plot below shows the relationship between similarity and distance when different exponents are used. Note that the smallest exponent of 0.1 creates a more local region than the larger exponents.

```{r}
ggplot(dist_data, aes(x = distance, y = similarity, color = exponent)) +
  geom_line() +
  viridis::scale_color_viridis(option = "inferno", discrete = T)
```

### 2020-12-16 README.Rmd
added headers
final clean up before making repo public
last few small changes
updated readme

@@
 
-Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository. For easy viewing of the journals, use these links:
+Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository.
+
+Descriptions of the work done can be found in the journals. Beware of typos in the journals. Not all of them have been proof read. For easy viewing of the journals, use these links:
 
@@
 10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)
+11. [Gower Exponent Examples](https://goodekat.github.io/LIME-research-journals/journals/11-gower-exponent-examples/11-gower-exponent-examples.html)
 
@@
 
-[**code**](code/)
+#### [**code**](code/)
 
@@
 
-[**figures**](figures)
+#### [**figures**](figures)
 
@@
 
-[**journals**](journals)
+#### [**journals**](journals)
 
@@
 
-[**old-journals**](old-journals)
+#### [**old-journals**](old-journals)
 
@@
 
-**main**
+#### **main**
 
